### 2017-09-13 parallel-tractability-J-v8/parallel-tractability-J.tex
The source codes of tex
The main tex file is "parallel-tractability-J.tex".

%\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
 \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
\usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}

\usepackage{amsmath}

\usepackage{CJK}
\usepackage{color}

\usepackage{enumitem}
\usepackage{rotating}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

%\journal{Nuclear Physics B}

\hyphenation{data-log}

\begin{document}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Parallel Tractability of Ontology\\
Materialization: Technique and Practice}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{}

\address{}

\begin{abstract}
Materialization is an important reasoning service for applications built
on the ontology languages, such as OWL. With a
rapid growth of semantic data, it is challenging to perform
materialization on large-scale ontologies efficiently.
Current work proposes parallel algorithms and employs computing
platforms of high-performance to make materialization sufficiently efficient and scalable in practice.
However, there do exist ontologies, for which
materialization cannot always be improved by parallelism (we use experiments to show it in Section~\ref{sec:evaluation}).
On the other hand, some well-known large-scale ontologies, such as YAGO, have been shown to have
good performance for parallel reasoning, but they are expressed in ontology languages
that are not parallelly tractable in theory, i.e., the efficiency of reasoning may not be improved
on a parallel implementation.
This motivates us to study the problem of \emph{parallel tractability} of ontology
materialization from a theoretical perspective.
That is, we aim to identify the ontologies for which materialization is
parallelly tractable, i.e., in \texttt{NC} complexity.
The results of the parallel tractability can be further used to optimize
materialization algorithms and to guide ontology engineers in creating parallelly tractable ontologies.

In this work, we focus on datalog rewritable ontology languages.
We propose some algorithms, called \texttt{NC} algorithms, to identify several classes of datalog rewritable
ontologies (called \emph{parallelly tractable classes})
such that materialization over them is parallelly tractable.
We then investigate the parallel tractability of materialization over
two datalog rewritable ontology languages DL-Lite and DHL (\emph{Description Horn Logic}).
We show that materialization over any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ is parallelly tractable.
For DHL, there exist ontologies where materialization can hardly be parallelized.
We propose to restrict the usage of DHL such that the restricted ontologies are parallelly tractable.
We further extend the results to an extension of DHL that also allows \emph{complex role inclusion axioms}.
To verify the practical usability of the above results, we analyze real-world datasets and show
that many ontologies expressed in DHL or its extension belong to
the parallelly tractable classes. Based on the results of parallel tractability,
we further implement an optimized parallel algorithm
and compare it to the state-of-the-art reasoner RDFox. The experimental results show that the
optimization used in our implementation results in a better
performance on parallelly tractable ontologies compared with RDFox.
\end{abstract}

\begin{keyword}
ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
\end{keyword}

\end{frontmatter}

%% \linenumbers

\section{Introduction}
\label{sec:introduction}

The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
is an important standard for ontology language in the Semantic Web and knowledge-based applications.
In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
are being generated at an increasing pace by sensor networks, government authorities and social
media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.

There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms 
for the ontology language RDFS and its extended
fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.

The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
improved on a parallel implementation. A possible reason of the high performance of parallel
reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
for which parallel tractability can be guaranteed theoretically.

According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
This complexity class consists of problems that can be solved efficiently in parallel.
To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
in parallel computation \cite{Raymond95}.
An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
However, current materialization algorithms of datalog rewritable ontology languages
(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
Thus, we first give \texttt{NC} algorithms that perform materialization,
and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
we also discuss how to optimize and implement them.

In the practical part of this work, we study specific datalog rewritable ontology languages.
We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
to study the parallel tractability of ontology materialization.
We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
proposed restrictions belong to the parallelly tractable classes.
We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
We compare our system to the state-of-the-art reasoner RDFox.
The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
tractable ontologies compared with RDFox.

The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
In Section~\ref{sec:practicalAlg},
we discuss how to optimize and implement the given \texttt{NC} algorithms.
We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.

\section{Background Knowledge}
\label{sec:background}

In this section, we introduce some basic notions that are needed to introduce our approach.

\subsection{Datalog}

We discuss the main issues in this paper using standard datalog notions.
In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
constants, then $A$ is called a \emph{ground atom}.
A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
A datalog program $P$ consists of rules and facts.
A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
if each defined $A\theta$ is a ground atom.
A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
the terms in this rule with respect to a finite set of constants occurring in $P$.
Furthermore the ground instantiation of $P$, denoted by $P^*$,
consists of all ground instantiations of rules in $P$.
The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
while the predicates that may occur as head atoms are called \emph{IDB predicates}.

\subsection{DHL and DL-Lite}

In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
to denote three disjoint countably
infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
where $R^-$ is the \emph{inverse role} of $R$.
For ease of discussion, we focus on the \emph{simple forms} of axioms shown
in the left column of Table~1. These simple forms can be obtained by using
well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.

DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
intersection of description logic (DL) and datalog in terms of expressivity.
We define a DHL ontology $\mathcal{O}$ as a triple:
$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
are roles in $\textbf{R}$.
For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
equivalent form $\exists R^-.A\sqsubseteq B$.

DHL is related with other ontology languages.
First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
disallowing \emph{nominal}, \emph{number restriction} and
right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
and, thus, is not parallelly tractable.
However, by applying some simplifications and restrictions, RDFS ontologies can be
expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
materialization.

\begin{table}
\begin{center}
\begin{tabular}{lcc}
\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
\hline
&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
\hline
\hline
(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\

\hline
(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\

\hline
(A1)& $A(a)$& $A(a)$\\
(A2)& $R(a,b)$& $R(a,b)$\\
\hline
\end{tabular}
\label{tab:dhl}
\end{center}
\end{table}

In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
naturally transformed to datalog rules.
In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
that allows complex RIAs. Since a complex RIA can be transformed to
several axioms of the form (R4), we then require that an
RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
axioms of the forms (R1-R4). Note that (R3) is actually a special
case of (R4).

DL-Lite is a group of ontology languages designed for highly-efficient
query answering through knowledge
and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
in DL-Lite.
DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
an ABox contains \emph{assertions} of the forms (A1) and (A2), and
RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
which allows involving RBoxes that contain axioms of the forms (R1-R2).
If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
in the following paragraphs}.

\subsection{Ontology Materialization via Datalog Programs}

An ontology
expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
(see the corresponding rules in the right column of Table~1).
Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.

In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
notion of \emph{simple role}, which is initially proposed to restrict the
usage of highly expressive ontology languages \cite{HorrocksS04}.
Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.

Based on the above representations, ontology materialization
corresponds to the evaluation of datalog programs.
Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
 $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.

\subsection{The $\texttt{NC}$ Complexity}

The parallel complexity class $\texttt{NC}$, known as Nick$'$s
Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
where each decision problem can be efficiently solved in parallel.
Specifically, a decision problem in the $\texttt{NC}$ class
can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.

From the perspective of implementations, the $\texttt{NC}$ problems are also highly
parallel feasible for other parallel models like BSP \cite{Valiant90}
and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
as a class of decision problems. Since we study the problem of materialization, we do not
require in this work that a problem should be a decision problem in $\texttt{NC}$.
In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
are implemented on shared-memory platforms, we
study all the issues in this work by assuming that the running machines are in
shared-memory configurations.

\section{Parallel Tractability of Datalog Programs}
\label{sec:ptclass}

Our target is to find for which kinds of ontologies (not ontology languages)
materialization is parallelly tractable.
Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
set $R$ is fixed, the materialization problem is thus in data complexity
$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
case \cite{Raymond95}. In other words, the materialization problem on general
datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
if there exists an algorithm that handles this class of datalog programs and runs in parallel
poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.

\subsection{Parallel Tractable Classes}

We first give the following definition for a parallel tractable class of datalog programs
where an \texttt{NC} algorithm exists for handling each datalog program in this class.

\begin{definition}\label{def:ptd}
\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
parallelly tractable ontology (\texttt{PTO}) class.
\end{definition}

According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
which is the class of all datalog programs that can be handled by $\mathsf{A}$.
However, current materialization algorithms of datalog rewritable ontology languages
(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
Thus we give our $\texttt{NC}$ algorithms.
In the following, we first give a parallel materialization algorithm that works for
general datalog programs. We then restrict this algorithm to an \texttt{NC} version
and identify the target \texttt{PTD} class.

\subsection{Materialization Graph}

In order to give a parallel materialization algorithm,
we introduce the notion of \emph{materialization graph}.
It makes the analysis of the given algorithm convenient.

\begin{definition}
\textbf{(Materialization Graph)}\label{def:mg}
A \emph{materialization graph}, with respect to
a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
denoted by $\mathcal{G}=\langle V, E\rangle$ where,
\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
\end{enumerate}
~~$\mathcal{G}$ satisfies the following condition:
\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
  $B_1,...,B_n\rightarrow H\in P^*$.
\end{enumerate}
\end{definition}

For some derived atom $H$, there may exist several rule instantiations where $H$
occurs as a head atom.
This also means that $H$ can be derived in different ways.
The condition in the definition above results in only one way of deriving $H$ being
described by a materialization graph.
Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
original facts in $\textbf{I}$.
The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
in $\mathcal{G}$.
We next give an example of a materialization graph.\\

\begin{example}\label{exp:mg}
Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
$k$ is an integer greater than $2$.
The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
where $\textbf{I}$ contains all the assertions in the ABox
and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
denoted by $\mathcal{G}_{ex_1}$.
The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
each of the other nodes corresponds to a ground instantiation of some rule.
For example, the node $A(a_k)$ corresponds to the ground rule instantiation
`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
The size of this materialization graph is the number of nodes, that is $3k$.
The depth of $\mathcal{G}_{ex_1}$ is $k$.
\end{example}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{fig-mg.eps}
\caption{An example of a materialization graph.}
\label{fig:mg}
\end{center}
\end{figure}

We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
The set of nodes in a complete materialization graph is actually the result
of materialization.
Thus, the procedure of materialization can be transformed to the construction of
a complete materialization graph.
We pay our attention to complete materialization graphs and do not distinguish it to the
notion `materialization graph'.
It should also be noted that there may exist several materialization graphs for a datalog program.

\subsection{A Basic Parallel Algorithm}

In this part, we propose a parallel algorithm
(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\

\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
Recall that $P^*$ denotes the ground instantiation of $P$,
which consists of all possible ground instantiations of rules in $R$.
Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
assigned to one processor.\footnote{This might not be practically feasible,
but we focus on a theoretical analysis here.}
Initially $\mathcal{G}$ is empty. The following three steps are then performed:
\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
    atom has been added to the materialization graph. This can be implemented by maintaining an
    index of polynomial size.}
    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
\end{enumerate}

\begin{example}
We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
$\mathcal{G}_{ex_1}$ by different processors.
For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
\end{example}

Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
in the appendix.

\begin{lemma}
\label{lemma:a1}
Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
\begin{enumerate}[leftmargin=4ex]
\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
\end{enumerate}
\end{lemma}

\begin{proof}[Proof sketch] This lemma can be proved by performing
an induction on $T_R^{\omega}(\textbf{I})$.
The stage (see the related contents in Section~\ref{sec:background}) of $P$
is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
its depth equals the depth of the stage.
\end{proof}

We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
new constants and each predicate has a constant arity,
one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
the number of processors is polynomially bounded.
(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
and \ref{alg1:halt} occupies constant time units because of parallelism.
(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
iteration of \ref{alg1:updateG}.
In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
Thus, in theory, \ref{alg1:updateG} costs one time unit.
The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
for any datalog program $P$, if we use $\psi(|P|)$ to
bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).

Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
by $\mathsf{A}_{bsc}^{\psi}$.
It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
We use the following theorem to further show that this class can be captured based on
the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.

\begin{theorem}\label{theorem:a1}
For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
materialization graph whose depth is upper-bounded by $\psi(|P|)$.
\end{theorem}

\begin{proof}[Proof sketch]
We can first prove that the number of iterations
of \ref{alg1:updateG} is actually the depth of the constructed materialization
graph. This theorem then follows by considering
Lemma~\ref{lemma:a1}.
\end{proof}

The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
graph of $P_{ex_1}$.
However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
We discuss this in the next part.

\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}

In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
we can identify another \texttt{PTD} class.

We discuss our optimization based on a specific case in Example~\ref{exp:general}.
We find that, in this kind of case, the construction of a materialization graph can be accelerated.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{fig-general.eps}
\caption{A partial materialization graph.}
\label{fig:general}
\end{center}
\end{figure}

\begin{example}\label{exp:general}
Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
In this snapshot, $v_0$ has been newly added
to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
while $v'$ has two parent nodes being not in $\mathcal{G}$.
All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
afterwards.
\end{example}

In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
node only depends on one of its parent nodes.
Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
we call such a path a \emph{single-way derivable} (SWD) path.
Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
$\mathcal{G}$ immediately.
Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
due to the single-way derivability condition.

Backing to Example~\ref{exp:general}, since
there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.

We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
describe the reachability between two nodes. To this extent, we use a
binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:

\begin{description}[leftmargin=2ex]
\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
where $H$ has been added to $\mathcal{G}$}:
\begin{enumerate}[leftmargin=2ex]
\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
\end{enumerate}
\end{description}

We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
The following algorithm applies this optimization strategy.\\

\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
being constructed from $P$. The following steps are performed:
\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
\end{enumerate}

It is well known that there is an \texttt{NC} algorithm for computing the
transitive closure \cite{Allender07}.
Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\

\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
\end{enumerate}

It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
Algorithm~$\mathsf{A}_{opt}$.
The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.

\begin{lemma}\label{lemma:a3}
Given a datalog program $P=\langle R, \textbf{I}\rangle$,
$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
\end{lemma}

\begin{example}\label{exp:opt}
We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
In the transitive closure of $S_{\textit{\tiny rch}}$,
one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
in the first iteration of \ref{alg3:updateG}.
\end{example}

We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.

Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.

\begin{corollary}
For any poly-logarithmically bounded function $\psi$,
we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
\end{corollary}

\begin{proof}[Proof sketch]
Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
if $\mathcal{G}$ is not the materialization graph constructed
by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
\end{proof}

\section{Parallel Tractability of Ontology Materialization in OWL}
\label{sec:ptonto}

In this section, we study the issue of parallel tractability
for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
based on Algorithm~$\mathsf{A}_{opt}$.
We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
there exists a poly-logarithmically bounded function $\psi$
such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
work by studying specific cases.
Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
of materialization.

\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}

In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
DL-Lite materialization and analyze its parallel tractability.
Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
the constructed materialization graph in the first iteration of \ref{alg3:updateG}
by performing Algorithm~$\mathsf{A}_{opt}$.

In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
we use the following example.

\begin{example}\label{exp:dllite}
Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
where its TBox and RBox contain the following axioms:
$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
its ABox contains an assertion $Q(a,b)$.
We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
as the only fact.
The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
\end{example}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
\label{fig:ex2}
\end{center}
\end{figure}

Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
(\uppercase\expandafter{\romannumeral2}) In the first iteration of
\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
(\uppercase\expandafter{\romannumeral3})
The two nodes $\bot(a)$ and $\bot(b)$
have no SWD path in the first iteration of \ref{alg3:updateG}.
They are left to be processed in the second iteration.
(\uppercase\expandafter{\romannumeral4})
Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
after two iterations (\ref{alg3:halt}).

From the above example, we can observe that SWD paths exist
for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.

\begin{lemma}\label{lemma:dllite}
For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
\end{lemma}

The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
have to be added to the constructed materialization graph in the first iteration of
\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
$\bot$ dose not occur on the left hand of any axiom. In other words,
an atom of the form $\bot(x)$ cannot be the parent of any other node.
This allows all atoms of the form $\bot(x)$ being added
to the constructed materialization graph in at most two iterations of
\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
there always exists a poly-logarithmically bounded function $\psi$ such that
Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
more precisely, we can set that $\psi=2$. This result is consistent with
that in \cite{CalvaneseGLLR07}.
Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.

\begin{theorem}\label{theorem:dl-lite}
There exists a poly-logarithmically bounded function $\psi$ s.t.
$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
\end{theorem}

\subsection{Parallelly Tractable Materialization of DHL}

In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
does not work for any poly-logarithmically bounded function $\psi$.
In the following, we first give such an ontology
to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
Based on the analysis of this case, we propose to restrict
the usage of DHL in order to achieve parallel tractability
of materialization.

We find that, an unlimited usage of axioms of the
form $B_1\sqcap B_2\sqsubseteq A$
may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
We use the following example to illustrate it.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
\label{fig:ex3_4}
\end{center}
\end{figure}

\begin{example}\label{exp:dhl}
Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
for $2\leq i\leq k$ and $k$ is an integer greater than 2.
We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
\end{example}

One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
each node of the form $A(a_i)$ (filled with black color,
and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
number of iterations.
The intuitive reason is that, at least two paths exist
starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
We use `\emph{path twisting}' to represent such cases.

In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
to avoid `path twisting'. An intuitive idea is to
ensure that \emph{there is only one path between each two atoms of the form $A(x)$
generated from the rules corresponding to (T1)}.
We explain it by using the following example where the ontology is modified from
that in Example~\ref{exp:dhl}.

\begin{example}\label{exp:simpleC}
Consider an ontology where the TBox contains three axioms:
$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
for $2\leq i\leq k$ and $k$ is an integer greater than 2.
We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
\end{example}

In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
since they have corresponding SWD paths;
after that, all the other nodes
can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
node has an SWD path).
Motivated by this example, we consider restricting the usage of
the axioms $B_1\sqcap B_2\sqsubseteq A$
such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
for some $y$.
To this end, we first define \emph{simple concepts} as follows:

\begin{definition}
Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
of some axiom; or (2) $A$ satisfies the following conditions:
\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
\end{enumerate}
\end{definition}

Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
(we call it \emph{simple-concept restriction}).
Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
is generated from the rules corresponding to (T1).

\begin{example}
In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
non-simple concepts.
In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
\end{example}

We define the following class of DHL ontologies based on the above restriction and
give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
for some poly-logarithmical function $\psi$.

\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
\end{definition}

\begin{theorem}\label{theorem:dhl}
There exists a poly-logarithmically bounded function $\psi$ s.t.
$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
\end{theorem}

\subsection{Parallelly Tractable Materialization of DHL($\circ$)}

In this part, we study parallelly tractable materialization
of DHL($\circ$) ontologies.
In addition to the rules in DHL, we also have to consider complex RIAs (R4).
We next show that complex RIAs may also cause the situation of `path twisting'.
Consider the following example.

\begin{example}\label{exp:complexRIA}
Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
the RBox $\mathcal{R}$ contains three axioms:
$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
for $2\leq i\leq k$ and $k$ is an integer greater than 2.
The corresponding datalog program $P_{ex_5}$
contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
\end{example}

One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.

Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
then, at least one of $R_1$ and $R_2$ is
a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
we can get a complex RIA in the form of
$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
If one of $R_1$ and $R_2$ is not a simple role, the corresponding
rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
The reason can be explained as follows.
Without loss of the generality,
$R_2$ is a simple role while $R_1$ is not.
For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
through the corresponding rule of $\alpha_3$. The similar analysis applies to
such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
Further, the situation of path twisting also exists.
To tackle the above issue,
we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
Combined with the simple-concept restriction,
we define a class of DHL($\circ$) ontologies as follows:

\begin{definition}\label{def:dhlplus}
$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
is rewritten from a DHL($\circ$) ontology and the following
conditions are satisfied:
\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
\end{enumerate}
\end{definition}

\begin{example}
For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
Consider the ontology $\mathcal{O}_{ex_1}$
in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
\end{example}

We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.

\begin{theorem}\label{theorem:dhlplus}
There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
\end{theorem}

\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
\label{sec:practicalAlg}

In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
and the role-concept restrictions.

\subsection{Reducing Computing Space}

In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
However, this algorithm can hardly work in practice due to its inherently
high requirement of computing space. Specifically,
Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
since there are two variables in this rule, the number of all possible rule instantiations
is $|\textbf{IN}|^2$; if there are
1000 individuals in \textbf{IN}, this number is 1 million.
Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
the number of all possible rule instantiations is $|\textbf{IN}|^3$.
It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
when the target datalog program or ontology
tends to be large in size.
On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
we can observe that the rule instantiations used for the construction
of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
by narrowing down the scope of rule instantiations to be checked.
Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
each of the checked rule instantiations should involve at least one body atom that has been
added to the constructed materialization graph}.
Since DHL$(\circ)$
is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
as follows.

We first consider a datalog rule of the
form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
This is because that, for each assertion $A(a)$,
the datalog rule `$A(x)\rightarrow B(x)$'
has only one rule instantiation `$A(a)\rightarrow B(a)$' where
the variable $x$ is substituted by the constant $a$.
The cases of (R1) and (R2) can be analyzed similarly.
We now consider the datalog rules that have two body atoms, i.e.,
the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
at least one body atom has been added to the constructed materialization
graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
the number of checked rule instantiations
is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
added to $\mathcal{G}$.
Note that, for rule instantiations of two body atoms,
we do not require that both of these two body atoms have been added to
the constructed materialization graph.
Otherwise, the algorithm would
perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.

\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}

We use the above method of narrowing down the scope of rule instantiations to
modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
Recall that,
in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
checks all possible rule instantiations and computes a \texttt{rch} relation
and its transitive closure to determine the existence of SWD paths.
We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
narrowing down the scope of rule instantiations to be checked as well. This can be described
by the following algorithm.\\

\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
and its datalog program $P=\langle R, \textbf{I}\rangle$;
(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
is computed from the following rule instantiations:

\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;

\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;

\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;

\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;

\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;

\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
    where $R_1\equiv R_2\equiv R_3$ is also involved),
    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
\end{enumerate}

Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
is thus given as follows:\\

\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
returns a materialization graph $\mathcal{G}$ of $P$.
Initially $\mathcal{G}$ is empty. The following steps are then performed:
\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
\end{enumerate}

\begin{theorem}\label{theorem:aprc}
For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
a materialization graph of $\mathcal{O}$.
\end{theorem}

The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
DHL$(\circ)$ materialization.

\begin{example}\label{exp:prc}
Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
Initially, Algorithm~$\mathsf{A}_{prc}$ adds
all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
and $\forall o\in$\textbf{IN},
an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
by Algorithm~$\mathsf{A}_{prc}$.
\end{example}

From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
that follow the simple-concept and the simple-role restrictions.
The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
does not influence the determination of the existence of SWD paths. The detailed analysis
can be found in the proof.

\begin{theorem}\label{theorem:aprcpt}
For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
restrictions,
there exists a poly-logarithmically bounded function $\psi$,
such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
a materialization graph of $\mathcal{O}$.
\end{theorem}

\section{Evaluation}
\label{sec:evaluation}

In the first part of this section, we analyze different kinds of ontologies and datasets
and investigate the usability of the results proposed above.
In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
and compare it to the reasoning system RDFox.

\subsection{Practical Usability of the Theoretical Results}

In this part, we analyze different kinds of ontologies and datasets
including benchmarks, real-world ontologies and
datasets that can be expressed in ontology languages.
Based on the analysis of these datasets,
we find that, ignoring imports, many of them
belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.

\textbf{Benchmarks}. In the
Semantic Web community, many benchmarks are proposed to
facilitate the evaluation of ontology-based systems
in a standard and systematic way. We investigate several
popular benchmarks using our results and find that
the ontologies used in some benchmarks have simple
structured TBoxes that can be expressed in RDFS
and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
(\emph{Social Network Intelligence BenchMark}),
BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
(\emph{Berlin SPARQL Benchmark}) and
LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
(\emph{Linked Open Data Integration Benchmark}).
The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.

In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
(The Lehigh University Benchmark),
there are 48 classes and 32 properties.
Statements about properties, such as inverse property statements,
can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
Most of the statements about classes can be rewritten into datalog rules that
are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
which requires existentially quantified variables in the rule head when rewriting
the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
where a new anonymous constant $y$ is introduced.
This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
On the other hand, in some cases, this kind of rule can also be
eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
In summary, if the above kind of rule is not considered,
the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.

\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
is constructed from Wikipedia and WordNet and the latest version
YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
(e.g., persons, organizations, cities, etc.)
and contains more than 120 million facts about these entities.
In order to balance the expressiveness and computing efficiency,
a YAGO-style language, called YAGO \emph{model}, is proposed based on
a slight extension of RDFS \cite{SuchanekKW08}.
In addition to the expressiveness of RDFS,
YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
However, in \cite{SuchanekKW08}, a group of materialization rules
is specified, which is more efficient.
All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.

\textbf{Real Ontologies}. We investigated
$151$ ontologies that cover many domains
like biomedicine, geography, etc.
These ontologies are collected
from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
Swoogle\footnote{http://swoogle.umbc.edu/}
and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
All ontologies are available online.\footnote{https://github.com/quanzz/PT}
Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
conjunctions and follow the simple-concept restriction.
The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
appears in these ontologies.
We also find two DHL($\circ$) ontologies
that follow the simple-role restriction.

The above investigation indicates that the simple-concept and the simple-role restrictions
are allowed in many real applications of different fields.
From the perspective of developers who work on building their own ontologies,
they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
to achieve the guarantee of the parallel tractability.

\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}

We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
that can also handle ontology materialization.

\textbf{Datasets}.
We select eight ontologies from the data sources given in the previous subsection;
four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
the rest of them do not follow the simple-concept or the simple-role
restriction.
The eight ontologies are real ontologies and are applied in different fields.
The basic information of these ontologies
is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).

\begin{center}
\begin{tabular}{ccrrc}
\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
\hline
~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
\hline

Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\

Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\

GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\

Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\

\hline

ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\

FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\

Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\

Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\

\hline
\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\

\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\

\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
\end{tabular}
\label{tab:info}
\end{center}

For the purpose of comparability in the ABox scale, we consider generating ABox assertions
to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
for evaluating ontology-based systems.
For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
we also use ``Finance series" to denote the five generated ontologies
for the ontology Finance. The other test ontologies are processed similarly.

\textbf{The Experimental Results}.
We run ParallelDHL and RDFox over the above eight ontology series respectively.
The running environment is a DELL server with a
memory of 16 GiB and 4 cores.
For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
to ParallelDHL and RDFox in each experiment. The results of reasoning
times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
where the abscissa of each line graph records the numbers of ABox assertions,
the ordinate records the values of reasoning time (millisecond per unit),
and each of the five curves in different colors denotes the trend of reasoning time with the
corresponding number of threads allocated (we use line-$k$ to denote the curve
corresponding to $k$ threads).

We further process the collected data and fill the results in Table~3, where each cell corresponds
to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
of ParallelDHL devided by the minimal reasoning time of RDFox;
(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
(3) \emph{the average speedup of RDFox}.
The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
threads allocated.
In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.

\textbf{The Analysis of the Experimental Results}.
According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
may not be parallelly tractable in terms of materialization. In other words,
parallel techniques may not work for improving the efficiency of materialization.
This is shown in the line graphs of Figure~\ref{fig:linegraph}.
We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
series is more obvious. For example, in line graph $lg1$,
line-2 stays higher than line-6, but lower than line-4.
The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
This is also supported by the results of the average speedups.
From Table~3, we can see that the average speedups of ParallelDHL and RDFox
for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
are more stable compared with the other ones, i.e., they are averagely 1.4
(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
the average speedups have a higher volatility. For example,
Finance and Skeleton series lead to high average speedups that reach up to 3,
while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
In summary, from the experiments on the test ontology series,
parallelism leads to a more effective improvement for materializing the ontology series
that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.

By analyzing the experimental results of ParallelDHL and RDFox, we have that
ParallelDHL is a competitive system.
From Table~3, we can find that most of the minimal time ratios are close to 1.
This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
only costs one fifth of the minimal reasoning time of RDFox.
On the other hand, for most ontology series,
the average speedups of ParallelDHL are overall higher than that of RDFox.
The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
The higher average speedups of PrallelDHL also verifies the validity of the optimizations
used in Algorithm~$\mathsf{A}_{opt}$.
One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
The main reason is that the computation of \texttt{rch} relations
occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
This makes the the optimization based on \texttt{rch} relations invalid as discussed
in Section~\ref{sec:ptonto}.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
\label{fig:linegraph}
\end{center}
\end{figure}

\begin{center}
\begin{tabular}{crrrrr}
\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
\hline
&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
\hline
&0.54&1.36&0.94&0.99&1.70\\
Finance&3.06&1.88&2.29&2.95&2.73\\
&1.01&1.04&1.13&1.11&1.19\\
\hline
&0.94&0.79&0.96&0.98&1.07\\
Molecule&1.04&1.24&1.13&1.07&1.05\\
&0.90&1.03&0.95&1.01&0.99\\
\hline
&0.65&0.48&0.84&0.77&0.83\\
GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
&0.87&0.99&0.94&0.96&0.98\\
\hline
&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
Skeleton&3.28&1.84&1.65&1.74&1.96\\
&1.13&1.01&1.06&1.08&1.08\\
\hline
&1.29&1.54&1.68&1.14&0.93\\
ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
&1.28&1.16&1.14&1.11&1.15\\
\hline
&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
&1.22&1.08&1.07&1.09&1.09\\
\hline
&1.19&1.19&0.99&0.84&0.89\\
Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
&1.24&1.07&1.13&1.10&1.12\\
\hline
&0.24&0.52&0.51&0.65&0.49\\
Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
&1.14&1.04&1.03&1.08&1.11\\
\hline
\end{tabular}
\label{tab:expresult}
\end{center}

\section{Related Work}
\label{sec:related}

The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation. RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages. Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4). The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor. Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox. It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$. We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable. Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.

There is work that studies parallel reasoning in RDFS and OWL. The current methods mainly focus on optimizing reasoning algorithms from different aspects. The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance. This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering. In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning. The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning. The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}. Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data). The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets. On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}. In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks. A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification. The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm. The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.

Another line of optimizing parallel reasoning is to utilize high-performance computing platforms. For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}. The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware. The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning. The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}. Different techniques are discussed in this work to tackle the special problems in distributed computing. However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}. This is not the focus in this paper.

Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data. The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.

\section{Conclusions}
\label{sec:conclusion}

In this paper, we studied the problem of parallel tractability of
materialization on the datalog rewritable ontologies.
To identify the parallelly tractable classes,
we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
datalog rewritable ontology languages.
Based on these algorithms, we identified the corresponding
parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
on the datalog programs in these classes is in the complexity class \texttt{NC}.
We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.

We verified the usefulness of our theoretical techniques in two ways. On the one hand,
we analyzed different kinds of datasets,
including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
Our analysis showed that many real ontologies belong to
the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
to create large-scale ontologies for which parallel tractability
is theoretically guaranteed. On the other hand,
we used an optimization strategy based on SWD paths
to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
also be restricted to an \texttt{NC} version, and can be implemented for practice.
We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
the state-of-the-art reasoner RDFox.
The experimental results showed that the optimization proposed in this paper results
in a better performance on parallelly tractable ontologies compared with RDFox.

In the future work, we will extend our work in two lines.
One line is a further study of the parallel tractability of
other expressive ontology languages, in addition to
datalog rewritable ones. Since different expressive OWL languages
have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
explore more restrictions that are practical and make materialization
parallelly tractable. Another line of the future work is to
study how to further apply the
results in practice.
One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
like ontology classification, ontology debugging and query answering.

\section*{Reference}

\bibliographystyle{elsarticle-num}
\bibliography{reference}

\clearpage

\section*{Appendix}

\appendix

\section{Proof of Lemma~\ref{lemma:a1}}

\textbf{Lemma~\ref{lemma:a1}}
\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\

\noindent\emph{Proof}:
(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
Thus $\mathcal{G}$ turns out to be an acyclic graph.
Second, to show $\mathcal{G}$ is a
complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
of $\mathsf{A}_{bsc}$.
For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
there has to be a processor that would add it to $\mathcal{G}$.

(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$

\section{Proof of Theorem~\ref{theorem:a1}}

\textbf{Theorem~\ref{theorem:a1}}
\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\

\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
is actually the depth of the constructed materialization graph.
We define the depths of nodes iteratively as follows:
for each explicit node $v$, \texttt{depth}($v$)=0;
for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
By performing an induction on the number of iterations of \ref{alg1:updateG},
one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
where $n$=\texttt{depth}($v'$).
Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).

($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
a materialization graph $\mathcal{G}$ of $P$.
Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.

($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
is upper-bounded by $\psi(|P|)$.
If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
and, thus, upper-bounded by $\psi(|P|)$.
If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
should have a smaller depth compared with $\mathcal{G}$.
In this case, this conclusion still holds.\hfill$\Box$

\section{Proof of Lemma~\ref{lemma:a3}}

\textbf{Lemma~\ref{lemma:a3}}
\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\

\noindent\emph{Proof}: this lemma can be proved by two stages:
(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
(2) $\mathcal{G}$ is a complete materialization graph.
We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.

\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
In this case, $\mathcal{G}$ is obviously a materialization graph.

\emph{Inductive case}.
According to the induction hypothesis, the partial graph constructed after
the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
of Algorithm~$\mathsf{Opt}$.
Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
In the above two cases, $H$ is a new node. Thus,
$\mathcal{G}^{i+1}$ is acyclic.
(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
the algorithm does nothing.
Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.

To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
performing $\mathsf{A}_{opt}$.
For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
of $\mathsf{A}_{opt}$.\hfill$\Box$

\section{Proof of Lemma~\ref{lemma:dllite}}

\textbf{Lemma~\ref{lemma:dllite}}
\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\

\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
the datalog rules corresponding to DL-Lite axioms.

\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
for any materialization graph.

\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
that is rewritten from some DL-Lite axiom, we have the induction hypothesis
that $B_1,...,B_n$ have SWD paths.
We are left to prove that $H$ has an SWD path as well
in all materialization graphs of $\mathcal{O}$.

If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
applying (T1) and (T3). Thus, we conduct the induction by
distinguish these two cases as follows.

\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
\item $B\sqsubseteq A$. According to the induction hypothesis,
node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
We have that, in some materialization graph, node $A(x)$
has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.

\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
denoted by $(v_1,...,v_n,R(x,y))$,
according to the induction hypothesis.
It is obvious that node $A(x)$
has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
in some materialization graph.
\end{enumerate}

Since node $A(x)$ can only be derived in either Case~1.1
or Case~1.2, we have that
node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.

It is similar to prove the case where $H$ is in the form of $R(x,y)$.
Since node $R(x,y)$ may be derived by
applying (R1) and (R2), we discuss these two cases.

\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
\item $S\sqsubseteq R$. According to the induction hypothesis,
node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
Obviously, node $R(x,y)$
has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
in some materialization graph.

\item $S\sqsubseteq R^-$. This case is similar to
the above case.
\end{enumerate}

In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$

\section{Proof of Theorem~\ref{theorem:dl-lite}}

\textbf{Theorem~\ref{theorem:dl-lite}}
\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\

\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
Specifically, for any DL-lite ontology $\mathcal{O}$,
there always exists a poly-logarithmically bounded function $\psi$ such that
$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
since in any materialization graph, each node has an SWD path.
More precisely, we can set that $\psi=2$.\hfill$\Box$

\section{Proof of Theorem~\ref{theorem:dhl}}

\textbf{Theorem~\ref{theorem:dhl}}
\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\

\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
This also indicates that, the materialization of a DHL
ontology can be separated into two stages: in the first stage (Stage~1), all the rules
of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
are then applied in Stage~2.
It is obvious that, if both of Stage~1 and Stage~2 can be handled
by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
In what follows, we investigate the above two stages respectively, and show that,
for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
such a poly-logarithmical function $\psi$ exists.

In Stage~1, the rules of the forms (R1-R3)
are applied to add new nodes to the constructed materialization graph.
We can observe that, rule (R3) is used for computation of transitive roles.
As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
handles Stage~1 for some poly-logarithmical function $\psi$}.
The proof of this result can be shown by separately considering non-transitive roles and
the roles that are transitive or influenced by transitive roles.
Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:

\begin{definition}\label{def:deltaRdhl}
For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
\item for each $R(a,b)\in\mathcal{A}$;
\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
\end{enumerate}
\end{definition}

Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
We then have the following lemma.

\begin{lemma}\label{lemma:ti}
$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
\end{lemma}

Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
In this sense, Lemma~\ref{lemma:ti} also indicates that:
(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
it can be added to a materialization graph by only applying (R1) and (R2);
(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
(3) for each role $R$ that is a TI role but not a transitive role,
one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
where $R'$ is a transitive role.
Since all nodes generated by only applying (R1) and (R2) have SWD paths,
the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
Thus, there exists a poly-logarithmical function $\psi$
such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.

The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
Based on the above analysis, this theorem holds.

We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
that are possibly applied to derive $R(a,b)$.

\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.

\emph{Inductive case}. We first study the case where $R$ is an NTI role.

\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}

\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}

\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
    an NTI role.
\end{enumerate}

We next study the case where $R$ is a transitive role.

\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.

    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
        the transitive closure of $\delta_{R''}$, we then have that there must
        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
        also holds.
    \end{enumerate}

\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.

    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
        the transitive closure of $\delta_{R''}$, we then have that there must
        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
        also holds.
    \end{enumerate}

\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
\end{enumerate}

We finally study the case where $R$ is a TI but not a transitive role.

\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.

    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
    \end{enumerate}

\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.

\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
    role.\hfill$\Box$
\end{enumerate}

\section{Proof of Theorem~\ref{theorem:dhlplus}}

\textbf{Theorem~\ref{theorem:dhlplus}}
\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\

\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
Thus we only consider Stage~1 here.

Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
distinguish all roles by whether they are transitively influenced. Since we have to consider
complex RIAs, we re-define TI and NTI roles as follows:
a role $R$ is \emph{transitively influenced} (TI)
if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
or (3) there exist a TI role $R'$ and an axiom of either of the form
$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
We say that a role is an NTI role if it is not transitively influenced.
The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
that is defined as follows:

\begin{definition}\label{def:language}
Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
 \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
\item $R'$, for each $R'\sqsubseteq_* R$;
\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
\end{enumerate}
\end{definition}

In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
We then give the following definition for $\delta_R$.

\begin{definition}\label{def:deltaRdhlplus}
For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
\item for each $R(a,b)\in\mathcal{A}$;
\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
\end{enumerate}
\end{definition}

\begin{lemma}\label{lemma:tiplus}
$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
\end{lemma}

The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
The above lemma says:
(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
it can be added to a materialization graph by only applying (R1), (R2) and (R4);
(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
(3) for each role $R$ that is a TI but not a transitive role,
one can further perform (R1), (R2) and (R4) iteratively based on all
transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
least one role in the left hand side of (R4) are restricted to be a simple role.
Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
In summary, there exists a poly-logarithmical function $\psi$
such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.

We now prove Lemma~\ref{lemma:tiplus}.
We conduct the proof by an induction on
the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
that are possibly applied to derive $R(a,b)$.

\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.

\emph{Inductive case}. We first study the case where $R$ is an NTI role.

\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}

\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}

\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:

    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.

    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.

    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
    \end{enumerate}

    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
    holds.\label{dhlplus:NTIcaseR4}

\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
    since $R$ is an NTI but not transitive role.
\end{enumerate}

We next study the case where $R$ is a transitive role.

\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
    which also means that $R'\sqsubseteq R\in\mathcal{R}$.

    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
        obviously, $R\in\mathcal{L}(R)$ holds.

    \item $R'$ is a TI but not a transitive role.
        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.

    \item $R'$ is a transitive role.
        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
    \end{enumerate}

\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.

    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
        obviously, $R\in\mathcal{L}(R)$ holds.

    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.

     \item $R'$ is a transitive role.
        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
    \end{enumerate}

\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
    Further, $R$ is a transitive role. According to the simple-role restriction,
    both of $R_1$ and $R_2$ are simple roles.
    This also
    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
    This case is similar to \ref{dhlplus:NTIcaseR4}.

\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
    Since $R$ is a TI role, by the induction hypothesis,
    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
\end{enumerate}

We finally study the case where $R$ is a TI but not a transitive role.

\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}

    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
        obviously, $R\in\mathcal{L}(R)$ holds.

    \item $R'$ is a TI but not a transitive role.
        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.

    \item $R'$ is a transitive role.
        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
        Then, $R'$ is actually the role sequence that satisfies the condition
        in this lemma.
    \end{enumerate}

\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.

    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
        obviously, $R\in\mathcal{L}(R)$ holds.

    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.

     \item $R'$ is a transitive role.
        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
        $R'^-$ is actually the role sequence that satisfies the condition
        in this lemma.
    \end{enumerate}

\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
    at least one of $R_1$ and $R_2$ is a simple role.
    W.l.o.g., let $R_2$ be a simple role, which also
    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
    are the starting and ending individual respectively.
    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}

\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
\end{enumerate}

\section{Proof of Theorem~\ref{theorem:aprc}}

\textbf{Theorem~\ref{theorem:aprc}}
\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
a materialization graph $\mathcal{O}$.}\\

\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
this theorem is proved in two stages:
(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
(2) $\mathcal{G}$ is a complete materialization graph.
One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
(see the proof of Lemma~\ref{lemma:a3}). This is because that
such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.

To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
performing $\mathsf{A}_{prc}$.
For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
of $\mathsf{A}_{prc}$.\hfill$\Box$

\section{Proof of Theorem~\ref{theorem:aprcpt}}

\textbf{Theorem~\ref{theorem:aprcpt}}
\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
restrictions,
there exists a poly-logarithmically bounded function $\psi$,
such that $\mathsf{A}_{prc}^{\psi}$ outputs
a materialization graph of $\mathcal{O}$.}\\

\noindent\emph{Proof}: similar to what we do when proving
Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
we separate the materialization of a DHL$(\circ)$ ontology
into two stages: the role materialization (all the rules
of the forms (R1-R4) are exhaustively applied) and the concept materialization
(the rules of the forms (T1-T3)
are then applied). The difference is that, we further separate the role materialization
into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
\emph{the non-simple role materialization} (Stage~NSRM).
Similarly, the concept materialization is also separated into successively two stages:
\emph{the simple concept materialization} (Stage~SCM) and
\emph{the non-simple concept materialization} (Stage~NSCM).
Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.

We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
there exists a poly-logarithmically bounded function $\psi'$
such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.

We first consider Stage~SCM.
Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
can be viewed as an EDB predicate. This further means that,
for each atom of the form $A(a)$ where $A$ is a simple concept,
$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
The atom $A(a)$ can be derived through either of the following rule instantiations:

\begin{enumerate}[leftmargin=12ex]
\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.

\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
    Thus, the existence of the SWD path of $A(a)$ can also be determined.
\end{enumerate}

We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
We also use an induction to show that
such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
here.

\begin{enumerate}[leftmargin=12ex]
\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
    If $A_1(a)$ is derived where $A_1$ is a simple concept,
    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
    according to Algorithm~$\mathsf{Prc}$.
    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
    Thus, the existence of the SWD path of $A(a)$ can also be determined.
    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
\end{enumerate}

The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
of role inclusions, i.e., the axioms of the forms (R1-R2).
It is easy to check that the simple-role materialization can be finished after the
first iteration of $\mathsf{A}_{prc}$.

We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
and not a transitive role,
$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
We use an induction to show that
such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
as follows.

\begin{enumerate}[leftmargin=12ex]
\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
    according to Algorithm~$\mathsf{Prc}$.
    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.

\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
    according to Algorithm~$\mathsf{Prc}$.
    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.

\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
    according to Algorithm~$\mathsf{Prc}$.
    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
\end{enumerate}

We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
is a transitive role.
Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
$R(a,b)\in\delta^*_R$ holds.
According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
or there exists such axioms
of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
at most two iterations (see Case~4, Case~5 and Case~6).
We should prove that the transitive closure $\delta^*_R$
can also be computed by $\mathsf{A}_{prc}^\psi$ for some
poly-logarithmically bounded function $\psi$.

\begin{enumerate}[leftmargin=12ex]
\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
    One can construct a binary tree $t$ where the root node is $R(a,b)$,
    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
    all nodes in each level of $t$ in one iteration from the bottom. Thus,
    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
\end{enumerate}

\end{document}
\endinput

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

### 2018-01-24 parallel-tractability-J-v9/response.tex
added review response file to keep track of fixed issues and the according reply

\documentclass{article}
\usepackage{amsmath}
\usepackage{url}

\let\quoteOld\quote
\let\endquoteOld\endquote
\renewenvironment{quote}{\quoteOld\itshape}{\endquoteOld}

% use the following command line to convert to standard text file
% pandoc reviews.tex -o rebuttal.txt
\setlength{\parindent}{0pt}

\begin{document}

We thank the reviewers for the time and effort invested in the detailed reviews and the valuable suggestions and comments to improve the quality of the paper.  Below we reply to the individual points of the reviewers.

\section{Rebuttal to Review 1}

\begin{quote}
There should, however, be some discussion somewhere in the paper on the
relationship between path length and KB size.   Even if a KB uses a
non-parallelizable ontology language this doesn't matter much if the paths
that cause problems are short compared to the size of the KB.  The
non-parallel aspects of path processing of short paths will not be noticable
with a small number of threads (certainly up to hundreds) and maybe not even
for very many threads (because of general overhead).
\end{quote}

We added xxx to adress this...

\begin{quote}
  The second sentence of Section 3 is badly stated and misleading.  It is definitely true that for a Datalog program $\langle R, I \rangle$ the rule set $R$ is fixed.  However, the initial facts $I$ are also fixed.
\end{quote}

We did ...

\begin{quote}
It is not clear whether the classes of Datalog programs considered in the
paper have to share the same rule set.  The discussion previous to
Definition 1 seems to so indicate, but there is nothing in the definition
that says so.
\end{quote}

We did...

\begin{quote}
There is no definition of what the parents of a node in a graph are.
However, it is quite obvious what the definition should be.
\end{quote}

...

\begin{quote}
Example 6 does need a bit of revision.  It is not the case that Oex3 cannot
be materialzed tractably in parallel.  Instead there has to be a class of
ontologies that cannot be so materialized.  
\end{quote}

...

\begin{quote}
It would be much better if the ontology names corresponded to the example
numbers, i.e., the ontology in Example 6 was Oex6.
\end{quote}

...

\begin{quote}
The notion of a simple concept is very much tied to the algorithm developed
in the paper.  How often do actual ontologies have constructs that could
make them intractable that are rended tractable by having simple concepts?
If there are none, then this class is uninteresting, particularly as the
paper makes such strong claims about worrying about particular ontologies.
This is different from an ontology only containing simple concepts.
\end{quote}

...

\begin{quote}
The paper is all about parallel tractability of materialization, both
theoretical and practical.  However the paper gives insufficient attention
to RDFS, which is the main ontology language used in practice, and
particularly for large knowledge bases.  Even though RDFS is laughably
simple it does not have parallel tractability of even entailment.  The paper
should better examine parallel tractability in the context of RDFS or RDFS
with minor extensions.

Of course, RDFS does not fit into the approach of the paper, as it does not
a-priori separate classes and individuals.  The paper needs to discuss this
issue, as it prominently mentions RDFS.   
\end{quote}

...

\begin{quote}
The paper does a bad job of describing why materialization in RDFS is not
parallizable.  RDFS KBs have an infinite number of consequences, so it is
certainly not possible to materialize all of them quickly.  There are,
however, well known tricks that can be used to generate a finite
representation of this infinite set of consequences.  However, even this
cannot be done quickly in parallel.  In fact, even RDFS entailment cannot be
done quickly in parallel, because RDFS allows for a kind of twisted
interaction (which I think it similar to twisted paths in the paper) when
computing subproperty relationships.  Of course, having subproperties of
rdfs:subPropertyOf is not a usual thing to do in RDFS.  The paper needs to
be much more clear on its relationship to RDFS.
\end{quote}

...

\begin{quote}
The paper mentions YAGO early on but does not indicate why YAGO admits good
performance for parallel reasoning.  YAGO uses a very simple ontology
language - RDFS plus two simple extensions.  It is thus a prime candidate
for close examination to show how practical results differ from worst-case
theoretical ones.  However, the paper does not have any examination of
reasoning on YAGO.  Such an examination is very much called for.  Similarly
an examination of the performance of other large RDFS-based KBs, such as
DBpedia, would be very useful.   If YAGO is not benchmarked then it needs to
be dropped entirely.   Similarly for LUBM.
\end{quote}

...

\begin{quote}
The benchmarking part of the paper is very limited and extremely hard to
follow.    Only eight ontologies were benchmarked.  Why were these eight
chosen?  Only considering at most eight threads is much too constricting.  
\end{quote}

...ontologies must satisfy the properties for parallel tractability...

\begin{quote}
More detail is needed on how the KBs were constructed.  Chain length is a
very important aspect of the KBs, but nothing is said of how the instances
in the KB are connected together.  It is not stated which ontologies belong
to which DL.
\end{quote}

...

\begin{quote}
Figure 5 is very misleading because it uses different scales for the two
systems.   There are several immediate questions that arise from this Figure
that are poorly handled in the paper.  First, why does going from one thread
to two make such a difference for ParallelDHL?  Without a convincing
explanation for this surprising aspect of the benchmarking it is hard to
trust any of the rest of the benchmarking.  The other surprising aspect of
Figure 5 is that RDFox speeds up so little.  There is a short explanation of
why this is so, but I would have liked to see a longer one.
\end{quote}

...

\begin{quote}
The computation of the speedup numbers is wholely unexplained.  Why should
this number have any importance?
\end{quote}

...

\begin{quote}
There is a claim that the benchmarking distinguishes between the Ddhlo and
D-dhlo.  However, Figure 5 doesn't really show this well, if at all.   For
example, why should processing slow down with more threads at all?  Further,
it appears that even for several of the more well-behaved ontologies that there
is very little speedup between 6 and 8 processors.
\end{quote}

...

\begin{quote}
The benchmarking should be redone with more ontologies and with more
threads.  As well, there needs to be better analysis of where parallelism is
failing.  For example, if chains are short, then there should be no problem
in achieving near-perfect thread utilization, ignoring memory contention
problems.
\end{quote}

\begin{quote}
Wording and structural problems:

The paper has so many grammatical errors near its beginning that I gave up
marking them after the first two pages.  I give a few that I noticed here.\\
- [high-performance] computing platforms [] to\\
- do exist ontologies[] for which materialization\\
- (we use experiments to show [this] in Section 6).\\ 
- There has been work [] propos[ing] parallel reasoning algorithms and employ[ing] parallel\\
- e.g., dictionary encoding, balanc[ing] workload, [and] data partitioning,\\
- It has also been shown that[] some well-known large-scale ontologies,\\
The paper needs to be carefully copy-edited before any publication to remove
these errors.

"parallely tractable" is very grating.  It would be better to rewrite
sentences to not use it.
\end{quote}

TODO: Remove the quote above once the issues are fixed.

The paper has been carefully proof-read and hopefully all wording and structural issues are fixed now.

\begin{quote} 
The abstract of the paper is much too long.  An abstract is supposed to be
one not-long paragraph.  Instead it is here two long paragraphs.  The
abstract needs to be cut down to a suitable size before any publication.
\end{quote}

TODO: shorten the abstract.

Indeed, the abstract has been shortened significantly now.

\section{Rebuttal to Review 2}

\begin{quote}
First, in the discussion under Lemma 1, it says $|P^*|$ is polynomial in the size of $P$, which is imprecise, as $|P^*|$ is polynomial in the size of $I$ but not necessarily in the size of $R$. This is not a big issue if one considers NC for data complexity. What is less straightforward and more of concern is the statement that Step~2 costs only one time unit. As Step~2 involves checking the applicability of $B_1, \ldots, B_n \to H$ in $G$ and updating $G$, it depends on the size of $G$ and the size of $G$ is not a constant w.r.t.\ that of $I$. Footnote~4 suggests checking applicability of the rule can be done in constant time via an index. What about updating $G$ and maintaining the index?
\end{quote}

...

\begin{quote}
The computation of the rch relation $S_{\text{rch}}$ ($\dag$) looks problematic, as it requires ``H has been added to G''. If it were the case, then in Example~4 the $S_{\text{rch}}$ would always be empty, as none of the rule heads $H$ would be added to $G$. Again, the complexity analysis of $A_{\text{opt}}$ is unclear and possibly flawed. Step~2 uses an NC algorithm to compute the transitive closure of $S_{\text{rch}}$, which runs in poly-logarithmic time w.r.t.\ the size of $S_{\text{rch}}$ not necessarily so w.r.t.\ the size of $I$. What is the size of $S_{\text{rch}}$ w.r.t.\ that of $I$? Similarly as above, it involves updating $G$, which depends on the sizes of both $G$ and $S_{\text{rch}}$. Would it be still in poly-logarithmic time? 
\end{quote}

...

\begin{quote}
Finally, the algorithms assume each processor handling a rule instantiation. I wonder how it is implemented in ParallelDHL.
\end{quote}

...

\begin{quote}
I list some relatively minor issues regarding presentation and technical details:

- p5, saying ``y is a free variable'' in $A(x) \to \exists y.R(x,y)$ is confusing\\
-  p6, the definition of (complete) materialisation graphs seems problematic. According to Definition~2, a graph containing all ground atoms in $T_R^\omega(I)$ but no edge is a materialisation graph and is complete. In particular,  it does not guarantee ``the nodes whose in-degree is $0$ are the original facts in I'' as claimed.\\
- p6, the use of $\forall$ in Definition~2 is confusing and even worse in p18 Algorithm PRC.\\
- p20, it mentions a group of materialisation rules in YAGO which belong to $D_{\text{dhl}}$. It deserves a clarification on what these rules are like and why they do not fall into existing parallel tractable classes.\\
- p20, Table 2, it should mention how these ontologies were selected. \\
- p21, ``devided'' —> ``divided''\\
- p21, the discussion on line graph lg1 is confusing (i.e.\ ``line-2 stays higher than line-6, but lower than line-4''). Maybe I was looking at the wrong place. \\
- p25, the section heading ``Reference'' occur twice.
\end{quote}

TODO: remove the quote once the issues are fixed.

All minor issues have been fixed.

\end{document}

### 2018-01-26 parallel-tractability-J-v9/parallel-tractability-J.tex
The latest version
fixed quote 2-4 of reviewer 1

--- 2017-09-13 parallel-tractability-J-v8/parallel-tractability-J.tex
@@
 
-\author{}
-
-\address{}
+\author[add1]{Zhangquan Zhou \corref{cor1}}
+\ead{quanzz1129@gmail.com}
+\cortext[cor1]{Corresponding author}
+
+\author[add1]{Guilin Qi}
+\ead{gqi@seu.edu.cn}
+
+\author[add2]{Birte Glimm}
+\ead{birte.glimm@uni-ulm.de}
+
+\address[add1]{
+    School of Computer Science, Southeast University, China
+}
+
+\address[add2]{
+    Institution of Artificial Intelligence, University of Ulm
+}
 
@@
 to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
+In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}
+for any class of datalog programs.
 
@@
 materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
+Since we assume that for any class of datalog programs where the rule
+set of each datalog program is fixed, the materialization problem is thus in data complexity
 $\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
@@
 \begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
+\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs where the
+same rule set is shared, we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
 if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
@@
   \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
+  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
+\end{enumerate}
+For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are the two nodes,
+we say that node $v_1$ is the parent of node $v_2$ and node $v_2$ is the child
+of node $v_1$. Further, $\mathcal{G}$ satisfies the following condition:
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
@@
 
+\section*{Acknowledgments}
+
+This work was partially supported by NSFC
+grant 61672153 and the 863 program under Grant
+2015AA015406.
+
 \section*{Reference}

### 2018-01-27 parallel-tractability-J-v9/response.tex
fixed quote 5,6 of reviewer 1

@@
 
-We did ...
+We made it clear that the rule set is fixed for a class of Datalog programs.
+We also revised the similar presentations in Section~2.
 
@@
 
-We did...
+We modified Definition~1 to make it clear that the Datalog programs
+in a class share the same rule set.
 
@@
 
-...
+We added the definition of the parents of a node in a materialization graph in Definition~2.
 
@@
 
-...
+We did the revision for Example~6 (see the paragraph following Example~6),
+and Example~1 (see the last paragraph of Section~3.2).
 
@@
 
-...
+We made the ontology subscripts correspond to the examples numbers
+for Example~5, Example~6, Example~7 and Example~9.
 

### 2018-01-27 parallel-tractability-J-v9/parallel-tractability-J.tex
fixed quote 5,6 of reviewer 1

@@
 For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are the two nodes,
-we say that node $v_1$ is the parent of node $v_2$ and node $v_2$ is the child
+we say that node $v_1$ is the parent node of node $v_2$ and node $v_2$ is the child node
 of node $v_1$. Further, $\mathcal{G}$ satisfies the following condition:
@@
 
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
+Consider Example~\ref{exp:mg} again. Let the integer $k$ be a variable. We can
+get a class of datalog programs, denoted by $\mathbb{P}_{ex_1}$, where the rule set 
+is $\{R(x,y),A(y)\rightarrow A(x), S(x,y),R(y,z)\rightarrow R(x,z)\}$ and the instance
+set varies according to $k$. The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{ex_1}$.
+It can be checked that, for some materialization graph $\mathcal{G}_{ex_1}$
+corresponding to a datalog program in $\mathbb{P}_{ex_1}$, \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$ for some $k$.
+This means that the depths of the materialization graphs are linearly bounded by $k$.
+On the other hand, the sizes of the datalog programs in $\mathbb{P}_{ex_1}$ are polynomial of $k$.
 Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
 enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
+graph for each datalog program in $\mathbb{P}_{ex_1}$.
+However there indeed exists an \texttt{NC} algorithm that can handle $\mathbb{P}_{ex_1}$.
 We discuss this in the next part.
@@
 such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
+However, for DHL and DHL($\circ$), there exist ontology classes such that Algorithm~$\mathsf{A}_{opt}^\psi$
 does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
@@
 \begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
+Given a DL-Lite ontology $\mathcal{O}_{ex_5}$
 where its TBox and RBox contain the following axioms:
@@
 its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{ex_5}$ by $P_{ex_5}=\langle R, \textbf{I}\rangle$,
 where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
 as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
+The unique materialization graph of $P_{ex_5}$ is denoted by $\mathcal{G}_{ex_5}$ (see Figure~\ref{fig:ex2}).
 \end{example}
@@
 \includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
+\caption{The materialization graph of $\mathcal{O}_{ex_5}$.}
 \label{fig:ex2}
@@
 
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
+Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_5}$ in Example~\ref{exp:dllite}.
 (\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
+to $\mathcal{G}_{ex_5}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
 (\uppercase\expandafter{\romannumeral2}) In the first iteration of
@@
 starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
+adds these nodes to $\mathcal{G}_{ex_5}$ immediately. We take an example of node $B_1(a)$,
 for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
+When updating $\mathcal{G}_{ex_5}$ by adding $B_1(a)$ to it,
 Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
+has been in $\mathcal{G}_{ex_5}$; if $A(a)$ is already in $\mathcal{G}_{ex_5}$, $B_1(a)$
+is added to $\mathcal{G}_{ex_5}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
+if $A(a)$ has not been added to $\mathcal{G}_{ex_5}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
+to $\mathcal{G}_{ex_5}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
 an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
@@
 (\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
+Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_5}$
 after two iterations (\ref{alg3:halt}).
@@
 of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
+(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_5}$ of
 Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
@@
 In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
+Unfortunately there exist DHL ontology classes such that Algorithm~$\mathsf{A}_{opt}^\psi$
 does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
+In the following, we first give such a case
 to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
@@
 form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
+makes it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
 in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
@@
 \includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
+\caption{(left) The materialization graph of $\mathcal{O}_{ex_6}$;
+(right) The materialization graph of $\mathcal{O}_{ex_7}$.}
 \label{fig:ex3_4}
@@
 \begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
+Given a DHL ontology $\mathcal{O}_{ex_6}$ where its TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
@@
 for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{ex_6}$ by $P_{ex_6}=\langle R, \textbf{I}\rangle$,
 where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
+The materialization graph of $P_{ex_6}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_6}$ (see Figure~\ref{fig:ex3_4}(left)).
 \end{example}
 
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
+One can check that $\mathcal{G}_{ex_6}$ is the unique materialization graph of $P_{ex_6}$.
 Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
+When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_6}$, it can be checked that
 each node of the form $A(a_i)$ (filled with black color,
 and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
+in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_6}$,
+and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_6}$.
+Similar to the datalog program class $\mathbb{P}_{ex_1}$, we can also get a 
+datalog program class $\mathbb{P}_{ex_6}$ for the ontology $\mathcal{O}_{ex_6}$
+when $k$ is a variable. Based on the above analysis, Algorithm~$\mathsf{A}_{opt}$ cannot complete the materialization
+for the datalog programs of $\mathbb{P}_{ex_6}$ in a poly-logarithmical
 number of iterations.
@@
 That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
+to $\mathcal{G}_{ex_6}$, there would not exist an available SWD path for $A(a_i)$.
 We use `\emph{path twisting}' to represent such cases.
@@
 \begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
+Consider an ontology $\mathcal{O}_{ex_7}$ where the TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
@@
 for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
+We denote the corresponding datalog program by $P_{ex_7}$ where the rule set contains:
 `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
+$P_{ex_7}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_7}$ (see Figure~\ref{fig:ex3_4}(right)).
 \end{example}
@@
 This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
+Further, when constructing $\mathcal{G}_{ex_7}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
 two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
+adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_7}$,
 since they have corresponding SWD paths;
 after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
+can be added to $\mathcal{G}_{ex_7}$ in the second iteration (because each
 node has an SWD path).
@@
 \begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
+Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_9}$ where its TBox is empty;
 the RBox $\mathcal{R}$ contains three axioms:
@@
 `$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
+The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_9}$.
 \end{example}
 
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
+One can check that the materialization graph $\mathcal{G}_{ex_9}$ has the same shape as that
+of $\mathcal{G}_{ex_6}$ in Figure~\ref{fig:ex3_4}.
+A twisted path exists in $\mathcal{G}_{ex_9}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
 Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
@@
 \begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
+For the ontology $\mathcal{O}_{ex_7}$ in Example~\ref{exp:complexRIA}, all of the roles
+$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_7}$ does not follow
 the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.

### 2018-01-27 parallel-tractability-J-v9/response.tex
fixed minor issues

@@
 marking them after the first two pages.  I give a few that I noticed here.\\
-- [high-performance] computing platforms [] to\\
-- do exist ontologies[] for which materialization\\
-- (we use experiments to show [this] in Section 6).\\
-- There has been work [] propos[ing] parallel reasoning algorithms and employ[ing] parallel\\
-- e.g., dictionary encoding, balanc[ing] workload, [and] data partitioning,\\
-- It has also been shown that[] some well-known large-scale ontologies,\\
-The paper needs to be carefully copy-edited before any publication to remove
-these errors.
 
@@
 
-- p5, saying ``y is a free variable'' in $A(x) \to \exists y.R(x,y)$ is confusing\\
--  p6, the definition of (complete) materialisation graphs seems problematic.
-According to Definition~2, a graph containing all ground atoms in $T_R^\omega(I)$ but no edge is a materialisation graph and is complete.
-In particular,  it does not guarantee ``the nodes whose in-degree is $0$ are the original facts in I'' as claimed.\\
-- p6, the use of $\forall$ in Definition~2 is confusing and even worse in p18 Algorithm PRC.\\
 - p20, it mentions a group of materialisation rules in YAGO which belong to $D_{\text{dhl}}$.
 It deserves a clarification on what these rules are like and why they do not fall into existing parallel tractable classes.\\
+
 - p20, Table 2, it should mention how these ontologies were selected. \\
-- p21, ``devided'' —> ``divided''\\
+
 - p21, the discussion on line graph lg1 is confusing (i.e.\ ``line-2 stays higher than line-6, but lower than line-4''). Maybe I was looking at the wrong place. \\
+
 - p25, the section heading ``Reference'' occur twice.

### 2018-01-27 parallel-tractability-J-v9/parallel-tractability-J.tex
fixed minor issues

@@
 However, there do exist ontologies, for which
-materialization cannot always be improved by parallelism (we use experiments to show it in Section~\ref{sec:evaluation}).
+materialization cannot always be improved by parallelism (we use experiments to show this in Section~\ref{sec:evaluation}).
 On the other hand, some well-known large-scale ontologies, such as YAGO, have been shown to have
@@
 
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms
+There has been work proposing parallel reasoning algorithms and employing parallel computing platforms
 for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
+fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balancing workload
+and data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
+reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}.
+On the other hand, several work utilizes different kinds of computing platforms to make reasoning tasks more efficient in parallel, such as supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
 MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
@@
 reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
+It has also been shown that some well-known large-scale ontologies, such as YAGO, have good performance for parallel
 reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
+On the other hand, there do exist ontologies for which materialization cannot
+always be improved by parallelism (we use experiments to show this in Section~\ref{sec:evaluation}). 
+The current work of parallel ontology reasoning can hardly explain this.
 While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
@@
 Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
+a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is called a \emph{free variable} (it is
+not occurring in the head atom $A(x)$).
 In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
@@
 For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are the two nodes,
-we say that node $v_1$ is the parent node of node $v_2$ and node $v_2$ is the child node
-of node $v_1$. Further, $\mathcal{G}$ satisfies the following condition:
+we say that node $v_1$ is the parent (node) of node $v_2$ and node $v_2$ is the child (node)
+of node $v_1$. Further, $\forall H,B_1,...,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
+  \item $H$ has a parent node or a child node;
+  \item $H$ is the original fact of $P$ if $H$ has the in-degree of $0$;
+  \item $B_1,...,B_n\rightarrow H\in P^*$ is satisfied if $e(B_1, H),...,e(B_n, H)\in E$ and
+  $B_1,...,B_n$ are \d{all} the parents of $H$.
 \end{enumerate}
@@
 and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
+(2) a (partial) materialization graph $\mathcal{G}=\langle V,E\rangle$ that is constructed from $P$.
 This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
+is computed as follows:
 
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
+\item add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A(a)\rightarrow B(a)\in P^*$, $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in V$;
+
+\item add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$ where $R(a,b),A(b)\rightarrow B(a)\in P^*$, $\exists R.A\sqsubseteq B\in\mathcal{T}$ and $R(a,b)\in V$;
+
+\item add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
+    $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$ and $A_1(a)\in V$;
+
+\item add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
+    $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$ and $A_2(a)\in V$;
+
+\item add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$ where $R(a,b)\rightarrow S(a,b)\in P^*$,
+    $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in V$;
+
+\item add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$ where $R(a,b)\rightarrow S(b,a)\in P^*$,
+    $\mathcal{O}\models R\sqsubseteq_* S^-$ and $R(a,b)\in V$;
+
+\item add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$, 
+    $R_1\circ R_2\sqsubseteq R_3\in\mathcal{R}$ (the case
+    where $R_1\equiv R_2\equiv R_3$ is also involved) and $R_1(a,b)\in V$;
+
+\item add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$,
+    $R_1\circ R_2\sqsubseteq R_3\in\mathcal{R}$ and $R_2(b,c)\in V$.\hfill$\Box$
 \end{enumerate}
@@
 the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
+of ParallelDHL divided by the minimal reasoning time of RDFox;
 (2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,

### 2018-01-27 parallel-tractability-J-v9/response.tex
fixed some quotes of reviewer 2

@@
 
-...
+In the paragraph under Lemma~1, we made it clear that $|P^*|$ is polynomial in the size of $I$ for a class of datalog programs.
+
+The statement that Step~2 costs only one time unit is based on the context of one processor. Since one processor
+is allocated one rule instance (see the first paragraph of Algorithm~$\mathsf{A}_{bsc}$), 
+the procedure can be completed in constant time units. We rewrote these sentences by clarifying this.
+
+(TODO) We added a paragraph to discuss the complexity of Algorithm~$\mathsf{A}_{bsc}$.
+The constant time of checking applicability ......
 
@@
 
-...
+The requirement ``H has been added to G'' in the description of computing the rch relation $S_{\text{rch}}$ ($\dag$) is indeed
+incorrect. It should be ``H has not been added to G''. We fixed this error.
+
+(TODO) We added a paragraph to discuss the complexity of Algorithm~$\mathsf{A}_{opt}$.
+In Step~2 of Algorithm~$\mathsf{A}_{opt}$, an NC algorithm is used to compute the transitive closure of $S_{\text{rch}}$.
+It can be checked that the scale of $S_{\text{rch}}$ is less than that of $P^*$ and is in polynomial of
+the size of inputs. Thus, the NC complexity of the computation of the transitive closure can be guaranteed.
 
@@
 
-...
+(TODO) We used a paragraph to discuss this after Algorithm~$\mathsf{A}_{prc}$.
 
@@
 It deserves a clarification on what these rules are like and why they do not fall into existing parallel tractable classes.\\
-
 - p20, Table 2, it should mention how these ontologies were selected. \\
-
 - p21, the discussion on line graph lg1 is confusing (i.e.\ ``line-2 stays higher than line-6, but lower than line-4''). Maybe I was looking at the wrong place. \\
-
 - p25, the section heading ``Reference'' occur twice.

### 2018-01-27 parallel-tractability-J-v9/parallel-tractability-J.tex
fixed some quotes of reviewer 2

@@
 We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
+(\uppercase\expandafter{\romannumeral1}) Given a class of datalog programs $\mathbb{P}$ where
+a rule set is shared for each datalog program $P=\langle R, \textbf{I}\rangle$ in $\mathbb{P}$,
+it can be checked that $|P^*|$ is polynomial in the size of $\textbf{I}$. 
+This is because that each predicate occurring in $\mathbb{P}$ has a constant arity
+and Algorithm~$\mathsf{A}_{bsc}$ does not introduce
+new constants. This also means that the number of processors is polynomially bounded.
 (\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
@@
 (\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
+iteration of \ref{alg1:updateG}. Since each processor handles one rule instance, 
+\ref{alg1:updateG} costs one time unit on each processor in theory. 
+Assume that there is no delay and other communication problems among all the processors.
+We have that the computing time of \ref{alg1:updateG} of the whole algorithm costs one time unit as well.
+Further, the whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
 We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
@@
 get a class of datalog programs, denoted by $\mathbb{P}_{ex_1}$, where the rule set
-is $\{R(x,y),A(y)\rightarrow A(x), S(x,y),R(y,z)\rightarrow R(x,z)\}$ and the instance
+is $\{R(x,y),A(y)\rightarrow A(x), S(x,y),R(y,z)\rightarrow R(x,z)\}$ and the fact
 set varies according to $k$. The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{ex_1}$.
@@
 \item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
+where $H$ has not been added to $\mathcal{G}$}:
 \begin{enumerate}[leftmargin=2ex]

### 2018-01-28 parallel-tractability-J-v9/response.tex
fixed quote 1 of reviewer 2

@@
 
-(TODO) We added a paragraph to discuss the complexity of Algorithm~$\mathsf{A}_{bsc}$.
-The constant time of checking applicability ......
+The constant time of checking applicability by a processor is based on a common assumption when
+analyzing the parallel complexity. That is the problem is encoded on a parallel configuration.
+Consider materializing datalog programs by Algorithm~$\mathsf{A}_{bsc}$. This assumption allows
+us mapping all possible substitutions of the atoms and all rule instances in $P^*$ to a unique memory
+location. Since each rule instance is allocated to a processor, there is a one-to-one relation between
+processors and rule instances. In this way, a processor can check the applicability of its corresponding
+rule instance and access the states of an atom occurring in this rule instance in constant time.
+Let $a$, $b$ and $c$ represent the maximum arity of any EDB predicate, the maximum number of variables
+in any datalog rule, and the number of datalog rules respectively. 
+Since $a, b$ and $c$ depend only on the rule set, they are constants.
+We further have that the number of 
+constant is at most $|\textbf{I}|a$ and the number of all possible rule instances in $P^*$
+is at most $c(|\textbf{I}|a)^b$. 
+Thus, the memory space for storing atoms and rule instances is polynomial in the size of $\textbf{I}$. 
+It is like that there is a polynomial size of index that maps each atom and rule instance to
+the corresponding memory location.
+
+The above assumption is also used for analying the computation of transitive closures and
+the problem of boolean matrix multiplication.
+In the revision, we gave detailed information about the assumption.
 

### 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
added the analysis of the complexity of Algorithm A_{bsc}

@@
 That is, we aim to identify the ontologies for which materialization is
-parallelly tractable, i.e., in \texttt{NC} complexity.
+parallelly tractable, i.e., in NC complexity.
 The results of the parallel tractability can be further used to optimize
@@
 In this work, we focus on datalog rewritable ontology languages.
-We propose some algorithms, called \texttt{NC} algorithms, to identify several classes of datalog rewritable
+We propose some algorithms, called NC algorithms, to identify several classes of datalog rewritable
 ontologies (called \emph{parallelly tractable classes})
@@
 \begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
+ontology \sep materialization \sep datalog \sep parallel tractability \sep NC complexity
 \end{keyword}
@@
 The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
+over these ontologies is parallelly tractable, i.e., in the parallel complexity class NC \cite{Raymond95}.
 This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
+To show that a problem is in the NC class, one can give an \emph{NC algorithm} that handles this problem
 in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
+An NC algorithm is required to terminate in parallel poly-logarithmic time.
 However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
+(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not NC algorithms,
 since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
+Thus, we first give NC algorithms that perform materialization,
 and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
+that can be handled by these NC algorithms. To make the proposed NC algorithms practical,
 we also discuss how to optimize and implement them.
@@
 In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
+We first focus on the ontology language DL-Lite to clarify how to apply the above NC algorithms
 to study the parallel tractability of ontology materialization.
@@
 Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
+restricted ontologies can be handled by the proposed NC algorithms.
 We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
@@
 proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
+We implement a system based on an optimized NC algorithm for DHL materialization.
 We compare our system to the state-of-the-art reasoner RDFox.
@@
 The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
+We then give two NC algorithms for ontology materialization in Section~\ref{sec:ptclass}.
 We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
 In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
+we discuss how to optimize and implement the given NC algorithms.
 We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
@@
 
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
+\subsection{The NC Complexity}
+
+The parallel complexity class NC, known as Nick$'$s
 Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
 where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
+Specifically, a decision problem in the NC class
+can be solved in poly-logarithmic time on a PRAM (parallel, random-access machine) with 
+a polynomial number of processors. We also say that an NC problem can be solved
+in \emph{parallel poly-logarithmic time}.
+Although the NC complexity is a theoretical analysis tool,
+it has been shown that many NC problems can be solved efficiently in practice \cite{Raymond95}.
+
+From the perspective of implementations, the NC problems are also highly
 parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
+and MapReduce \cite{KarloffSV10}. The NC complexity is originally defined
 as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
+require in this work that a problem should be a decision problem in NC.
 In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
@@
 case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
+datalog programs cannot be solved in parallel poly-logarithmic time unless P=NC.
 Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
 if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
+poly-logarithmic time (this algorithm is also called an NC algorithm)}.
+In this section, we identify such classes of datalog programs by studying different NC algorithms.
 
@@
 We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
+where an NC algorithm exists for handling each datalog program in this class.
 
@@
 same rule set is shared, we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
+if there exists an NC algorithm that performs sound and complete materialization for each datalog program
 in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
@@
 
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
+According to the above definition, if we find an NC algorithm $\mathsf{A}$
 for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
@@
 However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
+(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not NC algorithms
 due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
+Thus we give our NC algorithms.
 In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
+general datalog programs. We then restrict this algorithm to an NC version
 and identify the target \texttt{PTD} class.
@@
 In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
+(denoted by Algorithm~$\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.
+Our computational model is a PRAM (parallel, random-access machine) that is mostly used to analyze the parallel
+complexity. This model allows us giving \emph{the parallel assumption}: 
+for any datalog program $P=\langle R, \textbf{I}\rangle$,
+any substitution of some atom and any rule instance in $P^*$ can be mapped to a unique memory
+location; further, a one-to-one relation can be established between processors and rule instances.
+Under this assumption, a processor can check the applicability of its corresponding
+rule instance and access the state of an atom occurring in this rule instance in constant time.
+Algorithm~$\mathsf{A}_{bsc}$ is then given as follows.\\
+
+\noindent\texttt{Algorithm~$\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
 the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
 Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
+assigned to one processor.
 Initially $\mathcal{G}$ is empty. The following three steps are then performed:
@@
 
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Given a class of datalog programs $\mathbb{P}$ where
-a rule set is shared for each datalog program $P=\langle R, \textbf{I}\rangle$ in $\mathbb{P}$,
-it can be checked that $|P^*|$ is polynomial in the size of $\textbf{I}$. 
-This is because that each predicate occurring in $\mathbb{P}$ has a constant arity
-and Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants. This also means that the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}. Since each processor handles one rule instance, 
-\ref{alg1:updateG} costs one time unit on each processor in theory. 
-Assume that there is no delay and other communication problems among all the processors.
-We have that the computing time of \ref{alg1:updateG} of the whole algorithm costs one time unit as well.
-Further, the whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
+We now discuss the parallel complexity of Algorithm~$\mathsf{A}_{bsc}$.
+Given a class of datalog programs $\mathbb{P}$ where
+a rule set is shared for each datalog program $P=\langle R, \textbf{I}\rangle$ in $\mathbb{P}$.
+Let $e$, $v$ and $r$ represent the maximum arity of any EDB predicate, the maximum number of variables
+in any datalog rule, and the number of datalog rules respectively.
+We then have that the number of
+constants is at most $|\textbf{I}|e$, and the number of all possible rule instances in $P^*$
+is at most $r(|\textbf{I}|e)^v$.
+Note that $e, v$ and $r$ depend only on the rule set $R$ and not on the fact set $\textbf{I}$.
+Thus, the memory space for storing the atoms and the rule instances is polynomial in the size of $\textbf{I}$.
+This also means that the number of processors is polynomially bounded.
+The computing time of \ref{alg1:addFacts} and \ref{alg1:halt} occupies constant time (denoted by $c_1$) because of parallelism.
+Since Algorithm~$\mathsf{A}_{bsc}$ works under the parallel assumption, one iteration of
+\ref{alg1:updateG} also costs constant time (denoted by $c_2$). Thus, 
+the whole computing time of Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+l\cdot c_2$
+where $l$ denotes the number of iterations of \ref{alg1:updateG}.
+
+When we say that an algorithm is an NC algorithm. It should meet two requirements: first,
+it works on a polynomial number of processors; second, it halts in poly-logarithmic time.
+As discussed above, Algorithm~$\mathsf{A}_{bsc}$ meets the first requirement.
+If we want to restrict Algorithm~$\mathsf{A}_{bsc}$ to be an NC algorithm,
+we can make the number of iterations of \ref{alg1:updateG} to be poly-logarithmically bounded.
 We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
+For any datalog program, if we restrict that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|\textbf{I}|)$, 
+the computing time of Algorithm~$\mathsf{A}_{bsc}$
+is $c_1+\psi(|\textbf{I}|)\cdot c_2$. With this restriction, Algorithm~$\mathsf{A}_{bsc}$ is an NC algorithm denoted by
+$\mathsf{A}_{bsc}^{\psi}$.
 
@@
 graph for each datalog program in $\mathbb{P}_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $\mathbb{P}_{ex_1}$.
+However there indeed exists an NC algorithm that can handle $\mathbb{P}_{ex_1}$.
 We discuss this in the next part.
@@
 
-It is well known that there is an \texttt{NC} algorithm for computing the
+It is well known that there is an NC algorithm for computing the
 transitive closure \cite{Allender07}.
@@
 \item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
+\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an NC
     algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
@@
 
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
+We obtain an NC variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
 It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
+time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an NC algorithm.
 Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
+$\mathsf{A}_{opt}$ is an NC algorithm.
+Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an NC variant.
 Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
@@
 we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
+We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an NC version
 when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
@@
 \item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
+\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an NC
     algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
@@
 of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
+We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an NC version when handling ontologies
 that follow the simple-concept and the simple-role restrictions.
@@
 To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
+we proposed two NC algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
 and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
@@
 parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
+on the datalog programs in these classes is in the complexity class NC.
 We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
@@
 to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
+also be restricted to an NC version, and can be implemented for practice.
 We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
@@
 We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
+As mentioned before, there exists an NC algorithm for transitivity computation.
 Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
@@
 (2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
+which can be computed by an NC algorithm on $\delta_{R}$;
 (3) for each role $R$ that is a TI role but not a transitive role,
@@
 (2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
+which can be computed by an NC algorithm on $\delta_{R}$;
 (3) for each role $R$ that is a TI but not a transitive role,

### 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
added the analysis of complexity of Algorithm A_{opt}

@@
 \subsection{A Basic Parallel Algorithm}
+\label{sec:alg-bsc}
 
@@
 \item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
+    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,
     the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
@@
 This also means that the number of processors is polynomially bounded.
-The computing time of \ref{alg1:addFacts} and \ref{alg1:halt} occupies constant time (denoted by $c_1$) because of parallelism.
+The computing time of \ref{alg1:addFacts} and \ref{alg1:halt} occupy constant time (denoted by $c_1$) because of parallelism.
 Since Algorithm~$\mathsf{A}_{bsc}$ works under the parallel assumption, one iteration of
@@
 \noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
+returns a materialization graph $\mathcal{G}$ of $P$. 
+Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
+assigned to one processor.
+Initially $\mathcal{G}$ is empty. The following steps are then performed:
 \begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
@@
 
-We obtain an NC variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an NC algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an NC algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an NC variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
+The analysis of the parallel complexity of Algorithm~$\mathsf{A}_{opt}$ is given as follows.
+We use the same symbols $e$, $v$ and $r$ that are used for analyzing the complexity of Algorithm~$\mathsf{A}_{bsc}$
+(see Section~\ref{sec:alg-bsc}). Similarly to the analysis for Algorithm~$\mathsf{A}_{bsc}$, it can be checked that 
+the number of processors is polynomial of $|\textbf{I}|$, i.e., $r(|\textbf{I}|e)^v$.
+We now consider the computing time of Algorithm~$\mathsf{A}_{opt}$. It is obvious that \ref{alg3:addFacts}
+\ref{alg3:halt} occupy constant time (denoted by $c_1$). In \ref{alg3:updateG}, the phases of
+computing $S_{\textit{\tiny rch}}$ and updating $\mathcal{G}$ also take constant time (denoted by $c_2$)
+under the parallel assumption. Recall that the number of constants is at most $|\textbf{I}|e$ (see Section~\ref{sec:alg-bsc}).
+Let $w$ and $p$ represent the maximum arity of any predicate and the number of predicates respectively.
+We have that the number of all possible substitutions of atoms is at most $p(|\textbf{I}|e)^w$.
+The relation $S_{\textit{\tiny rch}}$ consists of pairs of the atoms. Thus, the size of $S_{\textit{\tiny rch}}$
+is bounded by $p^2(|\textbf{I}|e)^{2w}$. It can be checked that the computing time of the NC algorithm for computing the transitive
+closure of $S_{\textit{\tiny rch}}$ is poly-logarithmical in the size of $\textbf{I}$, more precisely $2\log(p)+2w\log(|\textbf{I}|e)$.
+We now have that the total computing time of Algorithm~$\mathsf{A}_{opt}$ is $c_1+lc_3+2lw\log(|\textbf{I}|e)$
+where $c_3=c_2+2\log(p)$ and $l$ denotes the number of iterations of \ref{alg3:updateG}.
+
+Algorithm~$\mathsf{A}_{opt}$ can be restricted to an NC algorithm analogously to the process 
+for Algorithm~$\mathsf{A}_{bsc}$. That is the number of iterations of \ref{alg3:updateG}
+is poly-logarithmically bounded, i.e., it is bounded by $\psi(|\textbf{I}|)$
+where $\psi$ is a poly-logarithmical function. In this way, the computing time of 
+Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+c_3\psi(|\textbf{I}|)+2w\psi(|\textbf{I}|)\log(|\textbf{I}|e)$,
+which is also poly-logarithmical in the size of $\textbf{I}$. We denote the 
+NC variant of Algorithm~$\mathsf{A}_{opt}$ by $\mathsf{A}_{opt}^{\psi}$.
 

### 2018-01-29 parallel-tractability-J-v9/response.tex
filled the rebuttal of some quotes of reviewer 2

--- 2018-01-27 parallel-tractability-J-v9/response.tex
@@
 
-In the paragraph under Lemma~1, we made it clear that $|P^*|$ is polynomial in the size of $I$ for a class of datalog programs.
+We rewrote the paragraph under Lemma~1 to analyze the parallel complexity of Algorithm~$\mathsf{A}_{bsc}$. 
+We made it clear that $|P^*|$ is polynomial in the size of $I$ for a class of datalog programs.\\
 
@@
 is allocated one rule instance (see the first paragraph of Algorithm~$\mathsf{A}_{bsc}$),
-the procedure can be completed in constant time units. We rewrote these sentences by clarifying this.
+the procedure can be completed in constant time units. \\
 
-(TODO) We added a paragraph to discuss the complexity of Algorithm~$\mathsf{A}_{bsc}$.
-The constant time of checking applicability ......
+The constant time of checking applicability by a processor is based on an assumption:
+for any datalog program $P=\langle R, \textbf{I}\rangle$,
+any substitution of some atom and any rule instance in $P^*$ can be mapped to a unique memory
+location; further, a one-to-one relation can be established between processors and rule instances.
+Under this assumption, a processor can check the applicability of its corresponding
+rule instance and access the state of an atom occurring in this rule instance in constant time.
+This assumption also applies to analyzing the computation of transitive closures \cite{Allender07} and
+the problem of boolean matrix multiplication \cite{Raymond95}. Without this assumption, the program
+costs at least linear time to load the inputs. Thus, the requirements of the NC algorithms
+cannot be satisfied.\\
+
+We gave detailed information about the above assumption before Algorithm~$\mathsf{A}_{bsc}$.
 
@@
 The requirement ``H has been added to G'' in the description of computing the rch relation $S_{\text{rch}}$ ($\dag$) is indeed
-incorrect. It should be ``H has not been added to G''. We fixed this error.
+incorrect. It should be ``H has not been added to G''. We fixed this error.\\
 
-(TODO) We added a paragraph to discuss the complexity of Algorithm~$\mathsf{A}_{opt}$.
+We rewrote the paragraph under Lemma~2 to analyze the parallel complexity of Algorithm~$\mathsf{A}_{opt}$.
 In Step~2 of Algorithm~$\mathsf{A}_{opt}$, an NC algorithm is used to compute the transitive closure of $S_{\text{rch}}$.
-It can be checked that the scale of $S_{\text{rch}}$ is less than that of $P^*$ and is in polynomial of
-the size of inputs. Thus, the NC complexity of the computation of the transitive closure can be guaranteed.
+It can be checked that the scale of $S_{\text{rch}}$ is polynomial in the size of inputs.
+The total computing time is still in poly-logarithmic time (see the detailed analysis in the revision).
 
@@
 
+\bibliographystyle{elsarticle-num}
+\bibliography{response}
+
 \end{document}

### 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
filled the rebuttal of some quotes of reviewer 2

@@
 is bounded by $p^2(|\textbf{I}|e)^{2w}$. It can be checked that the computing time of the NC algorithm for computing the transitive
-closure of $S_{\textit{\tiny rch}}$ is poly-logarithmical in the size of $\textbf{I}$, more precisely $2\log(p)+2w\log(|\textbf{I}|e)$.
-We now have that the total computing time of Algorithm~$\mathsf{A}_{opt}$ is $c_1+lc_3+2lw\log(|\textbf{I}|e)$
-where $c_3=c_2+2\log(p)$ and $l$ denotes the number of iterations of \ref{alg3:updateG}.
+closure of $S_{\textit{\tiny rch}}$ is poly-logarithmical in the size of $\textbf{I}$, more precisely,
+it is upper bounded to $\log^2(p^2(|\textbf{I}|e)^{2w})$ ($=4\log^2(p)+4w^2\log^2(|\textbf{I}|e)+8w\log(p)\log(|\textbf{I}|e)$).
+We now have that the total computing time of Algorithm~$\mathsf{A}_{opt}$ is $c_1+lc_3 + lc_4\log(|\textbf{I}|e) +lc_5\log^2(|\textbf{I}|e)$
+where $c_3=c_2+4\log^2(p)$, $c_4=8w\log(p)$, $c_5=4w^2$ and $l$ denotes the number of iterations of \ref{alg3:updateG}.
 
@@
 where $\psi$ is a poly-logarithmical function. In this way, the computing time of
-Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+c_3\psi(|\textbf{I}|)+2w\psi(|\textbf{I}|)\log(|\textbf{I}|e)$,
-which is also poly-logarithmical in the size of $\textbf{I}$. We denote the 
+Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+c_3\psi(|\textbf{I}|)+c_4\psi(|\textbf{I}|)\log(|\textbf{I}|e)+
+c_5\psi(|\textbf{I}|)\log^2(|\textbf{I}|e)$,
+which is still poly-logarithmical in the size of $\textbf{I}$. We denote the
 NC variant of Algorithm~$\mathsf{A}_{opt}$ by $\mathsf{A}_{opt}^{\psi}$.
@@
 
-\section*{Reference}
-
 \bibliographystyle{elsarticle-num}

### 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
tried to add the analysis of RDFS

@@
 \subsection{Parallelly Tractable Materialization of DHL}
+\label{sec:DHL}
 
@@
 \subsection{Parallelly Tractable Materialization of DHL($\circ$)}
+\label{sec:DHLo}
 
@@
 \end{theorem}
+
+\subsection{The Parallel Tractability of the Reasoning on RDFS Ontologies}
+
+In this part, we discuss about the parallel tractability of the reasoning on RDFS ontologies.
+Although RDFS is not a standard description logic, it can be described by a subset of the DL axioms \cite{GrosofHVD03}.
+The correspondence between the RDFS statements and the DL axioms is listed in Table~\ref{tab:rdfs}.
+We call the RDFS statements in the form of (1-4) \emph{the schema data}
+(which correspond to TBox axioms), the statements in the form of (5) and (6)
+\emph{the instance data} (which correspond to ABox axioms).
+
+\begin{table}
+\begin{center}
+\begin{tabular}{lcc}
+\multicolumn{3}{c}{\textbf{Table~\ref{tab:rdfs}: The RDFS statements and the corresponding DL axioms}}\\
+\hline
+&~~~~~~~~~~~~~RDFS statements~~~~~~~~~~~~~&~~~~~~~~~~~~~~Axiom~~~~~~~~~~~~~~\\
+\hline
+\hline
+(1)&$P~~\texttt{rdfs:domain}~~C$& $\top\sqsubseteq\forall P^-.C$\\
+
+(2)&$P~~\texttt{rdfs:range}~~C$& $\top\sqsubseteq\forall P.C$\\
+
+(3)&$B~~\texttt{rdfs:subClassOf}~~C$& $B\sqsubseteq C$\\
+
+(4)&$R~~\texttt{rdfs:subPropertyOf}~~S$& $R\sqsubseteq S$\\
+\hline
+(5)&$a~~\texttt{rdf:type}~~C$& $C(a)$\\
+
+(6)&$a~~R~~b$& $R(a,b)$\\
+\hline
+\end{tabular}
+\label{tab:rdfs}
+\end{center}
+\end{table}
+
+The original rule set for the reasoning task of RDFS ontologies is
+given in \cite{RDFSrec04}. By applying the rules in this rule set,
+new schema data would be derived. Thus, the reasoning task of RDFS
+is different from the task of materialization. Further, an RDFS ontology allows
+statements about blank nodes which play as variables. This semantically
+leads to infinite entailments. The author of \cite{Horst05} proves that
+the original rule set is incomplete with the restriction that
+blank nodes cannot occur in predicate positions. By loosening this restriction,
+the rule set turns out to be complete. The computational complexity
+of the reasoning task on RDFS ontologies is shown to be NC-complete \cite{Horst05},
+which is not considered to be prallel-tractable.
+
+The situation of path twisting may also happen when conducting reasoning
+on RDFS ontologies. Suppose $R_{subp}$ denotes the RDFS built-in property $\texttt{rdfs:subPropertyOf}$.
+We define the other three properties $R_1$, $R_2$ and $R_3$ by the following axioms:
+$R_1\sqsubseteq R_{subp}, R_2\sqsubseteq R_{subp}$ and $R_{subp}\sqsubseteq R_3$.
+It can be checked that these three axioms entail the complex RIA $R_1\circ R_2\sqsubseteq R_3$ (denoted by $\beta$).
+If axiom $\beta$ does not meet the simple-role restriction (see Section~\ref{sec:DHLo}),
+the situation of path twisting may also happen as shown in Example~\ref{exp:complexRIA}.
+
+In this work, we study the task of materialization. Similarly, we can only focus on
+the entailments of new instance data for the target RDFS ontologies. To this end,
+we assume that any class of RDFS ontologies has the same schema data (\uppercase\expandafter{\romannumeral1}). In this way,
+the axioms like $\beta$ cannot contribute to the computational complexity, since they
+only apply to schema data. Further, we restrict that blank nodes cannot occur in
+any class of RDFS ontologies (\uppercase\expandafter{\romannumeral2}). This allows an RDFS ontology
+being expressed in DHL (see Table~\ref{tab:rdfs}). Based on the two restrictions (\uppercase\expandafter{\romannumeral1})
+and (\uppercase\expandafter{\romannumeral2}), the reasoning task on RDFS ontologies
+is parallel-tractable (see Section~\ref{sec:DHL}).
 

### 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
abstract shortened

--- 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
@@
 \address[add2]{
-    Institution of Artificial Intelligence, University of Ulm
+    Institute of Artificial Intelligence, University of Ulm
 }
@@
 \begin{abstract}
-Materialization is an important reasoning service for applications built
-on the ontology languages, such as OWL. With a
-rapid growth of semantic data, it is challenging to perform
-materialization on large-scale ontologies efficiently.
-Current work proposes parallel algorithms and employs computing
-platforms of high-performance to make materialization sufficiently efficient and scalable in practice.
-However, there do exist ontologies, for which
-materialization cannot always be improved by parallelism (we use experiments to show this in Section~\ref{sec:evaluation}).
-On the other hand, some well-known large-scale ontologies, such as YAGO, have been shown to have
-good performance for parallel reasoning, but they are expressed in ontology languages
-that are not parallelly tractable in theory, i.e., the efficiency of reasoning may not be improved
-on a parallel implementation.
-This motivates us to study the problem of \emph{parallel tractability} of ontology
-materialization from a theoretical perspective.
-That is, we aim to identify the ontologies for which materialization is
-parallelly tractable, i.e., in NC complexity.
-The results of the parallel tractability can be further used to optimize
-materialization algorithms and to guide ontology engineers in creating parallelly tractable ontologies.
-
-In this work, we focus on datalog rewritable ontology languages.
-We propose some algorithms, called NC algorithms, to identify several classes of datalog rewritable
-ontologies (called \emph{parallelly tractable classes})
-such that materialization over them is parallelly tractable.
-We then investigate the parallel tractability of materialization over
-two datalog rewritable ontology languages DL-Lite and DHL (\emph{Description Horn Logic}).
-We show that materialization over any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ is parallelly tractable.
-For DHL, there exist ontologies where materialization can hardly be parallelized.
-We propose to restrict the usage of DHL such that the restricted ontologies are parallelly tractable.
-We further extend the results to an extension of DHL that also allows \emph{complex role inclusion axioms}.
-To verify the practical usability of the above results, we analyze real-world datasets and show
-that many ontologies expressed in DHL or its extension belong to
-the parallelly tractable classes. Based on the results of parallel tractability,
-we further implement an optimized parallel algorithm
-and compare it to the state-of-the-art reasoner RDFox. The experimental results show that the
-optimization used in our implementation results in a better
-performance on parallelly tractable ontologies compared with RDFox.
+  Materialization is an important reasoning service for many
+  ontology-based applications, but the rapid growth of semantic data
+  poses the challenge to efficiently perform materialization on
+  large-scale ontologies. Parallel materialization algorithms work
+  well for some ontologies, which is not always explained by the
+  theoretical results. For example, for the YAGO ontology
+  parallelization works well, although the reasoning problem for the
+  used ontology language is not in \texttt{NC}, i.e.\ the theoretical
+  complexity class for \emph{parallel tractability}. This motivates us
+  to study the problem of \emph{parallel tractability} of ontology
+  materialization from a theoretical perspective. We focus on the
+  datalog rewritable ontology languages DL-Lite and Description Horn
+  Logic (DHL) and propose algorithms, called \texttt{NC} algorithms,
+  to identify classes of ontologies for which materialization is
+  tractable in parallel. To verify the practical usability of the
+  above results, we analyze real-world datasets and show that for many
+  ontologies expressed in DHL materialization is tractable in
+  parallel. The implementation of our optimized parallel algorithm
+  shows performance improvements over the highly optimized
+  state-of-the-art reasoner RDFox on ontologies for which
+  materialization is tractable in parallel.
 \end{abstract}
@@
 \begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep NC complexity
+ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
 \end{keyword}
@@
 
-There has been work proposing parallel reasoning algorithms and employing parallel computing platforms
+There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms
 for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balancing workload
-and data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}.
-On the other hand, several work utilizes different kinds of computing platforms to make reasoning tasks more efficient in parallel, such as supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
+fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
+data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
+reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
+in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
 MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
@@
 reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that some well-known large-scale ontologies, such as YAGO, have good performance for parallel
+It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
 reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, there do exist ontologies for which materialization cannot
-always be improved by parallelism (we use experiments to show this in Section~\ref{sec:evaluation}).
-The current work of parallel ontology reasoning can hardly explain this.
+On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
+always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
 While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
@@
 The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class NC \cite{Raymond95}.
+over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
 This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the NC class, one can give an \emph{NC algorithm} that handles this problem
+To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
 in parallel computation \cite{Raymond95}.
-An NC algorithm is required to terminate in parallel poly-logarithmic time.
+An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
 However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not NC algorithms,
+(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
 since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give NC algorithms that perform materialization,
+Thus, we first give \texttt{NC} algorithms that perform materialization,
 and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these NC algorithms. To make the proposed NC algorithms practical,
+that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
 we also discuss how to optimize and implement them.
@@
 In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above NC algorithms
+We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
 to study the parallel tractability of ontology materialization.
@@
 Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed NC algorithms.
+restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
 We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
@@
 proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized NC algorithm for DHL materialization.
+We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
 We compare our system to the state-of-the-art reasoner RDFox.
@@
 The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two NC algorithms for ontology materialization in Section~\ref{sec:ptclass}.
+We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
 We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
 In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given NC algorithms.
+we discuss how to optimize and implement the given \texttt{NC} algorithms.
 We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
@@
 Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is called a \emph{free variable} (it is
-not occurring in the head atom $A(x)$).
+a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
 In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
@@
 to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}
-for any class of datalog programs.
-
-\subsection{The NC Complexity}
-
-The parallel complexity class NC, known as Nick$'$s
+In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
+
+\subsection{The $\texttt{NC}$ Complexity}
+
+The parallel complexity class $\texttt{NC}$, known as Nick$'$s
 Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
 where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the NC class
-can be solved in poly-logarithmic time on a PRAM (parallel, random-access machine) with 
-a polynomial number of processors. We also say that an NC problem can be solved
-in \emph{parallel poly-logarithmic time}.
-Although the NC complexity is a theoretical analysis tool,
-it has been shown that many NC problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the NC problems are also highly
+Specifically, a decision problem in the $\texttt{NC}$ class
+can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
+We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
+Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
+it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
+
+From the perspective of implementations, the $\texttt{NC}$ problems are also highly
 parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The NC complexity is originally defined
+and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
 as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in NC.
+require in this work that a problem should be a decision problem in $\texttt{NC}$.
 In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
@@
 materialization is parallelly tractable.
-Since we assume that for any class of datalog programs where the rule
-set of each datalog program is fixed, the materialization problem is thus in data complexity
+Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
+set $R$ is fixed, the materialization problem is thus in data complexity
 $\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
 case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless P=NC.
+datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
 Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
 if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an NC algorithm)}.
-In this section, we identify such classes of datalog programs by studying different NC algorithms.
+poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
+In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
 
@@
 We first give the following definition for a parallel tractable class of datalog programs
-where an NC algorithm exists for handling each datalog program in this class.
+where an \texttt{NC} algorithm exists for handling each datalog program in this class.
 
 \begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs where the
-same rule set is shared, we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an NC algorithm that performs sound and complete materialization for each datalog program
+\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
+we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
+if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
 in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
@@
 
-According to the above definition, if we find an NC algorithm $\mathsf{A}$
+According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
 for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
@@
 However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not NC algorithms
+(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
 due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our NC algorithms.
+Thus we give our $\texttt{NC}$ algorithms.
 In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an NC version
+general datalog programs. We then restrict this algorithm to an \texttt{NC} version
 and identify the target \texttt{PTD} class.
@@
   \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
-\end{enumerate}
-For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are the two nodes,
-we say that node $v_1$ is the parent (node) of node $v_2$ and node $v_2$ is the child (node)
-of node $v_1$. Further, $\forall H,B_1,...,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
+  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
+\end{enumerate}
+~~$\mathcal{G}$ satisfies the following condition:
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $H$ has a parent node or a child node;
-  \item $H$ is the original fact of $P$ if $H$ has the in-degree of $0$;
-  \item $B_1,...,B_n\rightarrow H\in P^*$ is satisfied if $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$.
+  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
+  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
+  $B_1,...,B_n\rightarrow H\in P^*$.
 \end{enumerate}
@@
 \subsection{A Basic Parallel Algorithm}
-\label{sec:alg-bsc}
 
 In this part, we propose a parallel algorithm
-(denoted by Algorithm~$\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.
-Our computational model is a PRAM (parallel, random-access machine) that is mostly used to analyze the parallel
-complexity. This model allows us giving \emph{the parallel assumption}: 
-for any datalog program $P=\langle R, \textbf{I}\rangle$,
-any substitution of some atom and any rule instance in $P^*$ can be mapped to a unique memory
-location; further, a one-to-one relation can be established between processors and rule instances.
-Under this assumption, a processor can check the applicability of its corresponding
-rule instance and access the state of an atom occurring in this rule instance in constant time.
-Algorithm~$\mathsf{A}_{bsc}$ is then given as follows.\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
+(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
+
+\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
 the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
+Recall that $P^*$ denotes the ground instantiation of $P$,
+which consists of all possible ground instantiations of rules in $R$.
 Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.
+assigned to one processor.\footnote{This might not be practically feasible,
+but we focus on a theoretical analysis here.}
 Initially $\mathcal{G}$ is empty. The following three steps are then performed:
@@
 \item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,
+    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
+    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
+    atom has been added to the materialization graph. This can be implemented by maintaining an
+    index of polynomial size.}
     the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
@@
 
-We now discuss the parallel complexity of Algorithm~$\mathsf{A}_{bsc}$.
-Given a class of datalog programs $\mathbb{P}$ where
-a rule set is shared for each datalog program $P=\langle R, \textbf{I}\rangle$ in $\mathbb{P}$.
-Let $e$, $v$ and $r$ represent the maximum arity of any EDB predicate, the maximum number of variables
-in any datalog rule, and the number of datalog rules respectively.
-We then have that the number of
-constants is at most $|\textbf{I}|e$, and the number of all possible rule instances in $P^*$
-is at most $r(|\textbf{I}|e)^v$.
-Note that $e, v$ and $r$ depend only on the rule set $R$ and not on the fact set $\textbf{I}$.
-Thus, the memory space for storing the atoms and the rule instances is polynomial in the size of $\textbf{I}$.
-This also means that the number of processors is polynomially bounded.
-The computing time of \ref{alg1:addFacts} and \ref{alg1:halt} occupy constant time (denoted by $c_1$) because of parallelism.
-Since Algorithm~$\mathsf{A}_{bsc}$ works under the parallel assumption, one iteration of
-\ref{alg1:updateG} also costs constant time (denoted by $c_2$). Thus, 
-the whole computing time of Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+l\cdot c_2$
-where $l$ denotes the number of iterations of \ref{alg1:updateG}.
-
-When we say that an algorithm is an NC algorithm. It should meet two requirements: first,
-it works on a polynomial number of processors; second, it halts in poly-logarithmic time.
-As discussed above, Algorithm~$\mathsf{A}_{bsc}$ meets the first requirement.
-If we want to restrict Algorithm~$\mathsf{A}_{bsc}$ to be an NC algorithm,
-we can make the number of iterations of \ref{alg1:updateG} to be poly-logarithmically bounded.
+We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
+(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
+new constants and each predicate has a constant arity,
+one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
+the number of processors is polynomially bounded.
+(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
+and \ref{alg1:halt} occupies constant time units because of parallelism.
+(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
+iteration of \ref{alg1:updateG}.
+In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
+Thus, in theory, \ref{alg1:updateG} costs one time unit.
+The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
 We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-For any datalog program, if we restrict that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|\textbf{I}|)$, 
-the computing time of Algorithm~$\mathsf{A}_{bsc}$
-is $c_1+\psi(|\textbf{I}|)\cdot c_2$. With this restriction, Algorithm~$\mathsf{A}_{bsc}$ is an NC algorithm denoted by
-$\mathsf{A}_{bsc}^{\psi}$.
+The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
+Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
+\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
+for any datalog program $P$, if we use $\psi(|P|)$ to
+bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
+is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
+means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
 
@@
 
-Consider Example~\ref{exp:mg} again. Let the integer $k$ be a variable. We can
-get a class of datalog programs, denoted by $\mathbb{P}_{ex_1}$, where the rule set
-is $\{R(x,y),A(y)\rightarrow A(x), S(x,y),R(y,z)\rightarrow R(x,z)\}$ and the fact
-set varies according to $k$. The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{ex_1}$.
-It can be checked that, for some materialization graph $\mathcal{G}_{ex_1}$
-corresponding to a datalog program in $\mathbb{P}_{ex_1}$, \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$ for some $k$.
-This means that the depths of the materialization graphs are linearly bounded by $k$.
-On the other hand, the sizes of the datalog programs in $\mathbb{P}_{ex_1}$ are polynomial of $k$.
+The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
+rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
+The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
+One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
+This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
+On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
 Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
 enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph for each datalog program in $\mathbb{P}_{ex_1}$.
-However there indeed exists an NC algorithm that can handle $\mathbb{P}_{ex_1}$.
+graph of $P_{ex_1}$.
+However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
 We discuss this in the next part.
@@
 \item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has not been added to $\mathcal{G}$}:
+where $H$ has been added to $\mathcal{G}$}:
 \begin{enumerate}[leftmargin=2ex]
@@
 
-It is well known that there is an NC algorithm for computing the
+It is well known that there is an \texttt{NC} algorithm for computing the
 transitive closure \cite{Allender07}.
@@
 \noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. 
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
+returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
 \begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
 \item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an NC
+\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
     algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
@@
 
-The analysis of the parallel complexity of Algorithm~$\mathsf{A}_{opt}$ is given as follows.
-We use the same symbols $e$, $v$ and $r$ that are used for analyzing the complexity of Algorithm~$\mathsf{A}_{bsc}$
-(see Section~\ref{sec:alg-bsc}). Similarly to the analysis for Algorithm~$\mathsf{A}_{bsc}$, it can be checked that 
-the number of processors is polynomial of $|\textbf{I}|$, i.e., $r(|\textbf{I}|e)^v$.
-We now consider the computing time of Algorithm~$\mathsf{A}_{opt}$. It is obvious that \ref{alg3:addFacts}
-\ref{alg3:halt} occupy constant time (denoted by $c_1$). In \ref{alg3:updateG}, the phases of
-computing $S_{\textit{\tiny rch}}$ and updating $\mathcal{G}$ also take constant time (denoted by $c_2$)
-under the parallel assumption. Recall that the number of constants is at most $|\textbf{I}|e$ (see Section~\ref{sec:alg-bsc}).
-Let $w$ and $p$ represent the maximum arity of any predicate and the number of predicates respectively.
-We have that the number of all possible substitutions of atoms is at most $p(|\textbf{I}|e)^w$.
-The relation $S_{\textit{\tiny rch}}$ consists of pairs of the atoms. Thus, the size of $S_{\textit{\tiny rch}}$
-is bounded by $p^2(|\textbf{I}|e)^{2w}$. It can be checked that the computing time of the NC algorithm for computing the transitive
-closure of $S_{\textit{\tiny rch}}$ is poly-logarithmical in the size of $\textbf{I}$, more precisely $2\log(p)+2w\log(|\textbf{I}|e)$.
-We now have that the total computing time of Algorithm~$\mathsf{A}_{opt}$ is $c_1+lc_3+2lw\log(|\textbf{I}|e)$
-where $c_3=c_2+2\log(p)$ and $l$ denotes the number of iterations of \ref{alg3:updateG}.
-
-Algorithm~$\mathsf{A}_{opt}$ can be restricted to an NC algorithm analogously to the process 
-for Algorithm~$\mathsf{A}_{bsc}$. That is the number of iterations of \ref{alg3:updateG}
-is poly-logarithmically bounded, i.e., it is bounded by $\psi(|\textbf{I}|)$
-where $\psi$ is a poly-logarithmical function. In this way, the computing time of 
-Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+c_3\psi(|\textbf{I}|)+2w\psi(|\textbf{I}|)\log(|\textbf{I}|e)$,
-which is also poly-logarithmical in the size of $\textbf{I}$. We denote the 
-NC variant of Algorithm~$\mathsf{A}_{opt}$ by $\mathsf{A}_{opt}^{\psi}$.
+We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
+It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
+time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
+Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
+$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
+Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
+Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
+is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
 
@@
 such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontology classes such that Algorithm~$\mathsf{A}_{opt}^\psi$
+However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
 does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
@@
 \begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_5}$
+Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
 where its TBox and RBox contain the following axioms:
@@
 its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_5}$ by $P_{ex_5}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
 where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
 as the only fact.
-The unique materialization graph of $P_{ex_5}$ is denoted by $\mathcal{G}_{ex_5}$ (see Figure~\ref{fig:ex2}).
+The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
 \end{example}
@@
 \includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_5}$.}
+\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
 \label{fig:ex2}
@@
 
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_5}$ in Example~\ref{exp:dllite}.
+Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
 (\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_5}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
+to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
 (\uppercase\expandafter{\romannumeral2}) In the first iteration of
@@
 starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_5}$ immediately. We take an example of node $B_1(a)$,
+adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
 for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_5}$ by adding $B_1(a)$ to it,
+When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
 Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_5}$; if $A(a)$ is already in $\mathcal{G}_{ex_5}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_5}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_5}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_5}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
+has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
+is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
+if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
+to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
 an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
@@
 (\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_5}$
+Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
 after two iterations (\ref{alg3:halt}).
@@
 of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_5}$ of
+(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
 Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
@@
 In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontology classes such that Algorithm~$\mathsf{A}_{opt}^\psi$
+Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
 does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such a case
+In the following, we first give such an ontology
 to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
@@
 form $B_1\sqcap B_2\sqsubseteq A$
-makes it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
+may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
 in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
@@
 \includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_6}$;
-(right) The materialization graph of $\mathcal{O}_{ex_7}$.}
+\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
+(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
 \label{fig:ex3_4}
@@
 \begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_6}$ where its TBox contains three axioms:
+Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
@@
 for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_6}$ by $P_{ex_6}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
 where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_6}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_6}$ (see Figure~\ref{fig:ex3_4}(left)).
+The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
 \end{example}
 
-One can check that $\mathcal{G}_{ex_6}$ is the unique materialization graph of $P_{ex_6}$.
+One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
 Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_6}$, it can be checked that
+When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
 each node of the form $A(a_i)$ (filled with black color,
 and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_6}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_6}$.
-Similar to the datalog program class $\mathbb{P}_{ex_1}$, we can also get a
-datalog program class $\mathbb{P}_{ex_6}$ for the ontology $\mathcal{O}_{ex_6}$
-when $k$ is a variable. Based on the above analysis, Algorithm~$\mathsf{A}_{opt}$ cannot complete the materialization
-for the datalog programs of $\mathbb{P}_{ex_6}$ in a poly-logarithmical
+in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
+and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
+Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
 number of iterations.
@@
 That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_6}$, there would not exist an available SWD path for $A(a_i)$.
+to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
 We use `\emph{path twisting}' to represent such cases.
@@
 \begin{example}\label{exp:simpleC}
-Consider an ontology $\mathcal{O}_{ex_7}$ where the TBox contains three axioms:
+Consider an ontology where the TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
@@
 for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_7}$ where the rule set contains:
+We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
 `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_7}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_7}$ (see Figure~\ref{fig:ex3_4}(right)).
+$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
 \end{example}
@@
 This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_7}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
+Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
 two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_7}$,
+adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
 since they have corresponding SWD paths;
 after that, all the other nodes
-can be added to $\mathcal{G}_{ex_7}$ in the second iteration (because each
+can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
 node has an SWD path).
@@
 \begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_9}$ where its TBox is empty;
+Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
 the RBox $\mathcal{R}$ contains three axioms:
@@
 `$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_9}$.
+The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
 \end{example}
 
-One can check that the materialization graph $\mathcal{G}_{ex_9}$ has the same shape as that
-of $\mathcal{G}_{ex_6}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_9}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
+One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
+of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
+A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
 Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
@@
 \begin{example}
-For the ontology $\mathcal{O}_{ex_7}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_7}$ does not follow
+For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
+$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
 the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
@@
 we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an NC version
+We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
 when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
@@
 and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}=\langle V,E\rangle$ that is constructed from $P$.
+(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
 This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed as follows:
+is computed from the following rule instantiations:
 
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A(a)\rightarrow B(a)\in P^*$, $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in V$;
-
-\item add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$ where $R(a,b),A(b)\rightarrow B(a)\in P^*$, $\exists R.A\sqsubseteq B\in\mathcal{T}$ and $R(a,b)\in V$;
-
-\item add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
-    $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$ and $A_1(a)\in V$;
-
-\item add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
-    $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$ and $A_2(a)\in V$;
-
-\item add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$ where $R(a,b)\rightarrow S(a,b)\in P^*$,
-    $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in V$;
-
-\item add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$ where $R(a,b)\rightarrow S(b,a)\in P^*$,
-    $\mathcal{O}\models R\sqsubseteq_* S^-$ and $R(a,b)\in V$;
-
-\item add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$,
-    $R_1\circ R_2\sqsubseteq R_3\in\mathcal{R}$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved) and $R_1(a,b)\in V$;
-
-\item add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$,
-    $R_1\circ R_2\sqsubseteq R_3\in\mathcal{R}$ and $R_2(b,c)\in V$.\hfill$\Box$
+\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
+    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
+
+\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
+    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
+
+\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
+    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
+    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
+
+\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
+    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
+
+\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
+    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
+
+\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
+    where $R_1\equiv R_2\equiv R_3$ is also involved),
+    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
+    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
 \end{enumerate}
@@
 \item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an NC
+\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
     algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
@@
 of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an NC version when handling ontologies
+We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
 that follow the simple-concept and the simple-role restrictions.
@@
 the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL divided by the minimal reasoning time of RDFox;
+of ParallelDHL devided by the minimal reasoning time of RDFox;
 (2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
@@
 To identify the parallelly tractable classes,
-we proposed two NC algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
+we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
 and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
@@
 parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class NC.
+on the datalog programs in these classes is in the complexity class \texttt{NC}.
 We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
@@
 to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an NC version, and can be implemented for practice.
+also be restricted to an \texttt{NC} version, and can be implemented for practice.
 We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
@@
 We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an NC algorithm for transitivity computation.
+As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
 Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
@@
 (2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an NC algorithm on $\delta_{R}$;
+which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
 (3) for each role $R$ that is a TI role but not a transitive role,
@@
 (2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an NC algorithm on $\delta_{R}$;
+which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
 (3) for each role $R$ that is a TI but not a transitive role,

### 2018-01-29 parallel-tractability-J-v9/appendix.tex
splitting the main file for better organization

--- 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
@@
-%\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
- \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-\usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-\usepackage{amsmath}
-
-\usepackage{CJK}
-\usepackage{color}
-
-\usepackage{enumitem}
-\usepackage{rotating}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-%\journal{Nuclear Physics B}
-
-\hyphenation{data-log}
-
-\begin{document}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Parallel Tractability of Ontology\\
-Materialization: Technique and Practice}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author[add1]{Zhangquan Zhou \corref{cor1}}
-\ead{quanzz1129@gmail.com}
-\cortext[cor1]{Corresponding author}
-
-\author[add1]{Guilin Qi}
-\ead{gqi@seu.edu.cn}
-
-\author[add2]{Birte Glimm}
-\ead{birte.glimm@uni-ulm.de}
-
-\address[add1]{
-    School of Computer Science, Southeast University, China
-}
-
-\address[add2]{
-    Institute of Artificial Intelligence, University of Ulm
-}
-
-\begin{abstract}
-  Materialization is an important reasoning service for many
-  ontology-based applications, but the rapid growth of semantic data
-  poses the challenge to efficiently perform materialization on
-  large-scale ontologies. Parallel materialization algorithms work
-  well for some ontologies, which is not always explained by the
-  theoretical results. For example, for the YAGO ontology
-  parallelization works well, although the reasoning problem for the
-  used ontology language is not in \texttt{NC}, i.e.\ the theoretical
-  complexity class for \emph{parallel tractability}. This motivates us
-  to study the problem of \emph{parallel tractability} of ontology
-  materialization from a theoretical perspective. We focus on the
-  datalog rewritable ontology languages DL-Lite and Description Horn
-  Logic (DHL) and propose algorithms, called \texttt{NC} algorithms,
-  to identify classes of ontologies for which materialization is
-  tractable in parallel. To verify the practical usability of the
-  above results, we analyze real-world datasets and show that for many
-  ontologies expressed in DHL materialization is tractable in
-  parallel. The implementation of our optimized parallel algorithm
-  shows performance improvements over the highly optimized
-  state-of-the-art reasoner RDFox on ontologies for which
-  materialization is tractable in parallel.
-\end{abstract}
-
-\begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-\section{Introduction}
-\label{sec:introduction}
-
-The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
-are being generated at an increasing pace by sensor networks, government authorities and social
-media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.
-
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
-MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
-
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
-While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
-for which parallel tractability can be guaranteed theoretically.
-
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
-This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
-we also discuss how to optimize and implement them.
-
-In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
-We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
-in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
-Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
-We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
-
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
-In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
-
-\section{Background Knowledge}
-\label{sec:background}
-
-In this section, we introduce some basic notions that are needed to introduce our approach.
-
-\subsection{Datalog}
-
-We discuss the main issues in this paper using standard datalog notions.
-In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
-constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
-represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
-of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
-the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
-A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
-For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
-with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
-if each defined $A\theta$ is a ground atom.
-A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
-the terms in this rule with respect to a finite set of constants occurring in $P$.
-Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
-The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
-while the predicates that may occur as head atoms are called \emph{IDB predicates}.
-
-\subsection{DHL and DL-Lite}
-
-In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
-to denote three disjoint countably
-infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
-The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
-where $R^-$ is the \emph{inverse role} of $R$.
-For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
-
-DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
-intersection of description logic (DL) and datalog in terms of expressivity.
-We define a DHL ontology $\mathcal{O}$ as a triple:
-$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
-$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
-$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
-$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
-In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
-are roles in $\textbf{R}$.
-For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
-equivalent form $\exists R^-.A\sqsubseteq B$.
-
-DHL is related with other ontology languages.
-First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
-Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
-Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
-However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
-materialization.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
-\hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
-\hline
-\hline
-(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
-(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
-(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
-(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\
-
-\hline
-(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
-(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
-(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
-(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\
-
-\hline
-(A1)& $A(a)$& $A(a)$\\
-(A2)& $R(a,b)$& $R(a,b)$\\
-\hline
-\end{tabular}
-\label{tab:dhl}
-\end{center}
-\end{table}
-
-In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
-In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
-that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
-RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
-axioms of the forms (R1-R4). Note that (R3) is actually a special
-case of (R4).
-
-DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
-and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
-(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
-where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
-an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
-which allows involving RBoxes that contain axioms of the forms (R1-R2).
-If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
-in the following paragraphs}.
-
-\subsection{Ontology Materialization via Datalog Programs}
-
-An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
-(see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
-
-In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
-$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
-Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
-between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
-usage of highly expressive ontology languages \cite{HorrocksS04}.
-Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
-occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.
-
-Based on the above representations, ontology materialization
-corresponds to the evaluation of datalog programs.
-Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
-where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
- $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
-The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
-and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
-$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
-We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
-to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
-
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
-Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
-where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
-as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
-In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
-are implemented on shared-memory platforms, we
-study all the issues in this work by assuming that the running machines are in
-shared-memory configurations.
-
-\section{Parallel Tractability of Datalog Programs}
-\label{sec:ptclass}
-
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
-if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
-
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
-
-\begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
-\end{definition}
-
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
-for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
-which is the class of all datalog programs that can be handled by $\mathsf{A}$.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
-In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
-and identify the target \texttt{PTD} class.
-
-\subsection{Materialization Graph}
-
-In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
-
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
-\end{enumerate}
-\end{definition}
-
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
-We next give an example of a materialization graph.\\
-
-\begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
-$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
-the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
-where $\textbf{I}$ contains all the assertions in the ABox
-and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
-and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
-each of the other nodes corresponds to a ground instantiation of some rule.
-For example, the node $A(a_k)$ corresponds to the ground rule instantiation
-`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
-The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
-\label{fig:mg}
-\end{center}
-\end{figure}
-
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
-The set of nodes in a complete materialization graph is actually the result
-of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
-a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
-It should also be noted that there may exist several materialization graphs for a datalog program.
-
-\subsection{A Basic Parallel Algorithm}
-
-In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
-Initially $\mathcal{G}$ is empty. The following three steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
-    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
-Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
-\end{example}
-
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
-materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
-in the appendix.
-
-\begin{lemma}
-\label{lemma:a1}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-\begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}[Proof sketch] This lemma can be proved by performing
-an induction on $T_R^{\omega}(\textbf{I})$.
-The stage (see the related contents in Section~\ref{sec:background}) of $P$
-is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
-its depth equals the depth of the stage.
-\end{proof}
-
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
-We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
-
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
-We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
-
-\begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
-\end{theorem}
-
-\begin{proof}[Proof sketch]
-We can first prove that the number of iterations
-of \ref{alg1:updateG} is actually the depth of the constructed materialization
-graph. This theorem then follows by considering
-Lemma~\ref{lemma:a1}.
-\end{proof}
-
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
-Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
-We discuss this in the next part.
-
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
-
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
-we can identify another \texttt{PTD} class.
-
-We discuss our optimization based on a specific case in Example~\ref{exp:general}.
-We find that, in this kind of case, the construction of a materialization graph can be accelerated.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
-\label{fig:general}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
-Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
-is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
-The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
-In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
-All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
-afterwards.
-\end{example}
-
-In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
-node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
-Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
-$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
-$\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
-due to the single-way derivability condition.
-
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
-can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
-
-We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
-describe the reachability between two nodes. To this extent, we use a
-binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
-e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
-
-\begin{description}[leftmargin=2ex]
-\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
-\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
-\end{enumerate}
-\end{description}
-
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
-The following algorithm applies this optimization strategy.\\
-
-\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
-a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
-being constructed from $P$. The following steps are performed:
-\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
-that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
-    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
-    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
-\end{enumerate}
-
-It is well known that there is an \texttt{NC} algorithm for computing the
-transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
-    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
-\end{enumerate}
-
-It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
-
-\begin{lemma}\label{lemma:a3}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
-\end{lemma}
-
-\begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
-In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
-one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
-in the first iteration of \ref{alg3:updateG}.
-\end{example}
-
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
-
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
-
-\begin{corollary}
-For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{corollary}
-
-\begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
-if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
-\end{proof}
-
-\section{Parallel Tractability of Ontology Materialization in OWL}
-\label{sec:ptonto}
-
-In this section, we study the issue of parallel tractability
-for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
-there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
-work by studying specific cases.
-Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
-of materialization.
-
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
-
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
-DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
-there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
-In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
-the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
-
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
-we use the following example.
-
-\begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
-where its TBox and RBox contain the following axioms:
-$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
-its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
-where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
-as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
-\label{fig:ex2}
-\end{center}
-\end{figure}
-
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
-(\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
-$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
-for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
-since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
-$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
-(\uppercase\expandafter{\romannumeral3})
-The two nodes $\bot(a)$ and $\bot(b)$
-have no SWD path in the first iteration of \ref{alg3:updateG}.
-They are left to be processed in the second iteration.
-(\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
-after two iterations (\ref{alg3:halt}).
-
-From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
-
-\begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
-\end{lemma}
-
-The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
-have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
-of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
-an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
-more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
-
-\begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL}
-
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
-Based on the analysis of this case, we propose to restrict
-the usage of DHL in order to achieve parallel tractability
-of materialization.
-
-We find that, an unlimited usage of axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
-\label{fig:ex3_4}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
-where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
-\end{example}
-
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
-each node of the form $A(a_i)$ (filled with black color,
-and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
-number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
-
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
-we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
-to avoid `path twisting'. An intuitive idea is to
-ensure that \emph{there is only one path between each two atoms of the form $A(x)$
-generated from the rules corresponding to (T1)}.
-We explain it by using the following example where the ontology is modified from
-that in Example~\ref{exp:dhl}.
-
-\begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
-`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
-\end{example}
-
-In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
-of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
-since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
-node has an SWD path).
-Motivated by this example, we consider restricting the usage of
-the axioms $B_1\sqcap B_2\sqsubseteq A$
-such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
-for some $y$.
-To this end, we first define \emph{simple concepts} as follows:
-
-\begin{definition}
-Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
-of some axiom; or (2) $A$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
-\end{enumerate}
-\end{definition}
-
-Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
-is generated from the rules corresponding to (T1).
-
-\begin{example}
-In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
-non-simple concepts.
-In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
-the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
-\end{example}
-
-We define the following class of DHL ontologies based on the above restriction and
-give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
-
-\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
-each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
-$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
-\end{definition}
-
-\begin{theorem}\label{theorem:dhl}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
-
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
-In addition to the rules in DHL, we also have to consider complex RIAs (R4).
-We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
-\begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
-the RBox $\mathcal{R}$ contains three axioms:
-$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
-the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
-contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
-`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
-\end{example}
-
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
-Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
-
-Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
-we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
-then, at least one of $R_1$ and $R_2$ is
-a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
-We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
-we can get a complex RIA in the form of
-$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
-If one of $R_1$ and $R_2$ is not a simple role, the corresponding
-rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
-and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
-Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
-For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
-role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
-a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
-Further, the situation of path twisting also exists.
-To tackle the above issue,
-we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
-Combined with the simple-concept restriction,
-we define a class of DHL($\circ$) ontologies as follows:
-
-\begin{definition}\label{def:dhlplus}
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
-is rewritten from a DHL($\circ$) ontology and the following
-conditions are satisfied:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
-\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
-\end{enumerate}
-\end{definition}
-
-\begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
-the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
-in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
-\end{example}
-
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
-
-\begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
-\label{sec:practicalAlg}
-
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
-
-\subsection{Reducing Computing Space}
-
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
-However, this algorithm can hardly work in practice due to its inherently
-high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
-Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
-when the target datalog program or ontology
-tends to be large in size.
-On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
-we can observe that the rule instantiations used for the construction
-of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
-by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-each of the checked rule instantiations should involve at least one body atom that has been
-added to the constructed materialization graph}.
-Since DHL$(\circ)$
-is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
-as follows.
-
-We first consider a datalog rule of the
-form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
-of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
-graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
-the datalog rule `$A(x)\rightarrow B(x)$'
-has only one rule instantiation `$A(a)\rightarrow B(a)$' where
-the variable $x$ is substituted by the constant $a$.
-The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
-`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
-at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
-added to $\mathcal{G}$.
-Note that, for rule instantiations of two body atoms,
-we do not require that both of these two body atoms have been added to
-the constructed materialization graph.
-Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
-
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
-
-We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
-and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
-narrowing down the scope of rule instantiations to be checked as well. This can be described
-by the following algorithm.\\
-
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
-and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
-
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
-\end{enumerate}
-
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
-datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
-returns a materialization graph $\mathcal{G}$ of $P$.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
-    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
-DHL$(\circ)$ materialization.
-
-\begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
-all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
-an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
-are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
-\end{example}
-
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
-
-\begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
-and compare it to the reasoning system RDFox.
-
-\subsection{Practical Usability of the Theoretical Results}
-
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
-facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
-
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
-
-\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
-
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
-
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
-
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
-
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
-restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
-
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
-\hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
-\hline
-
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
-\end{tabular}
-\label{tab:info}
-\end{center}
-
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
-
-\textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
-
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
-\end{center}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-\label{tab:expresult}
-\end{center}
-
-\section{Related Work}
-\label{sec:related}
-
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-There is work that studies parallel reasoning in RDFS and OWL.
-The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
-The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
-Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data).
-The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets.
-On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}.
-In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
-
-Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
-The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
-Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
-This is not the focus in this paper.
-
-Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data.
-The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
-datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
-
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
-
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
-other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
-have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
-explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
-study how to further apply the
-results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
-
-\section*{Acknowledgments}
-
-This work was partially supported by NSFC
-grant 61672153 and the 863 program under Grant
-2015AA015406.
-
-\section*{Reference}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{reference}
-
-\clearpage
-
 \section*{Appendix}
@@
 
-\end{document}
-\endinput
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-01-29 parallel-tractability-J-v9/background.tex
splitting the main file for better organization

--- 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
@@
-%\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
- \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-\usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-\usepackage{amsmath}
-
-\usepackage{CJK}
-\usepackage{color}
-
-\usepackage{enumitem}
-\usepackage{rotating}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-%\journal{Nuclear Physics B}
-
-\hyphenation{data-log}
-
-\begin{document}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Parallel Tractability of Ontology\\
-Materialization: Technique and Practice}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author[add1]{Zhangquan Zhou \corref{cor1}}
-\ead{quanzz1129@gmail.com}
-\cortext[cor1]{Corresponding author}
-
-\author[add1]{Guilin Qi}
-\ead{gqi@seu.edu.cn}
-
-\author[add2]{Birte Glimm}
-\ead{birte.glimm@uni-ulm.de}
-
-\address[add1]{
-    School of Computer Science, Southeast University, China
-}
-
-\address[add2]{
-    Institute of Artificial Intelligence, University of Ulm
-}
-
-\begin{abstract}
-  Materialization is an important reasoning service for many
-  ontology-based applications, but the rapid growth of semantic data
-  poses the challenge to efficiently perform materialization on
-  large-scale ontologies. Parallel materialization algorithms work
-  well for some ontologies, which is not always explained by the
-  theoretical results. For example, for the YAGO ontology
-  parallelization works well, although the reasoning problem for the
-  used ontology language is not in \texttt{NC}, i.e.\ the theoretical
-  complexity class for \emph{parallel tractability}. This motivates us
-  to study the problem of \emph{parallel tractability} of ontology
-  materialization from a theoretical perspective. We focus on the
-  datalog rewritable ontology languages DL-Lite and Description Horn
-  Logic (DHL) and propose algorithms, called \texttt{NC} algorithms,
-  to identify classes of ontologies for which materialization is
-  tractable in parallel. To verify the practical usability of the
-  above results, we analyze real-world datasets and show that for many
-  ontologies expressed in DHL materialization is tractable in
-  parallel. The implementation of our optimized parallel algorithm
-  shows performance improvements over the highly optimized
-  state-of-the-art reasoner RDFox on ontologies for which
-  materialization is tractable in parallel.
-\end{abstract}
-
-\begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-\section{Introduction}
-\label{sec:introduction}
-
-The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
-are being generated at an increasing pace by sensor networks, government authorities and social
-media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.
-
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
-MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
-
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
-While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
-for which parallel tractability can be guaranteed theoretically.
-
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
-This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
-we also discuss how to optimize and implement them.
-
-In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
-We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
-in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
-Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
-We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
-
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
-In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
-
 \section{Background Knowledge}
@@
 to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
+In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}
+for any class of datalog programs.
 
-\subsection{The $\texttt{NC}$ Complexity}
+\subsection{The NC Complexity}
 
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
+The parallel complexity class NC, known as Nick$'$s
 Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
 where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
+Specifically, a decision problem in the NC class
+can be solved in poly-logarithmic time on a PRAM (parallel, random-access machine) with
+a polynomial number of processors. We also say that an NC problem can be solved
+in \emph{parallel poly-logarithmic time}.
+Although the NC complexity is a theoretical analysis tool,
+it has been shown that many NC problems can be solved efficiently in practice \cite{Raymond95}.
 
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
+From the perspective of implementations, the NC problems are also highly
 parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
+and MapReduce \cite{KarloffSV10}. The NC complexity is originally defined
 as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
+require in this work that a problem should be a decision problem in NC.
 In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
@@
 
-\section{Parallel Tractability of Datalog Programs}
-\label{sec:ptclass}
-
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
-if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
-
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
-
-\begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
-\end{definition}
-
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
-for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
-which is the class of all datalog programs that can be handled by $\mathsf{A}$.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
-In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
-and identify the target \texttt{PTD} class.
-
-\subsection{Materialization Graph}
-
-In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
-
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
-\end{enumerate}
-\end{definition}
-
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
-We next give an example of a materialization graph.\\
-
-\begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
-$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
-the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
-where $\textbf{I}$ contains all the assertions in the ABox
-and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
-and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
-each of the other nodes corresponds to a ground instantiation of some rule.
-For example, the node $A(a_k)$ corresponds to the ground rule instantiation
-`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
-The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
-\label{fig:mg}
-\end{center}
-\end{figure}
-
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
-The set of nodes in a complete materialization graph is actually the result
-of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
-a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
-It should also be noted that there may exist several materialization graphs for a datalog program.
-
-\subsection{A Basic Parallel Algorithm}
-
-In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
-Initially $\mathcal{G}$ is empty. The following three steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
-    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
-Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
-\end{example}
-
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
-materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
-in the appendix.
-
-\begin{lemma}
-\label{lemma:a1}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-\begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}[Proof sketch] This lemma can be proved by performing
-an induction on $T_R^{\omega}(\textbf{I})$.
-The stage (see the related contents in Section~\ref{sec:background}) of $P$
-is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
-its depth equals the depth of the stage.
-\end{proof}
-
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
-We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
-
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
-We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
-
-\begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
-\end{theorem}
-
-\begin{proof}[Proof sketch]
-We can first prove that the number of iterations
-of \ref{alg1:updateG} is actually the depth of the constructed materialization
-graph. This theorem then follows by considering
-Lemma~\ref{lemma:a1}.
-\end{proof}
-
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
-Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
-We discuss this in the next part.
-
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
-
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
-we can identify another \texttt{PTD} class.
-
-We discuss our optimization based on a specific case in Example~\ref{exp:general}.
-We find that, in this kind of case, the construction of a materialization graph can be accelerated.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
-\label{fig:general}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
-Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
-is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
-The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
-In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
-All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
-afterwards.
-\end{example}
-
-In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
-node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
-Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
-$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
-$\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
-due to the single-way derivability condition.
-
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
-can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
-
-We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
-describe the reachability between two nodes. To this extent, we use a
-binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
-e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
-
-\begin{description}[leftmargin=2ex]
-\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
-\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
-\end{enumerate}
-\end{description}
-
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
-The following algorithm applies this optimization strategy.\\
-
-\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
-a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
-being constructed from $P$. The following steps are performed:
-\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
-that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
-    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
-    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
-\end{enumerate}
-
-It is well known that there is an \texttt{NC} algorithm for computing the
-transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
-    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
-\end{enumerate}
-
-It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
-
-\begin{lemma}\label{lemma:a3}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
-\end{lemma}
-
-\begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
-In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
-one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
-in the first iteration of \ref{alg3:updateG}.
-\end{example}
-
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
-
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
-
-\begin{corollary}
-For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{corollary}
-
-\begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
-if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
-\end{proof}
-
-\section{Parallel Tractability of Ontology Materialization in OWL}
-\label{sec:ptonto}
-
-In this section, we study the issue of parallel tractability
-for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
-there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
-work by studying specific cases.
-Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
-of materialization.
-
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
-
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
-DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
-there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
-In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
-the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
-
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
-we use the following example.
-
-\begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
-where its TBox and RBox contain the following axioms:
-$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
-its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
-where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
-as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
-\label{fig:ex2}
-\end{center}
-\end{figure}
-
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
-(\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
-$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
-for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
-since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
-$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
-(\uppercase\expandafter{\romannumeral3})
-The two nodes $\bot(a)$ and $\bot(b)$
-have no SWD path in the first iteration of \ref{alg3:updateG}.
-They are left to be processed in the second iteration.
-(\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
-after two iterations (\ref{alg3:halt}).
-
-From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
-
-\begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
-\end{lemma}
-
-The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
-have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
-of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
-an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
-more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
-
-\begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL}
-
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
-Based on the analysis of this case, we propose to restrict
-the usage of DHL in order to achieve parallel tractability
-of materialization.
-
-We find that, an unlimited usage of axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
-\label{fig:ex3_4}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
-where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
-\end{example}
-
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
-each node of the form $A(a_i)$ (filled with black color,
-and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
-number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
-
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
-we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
-to avoid `path twisting'. An intuitive idea is to
-ensure that \emph{there is only one path between each two atoms of the form $A(x)$
-generated from the rules corresponding to (T1)}.
-We explain it by using the following example where the ontology is modified from
-that in Example~\ref{exp:dhl}.
-
-\begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
-`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
-\end{example}
-
-In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
-of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
-since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
-node has an SWD path).
-Motivated by this example, we consider restricting the usage of
-the axioms $B_1\sqcap B_2\sqsubseteq A$
-such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
-for some $y$.
-To this end, we first define \emph{simple concepts} as follows:
-
-\begin{definition}
-Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
-of some axiom; or (2) $A$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
-\end{enumerate}
-\end{definition}
-
-Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
-is generated from the rules corresponding to (T1).
-
-\begin{example}
-In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
-non-simple concepts.
-In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
-the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
-\end{example}
-
-We define the following class of DHL ontologies based on the above restriction and
-give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
-
-\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
-each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
-$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
-\end{definition}
-
-\begin{theorem}\label{theorem:dhl}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
-
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
-In addition to the rules in DHL, we also have to consider complex RIAs (R4).
-We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
-\begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
-the RBox $\mathcal{R}$ contains three axioms:
-$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
-the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
-contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
-`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
-\end{example}
-
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
-Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
-
-Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
-we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
-then, at least one of $R_1$ and $R_2$ is
-a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
-We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
-we can get a complex RIA in the form of
-$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
-If one of $R_1$ and $R_2$ is not a simple role, the corresponding
-rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
-and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
-Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
-For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
-role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
-a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
-Further, the situation of path twisting also exists.
-To tackle the above issue,
-we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
-Combined with the simple-concept restriction,
-we define a class of DHL($\circ$) ontologies as follows:
-
-\begin{definition}\label{def:dhlplus}
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
-is rewritten from a DHL($\circ$) ontology and the following
-conditions are satisfied:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
-\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
-\end{enumerate}
-\end{definition}
-
-\begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
-the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
-in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
-\end{example}
-
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
-
-\begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
-\label{sec:practicalAlg}
-
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
-
-\subsection{Reducing Computing Space}
-
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
-However, this algorithm can hardly work in practice due to its inherently
-high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
-Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
-when the target datalog program or ontology
-tends to be large in size.
-On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
-we can observe that the rule instantiations used for the construction
-of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
-by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-each of the checked rule instantiations should involve at least one body atom that has been
-added to the constructed materialization graph}.
-Since DHL$(\circ)$
-is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
-as follows.
-
-We first consider a datalog rule of the
-form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
-of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
-graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
-the datalog rule `$A(x)\rightarrow B(x)$'
-has only one rule instantiation `$A(a)\rightarrow B(a)$' where
-the variable $x$ is substituted by the constant $a$.
-The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
-`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
-at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
-added to $\mathcal{G}$.
-Note that, for rule instantiations of two body atoms,
-we do not require that both of these two body atoms have been added to
-the constructed materialization graph.
-Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
-
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
-
-We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
-and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
-narrowing down the scope of rule instantiations to be checked as well. This can be described
-by the following algorithm.\\
-
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
-and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
-
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
-\end{enumerate}
-
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
-datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
-returns a materialization graph $\mathcal{G}$ of $P$.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
-    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
-DHL$(\circ)$ materialization.
-
-\begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
-all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
-an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
-are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
-\end{example}
-
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
-
-\begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
-and compare it to the reasoning system RDFox.
-
-\subsection{Practical Usability of the Theoretical Results}
-
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
-facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
-
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
-
-\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
-
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
-
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
-
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
-
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
-restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
-
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
-\hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
-\hline
-
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
-\end{tabular}
-\label{tab:info}
-\end{center}
-
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
-
-\textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
-
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
-\end{center}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-\label{tab:expresult}
-\end{center}
-
-\section{Related Work}
-\label{sec:related}
-
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-There is work that studies parallel reasoning in RDFS and OWL.
-The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
-The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
-Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data).
-The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets.
-On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}.
-In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
-
-Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
-The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
-Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
-This is not the focus in this paper.
-
-Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data.
-The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
-datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
-
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
-
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
-other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
-have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
-explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
-study how to further apply the
-results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
-
-\section*{Acknowledgments}
-
-This work was partially supported by NSFC
-grant 61672153 and the 863 program under Grant
-2015AA015406.
-
-\section*{Reference}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{reference}
-
-\clearpage
-
-\section*{Appendix}
-
-\appendix
-
-\section{Proof of Lemma~\ref{lemma:a1}}
-
-\textbf{Lemma~\ref{lemma:a1}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
-
-\noindent\emph{Proof}:
-(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
-check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
-Thus $\mathcal{G}$ turns out to be an acyclic graph.
-Second, to show $\mathcal{G}$ is a
-complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
-Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
-For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
-added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
-there has to be a processor that would add it to $\mathcal{G}$.
-
-(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
-of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
-Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:a1}}
-
-\textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
-
-\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
-is actually the depth of the constructed materialization graph.
-We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
-By performing an induction on the number of iterations of \ref{alg1:updateG},
-one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
-where $n$=\texttt{depth}($v'$).
-Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
-We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).
-
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
-a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
-
-($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
-If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
-the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
-should have a smaller depth compared with $\mathcal{G}$.
-In this case, this conclusion still holds.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:a3}}
-
-\textbf{Lemma~\ref{lemma:a3}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
-
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
-In this case, $\mathcal{G}$ is obviously a materialization graph.
-
-\emph{Inductive case}.
-According to the induction hypothesis, the partial graph constructed after
-the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
-also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
-It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
-and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-In the above two cases, $H$ is a new node. Thus,
-$\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
-the algorithm does nothing.
-Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.
-
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
-We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
-According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:dllite}}
-
-\textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
-
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
-$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
-for any materialization graph.
-
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
-We are left to prove that $H$ has an SWD path as well
-in all materialization graphs of $\mathcal{O}$.
-
-If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
-applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
-\item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
-We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
-
-\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
-according to the induction hypothesis.
-It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
-in some materialization graph.
-\end{enumerate}
-
-Since node $A(x)$ can only be derived in either Case~1.1
-or Case~1.2, we have that
-node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
-
-It is similar to prove the case where $H$ is in the form of $R(x,y)$.
-Since node $R(x,y)$ may be derived by
-applying (R1) and (R2), we discuss these two cases.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
-\item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
-Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
-in some materialization graph.
-
-\item $S\sqsubseteq R^-$. This case is similar to
-the above case.
-\end{enumerate}
-
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dl-lite}}
-
-\textbf{Theorem~\ref{theorem:dl-lite}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
-since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dhl}}
-
-\textbf{Theorem~\ref{theorem:dhl}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
-ontology can be separated into two stages: in the first stage (Stage~1), all the rules
-of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
-also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
-are then applied in Stage~2.
-It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
-for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
-such a poly-logarithmical function $\psi$ exists.
-
-In Stage~1, the rules of the forms (R1-R3)
-are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
-handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
-
-\begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
-\end{definition}
-
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
-We then have the following lemma.
-
-\begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
-\end{lemma}
-
-Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
-In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1) and (R2);
-(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
-where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
-generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
-
-We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
-    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.
-
-\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
-    role.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:dhlplus}}
-
-\textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
-That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
-all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
-
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
-that is defined as follows:
-
-\begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
-\end{definition}
-
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
-We then give the following definition for $\delta_R$.
-
-\begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
-\end{definition}
-
-\begin{lemma}\label{lemma:tiplus}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
-$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
-\end{lemma}
-
-The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
-Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
-The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1), (R2) and (R4);
-(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
-one can further perform (R1), (R2) and (R4) iteratively based on all
-transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
-All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-We now prove Lemma~\ref{lemma:tiplus}.
-We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
-
-    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
-    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.
-
-    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.
-
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
-    \end{enumerate}
-
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
-    holds.\label{dhlplus:NTIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Further, $R$ is a transitive role. According to the simple-role restriction,
-    both of $R_1$ and $R_2$ are simple roles.
-    This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
-    This case is similar to \ref{dhlplus:NTIcaseR4}.
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
-        Then, $R'$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
-        $R'^-$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
-    at least one of $R_1$ and $R_2$ is a simple role.
-    W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
-    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
-    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
-    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:aprc}}
-
-\textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
-this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
-(see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
-
-To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
-We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
-$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
-$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:aprcpt}}
-
-\textbf{Theorem~\ref{theorem:aprcpt}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that $\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
-\emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
-\emph{the simple concept materialization} (Stage~SCM) and
-\emph{the non-simple concept materialization} (Stage~NSCM).
-Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
-where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
-role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.
-
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
-such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
-Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
-there exists a poly-logarithmically bounded function $\psi'$
-such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.
-
-We first consider Stage~SCM.
-Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
-and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
-can be viewed as an EDB predicate. This further means that,
-for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
-Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
-The atom $A(a)$ can be derived through either of the following rule instantiations:
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
-
-\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
-    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
-    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-\end{enumerate}
-
-We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
-According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
-In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
-We also use an induction to show that
-such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
-here.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
-    If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
-\end{enumerate}
-
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
-
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
-We use an induction to show that
-such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
-as follows.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
-    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
-\end{enumerate}
-
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
-is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
-$R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
-of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
-can also be computed by $\mathsf{A}_{prc}^\psi$ for some
-poly-logarithmically bounded function $\psi$.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
-    One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
-    all nodes in each level of $t$ in one iteration from the bottom. Thus,
-    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
-\end{enumerate}
-
-\end{document}
-\endinput
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-01-29 parallel-tractability-J-v9/conclusions.tex
splitting the main file for better organization

--- 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
@@
-%\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
- \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-\usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-\usepackage{amsmath}
-
-\usepackage{CJK}
-\usepackage{color}
-
-\usepackage{enumitem}
-\usepackage{rotating}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-%\journal{Nuclear Physics B}
-
-\hyphenation{data-log}
-
-\begin{document}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Parallel Tractability of Ontology\\
-Materialization: Technique and Practice}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author[add1]{Zhangquan Zhou \corref{cor1}}
-\ead{quanzz1129@gmail.com}
-\cortext[cor1]{Corresponding author}
-
-\author[add1]{Guilin Qi}
-\ead{gqi@seu.edu.cn}
-
-\author[add2]{Birte Glimm}
-\ead{birte.glimm@uni-ulm.de}
-
-\address[add1]{
-    School of Computer Science, Southeast University, China
-}
-
-\address[add2]{
-    Institute of Artificial Intelligence, University of Ulm
-}
-
-\begin{abstract}
-  Materialization is an important reasoning service for many
-  ontology-based applications, but the rapid growth of semantic data
-  poses the challenge to efficiently perform materialization on
-  large-scale ontologies. Parallel materialization algorithms work
-  well for some ontologies, which is not always explained by the
-  theoretical results. For example, for the YAGO ontology
-  parallelization works well, although the reasoning problem for the
-  used ontology language is not in \texttt{NC}, i.e.\ the theoretical
-  complexity class for \emph{parallel tractability}. This motivates us
-  to study the problem of \emph{parallel tractability} of ontology
-  materialization from a theoretical perspective. We focus on the
-  datalog rewritable ontology languages DL-Lite and Description Horn
-  Logic (DHL) and propose algorithms, called \texttt{NC} algorithms,
-  to identify classes of ontologies for which materialization is
-  tractable in parallel. To verify the practical usability of the
-  above results, we analyze real-world datasets and show that for many
-  ontologies expressed in DHL materialization is tractable in
-  parallel. The implementation of our optimized parallel algorithm
-  shows performance improvements over the highly optimized
-  state-of-the-art reasoner RDFox on ontologies for which
-  materialization is tractable in parallel.
-\end{abstract}
-
-\begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-\section{Introduction}
-\label{sec:introduction}
-
-The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
-are being generated at an increasing pace by sensor networks, government authorities and social
-media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.
-
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
-MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
-
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
-While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
-for which parallel tractability can be guaranteed theoretically.
-
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
-This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
-we also discuss how to optimize and implement them.
-
-In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
-We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
-in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
-Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
-We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
-
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
-In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
-
-\section{Background Knowledge}
-\label{sec:background}
-
-In this section, we introduce some basic notions that are needed to introduce our approach.
-
-\subsection{Datalog}
-
-We discuss the main issues in this paper using standard datalog notions.
-In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
-constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
-represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
-of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
-the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
-A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
-For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
-with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
-if each defined $A\theta$ is a ground atom.
-A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
-the terms in this rule with respect to a finite set of constants occurring in $P$.
-Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
-The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
-while the predicates that may occur as head atoms are called \emph{IDB predicates}.
-
-\subsection{DHL and DL-Lite}
-
-In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
-to denote three disjoint countably
-infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
-The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
-where $R^-$ is the \emph{inverse role} of $R$.
-For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
-
-DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
-intersection of description logic (DL) and datalog in terms of expressivity.
-We define a DHL ontology $\mathcal{O}$ as a triple:
-$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
-$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
-$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
-$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
-In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
-are roles in $\textbf{R}$.
-For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
-equivalent form $\exists R^-.A\sqsubseteq B$.
-
-DHL is related with other ontology languages.
-First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
-Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
-Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
-However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
-materialization.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
-\hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
-\hline
-\hline
-(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
-(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
-(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
-(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\
-
-\hline
-(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
-(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
-(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
-(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\
-
-\hline
-(A1)& $A(a)$& $A(a)$\\
-(A2)& $R(a,b)$& $R(a,b)$\\
-\hline
-\end{tabular}
-\label{tab:dhl}
-\end{center}
-\end{table}
-
-In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
-In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
-that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
-RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
-axioms of the forms (R1-R4). Note that (R3) is actually a special
-case of (R4).
-
-DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
-and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
-(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
-where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
-an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
-which allows involving RBoxes that contain axioms of the forms (R1-R2).
-If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
-in the following paragraphs}.
-
-\subsection{Ontology Materialization via Datalog Programs}
-
-An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
-(see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
-
-In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
-$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
-Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
-between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
-usage of highly expressive ontology languages \cite{HorrocksS04}.
-Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
-occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.
-
-Based on the above representations, ontology materialization
-corresponds to the evaluation of datalog programs.
-Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
-where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
- $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
-The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
-and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
-$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
-We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
-to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
-
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
-Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
-where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
-as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
-In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
-are implemented on shared-memory platforms, we
-study all the issues in this work by assuming that the running machines are in
-shared-memory configurations.
-
-\section{Parallel Tractability of Datalog Programs}
-\label{sec:ptclass}
-
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
-if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
-
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
-
-\begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
-\end{definition}
-
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
-for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
-which is the class of all datalog programs that can be handled by $\mathsf{A}$.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
-In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
-and identify the target \texttt{PTD} class.
-
-\subsection{Materialization Graph}
-
-In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
-
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
-\end{enumerate}
-\end{definition}
-
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
-We next give an example of a materialization graph.\\
-
-\begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
-$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
-the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
-where $\textbf{I}$ contains all the assertions in the ABox
-and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
-and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
-each of the other nodes corresponds to a ground instantiation of some rule.
-For example, the node $A(a_k)$ corresponds to the ground rule instantiation
-`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
-The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
-\label{fig:mg}
-\end{center}
-\end{figure}
-
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
-The set of nodes in a complete materialization graph is actually the result
-of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
-a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
-It should also be noted that there may exist several materialization graphs for a datalog program.
-
-\subsection{A Basic Parallel Algorithm}
-
-In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
-Initially $\mathcal{G}$ is empty. The following three steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
-    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
-Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
-\end{example}
-
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
-materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
-in the appendix.
-
-\begin{lemma}
-\label{lemma:a1}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-\begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}[Proof sketch] This lemma can be proved by performing
-an induction on $T_R^{\omega}(\textbf{I})$.
-The stage (see the related contents in Section~\ref{sec:background}) of $P$
-is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
-its depth equals the depth of the stage.
-\end{proof}
-
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
-We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
-
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
-We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
-
-\begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
-\end{theorem}
-
-\begin{proof}[Proof sketch]
-We can first prove that the number of iterations
-of \ref{alg1:updateG} is actually the depth of the constructed materialization
-graph. This theorem then follows by considering
-Lemma~\ref{lemma:a1}.
-\end{proof}
-
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
-Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
-We discuss this in the next part.
-
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
-
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
-we can identify another \texttt{PTD} class.
-
-We discuss our optimization based on a specific case in Example~\ref{exp:general}.
-We find that, in this kind of case, the construction of a materialization graph can be accelerated.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
-\label{fig:general}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
-Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
-is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
-The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
-In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
-All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
-afterwards.
-\end{example}
-
-In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
-node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
-Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
-$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
-$\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
-due to the single-way derivability condition.
-
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
-can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
-
-We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
-describe the reachability between two nodes. To this extent, we use a
-binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
-e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
-
-\begin{description}[leftmargin=2ex]
-\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
-\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
-\end{enumerate}
-\end{description}
-
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
-The following algorithm applies this optimization strategy.\\
-
-\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
-a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
-being constructed from $P$. The following steps are performed:
-\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
-that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
-    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
-    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
-\end{enumerate}
-
-It is well known that there is an \texttt{NC} algorithm for computing the
-transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
-    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
-\end{enumerate}
-
-It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
-
-\begin{lemma}\label{lemma:a3}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
-\end{lemma}
-
-\begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
-In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
-one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
-in the first iteration of \ref{alg3:updateG}.
-\end{example}
-
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
-
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
-
-\begin{corollary}
-For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{corollary}
-
-\begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
-if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
-\end{proof}
-
-\section{Parallel Tractability of Ontology Materialization in OWL}
-\label{sec:ptonto}
-
-In this section, we study the issue of parallel tractability
-for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
-there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
-work by studying specific cases.
-Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
-of materialization.
-
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
-
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
-DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
-there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
-In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
-the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
-
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
-we use the following example.
-
-\begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
-where its TBox and RBox contain the following axioms:
-$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
-its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
-where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
-as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
-\label{fig:ex2}
-\end{center}
-\end{figure}
-
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
-(\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
-$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
-for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
-since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
-$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
-(\uppercase\expandafter{\romannumeral3})
-The two nodes $\bot(a)$ and $\bot(b)$
-have no SWD path in the first iteration of \ref{alg3:updateG}.
-They are left to be processed in the second iteration.
-(\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
-after two iterations (\ref{alg3:halt}).
-
-From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
-
-\begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
-\end{lemma}
-
-The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
-have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
-of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
-an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
-more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
-
-\begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL}
-
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
-Based on the analysis of this case, we propose to restrict
-the usage of DHL in order to achieve parallel tractability
-of materialization.
-
-We find that, an unlimited usage of axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
-\label{fig:ex3_4}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
-where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
-\end{example}
-
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
-each node of the form $A(a_i)$ (filled with black color,
-and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
-number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
-
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
-we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
-to avoid `path twisting'. An intuitive idea is to
-ensure that \emph{there is only one path between each two atoms of the form $A(x)$
-generated from the rules corresponding to (T1)}.
-We explain it by using the following example where the ontology is modified from
-that in Example~\ref{exp:dhl}.
-
-\begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
-`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
-\end{example}
-
-In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
-of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
-since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
-node has an SWD path).
-Motivated by this example, we consider restricting the usage of
-the axioms $B_1\sqcap B_2\sqsubseteq A$
-such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
-for some $y$.
-To this end, we first define \emph{simple concepts} as follows:
-
-\begin{definition}
-Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
-of some axiom; or (2) $A$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
-\end{enumerate}
-\end{definition}
-
-Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
-is generated from the rules corresponding to (T1).
-
-\begin{example}
-In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
-non-simple concepts.
-In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
-the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
-\end{example}
-
-We define the following class of DHL ontologies based on the above restriction and
-give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
-
-\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
-each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
-$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
-\end{definition}
-
-\begin{theorem}\label{theorem:dhl}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
-
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
-In addition to the rules in DHL, we also have to consider complex RIAs (R4).
-We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
-\begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
-the RBox $\mathcal{R}$ contains three axioms:
-$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
-the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
-contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
-`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
-\end{example}
-
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
-Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
-
-Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
-we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
-then, at least one of $R_1$ and $R_2$ is
-a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
-We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
-we can get a complex RIA in the form of
-$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
-If one of $R_1$ and $R_2$ is not a simple role, the corresponding
-rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
-and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
-Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
-For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
-role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
-a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
-Further, the situation of path twisting also exists.
-To tackle the above issue,
-we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
-Combined with the simple-concept restriction,
-we define a class of DHL($\circ$) ontologies as follows:
-
-\begin{definition}\label{def:dhlplus}
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
-is rewritten from a DHL($\circ$) ontology and the following
-conditions are satisfied:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
-\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
-\end{enumerate}
-\end{definition}
-
-\begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
-the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
-in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
-\end{example}
-
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
-
-\begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
-\label{sec:practicalAlg}
-
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
-
-\subsection{Reducing Computing Space}
-
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
-However, this algorithm can hardly work in practice due to its inherently
-high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
-Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
-when the target datalog program or ontology
-tends to be large in size.
-On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
-we can observe that the rule instantiations used for the construction
-of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
-by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-each of the checked rule instantiations should involve at least one body atom that has been
-added to the constructed materialization graph}.
-Since DHL$(\circ)$
-is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
-as follows.
-
-We first consider a datalog rule of the
-form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
-of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
-graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
-the datalog rule `$A(x)\rightarrow B(x)$'
-has only one rule instantiation `$A(a)\rightarrow B(a)$' where
-the variable $x$ is substituted by the constant $a$.
-The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
-`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
-at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
-added to $\mathcal{G}$.
-Note that, for rule instantiations of two body atoms,
-we do not require that both of these two body atoms have been added to
-the constructed materialization graph.
-Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
-
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
-
-We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
-and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
-narrowing down the scope of rule instantiations to be checked as well. This can be described
-by the following algorithm.\\
-
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
-and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
-
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
-\end{enumerate}
-
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
-datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
-returns a materialization graph $\mathcal{G}$ of $P$.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
-    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
-DHL$(\circ)$ materialization.
-
-\begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
-all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
-an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
-are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
-\end{example}
-
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
-
-\begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
-and compare it to the reasoning system RDFox.
-
-\subsection{Practical Usability of the Theoretical Results}
-
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
-facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
-
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
-
-\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
-
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
-
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
-
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
-
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
-restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
-
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
-\hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
-\hline
-
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
-\end{tabular}
-\label{tab:info}
-\end{center}
-
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
-
-\textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
-
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
-\end{center}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-\label{tab:expresult}
-\end{center}
-
-\section{Related Work}
-\label{sec:related}
-
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-There is work that studies parallel reasoning in RDFS and OWL.
-The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
-The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
-Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data).
-The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets.
-On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}.
-In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
-
-Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
-The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
-Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
-This is not the focus in this paper.
-
-Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data.
-The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.
-
 \section{Conclusions}
@@
 
-\section*{Acknowledgments}
-
-This work was partially supported by NSFC
-grant 61672153 and the 863 program under Grant
-2015AA015406.
-
-\section*{Reference}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{reference}
-
-\clearpage
-
-\section*{Appendix}
-
-\appendix
-
-\section{Proof of Lemma~\ref{lemma:a1}}
-
-\textbf{Lemma~\ref{lemma:a1}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
-
-\noindent\emph{Proof}:
-(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
-check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
-Thus $\mathcal{G}$ turns out to be an acyclic graph.
-Second, to show $\mathcal{G}$ is a
-complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
-Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
-For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
-added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
-there has to be a processor that would add it to $\mathcal{G}$.
-
-(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
-of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
-Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:a1}}
-
-\textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
-
-\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
-is actually the depth of the constructed materialization graph.
-We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
-By performing an induction on the number of iterations of \ref{alg1:updateG},
-one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
-where $n$=\texttt{depth}($v'$).
-Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
-We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).
-
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
-a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
-
-($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
-If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
-the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
-should have a smaller depth compared with $\mathcal{G}$.
-In this case, this conclusion still holds.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:a3}}
-
-\textbf{Lemma~\ref{lemma:a3}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
-
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
-In this case, $\mathcal{G}$ is obviously a materialization graph.
-
-\emph{Inductive case}.
-According to the induction hypothesis, the partial graph constructed after
-the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
-also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
-It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
-and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-In the above two cases, $H$ is a new node. Thus,
-$\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
-the algorithm does nothing.
-Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.
-
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
-We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
-According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:dllite}}
-
-\textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
-
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
-$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
-for any materialization graph.
-
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
-We are left to prove that $H$ has an SWD path as well
-in all materialization graphs of $\mathcal{O}$.
-
-If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
-applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
-\item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
-We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
-
-\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
-according to the induction hypothesis.
-It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
-in some materialization graph.
-\end{enumerate}
-
-Since node $A(x)$ can only be derived in either Case~1.1
-or Case~1.2, we have that
-node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
-
-It is similar to prove the case where $H$ is in the form of $R(x,y)$.
-Since node $R(x,y)$ may be derived by
-applying (R1) and (R2), we discuss these two cases.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
-\item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
-Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
-in some materialization graph.
-
-\item $S\sqsubseteq R^-$. This case is similar to
-the above case.
-\end{enumerate}
-
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dl-lite}}
-
-\textbf{Theorem~\ref{theorem:dl-lite}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
-since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dhl}}
-
-\textbf{Theorem~\ref{theorem:dhl}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
-ontology can be separated into two stages: in the first stage (Stage~1), all the rules
-of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
-also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
-are then applied in Stage~2.
-It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
-for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
-such a poly-logarithmical function $\psi$ exists.
-
-In Stage~1, the rules of the forms (R1-R3)
-are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
-handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
-
-\begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
-\end{definition}
-
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
-We then have the following lemma.
-
-\begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
-\end{lemma}
-
-Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
-In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1) and (R2);
-(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
-where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
-generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
-
-We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
-    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.
-
-\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
-    role.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:dhlplus}}
-
-\textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
-That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
-all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
-
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
-that is defined as follows:
-
-\begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
-\end{definition}
-
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
-We then give the following definition for $\delta_R$.
-
-\begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
-\end{definition}
-
-\begin{lemma}\label{lemma:tiplus}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
-$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
-\end{lemma}
-
-The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
-Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
-The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1), (R2) and (R4);
-(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
-one can further perform (R1), (R2) and (R4) iteratively based on all
-transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
-All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-We now prove Lemma~\ref{lemma:tiplus}.
-We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
-
-    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
-    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.
-
-    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.
-
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
-    \end{enumerate}
-
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
-    holds.\label{dhlplus:NTIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Further, $R$ is a transitive role. According to the simple-role restriction,
-    both of $R_1$ and $R_2$ are simple roles.
-    This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
-    This case is similar to \ref{dhlplus:NTIcaseR4}.
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
-        Then, $R'$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
-        $R'^-$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
-    at least one of $R_1$ and $R_2$ is a simple role.
-    W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
-    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
-    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
-    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:aprc}}
-
-\textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
-this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
-(see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
-
-To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
-We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
-$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
-$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:aprcpt}}
-
-\textbf{Theorem~\ref{theorem:aprcpt}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that $\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
-\emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
-\emph{the simple concept materialization} (Stage~SCM) and
-\emph{the non-simple concept materialization} (Stage~NSCM).
-Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
-where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
-role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.
-
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
-such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
-Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
-there exists a poly-logarithmically bounded function $\psi'$
-such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.
-
-We first consider Stage~SCM.
-Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
-and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
-can be viewed as an EDB predicate. This further means that,
-for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
-Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
-The atom $A(a)$ can be derived through either of the following rule instantiations:
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
-
-\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
-    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
-    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-\end{enumerate}
-
-We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
-According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
-In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
-We also use an induction to show that
-such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
-here.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
-    If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
-\end{enumerate}
-
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
-
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
-We use an induction to show that
-such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
-as follows.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
-    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
-\end{enumerate}
-
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
-is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
-$R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
-of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
-can also be computed by $\mathsf{A}_{prc}^\psi$ for some
-poly-logarithmically bounded function $\psi$.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
-    One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
-    all nodes in each level of $t$ in one iteration from the bottom. Thus,
-    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
-\end{enumerate}
-
-\end{document}
-\endinput
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-01-29 parallel-tractability-J-v9/evaluation.tex
splitting the main file for better organization

--- 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
@@
-%\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
- \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-\usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-\usepackage{amsmath}
-
-\usepackage{CJK}
-\usepackage{color}
-
-\usepackage{enumitem}
-\usepackage{rotating}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-%\journal{Nuclear Physics B}
-
-\hyphenation{data-log}
-
-\begin{document}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Parallel Tractability of Ontology\\
-Materialization: Technique and Practice}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author[add1]{Zhangquan Zhou \corref{cor1}}
-\ead{quanzz1129@gmail.com}
-\cortext[cor1]{Corresponding author}
-
-\author[add1]{Guilin Qi}
-\ead{gqi@seu.edu.cn}
-
-\author[add2]{Birte Glimm}
-\ead{birte.glimm@uni-ulm.de}
-
-\address[add1]{
-    School of Computer Science, Southeast University, China
-}
-
-\address[add2]{
-    Institute of Artificial Intelligence, University of Ulm
-}
-
-\begin{abstract}
-  Materialization is an important reasoning service for many
-  ontology-based applications, but the rapid growth of semantic data
-  poses the challenge to efficiently perform materialization on
-  large-scale ontologies. Parallel materialization algorithms work
-  well for some ontologies, which is not always explained by the
-  theoretical results. For example, for the YAGO ontology
-  parallelization works well, although the reasoning problem for the
-  used ontology language is not in \texttt{NC}, i.e.\ the theoretical
-  complexity class for \emph{parallel tractability}. This motivates us
-  to study the problem of \emph{parallel tractability} of ontology
-  materialization from a theoretical perspective. We focus on the
-  datalog rewritable ontology languages DL-Lite and Description Horn
-  Logic (DHL) and propose algorithms, called \texttt{NC} algorithms,
-  to identify classes of ontologies for which materialization is
-  tractable in parallel. To verify the practical usability of the
-  above results, we analyze real-world datasets and show that for many
-  ontologies expressed in DHL materialization is tractable in
-  parallel. The implementation of our optimized parallel algorithm
-  shows performance improvements over the highly optimized
-  state-of-the-art reasoner RDFox on ontologies for which
-  materialization is tractable in parallel.
-\end{abstract}
-
-\begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-\section{Introduction}
-\label{sec:introduction}
-
-The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
-are being generated at an increasing pace by sensor networks, government authorities and social
-media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.
-
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
-MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
-
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
-While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
-for which parallel tractability can be guaranteed theoretically.
-
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
-This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
-we also discuss how to optimize and implement them.
-
-In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
-We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
-in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
-Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
-We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
-
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
-In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
-
-\section{Background Knowledge}
-\label{sec:background}
-
-In this section, we introduce some basic notions that are needed to introduce our approach.
-
-\subsection{Datalog}
-
-We discuss the main issues in this paper using standard datalog notions.
-In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
-constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
-represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
-of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
-the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
-A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
-For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
-with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
-if each defined $A\theta$ is a ground atom.
-A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
-the terms in this rule with respect to a finite set of constants occurring in $P$.
-Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
-The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
-while the predicates that may occur as head atoms are called \emph{IDB predicates}.
-
-\subsection{DHL and DL-Lite}
-
-In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
-to denote three disjoint countably
-infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
-The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
-where $R^-$ is the \emph{inverse role} of $R$.
-For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
-
-DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
-intersection of description logic (DL) and datalog in terms of expressivity.
-We define a DHL ontology $\mathcal{O}$ as a triple:
-$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
-$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
-$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
-$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
-In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
-are roles in $\textbf{R}$.
-For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
-equivalent form $\exists R^-.A\sqsubseteq B$.
-
-DHL is related with other ontology languages.
-First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
-Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
-Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
-However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
-materialization.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
-\hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
-\hline
-\hline
-(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
-(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
-(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
-(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\
-
-\hline
-(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
-(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
-(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
-(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\
-
-\hline
-(A1)& $A(a)$& $A(a)$\\
-(A2)& $R(a,b)$& $R(a,b)$\\
-\hline
-\end{tabular}
-\label{tab:dhl}
-\end{center}
-\end{table}
-
-In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
-In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
-that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
-RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
-axioms of the forms (R1-R4). Note that (R3) is actually a special
-case of (R4).
-
-DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
-and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
-(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
-where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
-an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
-which allows involving RBoxes that contain axioms of the forms (R1-R2).
-If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
-in the following paragraphs}.
-
-\subsection{Ontology Materialization via Datalog Programs}
-
-An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
-(see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
-
-In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
-$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
-Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
-between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
-usage of highly expressive ontology languages \cite{HorrocksS04}.
-Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
-occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.
-
-Based on the above representations, ontology materialization
-corresponds to the evaluation of datalog programs.
-Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
-where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
- $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
-The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
-and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
-$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
-We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
-to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
-
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
-Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
-where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
-as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
-In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
-are implemented on shared-memory platforms, we
-study all the issues in this work by assuming that the running machines are in
-shared-memory configurations.
-
-\section{Parallel Tractability of Datalog Programs}
-\label{sec:ptclass}
-
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
-if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
-
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
-
-\begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
-\end{definition}
-
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
-for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
-which is the class of all datalog programs that can be handled by $\mathsf{A}$.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
-In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
-and identify the target \texttt{PTD} class.
-
-\subsection{Materialization Graph}
-
-In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
-
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
-\end{enumerate}
-\end{definition}
-
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
-We next give an example of a materialization graph.\\
-
-\begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
-$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
-the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
-where $\textbf{I}$ contains all the assertions in the ABox
-and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
-and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
-each of the other nodes corresponds to a ground instantiation of some rule.
-For example, the node $A(a_k)$ corresponds to the ground rule instantiation
-`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
-The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
-\label{fig:mg}
-\end{center}
-\end{figure}
-
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
-The set of nodes in a complete materialization graph is actually the result
-of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
-a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
-It should also be noted that there may exist several materialization graphs for a datalog program.
-
-\subsection{A Basic Parallel Algorithm}
-
-In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
-Initially $\mathcal{G}$ is empty. The following three steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
-    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
-Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
-\end{example}
-
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
-materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
-in the appendix.
-
-\begin{lemma}
-\label{lemma:a1}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-\begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}[Proof sketch] This lemma can be proved by performing
-an induction on $T_R^{\omega}(\textbf{I})$.
-The stage (see the related contents in Section~\ref{sec:background}) of $P$
-is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
-its depth equals the depth of the stage.
-\end{proof}
-
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
-We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
-
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
-We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
-
-\begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
-\end{theorem}
-
-\begin{proof}[Proof sketch]
-We can first prove that the number of iterations
-of \ref{alg1:updateG} is actually the depth of the constructed materialization
-graph. This theorem then follows by considering
-Lemma~\ref{lemma:a1}.
-\end{proof}
-
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
-Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
-We discuss this in the next part.
-
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
-
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
-we can identify another \texttt{PTD} class.
-
-We discuss our optimization based on a specific case in Example~\ref{exp:general}.
-We find that, in this kind of case, the construction of a materialization graph can be accelerated.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
-\label{fig:general}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
-Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
-is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
-The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
-In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
-All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
-afterwards.
-\end{example}
-
-In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
-node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
-Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
-$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
-$\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
-due to the single-way derivability condition.
-
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
-can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
-
-We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
-describe the reachability between two nodes. To this extent, we use a
-binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
-e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
-
-\begin{description}[leftmargin=2ex]
-\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
-\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
-\end{enumerate}
-\end{description}
-
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
-The following algorithm applies this optimization strategy.\\
-
-\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
-a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
-being constructed from $P$. The following steps are performed:
-\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
-that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
-    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
-    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
-\end{enumerate}
-
-It is well known that there is an \texttt{NC} algorithm for computing the
-transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
-    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
-\end{enumerate}
-
-It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
-
-\begin{lemma}\label{lemma:a3}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
-\end{lemma}
-
-\begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
-In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
-one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
-in the first iteration of \ref{alg3:updateG}.
-\end{example}
-
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
-
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
-
-\begin{corollary}
-For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{corollary}
-
-\begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
-if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
-\end{proof}
-
-\section{Parallel Tractability of Ontology Materialization in OWL}
-\label{sec:ptonto}
-
-In this section, we study the issue of parallel tractability
-for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
-there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
-work by studying specific cases.
-Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
-of materialization.
-
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
-
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
-DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
-there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
-In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
-the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
-
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
-we use the following example.
-
-\begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
-where its TBox and RBox contain the following axioms:
-$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
-its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
-where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
-as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
-\label{fig:ex2}
-\end{center}
-\end{figure}
-
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
-(\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
-$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
-for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
-since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
-$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
-(\uppercase\expandafter{\romannumeral3})
-The two nodes $\bot(a)$ and $\bot(b)$
-have no SWD path in the first iteration of \ref{alg3:updateG}.
-They are left to be processed in the second iteration.
-(\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
-after two iterations (\ref{alg3:halt}).
-
-From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
-
-\begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
-\end{lemma}
-
-The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
-have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
-of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
-an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
-more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
-
-\begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL}
-
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
-Based on the analysis of this case, we propose to restrict
-the usage of DHL in order to achieve parallel tractability
-of materialization.
-
-We find that, an unlimited usage of axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
-\label{fig:ex3_4}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
-where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
-\end{example}
-
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
-each node of the form $A(a_i)$ (filled with black color,
-and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
-number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
-
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
-we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
-to avoid `path twisting'. An intuitive idea is to
-ensure that \emph{there is only one path between each two atoms of the form $A(x)$
-generated from the rules corresponding to (T1)}.
-We explain it by using the following example where the ontology is modified from
-that in Example~\ref{exp:dhl}.
-
-\begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
-`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
-\end{example}
-
-In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
-of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
-since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
-node has an SWD path).
-Motivated by this example, we consider restricting the usage of
-the axioms $B_1\sqcap B_2\sqsubseteq A$
-such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
-for some $y$.
-To this end, we first define \emph{simple concepts} as follows:
-
-\begin{definition}
-Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
-of some axiom; or (2) $A$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
-\end{enumerate}
-\end{definition}
-
-Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
-is generated from the rules corresponding to (T1).
-
-\begin{example}
-In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
-non-simple concepts.
-In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
-the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
-\end{example}
-
-We define the following class of DHL ontologies based on the above restriction and
-give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
-
-\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
-each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
-$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
-\end{definition}
-
-\begin{theorem}\label{theorem:dhl}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
-
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
-In addition to the rules in DHL, we also have to consider complex RIAs (R4).
-We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
-\begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
-the RBox $\mathcal{R}$ contains three axioms:
-$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
-the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
-contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
-`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
-\end{example}
-
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
-Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
-
-Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
-we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
-then, at least one of $R_1$ and $R_2$ is
-a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
-We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
-we can get a complex RIA in the form of
-$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
-If one of $R_1$ and $R_2$ is not a simple role, the corresponding
-rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
-and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
-Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
-For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
-role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
-a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
-Further, the situation of path twisting also exists.
-To tackle the above issue,
-we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
-Combined with the simple-concept restriction,
-we define a class of DHL($\circ$) ontologies as follows:
-
-\begin{definition}\label{def:dhlplus}
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
-is rewritten from a DHL($\circ$) ontology and the following
-conditions are satisfied:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
-\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
-\end{enumerate}
-\end{definition}
-
-\begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
-the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
-in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
-\end{example}
-
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
-
-\begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
-\label{sec:practicalAlg}
-
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
-
-\subsection{Reducing Computing Space}
-
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
-However, this algorithm can hardly work in practice due to its inherently
-high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
-Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
-when the target datalog program or ontology
-tends to be large in size.
-On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
-we can observe that the rule instantiations used for the construction
-of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
-by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-each of the checked rule instantiations should involve at least one body atom that has been
-added to the constructed materialization graph}.
-Since DHL$(\circ)$
-is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
-as follows.
-
-We first consider a datalog rule of the
-form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
-of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
-graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
-the datalog rule `$A(x)\rightarrow B(x)$'
-has only one rule instantiation `$A(a)\rightarrow B(a)$' where
-the variable $x$ is substituted by the constant $a$.
-The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
-`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
-at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
-added to $\mathcal{G}$.
-Note that, for rule instantiations of two body atoms,
-we do not require that both of these two body atoms have been added to
-the constructed materialization graph.
-Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
-
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
-
-We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
-and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
-narrowing down the scope of rule instantiations to be checked as well. This can be described
-by the following algorithm.\\
-
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
-and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
-
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
-\end{enumerate}
-
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
-datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
-returns a materialization graph $\mathcal{G}$ of $P$.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
-    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
-DHL$(\circ)$ materialization.
-
-\begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
-all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
-an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
-are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
-\end{example}
-
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
-
-\begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
 \section{Evaluation}
@@
 
-\section{Related Work}
-\label{sec:related}
-
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-There is work that studies parallel reasoning in RDFS and OWL.
-The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
-The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
-Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data).
-The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets.
-On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}.
-In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
-
-Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
-The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
-Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
-This is not the focus in this paper.
-
-Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data.
-The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
-datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
-
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
-
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
-other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
-have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
-explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
-study how to further apply the
-results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
-
-\section*{Acknowledgments}
-
-This work was partially supported by NSFC
-grant 61672153 and the 863 program under Grant
-2015AA015406.
-
-\section*{Reference}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{reference}
-
-\clearpage
-
-\section*{Appendix}
-
-\appendix
-
-\section{Proof of Lemma~\ref{lemma:a1}}
-
-\textbf{Lemma~\ref{lemma:a1}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
-
-\noindent\emph{Proof}:
-(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
-check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
-Thus $\mathcal{G}$ turns out to be an acyclic graph.
-Second, to show $\mathcal{G}$ is a
-complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
-Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
-For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
-added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
-there has to be a processor that would add it to $\mathcal{G}$.
-
-(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
-of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
-Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:a1}}
-
-\textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
-
-\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
-is actually the depth of the constructed materialization graph.
-We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
-By performing an induction on the number of iterations of \ref{alg1:updateG},
-one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
-where $n$=\texttt{depth}($v'$).
-Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
-We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).
-
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
-a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
-
-($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
-If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
-the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
-should have a smaller depth compared with $\mathcal{G}$.
-In this case, this conclusion still holds.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:a3}}
-
-\textbf{Lemma~\ref{lemma:a3}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
-
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
-In this case, $\mathcal{G}$ is obviously a materialization graph.
-
-\emph{Inductive case}.
-According to the induction hypothesis, the partial graph constructed after
-the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
-also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
-It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
-and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-In the above two cases, $H$ is a new node. Thus,
-$\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
-the algorithm does nothing.
-Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.
-
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
-We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
-According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:dllite}}
-
-\textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
-
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
-$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
-for any materialization graph.
-
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
-We are left to prove that $H$ has an SWD path as well
-in all materialization graphs of $\mathcal{O}$.
-
-If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
-applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
-\item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
-We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
-
-\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
-according to the induction hypothesis.
-It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
-in some materialization graph.
-\end{enumerate}
-
-Since node $A(x)$ can only be derived in either Case~1.1
-or Case~1.2, we have that
-node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
-
-It is similar to prove the case where $H$ is in the form of $R(x,y)$.
-Since node $R(x,y)$ may be derived by
-applying (R1) and (R2), we discuss these two cases.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
-\item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
-Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
-in some materialization graph.
-
-\item $S\sqsubseteq R^-$. This case is similar to
-the above case.
-\end{enumerate}
-
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dl-lite}}
-
-\textbf{Theorem~\ref{theorem:dl-lite}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
-since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dhl}}
-
-\textbf{Theorem~\ref{theorem:dhl}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
-ontology can be separated into two stages: in the first stage (Stage~1), all the rules
-of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
-also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
-are then applied in Stage~2.
-It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
-for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
-such a poly-logarithmical function $\psi$ exists.
-
-In Stage~1, the rules of the forms (R1-R3)
-are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
-handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
-
-\begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
-\end{definition}
-
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
-We then have the following lemma.
-
-\begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
-\end{lemma}
-
-Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
-In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1) and (R2);
-(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
-where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
-generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
-
-We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
-    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.
-
-\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
-    role.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:dhlplus}}
-
-\textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
-That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
-all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
-
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
-that is defined as follows:
-
-\begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
-\end{definition}
-
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
-We then give the following definition for $\delta_R$.
-
-\begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
-\end{definition}
-
-\begin{lemma}\label{lemma:tiplus}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
-$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
-\end{lemma}
-
-The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
-Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
-The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1), (R2) and (R4);
-(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
-one can further perform (R1), (R2) and (R4) iteratively based on all
-transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
-All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-We now prove Lemma~\ref{lemma:tiplus}.
-We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
-
-    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
-    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.
-
-    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.
-
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
-    \end{enumerate}
-
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
-    holds.\label{dhlplus:NTIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Further, $R$ is a transitive role. According to the simple-role restriction,
-    both of $R_1$ and $R_2$ are simple roles.
-    This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
-    This case is similar to \ref{dhlplus:NTIcaseR4}.
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
-        Then, $R'$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
-        $R'^-$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
-    at least one of $R_1$ and $R_2$ is a simple role.
-    W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
-    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
-    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
-    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:aprc}}
-
-\textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
-this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
-(see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
-
-To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
-We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
-$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
-$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:aprcpt}}
-
-\textbf{Theorem~\ref{theorem:aprcpt}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that $\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
-\emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
-\emph{the simple concept materialization} (Stage~SCM) and
-\emph{the non-simple concept materialization} (Stage~NSCM).
-Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
-where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
-role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.
-
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
-such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
-Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
-there exists a poly-logarithmically bounded function $\psi'$
-such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.
-
-We first consider Stage~SCM.
-Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
-and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
-can be viewed as an EDB predicate. This further means that,
-for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
-Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
-The atom $A(a)$ can be derived through either of the following rule instantiations:
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
-
-\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
-    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
-    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-\end{enumerate}
-
-We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
-According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
-In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
-We also use an induction to show that
-such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
-here.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
-    If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
-\end{enumerate}
-
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
-
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
-We use an induction to show that
-such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
-as follows.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
-    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
-\end{enumerate}
-
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
-is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
-$R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
-of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
-can also be computed by $\mathsf{A}_{prc}^\psi$ for some
-poly-logarithmically bounded function $\psi$.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
-    One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
-    all nodes in each level of $t$ in one iteration from the bottom. Thus,
-    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
-\end{enumerate}
-
-\end{document}
-\endinput
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-01-29 parallel-tractability-J-v9/introduction.tex
splitting the main file for better organization

--- 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
@@
-%\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
- \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-\usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-\usepackage{amsmath}
-
-\usepackage{CJK}
-\usepackage{color}
-
-\usepackage{enumitem}
-\usepackage{rotating}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-%\journal{Nuclear Physics B}
-
-\hyphenation{data-log}
-
-\begin{document}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Parallel Tractability of Ontology\\
-Materialization: Technique and Practice}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author[add1]{Zhangquan Zhou \corref{cor1}}
-\ead{quanzz1129@gmail.com}
-\cortext[cor1]{Corresponding author}
-
-\author[add1]{Guilin Qi}
-\ead{gqi@seu.edu.cn}
-
-\author[add2]{Birte Glimm}
-\ead{birte.glimm@uni-ulm.de}
-
-\address[add1]{
-    School of Computer Science, Southeast University, China
-}
-
-\address[add2]{
-    Institute of Artificial Intelligence, University of Ulm
-}
-
-\begin{abstract}
-  Materialization is an important reasoning service for many
-  ontology-based applications, but the rapid growth of semantic data
-  poses the challenge to efficiently perform materialization on
-  large-scale ontologies. Parallel materialization algorithms work
-  well for some ontologies, which is not always explained by the
-  theoretical results. For example, for the YAGO ontology
-  parallelization works well, although the reasoning problem for the
-  used ontology language is not in \texttt{NC}, i.e.\ the theoretical
-  complexity class for \emph{parallel tractability}. This motivates us
-  to study the problem of \emph{parallel tractability} of ontology
-  materialization from a theoretical perspective. We focus on the
-  datalog rewritable ontology languages DL-Lite and Description Horn
-  Logic (DHL) and propose algorithms, called \texttt{NC} algorithms,
-  to identify classes of ontologies for which materialization is
-  tractable in parallel. To verify the practical usability of the
-  above results, we analyze real-world datasets and show that for many
-  ontologies expressed in DHL materialization is tractable in
-  parallel. The implementation of our optimized parallel algorithm
-  shows performance improvements over the highly optimized
-  state-of-the-art reasoner RDFox on ontologies for which
-  materialization is tractable in parallel.
-\end{abstract}
-
-\begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
 \section{Introduction}
@@
 reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
+It has also been shown that some well-known large-scale ontologies, such as YAGO, have good performance for parallel
 reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
+On the other hand, there do exist ontologies for which materialization cannot
+always be improved by parallelism (we use experiments to show this in Section~\ref{sec:evaluation}).
+The current work of parallel ontology reasoning can hardly explain this.
 While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
@@
 
-\section{Background Knowledge}
-\label{sec:background}
-
-In this section, we introduce some basic notions that are needed to introduce our approach.
-
-\subsection{Datalog}
-
-We discuss the main issues in this paper using standard datalog notions.
-In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
-constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
-represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
-of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
-the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
-A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
-For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
-with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
-if each defined $A\theta$ is a ground atom.
-A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
-the terms in this rule with respect to a finite set of constants occurring in $P$.
-Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
-The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
-while the predicates that may occur as head atoms are called \emph{IDB predicates}.
-
-\subsection{DHL and DL-Lite}
-
-In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
-to denote three disjoint countably
-infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
-The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
-where $R^-$ is the \emph{inverse role} of $R$.
-For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
-
-DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
-intersection of description logic (DL) and datalog in terms of expressivity.
-We define a DHL ontology $\mathcal{O}$ as a triple:
-$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
-$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
-$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
-$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
-In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
-are roles in $\textbf{R}$.
-For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
-equivalent form $\exists R^-.A\sqsubseteq B$.
-
-DHL is related with other ontology languages.
-First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
-Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
-Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
-However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
-materialization.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
-\hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
-\hline
-\hline
-(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
-(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
-(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
-(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\
-
-\hline
-(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
-(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
-(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
-(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\
-
-\hline
-(A1)& $A(a)$& $A(a)$\\
-(A2)& $R(a,b)$& $R(a,b)$\\
-\hline
-\end{tabular}
-\label{tab:dhl}
-\end{center}
-\end{table}
-
-In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
-In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
-that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
-RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
-axioms of the forms (R1-R4). Note that (R3) is actually a special
-case of (R4).
-
-DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
-and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
-(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
-where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
-an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
-which allows involving RBoxes that contain axioms of the forms (R1-R2).
-If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
-in the following paragraphs}.
-
-\subsection{Ontology Materialization via Datalog Programs}
-
-An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
-(see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
-
-In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
-$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
-Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
-between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
-usage of highly expressive ontology languages \cite{HorrocksS04}.
-Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
-occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.
-
-Based on the above representations, ontology materialization
-corresponds to the evaluation of datalog programs.
-Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
-where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
- $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
-The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
-and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
-$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
-We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
-to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
-
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
-Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
-where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
-as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
-In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
-are implemented on shared-memory platforms, we
-study all the issues in this work by assuming that the running machines are in
-shared-memory configurations.
-
-\section{Parallel Tractability of Datalog Programs}
-\label{sec:ptclass}
-
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
-if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
-
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
-
-\begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
-\end{definition}
-
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
-for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
-which is the class of all datalog programs that can be handled by $\mathsf{A}$.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
-In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
-and identify the target \texttt{PTD} class.
-
-\subsection{Materialization Graph}
-
-In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
-
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
-\end{enumerate}
-\end{definition}
-
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
-We next give an example of a materialization graph.\\
-
-\begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
-$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
-the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
-where $\textbf{I}$ contains all the assertions in the ABox
-and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
-and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
-each of the other nodes corresponds to a ground instantiation of some rule.
-For example, the node $A(a_k)$ corresponds to the ground rule instantiation
-`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
-The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
-\label{fig:mg}
-\end{center}
-\end{figure}
-
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
-The set of nodes in a complete materialization graph is actually the result
-of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
-a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
-It should also be noted that there may exist several materialization graphs for a datalog program.
-
-\subsection{A Basic Parallel Algorithm}
-
-In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
-Initially $\mathcal{G}$ is empty. The following three steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
-    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
-Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
-\end{example}
-
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
-materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
-in the appendix.
-
-\begin{lemma}
-\label{lemma:a1}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-\begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}[Proof sketch] This lemma can be proved by performing
-an induction on $T_R^{\omega}(\textbf{I})$.
-The stage (see the related contents in Section~\ref{sec:background}) of $P$
-is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
-its depth equals the depth of the stage.
-\end{proof}
-
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
-We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
-
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
-We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
-
-\begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
-\end{theorem}
-
-\begin{proof}[Proof sketch]
-We can first prove that the number of iterations
-of \ref{alg1:updateG} is actually the depth of the constructed materialization
-graph. This theorem then follows by considering
-Lemma~\ref{lemma:a1}.
-\end{proof}
-
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
-Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
-We discuss this in the next part.
-
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
-
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
-we can identify another \texttt{PTD} class.
-
-We discuss our optimization based on a specific case in Example~\ref{exp:general}.
-We find that, in this kind of case, the construction of a materialization graph can be accelerated.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
-\label{fig:general}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
-Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
-is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
-The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
-In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
-All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
-afterwards.
-\end{example}
-
-In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
-node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
-Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
-$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
-$\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
-due to the single-way derivability condition.
-
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
-can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
-
-We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
-describe the reachability between two nodes. To this extent, we use a
-binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
-e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
-
-\begin{description}[leftmargin=2ex]
-\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
-\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
-\end{enumerate}
-\end{description}
-
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
-The following algorithm applies this optimization strategy.\\
-
-\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
-a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
-being constructed from $P$. The following steps are performed:
-\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
-that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
-    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
-    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
-\end{enumerate}
-
-It is well known that there is an \texttt{NC} algorithm for computing the
-transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
-    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
-\end{enumerate}
-
-It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
-
-\begin{lemma}\label{lemma:a3}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
-\end{lemma}
-
-\begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
-In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
-one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
-in the first iteration of \ref{alg3:updateG}.
-\end{example}
-
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
-
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
-
-\begin{corollary}
-For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{corollary}
-
-\begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
-if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
-\end{proof}
-
-\section{Parallel Tractability of Ontology Materialization in OWL}
-\label{sec:ptonto}
-
-In this section, we study the issue of parallel tractability
-for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
-there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
-work by studying specific cases.
-Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
-of materialization.
-
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
-
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
-DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
-there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
-In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
-the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
-
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
-we use the following example.
-
-\begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
-where its TBox and RBox contain the following axioms:
-$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
-its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
-where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
-as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
-\label{fig:ex2}
-\end{center}
-\end{figure}
-
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
-(\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
-$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
-for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
-since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
-$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
-(\uppercase\expandafter{\romannumeral3})
-The two nodes $\bot(a)$ and $\bot(b)$
-have no SWD path in the first iteration of \ref{alg3:updateG}.
-They are left to be processed in the second iteration.
-(\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
-after two iterations (\ref{alg3:halt}).
-
-From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
-
-\begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
-\end{lemma}
-
-The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
-have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
-of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
-an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
-more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
-
-\begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL}
-
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
-Based on the analysis of this case, we propose to restrict
-the usage of DHL in order to achieve parallel tractability
-of materialization.
-
-We find that, an unlimited usage of axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
-\label{fig:ex3_4}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
-where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
-\end{example}
-
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
-each node of the form $A(a_i)$ (filled with black color,
-and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
-number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
-
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
-we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
-to avoid `path twisting'. An intuitive idea is to
-ensure that \emph{there is only one path between each two atoms of the form $A(x)$
-generated from the rules corresponding to (T1)}.
-We explain it by using the following example where the ontology is modified from
-that in Example~\ref{exp:dhl}.
-
-\begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
-`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
-\end{example}
-
-In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
-of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
-since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
-node has an SWD path).
-Motivated by this example, we consider restricting the usage of
-the axioms $B_1\sqcap B_2\sqsubseteq A$
-such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
-for some $y$.
-To this end, we first define \emph{simple concepts} as follows:
-
-\begin{definition}
-Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
-of some axiom; or (2) $A$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
-\end{enumerate}
-\end{definition}
-
-Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
-is generated from the rules corresponding to (T1).
-
-\begin{example}
-In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
-non-simple concepts.
-In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
-the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
-\end{example}
-
-We define the following class of DHL ontologies based on the above restriction and
-give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
-
-\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
-each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
-$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
-\end{definition}
-
-\begin{theorem}\label{theorem:dhl}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
-
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
-In addition to the rules in DHL, we also have to consider complex RIAs (R4).
-We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
-\begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
-the RBox $\mathcal{R}$ contains three axioms:
-$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
-the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
-contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
-`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
-\end{example}
-
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
-Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
-
-Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
-we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
-then, at least one of $R_1$ and $R_2$ is
-a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
-We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
-we can get a complex RIA in the form of
-$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
-If one of $R_1$ and $R_2$ is not a simple role, the corresponding
-rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
-and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
-Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
-For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
-role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
-a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
-Further, the situation of path twisting also exists.
-To tackle the above issue,
-we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
-Combined with the simple-concept restriction,
-we define a class of DHL($\circ$) ontologies as follows:
-
-\begin{definition}\label{def:dhlplus}
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
-is rewritten from a DHL($\circ$) ontology and the following
-conditions are satisfied:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
-\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
-\end{enumerate}
-\end{definition}
-
-\begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
-the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
-in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
-\end{example}
-
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
-
-\begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
-\label{sec:practicalAlg}
-
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
-
-\subsection{Reducing Computing Space}
-
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
-However, this algorithm can hardly work in practice due to its inherently
-high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
-Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
-when the target datalog program or ontology
-tends to be large in size.
-On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
-we can observe that the rule instantiations used for the construction
-of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
-by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-each of the checked rule instantiations should involve at least one body atom that has been
-added to the constructed materialization graph}.
-Since DHL$(\circ)$
-is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
-as follows.
-
-We first consider a datalog rule of the
-form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
-of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
-graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
-the datalog rule `$A(x)\rightarrow B(x)$'
-has only one rule instantiation `$A(a)\rightarrow B(a)$' where
-the variable $x$ is substituted by the constant $a$.
-The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
-`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
-at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
-added to $\mathcal{G}$.
-Note that, for rule instantiations of two body atoms,
-we do not require that both of these two body atoms have been added to
-the constructed materialization graph.
-Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
-
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
-
-We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
-and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
-narrowing down the scope of rule instantiations to be checked as well. This can be described
-by the following algorithm.\\
-
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
-and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
-
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
-\end{enumerate}
-
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
-datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
-returns a materialization graph $\mathcal{G}$ of $P$.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
-    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
-DHL$(\circ)$ materialization.
-
-\begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
-all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
-an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
-are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
-\end{example}
-
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
-
-\begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
-and compare it to the reasoning system RDFox.
-
-\subsection{Practical Usability of the Theoretical Results}
-
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
-facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
-
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
-
-\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
-
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
-
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
-
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
-
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
-restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
-
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
-\hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
-\hline
-
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
-\end{tabular}
-\label{tab:info}
-\end{center}
-
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
-
-\textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
-
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
-\end{center}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-\label{tab:expresult}
-\end{center}
-
-\section{Related Work}
-\label{sec:related}
-
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-There is work that studies parallel reasoning in RDFS and OWL.
-The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
-The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
-Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data).
-The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets.
-On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}.
-In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
-
-Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
-The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
-Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
-This is not the focus in this paper.
-
-Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data.
-The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
-datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
-
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
-
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
-other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
-have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
-explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
-study how to further apply the
-results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
-
-\section*{Acknowledgments}
-
-This work was partially supported by NSFC
-grant 61672153 and the 863 program under Grant
-2015AA015406.
-
-\section*{Reference}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{reference}
-
-\clearpage
-
-\section*{Appendix}
-
-\appendix
-
-\section{Proof of Lemma~\ref{lemma:a1}}
-
-\textbf{Lemma~\ref{lemma:a1}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
-
-\noindent\emph{Proof}:
-(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
-check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
-Thus $\mathcal{G}$ turns out to be an acyclic graph.
-Second, to show $\mathcal{G}$ is a
-complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
-Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
-For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
-added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
-there has to be a processor that would add it to $\mathcal{G}$.
-
-(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
-of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
-Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:a1}}
-
-\textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
-
-\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
-is actually the depth of the constructed materialization graph.
-We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
-By performing an induction on the number of iterations of \ref{alg1:updateG},
-one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
-where $n$=\texttt{depth}($v'$).
-Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
-We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).
-
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
-a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
-
-($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
-If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
-the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
-should have a smaller depth compared with $\mathcal{G}$.
-In this case, this conclusion still holds.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:a3}}
-
-\textbf{Lemma~\ref{lemma:a3}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
-
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
-In this case, $\mathcal{G}$ is obviously a materialization graph.
-
-\emph{Inductive case}.
-According to the induction hypothesis, the partial graph constructed after
-the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
-also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
-It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
-and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-In the above two cases, $H$ is a new node. Thus,
-$\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
-the algorithm does nothing.
-Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.
-
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
-We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
-According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:dllite}}
-
-\textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
-
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
-$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
-for any materialization graph.
-
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
-We are left to prove that $H$ has an SWD path as well
-in all materialization graphs of $\mathcal{O}$.
-
-If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
-applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
-\item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
-We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
-
-\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
-according to the induction hypothesis.
-It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
-in some materialization graph.
-\end{enumerate}
-
-Since node $A(x)$ can only be derived in either Case~1.1
-or Case~1.2, we have that
-node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
-
-It is similar to prove the case where $H$ is in the form of $R(x,y)$.
-Since node $R(x,y)$ may be derived by
-applying (R1) and (R2), we discuss these two cases.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
-\item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
-Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
-in some materialization graph.
-
-\item $S\sqsubseteq R^-$. This case is similar to
-the above case.
-\end{enumerate}
-
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dl-lite}}
-
-\textbf{Theorem~\ref{theorem:dl-lite}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
-since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dhl}}
-
-\textbf{Theorem~\ref{theorem:dhl}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
-ontology can be separated into two stages: in the first stage (Stage~1), all the rules
-of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
-also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
-are then applied in Stage~2.
-It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
-for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
-such a poly-logarithmical function $\psi$ exists.
-
-In Stage~1, the rules of the forms (R1-R3)
-are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
-handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
-
-\begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
-\end{definition}
-
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
-We then have the following lemma.
-
-\begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
-\end{lemma}
-
-Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
-In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1) and (R2);
-(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
-where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
-generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
-
-We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
-    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.
-
-\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
-    role.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:dhlplus}}
-
-\textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
-That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
-all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
-
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
-that is defined as follows:
-
-\begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
-\end{definition}
-
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
-We then give the following definition for $\delta_R$.
-
-\begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
-\end{definition}
-
-\begin{lemma}\label{lemma:tiplus}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
-$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
-\end{lemma}
-
-The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
-Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
-The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1), (R2) and (R4);
-(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
-one can further perform (R1), (R2) and (R4) iteratively based on all
-transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
-All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-We now prove Lemma~\ref{lemma:tiplus}.
-We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
-
-    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
-    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.
-
-    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.
-
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
-    \end{enumerate}
-
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
-    holds.\label{dhlplus:NTIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Further, $R$ is a transitive role. According to the simple-role restriction,
-    both of $R_1$ and $R_2$ are simple roles.
-    This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
-    This case is similar to \ref{dhlplus:NTIcaseR4}.
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
-        Then, $R'$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
-        $R'^-$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
-    at least one of $R_1$ and $R_2$ is a simple role.
-    W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
-    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
-    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
-    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:aprc}}
-
-\textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
-this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
-(see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
-
-To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
-We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
-$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
-$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:aprcpt}}
-
-\textbf{Theorem~\ref{theorem:aprcpt}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that $\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
-\emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
-\emph{the simple concept materialization} (Stage~SCM) and
-\emph{the non-simple concept materialization} (Stage~NSCM).
-Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
-where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
-role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.
-
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
-such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
-Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
-there exists a poly-logarithmically bounded function $\psi'$
-such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.
-
-We first consider Stage~SCM.
-Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
-and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
-can be viewed as an EDB predicate. This further means that,
-for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
-Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
-The atom $A(a)$ can be derived through either of the following rule instantiations:
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
-
-\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
-    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
-    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-\end{enumerate}
-
-We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
-According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
-In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
-We also use an induction to show that
-such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
-here.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
-    If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
-\end{enumerate}
-
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
-
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
-We use an induction to show that
-such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
-as follows.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
-    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
-\end{enumerate}
-
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
-is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
-$R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
-of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
-can also be computed by $\mathsf{A}_{prc}^\psi$ for some
-poly-logarithmically bounded function $\psi$.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
-    One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
-    all nodes in each level of $t$ in one iteration from the bottom. Thus,
-    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
-\end{enumerate}
-
-\end{document}
-\endinput
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-01-29 parallel-tractability-J-v9/optimizedAlgo.tex
splitting the main file for better organization

--- 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
@@
-%\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
- \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-\usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-\usepackage{amsmath}
-
-\usepackage{CJK}
-\usepackage{color}
-
-\usepackage{enumitem}
-\usepackage{rotating}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-%\journal{Nuclear Physics B}
-
-\hyphenation{data-log}
-
-\begin{document}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Parallel Tractability of Ontology\\
-Materialization: Technique and Practice}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author[add1]{Zhangquan Zhou \corref{cor1}}
-\ead{quanzz1129@gmail.com}
-\cortext[cor1]{Corresponding author}
-
-\author[add1]{Guilin Qi}
-\ead{gqi@seu.edu.cn}
-
-\author[add2]{Birte Glimm}
-\ead{birte.glimm@uni-ulm.de}
-
-\address[add1]{
-    School of Computer Science, Southeast University, China
-}
-
-\address[add2]{
-    Institute of Artificial Intelligence, University of Ulm
-}
-
-\begin{abstract}
-  Materialization is an important reasoning service for many
-  ontology-based applications, but the rapid growth of semantic data
-  poses the challenge to efficiently perform materialization on
-  large-scale ontologies. Parallel materialization algorithms work
-  well for some ontologies, which is not always explained by the
-  theoretical results. For example, for the YAGO ontology
-  parallelization works well, although the reasoning problem for the
-  used ontology language is not in \texttt{NC}, i.e.\ the theoretical
-  complexity class for \emph{parallel tractability}. This motivates us
-  to study the problem of \emph{parallel tractability} of ontology
-  materialization from a theoretical perspective. We focus on the
-  datalog rewritable ontology languages DL-Lite and Description Horn
-  Logic (DHL) and propose algorithms, called \texttt{NC} algorithms,
-  to identify classes of ontologies for which materialization is
-  tractable in parallel. To verify the practical usability of the
-  above results, we analyze real-world datasets and show that for many
-  ontologies expressed in DHL materialization is tractable in
-  parallel. The implementation of our optimized parallel algorithm
-  shows performance improvements over the highly optimized
-  state-of-the-art reasoner RDFox on ontologies for which
-  materialization is tractable in parallel.
-\end{abstract}
-
-\begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-\section{Introduction}
-\label{sec:introduction}
-
-The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
-are being generated at an increasing pace by sensor networks, government authorities and social
-media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.
-
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
-MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
-
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
-While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
-for which parallel tractability can be guaranteed theoretically.
-
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
-This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
-we also discuss how to optimize and implement them.
-
-In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
-We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
-in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
-Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
-We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
-
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
-In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
-
-\section{Background Knowledge}
-\label{sec:background}
-
-In this section, we introduce some basic notions that are needed to introduce our approach.
-
-\subsection{Datalog}
-
-We discuss the main issues in this paper using standard datalog notions.
-In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
-constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
-represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
-of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
-the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
-A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
-For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
-with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
-if each defined $A\theta$ is a ground atom.
-A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
-the terms in this rule with respect to a finite set of constants occurring in $P$.
-Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
-The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
-while the predicates that may occur as head atoms are called \emph{IDB predicates}.
-
-\subsection{DHL and DL-Lite}
-
-In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
-to denote three disjoint countably
-infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
-The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
-where $R^-$ is the \emph{inverse role} of $R$.
-For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
-
-DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
-intersection of description logic (DL) and datalog in terms of expressivity.
-We define a DHL ontology $\mathcal{O}$ as a triple:
-$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
-$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
-$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
-$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
-In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
-are roles in $\textbf{R}$.
-For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
-equivalent form $\exists R^-.A\sqsubseteq B$.
-
-DHL is related with other ontology languages.
-First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
-Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
-Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
-However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
-materialization.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
-\hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
-\hline
-\hline
-(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
-(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
-(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
-(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\
-
-\hline
-(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
-(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
-(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
-(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\
-
-\hline
-(A1)& $A(a)$& $A(a)$\\
-(A2)& $R(a,b)$& $R(a,b)$\\
-\hline
-\end{tabular}
-\label{tab:dhl}
-\end{center}
-\end{table}
-
-In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
-In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
-that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
-RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
-axioms of the forms (R1-R4). Note that (R3) is actually a special
-case of (R4).
-
-DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
-and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
-(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
-where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
-an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
-which allows involving RBoxes that contain axioms of the forms (R1-R2).
-If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
-in the following paragraphs}.
-
-\subsection{Ontology Materialization via Datalog Programs}
-
-An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
-(see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
-
-In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
-$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
-Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
-between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
-usage of highly expressive ontology languages \cite{HorrocksS04}.
-Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
-occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.
-
-Based on the above representations, ontology materialization
-corresponds to the evaluation of datalog programs.
-Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
-where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
- $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
-The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
-and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
-$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
-We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
-to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
-
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
-Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
-where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
-as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
-In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
-are implemented on shared-memory platforms, we
-study all the issues in this work by assuming that the running machines are in
-shared-memory configurations.
-
-\section{Parallel Tractability of Datalog Programs}
-\label{sec:ptclass}
-
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
-if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
-
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
-
-\begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
-\end{definition}
-
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
-for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
-which is the class of all datalog programs that can be handled by $\mathsf{A}$.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
-In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
-and identify the target \texttt{PTD} class.
-
-\subsection{Materialization Graph}
-
-In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
-
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
-\end{enumerate}
-\end{definition}
-
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
-We next give an example of a materialization graph.\\
-
-\begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
-$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
-the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
-where $\textbf{I}$ contains all the assertions in the ABox
-and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
-and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
-each of the other nodes corresponds to a ground instantiation of some rule.
-For example, the node $A(a_k)$ corresponds to the ground rule instantiation
-`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
-The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
-\label{fig:mg}
-\end{center}
-\end{figure}
-
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
-The set of nodes in a complete materialization graph is actually the result
-of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
-a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
-It should also be noted that there may exist several materialization graphs for a datalog program.
-
-\subsection{A Basic Parallel Algorithm}
-
-In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
-Initially $\mathcal{G}$ is empty. The following three steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
-    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
-Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
-\end{example}
-
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
-materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
-in the appendix.
-
-\begin{lemma}
-\label{lemma:a1}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-\begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}[Proof sketch] This lemma can be proved by performing
-an induction on $T_R^{\omega}(\textbf{I})$.
-The stage (see the related contents in Section~\ref{sec:background}) of $P$
-is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
-its depth equals the depth of the stage.
-\end{proof}
-
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
-We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
-
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
-We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
-
-\begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
-\end{theorem}
-
-\begin{proof}[Proof sketch]
-We can first prove that the number of iterations
-of \ref{alg1:updateG} is actually the depth of the constructed materialization
-graph. This theorem then follows by considering
-Lemma~\ref{lemma:a1}.
-\end{proof}
-
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
-Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
-We discuss this in the next part.
-
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
-
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
-we can identify another \texttt{PTD} class.
-
-We discuss our optimization based on a specific case in Example~\ref{exp:general}.
-We find that, in this kind of case, the construction of a materialization graph can be accelerated.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
-\label{fig:general}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
-Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
-is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
-The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
-In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
-All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
-afterwards.
-\end{example}
-
-In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
-node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
-Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
-$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
-$\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
-due to the single-way derivability condition.
-
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
-can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
-
-We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
-describe the reachability between two nodes. To this extent, we use a
-binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
-e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
-
-\begin{description}[leftmargin=2ex]
-\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
-\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
-\end{enumerate}
-\end{description}
-
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
-The following algorithm applies this optimization strategy.\\
-
-\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
-a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
-being constructed from $P$. The following steps are performed:
-\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
-that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
-    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
-    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
-\end{enumerate}
-
-It is well known that there is an \texttt{NC} algorithm for computing the
-transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
-    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
-\end{enumerate}
-
-It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
-
-\begin{lemma}\label{lemma:a3}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
-\end{lemma}
-
-\begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
-In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
-one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
-in the first iteration of \ref{alg3:updateG}.
-\end{example}
-
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
-
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
-
-\begin{corollary}
-For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{corollary}
-
-\begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
-if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
-\end{proof}
-
-\section{Parallel Tractability of Ontology Materialization in OWL}
-\label{sec:ptonto}
-
-In this section, we study the issue of parallel tractability
-for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
-there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
-work by studying specific cases.
-Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
-of materialization.
-
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
-
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
-DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
-there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
-In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
-the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
-
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
-we use the following example.
-
-\begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
-where its TBox and RBox contain the following axioms:
-$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
-its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
-where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
-as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
-\label{fig:ex2}
-\end{center}
-\end{figure}
-
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
-(\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
-$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
-for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
-since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
-$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
-(\uppercase\expandafter{\romannumeral3})
-The two nodes $\bot(a)$ and $\bot(b)$
-have no SWD path in the first iteration of \ref{alg3:updateG}.
-They are left to be processed in the second iteration.
-(\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
-after two iterations (\ref{alg3:halt}).
-
-From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
-
-\begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
-\end{lemma}
-
-The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
-have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
-of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
-an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
-more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
-
-\begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL}
-
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
-Based on the analysis of this case, we propose to restrict
-the usage of DHL in order to achieve parallel tractability
-of materialization.
-
-We find that, an unlimited usage of axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
-\label{fig:ex3_4}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
-where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
-\end{example}
-
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
-each node of the form $A(a_i)$ (filled with black color,
-and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
-number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
-
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
-we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
-to avoid `path twisting'. An intuitive idea is to
-ensure that \emph{there is only one path between each two atoms of the form $A(x)$
-generated from the rules corresponding to (T1)}.
-We explain it by using the following example where the ontology is modified from
-that in Example~\ref{exp:dhl}.
-
-\begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
-`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
-\end{example}
-
-In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
-of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
-since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
-node has an SWD path).
-Motivated by this example, we consider restricting the usage of
-the axioms $B_1\sqcap B_2\sqsubseteq A$
-such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
-for some $y$.
-To this end, we first define \emph{simple concepts} as follows:
-
-\begin{definition}
-Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
-of some axiom; or (2) $A$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
-\end{enumerate}
-\end{definition}
-
-Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
-is generated from the rules corresponding to (T1).
-
-\begin{example}
-In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
-non-simple concepts.
-In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
-the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
-\end{example}
-
-We define the following class of DHL ontologies based on the above restriction and
-give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
-
-\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
-each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
-$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
-\end{definition}
-
-\begin{theorem}\label{theorem:dhl}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
-
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
-In addition to the rules in DHL, we also have to consider complex RIAs (R4).
-We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
-\begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
-the RBox $\mathcal{R}$ contains three axioms:
-$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
-the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
-contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
-`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
-\end{example}
-
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
-Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
-
-Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
-we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
-then, at least one of $R_1$ and $R_2$ is
-a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
-We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
-we can get a complex RIA in the form of
-$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
-If one of $R_1$ and $R_2$ is not a simple role, the corresponding
-rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
-and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
-Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
-For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
-role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
-a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
-Further, the situation of path twisting also exists.
-To tackle the above issue,
-we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
-Combined with the simple-concept restriction,
-we define a class of DHL($\circ$) ontologies as follows:
-
-\begin{definition}\label{def:dhlplus}
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
-is rewritten from a DHL($\circ$) ontology and the following
-conditions are satisfied:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
-\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
-\end{enumerate}
-\end{definition}
-
-\begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
-the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
-in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
-\end{example}
-
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
-
-\begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
 \section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
@@
 and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
+(2) a (partial) materialization graph $\mathcal{G}=\langle V,E\rangle$ that is constructed from $P$.
 This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
+is computed as follows:
 
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
+\item add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A(a)\rightarrow B(a)\in P^*$, $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in V$;
 
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
+\item add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$ where $R(a,b),A(b)\rightarrow B(a)\in P^*$, $\exists R.A\sqsubseteq B\in\mathcal{T}$ and $R(a,b)\in V$;
 
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
+\item add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
+    $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$ and $A_1(a)\in V$;
 
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
+\item add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
+    $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$ and $A_2(a)\in V$;
 
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
+\item add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$ where $R(a,b)\rightarrow S(a,b)\in P^*$,
+    $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in V$;
 
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
+\item add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$ where $R(a,b)\rightarrow S(b,a)\in P^*$,
+    $\mathcal{O}\models R\sqsubseteq_* S^-$ and $R(a,b)\in V$;
+
+\item add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$,
+    $R_1\circ R_2\sqsubseteq R_3\in\mathcal{R}$ (the case
+    where $R_1\equiv R_2\equiv R_3$ is also involved) and $R_1(a,b)\in V$;
+
+\item add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$,
+    $R_1\circ R_2\sqsubseteq R_3\in\mathcal{R}$ and $R_2(b,c)\in V$.\hfill$\Box$
 \end{enumerate}
@@
 
-\section{Evaluation}
-\label{sec:evaluation}
-
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
-and compare it to the reasoning system RDFox.
-
-\subsection{Practical Usability of the Theoretical Results}
-
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
-facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
-
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
-
-\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
-
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
-
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
-
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
-
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
-restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
-
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
-\hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
-\hline
-
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
-\end{tabular}
-\label{tab:info}
-\end{center}
-
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
-
-\textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
-
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
-\end{center}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-\label{tab:expresult}
-\end{center}
-
-\section{Related Work}
-\label{sec:related}
-
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-There is work that studies parallel reasoning in RDFS and OWL.
-The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
-The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
-Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data).
-The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets.
-On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}.
-In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
-
-Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
-The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
-Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
-This is not the focus in this paper.
-
-Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data.
-The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
-datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
-
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
-
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
-other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
-have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
-explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
-study how to further apply the
-results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
-
-\section*{Acknowledgments}
-
-This work was partially supported by NSFC
-grant 61672153 and the 863 program under Grant
-2015AA015406.
-
-\section*{Reference}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{reference}
-
-\clearpage
-
-\section*{Appendix}
-
-\appendix
-
-\section{Proof of Lemma~\ref{lemma:a1}}
-
-\textbf{Lemma~\ref{lemma:a1}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
-
-\noindent\emph{Proof}:
-(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
-check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
-Thus $\mathcal{G}$ turns out to be an acyclic graph.
-Second, to show $\mathcal{G}$ is a
-complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
-Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
-For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
-added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
-there has to be a processor that would add it to $\mathcal{G}$.
-
-(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
-of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
-Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:a1}}
-
-\textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
-
-\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
-is actually the depth of the constructed materialization graph.
-We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
-By performing an induction on the number of iterations of \ref{alg1:updateG},
-one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
-where $n$=\texttt{depth}($v'$).
-Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
-We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).
-
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
-a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
-
-($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
-If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
-the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
-should have a smaller depth compared with $\mathcal{G}$.
-In this case, this conclusion still holds.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:a3}}
-
-\textbf{Lemma~\ref{lemma:a3}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
-
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
-In this case, $\mathcal{G}$ is obviously a materialization graph.
-
-\emph{Inductive case}.
-According to the induction hypothesis, the partial graph constructed after
-the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
-also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
-It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
-and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-In the above two cases, $H$ is a new node. Thus,
-$\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
-the algorithm does nothing.
-Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.
-
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
-We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
-According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:dllite}}
-
-\textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
-
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
-$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
-for any materialization graph.
-
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
-We are left to prove that $H$ has an SWD path as well
-in all materialization graphs of $\mathcal{O}$.
-
-If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
-applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
-\item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
-We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
-
-\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
-according to the induction hypothesis.
-It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
-in some materialization graph.
-\end{enumerate}
-
-Since node $A(x)$ can only be derived in either Case~1.1
-or Case~1.2, we have that
-node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
-
-It is similar to prove the case where $H$ is in the form of $R(x,y)$.
-Since node $R(x,y)$ may be derived by
-applying (R1) and (R2), we discuss these two cases.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
-\item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
-Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
-in some materialization graph.
-
-\item $S\sqsubseteq R^-$. This case is similar to
-the above case.
-\end{enumerate}
-
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dl-lite}}
-
-\textbf{Theorem~\ref{theorem:dl-lite}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
-since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dhl}}
-
-\textbf{Theorem~\ref{theorem:dhl}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
-ontology can be separated into two stages: in the first stage (Stage~1), all the rules
-of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
-also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
-are then applied in Stage~2.
-It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
-for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
-such a poly-logarithmical function $\psi$ exists.
-
-In Stage~1, the rules of the forms (R1-R3)
-are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
-handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
-
-\begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
-\end{definition}
-
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
-We then have the following lemma.
-
-\begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
-\end{lemma}
-
-Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
-In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1) and (R2);
-(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
-where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
-generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
-
-We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
-    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.
-
-\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
-    role.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:dhlplus}}
-
-\textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
-That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
-all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
-
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
-that is defined as follows:
-
-\begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
-\end{definition}
-
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
-We then give the following definition for $\delta_R$.
-
-\begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
-\end{definition}
-
-\begin{lemma}\label{lemma:tiplus}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
-$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
-\end{lemma}
-
-The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
-Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
-The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1), (R2) and (R4);
-(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
-one can further perform (R1), (R2) and (R4) iteratively based on all
-transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
-All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-We now prove Lemma~\ref{lemma:tiplus}.
-We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
-
-    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
-    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.
-
-    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.
-
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
-    \end{enumerate}
-
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
-    holds.\label{dhlplus:NTIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Further, $R$ is a transitive role. According to the simple-role restriction,
-    both of $R_1$ and $R_2$ are simple roles.
-    This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
-    This case is similar to \ref{dhlplus:NTIcaseR4}.
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
-        Then, $R'$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
-        $R'^-$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
-    at least one of $R_1$ and $R_2$ is a simple role.
-    W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
-    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
-    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
-    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:aprc}}
-
-\textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
-this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
-(see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
-
-To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
-We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
-$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
-$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:aprcpt}}
-
-\textbf{Theorem~\ref{theorem:aprcpt}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that $\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
-\emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
-\emph{the simple concept materialization} (Stage~SCM) and
-\emph{the non-simple concept materialization} (Stage~NSCM).
-Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
-where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
-role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.
-
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
-such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
-Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
-there exists a poly-logarithmically bounded function $\psi'$
-such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.
-
-We first consider Stage~SCM.
-Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
-and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
-can be viewed as an EDB predicate. This further means that,
-for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
-Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
-The atom $A(a)$ can be derived through either of the following rule instantiations:
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
-
-\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
-    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
-    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-\end{enumerate}
-
-We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
-According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
-In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
-We also use an induction to show that
-such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
-here.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
-    If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
-\end{enumerate}
-
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
-
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
-We use an induction to show that
-such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
-as follows.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
-    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
-\end{enumerate}
-
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
-is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
-$R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
-of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
-can also be computed by $\mathsf{A}_{prc}^\psi$ for some
-poly-logarithmically bounded function $\psi$.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
-    One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
-    all nodes in each level of $t$ in one iteration from the bottom. Thus,
-    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
-\end{enumerate}
-
-\end{document}
-\endinput
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
splitting the main file for better organization

--- 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
@@
 
-\section{Introduction}
-\label{sec:introduction}
+\input{introduction}
 
-The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
-are being generated at an increasing pace by sensor networks, government authorities and social
-media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.
+\input{background}
 
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
-MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
+\input{parallelTractabilityDatalog}
 
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
-While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
-for which parallel tractability can be guaranteed theoretically.
+\input{parallelTractabilityOntMat}
 
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
-This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
-we also discuss how to optimize and implement them.
+\input{optimizedAlgo}
 
-In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
-We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
-in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
-Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
-We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
+\input{evaluation}
 
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
-In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
+\input{relatedWork}
 
-\section{Background Knowledge}
-\label{sec:background}
-
-In this section, we introduce some basic notions that are needed to introduce our approach.
-
-\subsection{Datalog}
-
-We discuss the main issues in this paper using standard datalog notions.
-In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
-constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
-represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
-of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
-the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
-A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
-For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
-with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
-if each defined $A\theta$ is a ground atom.
-A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
-the terms in this rule with respect to a finite set of constants occurring in $P$.
-Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
-The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
-while the predicates that may occur as head atoms are called \emph{IDB predicates}.
-
-\subsection{DHL and DL-Lite}
-
-In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
-to denote three disjoint countably
-infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
-The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
-where $R^-$ is the \emph{inverse role} of $R$.
-For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
-
-DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
-intersection of description logic (DL) and datalog in terms of expressivity.
-We define a DHL ontology $\mathcal{O}$ as a triple:
-$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
-$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
-$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
-$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
-In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
-are roles in $\textbf{R}$.
-For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
-equivalent form $\exists R^-.A\sqsubseteq B$.
-
-DHL is related with other ontology languages.
-First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
-Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
-Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
-However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
-materialization.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
-\hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
-\hline
-\hline
-(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
-(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
-(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
-(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\
-
-\hline
-(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
-(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
-(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
-(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\
-
-\hline
-(A1)& $A(a)$& $A(a)$\\
-(A2)& $R(a,b)$& $R(a,b)$\\
-\hline
-\end{tabular}
-\label{tab:dhl}
-\end{center}
-\end{table}
-
-In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
-In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
-that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
-RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
-axioms of the forms (R1-R4). Note that (R3) is actually a special
-case of (R4).
-
-DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
-and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
-(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
-where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
-an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
-which allows involving RBoxes that contain axioms of the forms (R1-R2).
-If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
-in the following paragraphs}.
-
-\subsection{Ontology Materialization via Datalog Programs}
-
-An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
-(see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
-
-In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
-$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
-Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
-between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
-usage of highly expressive ontology languages \cite{HorrocksS04}.
-Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
-occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.
-
-Based on the above representations, ontology materialization
-corresponds to the evaluation of datalog programs.
-Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
-where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
- $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
-The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
-and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
-$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
-We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
-to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
-
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
-Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
-where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
-as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
-In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
-are implemented on shared-memory platforms, we
-study all the issues in this work by assuming that the running machines are in
-shared-memory configurations.
-
-\section{Parallel Tractability of Datalog Programs}
-\label{sec:ptclass}
-
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
-if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
-
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
-
-\begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
-\end{definition}
-
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
-for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
-which is the class of all datalog programs that can be handled by $\mathsf{A}$.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
-In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
-and identify the target \texttt{PTD} class.
-
-\subsection{Materialization Graph}
-
-In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
-
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
-\end{enumerate}
-\end{definition}
-
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
-We next give an example of a materialization graph.\\
-
-\begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
-$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
-the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
-where $\textbf{I}$ contains all the assertions in the ABox
-and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
-and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
-each of the other nodes corresponds to a ground instantiation of some rule.
-For example, the node $A(a_k)$ corresponds to the ground rule instantiation
-`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
-The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
-\label{fig:mg}
-\end{center}
-\end{figure}
-
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
-The set of nodes in a complete materialization graph is actually the result
-of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
-a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
-It should also be noted that there may exist several materialization graphs for a datalog program.
-
-\subsection{A Basic Parallel Algorithm}
-
-In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
-Initially $\mathcal{G}$ is empty. The following three steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
-    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
-Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
-\end{example}
-
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
-materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
-in the appendix.
-
-\begin{lemma}
-\label{lemma:a1}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-\begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}[Proof sketch] This lemma can be proved by performing
-an induction on $T_R^{\omega}(\textbf{I})$.
-The stage (see the related contents in Section~\ref{sec:background}) of $P$
-is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
-its depth equals the depth of the stage.
-\end{proof}
-
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
-We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
-
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
-We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
-
-\begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
-\end{theorem}
-
-\begin{proof}[Proof sketch]
-We can first prove that the number of iterations
-of \ref{alg1:updateG} is actually the depth of the constructed materialization
-graph. This theorem then follows by considering
-Lemma~\ref{lemma:a1}.
-\end{proof}
-
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
-Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
-We discuss this in the next part.
-
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
-
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
-we can identify another \texttt{PTD} class.
-
-We discuss our optimization based on a specific case in Example~\ref{exp:general}.
-We find that, in this kind of case, the construction of a materialization graph can be accelerated.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
-\label{fig:general}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
-Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
-is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
-The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
-In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
-All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
-afterwards.
-\end{example}
-
-In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
-node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
-Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
-$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
-$\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
-due to the single-way derivability condition.
-
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
-can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
-
-We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
-describe the reachability between two nodes. To this extent, we use a
-binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
-e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
-
-\begin{description}[leftmargin=2ex]
-\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
-\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
-\end{enumerate}
-\end{description}
-
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
-The following algorithm applies this optimization strategy.\\
-
-\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
-a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
-being constructed from $P$. The following steps are performed:
-\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
-that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
-    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
-    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
-\end{enumerate}
-
-It is well known that there is an \texttt{NC} algorithm for computing the
-transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
-    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
-\end{enumerate}
-
-It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
-
-\begin{lemma}\label{lemma:a3}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
-\end{lemma}
-
-\begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
-In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
-one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
-in the first iteration of \ref{alg3:updateG}.
-\end{example}
-
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
-
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
-
-\begin{corollary}
-For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{corollary}
-
-\begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
-if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
-\end{proof}
-
-\section{Parallel Tractability of Ontology Materialization in OWL}
-\label{sec:ptonto}
-
-In this section, we study the issue of parallel tractability
-for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
-there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
-work by studying specific cases.
-Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
-of materialization.
-
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
-
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
-DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
-there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
-In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
-the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
-
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
-we use the following example.
-
-\begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
-where its TBox and RBox contain the following axioms:
-$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
-its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
-where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
-as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
-\label{fig:ex2}
-\end{center}
-\end{figure}
-
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
-(\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
-$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
-for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
-since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
-$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
-(\uppercase\expandafter{\romannumeral3})
-The two nodes $\bot(a)$ and $\bot(b)$
-have no SWD path in the first iteration of \ref{alg3:updateG}.
-They are left to be processed in the second iteration.
-(\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
-after two iterations (\ref{alg3:halt}).
-
-From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
-
-\begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
-\end{lemma}
-
-The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
-have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
-of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
-an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
-more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
-
-\begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL}
-
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
-Based on the analysis of this case, we propose to restrict
-the usage of DHL in order to achieve parallel tractability
-of materialization.
-
-We find that, an unlimited usage of axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
-\label{fig:ex3_4}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
-where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
-\end{example}
-
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
-each node of the form $A(a_i)$ (filled with black color,
-and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
-number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
-
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
-we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
-to avoid `path twisting'. An intuitive idea is to
-ensure that \emph{there is only one path between each two atoms of the form $A(x)$
-generated from the rules corresponding to (T1)}.
-We explain it by using the following example where the ontology is modified from
-that in Example~\ref{exp:dhl}.
-
-\begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
-`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
-\end{example}
-
-In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
-of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
-since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
-node has an SWD path).
-Motivated by this example, we consider restricting the usage of
-the axioms $B_1\sqcap B_2\sqsubseteq A$
-such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
-for some $y$.
-To this end, we first define \emph{simple concepts} as follows:
-
-\begin{definition}
-Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
-of some axiom; or (2) $A$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
-\end{enumerate}
-\end{definition}
-
-Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
-is generated from the rules corresponding to (T1).
-
-\begin{example}
-In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
-non-simple concepts.
-In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
-the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
-\end{example}
-
-We define the following class of DHL ontologies based on the above restriction and
-give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
-
-\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
-each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
-$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
-\end{definition}
-
-\begin{theorem}\label{theorem:dhl}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
-
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
-In addition to the rules in DHL, we also have to consider complex RIAs (R4).
-We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
-\begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
-the RBox $\mathcal{R}$ contains three axioms:
-$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
-the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
-contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
-`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
-\end{example}
-
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
-Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
-
-Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
-we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
-then, at least one of $R_1$ and $R_2$ is
-a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
-We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
-we can get a complex RIA in the form of
-$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
-If one of $R_1$ and $R_2$ is not a simple role, the corresponding
-rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
-and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
-Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
-For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
-role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
-a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
-Further, the situation of path twisting also exists.
-To tackle the above issue,
-we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
-Combined with the simple-concept restriction,
-we define a class of DHL($\circ$) ontologies as follows:
-
-\begin{definition}\label{def:dhlplus}
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
-is rewritten from a DHL($\circ$) ontology and the following
-conditions are satisfied:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
-\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
-\end{enumerate}
-\end{definition}
-
-\begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
-the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
-in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
-\end{example}
-
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
-
-\begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
-\label{sec:practicalAlg}
-
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
-
-\subsection{Reducing Computing Space}
-
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
-However, this algorithm can hardly work in practice due to its inherently
-high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
-Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
-when the target datalog program or ontology
-tends to be large in size.
-On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
-we can observe that the rule instantiations used for the construction
-of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
-by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-each of the checked rule instantiations should involve at least one body atom that has been
-added to the constructed materialization graph}.
-Since DHL$(\circ)$
-is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
-as follows.
-
-We first consider a datalog rule of the
-form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
-of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
-graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
-the datalog rule `$A(x)\rightarrow B(x)$'
-has only one rule instantiation `$A(a)\rightarrow B(a)$' where
-the variable $x$ is substituted by the constant $a$.
-The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
-`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
-at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
-added to $\mathcal{G}$.
-Note that, for rule instantiations of two body atoms,
-we do not require that both of these two body atoms have been added to
-the constructed materialization graph.
-Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
-
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
-
-We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
-and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
-narrowing down the scope of rule instantiations to be checked as well. This can be described
-by the following algorithm.\\
-
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
-and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
-
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
-\end{enumerate}
-
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
-datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
-returns a materialization graph $\mathcal{G}$ of $P$.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
-    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
-DHL$(\circ)$ materialization.
-
-\begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
-all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
-an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
-are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
-\end{example}
-
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
-
-\begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
-and compare it to the reasoning system RDFox.
-
-\subsection{Practical Usability of the Theoretical Results}
-
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
-facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
-
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
-
-\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
-
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
-
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
-
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
-
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
-restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
-
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
-\hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
-\hline
-
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
-\end{tabular}
-\label{tab:info}
-\end{center}
-
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
-
-\textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
-
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
-\end{center}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-\label{tab:expresult}
-\end{center}
-
-\section{Related Work}
-\label{sec:related}
-
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-There is work that studies parallel reasoning in RDFS and OWL.
-The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
-The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
-Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data).
-The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets.
-On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}.
-In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
-
-Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
-The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
-Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
-This is not the focus in this paper.
-
-Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data.
-The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
-datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
-
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
-
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
-other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
-have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
-explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
-study how to further apply the
-results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
+\input{conclusions}
 
@@
 
-\section*{Appendix}
-
-\appendix
-
-\section{Proof of Lemma~\ref{lemma:a1}}
-
-\textbf{Lemma~\ref{lemma:a1}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
-
-\noindent\emph{Proof}:
-(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
-check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
-Thus $\mathcal{G}$ turns out to be an acyclic graph.
-Second, to show $\mathcal{G}$ is a
-complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
-Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
-For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
-added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
-there has to be a processor that would add it to $\mathcal{G}$.
-
-(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
-of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
-Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:a1}}
-
-\textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
-
-\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
-is actually the depth of the constructed materialization graph.
-We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
-By performing an induction on the number of iterations of \ref{alg1:updateG},
-one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
-where $n$=\texttt{depth}($v'$).
-Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
-We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).
-
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
-a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
-
-($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
-If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
-the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
-should have a smaller depth compared with $\mathcal{G}$.
-In this case, this conclusion still holds.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:a3}}
-
-\textbf{Lemma~\ref{lemma:a3}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
-
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
-In this case, $\mathcal{G}$ is obviously a materialization graph.
-
-\emph{Inductive case}.
-According to the induction hypothesis, the partial graph constructed after
-the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
-also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
-It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
-and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-In the above two cases, $H$ is a new node. Thus,
-$\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
-the algorithm does nothing.
-Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.
-
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
-We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
-According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:dllite}}
-
-\textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
-
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
-$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
-for any materialization graph.
-
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
-We are left to prove that $H$ has an SWD path as well
-in all materialization graphs of $\mathcal{O}$.
-
-If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
-applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
-\item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
-We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
-
-\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
-according to the induction hypothesis.
-It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
-in some materialization graph.
-\end{enumerate}
-
-Since node $A(x)$ can only be derived in either Case~1.1
-or Case~1.2, we have that
-node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
-
-It is similar to prove the case where $H$ is in the form of $R(x,y)$.
-Since node $R(x,y)$ may be derived by
-applying (R1) and (R2), we discuss these two cases.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
-\item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
-Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
-in some materialization graph.
-
-\item $S\sqsubseteq R^-$. This case is similar to
-the above case.
-\end{enumerate}
-
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dl-lite}}
-
-\textbf{Theorem~\ref{theorem:dl-lite}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
-since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dhl}}
-
-\textbf{Theorem~\ref{theorem:dhl}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
-ontology can be separated into two stages: in the first stage (Stage~1), all the rules
-of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
-also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
-are then applied in Stage~2.
-It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
-for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
-such a poly-logarithmical function $\psi$ exists.
-
-In Stage~1, the rules of the forms (R1-R3)
-are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
-handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
-
-\begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
-\end{definition}
-
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
-We then have the following lemma.
-
-\begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
-\end{lemma}
-
-Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
-In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1) and (R2);
-(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
-where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
-generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
-
-We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
-    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.
-
-\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
-    role.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:dhlplus}}
-
-\textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
-That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
-all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
-
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
-that is defined as follows:
-
-\begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
-\end{definition}
-
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
-We then give the following definition for $\delta_R$.
-
-\begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
-\end{definition}
-
-\begin{lemma}\label{lemma:tiplus}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
-$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
-\end{lemma}
-
-The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
-Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
-The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1), (R2) and (R4);
-(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
-one can further perform (R1), (R2) and (R4) iteratively based on all
-transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
-All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-We now prove Lemma~\ref{lemma:tiplus}.
-We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
-
-    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
-    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.
-
-    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.
-
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
-    \end{enumerate}
-
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
-    holds.\label{dhlplus:NTIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Further, $R$ is a transitive role. According to the simple-role restriction,
-    both of $R_1$ and $R_2$ are simple roles.
-    This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
-    This case is similar to \ref{dhlplus:NTIcaseR4}.
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
-        Then, $R'$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
-        $R'^-$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
-    at least one of $R_1$ and $R_2$ is a simple role.
-    W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
-    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
-    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
-    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:aprc}}
-
-\textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
-this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
-(see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
-
-To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
-We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
-$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
-$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:aprcpt}}
-
-\textbf{Theorem~\ref{theorem:aprcpt}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that $\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
-\emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
-\emph{the simple concept materialization} (Stage~SCM) and
-\emph{the non-simple concept materialization} (Stage~NSCM).
-Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
-where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
-role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.
-
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
-such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
-Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
-there exists a poly-logarithmically bounded function $\psi'$
-such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.
-
-We first consider Stage~SCM.
-Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
-and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
-can be viewed as an EDB predicate. This further means that,
-for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
-Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
-The atom $A(a)$ can be derived through either of the following rule instantiations:
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
-
-\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
-    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
-    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-\end{enumerate}
-
-We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
-According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
-In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
-We also use an induction to show that
-such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
-here.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
-    If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
-\end{enumerate}
-
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
-
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
-We use an induction to show that
-such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
-as follows.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
-    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
-\end{enumerate}
-
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
-is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
-$R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
-of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
-can also be computed by $\mathsf{A}_{prc}^\psi$ for some
-poly-logarithmically bounded function $\psi$.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
-    One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
-    all nodes in each level of $t$ in one iteration from the bottom. Thus,
-    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
-\end{enumerate}
+\input{appendix}
 

### 2018-01-29 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
splitting the main file for better organization

--- 2017-09-13 parallel-tractability-J-v8/parallel-tractability-J.tex
@@
-%\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
- \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-\usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-\usepackage{amsmath}
-
-\usepackage{CJK}
-\usepackage{color}
-
-\usepackage{enumitem}
-\usepackage{rotating}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-%\journal{Nuclear Physics B}
-
-\hyphenation{data-log}
-
-\begin{document}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Parallel Tractability of Ontology\\
-Materialization: Technique and Practice}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author{}
-
-\address{}
-
-\begin{abstract}
-Materialization is an important reasoning service for applications built
-on the ontology languages, such as OWL. With a
-rapid growth of semantic data, it is challenging to perform
-materialization on large-scale ontologies efficiently.
-Current work proposes parallel algorithms and employs computing
-platforms of high-performance to make materialization sufficiently efficient and scalable in practice.
-However, there do exist ontologies, for which
-materialization cannot always be improved by parallelism (we use experiments to show it in Section~\ref{sec:evaluation}).
-On the other hand, some well-known large-scale ontologies, such as YAGO, have been shown to have
-good performance for parallel reasoning, but they are expressed in ontology languages
-that are not parallelly tractable in theory, i.e., the efficiency of reasoning may not be improved
-on a parallel implementation.
-This motivates us to study the problem of \emph{parallel tractability} of ontology
-materialization from a theoretical perspective.
-That is, we aim to identify the ontologies for which materialization is
-parallelly tractable, i.e., in \texttt{NC} complexity.
-The results of the parallel tractability can be further used to optimize
-materialization algorithms and to guide ontology engineers in creating parallelly tractable ontologies.
-
-In this work, we focus on datalog rewritable ontology languages.
-We propose some algorithms, called \texttt{NC} algorithms, to identify several classes of datalog rewritable
-ontologies (called \emph{parallelly tractable classes})
-such that materialization over them is parallelly tractable.
-We then investigate the parallel tractability of materialization over
-two datalog rewritable ontology languages DL-Lite and DHL (\emph{Description Horn Logic}).
-We show that materialization over any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ is parallelly tractable.
-For DHL, there exist ontologies where materialization can hardly be parallelized.
-We propose to restrict the usage of DHL such that the restricted ontologies are parallelly tractable.
-We further extend the results to an extension of DHL that also allows \emph{complex role inclusion axioms}.
-To verify the practical usability of the above results, we analyze real-world datasets and show
-that many ontologies expressed in DHL or its extension belong to
-the parallelly tractable classes. Based on the results of parallel tractability,
-we further implement an optimized parallel algorithm
-and compare it to the state-of-the-art reasoner RDFox. The experimental results show that the
-optimization used in our implementation results in a better
-performance on parallelly tractable ontologies compared with RDFox.
-\end{abstract}
-
-\begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-\section{Introduction}
-\label{sec:introduction}
-
-The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
-are being generated at an increasing pace by sensor networks, government authorities and social
-media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.
-
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms 
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
-MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
-
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
-While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
-for which parallel tractability can be guaranteed theoretically.
-
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
-This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
-we also discuss how to optimize and implement them.
-
-In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
-We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
-in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
-Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
-We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
-
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
-In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
-
-\section{Background Knowledge}
-\label{sec:background}
-
-In this section, we introduce some basic notions that are needed to introduce our approach.
-
-\subsection{Datalog}
-
-We discuss the main issues in this paper using standard datalog notions.
-In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
-constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
-represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
-of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
-the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
-A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
-For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
-with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
-if each defined $A\theta$ is a ground atom.
-A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
-the terms in this rule with respect to a finite set of constants occurring in $P$.
-Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
-The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
-while the predicates that may occur as head atoms are called \emph{IDB predicates}.
-
-\subsection{DHL and DL-Lite}
-
-In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
-to denote three disjoint countably
-infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
-The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
-where $R^-$ is the \emph{inverse role} of $R$.
-For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
-
-DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
-intersection of description logic (DL) and datalog in terms of expressivity.
-We define a DHL ontology $\mathcal{O}$ as a triple:
-$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
-$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
-$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
-$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
-In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
-are roles in $\textbf{R}$.
-For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
-equivalent form $\exists R^-.A\sqsubseteq B$.
-
-DHL is related with other ontology languages.
-First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
-Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
-Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
-However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
-materialization.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
-\hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
-\hline
-\hline
-(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
-(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
-(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
-(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\
-
-\hline
-(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
-(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
-(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
-(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\
-
-\hline
-(A1)& $A(a)$& $A(a)$\\
-(A2)& $R(a,b)$& $R(a,b)$\\
-\hline
-\end{tabular}
-\label{tab:dhl}
-\end{center}
-\end{table}
-
-In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
-In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
-that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
-RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
-axioms of the forms (R1-R4). Note that (R3) is actually a special
-case of (R4).
-
-DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
-and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
-(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
-where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
-an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
-which allows involving RBoxes that contain axioms of the forms (R1-R2).
-If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
-in the following paragraphs}.
-
-\subsection{Ontology Materialization via Datalog Programs}
-
-An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
-(see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
-
-In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
-$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
-Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
-between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
-usage of highly expressive ontology languages \cite{HorrocksS04}.
-Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
-occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.
-
-Based on the above representations, ontology materialization
-corresponds to the evaluation of datalog programs.
-Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
-where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
- $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
-The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
-and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
-$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
-We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
-to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
-
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
-Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
-where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
-as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
-In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
-are implemented on shared-memory platforms, we
-study all the issues in this work by assuming that the running machines are in
-shared-memory configurations.
-
-\section{Parallel Tractability of Datalog Programs}
-\label{sec:ptclass}
-
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
-if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
-
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
-
-\begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
-\end{definition}
-
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
-for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
-which is the class of all datalog programs that can be handled by $\mathsf{A}$.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
-In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
-and identify the target \texttt{PTD} class.
-
-\subsection{Materialization Graph}
-
-In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
-
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
-\end{enumerate}
-\end{definition}
-
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
-We next give an example of a materialization graph.\\
-
-\begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
-$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
-the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
-where $\textbf{I}$ contains all the assertions in the ABox
-and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
-and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
-each of the other nodes corresponds to a ground instantiation of some rule.
-For example, the node $A(a_k)$ corresponds to the ground rule instantiation
-`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
-The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
-\label{fig:mg}
-\end{center}
-\end{figure}
-
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
-The set of nodes in a complete materialization graph is actually the result
-of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
-a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
-It should also be noted that there may exist several materialization graphs for a datalog program.
-
-\subsection{A Basic Parallel Algorithm}
-
-In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
-Initially $\mathcal{G}$ is empty. The following three steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
-    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
-Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
-\end{example}
-
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
-materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
-in the appendix.
-
-\begin{lemma}
-\label{lemma:a1}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-\begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}[Proof sketch] This lemma can be proved by performing
-an induction on $T_R^{\omega}(\textbf{I})$.
-The stage (see the related contents in Section~\ref{sec:background}) of $P$
-is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
-its depth equals the depth of the stage.
-\end{proof}
-
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
-We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
-
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
-We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
-
-\begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
-\end{theorem}
-
-\begin{proof}[Proof sketch]
-We can first prove that the number of iterations
-of \ref{alg1:updateG} is actually the depth of the constructed materialization
-graph. This theorem then follows by considering
-Lemma~\ref{lemma:a1}.
-\end{proof}
-
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
-Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
-We discuss this in the next part.
-
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
-
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
-we can identify another \texttt{PTD} class.
-
-We discuss our optimization based on a specific case in Example~\ref{exp:general}.
-We find that, in this kind of case, the construction of a materialization graph can be accelerated.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
-\label{fig:general}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
-Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
-is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
-The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
-In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
-All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
-afterwards.
-\end{example}
-
-In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
-node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
-Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
-$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
-$\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
-due to the single-way derivability condition.
-
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
-can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
-
-We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
-describe the reachability between two nodes. To this extent, we use a
-binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
-e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
-
-\begin{description}[leftmargin=2ex]
-\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
-\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
-\end{enumerate}
-\end{description}
-
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
-The following algorithm applies this optimization strategy.\\
-
-\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
-a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
-being constructed from $P$. The following steps are performed:
-\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
-that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
-    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
-    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
-\end{enumerate}
-
-It is well known that there is an \texttt{NC} algorithm for computing the
-transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
-    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
-\end{enumerate}
-
-It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
-
-\begin{lemma}\label{lemma:a3}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
-\end{lemma}
-
-\begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
-In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
-one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
-in the first iteration of \ref{alg3:updateG}.
-\end{example}
-
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
-
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
-
-\begin{corollary}
-For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{corollary}
-
-\begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
-if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
-\end{proof}
-
 \section{Parallel Tractability of Ontology Materialization in OWL}
@@
 \subsection{Parallelly Tractable Materialization of DHL}
+\label{sec:DHL}
 
 In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
+Unfortunately there exist DHL ontology classes such that Algorithm~$\mathsf{A}_{opt}^\psi$
 does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
+In the following, we first give such a case
 to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
@@
 for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{ex_6}$ by $P_{ex_6}=\langle R, \textbf{I}\rangle$,
 where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
+The materialization graph of $P_{ex_6}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_6}$ (see Figure~\ref{fig:ex3_4}(left)).
 \end{example}
 
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
+One can check that $\mathcal{G}_{ex_6}$ is the unique materialization graph of $P_{ex_6}$.
 Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
+When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_6}$, it can be checked that
 each node of the form $A(a_i)$ (filled with black color,
 and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
+in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_6}$,
+and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_6}$.
+Similar to the datalog program class $\mathbb{P}_{ex_1}$, we can also get a
+datalog program class $\mathbb{P}_{ex_6}$ for the ontology $\mathcal{O}_{ex_6}$
+when $k$ is a variable. Based on the above analysis, Algorithm~$\mathsf{A}_{opt}$ cannot complete the materialization
+for the datalog programs of $\mathbb{P}_{ex_6}$ in a poly-logarithmical
 number of iterations.
@@
 
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
-\label{sec:practicalAlg}
+\subsection{The Parallel Tractability of the Reasoning on RDFS Ontologies}
 
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
+In this part, we discuss about the parallel tractability of the reasoning on RDFS ontologies.
+Although RDFS is not a standard description logic, it can be described by a subset of the DL axioms \cite{GrosofHVD03}.
+The correspondence between the RDFS statements and the DL axioms is listed in Table~\ref{tab:rdfs}.
+We call the RDFS statements in the form of (1-4) \emph{the schema data}
+(which correspond to TBox axioms), the statements in the form of (5) and (6)
+\emph{the instance data} (which correspond to ABox axioms).
 
-\subsection{Reducing Computing Space}
+\begin{table}
+\begin{center}
+\begin{tabular}{lcc}
+\multicolumn{3}{c}{\textbf{Table~\ref{tab:rdfs}: The RDFS statements and the corresponding DL axioms}}\\
+\hline
+&~~~~~~~~~~~~~RDFS statements~~~~~~~~~~~~~&~~~~~~~~~~~~~~Axiom~~~~~~~~~~~~~~\\
+\hline
+\hline
+(1)&$P~~\texttt{rdfs:domain}~~C$& $\top\sqsubseteq\forall P^-.C$\\
 
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
-However, this algorithm can hardly work in practice due to its inherently
-high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
-Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
-when the target datalog program or ontology
-tends to be large in size.
-On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
-we can observe that the rule instantiations used for the construction
-of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
-by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-each of the checked rule instantiations should involve at least one body atom that has been
-added to the constructed materialization graph}.
-Since DHL$(\circ)$
-is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
-as follows.
+(2)&$P~~\texttt{rdfs:range}~~C$& $\top\sqsubseteq\forall P.C$\\
 
-We first consider a datalog rule of the
-form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
-of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
-graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
-the datalog rule `$A(x)\rightarrow B(x)$'
-has only one rule instantiation `$A(a)\rightarrow B(a)$' where
-the variable $x$ is substituted by the constant $a$.
-The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
-`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
-at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
-added to $\mathcal{G}$.
-Note that, for rule instantiations of two body atoms,
-we do not require that both of these two body atoms have been added to
-the constructed materialization graph.
-Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
+(3)&$B~~\texttt{rdfs:subClassOf}~~C$& $B\sqsubseteq C$\\
 
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
+(4)&$R~~\texttt{rdfs:subPropertyOf}~~S$& $R\sqsubseteq S$\\
+\hline
+(5)&$a~~\texttt{rdf:type}~~C$& $C(a)$\\
 
-We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
-and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
-narrowing down the scope of rule instantiations to be checked as well. This can be described
-by the following algorithm.\\
-
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
-and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
-
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
-\end{enumerate}
-
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
-datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
-returns a materialization graph $\mathcal{G}$ of $P$.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
-    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
-DHL$(\circ)$ materialization.
-
-\begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
-all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
-an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
-are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
-\end{example}
-
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
-
-\begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
-and compare it to the reasoning system RDFox.
-
-\subsection{Practical Usability of the Theoretical Results}
-
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
-facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
-
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
-
-\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
-
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
-
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
-
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
-
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
-restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
-
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
-\hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
-\hline
-
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
-\end{tabular}
-\label{tab:info}
-\end{center}
-
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
-
-\textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
-
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
-\end{center}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
+(6)&$a~~R~~b$& $R(a,b)$\\
 \hline
 \end{tabular}
-\label{tab:expresult}
+\label{tab:rdfs}
 \end{center}
+\end{table}
 
-\section{Related Work}
-\label{sec:related}
+The original rule set for the reasoning task of RDFS ontologies is
+given in \cite{RDFSrec04}. By applying the rules in this rule set,
+new schema data would be derived. Thus, the reasoning task of RDFS
+is different from the task of materialization. Further, an RDFS ontology allows
+statements about blank nodes which play as variables. This semantically
+leads to infinite entailments. The author of \cite{Horst05} proves that
+the original rule set is incomplete with the restriction that
+blank nodes cannot occur in predicate positions. By loosening this restriction,
+the rule set turns out to be complete. The computational complexity
+of the reasoning task on RDFS ontologies is shown to be NC-complete \cite{Horst05},
+which is not considered to be prallel-tractable.
 
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
+The situation of path twisting may also happen when conducting reasoning
+on RDFS ontologies. Suppose $R_{subp}$ denotes the RDFS built-in property $\texttt{rdfs:subPropertyOf}$.
+We define the other three properties $R_1$, $R_2$ and $R_3$ by the following axioms:
+$R_1\sqsubseteq R_{subp}, R_2\sqsubseteq R_{subp}$ and $R_{subp}\sqsubseteq R_3$.
+It can be checked that these three axioms entail the complex RIA $R_1\circ R_2\sqsubseteq R_3$ (denoted by $\beta$).
+If axiom $\beta$ does not meet the simple-role restriction (see Section~\ref{sec:DHLo}),
+the situation of path twisting may also happen as shown in Example~\ref{exp:complexRIA}.
 
-There is work that studies parallel reasoning in RDFS and OWL.
-The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
-The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
-Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data).
-The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets.
-On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}.
-In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
+In this work, we study the task of materialization. Similarly, we can only focus on
+the entailments of new instance data for the target RDFS ontologies. To this end,
+we assume that any class of RDFS ontologies has the same schema data (\uppercase\expandafter{\romannumeral1}). In this way,
+the axioms like $\beta$ cannot contribute to the computational complexity, since they
+only apply to schema data. Further, we restrict that blank nodes cannot occur in
+any class of RDFS ontologies (\uppercase\expandafter{\romannumeral2}). This allows an RDFS ontology
+being expressed in DHL (see Table~\ref{tab:rdfs}). Based on the two restrictions (\uppercase\expandafter{\romannumeral1})
+and (\uppercase\expandafter{\romannumeral2}), the reasoning task on RDFS ontologies
+is parallel-tractable (see Section~\ref{sec:DHL}).
 
-Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
-The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
-Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
-This is not the focus in this paper.
-
-Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data.
-The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
-datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
-
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
-
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
-other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
-have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
-explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
-study how to further apply the
-results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
-
-\section*{Reference}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{reference}
-
-\clearpage
-
-\section*{Appendix}
-
-\appendix
-
-\section{Proof of Lemma~\ref{lemma:a1}}
-
-\textbf{Lemma~\ref{lemma:a1}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
-
-\noindent\emph{Proof}:
-(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
-check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
-Thus $\mathcal{G}$ turns out to be an acyclic graph.
-Second, to show $\mathcal{G}$ is a
-complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
-Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
-For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
-added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
-there has to be a processor that would add it to $\mathcal{G}$.
-
-(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
-of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
-Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:a1}}
-
-\textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
-
-\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
-is actually the depth of the constructed materialization graph.
-We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
-By performing an induction on the number of iterations of \ref{alg1:updateG},
-one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
-where $n$=\texttt{depth}($v'$).
-Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
-We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).
-
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
-a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
-
-($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
-If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
-the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
-should have a smaller depth compared with $\mathcal{G}$.
-In this case, this conclusion still holds.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:a3}}
-
-\textbf{Lemma~\ref{lemma:a3}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
-
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
-In this case, $\mathcal{G}$ is obviously a materialization graph.
-
-\emph{Inductive case}.
-According to the induction hypothesis, the partial graph constructed after
-the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
-also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
-It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
-and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-In the above two cases, $H$ is a new node. Thus,
-$\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
-the algorithm does nothing.
-Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.
-
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
-We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
-According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:dllite}}
-
-\textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
-
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
-$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
-for any materialization graph.
-
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
-We are left to prove that $H$ has an SWD path as well
-in all materialization graphs of $\mathcal{O}$.
-
-If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
-applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
-\item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
-We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
-
-\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
-according to the induction hypothesis.
-It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
-in some materialization graph.
-\end{enumerate}
-
-Since node $A(x)$ can only be derived in either Case~1.1
-or Case~1.2, we have that
-node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
-
-It is similar to prove the case where $H$ is in the form of $R(x,y)$.
-Since node $R(x,y)$ may be derived by
-applying (R1) and (R2), we discuss these two cases.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
-\item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
-Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
-in some materialization graph.
-
-\item $S\sqsubseteq R^-$. This case is similar to
-the above case.
-\end{enumerate}
-
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dl-lite}}
-
-\textbf{Theorem~\ref{theorem:dl-lite}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
-since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dhl}}
-
-\textbf{Theorem~\ref{theorem:dhl}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
-ontology can be separated into two stages: in the first stage (Stage~1), all the rules
-of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
-also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
-are then applied in Stage~2.
-It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
-for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
-such a poly-logarithmical function $\psi$ exists.
-
-In Stage~1, the rules of the forms (R1-R3)
-are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
-handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
-
-\begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
-\end{definition}
-
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
-We then have the following lemma.
-
-\begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
-\end{lemma}
-
-Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
-In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1) and (R2);
-(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
-where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
-generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
-
-We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
-    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.
-
-\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
-    role.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:dhlplus}}
-
-\textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
-That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
-all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
-
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
-that is defined as follows:
-
-\begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
-\end{definition}
-
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
-We then give the following definition for $\delta_R$.
-
-\begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
-\end{definition}
-
-\begin{lemma}\label{lemma:tiplus}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
-$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
-\end{lemma}
-
-The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
-Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
-The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1), (R2) and (R4);
-(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
-one can further perform (R1), (R2) and (R4) iteratively based on all
-transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
-All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-We now prove Lemma~\ref{lemma:tiplus}.
-We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
-
-    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
-    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.
-
-    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.
-
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
-    \end{enumerate}
-
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
-    holds.\label{dhlplus:NTIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Further, $R$ is a transitive role. According to the simple-role restriction,
-    both of $R_1$ and $R_2$ are simple roles.
-    This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
-    This case is similar to \ref{dhlplus:NTIcaseR4}.
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
-        Then, $R'$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
-        $R'^-$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
-    at least one of $R_1$ and $R_2$ is a simple role.
-    W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
-    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
-    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
-    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:aprc}}
-
-\textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
-this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
-(see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
-
-To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
-We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
-$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
-$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:aprcpt}}
-
-\textbf{Theorem~\ref{theorem:aprcpt}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that $\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
-\emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
-\emph{the simple concept materialization} (Stage~SCM) and
-\emph{the non-simple concept materialization} (Stage~NSCM).
-Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
-where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
-role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.
-
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
-such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
-Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
-there exists a poly-logarithmically bounded function $\psi'$
-such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.
-
-We first consider Stage~SCM.
-Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
-and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
-can be viewed as an EDB predicate. This further means that,
-for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
-Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
-The atom $A(a)$ can be derived through either of the following rule instantiations:
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
-
-\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
-    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
-    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-\end{enumerate}
-
-We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
-According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
-In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
-We also use an induction to show that
-such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
-here.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
-    If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
-\end{enumerate}
-
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
-
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
-We use an induction to show that
-such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
-as follows.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
-    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
-\end{enumerate}
-
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
-is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
-$R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
-of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
-can also be computed by $\mathsf{A}_{prc}^\psi$ for some
-poly-logarithmically bounded function $\psi$.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
-    One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
-    all nodes in each level of $t$ in one iteration from the bottom. Thus,
-    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
-\end{enumerate}
-
-\end{document}
-\endinput
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-01-29 parallel-tractability-J-v9/relatedWork.tex
splitting the main file for better organization

--- 2017-09-13 parallel-tractability-J-v8/parallel-tractability-J.tex
@@
-%\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
- \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-\usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-\usepackage{amsmath}
-
-\usepackage{CJK}
-\usepackage{color}
-
-\usepackage{enumitem}
-\usepackage{rotating}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-%\journal{Nuclear Physics B}
-
-\hyphenation{data-log}
-
-\begin{document}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Parallel Tractability of Ontology\\
-Materialization: Technique and Practice}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author{}
-
-\address{}
-
-\begin{abstract}
-Materialization is an important reasoning service for applications built
-on the ontology languages, such as OWL. With a
-rapid growth of semantic data, it is challenging to perform
-materialization on large-scale ontologies efficiently.
-Current work proposes parallel algorithms and employs computing
-platforms of high-performance to make materialization sufficiently efficient and scalable in practice.
-However, there do exist ontologies, for which
-materialization cannot always be improved by parallelism (we use experiments to show it in Section~\ref{sec:evaluation}).
-On the other hand, some well-known large-scale ontologies, such as YAGO, have been shown to have
-good performance for parallel reasoning, but they are expressed in ontology languages
-that are not parallelly tractable in theory, i.e., the efficiency of reasoning may not be improved
-on a parallel implementation.
-This motivates us to study the problem of \emph{parallel tractability} of ontology
-materialization from a theoretical perspective.
-That is, we aim to identify the ontologies for which materialization is
-parallelly tractable, i.e., in \texttt{NC} complexity.
-The results of the parallel tractability can be further used to optimize
-materialization algorithms and to guide ontology engineers in creating parallelly tractable ontologies.
-
-In this work, we focus on datalog rewritable ontology languages.
-We propose some algorithms, called \texttt{NC} algorithms, to identify several classes of datalog rewritable
-ontologies (called \emph{parallelly tractable classes})
-such that materialization over them is parallelly tractable.
-We then investigate the parallel tractability of materialization over
-two datalog rewritable ontology languages DL-Lite and DHL (\emph{Description Horn Logic}).
-We show that materialization over any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ is parallelly tractable.
-For DHL, there exist ontologies where materialization can hardly be parallelized.
-We propose to restrict the usage of DHL such that the restricted ontologies are parallelly tractable.
-We further extend the results to an extension of DHL that also allows \emph{complex role inclusion axioms}.
-To verify the practical usability of the above results, we analyze real-world datasets and show
-that many ontologies expressed in DHL or its extension belong to
-the parallelly tractable classes. Based on the results of parallel tractability,
-we further implement an optimized parallel algorithm
-and compare it to the state-of-the-art reasoner RDFox. The experimental results show that the
-optimization used in our implementation results in a better
-performance on parallelly tractable ontologies compared with RDFox.
-\end{abstract}
-
-\begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-\section{Introduction}
-\label{sec:introduction}
-
-The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
-are being generated at an increasing pace by sensor networks, government authorities and social
-media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.
-
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms 
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
-MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
-
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
-While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
-for which parallel tractability can be guaranteed theoretically.
-
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
-This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
-we also discuss how to optimize and implement them.
-
-In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
-We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
-in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
-Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
-We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
-
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
-In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
-
-\section{Background Knowledge}
-\label{sec:background}
-
-In this section, we introduce some basic notions that are needed to introduce our approach.
-
-\subsection{Datalog}
-
-We discuss the main issues in this paper using standard datalog notions.
-In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
-constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
-represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
-of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
-the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
-A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
-For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
-with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
-if each defined $A\theta$ is a ground atom.
-A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
-the terms in this rule with respect to a finite set of constants occurring in $P$.
-Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
-The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
-while the predicates that may occur as head atoms are called \emph{IDB predicates}.
-
-\subsection{DHL and DL-Lite}
-
-In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
-to denote three disjoint countably
-infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
-The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
-where $R^-$ is the \emph{inverse role} of $R$.
-For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
-
-DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
-intersection of description logic (DL) and datalog in terms of expressivity.
-We define a DHL ontology $\mathcal{O}$ as a triple:
-$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
-$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
-$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
-$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
-In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
-are roles in $\textbf{R}$.
-For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
-equivalent form $\exists R^-.A\sqsubseteq B$.
-
-DHL is related with other ontology languages.
-First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
-Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
-Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
-However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
-materialization.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
-\hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
-\hline
-\hline
-(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
-(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
-(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
-(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\
-
-\hline
-(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
-(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
-(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
-(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\
-
-\hline
-(A1)& $A(a)$& $A(a)$\\
-(A2)& $R(a,b)$& $R(a,b)$\\
-\hline
-\end{tabular}
-\label{tab:dhl}
-\end{center}
-\end{table}
-
-In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
-In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
-that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
-RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
-axioms of the forms (R1-R4). Note that (R3) is actually a special
-case of (R4).
-
-DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
-and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
-(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
-where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
-an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
-which allows involving RBoxes that contain axioms of the forms (R1-R2).
-If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
-in the following paragraphs}.
-
-\subsection{Ontology Materialization via Datalog Programs}
-
-An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
-(see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
-
-In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
-$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
-Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
-between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
-usage of highly expressive ontology languages \cite{HorrocksS04}.
-Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
-occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.
-
-Based on the above representations, ontology materialization
-corresponds to the evaluation of datalog programs.
-Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
-where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
- $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
-The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
-and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
-$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
-We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
-to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
-
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
-Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
-where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
-as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
-In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
-are implemented on shared-memory platforms, we
-study all the issues in this work by assuming that the running machines are in
-shared-memory configurations.
-
-\section{Parallel Tractability of Datalog Programs}
-\label{sec:ptclass}
-
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
-datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
-if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
-In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
-
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
-
-\begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
-\end{definition}
-
-According to the above definition, if we find an \texttt{NC} algorithm $\mathsf{A}$
-for datalog materialization, then we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}}$,
-which is the class of all datalog programs that can be handled by $\mathsf{A}$.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
-In the following, we first give a parallel materialization algorithm that works for
-general datalog programs. We then restrict this algorithm to an \texttt{NC} version
-and identify the target \texttt{PTD} class.
-
-\subsection{Materialization Graph}
-
-In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
-
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
-\end{enumerate}
-\end{definition}
-
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
-We next give an example of a materialization graph.\\
-
-\begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
-$\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
-the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
-where $\textbf{I}$ contains all the assertions in the ABox
-and $R$ contains the two rules `$R(x,y),A(y)\rightarrow A(x)$'
-and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
-each of the other nodes corresponds to a ground instantiation of some rule.
-For example, the node $A(a_k)$ corresponds to the ground rule instantiation
-`$R(a_k,b),A(b)\rightarrow A(a_k)$'.
-The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
-\label{fig:mg}
-\end{center}
-\end{figure}
-
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
-The set of nodes in a complete materialization graph is actually the result
-of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
-a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
-It should also be noted that there may exist several materialization graphs for a datalog program.
-
-\subsection{A Basic Parallel Algorithm}
-
-In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
-Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
-Initially $\mathcal{G}$ is empty. The following three steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
-    the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
-Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
-\end{example}
-
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
-materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
-in the appendix.
-
-\begin{lemma}
-\label{lemma:a1}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-\begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-\item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
-\end{enumerate}
-\end{lemma}
-
-\begin{proof}[Proof sketch] This lemma can be proved by performing
-an induction on $T_R^{\omega}(\textbf{I})$.
-The stage (see the related contents in Section~\ref{sec:background}) of $P$
-is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
-its depth equals the depth of the stage.
-\end{proof}
-
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
-We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
-
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
-We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
-
-\begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
-\end{theorem}
-
-\begin{proof}[Proof sketch]
-We can first prove that the number of iterations
-of \ref{alg1:updateG} is actually the depth of the constructed materialization
-graph. This theorem then follows by considering
-Lemma~\ref{lemma:a1}.
-\end{proof}
-
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
-Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
-We discuss this in the next part.
-
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
-
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
-we can identify another \texttt{PTD} class.
-
-We discuss our optimization based on a specific case in Example~\ref{exp:general}.
-We find that, in this kind of case, the construction of a materialization graph can be accelerated.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
-\label{fig:general}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
-Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
-is being constructed for some datalog program $\langle R, \textbf{I}\rangle$.
-The nodes in the dashed box denote the ones that have been added to $\mathcal{G}$.
-In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
-All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
-afterwards.
-\end{example}
-
-In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
-node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
-Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
-$v_0$ is derivable. Thus, all of the nodes $v_i$ ($1\leq i\leq k$) can be added to
-$\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
-due to the single-way derivability condition.
-
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
-can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
-
-We next discuss how to determine the existence of SWD paths. Note that, SWD paths require us to
-describe the reachability between two nodes. To this extent, we use a
-binary transitive relation $\texttt{rch} \subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$,
-e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
-
-\begin{description}[leftmargin=2ex]
-\item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
-\item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
-\end{enumerate}
-\end{description}
-
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
-The following algorithm applies this optimization strategy.\\
-
-\noindent\texttt{Algorithm~$\mathsf{OPT}$}. The algorithm requires two inputs:
-a datalog program $P=\langle R, \textbf{I}\rangle$ and a (partial) materialization graph $\mathcal{G}$ that is
-being constructed from $P$. The following steps are performed:
-\begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
-that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
-    in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
-    to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
-\end{enumerate}
-
-It is well known that there is an \texttt{NC} algorithm for computing the
-transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg3:updateG}), terminate,
-    otherwise iterate \ref{alg3:updateG}. \label{alg3:halt}\hfill$\Box$
-\end{enumerate}
-
-It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
-
-\begin{lemma}\label{lemma:a3}
-Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
-\end{lemma}
-
-\begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
-In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
-one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
-in the first iteration of \ref{alg3:updateG}.
-\end{example}
-
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
-
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
-
-\begin{corollary}
-For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{corollary}
-
-\begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
-if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
-\end{proof}
-
-\section{Parallel Tractability of Ontology Materialization in OWL}
-\label{sec:ptonto}
-
-In this section, we study the issue of parallel tractability
-for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
-there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
-work by studying specific cases.
-Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
-of materialization.
-
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
-
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
-DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
-there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
-In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
-the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
-
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
-we use the following example.
-
-\begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
-where its TBox and RBox contain the following axioms:
-$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
-its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
-where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
-as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
-\label{fig:ex2}
-\end{center}
-\end{figure}
-
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
-(\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
-$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
-for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
-since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
-$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
-(\uppercase\expandafter{\romannumeral3})
-The two nodes $\bot(a)$ and $\bot(b)$
-have no SWD path in the first iteration of \ref{alg3:updateG}.
-They are left to be processed in the second iteration.
-(\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
-after two iterations (\ref{alg3:halt}).
-
-From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
-
-\begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
-\end{lemma}
-
-The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
-have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
-of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
-an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
-more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
-
-\begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL}
-
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
-Based on the analysis of this case, we propose to restrict
-the usage of DHL in order to achieve parallel tractability
-of materialization.
-
-We find that, an unlimited usage of axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
-\label{fig:ex3_4}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
-where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
-\end{example}
-
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
-each node of the form $A(a_i)$ (filled with black color,
-and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
-number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
-
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
-we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
-to avoid `path twisting'. An intuitive idea is to
-ensure that \emph{there is only one path between each two atoms of the form $A(x)$
-generated from the rules corresponding to (T1)}.
-We explain it by using the following example where the ontology is modified from
-that in Example~\ref{exp:dhl}.
-
-\begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
-`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
-\end{example}
-
-In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
-of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
-since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
-node has an SWD path).
-Motivated by this example, we consider restricting the usage of
-the axioms $B_1\sqcap B_2\sqsubseteq A$
-such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
-for some $y$.
-To this end, we first define \emph{simple concepts} as follows:
-
-\begin{definition}
-Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
-of some axiom; or (2) $A$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
-\end{enumerate}
-\end{definition}
-
-Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
-is generated from the rules corresponding to (T1).
-
-\begin{example}
-In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
-non-simple concepts.
-In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
-the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
-\end{example}
-
-We define the following class of DHL ontologies based on the above restriction and
-give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
-
-\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
-each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
-$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
-\end{definition}
-
-\begin{theorem}\label{theorem:dhl}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
-
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
-In addition to the rules in DHL, we also have to consider complex RIAs (R4).
-We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
-\begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
-the RBox $\mathcal{R}$ contains three axioms:
-$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
-the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
-contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
-`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
-\end{example}
-
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
-Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
-
-Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
-we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
-then, at least one of $R_1$ and $R_2$ is
-a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
-We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
-we can get a complex RIA in the form of
-$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
-If one of $R_1$ and $R_2$ is not a simple role, the corresponding
-rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
-and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
-Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
-For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
-role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
-a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
-Further, the situation of path twisting also exists.
-To tackle the above issue,
-we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
-Combined with the simple-concept restriction,
-we define a class of DHL($\circ$) ontologies as follows:
-
-\begin{definition}\label{def:dhlplus}
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
-is rewritten from a DHL($\circ$) ontology and the following
-conditions are satisfied:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
-\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
-\end{enumerate}
-\end{definition}
-
-\begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
-the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
-in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
-\end{example}
-
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
-
-\begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
-\label{sec:practicalAlg}
-
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
-
-\subsection{Reducing Computing Space}
-
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
-However, this algorithm can hardly work in practice due to its inherently
-high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
-Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
-when the target datalog program or ontology
-tends to be large in size.
-On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
-we can observe that the rule instantiations used for the construction
-of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
-by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-each of the checked rule instantiations should involve at least one body atom that has been
-added to the constructed materialization graph}.
-Since DHL$(\circ)$
-is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
-as follows.
-
-We first consider a datalog rule of the
-form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
-of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
-graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
-the datalog rule `$A(x)\rightarrow B(x)$'
-has only one rule instantiation `$A(a)\rightarrow B(a)$' where
-the variable $x$ is substituted by the constant $a$.
-The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
-`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
-at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
-added to $\mathcal{G}$.
-Note that, for rule instantiations of two body atoms,
-we do not require that both of these two body atoms have been added to
-the constructed materialization graph.
-Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
-
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
-
-We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
-and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
-narrowing down the scope of rule instantiations to be checked as well. This can be described
-by the following algorithm.\\
-
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
-and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
-
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
-\end{enumerate}
-
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
-datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
-returns a materialization graph $\mathcal{G}$ of $P$.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
-    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
-DHL$(\circ)$ materialization.
-
-\begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
-all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
-an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
-are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
-\end{example}
-
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
-
-\begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
-and compare it to the reasoning system RDFox.
-
-\subsection{Practical Usability of the Theoretical Results}
-
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
-facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
-
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
-
-\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
-
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
-
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
-
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
-
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
-restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
-
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
-\hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
-\hline
-
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
-\end{tabular}
-\label{tab:info}
-\end{center}
-
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
-
-\textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
-
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
-\end{center}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-\label{tab:expresult}
-\end{center}
-
 \section{Related Work}
@@
 
-\section{Conclusions}
-\label{sec:conclusion}
-
-In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
-datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
-
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
-
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
-other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
-have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
-explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
-study how to further apply the
-results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
-
-\section*{Reference}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{reference}
-
-\clearpage
-
-\section*{Appendix}
-
-\appendix
-
-\section{Proof of Lemma~\ref{lemma:a1}}
-
-\textbf{Lemma~\ref{lemma:a1}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
-
-\noindent\emph{Proof}:
-(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
-check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
-Thus $\mathcal{G}$ turns out to be an acyclic graph.
-Second, to show $\mathcal{G}$ is a
-complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
-Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
-For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
-added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
-there has to be a processor that would add it to $\mathcal{G}$.
-
-(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
-of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
-Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:a1}}
-
-\textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
-
-\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
-is actually the depth of the constructed materialization graph.
-We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
-By performing an induction on the number of iterations of \ref{alg1:updateG},
-one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
-where $n$=\texttt{depth}($v'$).
-Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
-We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).
-
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
-a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
-
-($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
-If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
-the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
-should have a smaller depth compared with $\mathcal{G}$.
-In this case, this conclusion still holds.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:a3}}
-
-\textbf{Lemma~\ref{lemma:a3}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
-
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
-In this case, $\mathcal{G}$ is obviously a materialization graph.
-
-\emph{Inductive case}.
-According to the induction hypothesis, the partial graph constructed after
-the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
-also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
-It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
-and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-In the above two cases, $H$ is a new node. Thus,
-$\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
-the algorithm does nothing.
-Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.
-
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
-We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
-According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:dllite}}
-
-\textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
-
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
-$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
-for any materialization graph.
-
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
-We are left to prove that $H$ has an SWD path as well
-in all materialization graphs of $\mathcal{O}$.
-
-If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
-applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
-\item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
-We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
-
-\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
-according to the induction hypothesis.
-It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
-in some materialization graph.
-\end{enumerate}
-
-Since node $A(x)$ can only be derived in either Case~1.1
-or Case~1.2, we have that
-node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
-
-It is similar to prove the case where $H$ is in the form of $R(x,y)$.
-Since node $R(x,y)$ may be derived by
-applying (R1) and (R2), we discuss these two cases.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
-\item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
-Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
-in some materialization graph.
-
-\item $S\sqsubseteq R^-$. This case is similar to
-the above case.
-\end{enumerate}
-
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dl-lite}}
-
-\textbf{Theorem~\ref{theorem:dl-lite}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
-since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dhl}}
-
-\textbf{Theorem~\ref{theorem:dhl}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
-ontology can be separated into two stages: in the first stage (Stage~1), all the rules
-of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
-also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
-are then applied in Stage~2.
-It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
-for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
-such a poly-logarithmical function $\psi$ exists.
-
-In Stage~1, the rules of the forms (R1-R3)
-are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
-handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
-
-\begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
-\end{definition}
-
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
-We then have the following lemma.
-
-\begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
-\end{lemma}
-
-Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
-In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1) and (R2);
-(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
-where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
-generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
-
-We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
-    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.
-
-\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
-    role.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:dhlplus}}
-
-\textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
-That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
-all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
-
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
-that is defined as follows:
-
-\begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
-\end{definition}
-
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
-We then give the following definition for $\delta_R$.
-
-\begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
-\end{definition}
-
-\begin{lemma}\label{lemma:tiplus}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
-$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
-\end{lemma}
-
-The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
-Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
-The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1), (R2) and (R4);
-(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
-one can further perform (R1), (R2) and (R4) iteratively based on all
-transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
-All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-We now prove Lemma~\ref{lemma:tiplus}.
-We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
-
-    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
-    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.
-
-    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.
-
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
-    \end{enumerate}
-
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
-    holds.\label{dhlplus:NTIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Further, $R$ is a transitive role. According to the simple-role restriction,
-    both of $R_1$ and $R_2$ are simple roles.
-    This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
-    This case is similar to \ref{dhlplus:NTIcaseR4}.
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
-        Then, $R'$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
-        $R'^-$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
-    at least one of $R_1$ and $R_2$ is a simple role.
-    W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
-    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
-    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
-    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:aprc}}
-
-\textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
-this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
-(see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
-
-To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
-We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
-$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
-$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:aprcpt}}
-
-\textbf{Theorem~\ref{theorem:aprcpt}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that $\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
-\emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
-\emph{the simple concept materialization} (Stage~SCM) and
-\emph{the non-simple concept materialization} (Stage~NSCM).
-Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
-where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
-role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.
-
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
-such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
-Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
-there exists a poly-logarithmically bounded function $\psi'$
-such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.
-
-We first consider Stage~SCM.
-Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
-and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
-can be viewed as an EDB predicate. This further means that,
-for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
-Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
-The atom $A(a)$ can be derived through either of the following rule instantiations:
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
-
-\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
-    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
-    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-\end{enumerate}
-
-We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
-According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
-In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
-We also use an induction to show that
-such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
-here.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
-    If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
-\end{enumerate}
-
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
-
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
-We use an induction to show that
-such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
-as follows.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
-    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
-\end{enumerate}
-
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
-is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
-$R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
-of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
-can also be computed by $\mathsf{A}_{prc}^\psi$ for some
-poly-logarithmically bounded function $\psi$.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
-    One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
-    all nodes in each level of $t$ in one iteration from the bottom. Thus,
-    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
-\end{enumerate}
-
-\end{document}
-\endinput
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-01-29 parallel-tractability-J-v9/introduction.tex
proof read and adapted intro

@@
 The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
+is an important standard for ontology languages in the Semantic Web and knowledge-based applications.
+In many of these applications, \emph{materialization} plays an important role, which is the reasoning task of computing all implicit
+\emph{facts} that follow from a given ontology \cite{handbook}.
+Ontology developers and users employ materialization to optimize tasks such as query answering, ontology diagnosis or debugging.
+Since large amounts of semantic data
 are being generated at an increasing pace by sensor networks, government authorities and social
@@
 
-There has been work proposing parallel reasoning algorithms and employing parallel computing platforms
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balancing workload
+For the ontology language RDFS and its extended fragments, approaches for parallel reasoning and for employing parallel computing platforms exist
+ \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balancing workload
 and data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}.
-On the other hand, several work utilizes different kinds of computing platforms to make reasoning tasks more efficient in parallel, such as supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
+reasoning over ontologies that use highly expressive ontology languages \cite{SteigmillerLG14,WuH12}.
+The different approaches utilize different kinds of computing platforms to make reasoning tasks more efficient in parallel, e.g., supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
 MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
 
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, there do exist ontologies for which materialization cannot
-always be improved by parallelism (we use experiments to show this in Section~\ref{sec:evaluation}).
-The current work of parallel ontology reasoning can hardly explain this.
+The effectiveness of parallel reasoning for the above mentioned techniques is empirically verified on different test datasets.
+However, materialization is not tractable in parallel for most of the popular ontology languages with \texttt{PTime}-complete or higher complexity \cite{Raymond95}.
+In particular, this is the case for RDFS and datalog rewritable ontology languages and, therefore, the efficiency of reasoning may not be
+improved using a parallel implementation. A possible reason for the apparent high performance of parallel
+reasoning is that the utilized test datasets do not fall into the worst cases in terms of computational complexity.
+Also some well-known, large-scale ontologies such as YAGO show good performance for parallel
+reasoning \cite{KolovskiWE10}, although they are expressed in ontology languages that are, in theory, not tractable in parallel.
+On the other hand, there are ontologies for which materialization performance does not improve by parallelism and our experiments in Section~\ref{sec:evaluation} confirm this.
+The current theoretical work of parallel ontology reasoning can hardly explain this.
 While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
+we study the problem of parallel tractability in theory and identify properties that make an ontology tractable in parallel.
+These properties can further be used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
 for which parallel tractability can be guaranteed theoretically.
 
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class NC \cite{Raymond95}.
+According to \citet{MotikNPHO14}, many real large-scale ontologies are essentially expressed in ontology languages
+that can be rewritten into datalog rules. We follow this argumentation and focus on such datalog rewritable ontology languages in this paper.
+The main target of this paper is to identify classes of datalog rewritable ontologies such that materialization
+over these ontologies is tractable in parallel, i.e., falls into the parallel complexity class \texttt{NC} \cite{Raymond95}.
 This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the NC class, one can give an \emph{NC algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An NC algorithm is required to terminate in parallel poly-logarithmic time.
+To show that a problem is in \texttt{NC}, one can give an \emph{\texttt{NC} algorithm} that handles this problem
+using parallel computation \cite{Raymond95}.
+An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
 However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not NC algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give NC algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these NC algorithms. To make the proposed NC algorithms practical,
+(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
+since they are designed for general datalog programs and have \texttt{PTime}-complete complexity.
+Thus, we first give \texttt{NC} algorithms that perform materialization
+and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallel tractability classes})
+that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
 we also discuss how to optimize and implement them.
@@
 In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above NC algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
+We first focus on the ontology language DL-Lite \cite{CalvaneseGLLR07} to clarify how to apply the above \texttt{NC} algorithms
+to study parallel tractability of ontology materialization.
+We show that DL-Lite$_{\text{core}}$ and DL-Lite$_\mathcal{R}$ are tractable in parallel.
 We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
@@
 Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed NC algorithms.
+restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
 We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
 Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized NC algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
+proposed restrictions belong to the parallel tractability classes.
+We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization, which we compare to the state-of-the-art reasoner RDFox.
+The experimental results show that the optimizations proposed in this paper result in a better performance on ontologies that are 
+tractable in parallel compared with RDFox.
 
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two NC algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
+The remainder of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
+We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
+We study parallel tractability of materialization in DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto}, respectively.
 In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given NC algorithms.
+we discuss how to optimize and implement the given \texttt{NC} algorithms.
 We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
+Finally, we discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}. Detailed proofs of the theorems and lemmas in this paper are given in the appendix.
 

### 2018-01-29 parallel-tractability-J-v9/parallel-tractability-J.tex
proof read and adapted intro

@@
   parallelization works well, although the reasoning problem for the
-  used ontology language is not in \texttt{NC}, i.e.\ the theoretical
+  used ontology language is not in \texttt{NC}, i.e., the theoretical
   complexity class for \emph{parallel tractability}. This motivates us
@@
 
-\bibliographystyle{elsarticle-num}
+%\bibliographystyle{elsarticle-num}
+\bibliographystyle{elsarticle-num-names}
 \bibliography{reference}

### 2018-01-30 parallel-tractability-J-v9/response.tex
added response for shortened abstract
added response of the RDFS analysis

@@
 
-We made the ontology subscripts correspond to the examples numbers
+We made the ontology subscripts correspond to the example numbers
 for Example~5, Example~6, Example~7 and Example~9.
@@
 
-...
+We used a new section (Section~4.4) in the revision to discuss why RDFS
+does not have parallel tractability of entailment.
 
@@
 
-...
+We gave an example that RDFS entailment may lead to the situation of path twisting in Section~4.4 of the revision.
+We also discussed in what cases RDFS has parallel tractability of entailment.
 
@@
 
-TODO: shorten the abstract.
-
 Indeed, the abstract has been shortened significantly now.

### 2018-01-30 parallel-tractability-J-v9/background.tex
Background proof-read

@@
 in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
+well-known \emph{structural transformation} techniques \cite{KrotzschRH07,Kazakov09}.
 
@@
 In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
+concept names, the \emph{top concept} ($\top$) or the \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
 are roles in $\textbf{R}$.
@@
 First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
+disallowing \emph{nominals}, \emph{number restrictions} and
+right-hand side \emph{existential restrictions} ($A\sqsubseteq\exists R.B$).
 Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
 Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
+and, thus, is not tractable in parallel.
 However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
+expressed in DHL \cite{GrosofHVD03}, which has \texttt{PTime}-complete complexity for
 materialization.
@@
 the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
+naturally transformed into datalog rules.
 In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
 that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
+several axioms of form (R4), we then require that an
 RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
@@
 DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
+query answering over knowledge bases
 and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
+DL-Lite$_{\text{core}}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
+of DL-Lite.
+DL-Lite$_{\text{core}}$ requires that a TBox only contains axioms of the forms (T1) $A\sqsubseteq B$,
 (T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
@@
 an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
+RBoxes are not allowed. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{\text{core}}$,
 which allows involving RBoxes that contain axioms of the forms (R1-R2).
@@
 An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
+expressed in DHL, DHL($\circ$), DL-Lite$_{\text{core}}$ or DL-Lite$_{\mathcal{R}}$ can be transformed into a datalog program
 (see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is called a \emph{free variable} (it is
-not occurring in the head atom $A(x)$).
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
+Note that an axiom of form (T4) $A\sqsubseteq\exists R$ should be
+transformed into a
+first-order logic rule of the form $A(x)\rightarrow \exists y(R(x,y))$, where $y$ is called a \emph{free variable} (it is
+not occurring in the body atom $A(x)$).
+In this work, such a free variable $y$ is eliminated via Skolemisation into a fresh individual $o_{R}^A$
+that corresponds to the concept $A$ and the role $R$. The elimination of free variables
+does not influence the result of materialization \cite{CalvaneseGLLR07}.
 
 In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
+we use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
+where $R$ is the set of rules obtained by transforming the axioms in
+$\mathcal{T}$ and $\mathcal{R}$ and
 $\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
@@
 and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
+notion of \emph{simple role}, which was initially proposed to restrict the
 usage of highly expressive ontology languages \cite{HorrocksS04}.
@@
 Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
+let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R,
+B_i\theta\in\textbf{I}, 1\leq i\leq n \}$,
 where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
@@
 
-\subsection{The NC Complexity}
+\subsection{The Complexity Class \texttt{NC}}
 
-The parallel complexity class NC, known as Nick$'$s
+The parallel complexity class \texttt{NC}, known as Nick's
 Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
 where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the NC class
+Specifically, a decision problem in the \texttt{NC} class
 can be solved in poly-logarithmic time on a PRAM (parallel, random-access machine) with
-a polynomial number of processors. We also say that an NC problem can be solved
+a polynomial number of processors. We also say that an \texttt{NC} problem can be solved
 in \emph{parallel poly-logarithmic time}.
-Although the NC complexity is a theoretical analysis tool,
-it has been shown that many NC problems can be solved efficiently in practice \cite{Raymond95}.
+Although the \texttt{NC} complexity class is a theoretical analysis tool,
+it has been shown that many \texttt{NC} problems can be solved efficiently in practice \cite{Raymond95}.
 
-From the perspective of implementations, the NC problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The NC complexity is originally defined
+From the perspective of implementations, \texttt{NC} problems are also
+highly feasible in parallel for other parallel models like BSP \cite{Valiant90}
+and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity class was originally defined
 as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in NC.
+require in this work that a problem is a decision problem in \texttt{NC}.
 In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})

### 2018-01-30 parallel-tractability-J-v9/response.tex
Section 3 up to optimized algo proof read

@@
 
-We made it clear that the rule set is fixed for a class of Datalog programs.
+We have rephrased the beginning of Section~3 and made it clear that the rule set is fixed for a class of Datalog programs.
 We also revised the similar presentations in Section~2.
@@
 
+...
+
 \begin{quote}
@@
 The paper has so many grammatical errors near its beginning that I gave up
-marking them after the first two pages.  I give a few that I noticed here.\\
-
-"parallely tractable" is very grating.  It would be better to rewrite
-sentences to not use it.
+marking them after the first two pages.  
 \end{quote}
@@
 The paper has been carefully proof-read and hopefully all wording and structural issues are fixed now.
+
+\begin{quote}
+"parallely tractable" is very grating.  It would be better to rewrite
+sentences to not use it.
+\end{quote}
+
+TODO: once done, check whether indeed all occurrences are removed
+
+We have removed all occurrences of ``parallely tractable'' and
+rephrased the sentenced to use ``tractable in parallel'' or ``parallel
+tractability'' instead.
 

### 2018-01-30 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
Section 3 up to optimized algo proof read

--- 2017-09-13 parallel-tractability-J-v8/parallel-tractability-J.tex
@@
-%\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
- \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-\usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-
-\usepackage{amsmath}
-
-\usepackage{CJK}
-\usepackage{color}
-
-\usepackage{enumitem}
-\usepackage{rotating}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-%\journal{Nuclear Physics B}
-
-\hyphenation{data-log}
-
-\begin{document}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Parallel Tractability of Ontology\\
-Materialization: Technique and Practice}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author{}
-
-\address{}
-
-\begin{abstract}
-Materialization is an important reasoning service for applications built
-on the ontology languages, such as OWL. With a
-rapid growth of semantic data, it is challenging to perform
-materialization on large-scale ontologies efficiently.
-Current work proposes parallel algorithms and employs computing
-platforms of high-performance to make materialization sufficiently efficient and scalable in practice.
-However, there do exist ontologies, for which
-materialization cannot always be improved by parallelism (we use experiments to show it in Section~\ref{sec:evaluation}).
-On the other hand, some well-known large-scale ontologies, such as YAGO, have been shown to have
-good performance for parallel reasoning, but they are expressed in ontology languages
-that are not parallelly tractable in theory, i.e., the efficiency of reasoning may not be improved
-on a parallel implementation.
-This motivates us to study the problem of \emph{parallel tractability} of ontology
-materialization from a theoretical perspective.
-That is, we aim to identify the ontologies for which materialization is
-parallelly tractable, i.e., in \texttt{NC} complexity.
-The results of the parallel tractability can be further used to optimize
-materialization algorithms and to guide ontology engineers in creating parallelly tractable ontologies.
-
-In this work, we focus on datalog rewritable ontology languages.
-We propose some algorithms, called \texttt{NC} algorithms, to identify several classes of datalog rewritable
-ontologies (called \emph{parallelly tractable classes})
-such that materialization over them is parallelly tractable.
-We then investigate the parallel tractability of materialization over
-two datalog rewritable ontology languages DL-Lite and DHL (\emph{Description Horn Logic}).
-We show that materialization over any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ is parallelly tractable.
-For DHL, there exist ontologies where materialization can hardly be parallelized.
-We propose to restrict the usage of DHL such that the restricted ontologies are parallelly tractable.
-We further extend the results to an extension of DHL that also allows \emph{complex role inclusion axioms}.
-To verify the practical usability of the above results, we analyze real-world datasets and show
-that many ontologies expressed in DHL or its extension belong to
-the parallelly tractable classes. Based on the results of parallel tractability,
-we further implement an optimized parallel algorithm
-and compare it to the state-of-the-art reasoner RDFox. The experimental results show that the
-optimization used in our implementation results in a better
-performance on parallelly tractable ontologies compared with RDFox.
-\end{abstract}
-
-\begin{keyword}
-ontology \sep materialization \sep datalog \sep parallel tractability \sep \texttt{NC} complexity
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-\section{Introduction}
-\label{sec:introduction}
-
-The Web Ontology Language (OWL)\footnote{The latest version is OWL 2: http://www.w3.org/TR/owl2-overview/}
-is an important standard for ontology language in the Semantic Web and knowledge-based applications.
-In these applications, \emph{materialization}, which is the reasoning task of computing all implicit
-facts that follow from a given ontology \cite{handbook}, plays an important role. By means of it, developers and users
-can optimize query answering, ontology diagnosis and debugging. Since huge amounts of semantic data
-are being generated at an increasing pace by sensor networks, government authorities and social
-media \cite{LehmbergRMB16,MeuselBP15}, it is challenging to conduct materialization on such large-scale ontologies efficiently.
-
-There has been work that proposes parallel reasoning algorithms and employs parallel computing platforms 
-for the ontology language RDFS and its extended
-fragments \cite{MotikNPHO14,PetersSZ15,SubercazeGCL16}. Several optimization strategies, e.g., dictionary encoding, balance workload,
-data partitioning, are further studied to enhance parallel RDFS reasoning. There are also parallel implementations for scalable
-reasoning of highly expressive ontology languages \cite{SteigmillerLG14,WuH12}. On the other hand, in order to make reasoning tasks more efficient
-in parallel, several work utilizes different kinds of high-performance computing platforms, like supercomputers \cite{Hoeksema2011,GoodmanJMAAH11},
-MapReduce \cite{UrbaniKMHB12} and GPU servers \cite{HeinoP12}.
-
-The above work verifies the effectiveness of parallel reasoning based on the evaluations on different test datasets.
-However, for most popular ontology languages, even RDFS and datalog rewritable ontology languages,
-which have \texttt{PTime}-complete or higher complexity of reasoning in the worst case,
-they are not parallelly tractable according to \cite{Raymond95}, i.e., the efficiency of reasoning may not be
-improved on a parallel implementation. A possible reason of the high performance of parallel
-reasoning is that the utilized test datasets do not fall in the worst cases in terms of computational complexity.
-It has also been shown that, some well-known large-scale ontologies, such as YAGO, have good performance for parallel
-reasoning \cite{KolovskiWE10}, but they are expressed in ontology languages that are not parallelly tractable in theory.
-On the other hand, we show in Section~\ref{sec:evaluation} that, there do exist some ontologies, for which materialization cannot
-always be improved by parallelism. The current work of parallel ontology reasoning can hardly explain this.
-While one can try out different parallel implementations to see whether an ontology can be handled by (one of) them efficiently,
-we study the problem of parallel tractability in theory and identify properties that make an ontology parallelly tractable.
-These properties can be further used to optimize parallel algorithms and to guide ontology engineers in creating ontologies
-for which parallel tractability can be guaranteed theoretically.
-
-According to \cite{MotikNPHO14}, many real large-scale ontologies are essentially expressed in the ontology languages
-that can be rewritten into datalog rules. Thus, we focus on such datalog rewritable ontology languages in this paper.
-The main target of this paper is to identify the classes of datalog rewritable ontologies such that materialization
-over these ontologies is parallelly tractable, i.e., in the parallel complexity class $\texttt{NC}$ \cite{Raymond95}.
-This complexity class consists of problems that can be solved efficiently in parallel.
-To show that a problem is in the \texttt{NC} class, one can give an \emph{\texttt{NC} algorithm} that handles this problem
-in parallel computation \cite{Raymond95}.
-An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
-(e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms,
-since they are designed for general datalog programs and has \texttt{PTime}-complete complexity.
-Thus, we first give \texttt{NC} algorithms that perform materialization,
-and then identify the corresponding classes of datalog rewritable ontologies (called \emph{parallelly tractable classes})
-that can be handled by these \texttt{NC} algorithms. To make the proposed \texttt{NC} algorithms practical,
-we also discuss how to optimize and implement them.
-
-In the practical part of this work, we study specific datalog rewritable ontology languages.
-We first focus on the ontology language DL-Lite to clarify how to apply the above \texttt{NC} algorithms
-to study the parallel tractability of ontology materialization.
-We show that DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ are parallelly tractable.
-We then study the ontology language Description Horn Logic (DHL) \cite{GrosofHVD03}, which is the intersection of datalog and OWL
-in terms of expressivity. We give a case of a DHL ontology where materialization can hardly be parallelized.
-Based on the analysis of this case, we propose to restrict the usage of DHL such that materialization over the
-restricted ontologies can be handled by the proposed \texttt{NC} algorithms.
-We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
-proposed restrictions belong to the parallelly tractable classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization.
-We compare our system to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimization proposed in this paper results in a better performance on parallelly
-tractable ontologies compared with RDFox.
-
-The rest of the paper is organized as follows. In Section~\ref{sec:background}, we introduce some basic notions.
-We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study the parallelly tractable materialization of DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto} respectively.
-In Section~\ref{sec:practicalAlg},
-we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
-We then discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}.
-The detailed proofs of the theorems and the lemmas in this paper are given in the appendix.
-
-\section{Background Knowledge}
-\label{sec:background}
-
-In this section, we introduce some basic notions that are needed to introduce our approach.
-
-\subsection{Datalog}
-
-We discuss the main issues in this paper using standard datalog notions.
-In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
-constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
-represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
-of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
-the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
-A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
-For an atom $A$, $A\theta$ is the result of replacing each variable $x$ in $A$
-with $\theta(x)$ if the latter is defined. We call $\theta$ a \emph{ground substitution}
-if each defined $A\theta$ is a ground atom.
-A \emph{ground instantiation} of a rule is obtained by applying a ground substitution on all
-the terms in this rule with respect to a finite set of constants occurring in $P$.
-Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
-The predicates occurring only in the body  of some rules are called \emph{EDB predicates},
-while the predicates that may occur as head atoms are called \emph{IDB predicates}.
-
-\subsection{DHL and DL-Lite}
-
-In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
-to denote three disjoint countably
-infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
-The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
-where $R^-$ is the \emph{inverse role} of $R$.
-For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
-well-known \emph{structure transformation} techniques \cite{KrotzschRH07,Kazakov09}.
-
-DHL (short for \emph{description horn logic}) \cite{GrosofHVD03} is introduced as an
-intersection of description logic (DL) and datalog in terms of expressivity.
-We define a DHL ontology $\mathcal{O}$ as a triple:
-$\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$, where
-$\mathcal{T}$ denotes the TBox containing axioms of the forms (T1-T3);
-$\mathcal{R}$ is the RBox that is a set of axioms of the forms (R1-R3);
-$\mathcal{A}$ is the ABox containing \emph{assertions} of the forms (A1) and (A2).
-In an axiom of either of  the forms (T1-T3 and R1-R3), concepts $A_{(i)}$ and $B$ are either
-concept names, \emph{top concept} ($\top$) or \emph{bottom concept} ($\bot$); $R$ and $S_{(i)}$
-are roles in $\textbf{R}$.
-For an axiom of the form $A\sqsubseteq\forall R.B$ that is also allowed in DHL, we only consider its
-equivalent form $\exists R^-.A\sqsubseteq B$.
-
-DHL is related with other ontology languages.
-First, DHL is essentially a fragment of the description logic Horn-$\mathcal{SHOIQ}$ with
-disallowing \emph{nominal}, \emph{number restriction} and
-right-hand \emph{existential restriction} ($A\sqsubseteq\exists R.B$).
-Second, the expressivity of DHL covers that of RDFS to some extent \cite{GrosofHVD03}.
-Reasoning with RDFS ontologies is \texttt{NP}-complete \cite{Horst05}
-and, thus, is not parallelly tractable.
-However, by applying some simplifications and restrictions, RDFS ontologies can be
-expressed in DHL \cite{GrosofHVD03} that has \texttt{PTime}-complete complexity for
-materialization.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
-\hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
-\hline
-\hline
-(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
-(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
-(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
-(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\
-
-\hline
-(R1)& $S\sqsubseteq R$& $S(x,y)\rightarrow R(x,y)$\\
-(R2)& $S\sqsubseteq R^-$& $S(x,y)\rightarrow R(y,x)$\\
-(R3)& $R\circ R\sqsubseteq R$& $R(x,y), R(y,z)\rightarrow R(x,z)$\\
-(R4)& $R_1\circ R_2\sqsubseteq R$&$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$\\
-
-\hline
-(A1)& $A(a)$& $A(a)$\\
-(A2)& $R(a,b)$& $R(a,b)$\\
-\hline
-\end{tabular}
-\label{tab:dhl}
-\end{center}
-\end{table}
-
-In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
-naturally transformed to datalog rules.
-In this paper, we also consider an extension of DHL (denoted by DHL($\circ$))
-that allows complex RIAs. Since a complex RIA can be transformed to
-several axioms of the form (R4), we then require that an
-RBox $\mathcal{R}$ of a DHL($\circ$) ontology can contain
-axioms of the forms (R1-R4). Note that (R3) is actually a special
-case of (R4).
-
-DL-Lite is a group of ontology languages designed for highly-efficient
-query answering through knowledge
-and underpins the OWL profile OWL QL \cite{CalvaneseGLLR07}.
-DL-Lite$_{core}$ and DL-Lite$_{\mathcal{R}}$ are the two basic fragments
-in DL-Lite.
-DL-Lite$_{core}$ requires that an TBox contains axioms of the forms (T1) $A\sqsubseteq B$,
-(T2) $A_1\sqcap A_2\sqsubseteq B$ where $B\equiv\bot$, (T3) $\exists R.A\sqsubseteq B$
-where $A\equiv\top$ or $B\equiv\bot$, and (T4) $A\sqsubseteq\exists R$,
-an ABox contains \emph{assertions} of the forms (A1) and (A2), and
-RBox is not involved. DL-Lite$_{\mathcal{R}}$ is an extension of DL-Lite$_{core}$,
-which allows involving RBoxes that contain axioms of the forms (R1-R2).
-If not specially specified, \emph{a DL-Lite ontology denotes a DL-Lite$_{\mathcal{R}}$ ontology
-in the following paragraphs}.
-
-\subsection{Ontology Materialization via Datalog Programs}
-
-An ontology
-expressed in DHL, DHL($\circ$), DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ can be transformed to a datalog program
-(see the corresponding rules in the right column of Table~1).
-Note that, for an axiom of the form (T4) $A\sqsubseteq\exists R$, it should be transformed to
-a first-order logic rule `$A(x)\rightarrow \exists y(R(x,y))$' where $y$ is a free variable.
-In this work, such a free variable $y$ is eliminated via Skolemisation into a new individual $o_{R}^A$
-that corresponds to concept $A$ and role $R$. One can check that the elimination of free variables
-does not influence the results of materialization by according to \cite{CalvaneseGLLR07}.
-
-In what follows, for an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-we also use $P=\langle R, \textbf{I}\rangle$ to represent the corresponding datalog program
-where $R$ is the set of rules transformed from the axioms in $\mathcal{T}$ and $\mathcal{R}$,
-$\textbf{I}$ is the set of facts that are directly copied from the assertions in $\mathcal{A}$.
-Further, we use $R_1\sqsubseteq_{*}R_2$ to denote the smallest transitive reflexive relation
-between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
-notion of \emph{simple role}, which is initially proposed to restrict the
-usage of highly expressive ontology languages \cite{HorrocksS04}.
-Specifically, a role $S\in\textbf{R}$ is \emph{simple} if, (1) it has no subrole (including $S$)
-occurring on the right-hand side of axioms of the forms (R3) and (R4); (2) $S^-$ is simple.
-
-Based on the above representations, ontology materialization
-corresponds to the evaluation of datalog programs.
-Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R, B_i\theta\in\textbf{I} (1\leq i\leq n)\}$,
-where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and
- $T_R^{i}(\textbf{I})=T_R^{i-1}(\textbf{I})\cup T_R(T_R^{i-1}(\textbf{I}))$ for each $i>0$.
-The smallest integer $n$ such that $T_R^{n}(\textbf{I})= T_R^{n+1}(\textbf{I})$ is called \emph{stage},
-and \emph{materialization} refers to the computation of $T_R^{n}(\textbf{I})$ with respect to $R$ and \textbf{I}.
-$T_R^{n}(\textbf{I})$ is also called the \emph{fixpoint} and denoted by $T_R^{\omega}(\textbf{I})$.
-We say that an atom $A$ is \emph{derivable} or can be \emph{derived} with respect
-to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}.
-
-\subsection{The $\texttt{NC}$ Complexity}
-
-The parallel complexity class $\texttt{NC}$, known as Nick$'$s
-Class \cite{Raymond95}, is studied by theorists as a parallel complexity class
-where each decision problem can be efficiently solved in parallel.
-Specifically, a decision problem in the $\texttt{NC}$ class
-can be solved in poly-logarithmic time on a parallel machine with a polynomial number of processors.
-We also say that an $\texttt{NC}$ problem can be solved in \emph{parallel poly-logarithmic time}.
-Although the $\texttt{NC}$ complexity is a theoretical analysis tool,
-it has been shown that many $\texttt{NC}$ problems can be solved efficiently in practice \cite{Raymond95}.
-
-From the perspective of implementations, the $\texttt{NC}$ problems are also highly
-parallel feasible for other parallel models like BSP \cite{Valiant90}
-and MapReduce \cite{KarloffSV10}. The \texttt{NC} complexity is originally defined
-as a class of decision problems. Since we study the problem of materialization, we do not
-require in this work that a problem should be a decision problem in $\texttt{NC}$.
-In addition, since many parallel reasoning systems (see related work in Section~\ref{sec:related})
-are implemented on shared-memory platforms, we
-study all the issues in this work by assuming that the running machines are in
-shared-memory configurations.
-
 \section{Parallel Tractability of Datalog Programs}
@@
 Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is parallelly tractable.
-Since we assume that for any datalog program $\langle R, \textbf{I}\rangle$ the rule
-set $R$ is fixed, the materialization problem is thus in data complexity
+materialization is tractable in parallel. We consider data complexity,
+i.e., we consider classes of datalog programs which share a fixed the rule set. 
+The data complexity of the materialization problem in this case is
 $\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}. In other words, the materialization problem on general
+case \cite{Raymond95}.
+% Since we assume that, for any class of datalog programs where the rule
+% set of each datalog program is fixed, the materialization problem is, thus, in data complexity
+% $\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
+% case \cite{Raymond95}.
+In other words, the materialization problem of 
 datalog programs cannot be solved in parallel poly-logarithmic time unless \texttt{P}=\texttt{NC}.
-Thus, we say that \emph{materialization on a class of datalog programs is parallelly tractable
+Thus, we say that \emph{materialization for a class of datalog programs is tractable in parallel
 if there exists an algorithm that handles this class of datalog programs and runs in parallel
-poly-logarithmic time (this algorithm is also called an \texttt{NC} algorithm)}.
+poly-logarithmic time. Such an algorithm is also called an \texttt{NC} algorithm.}
 In this section, we identify such classes of datalog programs by studying different \texttt{NC} algorithms.
 
-\subsection{Parallel Tractable Classes}
-
-We first give the following definition for a parallel tractable class of datalog programs
-where an \texttt{NC} algorithm exists for handling each datalog program in this class.
+\subsection{Parallel Tractability Classes}
+
+We first give the following definition for a class of datalog programs
+that is tractable in parallel, i.e., an \texttt{NC} algorithm exists for handling each datalog program in this class.
 
 \begin{definition}\label{def:ptd}
-\textbf{(Parallelly Tractable Class)} Given a class $\mathcal{D}$ of datalog programs,
-we say that $\mathcal{D}$ is a parallelly tractable datalog program (\texttt{PTD}) class
+\textbf{(Parallel Tractability Class)} Given a class $\mathcal{D}$ of
+datalog programs sharing the same rule set, we say that $\mathcal{D}$
+is a class of datalog program with \emph{p}arallel
+\emph{t}ractability, short a \emph{\texttt{PTD} class}, 
 if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
 in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-parallelly tractable ontology (\texttt{PTO}) class.
+class of ontologies with parallel tractability, short a \texttt{PTO} class.
 \end{definition}
@@
 (e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
-due to their \texttt{PTime}-complete complexity, since they are designed for handling general datalog programs.
-Thus we give our $\texttt{NC}$ algorithms.
+due to their \texttt{PTime}-complete complexity, since they are
+designed for handling general datalog programs. Thus, we proceed to
+devise specific \texttt{NC} algorithms.
 In the following, we first give a parallel materialization algorithm that works for
@@
 In order to give a parallel materialization algorithm,
-we introduce the notion of \emph{materialization graph}.
-It makes the analysis of the given algorithm convenient.
+we introduce the notion of \emph{materialization graphs}, which
+facilitates the analysis of the given algorithm.
 
@@
   \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$;
-\end{enumerate}
-~~$\mathcal{G}$ satisfies the following condition:
+  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
+\end{enumerate}
+For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are two nodes,
+we say that the node $v_1$ is the parent (node) of $v_2$ and the node $v_2$ is the child (node)
+of $v_1$. Further, $\forall H,B_1,...,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $\forall H,B_1,...,B_n\in V$ such that $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$, we have that
-  $B_1,...,B_n\rightarrow H\in P^*$.
+  \item $H$ has a parent node or a child node;
+  \item if $H$ has the in-degree of $0$, then $H$ is an original fact of $P$;
+  \item $B_1,...,B_n\rightarrow H\in P^*$ is satisfied if $e(B_1, H),...,e(B_n, H)\in E$ and
+  $B_1,...,B_n$ are \d{all} the parents of $H$.
 \end{enumerate}
@@
 described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph, the nodes whose in-degree is 0 are the
+Suppose $\mathcal{G}$ is a materialization graph such that the nodes
+with in-degree 0 are the
 original facts in $\textbf{I}$.
@@
 denoted by $\mathcal{G}_{ex_1}$.
-The nodes whose in-degree is 0 are the original facts in $\textbf{I}$;
+The nodes with in-degree 0 are the original facts in $\textbf{I}$;
 each of the other nodes corresponds to a ground instantiation of some rule.
@@
 of materialization.
-Thus, the procedure of materialization can be transformed to the construction of
+Thus, the procedure of materialization can be transformed into the construction of
 a complete materialization graph.
-We pay our attention to complete materialization graphs and do not distinguish it to the
-notion `materialization graph'.
+In the remainder, we only consider complete materialization graphs and
+do not distinguish the term from the
+notion of `materialization graphs'.
 It should also be noted that there may exist several materialization graphs for a datalog program.
@@
 \subsection{A Basic Parallel Algorithm}
+\label{sec:alg-bsc}
 
 In this part, we propose a parallel algorithm
-(denoted by $\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.\\
-
-\noindent\texttt{Algorithm $\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
+(denoted by Algorithm~$\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.
+Our computational model is a PRAM (parallel, random-access machine) that is mostly used to analyze parallel
+complexity. This model allows us to introduce \emph{the parallel assumption}:
+for any datalog program $P=\langle R, \textbf{I}\rangle$,
+any substitution of some atom and any rule instance in $P^*$ can be mapped to a unique memory
+location; further, a one-to-one relation can be established between processors and rule instances.
+Under this assumption, a processor can check the applicability of its corresponding
+rule instance and access the state of an atom occurring in this rule instance in constant time.
+Algorithm~$\mathsf{A}_{bsc}$ is then given as follows.\\
+
+\noindent\texttt{Algorithm~$\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
 the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
-Recall that $P^*$ denotes the ground instantiation of $P$,
-which consists of all possible ground instantiations of rules in $R$.
 Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
-assigned to one processor.\footnote{This might not be practically feasible,
-but we focus on a theoretical analysis here.}
+assigned to one processor.
 Initially $\mathcal{G}$ is empty. The following three steps are then performed:
@@
 \item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
-    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,\footnote{Suppose that each processor
-    can use $O(1)$ time units to access the state of ground atoms, i.e., whether this ground
-    atom has been added to the materialization graph. This can be implemented by maintaining an
-    index of polynomial size.}
+    in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,
     the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
     from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
-\item If no processor can add more nodes and edges to $\mathcal{G}$, terminate, otherwise iterate \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
+\item If no processor can add more nodes and edges to $\mathcal{G}$,
+  terminate, otherwise continue with \ref{alg1:updateG}.\label{alg1:halt}\hfill$\Box$
 \end{enumerate}
@@
 
-We now discuss how Algorithm~$\mathsf{A}_{bsc}$ can be restricted to an \texttt{NC} version.
-(\uppercase\expandafter{\romannumeral1}) Since Algorithm~$\mathsf{A}_{bsc}$ does not introduce
-new constants and each predicate has a constant arity,
-one can check that $|P^*|$ is polynomial in the size of $P$. This also means that
-the number of processors is polynomially bounded.
-(\uppercase\expandafter{\romannumeral2}) The computing time of \ref{alg1:addFacts}
-and \ref{alg1:halt} occupies constant time units because of parallelism.
-(\uppercase\expandafter{\romannumeral3}) The main computation part in Algorithm~$\mathsf{A}_{bsc}$ is the
-iteration of \ref{alg1:updateG}.
-In each iteration of \ref{alg1:updateG}, all processors work independently from each other.
-Thus, in theory, \ref{alg1:updateG} costs one time unit.
-The whole computing time turns out to be bounded by the number of iterations of \ref{alg1:updateG}. (\uppercase\expandafter{\romannumeral4})
+We now discuss the parallel complexity of Algorithm~$\mathsf{A}_{bsc}$.
+Given a class of datalog programs $\mathbb{P}$ where
+a rule set is shared for each datalog program $P=\langle R, \textbf{I}\rangle$ in $\mathbb{P}$.
+Let $e$, $v$ and $r$ represent the maximum arity of any EDB predicate, the maximum number of variables
+in any datalog rule, and the number of datalog rules, respectively.
+We then have that the number of
+constants is at most $|\textbf{I}|e$, and the number of all possible rule instances in $P^*$
+is at most $r(|\textbf{I}|e)^v$.
+Note that $e, v$ and $r$ depend only on the rule set $R$ and not on the fact set $\textbf{I}$.
+Thus, the memory space for storing the atoms and the rule instances is polynomial in the size of $\textbf{I}$.
+This also means that the number of processors is polynomially bounded.
+The computing time of \ref{alg1:addFacts} and \ref{alg1:halt} occupy constant time (denoted by $c_1$) because of parallelism.
+Since Algorithm~$\mathsf{A}_{bsc}$ works under the parallel assumption, one iteration of
+\ref{alg1:updateG} also costs constant time (denoted by $c_2$). Thus,
+the whole computing time of Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+l\cdot c_2$
+where $l$ denotes the number of iterations of \ref{alg1:updateG}.
+
+An \texttt{NC} algorithm should meet two requirements: first,
+it works on a polynomial number of processors; second, it halts in poly-logarithmic time.
+As discussed above, Algorithm~$\mathsf{A}_{bsc}$ meets the first requirement.
+If we want to restrict Algorithm~$\mathsf{A}_{bsc}$ to be an \texttt{NC} algorithm,
+we can make the number of iterations of \ref{alg1:updateG} to be poly-logarithmically bounded.
 We use the symbol $\psi$ to denote a poly-logarithmically bounded function.
-The input of $\psi$ is the size of $P$ and the output is a non-negative integer.
-Based on (\uppercase\expandafter{\romannumeral1}, \uppercase\expandafter{\romannumeral2},
-\uppercase\expandafter{\romannumeral3}, \uppercase\expandafter{\romannumeral4}),
-for any datalog program $P$, if we use $\psi(|P|)$ to
-bound the number of iterations of \ref{alg1:updateG}, then Algorithm~$\mathsf{A}_{bsc}$
-is an \texttt{NC} algorithm, denoted by $\mathsf{A}_{bsc}^{\psi}$ (this symbol also
-means that $\psi$ occurs as a configuration for Algorithm~$\mathsf{A}_{bsc}$).
+For any datalog program, if we restrict the number of iterations of
+\ref{alg1:updateG} to be bounded by $\psi(|\textbf{I}|)$,
+the computing time of Algorithm~$\mathsf{A}_{bsc}$
+is $c_1+\psi(|\textbf{I}|)\cdot c_2$. With this restriction, Algorithm~$\mathsf{A}_{bsc}$ is an \texttt{NC} algorithm denoted by
+$\mathsf{A}_{bsc}^{\psi}$.
 
@@
 
-The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the
-rather simple datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-The graph $\mathcal{G}_{ex_1}$ in Figure~\ref{fig:mg} is the unique materialization graph of $P_{ex_1}$.
-One can also check that \texttt{depth}($\mathcal{G}_{ex_1}$)$=k$.
-This means that the depth of $\mathcal{G}_{ex_1}$ is linearly bounded by $k$.
-On the other hand, the size of $P_{ex_1}$ is a polynomial of the integer $k$.
+Consider Example~\ref{exp:mg} again. Let the integer $k$ be a variable. We can
+get a class of datalog programs, denoted by $\mathbb{P}_{ex_1}$, where the rule set
+is $\{R(x,y),A(y)\rightarrow A(x), S(x,y),R(y,z)\rightarrow R(x,z)\}$ and the fact
+set varies according to $k$. The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{ex_1}$.
+Let $\mathcal{G}_{ex_1}$ be some materialization graph corresponding
+to some datalog program in $\mathbb{P}_{ex_1}$. It can be checked that
+\texttt{depth}($\mathcal{G}_{ex_1}$)$=k$ for some $k$.
+This means that the depths of the materialization graphs are linearly bounded by $k$.
+On the other hand, the sizes of the datalog programs in $\mathbb{P}_{ex_1}$ are polynomial in $k$.
 Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
 enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph of $P_{ex_1}$.
-However there indeed exists an \texttt{NC} algorithm that can handle $P_{ex_1}$.
+graph for each datalog program in $\mathbb{P}_{ex_1}$.
+However, there indeed exists an \texttt{NC} algorithm that can handle $\mathbb{P}_{ex_1}$.
 We discuss this in the next part.
 
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via the Single-Way Derivability}
+\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via Single-Way Derivability}
 
@@
 \includegraphics[width=0.7\textwidth]{fig-general.eps}
-\caption{A partial materialization graph.}
+\caption{A partial materialization graph}
 \label{fig:general}
@@
 \begin{example}\label{exp:general}
-Consider a snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
+Consider the  snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
 Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
@@
 In this snapshot, $v_0$ has been newly added
-to $\mathcal{G}$ in the $l^{th}$ ($l\geq 1$) iteration.
-Each of the nodes $v_i$ ($1\leq i\leq k$) has almost one parent node being not in $\mathcal{G}$,
-while $v'$ has two parent nodes being not in $\mathcal{G}$.
+to $\mathcal{G}$ in the $\ell^{th}$ ($\ell\geq 1$) iteration.
+Each of the nodes $v_i$ ($1\leq i\leq k$) has at most one parent node not in $\mathcal{G}$,
+while $v'$ has two parent nodes not in $\mathcal{G}$.
 All of the nodes $v_i$ ($1\leq i\leq k$) and $v'$ would be added to $\mathcal{G}$
@@
 iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
-We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this stage follows the condition:
-\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ has to be derivable} (this
-is because that, for node $v_i$, node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
-We call this condition \emph{the single-way derivability condition}, which intuitively says that the derivability of a
+We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this
+stage adheres to the condition:
+\emph{if the parent node $v_{i-1}$ is derivable, the child node $v_i$ is derivable} (this
+is because for a node $v_i$, the node $v_{i-1}$ is the only parent node that has not been added to $\mathcal{G}$).
+We call this condition the \emph{single-way derivability condition}, which intuitively says that the derivability of a
 node only depends on one of its parent nodes.
-Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,...,v_k)$ where
-each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) follows the single-way derivability condition;
-we call such a path a \emph{single-way derivable} (SWD) path.
+Observe that node $v_k$ is reachable from node $v_0$ through the path $\tau=(v_0,v_1,\ldots,v_k)$ where
+each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) satisfies the single-way derivability condition.
+We call such a path a \emph{single-way derivable} (SWD) path.
 Further, the starting node $v_0$ in $\tau$ has been added to $\mathcal{G}$; in other words,
@@
 Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
-exits for some node $v$; if there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
+exits for some node $v$. If there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
 due to the single-way derivability condition.
 
-Backing to Example~\ref{exp:general}, since
-there exists an SWD path $(v_0,...,v_i)$ for each node $v_i$ ($1\leq i\leq k$), all of these nodes
+For Example~\ref{exp:general},
+there exists an SWD path $(v_0,\ldots,v_i)$ for each node $v_i$
+($1\leq i\leq k$), hence, all of these nodes
 can be added to $\mathcal{G}$ right after $v_0$. On the other hand,
-node $v'$ has no SWD path, since it has two parent nodes being not in $\mathcal{G}$.
+node $v'$ has no SWD path since it has two parent nodes not in $\mathcal{G}$.
 
@@
 
-\begin{description}[leftmargin=2ex]
+\begin{description}[leftmargin=4ex]
 \item[(\textbf{\dag})] \emph{For each rule instantiation of the form $B_1,..,B_i,..,B_n\rightarrow H$
-where $H$ has been added to $\mathcal{G}$}:
-\begin{enumerate}[leftmargin=2ex]
-\item \emph{if the body atoms $B_1,...,B_n$ have all been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
+such that $H$ has not been added to $\mathcal{G}$}:
+\begin{enumerate}[leftmargin=0ex]
+\item \emph{if the all body atoms $B_1,...,B_n$ have been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
 \item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
@@
 
-We then compute the transitive closure (denoted by $S^*_{\textit{\tiny rch}}$) with respect to
-$S_{\textit{\tiny rch}}$. Based on the transitive closure, we can perform the optimization that,
-for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\textit{\tiny rch}}$
-where $v'$ has been added to $\mathcal{G}$, $v$ has an SWD path and can be added to $\mathcal{G}$.
+We then compute the transitive closure (denoted by $S^*_{\!\textit{\tiny rch}}$) with respect to
+$S_{\!\textit{\tiny rch}}$. Based on the transitive closure, we can
+perform the following optimization: 
+for a node $v$, if there is a relation $\texttt{rch}(v',v)\in S^*_{\!\textit{\tiny rch}}$
+such that $v'$ has been added to $\mathcal{G}$ and $v$ has an SWD
+path, then $v$ can be added to $\mathcal{G}$.
 The following algorithm applies this optimization strategy.\\
@@
 \begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
-\item Compute the transitive closure $S^*_{\textit{\tiny rch}}$ of $S_{\textit{\tiny rch}}$.\label{transClos}
-\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\textit{\tiny rch}}$
+\item Compute a \texttt{rch} relation $S_{\!\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
+\item Compute the transitive closure $S^*_{\!\textit{\tiny rch}}$ of $S_{\!\textit{\tiny rch}}$.\label{transClos}
+\item Update $\mathcal{G}$ as follows: for any \texttt{rch}$(B_i,H)\in S_{\!\textit{\tiny rch}}$
 that corresponds to `$B_1,..,B_i,..$ $,B_n\rightarrow H$'
-    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\textit{\tiny rch}}$ and $B'$ is
+    and there exists a node $B'$ such that \texttt{rch}$(B',B_i)\in S^*_{\!\textit{\tiny rch}}$ and $B'$ is
     in $\mathcal{G}$; if $H$ is not in $\mathcal{G}$ or $H$ is in $\mathcal{G}$ but has no parent pointing
@@
     $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
-    \texttt{rch}$(B_j,H)\in S_{\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
+    \texttt{rch}$(B_j,H)\in S_{\!\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
 \end{enumerate}
@@
 \noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
-returns a materialization graph $\mathcal{G}$ of $P$. Initially $\mathcal{G}$ is empty. The following steps are then performed:
+returns a materialization graph $\mathcal{G}$ of $P$.
+Suppose we have $|P^*|$ processors, and each rule instantiation in $P^*$ is
+assigned to one processor.
+Initially $\mathcal{G}$ is empty. The following steps are then performed:
 \begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
 \item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg3:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
+\item Compute $S_{\!\textit{\tiny rch}}$ by performing \ref{rch} in Algorithm~$\mathsf{OPT}$; use an \texttt{NC}
+    algorithm to compute the transitive closure $S^*_{\!\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
     update $\mathcal{G}$ by performing \ref{updateG}  in Algorithm~$\mathsf{OPT}$.\label{alg3:updateG}
@@
 `$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
+$S_{\!\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
 \cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
-In the transitive closure of $S_{\textit{\tiny rch}}$,
+In the transitive closure of $S_{\!\textit{\tiny rch}}$,
 one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\textit{\tiny rch}}(2\leq i\leq k)$.
+\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\!\textit{\tiny rch}}(2\leq i\leq k)$.
 Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
@@
 
-We obtain an \texttt{NC} variant of $\mathsf{A}_{opt}$ analogously to the process for Algorithm~$\mathsf{A}_{bsc}$.
-It can be checked that an iteration of \ref{alg3:updateG} in $\mathsf{A}_{opt}$ costs poly-logarithmic
-time, since the main part is computing $S^*_{\textit{\tiny rch}}$ by an \texttt{NC} algorithm.
-Thus, if the number of iterations of \ref{alg3:updateG} is upper-bounded by a poly-logarithmical function,
-$\mathsf{A}_{opt}$ is an \texttt{NC} algorithm.
-Analogously to $\mathsf{A}_{bsc}^{\psi}$, we use $\mathsf{A}_{opt}^{\psi}$ to denote an \texttt{NC} variant.
-Specifically, for any datalog program $P$, the number of iterations of \ref{alg3:updateG} in $\mathsf{A}_{opt}$
-is bounded by $\psi(|P|)$, where $\psi$ is a poly-logarithmically bounded function.
+The analysis of the parallel complexity of Algorithm~$\mathsf{A}_{opt}$ is given as follows.
+We use the same symbols $e$, $v$ and $r$ that are used for analyzing the complexity of Algorithm~$\mathsf{A}_{bsc}$
+(see Section~\ref{sec:alg-bsc}). Similarly to the analysis for Algorithm~$\mathsf{A}_{bsc}$, it can be checked that
+the number of processors is polynomial of $|\textbf{I}|$, i.e., $r(|\textbf{I}|e)^v$.
+We now consider the computing time of Algorithm~$\mathsf{A}_{opt}$. It is obvious that \ref{alg3:addFacts}
+\ref{alg3:halt} occupy constant time (denoted by $c_1$). In \ref{alg3:updateG}, the phases of
+computing $S_{\!\textit{\tiny rch}}$ and updating $\mathcal{G}$ also take constant time (denoted by $c_2$)
+under the parallel assumption. Recall that the number of constants is at most $|\textbf{I}|e$ (see Section~\ref{sec:alg-bsc}).
+Let $w$ and $p$ represent the maximum arity of any predicate and the number of predicates respectively.
+We have that the number of all possible substitutions of atoms is at most $p(|\textbf{I}|e)^w$.
+The relation $S_{\!\textit{\tiny rch}}$ consists of pairs of the atoms. Thus, the size of $S_{\!\textit{\tiny rch}}$
+is bounded by $p^2(|\textbf{I}|e)^{2w}$. It can be checked that the computing time of the \texttt{NC} algorithm for computing the transitive
+closure of $S_{\!\textit{\tiny rch}}$ is poly-logarithmical in the size of $\textbf{I}$, more precisely,
+it is upper bounded to $\log^2(p^2(|\textbf{I}|e)^{2w})$ ($=4\log^2(p)+4w^2\log^2(|\textbf{I}|e)+8w\log(p)\log(|\textbf{I}|e)$).
+We now have that the total computing time of Algorithm~$\mathsf{A}_{opt}$ is $c_1+lc_3 + lc_4\log(|\textbf{I}|e) +lc_5\log^2(|\textbf{I}|e)$
+where $c_3=c_2+4\log^2(p)$, $c_4=8w\log(p)$, $c_5=4w^2$ and $l$ denotes the number of iterations of \ref{alg3:updateG}.
+
+Algorithm~$\mathsf{A}_{opt}$ can be restricted to an \texttt{NC} algorithm analogously to the process
+for Algorithm~$\mathsf{A}_{bsc}$. That is the number of iterations of \ref{alg3:updateG}
+is poly-logarithmically bounded, i.e., it is bounded by $\psi(|\textbf{I}|)$
+where $\psi$ is a poly-logarithmical function. In this way, the computing time of
+Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+c_3\psi(|\textbf{I}|)+c_4\psi(|\textbf{I}|)\log(|\textbf{I}|e)+
+c_5\psi(|\textbf{I}|)\log^2(|\textbf{I}|e)$,
+which is still poly-logarithmical in the size of $\textbf{I}$. We denote the
+\texttt{NC} variant of Algorithm~$\mathsf{A}_{opt}$ by $\mathsf{A}_{opt}^{\psi}$.
 
@@
 
-\section{Parallel Tractability of Ontology Materialization in OWL}
-\label{sec:ptonto}
-
-In this section, we study the issue of parallel tractability
-for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
-there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
-work by studying specific cases.
-Further, we propose to restrict the usage of DHL and DHL($\circ$) in order to achieve parallel tractability
-of materialization.
-
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
-
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
-DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
-there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
-In other words, all atoms of the forms $A(a)$ and $R(a,b)$ can be added to
-the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
-
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
-we use the following example.
-
-\begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_2}$
-where its TBox and RBox contain the following axioms:
-$A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
-its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_2}$ by $P_{ex_2}=\langle R, \textbf{I}\rangle$,
-where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
-as the only fact.
-The unique materialization graph of $P_{ex_2}$ is denoted by $\mathcal{G}_{ex_2}$ (see Figure~\ref{fig:ex2}).
-\end{example}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_2}$.}
-\label{fig:ex2}
-\end{center}
-\end{figure}
-
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_2}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_2}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
-(\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
-$A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_2}$ immediately. We take an example of node $B_1(a)$,
-for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_2}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_2}$; if $A(a)$ is already in $\mathcal{G}_{ex_2}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_2}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_2}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_2}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
-since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
-$A(a)$, $S(b,a)$, $B_2(a)$ and $R(b,a)$ are processed similarly.
-(\uppercase\expandafter{\romannumeral3})
-The two nodes $\bot(a)$ and $\bot(b)$
-have no SWD path in the first iteration of \ref{alg3:updateG}.
-They are left to be processed in the second iteration.
-(\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_2}$
-after two iterations (\ref{alg3:halt}).
-
-From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
-
-\begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
-\end{lemma}
-
-The above lemma guarantees that all atoms of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$
-have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
-of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_2}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
-an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
-Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
-more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
-
-\begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL}
-
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontologies such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
-In the following, we first give such an ontology
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
-Based on the analysis of this case, we propose to restrict
-the usage of DHL in order to achieve parallel tractability
-of materialization.
-
-We find that, an unlimited usage of axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$
-may make it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_3}$;
-(right) The materialization graph of $\mathcal{O}_{ex_4}$.}
-\label{fig:ex3_4}
-\end{center}
-\end{figure}
-
-\begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_3}$ where its TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_3}$ by $P_{ex_3}=\langle R, \textbf{I}\rangle$,
-where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_3}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_3}$ (see Figure~\ref{fig:ex3_4}(left)).
-\end{example}
-
-One can check that $\mathcal{G}_{ex_3}$ is the unique materialization graph of $P_{ex_3}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_3}$, it can be checked that
-each node of the form $A(a_i)$ (filled with black color,
-and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_2}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_2}$.
-Thus, Algorithm~$\mathsf{A}_{opt}$ cannot handle $P_{ex_3}$ in a poly-logarithmical
-number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_2}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
-
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
-we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
-to avoid `path twisting'. An intuitive idea is to
-ensure that \emph{there is only one path between each two atoms of the form $A(x)$
-generated from the rules corresponding to (T1)}.
-We explain it by using the following example where the ontology is modified from
-that in Example~\ref{exp:dhl}.
-
-\begin{example}\label{exp:simpleC}
-Consider an ontology where the TBox contains three axioms:
-$B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
-the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_4}$ where the rule set contains:
-`$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_3}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_4}$ (see Figure~\ref{fig:ex3_4}(right)).
-\end{example}
-
-In the above example, for the axiom $B_1\sqcap B_2\sqsubseteq A$, all derived atoms
-of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_4}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_4}$,
-since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_4}$ in the second iteration (because each
-node has an SWD path).
-Motivated by this example, we consider restricting the usage of
-the axioms $B_1\sqcap B_2\sqsubseteq A$
-such that all atoms of the form $B_1(x)$ or $B_2(x)$ cannot be generated by an atom $A(y)$
-for some $y$.
-To this end, we first define \emph{simple concepts} as follows:
-
-\begin{definition}
-Given an ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
-a concept $A\in\textbf{CN}$ is simple, if (1) $A$ does not occur on the right-hand side
-of some axiom; or (2) $A$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item for each $\exists R.B\sqsubseteq A\in\mathcal{T}$, $B$ is simple;
-\item there is no axiom of the form $B_1\sqcap B_2\sqsubseteq A$ in $\mathcal{T}$.
-\end{enumerate}
-\end{definition}
-
-Based on simple concepts, we restrict DHL ontologies such that, in all axioms of the
-form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
-is generated from the rules corresponding to (T1).
-
-\begin{example}
-In the ontology of Example~\ref{exp:dhl}, all of $A$, $B_1$ and $B_2$ are
-non-simple concepts.
-In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
-the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
-\end{example}
-
-We define the following class of DHL ontologies based on the above restriction and
-give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
-
-\begin{definition} Let $\mathcal{D}_{\textit{\text{dhl}}}$ be a class of datalog programs where
-each program is rewritten from a DHL ontology that follows the condition that, for all axioms of the form
-$A_1\sqcap A_2\sqsubseteq B$, at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept}.
-\end{definition}
-
-\begin{theorem}\label{theorem:dhl}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
-
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
-In addition to the rules in DHL, we also have to consider complex RIAs (R4).
-We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
-\begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_5}$ where its TBox is empty;
-the RBox $\mathcal{R}$ contains three axioms:
-$R_1\circ R_2\sqsubseteq R$, $R_3\circ R\sqsubseteq R_1$ and $R\circ R_4\sqsubseteq R_2$;
-the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
-contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
-`$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_5}$.
-\end{example}
-
-One can check that the materialization graph $\mathcal{G}_{ex_5}$ has the same shape as that
-of $\mathcal{G}_{ex_3}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_5}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
-Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
-
-Inspired by what we do for axioms $B_1\sqcap B_2\sqsubseteq A$,
-we require that, for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-if $R$ is not a transitive role and no transitive role $S$ exists such that $R\sqsubseteq_* S$,
-then, at least one of $R_1$ and $R_2$ is
-a \emph{simple role}.\footnote{See the definition of a simple role in Section~\ref{sec:background}.}
-We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
-we can get a complex RIA in the form of
-$R_1\circ R_2\circ R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_3$).
-If one of $R_1$ and $R_2$ is not a simple role, the corresponding
-rule of $\alpha_3$ may also lead to `path twisting'.\footnote{Obviously, applying the rules of $\alpha_1$
-and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
-Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
-For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
-role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
-a complex RIA of the form $R_1\circ R_2\circ R_1\circ R_2\sqsubseteq S$.
-Further, the situation of path twisting also exists.
-To tackle the above issue,
-we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
-Combined with the simple-concept restriction,
-we define a class of DHL($\circ$) ontologies as follows:
-
-\begin{definition}\label{def:dhlplus}
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ is a class of datalog programs where each program
-is rewritten from a DHL($\circ$) ontology and the following
-conditions are satisfied:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
-\item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
-\end{enumerate}
-\end{definition}
-
-\begin{example}
-For the ontology $\mathcal{O}_{ex_4}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_4}$ does not follow
-the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
-in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
-\end{example}
-
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
-
-\begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-\end{theorem}
-
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
-\label{sec:practicalAlg}
-
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an $\texttt{NC}$ version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
-
-\subsection{Reducing Computing Space}
-
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
-However, this algorithm can hardly work in practice due to its inherently
-high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
-Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
-when the target datalog program or ontology
-tends to be large in size.
-On the other hand, from Examples~\ref{exp:mg}, \ref{exp:dllite} and \ref{exp:dhl},
-we can observe that the rule instantiations used for the construction
-of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
-by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-each of the checked rule instantiations should involve at least one body atom that has been
-added to the constructed materialization graph}.
-Since DHL$(\circ)$
-is our focus, we explain how to apply the above strategy in DHL$(\circ)$ materialization
-as follows.
-
-We first consider a datalog rule of the
-form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
-of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
-graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
-the datalog rule `$A(x)\rightarrow B(x)$'
-has only one rule instantiation `$A(a)\rightarrow B(a)$' where
-the variable $x$ is substituted by the constant $a$.
-The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
-`$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
-at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
-the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
-added to $\mathcal{G}$.
-Note that, for rule instantiations of two body atoms,
-we do not require that both of these two body atoms have been added to
-the constructed materialization graph.
-Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
-
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
-
-We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
-and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
-narrowing down the scope of rule instantiations to be checked as well. This can be described
-by the following algorithm.\\
-
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
-and its datalog program $P=\langle R, \textbf{I}\rangle$;
-(2) a (partial) materialization graph $\mathcal{G}$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
-is computed from the following rule instantiations:
-
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item $\forall A(a)\rightarrow B(a)$ where $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in\mathcal{G}$,
-    add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b),A(b)\rightarrow B(a)$ where $\exists R.A\sqsubseteq B\in\mathcal{T}$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall A_1(a),A_2(a)\rightarrow B(a)$ where $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$,
-    if $A_1(a)\in\mathcal{G}$, add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-    if $A_2(a)\in\mathcal{G}$, add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(a,b)$ where $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in\mathcal{G}$,
-    add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R(a,b)\rightarrow S(b,a)$ where $\mathcal{O}\models R\sqsubseteq_* S^-$
-    and $R(a,b)\in\mathcal{G}$, add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$;
-
-\item $\forall R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)$ where $R_1\circ R_2\sqsubseteq R_3$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved),
-    if $R_1(a,b)\in\mathcal{G}$, add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$;
-    If $R_2(b,c)\in\mathcal{G}$, add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$.\hfill$\Box$
-\end{enumerate}
-
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
-
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
-a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
-datalog program $P=\langle R, \textbf{I}\rangle$, this algorithm
-returns a materialization graph $\mathcal{G}$ of $P$.
-Initially $\mathcal{G}$ is empty. The following steps are then performed:
-\begin{enumerate}[leftmargin=8ex,label=(\textit{Step \arabic*}),ref=Step~\arabic*]
-\item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
-    algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
-    update $\mathcal{G}$ by performing \ref{updateG} in Algorithm~$\mathsf{OPT}$.\label{alg4:updateG}
-\item If no node has been added to $\mathcal{G}$ (in \ref{alg4:updateG}), terminate,
-    otherwise iterate \ref{alg4:updateG}. \label{alg4:halt}\hfill$\Box$
-\end{enumerate}
-
-\begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
-DHL$(\circ)$ materialization.
-
-\begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
-all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
-an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
-are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
-\end{example}
-
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an $\texttt{NC}$ version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
-
-\begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.
-\end{theorem}
-
-\section{Evaluation}
-\label{sec:evaluation}
-
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
-and compare it to the reasoning system RDFox.
-
-\subsection{Practical Usability of the Theoretical Results}
-
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
-facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
-
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
-
-\textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
-
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
-
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
-
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
-
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
-restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
-
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
-\hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
-\hline
-
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
-
-\hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
-\end{tabular}
-\label{tab:info}
-\end{center}
-
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
-
-\textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL devided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
-
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
-\end{center}
-\end{figure}
-
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-\label{tab:expresult}
-\end{center}
-
-\section{Related Work}
-\label{sec:related}
-
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-
-There is work that studies parallel reasoning in RDFS and OWL.
-The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
-The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
-Two approaches are explored, i.e., \emph{rule partitioning} (allocating parallel tasks to different processors based on rules) and \emph{data partitioning} (allocating parallel tasks based on data).
-The evaluation results indicate that the efficiency of balance distribution varies with respect to different datasets.
-On the other hand, parallel reasoning is also implemented for OWL fragments, e.g., OWL~RL \cite{KolovskiWE10}, OWL~EL \cite{KazakovKS14}, OWL~QL \cite{LemboSS13}, and even highly expressive languages \cite{SteigmillerLG14,LiebigM07,SchlichtS08,WuH12}.
-In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
-
-Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
-The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
-Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
-This is not the focus in this paper.
-
-Different from the above work, the purpose of this paper is to study the issue of the parallel tractability of materialization from the perspective of data.
-The results given in this paper guarantee the parallel tractability theoretically, regardless of what optimization techniques and platforms as discussed above are used.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
-datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class \texttt{NC}.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
-
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version, and can be implemented for practice.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
-
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
-other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
-have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to
-explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
-study how to further apply the
-results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
-
-\section*{Reference}
-
-\bibliographystyle{elsarticle-num}
-\bibliography{reference}
-
-\clearpage
-
-\section*{Appendix}
-
-\appendix
-
-\section{Proof of Lemma~\ref{lemma:a1}}
-
-\textbf{Lemma~\ref{lemma:a1}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
-(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
-
-\noindent\emph{Proof}:
-(1) First, whenever a processor $p$ adds a new node $v$ to $\mathcal{G}$, it has to first
-check whether $v$ has already been in $\mathcal{G}$ and does nothing if $v$ is in $\mathcal{G}$.
-Thus $\mathcal{G}$ turns out to be an acyclic graph.
-Second, to show $\mathcal{G}$ is a
-complete materialization graph, we perform an induction on $T_R^{\omega}(\textbf{I})$.
-Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
-For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-It can be checked that the atoms in $T_R^{i+1}(\textbf{I})$ have to be
-added to $\mathcal{G}$, since whenever a new node is derived from $T_R^{i}(\textbf{I})$,
-there has to be a processor that would add it to $\mathcal{G}$.
-
-(2) The \emph{stage} (see the related contents in Section~2.3) of $P$ is the lower bound of the depth
-of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
-Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:a1}}
-
-\textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
-
-\noindent\emph{Proof:} We first prove that the number of iterations of \ref{alg1:updateG}
-is actually the depth of the constructed materialization graph.
-We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
-By performing an induction on the number of iterations of \ref{alg1:updateG},
-one can check that an implicit node $v'$ has to be added to $\mathcal{G}$ in the $n^{th}$ iteration
-where $n$=\texttt{depth}($v'$).
-Further, \texttt{depth}($\mathcal{G}$)=$\max$$\{$\texttt{depth}($v_i$)$|v_i$ is in $\mathcal{G}\}$.
-We then have that the number of iterations of \ref{alg1:updateG} is \texttt{depth}($\mathcal{G}$).
-
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
-a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
-
-($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
-If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
-the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
-should have a smaller depth compared with $\mathcal{G}$.
-In this case, this conclusion still holds.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:a3}}
-
-\textbf{Lemma~\ref{lemma:a3}}
-\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
-
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
-In this case, $\mathcal{G}$ is obviously a materialization graph.
-
-\emph{Inductive case}.
-According to the induction hypothesis, the partial graph constructed after
-the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
-also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
-It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
-and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-In the above two cases, $H$ is a new node. Thus,
-$\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
-For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
-the algorithm does nothing.
-Thus, $\mathcal{G}^{i+1}$ is acyclic and satisfies the definition of materialization graph.
-
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
-We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
-According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
-
-\section{Proof of Lemma~\ref{lemma:dllite}}
-
-\textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
-
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
-
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
-$v$ has a special SWD path with $v$ as the unique node. This conclusion holds
-for any materialization graph.
-
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
-We are left to prove that $H$ has an SWD path as well
-in all materialization graphs of $\mathcal{O}$.
-
-If $H$ is in the form of $A(x)$ ($A\neq\bot$), it may be derived by
-applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*]
-\item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
-We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
-
-\item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
-according to the induction hypothesis.
-It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
-in some materialization graph.
-\end{enumerate}
-
-Since node $A(x)$ can only be derived in either Case~1.1
-or Case~1.2, we have that
-node $A(x)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
-
-It is similar to prove the case where $H$ is in the form of $R(x,y)$.
-Since node $R(x,y)$ may be derived by
-applying (R1) and (R2), we discuss these two cases.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*]
-\item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
-Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
-in some materialization graph.
-
-\item $S\sqsubseteq R^-$. This case is similar to
-the above case.
-\end{enumerate}
-
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dl-lite}}
-
-\textbf{Theorem~\ref{theorem:dl-lite}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
-there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
-since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:dhl}}
-
-\textbf{Theorem~\ref{theorem:dhl}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
-ontology can be separated into two stages: in the first stage (Stage~1), all the rules
-of the forms (R1-R3) are exhaustively applied; the consequences of the first stage
-also serve as the facts in the second stage (Stage~2). The rules of the forms (T1-T3)
-are then applied in Stage~2.
-It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
-for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
-such a poly-logarithmical function $\psi$ exists.
-
-In Stage~1, the rules of the forms (R1-R3)
-are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an \texttt{NC} algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
-handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
-
-\begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
-\end{definition}
-
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
-We then have the following lemma.
-
-\begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
-\end{lemma}
-
-Note that, for all roles $R$, $\delta_R$ can be computed by only applying (R1) and (R2).
-In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1) and (R2);
-(2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
-where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
-generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
-
-We are now left to prove Lemma~\ref{lemma:ti}. We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R3)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar
-    to \ref{dhl:NTIcaseR1}.\label{dhl:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:TcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(b,a)\in\delta_{R''}^*$. Since $\delta_{R''}^*$ is
-        the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
-        Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
-        also holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$. By the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta_{R}^*$ holds. Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhl:NTcaseR1}
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
-        Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
-
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
-        then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
-        $R''$ (if $R'$ is a transitive role, then $R''\equiv R'$) such that
-        $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. This case is similar to \ref{dhl:NTcaseR1}.
-
-\item $R(a,b)$ is derived by applying the rule (R3). This is impossible, since $R$ is not a transitive
-    role.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:dhlplus}}
-
-\textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
-
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
-That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
-all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
-
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
-that is defined as follows:
-
-\begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
-\end{definition}
-
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
-We then give the following definition for $\delta_R$.
-
-\begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
-\end{definition}
-
-\begin{lemma}\label{lemma:tiplus}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
-$R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
-\end{lemma}
-
-The set $\delta^*_R$ also denotes the transitive closure of $\delta_R$ where $R$ is a transitive role.
-Note that, for all roles $R$, $\delta_R$ can be computed by applying (R1), (R2) and (R4).
-The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
-it can be added to a materialization graph by only applying (R1), (R2) and (R4);
-(2) for transitive roles $R$, all implicit nodes are in the transitive closure $\delta^*_{R}$,
-which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
-one can further perform (R1), (R2) and (R4) iteratively based on all
-transitive closures $\delta^*_{R'}$ where $R'$ is a transitive role.
-All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
-In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
-
-We now prove Lemma~\ref{lemma:tiplus}.
-We conduct the proof by an induction on
-the derivation of $P=\langle R,\textbf{I}\rangle$. We distinguish inductive cases by different rules (R1-R4)
-that are possibly applied to derive $R(a,b)$.
-
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
-
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~1.\arabic*, ref=Case~1.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
-    role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
-
-    \begin{enumerate}[leftmargin=14ex,label=Case~1.3.\arabic*]
-    \item If there exists a role $R'_i$ such that $R'_i(c_i,c_{i+1})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i$, then we have that $L_i=R'_i$.
-
-    \item If there exists a role $R'_i$ such that $R'_i(c_{i+1},c_{i})\in\mathcal{A}$
-        and $R'_i\sqsubseteq_* R_i^-$, then we have that $L_i=R^{'-}_i$.
-
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
-    \end{enumerate}
-
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
-    holds.\label{dhlplus:NTIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
-\end{enumerate}
-
-We next study the case where $R$ is a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~2.\arabic*, ref=Case~2.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
-        Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_2(c_2,b)\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Further, $R$ is a transitive role. According to the simple-role restriction,
-    both of $R_1$ and $R_2$ are simple roles.
-    This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
-    This case is similar to \ref{dhlplus:NTIcaseR4}.
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
-    $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
-\end{enumerate}
-
-We finally study the case where $R$ is a TI but not a transitive role.
-
-\begin{enumerate}[leftmargin=12ex,label=Case~3.\arabic*, ref=Case~3.\arabic*]
-\item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:TIcaseR1}
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
-
-    \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        According to Definition~\ref{def:language}, $R'\in\mathcal{L}(R)$ holds.
-        Then, $R'$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(b,a)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$.
-
-    \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
-        obviously, $R\in\mathcal{L}(R)$ holds.
-
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
-
-     \item $R'$ is a transitive role.
-        By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Similarly to \ref{dhlplus:TIcaseR1} (Case~1.1.3), we have that
-        $R'^-$ is actually the role sequence that satisfies the condition
-        in this lemma.
-    \end{enumerate}
-
-\item $R(a,b)$ is derived by applying the rule (R4), w.l.o.g.,
-    $R_1(a,c_2),R_1(c_2,b)$ $\rightarrow R(a,b)$,
-    which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
-    at least one of $R_1$ and $R_2$ is a simple role.
-    W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
-    For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
-    On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
-    in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
-
-\item $R(a,b)$ is derived by applying the rule (R3), w.l.o.g., $R(a,c),R(c,b)\rightarrow R(a,b)$,
-    which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is not a transitive role, this case is impossible.\hfill$\Box$
-\end{enumerate}
-
-\section{Proof of Theorem~\ref{theorem:aprc}}
-
-\textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
-a materialization graph $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
-this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
-(2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
-(see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
-
-To prove that (2) holds, we conduct the induction used in the proof for Lemma~\ref{lemma:a1}.
-We aim to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
-with the induction hypothesis that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
-Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
-For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
-$\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
-$\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
-
-\section{Proof of Theorem~\ref{theorem:aprcpt}}
-
-\textbf{Theorem~\ref{theorem:aprcpt}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
-there exists a poly-logarithmically bounded function $\psi$,
-such that $\mathsf{A}_{prc}^{\psi}$ outputs
-a materialization graph of $\mathcal{O}$.}\\
-
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
-\emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
-\emph{the simple concept materialization} (Stage~SCM) and
-\emph{the non-simple concept materialization} (Stage~NSCM).
-Specifically, in Stage~SRM, all atoms of the form $R(a,b)$ are derived
-where $R$ is a simple role, while all atoms of the form $R(a,b)$ for the non-simple
-role $R$ are derived in Stage~NSRM. Stage~SCM and Stage~NSCM can be explained similarly.
-
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
-such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
-Stage~NSRM, Stage~SCM and Stage~NSCM. Based on the previous result, we have that
-there exists a poly-logarithmically bounded function $\psi'$
-such that $\mathsf{A}_{prc}^{\psi'}$ handles the whole materialization.
-
-We first consider Stage~SCM.
-Stage~SCM (the simple concept materialization) is conducted on axioms of two forms $A\sqsubseteq B$
-and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
-can be viewed as an EDB predicate. This further means that,
-for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
-Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
-The atom $A(a)$ can be derived through either of the following rule instantiations:
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
-
-\item[Case~2] $R(a,b),B(b)\rightarrow A(a)$ where $\exists R.B\sqsubseteq A\in\mathcal{T}$.
-    According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
-    By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-\end{enumerate}
-
-We next discuss the non-simple concept materialization (Stage~NSCM), which is conducted on axioms of forms (T1-T3).
-According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
-In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
-We also use an induction to show that
-such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
-here.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~3] $A_1(a),A_2(a)\rightarrow A(a)$ where $A_1\sqcap A_2\sqsubseteq A\in\mathcal{T}$.
-    If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
-\end{enumerate}
-
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
-
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
-We use an induction to show that
-such an SWD path of $R(a,b)$ can be determined by distinguishing different rule instantiations
-as follows.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
-    If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
-    according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
-\end{enumerate}
-
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
-is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
-$R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
-of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
-can also be computed by $\mathsf{A}_{prc}^\psi$ for some
-poly-logarithmically bounded function $\psi$.
-
-\begin{enumerate}[leftmargin=12ex]
-\item[Case~7] $R(a,c),R(c,b)\rightarrow R(a,b)$ where $R$ is a transitive role.
-    One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
-    all nodes in each level of $t$ in one iteration from the bottom. Thus,
-    $R(a,b)$ can be derived in at most $\log(|\delta_R|)$ iterations.\hfill$\Box$
-\end{enumerate}
-
-\end{document}
-\endinput
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-01-31 parallel-tractability-J-v9/fig-dllite.tex
figures in Latex/tikz to look nicer, correction in Sec. 3 datalog part

\documentclass[tikz,border=0mm]{standalone}
\usepackage{tikz}
\usetikzlibrary{positioning}
\tikzset{
    mynodee/.style={minimum height=0mm, minimum width=0mm, inner sep=0mm
  },
  mynode/.style={
    draw, circle, minimum height=1.7mm, minimum  width=1.7mm,line width=0.5mm
  },
  rect/.style={
    draw, rectangle, rounded corners, minimum height=7mm, minimum  width=30mm,line
    width=0.5mm, dotted
  }
}

\begin{document}

\begin{tikzpicture}
 \node[mynode, label=right:$\bot(a)$] (bota) at (0, 0) {};
 \node[mynode, label=right:$\bot(b)$] (botb) at (3, 0) {};
 \node[mynode, label=right:$B_1(a)$] (b1a) at (-1.5, -1.5) {};
 \node[mynode, label=right:$B_2(a)$] (b2a) at (1.5, -1.5) {};
 \node[mynode, label=right:{$R(b, a)$}] (rba) at (4.5, -1.5) {};
 \node[mynode, label=right:$A(a)$] (aa) at (0, -3) {};
 \node[mynode, label=right:{$S(b, a)$}] (sba) at (3, -3) {};
 \node[mynode, label=right:{$Q(a, b)$}] (qab) at (1.5, -4.5) {};

 \draw[-latex,line width=0.5mm] (b1a) -- (bota);
 \draw[-latex,line width=0.5mm] (b2a) -- (bota);
 \draw[-latex,line width=0.5mm] (b2a) -- (botb);
 \draw[-latex,line width=0.5mm] (rba) -- (botb);
 \draw[-latex,line width=0.5mm] (aa) -- (b1a);
 \draw[-latex,line width=0.5mm] (aa) -- (b2a);
 \draw[-latex,line width=0.5mm] (sba) -- (rba);
 \draw[-latex,line width=0.5mm] (qab) -- (aa);
 \draw[-latex,line width=0.5mm] (qab) -- (sba);
 \foreach \i in {0.75, -0.75, -2.25, -3.75} {
   \draw[very thin,gray] (-1.8, \i) -- (6, \i);
  }

\end{tikzpicture}

\end{document}

### 2018-01-31 parallel-tractability-J-v9/fig-general.tex
figures in Latex/tikz to look nicer, correction in Sec. 3 datalog part

\documentclass[tikz,border=0mm]{standalone}
\usepackage{tikz}
\usetikzlibrary{positioning}
\tikzset{
    mynodee/.style={minimum height=0mm, minimum width=0mm, inner sep=0mm
  },
  mynode/.style={
    draw, circle, minimum height=1.7mm, minimum  width=1.7mm,line width=0.5mm
  },
  rect/.style={
    draw, rectangle, rounded corners, minimum height=7mm, minimum  width=30mm,line
    width=0.5mm, dotted
  }
}

\begin{document}

\begin{tikzpicture}
 \node[mynode,label=0:$v'$] (vp) {};
 \node[mynodee, above left=6mm of vp] (alvp) {};
 \node[mynodee, above left=4mm of alvp] (alalvp) {};
 \node[mynode, below left=10mm of vp, label=left:$v_k$] (vk) {};
 \node[mynodee, below left=6mm of vk] (vk-1) {};
 \node[mynodee, below left=3mm of vk-1] (vk-2) {};
 \node[mynodee, below left=3mm of vk-2] (vk-3) {};
 \node[mynode, below left=6mm of vk-3, label=left:$v_1$] (v1) {};
 \node[mynode, fill=black!30,below left=10mm of v1, label=left:$v_0$] (v0) {};
 \node[mynodee, below left=8mm of v0] (v00) {};
 \node[mynodee, below left=6mm of v00] (v000) {};
 \node[mynodee, below right=8mm of v0] (v01) {};
 \node[mynodee, below right=6mm of v01] (v011) {};
 \node[mynode, below right=10mm of vp] (rovp) {};
 \node[mynodee, below=6mm of rovp] (brovp) {};
 \node[mynodee, below=4mm of brovp] (bbrovp) {};
 \node[mynode, below right=10mm of vk] (rovk) {};
 \node[mynodee, below=6mm of rovk] (brovk) {};
 \node[mynodee, below=4mm of brovk] (bbrovk) {};
 \node[mynodee, below left=5mm of rovk] (rovk-1) {};
 \node[mynode, below left=2mm of rovk-1] (rovk-2) {};
 \node[mynodee, below=6mm of rovk-2] (brovk-2) {};
 \node[mynodee, below=4mm of brovk-2] (bbrovk-2) {};
 \node[mynodee, below left=2mm of rovk-2] (rovk-3) {};
 \node[mynode, below left=5mm of rovk-3] (rov1) {};
 \node[mynodee, below=6mm of rov1] (brov1) {};
 \node[mynodee, below=4mm of brov1] (bbrov1) {};
 \node[rect,rotate=43] at (rovk-2) (rect) {};

 \draw[dotted,line width=0.5mm] (v000) -- (v00);
 \draw[-latex,line width=0.5mm] (v00) -- (v0);
 \draw[-latex,line width=0.5mm] (v0) -- (v1);
 \draw[-latex,line width=0.5mm] (v1) -- (vk-3);
 \draw[dotted,line width=0.5mm] (vk-3) -- (vk-2);
 \draw[dotted,line width=0.5mm] (vk-2) -- (vk-1);
 \draw[-latex,line width=0.5mm] (vk-1) -- (vk);
 \draw[-latex,line width=0.5mm] (vk) -- (vp);
 \draw[-latex,line width=0.5mm] (vp) -- (alvp);
 \draw[dotted,line width=0.5mm] (alvp) -- (alalvp);
 \draw[-latex,line width=0.5mm] (rovp) -- (vp);
 \draw[-latex,line width=0.5mm] (brovp) -- (rovp);
 \draw[dotted,line width=0.5mm] (bbrovp) -- (brovp);
 \draw[-latex,line width=0.5mm] (rovk) -- (vk);
 \draw[-latex,line width=0.5mm] (rovk-2) -- (vk-2);
 \draw[-latex,line width=0.5mm] (rov1) -- (v1);
 \draw[-latex,line width=0.5mm] (v01) -- (v0);
 \draw[dotted,line width=0.5mm] (v011) -- (v01);
 \draw[-latex,line width=0.5mm] (brovk) -- (rovk);
 \draw[dotted,line width=0.5mm] (bbrovk) -- (brovk);
 \draw[-latex,line width=0.5mm] (brovk-2) -- (rovk-2);
 \draw[dotted,line width=0.5mm] (bbrovk-2) -- (brovk-2);
 \draw[-latex,line width=0.5mm] (brov1) -- (rov1);
 \draw[dotted,line width=0.5mm] (bbrov1) -- (brov1);
 \draw[dotted,line width=0.5mm,shorten >=1.5mm,shorten <=1.5mm] (rov1) -- (rovk-2);
 \draw[dotted,line width=0.5mm,shorten >=1.5mm,shorten <=1.5mm] (rovk-2) -- (rovk);

 \foreach \i/\l in {{-4/}, {-3/\ell}, {-1.5/}, {-.5/\ell+k}, {.5/\ell+k+1}} {
   \draw[very thin,gray] (-5,\i) -- (2.8,\i) node [below] at (2.2,\i) {$\l$};
  }
  \node[gray] at (2.2,.9) {$\vdots$};
  \node[gray] at (2.2,-2.1) {$\vdots$};
  \node[gray] at (2.2,-2.7) {$\ell+1$};
  \node[gray] at (2.2,-4.3) {$\vdots$};
\end{tikzpicture}

\end{document}

### 2018-01-31 parallel-tractability-J-v9/fig-mg.tex
figures in Latex/tikz to look nicer, correction in Sec. 3 datalog part

\documentclass[tikz,border=0mm]{standalone}
\usepackage{tikz}
\usetikzlibrary{positioning}
\tikzset{
    mynodee/.style={minimum height=0mm, minimum width=0mm, inner sep=0mm
  },
  mynode/.style={
    draw, circle, minimum height=1.7mm, minimum  width=1.7mm,line width=0.5mm
  },
  rect/.style={
    draw, rectangle, rounded corners, minimum height=7mm, minimum  width=30mm,line
    width=0.5mm, dotted
  }
}

\begin{document}

\begin{tikzpicture}
 \node[mynode, label=below:{$S(a_k, a_{k-1})$}] (sakak-1) at (1, 0) {};
 \node[mynodee] (d) at (2.5, 0) {};
 \node[mynode, label=below:{$S(a_2, a_1)$}] (sa2a1) at (4, 0) {};
 \node[mynode, label=below:{$R(a_1, b)$}] (ra1b) at (7, 0) {};
 \node[mynode, label=below:{$A(b)$}] (ab) at (10, 0) {};
 \node[mynode, label=left:{$R(a_2, b)$}] (ra2b) at (5.5, 1.5) {};
 \node[mynode, label=left:{$A(a_1)$}] (aa1) at (8, 1.5) {};
 \node[mynode, label=left:{$R(a_k, b)$}] (rakb) at (3.75, 3) {};
 \node[mynode, label=left:{$A(a_2)$}] (aa2) at (7, 3) {};
 \node[mynode, label=left:{$A(a_k)$}] (aak) at (6, 5.5) {};

 \draw[-latex,line width=0.5mm] (sakak-1) -- (rakb);
 \draw[-latex,line width=0.5mm] (sa2a1) -- (ra2b);
 \draw[-latex,line width=0.5mm] (ra1b) -- (ra2b);
 \draw[-latex,line width=0.5mm] (ab) -- (aa1);
 \draw[-latex,line width=0.5mm] (ab) -- (aa2);
 \draw[-latex,line width=0.5mm] (ab) -- (aak);
 \draw[dotted,line width=0.5mm,shorten >=6mm,shorten <=6mm] (ra2b) -- (rakb);
 \draw[-latex,line width=0.5mm,shorten >=12mm] (ra2b) -- (rakb);
 \draw[-latex,line width=0.5mm,shorten <=12mm] (ra2b) -- (rakb);
 \draw[-latex,line width=0.5mm] (ra1b) -- (aa1);
 \draw[-latex,line width=0.5mm] (ra2b) -- (aa2);
 \draw[dotted,line width=0.5mm,shorten >=8mm,shorten <=5.5mm] (aa2) -- (aak);
 \draw[-latex,line width=0.5mm] (rakb) -- (aak);
 \draw[dotted,line width=0.5mm,shorten >=3mm,shorten <=3mm] (sakak-1) -- (d);
 \draw[dotted,line width=0.5mm,shorten >=3mm,shorten <=3mm] (d) -- (sa2a1);

 \foreach \i/\l in {{0.75/1}, {2.25/2}, {4.75/k}, {6.25/k+1}} {
   \draw[very thin,gray] (0,\i) -- (11,\i) node [below] at (10.5,\i) {$\l$};
  }
  \node[gray] at (10.5,3.5) {$\vdots$};
\end{tikzpicture}

\end{document}

### 2018-01-31 parallel-tractability-J-v9/fig-pathtwist.tex
figures in Latex/tikz to look nicer, correction in Sec. 3 datalog part

\documentclass[tikz,border=0mm]{standalone}
\usepackage{tikz}
\usetikzlibrary{positioning}
\tikzset{
    mynodee/.style={minimum height=0mm, minimum width=0mm, inner sep=0mm
  },
  mynode/.style={
    draw, circle, minimum height=1.7mm, minimum  width=1.7mm,line width=0.5mm
  },
  rect/.style={
    draw, rectangle, rounded corners, minimum height=7mm, minimum  width=30mm,line
    width=0.5mm, dotted
  }
}

\begin{document}

\newcommand{\twisted}{
 \node[mynodee] (l1) at (-3, -0.5) {};
 \node[mynodee] (l2) at (-3, 7.5) {};
 \node[mynode, label=left:{$S(a_2, a_1)$}] (sa2a1) at (0, 0) {};
 \node[mynode, label=right:{$A(a_1)$}] (aa1) at (2, 0) {};
 \node[mynode, label=right:{$R(a_2, a_1)$}] (ra2a1) at (4, 0) {};
 \node[mynode, label=left:{$B_1(a_2)$}] (b1a2) at (1, 1) {};
 \node[mynode, label=right:{$B_2(a_2)$}] (b2a2) at (3, 1) {};
 \node[mynode, fill=black, label=right:{$A(a_2)$}] (aa2) at (2, 2) {};
 \node[mynode, label=left:{$S(a_{k-1}, a_{k-2})$}] (sak-1ak-2) at (0, 3) {};
 \node[mynode, fill=black, label=right:{$A(a_{k-2})$}] (aak-2) at (2, 3) {};
 \node[mynode, label=right:{$R(a_{k-1}, a_{k-2})$}] (rak-1ak-2) at (4, 3) {};
 \node[mynode, label=left:{$B_1(a_{k-1})$}] (b1ak-1) at (1, 4) {};
 \node[mynode, label=right:{$B_2(a_{k-1})$}] (b2ak-1) at (3, 4) {};
 \node[mynode, label=left:{$S(a_k, a_{k-1})$}] (sakak-1) at (0, 5) {};
 \node[mynode, fill=black, label=right:{$A(a_{k-1})$}] (aak-1) at (2, 5) {};
 \node[mynode, label=right:{$R(a_k, a_{k-1})$}] (rakak-1) at (4, 5) {};
 \node[mynode, label=left:{$B_1(a_k)$}] (b1ak) at (1, 6) {};
 \node[mynode, label=right:{$B_2(a_k)$}] (b2ak) at (3, 6) {};
 \node[mynode, fill=black, label=right:{$A(a_k)$}] (aak) at (2, 7) {};

 \draw[-latex,line width=0.5mm] (sa2a1) -- (b1a2);
 \draw[-latex,line width=0.5mm] (aa1) -- (b1a2);
 \draw[-latex,line width=0.5mm] (ra2a1) -- (b2a2);
 \draw[-latex,line width=0.5mm] (b1a2) -- (aa2);
 \draw[-latex,line width=0.5mm] (b2a2) -- (aa2);

 \draw[dotted,line width=0.5mm] (aa2) -- (aak-2);
 \draw[dotted,line width=0.5mm,shorten >=10mm,shorten <=12mm] (sa2a1) -- (sak-1ak-2);
 \draw[dotted,line width=0.5mm,shorten >=10mm,shorten <=12mm] (ra2a1) -- (rak-1ak-2);

 \draw[-latex,line width=0.5mm] (sak-1ak-2) -- (b1ak-1);
 \draw[-latex,line width=0.5mm] (aak-2) -- (b1ak-1);
 \draw[-latex,line width=0.5mm] (rak-1ak-2) -- (b2ak-1);
 \draw[-latex,line width=0.5mm] (b1ak-1) -- (aak-1);
 \draw[-latex,line width=0.5mm] (b2ak-1) -- (aak-1);

 \draw[-latex,line width=0.5mm] (sakak-1) -- (b1ak);
 \draw[-latex,line width=0.5mm] (aak-1) -- (b1ak);
 \draw[-latex,line width=0.5mm] (rakak-1) -- (b2ak);
 \draw[-latex,line width=0.5mm] (b1ak) -- (aak);
 \draw[-latex,line width=0.5mm] (b2ak) -- (aak);
}

\begin{tikzpicture}
 \begin{scope}
 \twisted{}

 \draw[-latex,line width=0.5mm] (aa1) -- (b2a2);
 \draw[-latex,line width=0.5mm] (aak-2) -- (b2ak-1);
 \draw[-latex,line width=0.5mm] (aak-1) -- (b2ak);
 \end{scope}

 \begin{scope}[xshift=10cm]
  \twisted{}
 \draw[-,line width=0.3mm] (l1) -- (l2);
 \end{scope}
\end{tikzpicture}

\end{document}

### 2018-01-31 parallel-tractability-J-v9/background.tex
Section 4 and small adjustments done

@@
 In datalog \cite{database}, a \emph{term} is a variable or a constant. An \emph{atom} $A$
-is defined by $A\equiv p(t_1,...,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
-name, $t_1,...,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
+is defined by $A\equiv p(t_1,\ldots,t_n)$ where $p$ is a \emph{predicate} (or \emph{relational})
+name, $t_1,\ldots,t_n$ are terms, and $n$ is the arity of $p$. If all the terms in an atom $A$ are
 constants, then $A$ is called a \emph{ground atom}.
-A datalog \emph{rule} is of the form: `$B_1,...,B_n\rightarrow H$',\footnote{In datalog rules, a comma
+A datalog \emph{rule} is of the form: `$B_1,\ldots,B_n\rightarrow H$',\footnote{In datalog rules, a comma
 represents a Boolean conjunction `$\wedge$'.} where $H$ is referred to as
-the \emph{head atom} and $B_1,...,B_n$ the \emph{body atoms}. Each variable in the head atom
+the \emph{head atom} and $B_1,\ldots,B_n$ the \emph{body atoms}. Each variable in the head atom
 of a rule must occur in at least one body atom of the same rule. A \emph{fact} is a rule of
@@
 In the initial work of DHL \cite{GrosofHVD03}, \emph{complex role inclusion axioms} (complex RIAs) of
-the form $R_1\circ...\circ R_n\sqsubseteq R$ are not considered, although they can be
+the form $R_1\circ\ldots\circ R_n\sqsubseteq R$ are not considered, although they can be
 naturally transformed into datalog rules.
@@
 not occurring in the body atom $A(x)$).
-In this work, such a free variable $y$ is eliminated via Skolemisation into a fresh individual $o_{R}^A$
+In this work, such a free variable $y$ is eliminated via Skolemization into a fresh individual $o_{R}^A$
 that corresponds to the concept $A$ and the role $R$. The elimination of free variables
@@
 Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,...,B_n\rightarrow H\in R,
+let $T_R(\textbf{I})=\{H\theta|\forall B_1,\ldots,B_n\rightarrow H\in R,
 B_i\theta\in\textbf{I}, 1\leq i\leq n \}$,

### 2018-01-31 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
Section 4 and small adjustments done

@@
 we say that the node $v_1$ is the parent (node) of $v_2$ and the node $v_2$ is the child (node)
-of $v_1$. Further, $\forall H,B_1,...,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
+of $v_1$. Further, $\forall H,B_1,\ldots,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
@@
   \item if $H$ has the in-degree of $0$, then $H$ is an original fact of $P$;
-  \item $B_1,...,B_n\rightarrow H\in P^*$ is satisfied if $e(B_1, H),...,e(B_n, H)\in E$ and
-  $B_1,...,B_n$ are \d{all} the parents of $H$.
+  \item $B_1,\ldots,B_n\rightarrow H\in P^*$ is satisfied if $e(B_1, H),\ldots,e(B_n, H)\in E$ and
+  $B_1,\ldots,B_n$ are \d{all} the parents of $H$.
 \end{enumerate}
@@
 \begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{ex_1}$ where the TBox is
+Consider a DHL($\circ$) ontology $\mathcal{O}_{\text{ex}_1}$ where the TBox is
 $\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
 the ABox is $\{A(b),R(a_1,b),S(a_i,a_{i-1})\}$ for $2\leq i\leq k$ and
-$k$ is an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{ex_1}=\langle R, \textbf{I}\rangle$
+$k$ an integer greater than $2$.
+The corresponding datalog program of this ontology is $P_{\text{ex}_1}=\langle R, \textbf{I}\rangle$
 where $\textbf{I}$ contains all the assertions in the ABox
@@
 and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{ex_1}$,
-denoted by $\mathcal{G}_{ex_1}$.
+The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{\text{ex}_1}$,
+denoted by $\mathcal{G}_{\text{ex}_1}$.
 The nodes with in-degree 0 are the original facts in $\textbf{I}$;
@@
 The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{ex_1}$ is $k$.
+The depth of $\mathcal{G}_{\text{ex}_1}$ is $k$.
 \end{example}
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{fig-mg.eps}
-\caption{An example of a materialization graph.}
+\includegraphics[width=0.7\textwidth]{fig-mg.pdf}
+\caption{An example materialization graph}
 \label{fig:mg}
@@
 In this part, we propose a parallel algorithm
-(denoted by Algorithm~$\mathsf{A}_{bsc}$) that constructs a materialization graph for a given datalog program.
+(denoted by Algorithm~$\mathsf{A}_{\text{bsc}}$) that constructs a materialization graph for a given datalog program.
 Our computational model is a PRAM (parallel, random-access machine) that is mostly used to analyze parallel
@@
 rule instance and access the state of an atom occurring in this rule instance in constant time.
-Algorithm~$\mathsf{A}_{bsc}$ is then given as follows.\\
+Algorithm~$\mathsf{A}_{\text{bsc}}$ is then given as follows.\\
 
-\noindent\texttt{Algorithm~$\mathsf{A}_{bsc}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
+\noindent\texttt{Algorithm~$\mathsf{A}_{\text{bsc}}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$,
 the algorithm returns a materialization graph $\mathcal{G}$ of $P$.
@@
 \item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg1:addFacts}
-\item For each rule instantiation $B_1,...,B_n\rightarrow H$, if the body atoms are all
+\item For each rule instantiation $B_1,\ldots,B_n\rightarrow H$, if the body atoms are all
     in $\mathcal{G}$ while $H$ is not in $\mathcal{G}$,
     the corresponding processor adds $H$ to $\mathcal{G}$ and creates edges pointing
-    from $B_1,...,B_n$ to $H$.\label{alg1:updateG}
+    from $B_1,\ldots,B_n$ to $H$.\label{alg1:updateG}
 \item If no processor can add more nodes and edges to $\mathcal{G}$,
@@
 \begin{example}
-We consider the datalog program $P_{ex_1}$ in Example~\ref{exp:mg} again,
-and perform Algorithm~$\mathsf{A}_{bsc}$ on it.
-Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg1:addFacts}).
+We consider the datalog program $P_{\text{ex}_1}$ in Example~\ref{exp:mg} again,
+and perform Algorithm~$\mathsf{A}_{\text{bsc}}$ on it.
+Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),\ldots,S(a_{k},a_{k-1})$) are added to the
+result $\mathcal{G}_{\text{ex}_1}$ (\ref{alg1:addFacts}).
 Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{ex_1}$ by different processors.
+$\mathcal{G}_{\text{ex}_1}$ by different processors.
 For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{ex_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{ex_1}$.
-Algorithm~$\mathsf{A}_{bsc}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{ex_1}$ (\ref{alg1:halt}).
+Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{\text{ex}_1}$ after it checks that
+$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{\text{ex}_1}$.
+Algorithm~$\mathsf{A}_{\text{bsc}}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{\text{ex}_1}$ (\ref{alg1:halt}).
 \end{example}
 
-Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{bsc}$ and that, for any datalog program $P$,
-Algorithm~$\mathsf{A}_{bsc}$ always constructs a materialization graph with the minimum depth among all the
+Lemma~\ref{lemma:a1} shows the correctness of Algorithm~$\mathsf{A}_{\text{bsc}}$ and that, for any datalog program $P$,
+Algorithm~$\mathsf{A}_{\text{bsc}}$ always constructs a materialization graph with the minimum depth among all the
 materialization graphs of $P$. The detailed proofs of Lemma~\ref{lemma:a1} and other lemmas and theorems can be found
@@
 \begin{enumerate}[leftmargin=4ex]
-\item Algorithm~$\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
+\item Algorithm~$\mathsf{A}_{\text{bsc}}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
 \item $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.
@@
 is the lower-bound of the depth of the materialization graphs. Based on the previous induction,
-one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{bsc}$,
+one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{\text{bsc}}$,
 its depth equals the depth of the stage.
@@
 
-We now discuss the parallel complexity of Algorithm~$\mathsf{A}_{bsc}$.
+We now discuss the parallel complexity of Algorithm~$\mathsf{A}_{\text{bsc}}$.
 Given a class of datalog programs $\mathbb{P}$ where
 a rule set is shared for each datalog program $P=\langle R, \textbf{I}\rangle$ in $\mathbb{P}$.
-Let $e$, $v$ and $r$ represent the maximum arity of any EDB predicate, the maximum number of variables
-in any datalog rule, and the number of datalog rules, respectively.
+Let $e$, $v$ and $r$ represent the maximum arity of any predicate in $\textbf{I}$, the maximum number of variables
+in any datalog rule, and the number of datalog rules respectively.
 We then have that the number of
@@
 The computing time of \ref{alg1:addFacts} and \ref{alg1:halt} occupy constant time (denoted by $c_1$) because of parallelism.
-Since Algorithm~$\mathsf{A}_{bsc}$ works under the parallel assumption, one iteration of
+Since Algorithm~$\mathsf{A}_{\text{bsc}}$ works under the parallel assumption, one iteration of
 \ref{alg1:updateG} also costs constant time (denoted by $c_2$). Thus,
-the whole computing time of Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+l\cdot c_2$
-where $l$ denotes the number of iterations of \ref{alg1:updateG}.
+the whole computing time of Algorithm~$\mathsf{A}_{\text{bsc}}$ turns out to be $c_1+\ell\cdot c_2$
+where $\ell$ denotes the number of iterations of \ref{alg1:updateG}.
 
@@
 it works on a polynomial number of processors; second, it halts in poly-logarithmic time.
-As discussed above, Algorithm~$\mathsf{A}_{bsc}$ meets the first requirement.
-If we want to restrict Algorithm~$\mathsf{A}_{bsc}$ to be an \texttt{NC} algorithm,
+As discussed above, Algorithm~$\mathsf{A}_{\text{bsc}}$ meets the first requirement.
+If we want to restrict Algorithm~$\mathsf{A}_{\text{bsc}}$ to be an \texttt{NC} algorithm,
 we can make the number of iterations of \ref{alg1:updateG} to be poly-logarithmically bounded.
@@
 \ref{alg1:updateG} to be bounded by $\psi(|\textbf{I}|)$,
-the computing time of Algorithm~$\mathsf{A}_{bsc}$
-is $c_1+\psi(|\textbf{I}|)\cdot c_2$. With this restriction, Algorithm~$\mathsf{A}_{bsc}$ is an \texttt{NC} algorithm denoted by
-$\mathsf{A}_{bsc}^{\psi}$.
+the computing time of Algorithm~$\mathsf{A}_{\text{bsc}}$
+is $c_1+\psi(|\textbf{I}|)\cdot c_2$. With this restriction, Algorithm~$\mathsf{A}_{\text{bsc}}$ is an \texttt{NC} algorithm denoted by
+$\mathsf{A}_{\text{bsc}}^{\psi}$.
 
-Based on $\mathsf{A}_{bsc}^{\psi}$, we can identify a class of datalog programs
-$\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ such that all the datalog programs in it can be handled
-by $\mathsf{A}_{bsc}^{\psi}$.
-It is obvious that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ is a \texttt{PTD} class.
+Based on $\mathsf{A}_{\text{bsc}}^{\psi}$, we can identify a class of datalog programs
+$\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$ such that all the datalog programs in it can be handled
+by $\mathsf{A}_{\text{bsc}}^{\psi}$.
+It is obvious that $\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$ is a \texttt{PTD} class.
 We use the following theorem to further show that this class can be captured based on
-the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$.
+the materialization graphs of the datalog programs in $\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$.
 
 \begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff $P$ has a
+For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$ iff $P$ has a
 materialization graph whose depth is upper-bounded by $\psi(|P|)$.
@@
 Consider Example~\ref{exp:mg} again. Let the integer $k$ be a variable. We can
-get a class of datalog programs, denoted by $\mathbb{P}_{ex_1}$, where the rule set
+get a class of datalog programs, denoted by $\mathbb{P}_{\text{ex}_1}$, where the rule set
 is $\{R(x,y),A(y)\rightarrow A(x), S(x,y),R(y,z)\rightarrow R(x,z)\}$ and the fact
-set varies according to $k$. The algorithm $\mathsf{A}_{bsc}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{ex_1}$.
-Let $\mathcal{G}_{ex_1}$ be some materialization graph corresponding
-to some datalog program in $\mathbb{P}_{ex_1}$. It can be checked that
-\texttt{depth}($\mathcal{G}_{ex_1}$)$=k$ for some $k$.
+set varies according to $k$. The algorithm $\mathsf{A}_{\text{bsc}}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{\text{ex}_1}$.
+Let $\mathcal{G}_{\text{ex}_1}$ be some materialization graph corresponding
+to some datalog program in $\mathbb{P}_{\text{ex}_1}$. It can be checked that
+\texttt{depth}($\mathcal{G}_{\text{ex}_1}$)$=k$ for some $k$.
 This means that the depths of the materialization graphs are linearly bounded by $k$.
-On the other hand, the sizes of the datalog programs in $\mathbb{P}_{ex_1}$ are polynomial in $k$.
+On the other hand, the sizes of the datalog programs in $\mathbb{P}_{\text{ex}_1}$ are polynomial in $k$.
 Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
-enough such that $\mathsf{A}_{bsc}^{\psi}$ terminates without constructing a materialization
-graph for each datalog program in $\mathbb{P}_{ex_1}$.
-However, there indeed exists an \texttt{NC} algorithm that can handle $\mathbb{P}_{ex_1}$.
+enough such that $\mathsf{A}_{\text{bsc}}^{\psi}$ terminates without constructing a materialization
+graph for each datalog program in $\mathbb{P}_{\text{ex}_1}$.
+However, there indeed exists an \texttt{NC} algorithm that can handle $\mathbb{P}_{\text{ex}_1}$.
 We discuss this in the next part.
 
-\subsection{Optimizing Algorithm~$\mathsf{A}_{bsc}$ via Single-Way Derivability}
+\subsection{Optimizing Algorithm~$\mathsf{A}_{\text{bsc}}$ via Single-Way Derivability}
 
-In this part, we optimize Algorithm~$\mathsf{A}_{bsc}$ such that $P_{ex_1}$
-can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{bsc}$,
+In this part, we optimize Algorithm~$\mathsf{A}_{\text{bsc}}$ such that $P_{\text{ex}_1}$
+can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{\text{bsc}}$,
 we can identify another \texttt{PTD} class.
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.eps}
+\includegraphics[width=0.7\textwidth]{fig-general.pdf}
 \caption{A partial materialization graph}
@@
 \begin{example}\label{exp:general}
-Consider the  snapshot of Algorithm~$\mathsf{A}_{bsc}$ in
+Consider the  snapshot of Algorithm~$\mathsf{A}_{\text{bsc}}$ in
 Figure~\ref{fig:general}. A materialization graph $\mathcal{G}$
@@
 In Example~\ref{exp:general}, $v_k$ would be added to $\mathcal{G}$ after \emph{at least} $k$
-iterations by performing Algorithm~$\mathsf{A}_{bsc}$.
+iterations by performing Algorithm~$\mathsf{A}_{\text{bsc}}$.
 We can check that each edge $(v_{i-1},v_i)$ ($1\leq i\leq k$) in this
@@
 $\mathcal{G}$ immediately.
-Based on the above idea, we optimize Algorithm~$\mathsf{A}_{bsc}$ by checking whether such an SWD path
+Based on the above idea, we optimize Algorithm~$\mathsf{A}_{\text{bsc}}$ by checking whether such an SWD path
 exits for some node $v$. If there is an SWD path for node $v$, this node can be added to $\mathcal{G}$
@@
 e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{bsc}$, we further compute a \texttt{rch}
+In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{\text{bsc}}$, we further compute a \texttt{rch}
 relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
@@
 \begin{enumerate}[leftmargin=0ex]
-\item \emph{if the all body atoms $B_1,...,B_n$ have been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),...,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
+\item \emph{if the all body atoms $B_1,\ldots,B_n$ have been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),\ldots,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
 \item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
@@
 \begin{enumerate}[leftmargin=6ex,label=(\textbf{\roman*})]
-\item Compute a \texttt{rch} relation $S_{\!\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
+\item Compute the \texttt{rch} relation $S_{\!\textit{\tiny rch}}$ by following the above process (see $(\textbf{\dag})$).\label{rch}
 \item Compute the transitive closure $S^*_{\!\textit{\tiny rch}}$ of $S_{\!\textit{\tiny rch}}$.\label{transClos}
@@
     to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H),...,e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
+    $e(B_1, H), \ldots, e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
     \texttt{rch}$(B_j,H)\in S_{\!\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$
@@
 transitive closure \cite{Allender07}.
-Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{bsc}$:\\
+Based on this result and Algorithm~$\mathsf{OPT}$, we propose an optimized variant of Algorithm~$\mathsf{A}_{\text{bsc}}$:\\
 
-\noindent\texttt{Algorithm~$\mathsf{A}_{opt}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
+\noindent\texttt{Algorithm~$\mathsf{A}_{\text{opt}}$}. Given a datalog program $P=\langle R, \textbf{I}\rangle$, the algorithm
 returns a materialization graph $\mathcal{G}$ of $P$.
@@
 It should be noted that there has to be an SWD path for any derivable node in some iteration when performing
-Algorithm~$\mathsf{A}_{opt}$.
-The following lemma shows the correctness of Algorithm~$\mathsf{A}_{opt}$.
+Algorithm~$\mathsf{A}_{\text{opt}}$.
+The following lemma shows the correctness of Algorithm~$\mathsf{A}_{\text{opt}}$.
 
@@
 Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
+$\mathsf{A}_{\text{opt}}$ halts and outputs a materialization graph $\mathcal{G}$ of $P$.
 \end{lemma}
@@
 \begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{opt}$ on the datalog program $P_{ex_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{ex_1}$.
+We perform Algorithm~$\mathsf{A}_{\text{opt}}$ on the datalog program $P_{\text{ex}_1}$ in Example~\ref{exp:mg}.
+Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{\text{ex}_1}$.
 In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
-`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$' $(2\leq i\leq k)$,
-$S_{\!\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b), R(a_i,b))|2\leq i\leq k\}
-\cup\{$\texttt{rch}$(R(a_i,b), A(a_i))|1\leq i\leq k\}$.
+`$R(a_i,b),A(b)\rightarrow A(a_i)$' and `$S(a_i,a_{i-1}),$ $R(a_{i-1},b)\rightarrow R(a_i,b)$', $2\leq i\leq k$,
+$S_{\!\textit{\tiny rch}}$ is the set $\{$\texttt{rch}$(R(a_{i-1},b),
+R(a_i,b)) \mid 2\leq i\leq k\}
+\cup\{$\texttt{rch}$(R(a_i,b), A(a_i)) \mid 1\leq i\leq k\}$.
 In the transitive closure of $S_{\!\textit{\tiny rch}}$,
 one can check that \texttt{rch}$(R(a_1,b), R(a_i,b)),$
-\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\!\textit{\tiny rch}}(2\leq i\leq k)$.
-Thus, $R(a_i,b)$ and $A(a_i)$ ($2\leq i\leq k$) can all be added to $\mathcal{G}_{ex_1}$
+\texttt{rch}$(R(a_1,b), A(a_i))\in S^*_{\!\textit{\tiny rch}}, 2\leq i\leq k$.
+Thus, $R(a_i,b)$ and $A(a_i)$, $2\leq i\leq k$, can all be added to
+$\mathcal{G}_{\text{ex}_1}$
 in the first iteration of \ref{alg3:updateG}.
@@
 
-The analysis of the parallel complexity of Algorithm~$\mathsf{A}_{opt}$ is given as follows.
-We use the same symbols $e$, $v$ and $r$ that are used for analyzing the complexity of Algorithm~$\mathsf{A}_{bsc}$
-(see Section~\ref{sec:alg-bsc}). Similarly to the analysis for Algorithm~$\mathsf{A}_{bsc}$, it can be checked that
-the number of processors is polynomial of $|\textbf{I}|$, i.e., $r(|\textbf{I}|e)^v$.
-We now consider the computing time of Algorithm~$\mathsf{A}_{opt}$. It is obvious that \ref{alg3:addFacts}
+We now analyse the parallel complexity of Algorithm~$\mathsf{A}_{\text{opt}}$.
+We use the same symbols $e$, $v$ and $r$ that are used for analyzing the complexity of Algorithm~$\mathsf{A}_{\text{bsc}}$
+(see Section~\ref{sec:alg-bsc}). Similarly to the analysis for Algorithm~$\mathsf{A}_{\text{bsc}}$, it can be checked that
+the number of processors is polynomial in $|\textbf{I}|$, i.e., $r(|\textbf{I}|e)^v$.
+We now consider the computing time of Algorithm~$\mathsf{A}_{\text{opt}}$. It
+is obvious that \ref{alg3:addFacts} and
 \ref{alg3:halt} occupy constant time (denoted by $c_1$). In \ref{alg3:updateG}, the phases of
@@
 under the parallel assumption. Recall that the number of constants is at most $|\textbf{I}|e$ (see Section~\ref{sec:alg-bsc}).
-Let $w$ and $p$ represent the maximum arity of any predicate and the number of predicates respectively.
+Let $w$ and $p$ represent the maximum arity of any predicate and the number of predicates, respectively.
 We have that the number of all possible substitutions of atoms is at most $p(|\textbf{I}|e)^w$.
@@
 is bounded by $p^2(|\textbf{I}|e)^{2w}$. It can be checked that the computing time of the \texttt{NC} algorithm for computing the transitive
-closure of $S_{\!\textit{\tiny rch}}$ is poly-logarithmical in the size of $\textbf{I}$, more precisely,
-it is upper bounded to $\log^2(p^2(|\textbf{I}|e)^{2w})$ ($=4\log^2(p)+4w^2\log^2(|\textbf{I}|e)+8w\log(p)\log(|\textbf{I}|e)$).
-We now have that the total computing time of Algorithm~$\mathsf{A}_{opt}$ is $c_1+lc_3 + lc_4\log(|\textbf{I}|e) +lc_5\log^2(|\textbf{I}|e)$
-where $c_3=c_2+4\log^2(p)$, $c_4=8w\log(p)$, $c_5=4w^2$ and $l$ denotes the number of iterations of \ref{alg3:updateG}.
+closure of $S_{\!\textit{\tiny rch}}$ is poly-logarithmic in the size of $\textbf{I}$, more precisely,
+it is upper bounded by $\log^2(p^2(|\textbf{I}|e)^{2w})$ ($=4\log^2(p)+4w^2\log^2(|\textbf{I}|e)+8w\log(p)\log(|\textbf{I}|e)$).
+We now have that the total computing time of
+Algorithm~$\mathsf{A}_{\text{opt}}$ is $c_1+\ell c_3 + \ell
+c_4\log(|\textbf{I}|e) +\ell c_5\log^2(|\textbf{I}|e)$
+where $c_3=c_2+4\log^2(p)$, $c_4=8w\log(p)$, $c_5=4w^2$ and $\ell$ denotes the number of iterations of \ref{alg3:updateG}.
 
-Algorithm~$\mathsf{A}_{opt}$ can be restricted to an \texttt{NC} algorithm analogously to the process
-for Algorithm~$\mathsf{A}_{bsc}$. That is the number of iterations of \ref{alg3:updateG}
+Algorithm~$\mathsf{A}_{\text{opt}}$ can be restricted to an \texttt{NC} algorithm analogously to the process
+for Algorithm~$\mathsf{A}_{\text{bsc}}$. That is the number of iterations of \ref{alg3:updateG}
 is poly-logarithmically bounded, i.e., it is bounded by $\psi(|\textbf{I}|)$
-where $\psi$ is a poly-logarithmical function. In this way, the computing time of
-Algorithm~$\mathsf{A}_{bsc}$ turns out to be $c_1+c_3\psi(|\textbf{I}|)+c_4\psi(|\textbf{I}|)\log(|\textbf{I}|e)+
+where $\psi$ is a poly-logarithmic function. In this way, the computing time of
+Algorithm~$\mathsf{A}_{\text{bsc}}$ turns out to be $c_1+c_3\psi(|\textbf{I}|)+c_4\psi(|\textbf{I}|)\log(|\textbf{I}|e)+
 c_5\psi(|\textbf{I}|)\log^2(|\textbf{I}|e)$,
 which is still poly-logarithmical in the size of $\textbf{I}$. We denote the
-\texttt{NC} variant of Algorithm~$\mathsf{A}_{opt}$ by $\mathsf{A}_{opt}^{\psi}$.
+\texttt{NC} variant of Algorithm~$\mathsf{A}_{\text{opt}}$ by $\mathsf{A}_{\text{opt}}^{\psi}$.
 
-Based on $\mathsf{A}_{opt}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
-Further, we have the following corollary which implies that $\mathsf{A}_{opt}^{\psi}$ performs better
-than $\mathsf{A}_{bsc}^{\psi}$ in terms of computing time.
+Based on $\mathsf{A}_{\text{opt}}^{\psi}$, we can identify a \texttt{PTD} class $\mathcal{D}_{\mathsf{A}_{\text{opt}}^{\psi}}$.
+Further, we have the following corollary, which implies that $\mathsf{A}_{\text{opt}}^{\psi}$ performs better
+than $\mathsf{A}_{\text{bsc}}^{\psi}$ in terms of computing time.
 
@@
 For any poly-logarithmically bounded function $\psi$,
-we have that $\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
+we have that $\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}\subseteq\mathcal{D}_{\mathsf{A}_{\text{opt}}^{\psi}}$.
 \end{corollary}
@@
 \begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{bsc}^{\psi}$ is upper-bounded by $\psi(|P|)$.
+Suppose $P\in\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$. According to Theorem~\ref{theorem:a1},
+the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{\text{bsc}}^{\psi}$ is upper-bounded by $\psi(|P|)$.
 It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
-According to the optimization strategy applied in $\mathsf{A}_{opt}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{opt}$, the number of iterations of $\mathsf{A}_{opt}$ has to be upper-bounded by $\psi(|P|)$;
+According to the optimization strategy applied in $\mathsf{A}_{\text{opt}}$, if $\mathcal{G}$ can be constructed
+by $\mathsf{A}_{\text{opt}}$, the number of iterations of $\mathsf{A}_{\text{opt}}$ has to be upper-bounded by $\psi(|P|)$;
 if $\mathcal{G}$ is not the materialization graph constructed
-by $\mathsf{A}_{opt}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{opt}$
-and $\mathcal{G}'$ has a smaller depth compared with $\mathcal{G}$.
+by $\mathsf{A}_{\text{opt}}$, then there has to exist another materialization graph $\mathcal{G}'$ constructed by $\mathsf{A}_{\text{opt}}$
+and $\mathcal{G}'$ has a smaller depth compared to $\mathcal{G}$.
 \end{proof}

### 2018-01-31 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
Section 4 and small adjustments done

@@
 for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{opt}$.
-We show that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
+based on Algorithm~$\mathsf{A}_{\text{opt}}$. 1We show that, for any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
 there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle materialization of $\mathcal{O}$.
-However, for DHL and DHL($\circ$), there exist ontology classes such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot always
+such that Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$ can handle materialization of $\mathcal{O}$.
+However, for DHL and DHL($\circ$), there exist ontology classes such that Algorithm~$\mathsf{A}_{\text{opt}}^\psi$
+does not work. We illustrate the reason why Algorithm~$\mathsf{A}_{\text{opt}}^\psi$ cannot always
 work by studying specific cases.
@@
 
-\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{opt}$}
+\subsection{Materialization of DL-Lite Ontologies via Algorithm~$\mathsf{A}_{\text{opt}}$}
 
-In this part, we show how to use Algorithm~$\mathsf{A}_{opt}$ to handle
+In this part, we show how to use Algorithm~$\mathsf{A}_{\text{opt}}$ to handle
 DL-Lite materialization and analyze its parallel tractability.
-Based on the analysis, we have that, for any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology
+Based on the analysis, we have that, for any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology
 there always exists an SWD path for each atom of the form $A(a)$ or $R(a,b)$.
@@
 the constructed materialization graph in the first iteration of \ref{alg3:updateG}
-by performing Algorithm~$\mathsf{A}_{opt}$.
+by performing Algorithm~$\mathsf{A}_{\text{opt}}$.
 
-In order to show how Algorithm~$\mathsf{A}_{opt}$ handles DL-Lite materialization,
+In order to show how Algorithm~$\mathsf{A}_{\text{opt}}$ handles DL-Lite materialization,
 we use the following example.
@@
 \begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{ex_5}$
-where its TBox and RBox contain the following axioms:
+Given a DL-Lite ontology $\mathcal{O}_{\text{ex}_5}$
+where the TBox and RBox contain the following axioms:
 $A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
@@
 its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_5}$ by $P_{ex_5}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_5}$ by $P_{\text{ex}_5}=\langle R, \textbf{I}\rangle$,
 where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
 as the only fact.
-The unique materialization graph of $P_{ex_5}$ is denoted by $\mathcal{G}_{ex_5}$ (see Figure~\ref{fig:ex2}).
+The unique materialization graph of $P_{\text{ex}_5}$ is denoted by $\mathcal{G}_{\text{ex}_5}$ (see Figure~\ref{fig:ex2}).
 \end{example}
@@
 \begin{center}
-\includegraphics[width=0.6\textwidth]{fig-dllite.eps}
-\caption{The materialization graph of $\mathcal{O}_{ex_5}$.}
+\includegraphics[width=0.5\textwidth]{fig-dllite.pdf}
+\caption{The materialization graph of $\mathcal{O}_{\text{ex}_5}$}
 \label{fig:ex2}
@@
 
-Consider performing Algorithm~$\mathsf{A}_{opt}$ on the ontology $\mathcal{O}_{ex_5}$ in Example~\ref{exp:dllite}.
-(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{opt}$ adds all ABox assertions (only $Q(a,b)$ here)
-to $\mathcal{G}_{ex_5}$ that is initially an empty graph (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{opt}$).
+Consider performing Algorithm~$\mathsf{A}_{\text{opt}}$ on the ontology $\mathcal{O}_{\text{ex}_5}$ in Example~\ref{exp:dllite}.
+(\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{\text{opt}}$ adds all ABox assertions (only $Q(a,b)$ here)
+to the initially empty graph $\mathcal{G}_{\text{ex}_5}$ (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{\text{opt}}$).
 (\uppercase\expandafter{\romannumeral2}) In the first iteration of
-\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$ checks that all of the nodes
+\ref{alg3:updateG}, Algorithm~$\mathsf{A}_{\text{opt}}$ checks that all of the nodes
 $A(a)$, $S(b,a)$, $B_1(a)$, $B_2(a)$ and $R(b,a)$ have corresponding SWD paths
-starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{opt}$
-adds these nodes to $\mathcal{G}_{ex_5}$ immediately. We take an example of node $B_1(a)$,
+starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{\text{opt}}$
+adds these nodes to $\mathcal{G}_{\text{ex}_5}$ immediately. We take an example of node $B_1(a)$,
 for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{ex_5}$ by adding $B_1(a)$ to it,
-Algorithm~$\mathsf{A}_{opt}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{ex_5}$; if $A(a)$ is already in $\mathcal{G}_{ex_5}$, $B_1(a)$
-is added to $\mathcal{G}_{ex_5}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{ex_5}$, Algorithm~$\mathsf{A}_{opt}$ adds $A(a)$ (resp., $B_1(a)$)
-to $\mathcal{G}_{ex_5}$ and creates an edge pointing from $Q(a,b)$ to $A(a)$ (resp.,
-an edge pointing from $A(a)$ to $B_1(a)$).\footnote{These two cases may happen simultaneously,
+When updating $\mathcal{G}_{\text{ex}_5}$ by adding $B_1(a)$ to it,
+Algorithm~$\mathsf{A}_{\text{opt}}$ first checks whether the parent node $A(a)$ of $B_1(a)$
+has been in $\mathcal{G}_{\text{ex}_5}$; if $A(a)$ is already in $\mathcal{G}_{\text{ex}_5}$, $B_1(a)$
+is added to $\mathcal{G}_{\text{ex}_5}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
+if $A(a)$ has not been added to $\mathcal{G}_{\text{ex}_5}$,
+Algorithm~$\mathsf{A}_{\text{opt}}$ adds $A(a)$ ($B_1(a)$, respectively)
+to $\mathcal{G}_{\text{ex}_5}$ and creates an edge pointing from
+$Q(a,b)$ to $A(a)$ (an edge pointing from $A(a)$ to $B_1(a)$, respectively).\footnote{These two cases may happen simultaneously,
 since node $A(a)$ and node $B_1(a)$ are being processed in parallel.} The other nodes
@@
 (\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{opt}$ finishes constructing $\mathcal{G}_{ex_5}$
+Finally, Algorithm~$\mathsf{A}_{\text{opt}}$ finishes constructing $\mathcal{G}_{\text{ex}_5}$
 after two iterations (\ref{alg3:halt}).
@@
 From the above example, we can observe that SWD paths exist
-for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{opt}$.
-Further, we give the following lemma that satisfies any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology.
+for all nodes except $\bot(a)$ and $\bot(b)$ in the first iteration of Algorithm~$\mathsf{A}_{\text{opt}}$.
+Further, we give the following lemma that holds for any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology.
 
 \begin{lemma}\label{lemma:dllite}
-For any DL-Lite$_{core}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
+For any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
 each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.
@@
 have to be added to the constructed materialization graph in the first iteration of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
+\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{\text{opt}}$.
 For each atom of the form $\bot(x)$, there may not exist an SWD path in the first iteration
 of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{ex_5}$ of
-Example~\ref{exp:dllite}). On the other hand, according to the syntaxes of DL-Lite,
-$\bot$ dose not occur on the left hand of any axiom. In other words,
+(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{\text{ex}_5}$ of
+Example~\ref{exp:dllite}). On the other hand, according to the syntax of DL-Lite,
+$\bot$ does not occur on the left-hand side of any axiom. In other words,
 an atom of the form $\bot(x)$ cannot be the parent of any other node.
-This allows all atoms of the form $\bot(x)$ being added
-to the constructed materialization graph in at most two iterations of
-\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{opt}$.
+This allows for adding all atoms of the form $\bot(x)$ to the constructed materialization graph in at most two iterations of
+\ref{alg3:updateG} by applying Algorithm~$\mathsf{A}_{\text{opt}}$.
 Based on the above discussion, for any DL-Lite ontology $\mathcal{O}$,
 there always exists a poly-logarithmically bounded function $\psi$ such that
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$;
+Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$ can handle the materialization of $\mathcal{O}$;
 more precisely, we can set that $\psi=2$. This result is consistent with
-that in \cite{CalvaneseGLLR07}.
-Formally, we use $\mathcal{D}_{\textit{\text{dl\_lite}}}$
-to denote the set of all DL-Lite$_{core}$ and DL-Lite$_\mathcal{R}$ ontologies, and give the following theorem.
+that by \citet{CalvaneseGLLR07}.
+Formally, we use $\mathcal{D}_{\textit{dl\_lite}}$
+to denote the set of all DL-Lite$_{\text{core}}$ and DL-Lite$_\mathcal{R}$ ontologies and give the following theorem.
 
 \begin{theorem}\label{theorem:dl-lite}
-There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl\_lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
+There exists a poly-logarithmically bounded function $\psi$ such that
+$\mathcal{D}_{\textit{dl\_lite}}\subseteq\mathcal{D}_{\mathsf{A}_{\text{opt}}^{\psi}}$.
 \end{theorem}
 
-\subsection{Parallelly Tractable Materialization of DHL}
+\subsection{Parallel Tractability of  DHL Materialization}
 \label{sec:DHL}
 
-In this part, we study whether Algorithm~$\mathsf{A}_{opt}^\psi$ can handle DHL ontologies.
-Unfortunately there exist DHL ontology classes such that Algorithm~$\mathsf{A}_{opt}^\psi$
-does not work for any poly-logarithmically bounded function $\psi$.
+In this part, we study whether Algorithm~$\mathsf{A}_{\text{opt}}^\psi$ can handle DHL ontologies.
+Unfortunately there exist DHL ontology classes such that Algorithm~$\mathsf{A}_{\text{opt}}^\psi$
+does not work for any poly-lo\-ga\-rith\-mi\-cal\-ly bounded function $\psi$.
 In the following, we first give such a case
-to illustrate the reason why Algorithm~$\mathsf{A}_{opt}^\psi$ cannot work.
+to illustrate the reason why Algorithm~$\mathsf{A}_{\text{opt}}^\psi$ cannot work.
 Based on the analysis of this case, we propose to restrict
@@
 form $B_1\sqcap B_2\sqsubseteq A$
-makes it impossible for Algorithm~$\mathsf{A}_{opt}$ to construct a materialization graph
-in a poly-logarithmical number of iterations of \ref{alg3:updateG}.
-We use the following example to illustrate it.
+makes it impossible for Algorithm~$\mathsf{A}_{\text{opt}}$ to construct a materialization graph
+in a poly-logarithmic number of iterations of \ref{alg3:updateG}.
+We use the following example to illustrate this.
 
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.eps}
-\caption{(left) The materialization graph of $\mathcal{O}_{ex_6}$;
-(right) The materialization graph of $\mathcal{O}_{ex_7}$.}
+\includegraphics[width=0.9\textwidth]{fig-pathtwist.pdf}
+\caption{The materialization graph of $\mathcal{O}_{\text{ex}_6}$
+  (left) and of $\mathcal{O}_{\text{ex}_7}$ (right)}
 \label{fig:ex3_4}
@@
 \begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{ex_6}$ where its TBox contains three axioms:
+Given a DHL ontology $\mathcal{O}_{\text{ex}_6}$ where the TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
 the ABox is $\{S(a_i,a_{i-1}), R(a_i,a_{i-1}), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program of $\mathcal{O}_{ex_6}$ by $P_{ex_6}=\langle R, \textbf{I}\rangle$,
+for $2\leq i\leq k$ and $k$ an integer greater than $2$.
+We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_6}$ by $P_{\text{ex}_6}=\langle R, \textbf{I}\rangle$,
 where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{ex_6}$ constructed by $\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_6}$ (see Figure~\ref{fig:ex3_4}(left)).
+The materialization graph of $P_{\text{ex}_6}$ constructed by
+$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_6}$
+(see Figure~\ref{fig:ex3_4}~(left)).
 \end{example}
 
-One can check that $\mathcal{G}_{ex_6}$ is the unique materialization graph of $P_{ex_6}$.
-Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),...,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{opt}$ on $P_{ex_6}$, it can be checked that
+One can check that $\mathcal{G}_{\text{ex}_6}$ is the unique materialization graph of $P_{\text{ex}_6}$.
+Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),\ldots,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
+When performing Algorithm~$\mathsf{A}_{\text{opt}}$ on $P_{\text{ex}_6}$, it can be checked that
 each node of the form $A(a_i)$ (filled with black color,
 and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{ex_6}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{ex_6}$.
-Similar to the datalog program class $\mathbb{P}_{ex_1}$, we can also get a
-datalog program class $\mathbb{P}_{ex_6}$ for the ontology $\mathcal{O}_{ex_6}$
-when $k$ is a variable. Based on the above analysis, Algorithm~$\mathsf{A}_{opt}$ cannot complete the materialization
-for the datalog programs of $\mathbb{P}_{ex_6}$ in a poly-logarithmical
+in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{\text{ex}_6}$,
+and, $A(a_i)$ can also be added to $\mathcal{G}_{\text{ex}_6}$.
+Similar to the datalog program class $\mathbb{P}_{\text{ex}_1}$, we can also get a
+datalog program class $\mathbb{P}_{\text{ex}_6}$ for the ontology $\mathcal{O}_{\text{ex}_6}$
+when $k$ is a variable. Based on the above analysis, Algorithm~$\mathsf{A}_{\text{opt}}$ cannot complete the materialization
+for the datalog programs of $\mathbb{P}_{\text{ex}_6}$ in a poly-logarithmic
 number of iterations.
-The intuitive reason is that, at least two paths exist
-starting from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
-It makes the optimization of acceleration used in Algorithm~$\mathsf{A}_{opt}$ invalid.
-That is, for each node $A(a_i)$ ($2\leq i\leq k$), until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{ex_6}$, there would not exist an available SWD path for $A(a_i)$.
-We use `\emph{path twisting}' to represent such cases.
+The intuitive reason is that at least two paths exist
+from $A(a_1)$ to $A(a_k)$. These paths \emph{twist} mutually and share the same joint nodes (see the black nodes).
+This invalidates the optimization used in Algorithm~$\mathsf{A}_{\text{opt}}$.
+That is, for each node $A(a_i)$, $2\leq i\leq k$, until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
+to $\mathcal{G}_{\text{ex}_6}$, there would not exist an available SWD path for $A(a_i)$.
+We use the term `\emph{path twisting}' to refer to such cases.
 
-In order to make Algorithm~$\mathsf{A}_{opt}$ terminate in a poly-logarithmical number of iterations,
+In order to make Algorithm~$\mathsf{A}_{\text{opt}}$ terminate in a poly-logarithmic number of iterations,
 we consider restricting the usage of axioms of the form $B_1\sqcap B_2\sqsubseteq A$
@@
 \begin{example}\label{exp:simpleC}
-Consider an ontology $\mathcal{O}_{ex_7}$ where the TBox contains three axioms:
+Consider an ontology $\mathcal{O}_{\text{ex}_7}$ where the TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
 the ABox is $\{S(a_i,a_{i-1}), B_3(a_i), A(a_1)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-We denote the corresponding datalog program by $P_{ex_7}$ where the rule set contains:
+for $2\leq i\leq k$ and $k$ an integer greater than $2$.
+We denote the corresponding datalog program by $P_{\text{ex}_7}$ where the rule set contains:
 `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{ex_7}$ has a unique materialization graph denoted by $\mathcal{G}_{ex_7}$ (see Figure~\ref{fig:ex3_4}(right)).
+$P_{\text{ex}_7}$ has a unique materialization graph denoted by $\mathcal{G}_{\text{ex}_7}$ (see Figure~\ref{fig:ex3_4}~(right)).
 \end{example}
@@
 of the form $B_2(x)$ must not be child nodes of an atom $A(y)$ for some $y$.
-This ensures that only one path exists between each two nodes among $A(a_2),...,A(a_k)$.
-Further, when constructing $\mathcal{G}_{ex_7}$, Algorithm~$\mathsf{A}_{opt}$ can terminate after
-two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{opt}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$ ($2\leq i\leq k$) to $\mathcal{G}_{ex_7}$,
+This ensures that only one path exists between each two nodes among $A(a_2),\ldots,A(a_k)$.
+Further, when constructing $\mathcal{G}_{\text{ex}_7}$, Algorithm~$\mathsf{A}_{\text{opt}}$ can terminate after
+two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{\text{opt}}$
+adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$, $2\leq i\leq k$, to $\mathcal{G}_{\text{ex}_7}$
 since they have corresponding SWD paths;
-after that, all the other nodes
-can be added to $\mathcal{G}_{ex_7}$ in the second iteration (because each
+after that, all other nodes
+can be added to $\mathcal{G}_{\text{ex}_7}$ in the second iteration (because each
 node has an SWD path).
@@
 form $B_1\sqcap B_2\sqsubseteq A$, at least one concept of $B_1$ and $B_2$ should be a simple concept
-(we call it \emph{simple-concept restriction}).
-Intuitively, for the restricted DHL ontologies, the situation of `path twisting' would not happen.
-This is because, if in each axiom of the form $B_1\sqcap B_2\sqsubseteq A$, w.l.o.g., $B_1$
-is a simple concept, then none of ancestors of $B_1(x)$ for some $x$
+(we call this the \emph{simple-concept restriction}).
+Intuitively, for such restricted DHL ontologies, the situation of `path twisting' does not happen.
+This is because, for each axiom of the form $B_1\sqcap B_2\sqsubseteq
+A$ such that, w.l.o.g., $B_1$
+is a simple concept, none of the ancestors of $B_1(x)$ for some $x$
 is generated from the rules corresponding to (T1).
@@
 In the ontology of Example~\ref{exp:simpleC}, $A$ and $B_1$ are non-simple concepts,
-while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that,
+while $B_3$ and $B_2$ are simple concepts. Further, it can be checked that
 the ontology  of Example~\ref{exp:simpleC} follows the simple-concept restriction
-and can be handled by Algorithm~$\mathsf{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$.
+and can be handled by Algorithm~$\mathsf{A}_{\text{opt}}^\psi$ for some poly-logarithmic function $\psi$.
 \end{example}
@@
 give Theorem \ref{theorem:dhl} to show that any DHL ontology that satisfies the
-simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{opt}$
-for some poly-logarithmical function $\psi$.
+simple-concept restriction can be handled by Algorithm~$\mathsf{A}^\psi_{\text{opt}}$
+for some poly-logarithmic function $\psi$.
 
@@
 There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
+$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{\text{opt}}^{\psi}}$.
 \end{theorem}
 
-\subsection{Parallelly Tractable Materialization of DHL($\circ$)}
+\subsection{Parallel Tractability of DHL($\circ$) Materialization}
 \label{sec:DHLo}
 
-In this part, we study parallelly tractable materialization
-of DHL($\circ$) ontologies.
+In this part, we study materialization tractable in parallel for DHL($\circ$) ontologies.
 In addition to the rules in DHL, we also have to consider complex RIAs (R4).
 We next show that complex RIAs may also cause the situation of `path twisting'.
-Consider the following example.
-
+Consider the following example:
+%
 \begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{ex_9}$ where its TBox is empty;
+Given a DHL$(\circ)$ ontology $\mathcal{O}_{\text{ex}_9}$ where the TBox is empty;
 the RBox $\mathcal{R}$ contains three axioms:
@@
 the ABox $\mathcal{A}$ is $\{R(a_1,a_1), R_3(a_i,a_{i-1}), R_4(a_{i-1},a_i)\}$
-for $2\leq i\leq k$ and $k$ is an integer greater than 2.
-The corresponding datalog program $P_{ex_5}$
+for $2\leq i\leq k$ and $k$ an integer greater than $2$.
+The corresponding datalog program $P_{\text{ex}_5}$
 contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
 `$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{ex_5}$ constructed by Algorithm~$\mathsf{A}_{opt}$ is denoted by $\mathcal{G}_{ex_9}$.
+The materialization graph of $P_{\text{ex}_5}$ constructed by Algorithm~$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_9}$.
 \end{example}
 
-One can check that the materialization graph $\mathcal{G}_{ex_9}$ has the same shape as that
-of $\mathcal{G}_{ex_6}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{ex_9}$ involving $R(a_i,a_i) (2\leq i\leq k)$ as the joint nodes.
+One can check that the materialization graph $\mathcal{G}_{\text{ex}_9}$ has the same shape as that
+of $\mathcal{G}_{\text{ex}_6}$ in Figure~\ref{fig:ex3_4}.
+A twisted path exists in $\mathcal{G}_{\text{ex}_9}$ involving
+$R(a_i,a_i)$, $2\leq i\leq k$, as the joint nodes.
 Further, all the roles $R_1$, $R_2$, $R_3$, $R_4$ and $R$ in this example are non-transitive roles.
@@
 We now consider such an axiom $R_1\circ R_2\sqsubseteq R$ (denoted by $\alpha_1$) where $R$ is a transitive role.
-That is we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
-By replacing $R$ on the left-hand of $\alpha_2$ using $R_1$ and $R_2$,
+That is, we also have $R\circ R\sqsubseteq R$ (denoted by $\alpha_2$).
+By replacing $R$ on the left-hand side of $\alpha_2$ using $R_1$ and $R_2$,
 we can get a complex RIA in the form of
@@
 and $\alpha_2$ separately has the same effect to that of only applying the rule of $\alpha_3$.}
-The reason can be explained as follows.
+This can be explained as follows: 
 Without loss of the generality,
-$R_2$ is a simple role while $R_1$ is not.
+$R_2$ is a simple role, while $R_1$ is not.
 For some atom $R(x,y)$, it may depend on two different nodes of the predicate $R_1$
-through the corresponding rule of $\alpha_3$. The similar analysis applies to
-such cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
+through the corresponding rule of $\alpha_3$. A similar analysis applies to
+the cases of $\alpha_1$ where $R$ is not a transitive role, while another transitive
 role $S$ exists such that $R\sqsubseteq_* S$. That is, we can obtain
@@
 we require both of $R_1$ and $R_2$ in $\alpha_1$ to be simple roles
-(we call the above restriction for transitive and non-transitive roles \emph{simple-role restriction}).
+(we call the above restriction for transitive and non-transitive roles
+the \emph{simple-role restriction}).
 Combined with the simple-concept restriction,
@@
 \item for all axioms of the form $A_1\sqcap A_2\sqsubseteq B$,
-    at least one concept of $A_1$ and $A_2$ should be a \emph{simple concept};
+    at least one concept of $A_1$ and $A_2$ is a \emph{simple concept};
 \item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does not exits a transitive role $S$ such that $R\sqsubseteq_* S$, then,
-    at least one of $R_1$ and $R_2$ is a \emph{simple role}; otherwise, both of $R_1$ and $R_2$ are \emph{simple roles}.
+    if there does exits a transitive role $S$ such that
+    $R\sqsubseteq_* S$, then both $R_1$ and $R_2$ are \emph{simple
+      roles}; otherwise at least one of $R_1$ and $R_2$ is a \emph{simple role}.
 \end{enumerate}
@@
 \begin{example}
-For the ontology $\mathcal{O}_{ex_7}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{ex_7}$ does not follow
+For the ontology $\mathcal{O}_{\text{ex}_7}$ in Example~\ref{exp:complexRIA}, all of the roles
+$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{\text{ex}_7}$ does not follow
 the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{ex_1}$
+Consider the ontology $\mathcal{O}_{\text{ex}_1}$
 in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus $\mathcal{O}_{ex_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{ex_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{ex_1}$ by Algorithm~$\mathsf{A}_{opt}$.
+Thus, $\mathcal{O}_{\text{ex}_1}$ follows the simple-role restriction. All the implicit nodes
+in $\mathcal{G}_{\text{ex}_1}$ have corresponding SWD paths in the first iteration.
+Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{\text{ex}_1}$ by Algorithm~$\mathsf{A}_{\text{opt}}$.
 \end{example}
 
-We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{opt}^{\psi}$ can handle
-all the datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmical function $\psi$.
+We further give Theorem~\ref{theorem:dhlplus} to show that Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$ can handle
+all datalog programs in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ for some poly-logarithmic function $\psi$.
 
 \begin{theorem}\label{theorem:dhlplus}
-There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.
+There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{\text{opt}}^{\psi}}$.
 \end{theorem}
 
-\subsection{The Parallel Tractability of the Reasoning on RDFS Ontologies}
+\subsection{Parallel Tractability of Reasoning over RDFS Ontologies}
 
-In this part, we discuss about the parallel tractability of the reasoning on RDFS ontologies.
-Although RDFS is not a standard description logic, it can be described by a subset of the DL axioms \cite{GrosofHVD03}.
-The correspondence between the RDFS statements and the DL axioms is listed in Table~\ref{tab:rdfs}.
-We call the RDFS statements in the form of (1-4) \emph{the schema data}
-(which correspond to TBox axioms), the statements in the form of (5) and (6)
+In this part, we discuss parallel tractability of reasoning over RDFS ontologies.
+Although RDFS is not directly based on a description logic, it can (partly) be described by a set of DL axioms \cite{GrosofHVD03}.
+The correspondence between RDFS statements and DL axioms is listed in Table~\ref{tab:rdfs}.
+We call RDFS statements of the form (1--4) \emph{the schema data}
+(which correspond to TBox axioms), statements of the form~(5) and~(6)
 \emph{the instance data} (which correspond to ABox axioms).
@@
 
-The original rule set for the reasoning task of RDFS ontologies is
-given in \cite{RDFSrec04}. By applying the rules in this rule set,
-new schema data would be derived. Thus, the reasoning task of RDFS
+The original rule set for RDFS reasoning is
+given by \citet{RDFSrec04}. By applying the rules in this rule set,
+new schema data could be derived. Thus, the reasoning task of RDFS
 is different from the task of materialization. Further, an RDFS ontology allows
-statements about blank nodes which play as variables. This semantically
-leads to infinite entailments. The author of \cite{Horst05} proves that
-the original rule set is incomplete with the restriction that
-blank nodes cannot occur in predicate positions. By loosening this restriction,
+statements about blank nodes which act like variables. This possibly
+leads to infinite entailments. Additionally, the original rule set is
+incomplete with the RDF restriction that
+blank nodes cannot occur in predicate positions \cite{Horst05},
+however, by allowing blank nodes in predicate position
 the rule set turns out to be complete. The computational complexity
-of the reasoning task on RDFS ontologies is shown to be NC-complete \cite{Horst05},
-which is not considered to be prallel-tractable.
+of RDFS reasoning is NC-complete \cite{Horst05},
+which is not considered to be tractable in parallel.
 
 The situation of path twisting may also happen when conducting reasoning
-on RDFS ontologies. Suppose $R_{subp}$ denotes the RDFS built-in property $\texttt{rdfs:subPropertyOf}$.
-We define the other three properties $R_1$, $R_2$ and $R_3$ by the following axioms:
-$R_1\sqsubseteq R_{subp}, R_2\sqsubseteq R_{subp}$ and $R_{subp}\sqsubseteq R_3$.
+on RDFS ontologies. Suppose $R_{\text{subp}}$ denotes the RDFS built-in property $\texttt{rdfs:subPropertyOf}$.
+We define three further properties $R_1$, $R_2$ and $R_3$ by the following axioms:
+$R_1\sqsubseteq R_{\text{subp}}, R_2\sqsubseteq R_{\text{subp}}$ and $R_{\text{subp}}\sqsubseteq R_3$.
 It can be checked that these three axioms entail the complex RIA $R_1\circ R_2\sqsubseteq R_3$ (denoted by $\beta$).
@@
 
-In this work, we study the task of materialization. Similarly, we can only focus on
-the entailments of new instance data for the target RDFS ontologies. To this end,
+In this work, we study the task of materialization, hence, we can only focus on
+newly entailed instance data for the RDFS ontologies. To this end,
 we assume that any class of RDFS ontologies has the same schema data (\uppercase\expandafter{\romannumeral1}). In this way,
-the axioms like $\beta$ cannot contribute to the computational complexity, since they
-only apply to schema data. Further, we restrict that blank nodes cannot occur in
-any class of RDFS ontologies (\uppercase\expandafter{\romannumeral2}). This allows an RDFS ontology
-being expressed in DHL (see Table~\ref{tab:rdfs}). Based on the two restrictions (\uppercase\expandafter{\romannumeral1})
-and (\uppercase\expandafter{\romannumeral2}), the reasoning task on RDFS ontologies
-is parallel-tractable (see Section~\ref{sec:DHL}).
+axioms such as $\beta$ cannot contribute to the computational complexity, since they
+only apply to schema data. Further, we assume blank nodes not to occur in
+any class of RDFS ontologies
+(\uppercase\expandafter{\romannumeral2}). This allows for expressing RDFS ontology
+in DHL (see Table~\ref{tab:rdfs}). Based on the two restrictions (\uppercase\expandafter{\romannumeral1})
+and (\uppercase\expandafter{\romannumeral2}), the materialization of RDFS ontologies
+is tractable in parallel (see Section~\ref{sec:DHL}).
 

### 2018-01-31 parallel-tractability-J-v9/appendix.tex
Finished the proof-reading of the optimized algorithm section

@@
 of Algorithm~$\mathsf{Opt}$.
-Suppose that \texttt{rch}$(B_k,H)\in S_{\tiny rch}$ is checked.
+Suppose that \texttt{rch}$(B_k,H)\in S_{\textit{\!\tiny rch}}$ is checked.
 It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
 Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
-\texttt{rch}$(B',B_k)\in S^*_{\tiny rch}$
+\texttt{rch}$(B',B_k)\in S^*_{\!\tiny rch}$
 and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
@@
 (see the proof of Lemma~\ref{lemma:a3}). This is because that
-such an induction is performed regardless of how the relation $S_{\textit{\tiny rch}}$ is computed.
+such an induction is performed regardless of how the relation $S_{\textit{\!\tiny rch}}$ is computed.
 
@@
 For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
-in $S_{\textit{\tiny rch}}$ obtained in some iteration; further
+in $S_{\textit{\!\tiny rch}}$ obtained in some iteration; further
 $\beta$ is already in $\mathcal{G}$ according to the inductive hypothesis. Thus,
@@
 Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
-such an SWD path of $A(a)$ can be determined by $S_{\textit{\tiny rch}}$.
+such an SWD path of $A(a)$ can be determined by $S_{\textit{\!\tiny rch}}$.
 The atom $A(a)$ can be derived through either of the following rule instantiations:
@@
 \item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
-    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
+    that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\!\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
     By the induction hypothesis, the existence of the SWD path for $B(a)$ can be determined.
-    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\tiny rch}}$.
+    Thus, the existence of the SWD path of $A(a)$ can also be determined by $S_{\textit{\!\tiny rch}}$.
 
@@
     According to Algorithm~$\mathsf{Prc}$ and the fact that $R(a,b)$ has to be derived,
-    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\tiny rch}}$.
+    we have that \texttt{rch}$(B(b),$ $A(a))$ is in $S_{\textit{\!\tiny rch}}$.
     By the induction hypothesis, the existence of the SWD path for $B(b)$ can be determined.
@@
     If $A_1(a)$ is derived where $A_1$ is a simple concept,
-    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\tiny rch}}$
+    we have that \texttt{rch}$(A_2(a),A(a))$ is in $S_{\textit{\!\tiny rch}}$
     according to Algorithm~$\mathsf{Prc}$.
@@
 \item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
-    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
+    We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\!\tiny rch}}$
     according to Algorithm~$\mathsf{Prc}$.
@@
 \item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
-    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\tiny rch}}$
+    We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\!\tiny rch}}$
     according to Algorithm~$\mathsf{Prc}$.
@@
     If $R_1(a,c)$ is derived where $R_1$ is a simple role,
-    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\tiny rch}}$
+    we have that \texttt{rch}$(R_2(c,b),R(a,b))$ is in $S_{\textit{\!\tiny rch}}$
     according to Algorithm~$\mathsf{Prc}$.

### 2018-01-31 parallel-tractability-J-v9/optimizedAlgo.tex
Finished the proof-reading of the optimized algorithm section

@@
-\section{A Further Optimized Algorithm for DHL$(\circ)$ Materialization}
+\section{Further Optimizing DHL$(\circ)$ Materialization}
 \label{sec:practicalAlg}
 
-In this section, we first discuss that Algorithm~$\mathsf{A}_{opt}$ can hardly work in practice.
-In order to make Algorithm~$\mathsf{A}_{opt}$ more practical,
-we propose to modify Algorithm~$\mathsf{A}_{opt}$ and give an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
-We show that Algorithm~$\mathsf{A}_{prc}$ can also be restricted to an NC version
-when materializing DHL$(\circ)$ ontologies that follow both of the simple-concept
-and the role-concept restrictions.
+In this section, we first discuss why Algorithm~$\mathsf{A}_{\text{opt}}$ can hardly work in practice.
+In order to make Algorithm~$\mathsf{A}_{\text{opt}}$ more practical,
+we propose to modify Algorithm~$\mathsf{A}_{\text{opt}}$ and give an algorithm variant Algorithm~$\mathsf{A}_{\text{prc}}$.
+We show that Algorithm~$\mathsf{A}_{\text{prc}}$ can also be restricted to an \texttt{NC} version
+when materializing DHL$(\circ)$ ontologies that satisfy both the simple-concept
+and the simple-role restriction.
 
@@
 
-In previous sections, Algorithm~$\mathsf{A}_{opt}$ is mainly used for theoretical analysis.
+In previous sections, Algorithm~$\mathsf{A}_{\text{opt}}$ is mainly used for theoretical analysis.
 However, this algorithm can hardly work in practice due to its inherently
 high requirement of computing space. Specifically,
-Algorithm~$\mathsf{A}_{opt}$ constructs a materialization graph by checking all possible rule
-instantiations in $P^*$ where $P$ is a datalog program that corresponds to an ontology.
-One can check that $|P^*|$ could be the square or cube of the number of constants occurring in $P$.
-Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'
-that is rewritten from the axiom of the form $\exists R.A\sqsubseteq B$;
-since there are two variables in this rule, the number of all possible rule instantiations
-is $|\textbf{IN}|^2$; if there are
-1000 individuals in \textbf{IN}, this number is 1 million.
+Algorithm~$\mathsf{A}_{\text{opt}}$ constructs a materialization graph of the given
+datalog program $P$ by checking all possible rule
+instantiations in $P^*$.
+One can check that $|P^*|$ could be the quadratic or cubic in the number of constants occurring in $P$.
+Recall the analysis of the parallel complexity of Algorithm~$\mathsf{A}_{bsc}$ and Algorithm~$\mathsf{A}_{\text{opt}}$.
+The number of constants is at most $|\textbf{I}|e$ where $e$ denotes the maximum arity of any predicate in $\textbf{I}$.
+Consider a datalog rule of the form `$R(x,y),A(y)\rightarrow B(x)$'.
+Since there are two variables in this rule, the number of all possible rule instantiations
+is $(|\textbf{I}|e)^2$.
 Similarly, for a datalog rule rewritten from an axiom of the form (R3) or (R4),
-the number of all possible rule instantiations is $|\textbf{IN}|^3$.
-It is no doubt that a plain implementation of Algorithm~$\mathsf{A}_{opt}$ would be delayed
+the number of all possible rule instantiations is $(|\textbf{I}|e)^3$.
+Undoubtedly, a plain implementation of Algorithm~$\mathsf{A}_{\text{opt}}$ would be slow
 when the target datalog program or ontology
@@
 of materialization graphs always cover a small part of $P^*$ with respect to the target datalog program $P$.
-Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{opt}$
+Thus, we consider reducing the computing space of Algorithm~$\mathsf{A}_{\text{opt}}$
 by narrowing down the scope of rule instantiations to be checked.
-Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{opt}$,
+Our strategy is to restrict that, \emph{in each iteration of Algorithm~$\mathsf{A}_{\text{opt}}$,
 each of the checked rule instantiations should involve at least one body atom that has been
@@
 form `$A(x)\rightarrow B(x)$' that corresponds to (T1). The above strategy requires that,
-in each iteration, Algorithm~$\mathsf{A}_{opt}$ can only check the rule instantiations
+in each iteration, Algorithm~$\mathsf{A}_{\text{opt}}$ can only check the rule instantiations
 of the form `$A(a)\rightarrow B(a)$' where $A(a)$ has been added to the constructed materialization
 graph $\mathcal{G}$. If there are $n$ atoms of the form $A(x)$ that have been added to $\mathcal{G}$,
-the number of all checked rule instantiations of the above rule is also $n$, instead of $|\textbf{IN}|$.
-This is because that, for each assertion $A(a)$,
+the number of all checked rule instantiations of the above rule is also $n$, instead of $(|\textbf{I}|e)$.
+This is because, for each assertion $A(a)$,
 the datalog rule `$A(x)\rightarrow B(x)$'
@@
 The cases of (R1) and (R2) can be analyzed similarly.
-We now consider the datalog rules that have two body atoms, i.e.,
-the datalog rules of the forms `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
+We now consider datalog rules that have two body atoms, i.e.,
+datalog rules of the form `$R(x,y),A(y)\rightarrow B(x)$' (see (T3)),
 `$A_1(x),A_2(x)\rightarrow B(x)$' (see (T2)) and `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$' (see (R3) and (R4)).
-We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{opt}$,
+We require that, for each rule instantiation of these rules checked by Algorithm~$\mathsf{A}_{\text{opt}}$,
 at least one body atom has been added to the constructed materialization
-graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{opt}$,
+graph $\mathcal{G}$; thus, it can be checked that, in each iteration of Algorithm~$\mathsf{A}_{\text{opt}}$,
 the number of checked rule instantiations
-is at most $k|\textbf{IN}|$ where $k$ is the number of atoms that have been
+is at most $k(|\textbf{I}|e)$ where $k$ is the number of atoms that have been
 added to $\mathcal{G}$.
@@
 Otherwise, the algorithm would
-perform as the same as Algorithm~$\mathsf{A}_{bsc}$, and thus, the
-optimizations used in Algorithm~$\mathsf{A}_{opt}$ cannot further work.
+perform as Algorithm~$\mathsf{A}_{bsc}$ and, thus, the
+optimizations used in Algorithm~$\mathsf{A}_{\text{opt}}$ cannot further work.
 
-\subsection{Further Optimizing Algorithm~$\mathsf{A}_{opt}$}
+\subsection{Further Optimizing Algorithm~$\mathsf{A}_{\text{opt}}$}
 
 We use the above method of narrowing down the scope of rule instantiations to
-modify Algorithm~$\mathsf{A}_{opt}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{prc}$.
+modify Algorithm~$\mathsf{A}_{\text{opt}}$ and obtain an algorithm variant Algorithm~$\mathsf{A}_{\text{prc}}$.
 Recall that,
-in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{opt}$
-checks all possible rule instantiations and computes a \texttt{rch} relation
+in each iteration of \ref{alg3:updateG}, Algorithm~$\mathsf{A}_{\text{opt}}$
+checks all possible rule instantiations and computes an \texttt{rch} relation
 and its transitive closure to determine the existence of SWD paths.
-We let Algorithm~$\mathsf{A}_{prc}$ conduct the same work with
+We let Algorithm~$\mathsf{A}_{\text{prc}}$ conduct the same work with
 narrowing down the scope of rule instantiations to be checked as well. This can be described
@@
 
-\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has inputs (1)
+\noindent\texttt{Algorithm~$\mathsf{PRC}$}. This algorithm has as inputs (1)
 a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$
@@
 (2) a (partial) materialization graph $\mathcal{G}=\langle V,E\rangle$ that is constructed from $P$.
-This algorithm outputs a \texttt{rch} relation $S_{\textit{\tiny rch}}$ that
+This algorithm outputs an \texttt{rch} relation $S_{\!\textit{\tiny rch}}$ that
 is computed as follows:
@@
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A(a)\rightarrow B(a)\in P^*$, $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in V$;
+\item add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\!\tiny rch}}$ where $A(a)\rightarrow B(a)\in P^*$, $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in V$;
 
-\item add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\tiny rch}}$ where $R(a,b),A(b)\rightarrow B(a)\in P^*$, $\exists R.A\sqsubseteq B\in\mathcal{T}$ and $R(a,b)\in V$;
+\item add \texttt{rch}$(A(b),B(a))$ to $S_{\textit{\!\tiny rch}}$ where $R(a,b),A(b)\rightarrow B(a)\in P^*$, $\exists R.A\sqsubseteq B\in\mathcal{T}$ and $R(a,b)\in V$;
 
-\item add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
+\item add \texttt{rch}$(A_2(a),B(a))$ to $S_{\textit{\!\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
     $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$ and $A_1(a)\in V$;
 
-\item add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
+\item add \texttt{rch}$(A_1(a),B(a))$ to $S_{\textit{\!\tiny rch}}$ where $A_1(a),A_2(a)\rightarrow B(a)\in P^*$,
     $A_1\sqcap A_2\sqsubseteq B\in\mathcal{T}$ and $A_2(a)\in V$;
 
-\item add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\tiny rch}}$ where $R(a,b)\rightarrow S(a,b)\in P^*$,
+\item add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\!\tiny rch}}$ where $R(a,b)\rightarrow S(a,b)\in P^*$,
     $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in V$;
 
-\item add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\tiny rch}}$ where $R(a,b)\rightarrow S(b,a)\in P^*$,
+\item add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\!\tiny rch}}$ where $R(a,b)\rightarrow S(b,a)\in P^*$,
     $\mathcal{O}\models R\sqsubseteq_* S^-$ and $R(a,b)\in V$;
 
-\item add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$,
+\item add \texttt{rch}$(R_2(b,c),R_3(a,c))$ to $S_{\textit{\!\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$,
     $R_1\circ R_2\sqsubseteq R_3\in\mathcal{R}$ (the case
-    where $R_1\equiv R_2\equiv R_3$ is also involved) and $R_1(a,b)\in V$;
+    where $R_1\equiv R_2\equiv R_3$ is also included) and $R_1(a,b)\in V$;
 
-\item add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$,
+\item add \texttt{rch}$(R_1(a,b)$, $R_3(a,c))$ to $S_{\textit{\!\tiny rch}}$ where $R_1(a,b),R_2(b,c)\rightarrow R_3(a,c)\in P^*$,
     $R_1\circ R_2\sqsubseteq R_3\in\mathcal{R}$ and $R_2(b,c)\in V$.\hfill$\Box$
@@
 
-Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{opt}$
-by replacing the step \ref{rch} of Algorithm~$\mathsf{OPT}$
-to Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{prc}$
-is thus given as follows:\\
+Based on Algorithm~$\mathsf{PRC}$, we modify Algorithm~$\mathsf{A}_{\text{opt}}$
+by replacing Step~\ref{rch} of Algorithm~$\mathsf{OPT}$
+with Algorithm~$\mathsf{PRC}$. Algorithm~$\mathsf{A}_{\text{prc}}$
+is, thus, given as follows:\\
 
-\noindent\texttt{Algorithm~$\mathsf{A}_{prc}$}. Given
+\noindent\texttt{Algorithm~$\mathsf{A}_{\text{prc}}$}. Given
 a DHL$(\circ)$ ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ and its
@@
 \item Add all facts in $\textbf{I}$ to $\mathcal{G}$.\label{alg4:addFacts}
-\item Compute $S_{\textit{\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an NC
+\item Compute $S_{\textit{\!\tiny rch}}$ by performing Algorithm~$\mathsf{PRC}$; use an \texttt{NC}
     algorithm to compute the transitive closure $S^*_{\textit{\tiny rch}}$ (see \ref{transClos} in Algorithm~$\mathsf{OPT}$);
@@
 \begin{theorem}\label{theorem:aprc}
-For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
+For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{\text{prc}}$ halts and outputs
 a materialization graph of $\mathcal{O}$.
@@
 
-The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{prc}$.
-We next use an example to show how Algorithm~$\mathsf{A}_{prc}$ handles
+The above theorem is given to show the correctness of Algorithm~$\mathsf{A}_{\text{prc}}$.
+Since Algorithm~$\mathsf{A}_{\text{prc}}$ is almost identical with Algorithm~$\mathsf{A}_{\text{opt}}$,
+it has the same upper bound of the computing time, i.e., $c_1+\ell'c_3 + \ell'c_4\log(|\textbf{I}|e) +\ell'c_5\log^2(|\textbf{I}|e)$,
+where $\ell'$ denotes the number of iterations of \ref{alg4:updateG}, and the symbols
+$c_1, c_3, c_4, c_5$ have the same meanings as those in the analysis of Algorithm~$\mathsf{A}_{\text{opt}}$.
+The difference between the two algorithms is that Algorithm~$\mathsf{A}_{\text{prc}}$
+considers a smaller scope of rule instantiations. This gives rise to smaller sizes of
+the relation $S_{\textit{\!\tiny rch}}$. Based on the above discussion and Algorithm~$\mathsf{PRC}$,
+the size of relation $S_{\textit{\!\tiny rch}}$ is bounded by
+$h(|\textbf{I}|e)$ (where $h$
+denotes the number of nodes that have been added to the graph), while
+the size of the relation $S_{\textit{\!\tiny rch}}$ as computed by Algorithm~$\mathsf{A}_{\text{opt}}$
+is at most $p^2(|\textbf{I}|e)^{2w}$.
+
+We next use an example to show how Algorithm~$\mathsf{A}_{\text{prc}}$ handles
 DHL$(\circ)$ materialization.
@@
 \begin{example}\label{exp:prc}
-Consider performing Algorithm~$\mathsf{A}_{prc}$ on the ontology
-$\mathcal{O}_{ex_1}$ in Example~\ref{exp:mg}. Note that the individual
-set \textbf{IN}$=\{a_1,...,a_k,b\}$ where $k+1$ individuals are involved.
-Initially, Algorithm~$\mathsf{A}_{prc}$ adds
+Consider performing Algorithm~$\mathsf{A}_{\text{prc}}$ on the ontology
+$\mathcal{O}_{ex_1}$ of Example~\ref{exp:mg}. Note that the individual
+set \textbf{IN} is $\{a_1,...,a_k,b\}$, i.e., $k+1$ individuals are involved.
+Initially, Algorithm~$\mathsf{A}_{\text{prc}}$ adds
 all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
 result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
-\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{prc}$ computes $S_{\textit{\tiny rch}}$ first.
-According to Algorithm~$\mathsf{PRC}$, for each atom of the form $S(a_i,a_{i-1})$ ($2\leq i\leq k$)
-and $\forall o\in$\textbf{IN},
+\ref{alg4:updateG}, Algorithm~$\mathsf{A}_{\text{prc}}$ computes $S_{\textit{\!\tiny rch}}$ first.
+According to Algorithm~$\mathsf{PRC}$, for each atom of the form
+$S(a_i,a_{i-1})$, $2\leq i\leq k$,
+and $\forall o\in \mbox{\textbf{IN}}$,
 an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
-Algorithm~$\mathsf{A}_{prc}$ checks that all atoms of the form $R(a_i,b)$ ($2\leq i\leq k$)
+$S_{\textit{\!\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
+Algorithm~$\mathsf{A}_{\text{prc}}$ checks that all atoms of the form
+$R(a_i,b)$, $2\leq i\leq k$,
 have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
-In the second iteration of \ref{alg4:updateG}, since all atoms of the form $R(a_i,b)$ ($1\leq i\leq k$)
+In the second iteration of \ref{alg4:updateG}, since all atoms of the
+form $R(a_i,b)$, $1\leq i\leq k$,
 have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
 are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$ ($1\leq i\leq k$) are finally added to $\mathcal{G}_{ex_1}$
-by Algorithm~$\mathsf{A}_{prc}$.
+atoms of the form $A(a_i)$, $1\leq i\leq k$, are finally added to $\mathcal{G}_{ex_1}$
+by Algorithm~$\mathsf{A}_{\text{prc}}$.
 \end{example}
 
-From the above example, one can find that Algorithm~$\mathsf{A}_{prc}$ terminates after two iterations
-of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{opt}$ (see Example~\ref{exp:opt}).
-We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{prc}$ also has an NC version when handling ontologies
-that follow the simple-concept and the simple-role restrictions.
-The correctness of this theorem is based on that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{prc}$
-does not influence the determination of the existence of SWD paths. The detailed analysis
-can be found in the proof.
+From the above example, one can find that Algorithm~$\mathsf{A}_{\text{prc}}$ terminates after two iterations
+of \ref{alg4:updateG}. This is the same as Algorithm~$\mathsf{A}_{\text{opt}}$ (see Example~\ref{exp:opt}).
+We use Theorem~\ref{theorem:aprcpt} to show that Algorithm~$\mathsf{A}_{\text{prc}}$ also has an \texttt{NC} version when handling ontologies
+that satisfy the simple-concept and the simple-role restrictions.
+The correctness of this theorem is based on the fact that the method of narrowing down the scope of rule instantiations in Algorithm~$\mathsf{A}_{\text{prc}}$
+does not influence the determination of the existence of SWD paths. A detailed analysis
+can be found in the proof in the appendix.
 
 \begin{theorem}\label{theorem:aprcpt}
-For any DHL$(\circ)$ ontology $\mathcal{O}$ that follows the simple-concept and the simple-role
-restrictions,
+For any DHL$(\circ)$ ontology $\mathcal{O}$ that satisfies the simple-concept and the simple-role
+restriction,
 there exists a poly-logarithmically bounded function $\psi$,
-such that Algorithm~$\mathsf{A}_{prc}^{\psi}$ outputs
+such that Algorithm~$\mathsf{A}_{\text{prc}}^{\psi}$ outputs
 a materialization graph of $\mathcal{O}$.

### 2018-01-31 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
Finished the proof-reading of the optimized algorithm section

@@
 e.g., \texttt{rch}$(v_1,v_2)$ means that $v_2$ is reachable from $v_1$.
-In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{\text{bsc}}$, we further compute a \texttt{rch}
-relation (denoted by $S_{\textit{\tiny rch}}$) by performing the following process:
+In each iteration of \ref{alg1:updateG} in Algorithm~$\mathsf{A}_{\text{bsc}}$, we further compute as \texttt{rch}
+relation (denoted by $S_{\textit{\!\tiny rch}}$) by performing the following process:
 
@@
 \begin{enumerate}[leftmargin=0ex]
-\item \emph{if the all body atoms $B_1,\ldots,B_n$ have been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),\ldots,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\tiny rch}}$};
+\item \emph{if the all body atoms $B_1,\ldots,B_n$ have been added to $\mathcal{G}$, put \texttt{rch}$(B_1,H),\ldots,$ \texttt{rch}$(B_n,H)$ in $S_{\textit{\!\tiny rch}}$};
 \item \emph{if $B_i$ is the only node in the body that has not been added to $\mathcal{G}$,
-    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\tiny rch}}$}.\hfill$\Box$
+    put \texttt{rch}$(B_i,H)$ in $S_{\textit{\!\tiny rch}}$}.\hfill$\Box$
 \end{enumerate}

### 2018-02-01 parallel-tractability-J-v9/background.tex
worked on experimental section, fixed table layout and captions

@@
 For ease of discussion, we focus on the \emph{simple forms} of axioms shown
-in the left column of Table~1. These simple forms can be obtained by using
+in the left column of Table~\ref{tab:dhl}. These simple forms can be obtained by using
 well-known \emph{structural transformation} techniques \cite{KrotzschRH07,Kazakov09}.
@@
 \begin{table}
-\begin{center}
-\begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
+\centering
+\caption{Axioms and corresponding datalog rules}
+\begin{tabular}{l >{\hspace*{12mm}}c<{\hspace*{12mm}} >{\hspace*{12mm}}c<{\hspace*{12mm}}}
 \hline
-&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
+& Axioms & Datalog Rules\\
 \hline
@@
 \label{tab:dhl}
-\end{center}
 \end{table}
@@
 expressed in DHL, DHL($\circ$), DL-Lite$_{\text{core}}$ or DL-Lite$_{\mathcal{R}}$ can be transformed into a datalog program
-(see the corresponding rules in the right column of Table~1).
+(see the corresponding rules in the right column of Table~\ref{tab:dhl}).
 Note that an axiom of form (T4) $A\sqsubseteq\exists R$ should be

### 2018-02-01 parallel-tractability-J-v9/evaluation.tex
worked on experimental section, fixed table layout and captions

@@
 and investigate the usability of the results proposed above.
-In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{prc}$
+In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{\text{prc}}$
 and compare it to the reasoning system RDFox.
@@
 in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
+popular benchmarks using our results. For some benchmarks, the ontologies have TBoxes with a simple
+structure. These ontologies can be expressed in RDFS
 and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
@@
 The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
+(\emph{The ISLab Instance Matching Benchmark}) satisfies the simple-concept restriction.
 
@@
 In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
+the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$.
 
@@
 In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
+YAGO \emph{model} also allows for stating the \emph{transitivity} and \emph{acyclicity} of a property.
 Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
+However, \citet{SuchanekKW08} specify a more efficient set of materialization rules.
 All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
@@
 Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
+and the Oxford ontology library.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
 All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
+Among these ontologies, $111$ belong to $\mathcal{D}_{\textit{\text{dhl}}}$
+or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$; $21$ of the DHL ontologies contain
+conjunctions and satisfy the simple-concept restriction.
 The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
 appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
+We also find two DHL($\circ$) ontologies and both satisfy the simple-role restriction.
 
 The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
+is naturally satisfied in many real applications of different fields.
 From the perspective of developers who work on building their own ontologies,
@@
 
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
+\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{\text{prc}}$}
 
 We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. In this part, we evaluate ParallelDHL and
+based on Algorithm~$\mathsf{A}_{\text{prc}}$. In this part, we evaluate ParallelDHL and
 compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
@@
 four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them do not follow the simple-concept or the simple-role
+the rest of them does not satisfy the simple-concept or the simple-role
 restriction.
-The eight ontologies are real ontologies and are applied in different fields.
-The basic information of these ontologies
-is summarized in Table~2 (we use $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-to denote the complementary set of $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$).
+The chosen eight ontologies are real ontologies and are applied in different fields.
+The basic information for these ontologies
+is summarized in Table~\ref{tab:info}.
 
-\begin{center}
-\begin{tabular}{ccrrc}
-\multicolumn{5}{c}{\textbf{Table 2: The Information of the Test Ontologies}}\\
+\begin{table}[htb]
+\centering
+\caption{Information about the test ontologies, where
+  $|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring
+  in the ontology, $|\mathcal{A}|$ denotes the number of assertions
+  in the ABox and the last column states whether the
+  ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$}
+\begin{tabular}{>{\hspace*{5mm}}ccrrc<{\hspace*{5mm}}}
 \hline
-~~~~~\textbf{Ontology Name}~~~~~&~~~~~\textbf{Field}~~~~~&~~~~~$|\mathcal{T}|+|\mathcal{R}|^a$&~~~~~$|\mathcal{A}|^b$&~~~~~\textbf{Type}$^c$~~~~~\\
+\textbf{Ontology Name} & \textbf{Field} &
+                                          $|\mathcal{T}|+|\mathcal{R}|$
+  & $|\mathcal{A}|$ & $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
 \hline
 
-Finance&finance&1,934&6,152&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
+Finance&finance&1,934&6,152&no\\
 
-Molecule&chemistry&43&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
+Molecule&chemistry&43&0&no\\
 
-GrossAnatomy&anatomy&2,276&13&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
+GrossAnatomy&anatomy&2,276&13&no\\
 
-Skeleton&medicine&815&0&$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$\\
+Skeleton&medicine&815&0&no\\
 
@@
 
-ChemistryPrimitive&chemistry&167&0&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
+ChemistryPrimitive&chemistry&167&0& yes\\
 
-FacebookOnto&social networking&185&28&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
+FacebookOnto&social networking&185&28& yes\\
 
-Mahabharata&literature&69&2,036&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
+Mahabharata&literature&69&2,036& yes\\
 
-Transportation&traffic&925&511&$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
+Transportation&traffic&925&511& yes\\
 
 \hline
-\multicolumn{5}{l}{$^a$ \footnotesize$|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring in the ontology.}\\
-
-\multicolumn{5}{l}{$^b$ \footnotesize$|\mathcal{A}|$ denotes the number of assertions occurring in the ABox.}\\
-
-\multicolumn{5}{l}{$^c$ \footnotesize$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$)
-means that the ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ (resp., $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$).}\\
 \end{tabular}
 \label{tab:info}
-\end{center}
+\end{table}
 
-For the purpose of comparability in the ABox scale, we consider generating ABox assertions
-to a limited number with respect to the TBoxes and RBoxes of the test ontologies.
-The generation method is based on the work \cite{Elhaik98} where a benchmark generator is proposed
-for evaluating ontology-based systems.
-For each test ontology, e.g., the ontology Finance, we generate 5 new ontologies with different ABoxes;
-these ontologies are denoted by Finance-$i$ ($i\in\{1,2,3,4,5\}$) where $i$ represents that the number
-of assertions in the ABox of Finance-$i$ reaches to $i\times100,000$;
-we also use ``Finance series" to denote the five generated ontologies
-for the ontology Finance. The other test ontologies are processed similarly.
+In order to compare ABoxes of a similar scale, we generate a limited
+number of ABox assertions with respect to the TBoxes and RBoxes for
+the test ontologies using the generation method proposed by
+\citet{Elhaik98}.  For each test ontology, e.g., the Finance ontology,
+we generate 5 new ontologies with different ABoxes, denoted
+Finance-$i$ ($i\in\{1,2,3,4,5\}$). The index $i$ indicates that the
+number of ABox assertions of Finance-$i$ is $i\times100,000$. We also
+use the term ``Finance series" to denote the five generated ontologies
+for the Finance ontology. The other test ontologies are processed
+similarly.
+
+\begin{table}[htb]
+\centering
+\caption{Analysis of the reasoning results, where the \emph{minimal time
+  ratio} is the minimal reasoning time
+of ParallelDHL divided by the minimal reasoning time of RDFox and the
+\emph{average speedup} is $1/4 (T_1/T_2 + T_2/T_4 + T_4/T_6 + T_6/T_8)$,
+ where $T_i$ is the reasoning time with $i$ threads allocated}
+{\setlength{\tabcolsep}{6mm}
+\begin{tabular}{crrrrr}
+\hline
+series & 1 & 2 & 3 & 4 & 5\\
+\hline
+\multicolumn{6}{c}{minimal time ratio}\\%[-1mm]
+% \multicolumn{6}{c}{{\footnotesize minimal reasoning time
+% of ParallelDHL/minimal reasoning time of RDFox}}\\
+\hline
+Finance&0.54&1.36&0.94&0.99&1.70\\
+Molecule&0.94&0.79&0.96&0.98&1.07\\
+GrossAnatomy&0.65&0.48&0.84&0.77&0.83\\
+Skeleton&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
+ChemistryPrimitive&1.29&1.54&1.68&1.14&0.93\\
+FacebookOnto&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
+Mahabharata&1.19&1.19&0.99&0.84&0.89\\
+Transportation&0.24&0.52&0.51&0.65&0.49\\
+\hline
+\multicolumn{6}{c}{average speedup of ParallelDHL with increasing
+  number of threads}\\%[-1mm]
+% \multicolumn{6}{c}{{\footnotesize
+%   $1/4 (T_1/T_2 + T_2/T_4 + T_4/T_6 + T_6/T_8)$,
+%  where $T_i$ is the reasoning time with $i$ threads allocated}}\\
+\hline
+Finance&3.06&1.88&2.29&2.95&2.73\\
+Molecule&1.04&1.24&1.13&1.07&1.05\\
+GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
+Skeleton&3.28&1.84&1.65&1.74&1.96\\
+ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
+FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
+Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
+Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
+\hline
+\multicolumn{6}{c}{average speedup of RDFox with increasing
+  number of threads}\\%[-1mm]
+% \multicolumn{6}{c}{{\footnotesize
+%   $1/4 (T_1/T_2 + T_2/T_4 + T_4/T_6 + T_6/T_8)$,
+%  where $T_i$ is the reasoning time with $i$ threads allocated}}\\
+\hline
+Finance&1.01&1.04&1.13&1.11&1.19\\
+Molecule&0.90&1.03&0.95&1.01&0.99\\
+GrossAnatomy&0.87&0.99&0.94&0.96&0.98\\
+Skeleton&1.13&1.01&1.06&1.08&1.08\\
+ChemistryPrimitive&1.28&1.16&1.14&1.11&1.15\\
+FacebookOnto&1.22&1.08&1.07&1.09&1.09\\
+Mahabharata&1.24&1.07&1.13&1.10&1.12\\
+Transportation&1.14&1.04&1.03&1.08&1.11\\
+\hline
+\end{tabular}
+% \begin{tabular}{crrrrr}
+% \hline
+% series & 1 & 2 & 3 & 4 & 5\\
+% \hline
+% &0.54&1.36&0.94&0.99&1.70\\
+% Finance&3.06&1.88&2.29&2.95&2.73\\
+% &1.01&1.04&1.13&1.11&1.19\\
+% \hline
+% &0.94&0.79&0.96&0.98&1.07\\
+% Molecule&1.04&1.24&1.13&1.07&1.05\\
+% &0.90&1.03&0.95&1.01&0.99\\
+% \hline
+% &0.65&0.48&0.84&0.77&0.83\\
+% GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
+% &0.87&0.99&0.94&0.96&0.98\\
+% \hline
+% &1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
+% Skeleton&3.28&1.84&1.65&1.74&1.96\\
+% &1.13&1.01&1.06&1.08&1.08\\
+% \hline
+% &1.29&1.54&1.68&1.14&0.93\\
+% ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
+% &1.28&1.16&1.14&1.11&1.15\\
+% \hline
+% &\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
+% FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
+% &1.22&1.08&1.07&1.09&1.09\\
+% \hline
+% &1.19&1.19&0.99&0.84&0.89\\
+% Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
+% &1.24&1.07&1.13&1.10&1.12\\
+% \hline
+% &0.24&0.52&0.51&0.65&0.49\\
+% Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
+% &1.14&1.04&1.03&1.08&1.11\\
+% \hline
+% \end{tabular}
+}
+\label{tab:expresult}
+\end{table}
 
 \textbf{The Experimental Results}.
-We run ParallelDHL and RDFox over the above eight ontology series respectively.
+We evaluated ParallelDHL and RDFox over the above eight ontology series.
 The running environment is a DELL server with a
 memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads respectively)
-to ParallelDHL and RDFox in each experiment. The results of reasoning
+For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads, respectively)
+for ParallelDHL and RDFox in each experiment. The resulting reasoning
 times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
@@
 where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the values of reasoning time (millisecond per unit),
+the ordinate records the reasoning times (in milliseconds),
 and each of the five curves in different colors denotes the trend of reasoning time with the
@@
 
-We further process the collected data and fill the results in Table~3, where each cell corresponds
-to a test ontology (see the row label) and a new generated ABox (distinguished by the column labels);
-the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-of ParallelDHL divided by the minimal reasoning time of RDFox;
-(2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-(3) \emph{the average speedup of RDFox}.
+% We further process the collected data and fill the results in Table~\ref{tab:expresult}, where each cell corresponds
+% to a test ontology (see the row label) and a newly generated ABox (distinguished by the column labels);
+% the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
+% of ParallelDHL divided by the minimal reasoning time of RDFox;
+% (2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
+% the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
+% (3) \emph{the average speedup of RDFox}.
+% The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
+% The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
+% Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
+% threads allocated.
+% In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~\ref{tab:expresult}.
+
+We further process the collected data and fill the results in Table~\ref{tab:expresult}, where each cell corresponds
+to a test ontology (see the row label) and a newly generated ABox
+(distinguished by the series column labels). 
 The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
@@
 threads allocated.
-In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~3.
+In the following, we give a detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~\ref{tab:expresult}.
 
-\textbf{The Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto}, the ontologies belonging to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$
-may not be parallelly tractable in terms of materialization. In other words,
+\textbf{Analysis of the Experimental Results}.
+According to the theoretical results in Section~\ref{sec:ptonto},
+materialization of the
+ontologies not belonging to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
+(Finance, Molecule, GrossAnatomy and Skeleton)
+may not be tractable in parallel. In other words,
 parallel techniques may not work for improving the efficiency of materialization.
@@
 This is also supported by the results of the average speedups.
-From Table~3, we can see that the average speedups of ParallelDHL and RDFox
+From Table~\ref{tab:expresult}, we can see that the average speedups of ParallelDHL and RDFox
 for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
@@
 ParallelDHL is a competitive system.
-From Table~3, we can find that most of the minimal time ratios are close to 1.
+From Table~\ref{tab:expresult}, we can find that most of the minimal time ratios are close to 1.
 This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
@@
 The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{opt}$ (see Section~\ref{sec:ptclass}).
+the optimizations designed for Algorithm~$\mathsf{A}_{\text{opt}}$ (see Section~\ref{sec:ptclass}).
 The higher average speedups of PrallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{opt}$.
+used in Algorithm~$\mathsf{A}_{\text{opt}}$.
 One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
@@
 
-\begin{center}
-\begin{tabular}{crrrrr}
-\multicolumn{6}{c}{\textbf{Table 3: The Analysis of Reasoning Results}}\\
-\hline
-&~~~~~~~~~~~~~~~1&~~~~~~~~~~~~~~~2&~~~~~~~~~~~~~~~3&~~~~~~~~~~~~~~~4&~~~~~~~~~~~~~~~5\\
-\hline
-&0.54&1.36&0.94&0.99&1.70\\
-Finance&3.06&1.88&2.29&2.95&2.73\\
-&1.01&1.04&1.13&1.11&1.19\\
-\hline
-&0.94&0.79&0.96&0.98&1.07\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-&0.90&1.03&0.95&1.01&0.99\\
-\hline
-&0.65&0.48&0.84&0.77&0.83\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-&0.87&0.99&0.94&0.96&0.98\\
-\hline
-&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-&1.13&1.01&1.06&1.08&1.08\\
-\hline
-&1.29&1.54&1.68&1.14&0.93\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-&1.28&1.16&1.14&1.11&1.15\\
-\hline
-&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-&1.22&1.08&1.07&1.09&1.09\\
-\hline
-&1.19&1.19&0.99&0.84&0.89\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-&1.24&1.07&1.13&1.10&1.12\\
-\hline
-&0.24&0.52&0.51&0.65&0.49\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-\label{tab:expresult}
-\end{center}
+\begin{figure}[htbp]
+  \centering
+  \begin{minipage}{.24\textwidth}
+    \includegraphics[width=\textwidth]{experimentalResults/1-Finance-simple}
+    \subcaption{lg1\label{fig:financepdhl}} 
+  \end{minipage}
+  \begin{minipage}{.24\textwidth}
+    \includegraphics[width=\textwidth]{experimentalResults/2-molecule-simple}
+    \subcaption{lg3\label{fig:moleculepdhl}}
+  \end{minipage}
+  \begin{minipage}{.24\textwidth}
+    \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-simple}
+    \subcaption{lg5\label{fig:grossanatomypdhl}}
+  \end{minipage}
+  \begin{minipage}{.24\textwidth}
+    \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-simple}
+    \subcaption{lg7\label{fig:skeletonpdhl}}
+  \end{minipage}
+  \caption{Materialization time in ms for ParallelDHL for the
+    ontologies that do not belonging to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.~\label{fig:eval}}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \begin{minipage}{.5\textwidth}
+    \includegraphics[width=\textwidth]{experimentalResults/1-Finance-rdfox}
+    \subcaption{lg2\label{fig:financerdfox}} 
+  \end{minipage}
+  \begin{minipage}{.5\textwidth}
+    \includegraphics[width=\textwidth]{experimentalResults/2-molecule-rdfox}
+    \subcaption{lg4\label{fig:moleculerdfox}}
+  \end{minipage}\\
+  \begin{minipage}{.5\textwidth}
+    \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-rdfox}
+    \subcaption{lg6\label{fig:grossanatomyrdfox}}
+  \end{minipage}
+  \begin{minipage}{.5\textwidth}
+    \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-rdfox}
+    \subcaption{lg8\label{fig:skeletonrdfox}}
+  \end{minipage}
+  \caption{Materialization time in ms for RDFox for the
+    ontologies that do not belonging to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.~\label{fig:eval}}
+\end{figure}
 

### 2018-02-01 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
worked on experimental section, fixed table layout and captions

@@
 for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{\text{opt}}$. 1We show that, for any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
+based on Algorithm~$\mathsf{A}_{\text{opt}}$. We show that, for any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
 there exists a poly-logarithmically bounded function $\psi$
@@
 \begin{table}
-\begin{center}
+\centering
+\caption{RDFS statements and the corresponding DL axioms}
+{\setlength{\tabcolsep}{6mm}
 \begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table~\ref{tab:rdfs}: The RDFS statements and the corresponding DL axioms}}\\
 \hline
-&~~~~~~~~~~~~~RDFS statements~~~~~~~~~~~~~&~~~~~~~~~~~~~~Axiom~~~~~~~~~~~~~~\\
+& RDFS statements & Axiom\\
 \hline
@@
 \hline
-\end{tabular}
+\end{tabular}}
 \label{tab:rdfs}
-\end{center}
 \end{table}

### 2018-02-02 parallel-tractability-J-v9/background.tex
rewrote the analysis for LUBM and YAGO

--- 2018-01-31 parallel-tractability-J-v9/background.tex
@@
 \begin{tabular}{lcc}
-\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
+\multicolumn{3}{c}{\textbf{Table~\ref{tab:dhl}: Axioms and corresponding datalog rules}}\\
 \hline

### 2018-02-02 parallel-tractability-J-v9/evaluation.tex
rewrote the analysis for LUBM and YAGO

--- 2018-01-29 parallel-tractability-J-v9/evaluation.tex
@@
 
-\subsection{Practical Usability of the Theoretical Results}
+\subsection{The Parallel Tractability of the LUBM Datasets and YAGO Ontologies}
 
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
+In this part, we analyze two popular datasets, LUBM and YAGO, and show the relations
+between these two datasets and the theoretical results of the parallel tractability.
 
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
+\textbf{LUBM}. In the Semantic Web community, LUBM
+(The Lehigh University Benchmark) is proposed to
 facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results and find that
-the ontologies used in some benchmarks have simple
-structured TBoxes that can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) follows the simple-concept restriction.
+in a standard and systematic way.
+In the latest version of LUBM,\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
+the core ontology contains 48 classes and 32 properties
+that are used to describe the departments and the staffs in
+universities. By setting different numbers of universities to an ontology-generating
+program, users can get datasets of any size based on the core ontology.
 
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
+In the core ontology of LUBM, the statements about properties, such as inverse property statements,
+can be rewritten into the datalog rules of the form (R1), (R2) and (R3) in Table~\ref{tab:dhl}.
+Most of the statements about classes can be rewritten into the datalog rules of the form (T1) and (T3)
+in Table~\ref{tab:dhl}. Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
 which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
+the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$ ($\tau$),
+where a free variable $y$ is introduced. This kind of axiom is a general case of (T4) in Table~\ref{tab:dhl}
+for which $A$ is actually replaced by the top concept $\top$.
+Similarly to how we handle (T4), we can also eliminate the free variable $y$
+in rule $\tau$ via Skolemization, i.e., replacing the variable $y$ by a new constant $o_R^{A,B}$.
+In this way, rule $\tau$ can be rewritten into $A(x)\rightarrow\exists R(x,o_R^{A,B})\wedge B(o_R^{A,B})$.
+If we only focus on the materialization task, the rewriting approach via Skolemization guarantees the
+completeness and correctness \cite{GrauHKKMMW13}.
+On the other hand, rule $\tau$ is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
 In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
+the materialization of LUBM datasets can be handled by Algorithm~$\mathsf{A}_{opt}^{\psi}$.
 
 \textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
+is constructed from Wikipedia and WordNet. The latest version
 YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
@@
 and contains more than 120 million facts about these entities.
+
 In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, in \cite{SuchanekKW08}, a group of materialization rules
-is specified, which is more efficient.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
+a YAGO-style language, called the \emph{YAGO model}, is proposed based on
+a slight extension of RDFS \cite{SuchanekKW08}. The YAGO model defines
+a set of properties: \texttt{domain, range, subClassOf, subRelationOf} and \texttt{type},
+and a set of classes: \texttt{entity, class, relation} and \texttt{acyclicTransitiveRelation}.
+The facts in the YAGO model are stated by triples, e.g., ($r_1,\texttt{subRelationOf},r_2$),
+which are similar to the RDFS statements.
+A group of rules for the reasoning over YAGO ontologies
+is specified as follows \cite{SuchanekKW08}:
+\begin{enumerate}[leftmargin=8ex,label=(\arabic*),ref=\arabic*]
+  \item ($r,\texttt{domain},c$),($x,r,y$)$\rightarrow$($x,\texttt{type},c$)\label{yago:r1}
+  \item ($r,\texttt{range},c$),($x,r,y$)$\rightarrow$($y,\texttt{type},c$)\label{yago:r2}
+  \item ($c_1,\texttt{subClassOf},c_2$),($x,\texttt{type},c_1$)$\rightarrow$($x,\texttt{type},c_2$)\label{yago:r3}
+  \item ($r_1,\texttt{subRelationOf},r_2$),($x,r_1,y$)$\rightarrow$($x,r_2,y$)\label{yago:r4}
+  \item ($r,\texttt{type},\texttt{acyclicTransitiveRelation}$),($x,r,y$),($y,r,z$)$\rightarrow$($x,r,z$)\label{yago:r5}
+\end{enumerate}
 
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ of them belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, and $21$ DHL ontologies contain
-conjunctions and follow the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies
-that follow the simple-role restriction.
+According to the semantics given to YAGO \cite{SuchanekKW08}, the built-in properties in YAGO,
+i.e., \texttt{domain, range, subClassOf, subRelationOf} and \texttt{type} act in the same
+way as the terms in RDFS statements of the form (1-5) in Table~\ref{tab:rdfs} respectively.
+Different from RDFS, YAGO also allows stating acyclic and transitive properties based on the
+class \texttt{acyclicTransitiveRelation}; further, any fact in some YAGO ontology cannot be
+described by blank nodes. On the other hand,
+by carefully observing the rules (\ref{yago:r1}-\ref{yago:r5}) for the reasoning over YAGO ontologies,
+one can check that these rules can be rewritten into the datalog rules (T3),\footnote{Both of Rule (\ref{yago:r1}) and
+Rule (\ref{yago:r2}) can be rewritten into (T3).} (T1), (R1) and (R3) in Table~\ref{tab:dhl} respectively.
+Further, DHL does not restrict any role to be acyclic.
+Based on the above analysis, any YAGO ontology can be expressed in DHL
+and satisfies the simple-class and the simple-role restrictions. We then have that
+for any well-constructed class of YAGO ontologies Algorithm~$\mathsf{A}_{opt}^{\psi}$
+can handle all of the ontologies in the class.
 
-The above investigation indicates that the simple-concept and the simple-role restrictions
-are allowed in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
+In addition to LUBM and YAGO, we further investigate different kinds of ontologies and datasets
+including benchmarks, real-world ontologies and datasets that can be expressed in ontology languages.
+These ontologies and datsets are collected from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
+Swoogle\footnote{http://swoogle.umbc.edu/} and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
+Based on the analysis of these ontologies, we found that, ignoring imports, many of them
+belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
+All of these investigated ontologies and the analysis results are available online.\footnote{https://github.com/quanzz/PT}
 

### 2018-02-02 parallel-tractability-J-v9/evaluation.tex
worked on experimental section, fixed table layout and captions

--- 2018-02-01 parallel-tractability-J-v9/evaluation.tex
@@
 
-\subsection{Practical Usability of the Theoretical Results}
+\subsection{The Parallel Tractability of the LUBM Datasets and YAGO Ontologies}
 
-In this part, we analyze different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and
-datasets that can be expressed in ontology languages.
-Based on the analysis of these datasets,
-we find that, ignoring imports, many of them
-belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
+In this part, we analyze two popular datasets, LUBM and YAGO, and show the relations
+between these two datasets and the theoretical results of the parallel tractability.
 
-\textbf{Benchmarks}. In the
-Semantic Web community, many benchmarks are proposed to
+\textbf{LUBM}. In the Semantic Web community, LUBM
+(The Lehigh University Benchmark) is proposed to
 facilitate the evaluation of ontology-based systems
-in a standard and systematic way. We investigate several
-popular benchmarks using our results. For some benchmarks, the ontologies have TBoxes with a simple
-structure. These ontologies can be expressed in RDFS
-and belong to $\mathcal{D}_{\textit{\text{dhl}}}$.
-These benchmarks include SIB\footnote{https://www.w3.org/wiki/Social$\underline{~}$Network$\underline{~}$Intelligence$\underline{~}$BenchMark}
-(\emph{Social Network Intelligence BenchMark}),
-BSBM\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}
-(\emph{Berlin SPARQL Benchmark}) and
-LODIB\footnote{http://wifo5-03.informatik.uni-mannheim.de/bizer/lodib/}
-(\emph{Linked Open Data Integration Benchmark}).
-The ontology used in IIMB\footnote{http://islab.di.unimi.it/iimb/}
-(\emph{The ISLab Instance Matching Benchmark}) satisfies the simple-concept restriction.
+in a standard and systematic way.
+In the latest version of LUBM,\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
+the core ontology contains 48 classes and 32 properties
+that are used to describe the departments and the staffs in
+universities. By setting different numbers of universities to an ontology-generating
+program, users can get datasets of any size based on the core ontology.
 
-In the latest version of LUBM\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-(The Lehigh University Benchmark),
-there are 48 classes and 32 properties.
-Statements about properties, such as inverse property statements,
-can be rewritten into datalog rules allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Most of the statements about classes can be rewritten into datalog rules that
-are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
+In the core ontology of LUBM, the statements about properties, such as inverse property statements,
+can be rewritten into the datalog rules of the form (R1), (R2) and (R3) in Table~\ref{tab:dhl}.
+Most of the statements about classes can be rewritten into the datalog rules of the form (T1) and (T3)
+in Table~\ref{tab:dhl}. Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
 which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$,
-where a new anonymous constant $y$ is introduced.
-This kind of rule is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-On the other hand, in some cases, this kind of rule can also be
-eliminated when taking a rewriting approach \cite{GrauHKKMMW13}.
+the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$ ($\tau$),
+where a free variable $y$ is introduced. This kind of axiom is a general case of (T4) in Table~\ref{tab:dhl}
+for which $A$ is actually replaced by the top concept $\top$.
+Similarly to how we handle (T4), we can also eliminate the free variable $y$
+in rule $\tau$ via Skolemization, i.e., replacing the variable $y$ by a new constant $o_R^{A,B}$.
+In this way, rule $\tau$ can be rewritten into $A(x)\rightarrow\exists R(x,o_R^{A,B})\wedge B(o_R^{A,B})$.
+If we only focus on the materialization task, the rewriting approach via Skolemization guarantees the
+completeness and correctness \cite{GrauHKKMMW13}.
+On the other hand, rule $\tau$ is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
 In summary, if the above kind of rule is not considered,
@@
 \textbf{YAGO}. The knowledge base YAGO\footnote{http://www.mpi-inf.mpg.de/home/}
-is constructed from Wikipedia and WordNet and the latest version
+is constructed from Wikipedia and WordNet. The latest version
 YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
@@
 and contains more than 120 million facts about these entities.
+
 In order to balance the expressiveness and computing efficiency,
-a YAGO-style language, called YAGO \emph{model}, is proposed based on
-a slight extension of RDFS \cite{SuchanekKW08}.
-In addition to the expressiveness of RDFS,
-YAGO \emph{model} also allows for stating the \emph{transitivity} and \emph{acyclicity} of a property.
-Making full use of RDFS features cannot lead to parallel tractability \cite{Horst05}.
-However, \citet{SuchanekKW08} specify a more efficient set of materialization rules.
-All of these rules are allowed in $\mathcal{D}_{\textit{\text{dhl}}}$.
-Thus, we have that a well-constructed YAGO dataset belongs to $\mathcal{D}_{\textit{\text{dhl}}}$.
+a YAGO-style language, called the \emph{YAGO model}, is proposed based on
+a slight extension of RDFS \cite{SuchanekKW08}. The YAGO model defines
+a set of properties: \texttt{domain, range, subClassOf, subRelationOf} and \texttt{type},
+and a set of classes: \texttt{entity, class, relation} and \texttt{acyclicTransitiveRelation}.
+The facts in the YAGO model are stated by triples, e.g., ($r_1,\texttt{subRelationOf},r_2$),
+which are similar to the RDFS statements.
+A group of rules for the reasoning over YAGO ontologies
+is specified as follows \cite{SuchanekKW08}:
+\begin{enumerate}[leftmargin=8ex,label=(\arabic*),ref=\arabic*]
+  \item ($r,\texttt{domain},c$),($x,r,y$)$\rightarrow$($x,\texttt{type},c$)\label{yago:r1}
+  \item ($r,\texttt{range},c$),($x,r,y$)$\rightarrow$($y,\texttt{type},c$)\label{yago:r2}
+  \item ($c_1,\texttt{subClassOf},c_2$),($x,\texttt{type},c_1$)$\rightarrow$($x,\texttt{type},c_2$)\label{yago:r3}
+  \item ($r_1,\texttt{subRelationOf},r_2$),($x,r_1,y$)$\rightarrow$($x,r_2,y$)\label{yago:r4}
+  \item ($r,\texttt{type},\texttt{acyclicTransitiveRelation}$),($x,r,y$),($y,r,z$)$\rightarrow$($x,r,z$)\label{yago:r5}
+\end{enumerate}
 
-\textbf{Real Ontologies}. We investigated
-$151$ ontologies that cover many domains
-like biomedicine, geography, etc.
-These ontologies are collected
-from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/}
-and the Oxford ontology library.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
-All ontologies are available online.\footnote{https://github.com/quanzz/PT}
-Among these ontologies, $111$ belong to $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$; $21$ of the DHL ontologies contain
-conjunctions and satisfy the simple-concept restriction.
-The remaining ontologies have simple TBoxes, i.e., no conjunction ($A_1\sqcap A_2$)
-appears in these ontologies.
-We also find two DHL($\circ$) ontologies and both satisfy the simple-role restriction.
+According to the semantics given to YAGO \cite{SuchanekKW08}, the built-in properties in YAGO,
+i.e., \texttt{domain, range, subClassOf, subRelationOf} and \texttt{type} act in the same
+way as the terms in RDFS statements of the form (1-5) in Table~\ref{tab:rdfs} respectively.
+Different from RDFS, YAGO also allows stating acyclic and transitive properties based on the
+class \texttt{acyclicTransitiveRelation}; further, any fact in some YAGO ontology cannot be
+described by blank nodes. On the other hand,
+by carefully observing the rules (\ref{yago:r1}-\ref{yago:r5}) for the reasoning over YAGO ontologies,
+one can check that these rules can be rewritten into the datalog rules (T3),\footnote{Both of Rule (\ref{yago:r1}) and
+Rule (\ref{yago:r2}) can be rewritten into (T3).} (T1), (R1) and (R3) in Table~\ref{tab:dhl} respectively.
+Further, DHL does not restrict any role to be acyclic.
+Based on the above analysis, any YAGO ontology can be expressed in DHL
+and satisfies the simple-class and the simple-role restrictions. We then have that
+for any well-constructed class of YAGO ontologies Algorithm~$\mathsf{A}_{opt}^{\psi}$
+can handle all of the ontologies in the class.
 
-The above investigation indicates that the simple-concept and the simple-role restrictions
-is naturally satisfied in many real applications of different fields.
-From the perspective of developers who work on building their own ontologies,
-they can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$ and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to achieve the guarantee of the parallel tractability.
+In addition to LUBM and YAGO, we further investigate different kinds of ontologies and datasets
+including benchmarks, real-world ontologies and datasets that can be expressed in ontology languages.
+These ontologies and datsets are collected from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
+Swoogle\footnote{http://swoogle.umbc.edu/} and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
+Based on the analysis of these ontologies, we found that, ignoring imports, many of them
+belong to $\mathcal{D}_{\textit{\text{dhl}}}$ or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
+All of these investigated ontologies and the analysis results are available online.\footnote{https://github.com/quanzz/PT}
 
@@
   \centering
-  \begin{minipage}{.24\textwidth}
+  \begin{minipage}{.45\textwidth}
     \includegraphics[width=\textwidth]{experimentalResults/1-Finance-simple}
@@
   \end{minipage}
-  \begin{minipage}{.24\textwidth}
+  \begin{minipage}{.45\textwidth}
     \includegraphics[width=\textwidth]{experimentalResults/2-molecule-simple}
     \subcaption{lg3\label{fig:moleculepdhl}}
-  \end{minipage}
-  \begin{minipage}{.24\textwidth}
+  \end{minipage}\\
+  \begin{minipage}{.45\textwidth}
     \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-simple}
@@
   \end{minipage}
-  \begin{minipage}{.24\textwidth}
+  \begin{minipage}{.45\textwidth}
     \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-simple}
@@
   \centering
-  \begin{minipage}{.5\textwidth}
+  \begin{minipage}{.45\textwidth}
     \includegraphics[width=\textwidth]{experimentalResults/1-Finance-rdfox}
@@
   \end{minipage}
-  \begin{minipage}{.5\textwidth}
+  \begin{minipage}{.45\textwidth}
     \includegraphics[width=\textwidth]{experimentalResults/2-molecule-rdfox}
@@
   \end{minipage}\\
-  \begin{minipage}{.5\textwidth}
+  \begin{minipage}{.45\textwidth}
     \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-rdfox}
@@
   \end{minipage}
-  \begin{minipage}{.5\textwidth}
+  \begin{minipage}{.45\textwidth}
     \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-rdfox}

### 2018-02-02 parallel-tractability-J-v9/evaluation.tex
eval section

@@
 In this part, we analyze two popular datasets, LUBM and YAGO, and show the relations
-between these two datasets and the theoretical results of the parallel tractability.
+between these two datasets and the theoretical results regarding parallel tractability.
 
@@
 In the latest version of LUBM,\footnote{http://swat.cse.lehigh.edu/projects/lubm/}
-the core ontology contains 48 classes and 32 properties
-that are used to describe the departments and the staffs in
-universities. By setting different numbers of universities to an ontology-generating
-program, users can get datasets of any size based on the core ontology.
-
-In the core ontology of LUBM, the statements about properties, such as inverse property statements,
+the core ontology contains 48 classes and 32 properties, used to describe the departments and the staff of
+universities. By setting a different number of universities for an ontology-generator, users can get datasets of any size based on the core ontology.
+%
+The statements about properties in the LUBM core ontology, such as inverse property statements,
 can be rewritten into the datalog rules of the form (R1), (R2) and (R3) in Table~\ref{tab:dhl}.
@@
 Similarly to how we handle (T4), we can also eliminate the free variable $y$
-in rule $\tau$ via Skolemization, i.e., replacing the variable $y$ by a new constant $o_R^{A,B}$.
-In this way, rule $\tau$ can be rewritten into $A(x)\rightarrow\exists R(x,o_R^{A,B})\wedge B(o_R^{A,B})$.
+in rule $\tau$ via Skolemization, i.e., by replacing the variable $y$ with a new constant $o_R^{A,B}$.
+In this way, rule $\tau$ can be rewritten into $A(x)\rightarrow R(x,o_R^{A,B})\wedge B(o_R^{A,B})$.
 If we only focus on the materialization task, the rewriting approach via Skolemization guarantees the
@@
 On the other hand, rule $\tau$ is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-In summary, if the above kind of rule is not considered,
-the materialization of a LUBM dataset can be handled by Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$.
+In summary, if the above kind of rule is not considered {\color{red}
+  or rewriting is used},
+the materialization of a LUBM dataset can be handled by
+Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$. {\color{red}(Did you use
+  rewriting or did you drop the axioms?)}
 
@@
 and a set of classes: \texttt{entity, class, relation} and \texttt{acyclicTransitiveRelation}.
-The facts in the YAGO model are stated by triples, e.g., ($r_1,\texttt{subRelationOf},r_2$),
+The facts in the YAGO model are stated by triples, e.g., $(r_1,
+\texttt{subRelationOf}, r_2)$,
 which are similar to the RDFS statements.
-A group of rules for the reasoning over YAGO ontologies
+A group of rules for reasoning over YAGO ontologies
 is specified as follows \cite{SuchanekKW08}:
 \begin{enumerate}[leftmargin=8ex,label=(\arabic*),ref=\arabic*]
-  \item ($r,\texttt{domain},c$),($x,r,y$)$\rightarrow$($x,\texttt{type},c$)\label{yago:r1}
-  \item ($r,\texttt{range},c$),($x,r,y$)$\rightarrow$($y,\texttt{type},c$)\label{yago:r2}
-  \item ($c_1,\texttt{subClassOf},c_2$),($x,\texttt{type},c_1$)$\rightarrow$($x,\texttt{type},c_2$)\label{yago:r3}
-  \item ($r_1,\texttt{subRelationOf},r_2$),($x,r_1,y$)$\rightarrow$($x,r_2,y$)\label{yago:r4}
-  \item ($r,\texttt{type},\texttt{acyclicTransitiveRelation}$),($x,r,y$),($y,r,z$)$\rightarrow$($x,r,z$)\label{yago:r5}
+  \item $(r,\texttt{domain}, c), (x, r, y) \rightarrow (x,
+    \texttt{type}, c)$\label{yago:r1}
+  \item $(r,\texttt{range}, c), (x, r, y) \rightarrow (y,
+    \texttt{type}, c)$\label{yago:r2}
+  \item $(c_1, \texttt{subClassOf}, c_2), (x, \texttt{type}, c_1)
+    \rightarrow (x, \texttt{type}, c_2)$\label{yago:r3}
+  \item $(r_1, \texttt{subRelationOf}, r_2), (x, r_1, y) \rightarrow
+    (x, r_2, y)$\label{yago:r4}
+  \item $(r, \texttt{type}, \texttt{acyclicTransitiveRelation}), (x,
+    r, y), (y, r, z) \rightarrow (x, r, z)$\label{yago:r5}
 \end{enumerate}
@@
 i.e., \texttt{domain, range, subClassOf, subRelationOf} and \texttt{type} act in the same
-way as the terms in RDFS statements of the form (1-5) in Table~\ref{tab:rdfs} respectively.
-Different from RDFS, YAGO also allows stating acyclic and transitive properties based on the
+way as the terms in RDFS statements of the form (1--5) in Table~\ref{tab:rdfs}, respectively.
+In contrast to RDFS, YAGO also allows for defining acyclic 
+transitive properties using the
 class \texttt{acyclicTransitiveRelation}; further, any fact in some YAGO ontology cannot be
-described by blank nodes. On the other hand,
-by carefully observing the rules (\ref{yago:r1}-\ref{yago:r5}) for the reasoning over YAGO ontologies,
-one can check that these rules can be rewritten into the datalog rules (T3),\footnote{Both of Rule (\ref{yago:r1}) and
-Rule (\ref{yago:r2}) can be rewritten into (T3).} (T1), (R1) and (R3) in Table~\ref{tab:dhl} respectively.
-Further, DHL does not restrict any role to be acyclic.
+described using blank nodes. By carefully checking the rules (\ref{yago:r1}--\ref{yago:r5}) for the reasoning over YAGO ontologies,
+one can see that these rules can be rewritten into the datalog rules
+of the form (T3),\footnote{Both of Rule (\ref{yago:r1}) and
+Rule (\ref{yago:r2}) can be rewritten into (T3).} (T1), (R1) and (R3) in Table~\ref{tab:dhl}, respectively.
+{\color{red}I am not sure why in YAGO it is called acyclic transitive
+  relation. The rule (in YAGO) is just for transitivity and their
+  argument the subclassof is acyclic and transitive does not make much
+sense as I can have equivalent classes: C subclassof D, D subclassof
+C. That is allowed and cyclic. I would tend to just omit the next
+remark. } Further, DHL does not restrict any role to be acyclic.
 Based on the above analysis, any YAGO ontology can be expressed in DHL
-and satisfies the simple-class and the simple-role restrictions. We then have that
-for any well-constructed class of YAGO ontologies Algorithm~$\mathsf{A}_{opt}^{\psi}$
+and satisfies the simple-concept and the simple-role restrictions. We then have that,
+for any well-constructed class of YAGO ontologies,
+Algorithm~$\mathsf{A}_{opt}^{\psi}$ {\color{red} $\mathsf{A}_{prc}$?
+  both is correct, but as we are evaluating $\mathsf{A}_{prc}$ this
+  might be better?}
 can handle all of the ontologies in the class.
@@
 In addition to LUBM and YAGO, we further investigate different kinds of ontologies and datasets
-including benchmarks, real-world ontologies and datasets that can be expressed in ontology languages.
-These ontologies and datsets are collected from the Protege ontology library,\footnote{http://protegewiki.stanford.edu/wiki/Protege$\underline{~}$Ontology$\underline{~}$Library}
-Swoogle\footnote{http://swoogle.umbc.edu/} and Oxford ontology lib.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
+including benchmarks, real-world ontologies and datasets that can be
+expressed in ontology languages.
+These ontologies and datsets are collected from the Prot\'{e}g\'{e}
+ontology
+library,\footnote{http://protegewiki.stanford.edu/wiki/Protege\textunderscore
+  Ontology\textunderscore Library}
+Swoogle\footnote{http://swoogle.umbc.edu/} and the Oxford ontology library.\footnote{http://www.cs.ox.ac.uk/isg/ontologies/lib/}
 Based on the analysis of these ontologies, we found that, ignoring imports, many of them
@@
 
-We implemented a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{\text{prc}}$. In this part, we evaluate ParallelDHL and
-compare it to the state-of-the-art reasoning system, RDFox \cite{MotikNPHO14},
-that can also handle ontology materialization.
+In this part, we evaluate the implemented prototype system ParallelDHL
+for DHL$(\circ)$ materialization based on
+Algorithm~$\mathsf{A}_{\text{prc}}$. We also provide evaluation
+results for the state-of-the-art reasoning system RDFox
+\cite{MotikNPHO14}, which can also handle parallel ontology
+materialization. Since RDFox is already a mature system, developed by
+several people over several years, we only provide the results for
+reference, as a direct comparison with our initial, not yet optimized
+prototype is not possible.
 
@@
 The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
+The indicator `speedup' and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
 Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
@@
 We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This situation in the line graphs for Finance and GrossAnatomy
-series is more obvious. For example, in line graph $lg1$,
+that do not belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
+intersect to some degree. This is more obvious in the line graphs for
+the Finance and GrossAnatomy
+series. For example, in line graph $lg1$,
 line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot be obviously reduced with more threads allocated.
+The intersection of lines indicates that reasoning time cannot
+obviously be reduced with more threads allocated.
 This is also supported by the results of the average speedups.
 From Table~\ref{tab:expresult}, we can see that the average speedups of ParallelDHL and RDFox
-for ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., they are averagely 1.4
-(it means that the reasoning time can be reduced averagely by 1.4 times with two more threads allocated)
-for ParallelDHL, and, 1.1 for RDFox. For the four ontology series that belong to $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$,
+for the ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
+are more stable compared with the other ones, i.e., with an average of
+$1.4$ for ParallelDHL. This means that the reasoning time can be reduced on average
+by $1.4$ times with two more threads allocated 
+for ParallelDHL, and, $1.1$ for RDFox. For the four ontology series
+that do not belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$,
 the average speedups have a higher volatility. For example,
-Finance and Skeleton series lead to high average speedups that reach up to 3,
-while, for Molecule and GrossAnatomy series, the average speedups are even lower than 1.
+the Finance and Skeleton series lead to high average speedups that reach up to $3$,
+while, for the Molecule and GrossAnatomy series, the average speedups are even below $1$.
 In summary, from the experiments on the test ontology series,
 parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared with the ones in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
+that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared
+with the ones outside of this fragment.
 
 By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is a competitive system.
-From Table~\ref{tab:expresult}, we can find that most of the minimal time ratios are close to 1.
+ParallelDHL is competitive system despite not yet being highly optimized.
+From Table~\ref{tab:expresult}, we can find that most of the minimal time ratios are close to $1$.
 This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
+In particular, for the GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
 much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only costs one fifth of the minimal reasoning time of RDFox.
+only requires one fifth of the minimal reasoning time of RDFox.
 On the other hand, for most ontology series,
 the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference of ParallelDHL and RDFox lies in that ParallelDHL applies
+The main difference between ParallelDHL and RDFox lies in that ParallelDHL applies
 the optimizations designed for Algorithm~$\mathsf{A}_{\text{opt}}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of PrallelDHL also verifies the validity of the optimizations
+The higher average speedups of ParallelDHL also verifies the validity of the optimizations
 used in Algorithm~$\mathsf{A}_{\text{opt}}$.
-One may note that, ParallelDHL is averagely 3 times slower than RDFox when handling Skeleton series.
-The main reason is that the computation of \texttt{rch} relations
-occupies a large amount of time. We have checked that, the situation of path twisting occurs in Skeleton series.
+One may note that ParallelDHL is on average 3 times slower than RDFox
+when handling the Skeleton series.
+The main reason is that the computation of the \texttt{rch} relations
+requires a large amount of time and the situation of path twisting occurs in Skeleton series.
 This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}.
+in Section~\ref{sec:ptonto}. {\color{red}What does the bold font in
+  the table mean?}
 
@@
     \includegraphics[width=\textwidth]{experimentalResults/1-Finance-simple}
-    \subcaption{lg1\label{fig:financepdhl}} 
+    \subcaption{Finance (lg1)\label{fig:financepdhl}} 
   \end{minipage}
@@
     \includegraphics[width=\textwidth]{experimentalResults/2-molecule-simple}
-    \subcaption{lg3\label{fig:moleculepdhl}}
+    \subcaption{Molecule (lg3)\label{fig:moleculepdhl}}
   \end{minipage}\\
@@
     \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-simple}
-    \subcaption{lg5\label{fig:grossanatomypdhl}}
+    \subcaption{GrossAnatomy (lg5)\label{fig:grossanatomypdhl}}
   \end{minipage}
@@
     \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-simple}
-    \subcaption{lg7\label{fig:skeletonpdhl}}
+    \subcaption{Skeleton (lg7)\label{fig:skeletonpdhl}}
   \end{minipage}
@@
     \includegraphics[width=\textwidth]{experimentalResults/1-Finance-rdfox}
-    \subcaption{lg2\label{fig:financerdfox}} 
+    \subcaption{Finance (lg2)\label{fig:financerdfox}} 
   \end{minipage}
@@
     \includegraphics[width=\textwidth]{experimentalResults/2-molecule-rdfox}
-    \subcaption{lg4\label{fig:moleculerdfox}}
+    \subcaption{Molecule (lg4)\label{fig:moleculerdfox}}
   \end{minipage}\\
@@
     \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-rdfox}
-    \subcaption{lg6\label{fig:grossanatomyrdfox}}
+    \subcaption{GrossAnatomy (lg6)\label{fig:grossanatomyrdfox}}
   \end{minipage}
@@
     \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-rdfox}
-    \subcaption{lg8\label{fig:skeletonrdfox}}
+    \subcaption{Skeleton (lg8)\label{fig:skeletonrdfox}}
   \end{minipage}

### 2018-02-04 parallel-tractability-J-v9/evaluation.tex
small changes

@@
 On the other hand, rule $\tau$ is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
-In summary, if the above kind of rule is not considered {\color{red}
-  or rewriting is used},
+In summary, if the rewriting approach is used for the above kind of rule,
 the materialization of a LUBM dataset can be handled by
-Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$. {\color{red}(Did you use
-  rewriting or did you drop the axioms?)}
+Algorithm~$\mathsf{A}_{\text{prc}}$.
 
@@
 way as the terms in RDFS statements of the form (1--5) in Table~\ref{tab:rdfs}, respectively.
-In contrast to RDFS, YAGO also allows for defining acyclic 
+In contrast to RDFS, YAGO also allows for defining
 transitive properties using the
@@
 Rule (\ref{yago:r2}) can be rewritten into (T3).} (T1), (R1) and (R3) in Table~\ref{tab:dhl}, respectively.
-{\color{red}I am not sure why in YAGO it is called acyclic transitive
-  relation. The rule (in YAGO) is just for transitivity and their
-  argument the subclassof is acyclic and transitive does not make much
-sense as I can have equivalent classes: C subclassof D, D subclassof
-C. That is allowed and cyclic. I would tend to just omit the next
-remark. } Further, DHL does not restrict any role to be acyclic.
 Based on the above analysis, any YAGO ontology can be expressed in DHL
@@
 for any well-constructed class of YAGO ontologies,
-Algorithm~$\mathsf{A}_{opt}^{\psi}$ {\color{red} $\mathsf{A}_{prc}$?
-  both is correct, but as we are evaluating $\mathsf{A}_{prc}$ this
-  might be better?}
+Algorithm~$\mathsf{A}_{prc}$ 
 can handle all of the ontologies in the class.

### 2018-02-05 parallel-tractability-J-v9/evaluation.tex
added the experiments of lubm and yago

@@
 
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{\text{prc}}$}
+\begin{table}
+\centering
+\caption{The statistics of the test ontologies}
+\begin{tabular}{|l|r|r|r|r|r|}
+\hline
+ontology&$\sharp$concept&$\sharp$role&$\sharp$individual&$\sharp$axiom$^{a}$&$\sharp$assertion\\
+\hline
+lubm-50&48&32&1,082,818&99&11,601,923\\
+lubm-100&48&32&2,179,766&99&23,837,579\\
+lubm-150&48&32&3,243,523&99&35,466,709\\
+lubm-200&48&32&4,341,309&99&46,537,764\\
+lubm-250&48&32&5,421,894&99&58,125,155\\
+yago-core&65,318&74&4,077,882&55,615&45,277,896\\
+\hline
+\multicolumn{5}{l}{$^{a}$ \small the number of TBox and RBox axioms.}\\
+\end{tabular}
+\label{tab:onto}
+\end{table}
 
-In this part, we evaluate the implemented prototype system ParallelDHL
-for DHL$(\circ)$ materialization based on
-Algorithm~$\mathsf{A}_{\text{prc}}$. We also provide evaluation
-results for the state-of-the-art reasoning system RDFox
-\cite{MotikNPHO14}, which can also handle parallel ontology
-materialization. Since RDFox is already a mature system, developed by
-several people over several years, we only provide the results for
-reference, as a direct comparison with our initial, not yet optimized
-prototype is not possible.
+\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
 
-\textbf{Datasets}.
-We select eight ontologies from the data sources given in the previous subsection;
-four of the eight ontologies belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-the rest of them does not satisfy the simple-concept or the simple-role
-restriction.
-The chosen eight ontologies are real ontologies and are applied in different fields.
-The basic information for these ontologies
-is summarized in Table~\ref{tab:info}.
+We implement a prototype system ParallelDHL for DHL$(\circ)$ materialization
+based on Algorithm~$\mathsf{A}_{prc}$. Since ParallelDHL is evaluated in the
+platform which has the limited memory space and the fixed number of processors,
+the parallel assumption given in Section~\ref{sec:alg-bsc} does not apply to ParallelDHL.
+In the implementation of ParallelDHL, we use a hash function to map any rule instance
+to the identifier of some processor. Thus, when performing ParallelDHL,
+each processor handles a group of rule instances.
 
-\begin{table}[htb]
+We run ParallelDHL on LUBM and YAGO to further analyze these
+two kinds of ontologies. We also use the reasoning system, RDFox \cite{MotikNPHO14},
+for comparison. We use five LUBM ontologies, lubm-50, lubm-100, lubm-150, lubm-200
+and lubm-250, where lubm-50 contains the descriptions of 50 universities (the other ontologies
+are explained similarly). For YAGO, we use its core version, denoted by yago-core.\footnote{
+The yago-core ontology is available at https://www.mpi-inf.mpg.de/departments/databases-and-information-systems/research/yago-naga/yago/downloads/.}
+The yago-core ontology is a subset of the full YAGO dataset. It does not include the datatype statements, the links
+between different data sources, the degrees of confidence and other kinds of
+annotations that we do not consider in this work. The statistics of the above ontologies is given in Table~\ref{tab:onto}.
+The running platform for this experiment is a server with a 50 Gigabyte RAM and 8 physical cores, in each core
+three logic threads can be allocated.
+
+We run the LUBM ontologies and the yago-core ontology on RDFox and ParallelDHL with different numbers of
+threads (respectively 1,4,8,16 and 24).
+The reasoning times are collected in Table~\ref{tab:result}. We also give Figure~\ref{fig:reasoningtime} to
+clearly compare the two systems.
+In Figure~\ref{fig:reasoningtime}(left), the abscissa records the five LUBM ontologies,
+the ordinate records the reasoning times with 24 threads being allocated;
+In Figure~\ref{fig:reasoningtime}(right), the abscissa records the reciprocal of the number of threads, and
+the ordinate records the reasoning times over the yago-core ontology.
+
+\begin{table}
 \centering
-\caption{Information about the test ontologies, where
-  $|\mathcal{T}|+|\mathcal{R}|$ denotes the number of axioms occurring
-  in the ontology, $|\mathcal{A}|$ denotes the number of assertions
-  in the ABox and the last column states whether the
-  ontology belongs to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$}
-\begin{tabular}{>{\hspace*{5mm}}ccrrc<{\hspace*{5mm}}}
+\caption{The reasoning-time results (seconds)}
+\begin{tabular}{|l|r|r|r|r|r|r|r|}
 \hline
-\textbf{Ontology Name} & \textbf{Field} &
-                                          $|\mathcal{T}|+|\mathcal{R}|$
-  & $|\mathcal{A}|$ & $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$\\
+&\small$\sharp$thread&lubm-50&lubm-100&lubm-150&lubm-200&lubm-250&yago-core\\
 \hline
-
-Finance&finance&1,934&6,152&no\\
-
-Molecule&chemistry&43&0&no\\
-
-GrossAnatomy&anatomy&2,276&13&no\\
-
-Skeleton&medicine&815&0&no\\
-
+\multirow{5}{*}{ \textbf{RDFox}}&1&23.01&42.8&71.92&88.64&111.96&105.73\\
+                    &4&5.97&11.64&18.5&22.31&25.59&35.5\\
+                    &8&4.88&5.89&9.95&11.21&12.8&19.07\\
+                    &16&3.18&3.75&8.37&9.16&12.19&13.22\\
+                    &24&1.92&3.9&6.21&7.74&9.58&11.81\\
 \hline
-
-ChemistryPrimitive&chemistry&167&0& yes\\
-
-FacebookOnto&social networking&185&28& yes\\
-
-Mahabharata&literature&69&2,036& yes\\
-
-Transportation&traffic&925&511& yes\\
-
+\multirow{5}{*}{ \small{\textbf{ParallelDHL}}}&1&93.66&213.75&376.39&498.34&693.49&773.06\\
+                    &4&21.71&54.03&111.2&123.76&159.82&223.4\\
+                    &8&9.44&23.04&55.78&67.29&86.41&98.33\\
+                    &16&4.02&12.7&20.9&35.63&43.91&47.08\\
+                    &24&4.06&9.82&16.84&22.31&27.47&34.48\\
 \hline
 \end{tabular}
-\label{tab:info}
+\label{tab:result}
 \end{table}
-
-In order to compare ABoxes of a similar scale, we generate a limited
-number of ABox assertions with respect to the TBoxes and RBoxes for
-the test ontologies using the generation method proposed by
-\citet{Elhaik98}.  For each test ontology, e.g., the Finance ontology,
-we generate 5 new ontologies with different ABoxes, denoted
-Finance-$i$ ($i\in\{1,2,3,4,5\}$). The index $i$ indicates that the
-number of ABox assertions of Finance-$i$ is $i\times100,000$. We also
-use the term ``Finance series" to denote the five generated ontologies
-for the Finance ontology. The other test ontologies are processed
-similarly.
-
-\begin{table}[htb]
-\centering
-\caption{Analysis of the reasoning results, where the \emph{minimal time
-  ratio} is the minimal reasoning time
-of ParallelDHL divided by the minimal reasoning time of RDFox and the
-\emph{average speedup} is $1/4 (T_1/T_2 + T_2/T_4 + T_4/T_6 + T_6/T_8)$,
- where $T_i$ is the reasoning time with $i$ threads allocated}
-{\setlength{\tabcolsep}{6mm}
-\begin{tabular}{crrrrr}
-\hline
-series & 1 & 2 & 3 & 4 & 5\\
-\hline
-\multicolumn{6}{c}{minimal time ratio}\\%[-1mm]
-% \multicolumn{6}{c}{{\footnotesize minimal reasoning time
-% of ParallelDHL/minimal reasoning time of RDFox}}\\
-\hline
-Finance&0.54&1.36&0.94&0.99&1.70\\
-Molecule&0.94&0.79&0.96&0.98&1.07\\
-GrossAnatomy&0.65&0.48&0.84&0.77&0.83\\
-Skeleton&1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-ChemistryPrimitive&1.29&1.54&1.68&1.14&0.93\\
-FacebookOnto&\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-Mahabharata&1.19&1.19&0.99&0.84&0.89\\
-Transportation&0.24&0.52&0.51&0.65&0.49\\
-\hline
-\multicolumn{6}{c}{average speedup of ParallelDHL with increasing
-  number of threads}\\%[-1mm]
-% \multicolumn{6}{c}{{\footnotesize
-%   $1/4 (T_1/T_2 + T_2/T_4 + T_4/T_6 + T_6/T_8)$,
-%  where $T_i$ is the reasoning time with $i$ threads allocated}}\\
-\hline
-Finance&3.06&1.88&2.29&2.95&2.73\\
-Molecule&1.04&1.24&1.13&1.07&1.05\\
-GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-Skeleton&3.28&1.84&1.65&1.74&1.96\\
-ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-\hline
-\multicolumn{6}{c}{average speedup of RDFox with increasing
-  number of threads}\\%[-1mm]
-% \multicolumn{6}{c}{{\footnotesize
-%   $1/4 (T_1/T_2 + T_2/T_4 + T_4/T_6 + T_6/T_8)$,
-%  where $T_i$ is the reasoning time with $i$ threads allocated}}\\
-\hline
-Finance&1.01&1.04&1.13&1.11&1.19\\
-Molecule&0.90&1.03&0.95&1.01&0.99\\
-GrossAnatomy&0.87&0.99&0.94&0.96&0.98\\
-Skeleton&1.13&1.01&1.06&1.08&1.08\\
-ChemistryPrimitive&1.28&1.16&1.14&1.11&1.15\\
-FacebookOnto&1.22&1.08&1.07&1.09&1.09\\
-Mahabharata&1.24&1.07&1.13&1.10&1.12\\
-Transportation&1.14&1.04&1.03&1.08&1.11\\
-\hline
-\end{tabular}
-% \begin{tabular}{crrrrr}
-% \hline
-% series & 1 & 2 & 3 & 4 & 5\\
-% \hline
-% &0.54&1.36&0.94&0.99&1.70\\
-% Finance&3.06&1.88&2.29&2.95&2.73\\
-% &1.01&1.04&1.13&1.11&1.19\\
-% \hline
-% &0.94&0.79&0.96&0.98&1.07\\
-% Molecule&1.04&1.24&1.13&1.07&1.05\\
-% &0.90&1.03&0.95&1.01&0.99\\
-% \hline
-% &0.65&0.48&0.84&0.77&0.83\\
-% GrossAnatomy&1.41&1.69&1.33&1.32&1.22\\
-% &0.87&0.99&0.94&0.96&0.98\\
-% \hline
-% &1.11&\textbf{3.08}&\textbf{3.03}&\textbf{3.04}&\textbf{2.75}\\
-% Skeleton&3.28&1.84&1.65&1.74&1.96\\
-% &1.13&1.01&1.06&1.08&1.08\\
-% \hline
-% &1.29&1.54&1.68&1.14&0.93\\
-% ChemistryPrimitive&\textbf{1.46}&\textbf{1.43}&\textbf{1.44}&\textbf{1.51}&\textbf{1.65}\\
-% &1.28&1.16&1.14&1.11&1.15\\
-% \hline
-% &\textbf{0.23}&\textbf{0.22}&\textbf{0.19}&\textbf{0.24}&\textbf{0.22}\\
-% FacebookOnto&\textbf{1.81}&\textbf{1.83}&\textbf{1.82}&\textbf{1.61}&\textbf{1.78}\\
-% &1.22&1.08&1.07&1.09&1.09\\
-% \hline
-% &1.19&1.19&0.99&0.84&0.89\\
-% Mahabharata&\textbf{1.41}&\textbf{1.46}&\textbf{1.51}&\textbf{1.47}&\textbf{1.56}\\
-% &1.24&1.07&1.13&1.10&1.12\\
-% \hline
-% &0.24&0.52&0.51&0.65&0.49\\
-% Transportation&\textbf{1.98}&\textbf{1.57}&\textbf{1.61}&\textbf{1.55}&\textbf{1.59}\\
-% &1.14&1.04&1.03&1.08&1.11\\
-% \hline
-% \end{tabular}
-}
-\label{tab:expresult}
-\end{table}
-
-\textbf{The Experimental Results}.
-We evaluated ParallelDHL and RDFox over the above eight ontology series.
-The running environment is a DELL server with a
-memory of 16 GiB and 4 cores.
-For fairness, we set the same number of threads (i.e., 1,2,4,6 and 8 threads, respectively)
-for ParallelDHL and RDFox in each experiment. The resulting reasoning
-times\footnote{The experimental results can be found at https://github.com/quanzz/PT.} are
-presented in the 16 line graphs (denoted by $lg1$,...,$lg16$) of Figure~\ref{fig:linegraph},
-where the abscissa of each line graph records the numbers of ABox assertions,
-the ordinate records the reasoning times (in milliseconds),
-and each of the five curves in different colors denotes the trend of reasoning time with the
-corresponding number of threads allocated (we use line-$k$ to denote the curve
-corresponding to $k$ threads).
-
-% We further process the collected data and fill the results in Table~\ref{tab:expresult}, where each cell corresponds
-% to a test ontology (see the row label) and a newly generated ABox (distinguished by the column labels);
-% the three values from above to below in each cell are: (1) \emph{the minimal time ratio} - the minimal reasoning time
-% of ParallelDHL divided by the minimal reasoning time of RDFox;
-% (2) \emph{the average speedup of ParallelDHL};\footnote{Suppose $T_i$ is the reasoning time with $i$ threads allocated,
-% the average speedup is $\frac{1}{4}(\frac{T_1}{T_2}+\frac{T_2}{T_4}+\frac{T_4}{T_6}+\frac{T_6}{T_8})$.}
-% (3) \emph{the average speedup of RDFox}.
-% The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-% The indicator speedup and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-% Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-% threads allocated.
-% In the following, we give the detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~\ref{tab:expresult}.
-
-We further process the collected data and fill the results in Table~\ref{tab:expresult}, where each cell corresponds
-to a test ontology (see the row label) and a newly generated ABox
-(distinguished by the series column labels).
-The minimal time ratio describes the performance of ParallelDHL by using RDFox as the baseline.
-The indicator `speedup' and its derived indicators are the most common tools used for measuring the capacity of parallelism \cite{MotikNPHO14,KazakovKS14,UrbaniKMHB12}.
-Here, we use the average speedup \cite{ichiyoshiK92} to describe the average capacity of parallelism with different
-threads allocated.
-In the following, we give a detailed analysis based on the contents in Figure~\ref{fig:linegraph} and Table~\ref{tab:expresult}.
-
-\textbf{Analysis of the Experimental Results}.
-According to the theoretical results in Section~\ref{sec:ptonto},
-materialization of the
-ontologies not belonging to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-(Finance, Molecule, GrossAnatomy and Skeleton)
-may not be tractable in parallel. In other words,
-parallel techniques may not work for improving the efficiency of materialization.
-This is shown in the line graphs of Figure~\ref{fig:linegraph}.
-We can see that, in the line graphs ($lg1$-$lg8$) of the ontology series
-that do not belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, the four lines, line-2, line-4, line-6 and line-8,
-intersect to some degree. This is more obvious in the line graphs for
-the Finance and GrossAnatomy
-series. For example, in line graph $lg1$,
-line-2 stays higher than line-6, but lower than line-4.
-The intersection of lines indicates that reasoning time cannot
-obviously be reduced with more threads allocated.
-This is also supported by the results of the average speedups.
-From Table~\ref{tab:expresult}, we can see that the average speedups of ParallelDHL and RDFox
-for the ChemistryPrimitive, FacebookOnto, Mahabharata and Transportation series
-are more stable compared with the other ones, i.e., with an average of
-$1.4$ for ParallelDHL. This means that the reasoning time can be reduced on average
-by $1.4$ times with two more threads allocated
-for ParallelDHL, and, $1.1$ for RDFox. For the four ontology series
-that do not belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$,
-the average speedups have a higher volatility. For example,
-the Finance and Skeleton series lead to high average speedups that reach up to $3$,
-while, for the Molecule and GrossAnatomy series, the average speedups are even below $1$.
-In summary, from the experiments on the test ontology series,
-parallelism leads to a more effective improvement for materializing the ontology series
-that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ compared
-with the ones outside of this fragment.
-
-By analyzing the experimental results of ParallelDHL and RDFox, we have that
-ParallelDHL is competitive system despite not yet being highly optimized.
-From Table~\ref{tab:expresult}, we can find that most of the minimal time ratios are close to $1$.
-This means that the reasoning times of ParallelDHL are close to that of RDFox in parallel.
-In particular, for the GrossAnatomy, FacebookOnto and Transportation series, ParallelDHL performs
-much better than RDFox; therein, for materializing FacebookOnto-3, ParallelDHL
-only requires one fifth of the minimal reasoning time of RDFox.
-On the other hand, for most ontology series,
-the average speedups of ParallelDHL are overall higher than that of RDFox.
-The main difference between ParallelDHL and RDFox lies in that ParallelDHL applies
-the optimizations designed for Algorithm~$\mathsf{A}_{\text{opt}}$ (see Section~\ref{sec:ptclass}).
-The higher average speedups of ParallelDHL also verifies the validity of the optimizations
-used in Algorithm~$\mathsf{A}_{\text{opt}}$.
-One may note that ParallelDHL is on average 3 times slower than RDFox
-when handling the Skeleton series.
-The main reason is that the computation of the \texttt{rch} relations
-requires a large amount of time and the situation of path twisting occurs in Skeleton series.
-This makes the the optimization based on \texttt{rch} relations invalid as discussed
-in Section~\ref{sec:ptonto}. {\color{red}What does the bold font in
-  the table mean?}
 
@@
 \begin{center}
-\includegraphics[width=1.5\textwidth,angle=270]{fig-lineGraph.eps}
-\caption{The line graphs of all experiments. The 16 line graphs are labeled by $lg1$,...,$lg16$ respectively.}
-\label{fig:linegraph}
+\includegraphics[width=1\textwidth]{fig-reasoningtime.eps}
+\caption{(left) the reasoning times over LUBM ontologies; (right) the reasoning times over yago-core.}
+\label{fig:reasoningtime}
 \end{center}
@@
 
+From Table~\ref{tab:result}, we can see that for lubm-50 these two systems perform equally well.
+For the other ontologies, ParallelDHL is comparable to RDFox with several threads being allocated.
+For lubm-250 and yago-core, ParallelDHL delays obviously when only one thread is allocated.
+The reason is that the computation of the relation $S_{\textit{\!\tiny rch}}$ occupies a large amount of time. When
+more threads are allocated, ParallelDHL has a better efficiency.
+Although ParallelDHL is not such optimized as RDFox, it also shows the scalability.
+From the two line graphs in Figure~\ref{fig:reasoningtime},
+we can see a linear trend of the reasoning times of both RDFox and ParallelDHL.
+This also indicates that ParallelDHL will finish the materialization tasks on the test ontologies
+in a shorter period of time with more threads being allocated.
+
+\subsection{The Discussion of The Depths of Materialization Graphs}
+
+From the complexity analysis for Algorithm~$\mathsf{A}_{bsc}$, we have that the computing time of
+Algorithm~$\mathsf{A}_{bsc}$ depends on the number of iterations of \ref{alg1:updateG},
+which equals to the depth of the constructed materialization graph (see the proof of Theorem~\ref{theorem:a1}).
+Thus, the depth of the target materialization graph determines the computing time of
+Algorithm~$\mathsf{A}_{bsc}$. This conclusion also applies to Algorithm~$\mathsf{A}_{opt}$
+based on the analysis in Section~\ref{sec:opt}. In this part,
+we discuss the influence of the depths of the materialization graphs
+for the test ontologies.
+
 \begin{figure}[htbp]
-  \centering
-  \begin{minipage}{.45\textwidth}
-    \includegraphics[width=\textwidth]{experimentalResults/1-Finance-simple}
-    \subcaption{Finance (lg1)\label{fig:financepdhl}}
-  \end{minipage}
-  \begin{minipage}{.45\textwidth}
-    \includegraphics[width=\textwidth]{experimentalResults/2-molecule-simple}
-    \subcaption{Molecule (lg3)\label{fig:moleculepdhl}}
-  \end{minipage}\\
-  \begin{minipage}{.45\textwidth}
-    \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-simple}
-    \subcaption{GrossAnatomy (lg5)\label{fig:grossanatomypdhl}}
-  \end{minipage}
-  \begin{minipage}{.45\textwidth}
-    \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-simple}
-    \subcaption{Skeleton (lg7)\label{fig:skeletonpdhl}}
-  \end{minipage}
-  \caption{Materialization time in ms for ParallelDHL for the
-    ontologies that do not belonging to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.~\label{fig:eval}}
+\begin{center}
+\includegraphics[width=1\textwidth]{fig-graphdepth.eps}
+\caption{The statistics of the materialization graphs of lubm-250 (left) and yago-core (right).}
+\label{fig:graphdepth}
+\end{center}
 \end{figure}
 
-\begin{figure}[htbp]
-  \centering
-  \begin{minipage}{.45\textwidth}
-    \includegraphics[width=\textwidth]{experimentalResults/1-Finance-rdfox}
-    \subcaption{Finance (lg2)\label{fig:financerdfox}}
-  \end{minipage}
-  \begin{minipage}{.45\textwidth}
-    \includegraphics[width=\textwidth]{experimentalResults/2-molecule-rdfox}
-    \subcaption{Molecule (lg4)\label{fig:moleculerdfox}}
-  \end{minipage}\\
-  \begin{minipage}{.45\textwidth}
-    \includegraphics[width=\textwidth]{experimentalResults/3-NIF_GrossAnatomy-rdfox}
-    \subcaption{GrossAnatomy (lg6)\label{fig:grossanatomyrdfox}}
-  \end{minipage}
-  \begin{minipage}{.45\textwidth}
-    \includegraphics[width=\textwidth]{experimentalResults/4-skeleton-rdfox}
-    \subcaption{Skeleton (lg8)\label{fig:skeletonrdfox}}
-  \end{minipage}
-  \caption{Materialization time in ms for RDFox for the
-    ontologies that do not belonging to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.~\label{fig:eval}}
-\end{figure}
+For the five test LUBM ontologies and the yago-core ontology, we record the total depth
+of the materialization graph for each ontology and the number of nodes in different depths.
+We have that all of the LUBM ontologies have the depth of 6 for their
+materialization graphs, while the materialization graph of the yago-core ontology
+has the depth of 9.
+We use the histograms to graphically display the detailed data of lubm-250 and yago-core in Figure~\ref{fig:graphdepth},
+where for each of the two histograms
+the abscissa records the depths from the bottom of a materialization graph to the top,
+the histograms denote the amount of nodes in each depth.
+
+From the above results, we can find that the graph depths are far less than
+the sizes of the input ontologies. Since the graph depth determines the computing
+time of Algorithm~$\mathsf{A}_{bsc}$ and Algorithm~$\mathsf{A}_{opt}$ as discussed
+at the beginning of this part,
+the test ontologies should be materialized efficiently using these two algorithms.
+The obvious difference of the reasoning times of the test ontologies is due to the limited memory space and the fixed number
+of processors and the inapplicability of the parallel assumption given in Section~\ref{sec:alg-bsc}.
+This results in that the computing
+time of ParallelDHL does not depend only on the number of iterations of \ref{alg4:updateG}
+of Algorithm~$\mathsf{A}_{prc}$ as analyzed in Section~\ref{sec:practicalAlg}.
+It depends on several factors: the balancing of workload, the delay of some processors,
+the I/O blocking, etc. Since these issues are not our focus, we do not analyze them in this work.
+On the other hand, the results of the graph depths
+indicate that we can improve the performance of the materialization task by using more
+memory space and more processors.
 

### 2018-02-06 parallel-tractability-J-v9/response.tex
worked on experimental section, fixed table layout and captions
added the response for the two reviewers

@@
 
-We added xxx to adress this...
+We added the parallel complexity analysis for Algorithm~$\mathsf{A}_{\text{bsc}}$
+and Algorithm~$\mathsf{A}_{\text{opt}}$
+in Section~3.3 and Section~3.4 respectively. 
+Based on the analysis and Theorem~1, we have that the parallel complexity
+of Algorithm~$\mathsf{A}_{\text{bsc}}$ depends only on the graph depths,
+while the parallel complexity of Algorithm~$\mathsf{A}_{\text{opt}}$
+depends on both of the graph depths and the sizes of inputs.\\
+
+We added the discussion of the graph depths for real ontologies in Section~6.3.
+From the evaluation, we observed that the graph depths were far less than
+the sizes of the input ontologies. Thus, the reasoning times of the test ontologies
+were mainly determined by the input sizes.
 
@@
 
-...
+We investigated many real ontologies from different data source. These ontologies cover
+several domains and only contain  simple concepts (see Section~6.1). \\
+
+In this work, we focused on exploring the properties
+that make ontologies tractable in parallel. Thus, we did not study the problem of making ontologies
+tractable in parallel by having simple concepts and its influence. We will study this problem
+in the future work.
 
@@
 
-...
+We extended the discussion for YAGO and LUBM in Section~6.1. We added the evaluation
+for these two kinds of ontologies in Section~6.2.
 
@@
 
-...ontologies must satisfy the properties for parallel tractability...
+The eight ontologies are selected since they satisfy the properties for parallel tractability.
+We evaluated them to show the difference between the ontologies of tractable and intractable
+in parallel.
 
@@
 
-...
+In order to make the experiments close to real scenes, we did not
+construct these eight ontologies for some purpose, e.g., to
+make the graph depth deeper. Thus, these ontologies acted like common ones.
 
@@
 
-...
+We checked that ParallelDHL costed a large amount of time for computing
+the relation $S_{\textit{\!\tiny rch}}$ when only one thread being allocated.
+When more than one thread is allocated, ParallelDHL has a better efficiency.
+This also resulted in the difference of the speedup between RDFox and ParallelDHL.
 
@@
 
-...
+We used the speedup numbers to show the distinguishes of reasoning performance between the ontologies in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
+$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
 
@@
 
-...
+We did not
+construct the eight ontologies for some purpose.
+Thus, these ontologies acted like common ones.
+From Figure~5, the distinguishes between the ontologies in
+$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
+$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$ were not shown
+for all the test ontologies.
 
@@
 
-...
+We added the detailed analysis for LUBM and YAGO and the influence of
+graph depths in the revision.
 
@@
 \end{quote}
-
-TODO: Remove the quote above once the issues are fixed.
 
@@
 
-We rewrote the paragraph under Lemma~2 to analyze the parallel complexity of Algorithm~$\mathsf{A}_{opt}$.
+We rewrote the paragraph under Lemma~2 to give a more detailed
+analysis of the parallel complexity of Algorithm~$\mathsf{A}_{opt}$.
 In Step~2 of Algorithm~$\mathsf{A}_{opt}$, an NC algorithm is used to compute the transitive closure of $S_{\text{rch}}$.
@@
 
-(TODO) We used a paragraph to discuss this after Algorithm~$\mathsf{A}_{prc}$.
+We added the discussion of how each processor handles rule instantiations at the beginning of Section~6.2.
 

### 2018-02-06 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
added the experiments of lubm and yago
added the response for the two reviewers

@@
 \begin{theorem}\label{theorem:a1}
-For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$ iff $P$ has a
-materialization graph whose depth is upper-bounded by $\psi(|P|)$.
+For any datalog program $P=\langle R, \textbf{I}\rangle$, $P\in\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$ iff $P$ has a
+materialization graph whose depth is upper-bounded by $\psi(|\textbf{I}|)$.
 \end{theorem}
@@
 \subsection{Optimizing Algorithm~$\mathsf{A}_{\text{bsc}}$ via Single-Way Derivability}
+\label{sec:opt}
 

### 2018-02-07 parallel-tractability-J-v9/conclusions.tex
overall revision to make some presentations consistent

@@
 materialization on the datalog rewritable ontologies.
-To identify the parallelly tractable classes,
-we proposed two NC algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
+To identify the parallel tractability classes,
+we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
 and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
@@
 Based on these algorithms, we identified the corresponding
-parallelly tractable datalog program (\texttt{PTD}) classes such that materialization
-on the datalog programs in these classes is in the complexity class NC.
+parallel tractability classes such that materialization
+on the datalog programs in these classes is in the NC complexity.
 We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is parallelly tractable.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is parallelly tractable.
+We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is tractable in parallel.
+For DHL and DHL($\circ$), we proposed two restrictions such that materialization is tractable in parallel.
 
-We verified the usefulness of our theoretical techniques in two ways. On the one hand,
-we analyzed different kinds of datasets,
-including well-known benchmarks, real-world ontologies and a famous dataset YAGO.
-Our analysis showed that many real ontologies belong to
-the parallelly tractable class $\mathcal{D}_{\textit{\text{dhl}}}$
-or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$. The
-developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
-and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
-to create large-scale ontologies for which parallel tractability
-is theoretically guaranteed. On the other hand,
-we used an optimization strategy based on SWD paths
+We analyzed the benchmark LUBM and the real-world dataset YAGO
+and gave the cases where these ontologies belong to parallel tractability classes.
+On the other hand, we used an optimization strategy based on SWD paths
 to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an NC version, and can be implemented for practice.
+also be restricted to an \texttt{NC} version.
 We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
 the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimization proposed in this paper results
-in a better performance on parallelly tractable ontologies compared with RDFox.
+The experimental results showed that our system is comparable to RDFox when handling
+the LUBM and the YAGO ontologies.
 
@@
 explore more restrictions that are practical and make materialization
-parallelly tractable. Another line of the future work is to
+tractable in parallel. Another line of the future work is to
 study how to further apply the

### 2018-02-07 parallel-tractability-J-v9/evaluation.tex
overall revision to make some presentations consistent

@@
-\section{Evaluation}
+\section{Evaluation and Analysis}
 \label{sec:evaluation}
 
-In the first part of this section, we analyze different kinds of ontologies and datasets
-and investigate the usability of the results proposed above.
+In the first part of this section, we analyze the well-known benchmark, LUBM, 
+and the real-world dataset, YAGO, and
+show the cases where these ontologies belong to the parallel tractability classes.
 In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{\text{prc}}$
@@
 \subsection{The Parallel Tractability of the LUBM Datasets and YAGO Ontologies}
-
-In this part, we analyze two popular datasets, LUBM and YAGO, and show the relations
-between these two datasets and the theoretical results regarding parallel tractability.
 
@@
 In summary, if the rewriting approach is used for the above kind of rule,
-the materialization of a LUBM dataset can be handled by
+the materialization of LUBM datasets is tractable in parallel and can be handled by
 Algorithm~$\mathsf{A}_{\text{prc}}$.
@@
 is constructed from Wikipedia and WordNet. The latest version
-YAGO3 \cite{MahdisoltaniBS15} has more than 10 million entities
-(e.g., persons, organizations, cities, etc.)
-and contains more than 120 million facts about these entities.
-
+YAGO3 \cite{MahdisoltaniBS15} has millions of facts.
 In order to balance the expressiveness and computing efficiency,
@@
 
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
-
-We implement a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. Since ParallelDHL is evaluated in the
-platform which has the limited memory space and the fixed number of processors,
-the parallel assumption given in Section~\ref{sec:alg-bsc} does not apply to ParallelDHL.
-In the implementation of ParallelDHL, we use a hash function to map any rule instance
-to the identifier of some processor. Thus, when performing ParallelDHL,
-each processor handles a group of rule instances.
-
-We run ParallelDHL on LUBM and YAGO to further analyze these
-two kinds of ontologies. We also use the reasoning system, RDFox \cite{MotikNPHO14},
-for comparison. We use five LUBM ontologies, lubm-50, lubm-100, lubm-150, lubm-200
-and lubm-250, where lubm-50 contains the descriptions of 50 universities (the other ontologies
-are explained similarly). For YAGO, we use its core version, denoted by yago-core.\footnote{
-The yago-core ontology is available at https://www.mpi-inf.mpg.de/departments/databases-and-information-systems/research/yago-naga/yago/downloads/.}
-The yago-core ontology is a subset of the full YAGO dataset. It does not include the datatype statements, the links
-between different data sources, the degrees of confidence and other kinds of
-annotations that we do not consider in this work. The statistics of the above ontologies is given in Table~\ref{tab:onto}.
-The running platform for this experiment is a server with a 50 Gigabyte RAM and 8 physical cores, in each core
-three logic threads can be allocated.
-
-We run the LUBM ontologies and the yago-core ontology on RDFox and ParallelDHL with different numbers of
-threads (respectively 1,4,8,16 and 24).
-The reasoning times are collected in Table~\ref{tab:result}. We also give Figure~\ref{fig:reasoningtime} to
-clearly compare the two systems.
-In Figure~\ref{fig:reasoningtime}(left), the abscissa records the five LUBM ontologies,
-the ordinate records the reasoning times with 24 threads being allocated;
-In Figure~\ref{fig:reasoningtime}(right), the abscissa records the reciprocal of the number of threads, and
-the ordinate records the reasoning times over the yago-core ontology.
-
 \begin{table}
@@
 
+\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
+
+We implement a prototype system ParallelDHL for DHL$(\circ)$ materialization
+based on Algorithm~$\mathsf{A}_{prc}$. Since ParallelDHL is evaluated in the
+platform which has the limited memory space and the fixed number of processors,
+the parallel assumption given in Section~\ref{sec:alg-bsc} does not apply to ParallelDHL.
+In the implementation of ParallelDHL, we use a hash function to map any rule instance
+to the identifier of some processor. Thus, when performing ParallelDHL,
+each processor handles a group of rule instances.
+
+We run ParallelDHL on the LUBM and the YAGO ontologies to further analyze these
+two kinds of ontologies. We also use the reasoning system, RDFox \cite{MotikNPHO14},
+for comparison. We use five LUBM ontologies, lubm-50, lubm-100, lubm-150, lubm-200
+and lubm-250, where lubm-50 contains the descriptions of 50 universities (the other ontologies
+are explained similarly). For YAGO, we use its core version, denoted by yago-core.\footnote{
+The yago-core ontology is available at https://www.mpi-inf.mpg.de/departments/databases-and-information-systems/research/yago-naga/yago/downloads/.}
+The yago-core ontology is a subset of the full YAGO dataset without imports. It does not include the datatype statements, the links
+between different data sources, the degrees of confidence and other kinds of
+annotations that we do not consider in this work. The statistics of the above ontologies is given in Table~\ref{tab:onto}.
+The running platform for this experiment is a server with a 50 Gigabyte RAM and 8 physical cores, in each core
+three logic threads can be allocated.
+
+We run the LUBM ontologies and the yago-core ontology on RDFox and ParallelDHL with different numbers of
+threads (respectively 1,4,8,16 and 24).
+The reasoning times are collected in Table~\ref{tab:result}. We also give Figure~\ref{fig:reasoningtime} to
+clearly compare the two systems.
+In Figure~\ref{fig:reasoningtime}(left), the abscissa records the five LUBM ontologies,
+the ordinate records the reasoning times with 24 threads being allocated;
+In Figure~\ref{fig:reasoningtime}(right), the abscissa records the reciprocals of the numbers of threads, and
+the ordinate records the reasoning times over the yago-core ontology.
+
 \begin{figure}[htbp]
@@
 \includegraphics[width=1\textwidth]{fig-reasoningtime.eps}
-\caption{(left) the reasoning times over LUBM ontologies; (right) the reasoning times over yago-core.}
+\caption{(left) the reasoning times over the LUBM ontologies; (right) the reasoning times over yago-core.}
 \label{fig:reasoningtime}
@@
 On the other hand, the results of the graph depths
-indicate that we can improve the performance of the materialization task by using more
+indicate that we can further improve the performance of the materialization task by using more
 memory space and more processors.

### 2018-02-07 parallel-tractability-J-v9/introduction.tex
overall revision to make some presentations consistent

@@
 In particular, this is the case for RDFS and datalog rewritable ontology languages and, therefore, the efficiency of reasoning may not be
-improved using a parallel implementation. A possible reason for the apparent high performance of parallel
+improved using a parallel implementation in theory. A possible reason for the apparent high performance of parallel
 reasoning is that the utilized test datasets do not fall into the worst cases in terms of computational complexity.
@@
 reasoning \cite{KolovskiWE10}, although they are expressed in ontology languages that are, in theory, not tractable in parallel.
-On the other hand, there are ontologies for which materialization performance does not improve by parallelism and our experiments in Section~\ref{sec:evaluation} confirm this.
 The current theoretical work of parallel ontology reasoning can hardly explain this.
@@
 We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
+Finally, we analyze the well-known benchmark, LUBM, and the real-world dataset, YAGO, and 
+show that these ontologies following the
 proposed restrictions belong to the parallel tractability classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization, which we compare to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimizations proposed in this paper result in a better performance on ontologies that are 
-tractable in parallel compared with RDFox.
+We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization
+and show that this system is comparable to the state-of-the-art reasoner RDFox
+when handling the LUBM and the YAGO ontologies.
 
@@
 we discuss how to optimize and implement the given \texttt{NC} algorithms.
-We analyze real-world datasets and evaluate our implementation in Section~\ref{sec:evaluation}.
+We analyze the LUBM and the YAGO ontologies and evaluate our implementation in Section~\ref{sec:evaluation}.
 Finally, we discuss related work in Section~\ref{sec:related} and conclude in Section~\ref{sec:conclusion}. Detailed proofs of the theorems and lemmas in this paper are given in the appendix.

### 2018-02-07 parallel-tractability-J-v9/parallel-tractability-J.tex
worked on experimental section, fixed table layout and captions
added the experiments of lubm and yago
overall revision to make some presentations consistent

@@
 \usepackage{amsthm}
-
 \usepackage{amsmath}
-
+\usepackage{multirow}
 \usepackage{CJK}
@@
 \usepackage{rotating}
+
+\usepackage{array}
+\usepackage{subcaption}
+\captionsetup[subfigure]{skip=-10pt}
 
@@
   large-scale ontologies. Parallel materialization algorithms work
-  well for some ontologies, which is not always explained by the
-  theoretical results. For example, for the YAGO ontology
-  parallelization works well, although the reasoning problem for the
+  well for some ontologies, although the reasoning problem for the
   used ontology language is not in \texttt{NC}, i.e., the theoretical
@@
   tractable in parallel. To verify the practical usability of the
-  above results, we analyze real-world datasets and show that for many
+  above results, we analyze benchmark and real-world datasets, including the LUBM
+  and the YAGO ontologies, and show that for many
   ontologies expressed in DHL materialization is tractable in
   parallel. The implementation of our optimized parallel algorithm
-  shows performance improvements over the highly optimized
-  state-of-the-art reasoner RDFox on ontologies for which
-  materialization is tractable in parallel.
+  shows comparable performance with compared to the highly optimized
+  state-of-the-art reasoner RDFox.
 \end{abstract}
@@
 %% \label{}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "parallel-tractability-J"
+%%% End:

### 2018-02-07 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
overall revision to make some presentations consistent

@@
 materialization is tractable in parallel. We consider data complexity,
-i.e., we consider classes of datalog programs which share a fixed the rule set.
+i.e., we consider classes of datalog programs which share a fixed rule set.
 The data complexity of the materialization problem in this case is
@@
 \begin{center}
-\includegraphics[width=0.7\textwidth]{fig-general.pdf}
+\includegraphics[width=0.6\textwidth]{fig-general.pdf}
 \caption{A partial materialization graph}
@@
 \begin{proof}[Proof sketch]
-Suppose $P\in\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$. According to Theorem~\ref{theorem:a1},
-the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{\text{bsc}}^{\psi}$ is upper-bounded by $\psi(|P|)$.
-It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|P|)$.
+Suppose $P=\langle R,\textbf{I}\rangle\in\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$. According to Theorem~\ref{theorem:a1},
+the depth of the materialization graph $\mathcal{G}$ constructed by $\mathsf{A}_{\text{bsc}}^{\psi}$ is 
+upper-bounded by $\psi(|\textbf{I}|)$.
+It is obvious that the number of nodes in each path of $\mathcal{G}$ is also upper-bounded by $\psi(|\textbf{I}|)$.
 According to the optimization strategy applied in $\mathsf{A}_{\text{opt}}$, if $\mathcal{G}$ can be constructed
-by $\mathsf{A}_{\text{opt}}$, the number of iterations of $\mathsf{A}_{\text{opt}}$ has to be upper-bounded by $\psi(|P|)$;
+by $\mathsf{A}_{\text{opt}}$, the number of iterations of $\mathsf{A}_{\text{opt}}$ has to be upper-bounded by $\psi(|\textbf{I}|)$;
 if $\mathcal{G}$ is not the materialization graph constructed

### 2018-02-07 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
overall revision to make some presentations consistent

@@
 for materialization of DL-Lite and DHL (DHL($\circ$)) ontologies
-based on Algorithm~$\mathsf{A}_{\text{opt}}$. We show that, for any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
+based on Algorithm~$\mathsf{A}_{\text{opt}}$. We show that, for any class $\mathbb{O}$ of
+DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontologies,
 there exists a poly-logarithmically bounded function $\psi$
-such that Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$ can handle materialization of $\mathcal{O}$.
+such that Algorithm~$\mathsf{A}_{\text{opt}}^{\psi}$ can handle materialization of the ontologies in $\mathbb{O}$.
 However, for DHL and DHL($\circ$), there exist ontology classes such that Algorithm~$\mathsf{A}_{\text{opt}}^\psi$
@@
 for $2\leq i\leq k$ and $k$ an integer greater than $2$.
-The corresponding datalog program $P_{\text{ex}_5}$
+The corresponding datalog program $P_{\text{ex}_9}$
 contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
 `$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{\text{ex}_5}$ constructed by Algorithm~$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_9}$.
+The materialization graph of $P_{\text{ex}_9}$ constructed by Algorithm~$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_9}$.
 \end{example}
@@
 \begin{example}
-For the ontology $\mathcal{O}_{\text{ex}_7}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{\text{ex}_7}$ does not follow
+For the ontology $\mathcal{O}_{\text{ex}_9}$ in Example~\ref{exp:complexRIA}, all of the roles
+$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{\text{ex}_9}$ does not follow
 the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.

### 2018-02-07 parallel-tractability-J-v9/relatedWork.tex
overall revision to make some presentations consistent

@@
 The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial on RDFox.
-It is also shown from the experiments that parallelism does not lead to a remarkable improvement when RDFox handles the ontology series in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also parallelly tractable.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, has also been shown to have a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
+Analogous to the method used in RDFox, ParallelDHL is also implemented by assigning a group of
+rule instantiations to a processor.
+The experimental results show that ParallelDHL is comparable to RDFox when handling
+the LUBM and the YAGO ontologies.
 

### 2018-02-07 parallel-tractability-J-v9/conclusions.tex
proof read related work and conclusions

@@
 In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
-To identify the parallel tractability classes,
+materialization of datalog rewritable ontologies.
+To identify classes that are tractable in parallel,
 we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
@@
 datalog rewritable ontology languages.
-Based on these algorithms, we identified the corresponding
-parallel tractability classes such that materialization
-on the datalog programs in these classes is in the NC complexity.
-We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
-We showed that any ontology expressed in DL-Lite$_{core}$ or DL-Lite$_{\mathcal{R}}$ is tractable in parallel.
-For DHL and DHL($\circ$), we proposed two restrictions such that materialization is tractable in parallel.
+Based on these algorithms, we identified the corresponding classes of
+datalog program for which materialization is tractable in
+parallel (\texttt{PTD} classes), i.e., in the complexity class \texttt{NC}.
+We further studied two specific ontology languages, DL-Lite and DHL (including an extension).
+We showed that any ontology expressed in DL-Lite$_{\text{core}}$ or
+DL-Lite$_{\mathcal{R}}$ is tractable in parallel.
+For DHL and DHL($\circ$), we proposed two restrictions such that
+materialization is tractable in parallel.
 
-We analyzed the benchmark LUBM and the real-world dataset YAGO
-and gave the cases where these ontologies belong to parallel tractability classes.
-On the other hand, we used an optimization strategy based on SWD paths
+We verified the usefulness of our theoretical results in two ways. On the one hand,
+we analyzed different kinds of datasets,
+including well-known benchmarks, real-world ontologies and the famous YAGO dataset.
+Our analysis showed that many real ontologies belong to
+the class $\mathcal{D}_{\textit{\text{dhl}}}$ or $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$, for which
+materialization is tractable in parallel. The
+developers and users can also refer to $\mathcal{D}_{\textit{\text{dhl}}}$
+and $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$
+to create large-scale ontologies for which parallel tractability
+is theoretically guaranteed. On the other hand,
+we used an optimization strategy based on SWD paths
 to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
-also be restricted to an \texttt{NC} version.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
-the state-of-the-art reasoner RDFox.
-The experimental results showed that our system is comparable to RDFox when handling
-the LUBM and the YAGO ontologies.
+also be restricted to an \texttt{NC} version and can be implemented in practice.
+We implemented a system based on Algorithm~$\mathsf{A}_{prc}$.
+The experimental results showed that the optimizations proposed in this paper result
+in a better performance on ontologies with parallel tractability compared
+to the state-of-the-art reasoner RDFox.
 
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
+In future work, we plan to extend our work in two lines.
+One line is a further study of parallel tractability of
 other expressive ontology languages, in addition to
@@
 explore more restrictions that are practical and make materialization
-tractable in parallel. Another line of the future work is to
+tractable in parallel. Another line of work is to
 study how to further apply the
 results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
+One idea is to apply the technique of SWD paths to enhance other
+reasoning-based tasks such as ontology classification, ontology debugging and query answering.
 

### 2018-02-07 parallel-tractability-J-v9/relatedWork.tex
proof read related work and conclusions

@@
 RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Analogous to the method used in RDFox, ParallelDHL is also implemented by assigning a group of
-rule instantiations to a processor.
-The experimental results show that ParallelDHL is comparable to RDFox when handling
-the LUBM and the YAGO ontologies.
+Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass}, is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
+The main difference is that a group of rule instantiations is handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
+Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial in RDFox {\color{red}The example has two rules.
+Why can they not be parallelized in RDFox?}.
+ItThe experiments also show that parallelism does not lead to a remarkable improvement for RDFox for the ontology series not in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
+We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also tractable in parallel.
+Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, also shows a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
 
@@
 The current methods mainly focus on optimizing reasoning algorithms from different aspects.
-The authors of \cite{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
-This method can significantly yield a throughput improvement and optimize the parallel RDF reasoning and query answering.
-In the work of \cite{PetersSZ15}, the RETE algorithm is used to accelerate rule matching for RDFS reasoning.
-The authors of \cite{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
+\citet{GoodmanJMAAH11} propose a new kind of encoding method for RDF triples to achieve a high performance.
+This method can significantly yield a throughput improvement and optimize parallel RDF reasoning and query answering.
+\citet{PetersSZ15} use the RETE algorithm to accelerate rule matching for RDFS reasoning.
+\citet{SubercazeGCL16} propose a more efficient storage technique and optimize the join operations in parallel reasoning.
 The issue of balance distribution of parallel tasks is also studied \cite{SomaP08,WeaverH09}.
@@
 In current work, several techniques are proposed to adapt parallel computation to OWL reasoning tasks.
-A kind of graph-based method is discussed in \cite{LemboSS13} to enhance OWL~QL classification.
-The authors of \cite{LiebigM07,SchlichtS08,WuH12} propose pruning techniques to optimize the Tableaux algorithm.
-The \emph{lock-free technique} is applied in the work \cite{KazakovKS14,SteigmillerLG14}.
+A kind of graph-based method is discussed by \citet{LemboSS13} to enhance OWL~QL classification.
+Several pruning techniques are proposed to optimize the Tableaux algorithm \cite{LiebigM07,SchlichtS08,WuH12}.
+The \emph{lock-free technique} is applied by \citet{KazakovKS14} and \citet{SteigmillerLG14}.
 
 Another line of optimizing parallel reasoning is to utilize high-performance computing platforms.
-For in-memory platforms, different supercomputers, like Cray XMT, Yahoo S4, have early been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
-The authors of \cite{HeinoP12} report their work on RDFS reasoning based on massively parallel GPU hardware.
-The distributed parallel platforms, like MapReduce and Peer-to-Peer networks, are also used for RDFS reasoning.
+For in-memory platforms, different supercomputers such as Cray XMT or Yahoo S4 have early on been used in parallel RDF reasoning \cite{Hoeksema2011,GoodmanJMAAH11}.
+\citet{HeinoP12} report on their work on RDFS reasoning based on massively parallel GPU hardware.
+Distributed parallel platforms such as MapReduce and Peer-to-Peer networks are also used for RDFS reasoning.
 The representative systems are WebPIE \cite{UrbaniKMHB12}, Marvin \cite{oren2009marvin} and SAOR \cite{HoganHP09}.
 Different techniques are discussed in this work to tackle the special problems in distributed computing.
-However, to study the issue of parallel tractability on distributed platforms, we have to discuss more issues, e.g., \emph{network structures} and \emph{communications}.
+However, to study the issue of parallel tractability on distributed platforms,  more issues have to be discussed, e.g., \emph{network structures} and \emph{communications}.
 This is not the focus in this paper.

### 2018-02-20 parallel-tractability-J-v9/evaluation.tex
evaluation updated

@@
 show the cases where these ontologies belong to the parallel tractability classes.
+%
 In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{\text{prc}}$
 and compare it to the reasoning system RDFox.
+%
+In the third part, we examine the effects of the depths of materialization graphs
+based on two modified ontologies of LUBM.
 
 \subsection{The Parallel Tractability of the LUBM Datasets and YAGO Ontologies}
+\label{sec:lubm-yago}
 
@@
 %
-The statements about properties in the LUBM core ontology, such as inverse property statements,
+For the simple form of the core ontology,
+the statements about properties in the LUBM core ontology, such as inverse property statements,
 can be rewritten into the datalog rules of the form (R1), (R2) and (R3) in Table~\ref{tab:dhl}.
 Most of the statements about classes can be rewritten into the datalog rules of the form (T1) and (T3)
-in Table~\ref{tab:dhl}. Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$ ($\tau$),
+in Table~\ref{tab:dhl}. There are six axioms of the form (T2) as listed below:
+\begin{enumerate}[leftmargin=8ex,label=($\alpha_{\arabic*}$),ref=$\alpha_{\arabic*}$]
+  \item $\texttt{Person}\sqcap\texttt{CourseTaker}\sqsubseteq\texttt{Student}$\label{lubm:a1}
+  \item $\texttt{Person}\sqcap\texttt{OrganizationWorker}\sqsubseteq\texttt{Employee}$\label{lubm:a2}
+  \item $\texttt{Person}\sqcap\texttt{DepartmentHead}\sqsubseteq\texttt{Chair}$\label{lubm:a3}
+  \item $\texttt{Person}\sqcap\texttt{ProgramHead}\sqsubseteq\texttt{Director}$\label{lubm:a4}
+  \item $\texttt{Person}\sqcap\texttt{CourseAssistant}\sqsubseteq\texttt{TeachingAssistant}$\label{lubm:a5}
+  \item $\texttt{Person}\sqcap\texttt{CollegeHead}\sqsubseteq\texttt{Dean}$\label{lubm:a6}
+\end{enumerate}
+In the above axioms, the six concepts \texttt{CourseTaker}, \texttt{OrganizationWorker},
+\texttt{DepartmentHead}, \texttt{ProgramHead}, \texttt{CourseAssistant}
+and \texttt{CollegeHead} have the corresponding definition statements.
+For example, concept \texttt{CourseTaker} is stated by the axiom:
+$\texttt{CourseTaker}\equiv\exists\texttt{take}.\texttt{Course}$,
+which is equivalent to the two axioms of simple form,
+$\exists\texttt{take}.\texttt{Course}\sqsubseteq\texttt{CourseTaker}$
+and $\texttt{CourseTaker}\sqsubseteq\exists\texttt{take}.\texttt{Course}$.
+The axiom $\exists\texttt{take}.\texttt{Course}\sqsubseteq\texttt{CourseTaker}$
+is in the form of (T3). The axiom $\texttt{CourseTaker}\sqsubseteq\exists\texttt{take}.\texttt{Course}$
+requires existentially quantified variables in the rule head when rewriting
+the axiom into a logic rule: $\texttt{CourseTaker}(x)\rightarrow\exists y(\texttt{take}(x,y)\wedge \texttt{Course}(y))$ ($\tau$),
 where a free variable $y$ is introduced. This kind of axiom is a general case of (T4) in Table~\ref{tab:dhl}
@@
 Similarly to how we handle (T4), we can also eliminate the free variable $y$
-in rule $\tau$ via Skolemization, i.e., by replacing the variable $y$ with a new constant $o_R^{A,B}$.
-In this way, rule $\tau$ can be rewritten into $A(x)\rightarrow R(x,o_R^{A,B})\wedge B(o_R^{A,B})$.
+in rule $\tau$ via Skolemization, i.e., by replacing the variable $y$ with a new constant $o$.
+In this way, rule $\tau$ can be rewritten into $\texttt{CourseTaker}(x)\rightarrow\texttt{take}(x,o)\wedge \texttt{Course}(o)$.
 If we only focus on the materialization task, the rewriting approach via Skolemization guarantees the
@@
 In summary, if the rewriting approach is used for the above kind of rule,
+the core ontology can be expressed in DHL.
+We can further check that the concepts occurring in (\ref{lubm:a1}--\ref{lubm:a6})
+are all simple concepts. Thus,
 the materialization of LUBM datasets is tractable in parallel and can be handled by
-Algorithm~$\mathsf{A}_{\text{prc}}$.
+Algorithm~$\mathsf{A}_{\texttt{prc}}$.
 
@@
 \end{enumerate}
-
 According to the semantics given to YAGO \cite{SuchanekKW08}, the built-in properties in YAGO,
@@
 for any well-constructed class of YAGO ontologies,
-Algorithm~$\mathsf{A}_{prc}$
+Algorithm~$\mathsf{A}_{\texttt{prc}}$
 can handle all of the ontologies in the class.
@@
 \hline
-lubm-50&48&32&1,082,818&99&11,601,923\\
-lubm-100&48&32&2,179,766&99&23,837,579\\
-lubm-150&48&32&3,243,523&99&35,466,709\\
-lubm-200&48&32&4,341,309&99&46,537,764\\
-lubm-250&48&32&5,421,894&99&58,125,155\\
+lubm-50&\multirow{5}{*}{48}&\multirow{5}{*}{32}&1,082,818&\multirow{5}{*}{99}&11,601,923\\
+lubm-100&&&2,179,766&&23,837,579\\
+lubm-150&&&3,243,523&&35,466,709\\
+lubm-200&&&4,341,309&&46,537,764\\
+lubm-250&&&5,421,894&&58,125,155\\
+\hline
 yago-core&65,318&74&4,077,882&55,615&45,277,896\\
@@
 \hline
-\multirow{5}{*}{ \textbf{RDFox}}&1&23.01&42.8&71.92&88.64&111.96&105.73\\
+\multirow{5}{*}{ \small{\textbf{RDFox}}}&1&23.01&42.8&71.92&88.64&111.96&105.73\\
                     &4&5.97&11.64&18.5&22.31&25.59&35.5\\
@@
 \hline
-\multirow{5}{*}{ \small{\textbf{ParallelDHL}}}&1&93.66&213.75&376.39&498.34&693.49&773.06\\
-                    &4&21.71&54.03&111.2&123.76&159.82&223.4\\
+\multirow{2}{*}{ \small{\textbf{Parallel-}}}&1&93.66&213.75&376.39&498.34&693.49&773.06\\
+\multirow{3}{*}{ \small{\textbf{DHL}}}&4&21.71&54.03&111.2&123.76&159.82&223.4\\
                     &8&9.44&23.04&55.78&67.29&86.41&98.33\\
@@
 
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
+\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{\texttt{prc}}$}
 
 We implement a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. Since ParallelDHL is evaluated in the
+based on Algorithm~$\mathsf{A}_{\texttt{prc}}$. Since ParallelDHL is evaluated in the
 platform which has the limited memory space and the fixed number of processors,
@@
 
-We run ParallelDHL on the LUBM and the YAGO ontologies to further analyze these
+We run ParallelDHL on LUBM and YAGO to further analyze these
 two kinds of ontologies. We also use the reasoning system, RDFox \cite{MotikNPHO14},
-for comparison. We use five LUBM ontologies, lubm-50, lubm-100, lubm-150, lubm-200
-and lubm-250, where lubm-50 contains the descriptions of 50 universities (the other ontologies
+for comparison. We use five generated LUBM datasets, lubm-50, lubm-100, lubm-150, lubm-200
+and lubm-250, where lubm-50 contains the descriptions of 50 universities (the other datasets
 are explained similarly). For YAGO, we use its core version, denoted by yago-core.\footnote{
 The yago-core ontology is available at https://www.mpi-inf.mpg.de/departments/databases-and-information-systems/research/yago-naga/yago/downloads/.}
-The yago-core ontology is a subset of the full YAGO dataset without imports. It does not include the datatype statements, the links
+The yago-core ontology is a subset of the full YAGO dataset without any import.
+It does not include the datatype statements, the links
 between different data sources, the degrees of confidence and other kinds of
@@
 
-We run the LUBM ontologies and the yago-core ontology on RDFox and ParallelDHL with different numbers of
+We run the LUBM datasets and the yago-core ontology on RDFox and ParallelDHL under different numbers of
 threads (respectively 1,4,8,16 and 24).
 The reasoning times are collected in Table~\ref{tab:result}. We also give Figure~\ref{fig:reasoningtime} to
-clearly compare the two systems.
-In Figure~\ref{fig:reasoningtime}(left), the abscissa records the five LUBM ontologies,
+graphically compare the two systems.
+In Figure~\ref{fig:reasoningtime}(left), the abscissa records the five LUBM datasets,
 the ordinate records the reasoning times with 24 threads being allocated;
@@
 For the other ontologies, ParallelDHL is comparable to RDFox with several threads being allocated.
-For lubm-250 and yago-core, ParallelDHL delays obviously when only one thread is allocated.
+For lubm-250 and yago-core, ParallelDHL delays obviously under only one thread.
 The reason is that the computation of the relation $S_{\textit{\!\tiny rch}}$ occupies a large amount of time. When
-more threads are allocated, ParallelDHL has a better efficiency.
+four and more threads are allocated, ParallelDHL has a better efficiency.
 Although ParallelDHL is not such optimized as RDFox, it also shows the scalability.
@@
 
-\subsection{The Discussion of The Depths of Materialization Graphs}
+\subsection{The Experiments on The Depths of Materialization Graphs}
 
-From the complexity analysis for Algorithm~$\mathsf{A}_{bsc}$, we have that the computing time of
-Algorithm~$\mathsf{A}_{bsc}$ depends on the number of iterations of \ref{alg1:updateG},
-which equals to the depth of the constructed materialization graph (see the proof of Theorem~\ref{theorem:a1}).
-Thus, the depth of the target materialization graph determines the computing time of
-Algorithm~$\mathsf{A}_{bsc}$. This conclusion also applies to Algorithm~$\mathsf{A}_{opt}$
-based on the analysis in Section~\ref{sec:opt}. In this part,
-we discuss the influence of the depths of the materialization graphs
-for the test ontologies.
+From the complexity analysis for Algorithm~$\mathsf{A}_{bsc}$ (see Section~\ref{sec:alg-bsc}),
+we have that the computing time of
+Algorithm~$\mathsf{A}_{bsc}$ depends on the sizes of the input ontologies and the
+numbers of iterations of \ref{alg1:updateG},
+which equals to the depth of the target materialization graph (in the following,
+we use the notion \emph{MG-depth} for short).
+Thus, the MG-depth also determines the computing time of
+Algorithm~$\mathsf{A}_{bsc}$ in theory.
+This conclusion also applies to Algorithm~$\mathsf{A}_{opt}$ and Algorithm~$\mathsf{A}_{\texttt{prc}}$
+based on the analysis in Section~\ref{sec:opt} and Section~\ref{sec:practicalAlg} respectively.
+In this part, we examine the effects of MG-depths.
 
@@
 \includegraphics[width=1\textwidth]{fig-graphdepth.eps}
-\caption{The statistics of the materialization graphs of lubm-250 (left) and yago-core (right).}
+\caption{The numbers of nodes in different depths of lubm-250 (left) and yago-core (right).}
 \label{fig:graphdepth}
@@
 
-For the five test LUBM ontologies and the yago-core ontology, we record the total depth
-of the materialization graph for each ontology and the number of nodes in different depths.
-We have that all of the LUBM ontologies have the depth of 6 for their
-materialization graphs, while the materialization graph of the yago-core ontology
-has the depth of 9.
+\textbf{The MG-Depths of LUBM and YAGO.}
+For the five generated LUBM datasets and the yago-core ontology, we record the MG-depth
+for each ontology and the number of nodes in different depths.
+We have that all of the LUBM datasets have the MG-depth of 6,
+and the MG-depth of the yago-core ontology is 9.
 We use the histograms to graphically display the detailed data of lubm-250 and yago-core in Figure~\ref{fig:graphdepth},
@@
 the histograms denote the amount of nodes in each depth.
+%
+From the above results, we can find that the MG-depths are far less than
+the sizes of the input ontologies. In these cases, the input ontology size
+turns out to be the dominant factor for the reasoning efficiency.
+This is also shown in Figure~\ref{fig:reasoningtime}(left) for the LUBM datasets,
+where the reasoning times grow proportionally with the increasing of the number
+of universities.
+%
+Thus, it is hard for us to use the above experiments to
+observe the effects of MG-depths.
 
-From the above results, we can find that the graph depths are far less than
-the sizes of the input ontologies. Since the graph depth determines the computing
-time of Algorithm~$\mathsf{A}_{bsc}$ and Algorithm~$\mathsf{A}_{opt}$ as discussed
-at the beginning of this part,
-the test ontologies should be materialized efficiently using these two algorithms.
-The obvious difference of the reasoning times of the test ontologies is due to the limited memory space and the fixed number
-of processors and the inapplicability of the parallel assumption given in Section~\ref{sec:alg-bsc}.
-This results in that the computing
-time of ParallelDHL does not depend only on the number of iterations of \ref{alg4:updateG}
-of Algorithm~$\mathsf{A}_{prc}$ as analyzed in Section~\ref{sec:practicalAlg}.
-It depends on several factors: the balancing of workload, the delay of some processors,
-the I/O blocking, etc. Since these issues are not our focus, we do not analyze them in this work.
-On the other hand, the results of the graph depths
-indicate that we can further improve the performance of the materialization task by using more
-memory space and more processors.
+\textbf{Generating Ontologies of Different MG-Depths}.
+In order to examine the effects of MG-depths, we consider modifying the core LUBM ontology
+such that ontologies of different MG-depths can be obtained.
+Inspired by Example~\ref{exp:simpleC},
+we add to the core LUBM ontology the following three axioms to
+describe the reference relationships among articles:
+\begin{enumerate}[leftmargin=8ex,label=($\beta_{\arabic*}$),ref=$\beta_{\arabic*}$]
+  \item $\exists\texttt{referTo}.\texttt{CollegeArtical}\sqsubseteq\texttt{CollegeConference}$\label{ptu:a1}
+  \item $\exists\texttt{cite}.\top\sqsubseteq\texttt{CollegeSession}$\label{ptu:a2}
+  \item $\texttt{CollegeConference}\sqcap\texttt{CollegeSession}\sqsubseteq\texttt{CollegeArtical}$\label{ptu:a3}
+\end{enumerate}
+where axiom~\ref{ptu:a1}, axiom~\ref{ptu:a2} and axiom~\ref{ptu:a3} give the
+statements respectively: any article referring to a college article is published in a
+college conference, any article having citations is published in a college session,
+any article published in both of a college conference and a college session is
+a college article.
+
+We name the above new ontology PTU.
+Based on the new added axioms in PTU, we further modify the ontology-generator
+of LUBM such that a \emph{reference chain} of articles can be generated as follows:
+$\texttt{referTo}(\texttt{a}_i,\texttt{a}_{i+1})$ and
+$\texttt{cite}(\texttt{a}_i,\texttt{a}_{i+1})$ ($i\in\{0,1,2,...\}$),
+where $\texttt{a}_i$ denotes an article instance.
+As discussed in Section~\ref{sec:lubm-yago},
+the original core ontology of LUBM is tractable in parallel via
+Skolemization. Further, it can be checked that the concepts in PTU
+are all simple concepts. Thus, PTU belongs to the parallel tractability class.
+For comparison, we create another core ontology, named NPTU, which
+is not tractable in parallel. NPTU is almost the same as PTU except that
+axiom~\ref{ptu:a2} in PTU is replaced by the following axiom:
+\begin{enumerate}[leftmargin=8ex]
+  \item[($\beta_4$)] $\exists\texttt{cite}.\texttt{CollegeArtical}\sqsubseteq\texttt{CollegeSession}$\label{nptu:a1}
+\end{enumerate}
+which describes that any article citing a college article is published in a
+college session.
+It can be checked that NPTU does not follow the simple-concept restriction
+by referring to Example~\ref{exp:dhl}.
+
+The two core ontologies, PTU and NPTU,
+and the modified ontology-generator are available online.\footnote{https://github.com/quanzz/PT}
+To reduce the effects of ontology sizes, we generate five datasets of
+the similar sizes for PTU (resp., NPTU), denoted by
+ptu-$4m$-$i$ (resp., nptu-$4m$-$i$), $i\in\{1,2,4,8,16\}$,
+where $i$ is the number of article reference chains
+and $4m$ denotes that 4 million articles are involved averagely in all of the reference chains.
+The statistics of the these generated datasets are given in Table~\ref{tab:generated}.
+We can check from Table~\ref{tab:generated} that the datasets ptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$)
+have the close number of assertions while the MG-depths decrease proportionally. This is
+similar to the datasets nptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$).
+
+\begin{table}
+\centering
+\caption{The statistics of the generated datasets}
+\begin{tabular}{|l|r|r|r|r|r|r|}
+\hline
+ontology&$\sharp$concept&$\sharp$role&$\sharp$individual&$\sharp$axiom&$\sharp$assertion&MG-depth\\
+\hline
+ptu-$4m$-1&\multirow{10}{*}{51}&\multirow{10}{*}{34}&\multirow{10}{*}{4,000,440}&\multirow{10}{*}{102}&8,000,839&8,000,799\\
+ptu-$4m$-2&&&&&8,000,837&4,000,399\\
+ptu-$4m$-4&&&&&8,000,835&2,000,199\\
+ptu-$4m$-8&&&&&8,000,833&1,000,099\\
+ptu-$4m$-16&&&&&8,000,831&500,049\\
+nptu-$4m$-1&&&&&8,000,839&8,000,799\\
+nptu-$4m$-2&&&&&8,000,837&4,000,399\\
+nptu-$4m$-4&&&&&8,000,835&2,000,199\\
+nptu-$4m$-8&&&&&8,000,833&1,000,099\\
+nptu-$4m$-16&&&&&8,000,831&500,049\\
+\hline
+\end{tabular}
+\label{tab:generated}
+\end{table}
+
+\textbf{Experimental Results and Analysis}.
+We run RDFox and ParallelDHL on the generated datasets respectively. The detailed experimental results
+can be found at the address.\footnote{https://github.com/quanzz/PT} We give Table~\ref{tab:speedup} to compare the reasoning times and
+speedups\footnote{The speedup is computed by $\frac{T_1}{T_n}$ where $T_1$ is the computing time
+under 1 thread and $T_n$ is the computing time under $n$ thread(s).}
+of the two systems when handling nptu-$4m$-1 and ptu-$4m$-1.
+We further give Figure~\ref{fig:diffdepths} and Figure~\ref{fig:diffthreads} to show the trends of
+reasoning times. Specifically, the two line graphs of Figure~\ref{fig:diffdepths}
+show the reasoning times of RDFox and ParallelDHL over
+all the generated datasets with 24 threads being allocated;
+in Figure~\ref{fig:diffthreads},
+the abscissas of the two line graphs record the reciprocals of the numbers of threads, and
+the ordinates record the reasoning times over nptu-$4m$-1 and ptu-$4m$-1 respectively.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1\textwidth]{fig-diff-depths.eps}
+\caption{(left) the reasoning times over NPTU datasets; (right) the reasoning times over PTU datasets.}
+\label{fig:diffdepths}
+\end{center}
+\end{figure}
+
+It can be shown from Figure~\ref{fig:diffdepths} that MG-depths indeed determine
+the reasoning times.
+For the five datasets, nptu-$4m$-$i$, where $i\in\{1,2,4,8,16\}$, the experimental
+results show an obvious downtrend of the reasoning times with the declining of the MG-depths for
+both of RDFox and ParallelDHL (see Figure~\ref{fig:diffdepths}(left)).
+The downtrend of reasoning times also exists
+when handling the datasets ptu-$4m$-$i$ (see Figure~\ref{fig:diffdepths}(right)), where $i\in\{1,2,4,8,16\}$.
+Although the NPTU and PTU datasets are unrealistic in practice, these experiments indeed
+verify that MG-depths determines the reasoning time in parallel
+considering that the input ontology sizes are close.
+
+\begin{table}
+\centering
+\caption{The reasoning-times (seconds) and speedups}
+\begin{tabular}{|l|r|r|r|r|r|}
+\hline
+&\small$\sharp$thread&nptu-$4m$-1&speedup&ptu-$4m$-1&speedup\\
+\hline
+\multirow{5}{*}{ \textbf{RDFox}}&1&50.95&1&20.55&1\\
+                                &4&72.42&0.7&56.48&0.36\\
+                                &8&74.43&0.68&54.52&0.38\\
+                                &16&74.23&0.69&60.98&0.34\\
+                                &24&79.46&0.64&58.47&0.35\\
+\hline
+\multirow{5}{*}{ \small{\textbf{ParallelDHL}}}&1&135.79&1&252.13&1\\
+                                &4&142.34&0.95&147.2&1.71\\
+                                &8&145.04&0.93&102.83&2.45\\
+                                &16&156.05&0.87&56.48&4.46\\
+                                &24&172.81&078&48.19&5.23\\
+\hline
+\end{tabular}
+\label{tab:speedup}
+\end{table}
+
+We now discuss the issue of parallel tractability based on the experimental
+results of nptu-$4m$-1 and ptu-$4m$-1.
+From Figure~\ref{fig:diffthreads}(left),
+we can see that for both of RDFox and ParallelDHL the reasoning efficiency are not
+improved when several threads are allocated. On the contrary, with less than 24 threads are allocated,
+the materialization costs less time. In detail,
+the reasoning time of RDFox under 24 threads
+is 79.46 seconds, while it costs 50.95 seconds under only one thread.
+Further, the speedups of RDFox stay below 1 under more than 1 threads (see Table~\ref{tab:speedup}).
+This means that the reasoning times cannot reduced with more than 1 threads being
+allocated.
+This ``abnormal" situation also happens for ParallelDHL.
+This situation is caused by the issue of path twisting.
+The NPTU ontology does not follow the simple-concept restriction since
+concepts \texttt{CollegeConference} and \texttt{CollegeSession} are not simple.
+The materialization over nptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$) suffers from the issue
+of path twisting which is similar to the case in Example~\ref{exp:dhl}.
+Specifically, the axioms of the form \texttt{CollegeArtical}$(a_i)$ are
+the joint nodes in the twisted path.
+According to the analysis for Example~\ref{exp:dhl}, parallel computation can hardly
+handle this case. Moreover, the dataset nptu-$4m$-1 has only one
+article reference chain. This means that all
+the axioms of the form \texttt{CollegeArtical}$(a_i)$ actually
+appear in one path of the target materialization graph.
+Thus, they depends on each other and cannot be derived in parallel.
+On the other hand, the working mechanism of RDFox and ParallelDHL is based on
+a thread pool, where several threads are maintained and scheduled.
+The maintaining and scheduling of the thread pool also produce
+overheads, in particular, when the parallel computation
+cannot improve the total efficiency.
+This is why the materialization over nptu-$4m$-1 under one
+thread has a better performance.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1\textwidth]{fig-diff-threads.eps}
+\caption{(left) the reasoning times over nptu-$4m$-1; (right) the reasoning times over ptu-$4m$-1.}
+\label{fig:diffthreads}
+\end{center}
+\end{figure}
+
+For the dataset ptu-$4m$-1, the trends of reasoning times are different
+between RDFox and ParallelDHL.
+Similarly to the case of handling nptu-$4m$-1,
+the acceleration effect for RDFox is not outstanding
+over ptu-$4m$-1. The speedups under different numbers of threads stay around 1 (see Table~\ref{tab:speedup}).
+This means that reasoning times are not reduced with the increasing of the number of threads.
+The results of ParallelDHL show a better acceleration effect.
+From Table~\ref{tab:speedup}, with only one thread being allocated, ParallelDHL finishes
+the materialization on ptu-$4m$-1 in 135.79 seconds. When four and more threads
+are allocated, the reasoning performance is obviously improved.
+The maximal speedup reaches up to 5.23 under 24 threads.
+Specially, under more than 16 threads, ParallelDHL
+costs less time to finish the materialization with compared to RDFox.
+From Figure~\ref{fig:diffthreads}(right), there is an obvious downtrend of the reasoning times
+from one thread to 24 threads.
+The main reason of the difference between RDFox and ParallelDHL
+lays in that the PTU ontology is tractable in parallel and ParallelDHL
+is optimized based on the SWD paths. The PTU ontology follows the
+simple-concept restriction. Thus, there is no twisting path in
+the materialization graph of ptu-$4m$-1 although all articles are involved
+in one reference chain. This allows that the relation $S_{\textit{\!\tiny rch}}$ can be computed
+only once in the second iteration of \ref{alg3:updateG} of Algorithm~$\mathsf{A}_{\text{prc}}$
+when handling ptu-$4m$-1 (referring to the analysis for Example~\ref{exp:simpleC}).
+It can also be checked that all the axioms of the form \texttt{CollegeArtical}$(a_i)$ occur in
+an SWD path. Thus, the optimization based on SWD paths work when handling ptu-$4m$-1.
+For RDFox, since it is not optimized specially for this case, it performs the task of
+materialization over ptu-$4m$-1 similarly to that over nptu-$4m$-1;
+specifically, the axioms of the form \texttt{CollegeArtical}$(a_i)$ are derived sequentially.
+From Figure~\ref{fig:diffdepths}(right), we can see that the optimization used in ParallelDHL
+also leads to a better performance compared to
+RDFox when handling ptu-$4m$-1, ptu-$4m$-2 and ptu-$4m$-4 under 24 threads.
 

### 2018-02-21 parallel-tractability-J-v9/evaluation.tex
Proof-read eval section

--- 2018-02-07 parallel-tractability-J-v9/evaluation.tex
@@
 
-In the first part of this section, we analyze the well-known benchmark, LUBM, 
-and the real-world dataset, YAGO, and
-show the cases where these ontologies belong to the parallel tractability classes.
+In the first part of this section, we analyze the well-known benchmark LUBM
+and the real-world dataset YAGO and
+show cases where these ontologies belong to the parallel tractability classes.
+%
 In the second part, we evaluate the implementation of Algorithm~$\mathsf{A}_{\text{prc}}$
 and compare it to the reasoning system RDFox.
+%
+In the third part, we examine the effects of the depths of materialization graphs
+based on two modified versions of LUBM.
 
-\subsection{The Parallel Tractability of the LUBM Datasets and YAGO Ontologies}
+\subsection{Parallel Tractability of the LUBM Datasets and YAGO Ontologies}
+\label{sec:lubm-yago}
 
@@
 %
-The statements about properties in the LUBM core ontology, such as inverse property statements,
-can be rewritten into the datalog rules of the form (R1), (R2) and (R3) in Table~\ref{tab:dhl}.
-Most of the statements about classes can be rewritten into the datalog rules of the form (T1) and (T3)
-in Table~\ref{tab:dhl}. Five axioms have, however, the form $A\sqsubseteq\exists R.B$,
-which requires existentially quantified variables in the rule head when rewriting
-the axiom into a logic rule: $A(x)\rightarrow\exists y(R(x,y)\wedge B(y))$ ($\tau$),
+For the simple form of the core ontology,
+the statements about properties, such as inverse property statements,
+can be rewritten into datalog rules of the form (R1), (R2) and (R3) in Table~\ref{tab:dhl}.
+Most of the statements about classes can be rewritten into datalog rules of the form (T1) and (T3)
+in Table~\ref{tab:dhl}. There are six axioms of form (T2) as listed below:
+% \begin{enumerate}[leftmargin=8ex,label=($\alpha_{\arabic*}$),ref=$\alpha_{\arabic*}$]
+%   \item $\texttt{Person}\sqcap\texttt{CourseTaker}\sqsubseteq\texttt{Student}$\label{lubm:a1}
+%   \item $\texttt{Person}\sqcap\texttt{OrganizationWorker}\sqsubseteq\texttt{Employee}$\label{lubm:a2}
+%   \item $\texttt{Person}\sqcap\texttt{DepartmentHead}\sqsubseteq\texttt{Chair}$\label{lubm:a3}
+%   \item $\texttt{Person}\sqcap\texttt{ProgramHead}\sqsubseteq\texttt{Director}$\label{lubm:a4}
+%   \item $\texttt{Person}\sqcap\texttt{CourseAssistant}\sqsubseteq\texttt{TeachingAssistant}$\label{lubm:a5}
+%   \item $\texttt{Person}\sqcap\texttt{CollegeHead}\sqsubseteq\texttt{Dean}$\label{lubm:a6}
+% \end{enumerate}
+\begin{align}
+\texttt{Person}\sqcap\texttt{CourseTaker} & \sqsubseteq\texttt{Student}\label{lubm:a1}\tag{$\alpha_1$}\\
+\texttt{Person}\sqcap\texttt{OrganizationWorker} & \sqsubseteq\texttt{Employee}\label{lubm:a2}\tag{$\alpha_2$}\\
+\texttt{Person}\sqcap\texttt{DepartmentHead} & \sqsubseteq\texttt{Chair}\label{lubm:a3}\tag{$\alpha_3$}\\
+\texttt{Person}\sqcap\texttt{ProgramHead} & \sqsubseteq\texttt{Director}\label{lubm:a4}\tag{$\alpha_4$}\\
+\texttt{Person}\sqcap\texttt{CourseAssistant} & \sqsubseteq\texttt{TeachingAssistant}\label{lubm:a5}\tag{$\alpha_5$}\\
+\texttt{Person}\sqcap\texttt{CollegeHead} & \sqsubseteq\texttt{Dean}\label{lubm:a6}\tag{$\alpha_6$}
+\end{align}
+In the above axioms, the six concepts \texttt{CourseTaker}, \texttt{OrganizationWorker},
+\texttt{DepartmentHead}, \texttt{ProgramHead}, \texttt{CourseAssistant}
+and \texttt{CollegeHead} have corresponding definitions.
+For example, the concept \texttt{CourseTaker} is defined by:
+\begin{align}
+  \texttt{CourseTaker} & \equiv\exists\texttt{take}.\texttt{Course},\notag\\
+  \intertext{which is equivalent to the two axioms of simple form,}
+  \exists\texttt{take}.\texttt{Course} &
+                                         \sqsubseteq\texttt{CourseTaker} \mbox{ and}\label{coursetaker1}\\
+  \texttt{CourseTaker} &
+                         \sqsubseteq\exists\texttt{take}.\texttt{Course}.\label{coursetaker2}
+\end{align}
+Axiom~\eqref{coursetaker1} corresponds to form
+(T3). Axiom~\eqref{coursetaker2} requires existentially quantified
+variables in the rule head when rewriting the axiom into a logic rule:
+\begin{align}
+\texttt{CourseTaker}(x)\rightarrow\exists y(\texttt{take}(x,y)\wedge
+  \texttt{Course}(y))\label{tau}\tag{$\tau$}
+\end{align}
 where a free variable $y$ is introduced. This kind of axiom is a general case of (T4) in Table~\ref{tab:dhl}
@@
 Similarly to how we handle (T4), we can also eliminate the free variable $y$
-in rule $\tau$ via Skolemization, i.e., by replacing the variable $y$ with a new constant $o_R^{A,B}$.
-In this way, rule $\tau$ can be rewritten into $A(x)\rightarrow R(x,o_R^{A,B})\wedge B(o_R^{A,B})$.
-If we only focus on the materialization task, the rewriting approach via Skolemization guarantees the
-completeness and correctness \cite{GrauHKKMMW13}.
-On the other hand, rule $\tau$ is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
+in Rule~\eqref{tau} via Skolemization, i.e., by replacing the variable $y$ with a new constant $o$.
+In this way, Rule~\eqref{tau} can be rewritten into $\texttt{CourseTaker}(x)\rightarrow\texttt{take}(x,o)\wedge \texttt{Course}(o)$.
+If we only focus on the materialization task, the rewriting approach via Skolemization guarantees 
+correctness \cite{GrauHKKMMW13}.
+On the other hand, Rule~\eqref{tau} is not considered when using OWL RL reasoners to handle LUBM \cite{UrbaniKMHB12,WeaverH09}.
 In summary, if the rewriting approach is used for the above kind of rule,
+the core ontology can be expressed in DHL.
+We can further check that the concepts occurring in (\ref{lubm:a1}--\ref{lubm:a6})
+are all simple concepts. Thus,
 the materialization of LUBM datasets is tractable in parallel and can be handled by
-Algorithm~$\mathsf{A}_{\text{prc}}$.
+Algorithm~$\mathsf{A}_{\texttt{prc}}$.
 
@@
 \texttt{subRelationOf}, r_2)$,
-which are similar to the RDFS statements.
+which are similar to RDFS statements.
 A group of rules for reasoning over YAGO ontologies
-is specified as follows \cite{SuchanekKW08}:
-\begin{enumerate}[leftmargin=8ex,label=(\arabic*),ref=\arabic*]
-  \item $(r,\texttt{domain}, c), (x, r, y) \rightarrow (x,
-    \texttt{type}, c)$\label{yago:r1}
-  \item $(r,\texttt{range}, c), (x, r, y) \rightarrow (y,
-    \texttt{type}, c)$\label{yago:r2}
-  \item $(c_1, \texttt{subClassOf}, c_2), (x, \texttt{type}, c_1)
-    \rightarrow (x, \texttt{type}, c_2)$\label{yago:r3}
-  \item $(r_1, \texttt{subRelationOf}, r_2), (x, r_1, y) \rightarrow
-    (x, r_2, y)$\label{yago:r4}
-  \item $(r, \texttt{type}, \texttt{acyclicTransitiveRelation}), (x,
-    r, y), (y, r, z) \rightarrow (x, r, z)$\label{yago:r5}
-\end{enumerate}
-
+is specified by \citet{SuchanekKW08}:
+\begin{align}
+(r,\texttt{domain}, c), (x, r, y) & \rightarrow (x,
+    \texttt{type}, c)\label{yago:r1}\\
+(r,\texttt{range}, c), (x, r, y) & \rightarrow (y,
+    \texttt{type}, c)\label{yago:r2}\\
+(c_1, \texttt{subClassOf}, c_2), (x, \texttt{type}, c_1)
+    & \rightarrow (x, \texttt{type}, c_2)\label{yago:r3}\\
+(r_1, \texttt{subRelationOf}, r_2), (x, r_1, y) & \rightarrow
+    (x, r_2, y)\label{yago:r4}\\
+(r, \texttt{type}, \texttt{acyclicTransitiveRelation}), (x,
+    r, y), (y, r, z) & \rightarrow (x, r, z)\label{yago:r5}
+\end{align}
 According to the semantics given to YAGO \cite{SuchanekKW08}, the built-in properties in YAGO,
 i.e., \texttt{domain, range, subClassOf, subRelationOf} and \texttt{type} act in the same
-way as the terms in RDFS statements of the form (1--5) in Table~\ref{tab:rdfs}, respectively.
+way as the terms in RDFS statements of the form (S1--S5) in Table~\ref{tab:rdfs}, respectively.
 In contrast to RDFS, YAGO also allows for defining
@@
 class \texttt{acyclicTransitiveRelation}; further, any fact in some YAGO ontology cannot be
-described using blank nodes. By carefully checking the rules (\ref{yago:r1}--\ref{yago:r5}) for the reasoning over YAGO ontologies,
-one can see that these rules can be rewritten into the datalog rules
+described using blank nodes. By carefully checking the rules (\ref{yago:r1}--\ref{yago:r5}) for reasoning over YAGO ontologies,
+one can see that these rules can be rewritten into datalog rules
 of the form (T3),\footnote{Both of Rule (\ref{yago:r1}) and
@@
 expressed in ontology languages.
-These ontologies and datsets are collected from the Prot\'{e}g\'{e}
+These ontologies and datasets are collected from the Prot\'{e}g\'{e}
 ontology
@@
 \centering
-\caption{The statistics of the test ontologies}
+\caption{The statistics of the test ontologies, where $\sharp$concept
+  denotes the number of concept names, $\sharp$role the number of role
+  names, $\sharp$axiom the number of TBox and RBox axioms,
+  $\sharp$individual  the number of individuals and $\sharp$assertion
+  the number of assertions in the ontology\BG{I swapped the column
+    order to have TBox and ABox statistics together rather than
+    signature size and then number of axioms and assertions,
+    analogously for Table~\ref{tab:generated}}}
 \begin{tabular}{|l|r|r|r|r|r|}
 \hline
-ontology&$\sharp$concept&$\sharp$role&$\sharp$individual&$\sharp$axiom$^{a}$&$\sharp$assertion\\
+ontology&$\sharp$concept&$\sharp$role&$\sharp$axiom&$\sharp$individual&$\sharp$assertion\\
 \hline
-lubm-50&48&32&1,082,818&99&11,601,923\\
-lubm-100&48&32&2,179,766&99&23,837,579\\
-lubm-150&48&32&3,243,523&99&35,466,709\\
-lubm-200&48&32&4,341,309&99&46,537,764\\
-lubm-250&48&32&5,421,894&99&58,125,155\\
-yago-core&65,318&74&4,077,882&55,615&45,277,896\\
+lubm-50&\multirow{5}{*}{48}&\multirow{5}{*}{32}&\multirow{5}{*}{99}&1,082,818&11,601,923\\
+lubm-100&&&&2,179,766&23,837,579\\
+lubm-150&&&&3,243,523&35,466,709\\
+lubm-200&&&&4,341,309&46,537,764\\
+lubm-250&&&&5,421,894&58,125,155\\
 \hline
-\multicolumn{5}{l}{$^{a}$ \small the number of TBox and RBox axioms.}\\
+yago-core&65,318&74&55,615&4,077,882&45,277,896\\
+\hline
 \end{tabular}
@@
 \centering
-\caption{The reasoning-time results (seconds)}
+\caption{The reasoning time results in seconds}
+{\setlength{\tabcolsep}{1.5mm}
 \begin{tabular}{|l|r|r|r|r|r|r|r|}
@@
 &\small$\sharp$thread&lubm-50&lubm-100&lubm-150&lubm-200&lubm-250&yago-core\\
-\hline
-\multirow{5}{*}{ \textbf{RDFox}}&1&23.01&42.8&71.92&88.64&111.96&105.73\\
-                    &4&5.97&11.64&18.5&22.31&25.59&35.5\\
-                    &8&4.88&5.89&9.95&11.21&12.8&19.07\\
-                    &16&3.18&3.75&8.37&9.16&12.19&13.22\\
-                    &24&1.92&3.9&6.21&7.74&9.58&11.81\\
 \hline
@@
 \hline
-\end{tabular}
+\multirow{5}{*}{ \small{\textbf{RDFox}}}&1&23.01&42.8&71.92&88.64&111.96&105.73\\
+                    &4&5.97&11.64&18.5&22.31&25.59&35.5\\
+                    &8&4.88&5.89&9.95&11.21&12.8&19.07\\
+                    &16&3.18&3.75&8.37&9.16&12.19&13.22\\
+                    &24&1.92&3.9&6.21&7.74&9.58&11.81\\
+\hline
+\end{tabular}}
 \label{tab:result}
@@
 
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{prc}$}
+\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{\texttt{prc}}$}
 
 We implement a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{prc}$. Since ParallelDHL is evaluated in the
-platform which has the limited memory space and the fixed number of processors,
+based on Algorithm~$\mathsf{A}_{\texttt{prc}}$. Since ParallelDHL is
+evaluated on a
+platform which has limited memory space and a fixed number of processors,
 the parallel assumption given in Section~\ref{sec:alg-bsc} does not apply to ParallelDHL.
@@
 
-We run ParallelDHL on the LUBM and the YAGO ontologies to further analyze these
-two kinds of ontologies. We also use the reasoning system, RDFox \cite{MotikNPHO14},
-for comparison. We use five LUBM ontologies, lubm-50, lubm-100, lubm-150, lubm-200
-and lubm-250, where lubm-50 contains the descriptions of 50 universities (the other ontologies
-are explained similarly). For YAGO, we use its core version, denoted by yago-core.\footnote{
+We run ParallelDHL on LUBM and YAGO to further analyze these
+two kinds of ontologies. We also use the reasoning system RDFox \cite{MotikNPHO14}
+for comparison. We use five generated LUBM datasets, lubm-50, lubm-100, lubm-150, lubm-200
+and lubm-250, where lubm-50 contains the descriptions of 50
+universities (and analogously for the other datasets). For YAGO, we use its core version, denoted by yago-core.\footnote{
 The yago-core ontology is available at https://www.mpi-inf.mpg.de/departments/databases-and-information-systems/research/yago-naga/yago/downloads/.}
-The yago-core ontology is a subset of the full YAGO dataset without imports. It does not include the datatype statements, the links
+The yago-core ontology is a subset of the full YAGO dataset without any imports.
+It does not include datatype statements, the links
 between different data sources, the degrees of confidence and other kinds of
 annotations that we do not consider in this work. The statistics of the above ontologies is given in Table~\ref{tab:onto}.
-The running platform for this experiment is a server with a 50 Gigabyte RAM and 8 physical cores, in each core
-three logic threads can be allocated.
+The running platform for this experiment is a server with 50 Gigabyte RAM and eight physical cores, in each core
+three logical threads can be allocated.
 
-We run the LUBM ontologies and the yago-core ontology on RDFox and ParallelDHL with different numbers of
-threads (respectively 1,4,8,16 and 24).
-The reasoning times are collected in Table~\ref{tab:result}. We also give Figure~\ref{fig:reasoningtime} to
-clearly compare the two systems.
-In Figure~\ref{fig:reasoningtime}(left), the abscissa records the five LUBM ontologies,
-the ordinate records the reasoning times with 24 threads being allocated;
-In Figure~\ref{fig:reasoningtime}(right), the abscissa records the reciprocals of the numbers of threads, and
-the ordinate records the reasoning times over the yago-core ontology.
+We materialize the LUBM datasets and the yago-core ontology with ParallelDHL and RDFox using different numbers of
+threads (1, 4, 8, 16 and 24, respectively).
+The reasoning times are given in Table~\ref{tab:result}. We also give Figure~\ref{fig:reasoningtime} to
+graphically compare the two systems.
+In Figure~\ref{fig:reasoningtime}(left), the abscissa records the five
+LUBM datasets and
+the ordinate records the reasoning times in seconds with $24$ threads being allocated.
+In Figure~\ref{fig:reasoningtime}(right), the abscissa records the
+reciprocals \BG{Why the reciprocals and not directly the number of threads?} of the numbers of threads and
+the ordinate records the reasoning times in seconds over the yago-core ontology.
 
@@
 \begin{center}
-\includegraphics[width=1\textwidth]{fig-reasoningtime.eps}
-\caption{(left) the reasoning times over the LUBM ontologies; (right) the reasoning times over yago-core.}
+\includegraphics[width=\textwidth]{fig-reasoningtime.eps}
+\caption{(left) The reasoning times over the LUBM ontologies; (right)
+  the reasoning times over yago-core \BG{Could you swap the legend
+    entries for (left) so that ParallelDHL is given above RDFox as in (right)}}
 \label{fig:reasoningtime}
@@
 
-From Table~\ref{tab:result}, we can see that for lubm-50 these two systems perform equally well.
-For the other ontologies, ParallelDHL is comparable to RDFox with several threads being allocated.
-For lubm-250 and yago-core, ParallelDHL delays obviously when only one thread is allocated.
-The reason is that the computation of the relation $S_{\textit{\!\tiny rch}}$ occupies a large amount of time. When
-more threads are allocated, ParallelDHL has a better efficiency.
-Although ParallelDHL is not such optimized as RDFox, it also shows the scalability.
+From Table~\ref{tab:result}, we can see that for lubm-50 the two systems perform similarly.
+For the other ontologies, ParallelDHL scales comparable to RDFox with several threads being allocated.
+For lubm-250 and yago-core, when only one thread is used, ParallelDHL
+is significantly slower.
+The reason is that the computation of the relation $S_{\textit{\!\tiny rch}}$ requires a large amount of time. When
+four and more threads are allocated, ParallelDHL has a better efficiency.
+Although ParallelDHL is by far not as optimized as RDFox, it also shows the scalability.
 From the two line graphs in Figure~\ref{fig:reasoningtime},
@@
 
-\subsection{The Discussion of The Depths of Materialization Graphs}
+\subsection{Depths of Materialization Graphs}
 
-From the complexity analysis for Algorithm~$\mathsf{A}_{bsc}$, we have that the computing time of
-Algorithm~$\mathsf{A}_{bsc}$ depends on the number of iterations of \ref{alg1:updateG},
-which equals to the depth of the constructed materialization graph (see the proof of Theorem~\ref{theorem:a1}).
-Thus, the depth of the target materialization graph determines the computing time of
-Algorithm~$\mathsf{A}_{bsc}$. This conclusion also applies to Algorithm~$\mathsf{A}_{opt}$
-based on the analysis in Section~\ref{sec:opt}. In this part,
-we discuss the influence of the depths of the materialization graphs
-for the test ontologies.
+From the complexity analysis for Algorithm~$\mathsf{A}_{\texttt{bsc}}$ (see Section~\ref{sec:alg-bsc}),
+we have that the computing time of
+Algorithm~$\mathsf{A}_{\texttt{bsc}}$ depends on the sizes of the input ontologies and the
+numbers of iterations of \ref{alg1:updateG},
+which is equal to the \emph{depth of the target materialization
+  graph}, which we abbreviate with \emph{MG-depth} in the remainder.
+Thus, the MG-depth also determines the computing time of
+Algorithm~$\mathsf{A}_{\texttt{bsc}}$ in theory.
+This conclusion also applies to Algorithm~$\mathsf{A}_{\texttt{opt}}$ and Algorithm~$\mathsf{A}_{\texttt{prc}}$
+based on the analysis in Section~\ref{sec:opt} and Section~\ref{sec:practicalAlg}, respectively.
+In this part, we examine the effects of MG-depths.
 
@@
 \includegraphics[width=1\textwidth]{fig-graphdepth.eps}
-\caption{The statistics of the materialization graphs of lubm-250 (left) and yago-core (right).}
+\caption{The numbers of nodes in different depths of lubm-250 (left)
+  and yago-core (right) \BG{Could you move the right diagram away from
+  the border so that the axis marks do not run into the border?}}
 \label{fig:graphdepth}
@@
 
-For the five test LUBM ontologies and the yago-core ontology, we record the total depth
-of the materialization graph for each ontology and the number of nodes in different depths.
-We have that all of the LUBM ontologies have the depth of 6 for their
-materialization graphs, while the materialization graph of the yago-core ontology
-has the depth of 9.
-We use the histograms to graphically display the detailed data of lubm-250 and yago-core in Figure~\ref{fig:graphdepth},
-where for each of the two histograms
-the abscissa records the depths from the bottom of a materialization graph to the top,
-the histograms denote the amount of nodes in each depth.
+\textbf{MG-Depths of LUBM and YAGO.}
+For the five generated LUBM datasets and the yago-core ontology, we record the MG-depth
+for each ontology and the number of nodes in different depths.
+We have that all of the LUBM datasets have an MG-depth of 6,
+and the MG-depth of the yago-core ontology is 9.
+The two histograms in Figure~\ref{fig:graphdepth} visualize the number
+of nodes in different depths for lubm-250 and yago-core,
+respectively. 
+The abscissa records the depths from the bottom of a materialization
+graph to the top with
+the histograms showing the amount of nodes for each depth.
+%
+From the above results, we can see that the MG-depths are far less than
+the sizes of the input ontologies. In these cases, the input ontology size
+turns out to be the dominant factor for the reasoning efficiency.
+This is also shown in Figure~\ref{fig:reasoningtime}(left) for the LUBM datasets,
+where the reasoning times grow proportionally with the increasing number
+of universities.
+%
+Thus, the above experiments hardly show the effects of MG-depths.
 
-From the above results, we can find that the graph depths are far less than
-the sizes of the input ontologies. Since the graph depth determines the computing
-time of Algorithm~$\mathsf{A}_{bsc}$ and Algorithm~$\mathsf{A}_{opt}$ as discussed
-at the beginning of this part,
-the test ontologies should be materialized efficiently using these two algorithms.
-The obvious difference of the reasoning times of the test ontologies is due to the limited memory space and the fixed number
-of processors and the inapplicability of the parallel assumption given in Section~\ref{sec:alg-bsc}.
-This results in that the computing
-time of ParallelDHL does not depend only on the number of iterations of \ref{alg4:updateG}
-of Algorithm~$\mathsf{A}_{prc}$ as analyzed in Section~\ref{sec:practicalAlg}.
-It depends on several factors: the balancing of workload, the delay of some processors,
-the I/O blocking, etc. Since these issues are not our focus, we do not analyze them in this work.
-On the other hand, the results of the graph depths
-indicate that we can further improve the performance of the materialization task by using more
-memory space and more processors.
+\textbf{Generating Ontologies of Different MG-Depths}.
+In order to examine the effects of MG-depths, we consider modifying the core LUBM ontology
+such that ontologies of different MG-depths can be obtained.
+Inspired by Example~\ref{exp:simpleC},
+we add to the core LUBM ontology the following three axioms to
+describe the reference relationships among articles:\BG{I assume you
+  mean \texttt{CollegeArtic*le*} instead of the consistently used
+  \texttt{CollegeArtic*al*}. Global search and replace should fix that...}
+\begin{align}
+\exists\texttt{referTo}.\texttt{CollegeArtical} & \sqsubseteq\texttt{CollegeConference}\label{ptu:a1}\tag{$\beta_1$}\\
+\exists\texttt{cite}.\top & \sqsubseteq\texttt{CollegeSession}\label{ptu:a2}\tag{$\beta_2$}\\
+\texttt{CollegeConference}\sqcap\texttt{CollegeSession} & \sqsubseteq\texttt{CollegeArtical}\label{ptu:a3}\tag{$\beta_3$}
+\end{align}
+where Axiom~\eqref{ptu:a1} states that any article referring to a
+college article is published in a college conference,
+Axiom~\eqref{ptu:a2} defines that any article having citations is
+published in a college session and Axiom~\eqref{ptu:a3} states that
+any article published in both a college conference and a college
+session is a college article.
+
+We name the above new ontology PTU.
+Based on the newly added axioms in PTU, we further modify the ontology-generator
+of LUBM such that a \emph{reference chain} of articles can be generated as follows:
+$\texttt{referTo}(\texttt{a}_i,\texttt{a}_{i+1})$ and
+$\texttt{cite}(\texttt{a}_i,\texttt{a}_{i+1})$ ($i\in\{0,1,2,...\}$),
+where $\texttt{a}_i$ denotes an article instance.
+As discussed in Section~\ref{sec:lubm-yago},
+the original core ontology of LUBM is tractable in parallel via
+Skolemization. Further, it can be checked that the concepts in PTU
+are all simple concepts. Thus, PTU belongs to the parallel tractability class.
+For comparison, we create another core ontology, named NPTU, which
+is not tractable in parallel. NPTU is almost the same as PTU except that
+axiom~\ref{ptu:a2} in PTU is replaced by:
+\begin{align}
+\exists\texttt{cite}.\texttt{CollegeArtical}\sqsubseteq\texttt{CollegeSession}\label{nptu:a1}\tag{$\beta_4$}
+\end{align}
+which describes that any article citing a college article is published in a
+college session.
+It can be checked that NPTU does not satisfy the simple-concept
+restriction following analogous arguments to those given in Example~\ref{exp:dhl}.
+
+The two core ontologies, PTU and NPTU,
+and the modified ontology-generator are available online.\footnote{https://github.com/quanzz/PT}
+To reduce the effects of ontology sizes, we generate five datasets of
+the similar sizes for PTU (NPTU, respectively), denoted by
+ptu-$4m$-$i$ (nptu-$4m$-$i$, respectively), $i\in\{1,2,4,8,16\}$,
+where $i$ is the number of article reference chains
+and $4m$ denotes that $4$ million articles are involved on average in all of the reference chains.
+The statistics for the these generated datasets are given in Table~\ref{tab:generated}.
+Table~\ref{tab:generated} shows that the datasets ptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$)
+have an almost identical number of assertions while the MG-depth
+decreases proportionally, e.g., the MG-depth of ptu-$4m$-$1$ is
+$8,000,799$, while the MG-depth of ptu-$4m$-$16$ is just
+$500,049$. This is
+analogous for the datasets nptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$).
+
+\begin{table}
+\centering
+\caption{The statistics of the generated datasets}
+\begin{tabular}{|l|r|r|r|r|r|r|}
+\hline
+ontology&$\sharp$concept&$\sharp$role&$\sharp$axiom&$\sharp$individual&$\sharp$assertion&MG-depth\\
+\hline
+ptu-$4m$-1&\multirow{10}{*}{51}&\multirow{10}{*}{34}&\multirow{10}{*}{102}&\multirow{10}{*}{4,000,440}&8,000,839&8,000,799\\
+ptu-$4m$-2&&&&&8,000,837&4,000,399\\
+ptu-$4m$-4&&&&&8,000,835&2,000,199\\
+ptu-$4m$-8&&&&&8,000,833&1,000,099\\
+ptu-$4m$-16&&&&&8,000,831&500,049\\
+nptu-$4m$-1&&&&&8,000,839&8,000,799\\
+nptu-$4m$-2&&&&&8,000,837&4,000,399\\
+nptu-$4m$-4&&&&&8,000,835&2,000,199\\
+nptu-$4m$-8&&&&&8,000,833&1,000,099\\
+nptu-$4m$-16&&&&&8,000,831&500,049\\
+\hline
+\end{tabular}
+\label{tab:generated}
+\end{table}
+
+\textbf{Experimental Results and Analysis}.
+Table~\ref{tab:speedup} compares the reasoning times and
+speedups\footnote{The speedup is computed by $\frac{T_1}{T_n}$ where $T_1$ is the computing time
+using 1 thread and $T_n$ is the computing time using $n$ thread(s).}
+of ParallelDHL and RDFox for materializing ptu-$4m$-1 and
+nptu-$4m$-1.\footnote{The detailed experimental results are available
+  online at https://github.com/quanzz/PT.} 
+Figure~\ref{fig:diffdepths} and~\ref{fig:diffthreads} show the trends of
+reasoning times. Specifically, the two line graphs of Figure~\ref{fig:diffdepths}
+show the reasoning times in seconds of ParallelDHL and RDFox over
+all the generated datasets with 24 threads being allocated. In Figure~\ref{fig:diffthreads},
+the abscissas of the two line graphs record the reciprocals of the numbers of threads and
+the ordinates record the reasoning times over ptu-$4m$-1 and nptu-$4m$-1, respectively.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1\textwidth]{fig-diff-depths.eps}
+\caption{(left) reasoning times over the NPTU datasets; (right)
+  reasoning times over the PTU datasets\BG{Could we consistently have
+    first ParellelDHL and then RDFox in the legends (also in the text
+    I prefer to name ParallelDHL first as it is the main system
+    treated in the article). I would also suggest to first (left) have
+  the PTU and then (right) the NPTU diagram as this is the order now
+  consistently used in the text and PTU is the main focus here. }}
+\label{fig:diffdepths}
+\end{center}
+\end{figure}
+
+Figure~\ref{fig:diffdepths} shows that MG-depths indeed determines
+the reasoning times.
+For the five datasets nptu-$4m$-$i$, $i\in\{1,2,4,8,16\}$, the experimental
+results show an obvious downtrend of the reasoning times with declining MG-depths for
+both ParallelDHL and RDFox (see Figure~\ref{fig:diffdepths}(left))
+\BG{left should be adjusted to right if you follow my suggestion to
+  swap the two diagrams; analogously for the next sentence}.
+The downtrend of reasoning times also exists
+when handling the datasets ptu-$4m$-$i$, $i\in\{1,2,4,8,16\}$ (see Figure~\ref{fig:diffdepths}(right)).
+Although the NPTU and PTU datasets are unrealistic in practice, these experiments indeed
+verify that MG-depths determines the reasoning time in parallel
+considering that the input ontology sizes are close.\BG{For this whole
+paragraph (and the figures) I would prefer to first discuss the PT
+case (PTU) and then the non PT (NPTU) case and always list/name the main
+system (ParallelDHL) first and then RDFox. }
+
+\begin{table}
+\centering
+\caption{The reasoning-times in seconds and speedups}
+% \begin{tabular}{|l|r|r|r|r|r|}
+% \hline
+% &\small$\sharp$thread&nptu-$4m$-1&speedup&ptu-$4m$-1&speedup\\
+% \hline
+% \multirow{5}{*}{ \small{\textbf{ParallelDHL}}}&1&135.79&1&252.13&1\\
+%                                 &4&142.34&0.95&147.20&1.71\\
+%                                 &8&145.04&0.93&102.83&2.45\\
+%                                 &16&156.05&0.87&56.48&4.46\\
+%                                 &24&172.81&078\BG{decimal point missing?}&48.19&5.23\\
+% \hline
+% \multirow{5}{*}{ \textbf{RDFox}}&1&50.95&1&20.55&1\\
+%                                 &4&72.42&0.7&56.48&0.36\\
+%                                 &8&74.43&0.68&54.52&0.38\\
+%                                 &16&74.23&0.69&60.98&0.34\\
+%                                 &24&79.46&0.64&58.47&0.35\\
+% \hline
+% \end{tabular}
+\begin{tabular}{|l|r|r|r|r|r|}
+\hline
+&\small$\sharp$thread&ptu-$4m$-1&speedup&nptu-$4m$-1&speedup\\
+\hline
+\multirow{5}{*}{ \small{\textbf{ParallelDHL}}}&1&252.13&1&135.79&1\\
+                                &4&147.20&1.71&142.34&0.95\\
+                                &8&102.83&2.45&145.04&0.93\\
+                                &16&56.48&4.46&156.05&0.87\\
+                                &24&48.19&5.23&172.81&078\BG{decimal point missing?}\\
+\hline
+\multirow{5}{*}{ \textbf{RDFox}}&1&20.55&1&50.95&1\\
+                                &4&56.48&0.36&72.42&0.7\\
+                                &8&54.52&0.38&74.43&0.68\\
+                                &16&60.98&0.34&74.23&0.69\\
+                                &24&58.47&0.35&79.46&0.64\\
+\hline
+\end{tabular}
+\label{tab:speedup}
+\end{table}
+
+We now discuss the issue of parallel tractability based on the experimental
+results of ptu-$4m$-1 and nptu-$4m$-1.
+From Figure~\ref{fig:diffthreads}(left),
+we can see that for both ParallelDHL and RDFox the reasoning efficiency is not
+improved when several threads are allocated. On the contrary, with less than 24 threads allocated,
+materialization takes less time. In detail,
+the reasoning time of RDFox using $24$ threads
+is $79.46$ seconds, while it is $50.95$ seconds using only one thread.
+Further, the speedups of RDFox stay below $1$ using more than $1$ threads (see Table~\ref{tab:speedup}).
+This means that the reasoning times cannot be reduced with several threads being
+allocated.
+This maybe unexpected behavior is also shown by ParallelDHL and is caused by the issue of path twisting.
+The NPTU ontology does not follow the simple-concept restriction since
+the concepts \texttt{CollegeConference} and \texttt{CollegeSession} are not simple.
+The materialization of nptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$) suffers from the issue
+of path twisting which is similar to the case in Example~\ref{exp:dhl}.
+Specifically, the axioms of the form \texttt{CollegeArtical}$(a_i)$ are
+the joint nodes in the twisted path.
+According to the analysis in Example~\ref{exp:dhl}, parallel computation can hardly
+handle this case. Moreover, the dataset nptu-$4m$-1 has only one
+article reference chain. This means that all
+the axioms of the form \texttt{CollegeArtical}$(a_i)$ actually
+appear in one path of the target materialization graph.
+Thus, they depend on each other and cannot be derived in parallel.
+On the other hand, the working mechanism of ParallelDHL and RDFox is based on
+a thread pool, where several threads are maintained and scheduled.
+The maintenance and scheduling of the thread pool also produces
+overheads, in particular, when the parallel computation
+cannot improve the total efficiency.
+This is why the materialization of nptu-$4m$-1 using one$1$
+thread has a better performance.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1\textwidth]{fig-diff-threads.eps}
+\caption{(left) the reasoning times over nptu-$4m$-1; (right) the reasoning times over ptu-$4m$-1.}
+\label{fig:diffthreads}
+\end{center}
+\end{figure}
+
+For the dataset ptu-$4m$-1, the trends of reasoning times are different
+between ParallelDHL and RDFox.
+Similarly to the case of handling nptu-$4m$-1,
+RDFox does not benefit from the allocation of several threads for ptu-$4m$-1. The speedups under different numbers of threads stay around 1 (see Table~\ref{tab:speedup}).
+This means that reasoning times are not reduced with an increasing number of threads.
+ParallelDHL shows a better speedup effect. With only one allocated thread, ParallelDHL finishes
+the materialization of ptu-$4m$-1 in $135.79$ seconds (Table~\ref{tab:speedup}). When four and more threads
+are allocated, the reasoning performance is improved significantly.
+The maximal speedup is $5.23$ using $24$ threads.
+Specially, with $16$ or more threads, ParallelDHL
+requires less time to finish the materialization compared to RDFox.
+From Figure~\ref{fig:diffthreads}(right), there is an obvious downtrend of the reasoning times
+from one thread to $24$ threads.
+The main reason for the difference between ParallelDHL and RDFox
+is that the PTU ontology is tractable in parallel and ParallelDHL
+is optimized based on SWD paths. The PTU ontology follows the
+simple-concept restriction. Thus, there is no twisting path in
+the materialization graph of ptu-$4m$-1 although all articles are involved
+in one reference chain. This allows for computing the relation $S_{\textit{\!\tiny
+    rch}}$ only once in the second iteration of \ref{alg3:updateG} of Algorithm~$\mathsf{A}_{\texttt{prc}}$
+when handling ptu-$4m$-1 (referring to the analysis for Example~\ref{exp:simpleC}).
+It can also be checked that all the axioms of the form \texttt{CollegeArtical}$(a_i)$ occur in
+an SWD path. Thus, the optimization based on SWD paths works when handling ptu-$4m$-1.
+For RDFox, since it is not optimized specially for this case, it performs the task of
+materialization over ptu-$4m$-1 similarly to that over nptu-$4m$-1;
+specifically, the axioms of the form \texttt{CollegeArtical}$(a_i)$ are derived sequentially.
+From Figure~\ref{fig:diffdepths}(right), we can see that the optimization used in ParallelDHL
+also leads to a better performance compared to
+RDFox when handling ptu-$4m$-1, ptu-$4m$-2 and ptu-$4m$-4 using $24$ threads.
 

### 2018-02-21 parallel-tractability-J-v9/appendix.tex
checking appendix

@@
 Specifically, all the facts in $T_R^{0}(\textbf{I})$ have to be in $\mathcal{G}$ by \ref{alg1:addFacts}
-of $\mathsf{A}_{bsc}$.
+of $\mathsf{A}_{\text{bsc}}$.
 For $i>0$, suppose that the ground atoms in $T_R^{i}(\textbf{I})$ are in $\mathcal{G}$.
@@
 of all materialization graphs. One can further check that, for the materialization graph $\mathcal{G}$
-constructed by $\mathsf{A}_{bsc}$, its depth equals to the stage based on the induction above.
+constructed by $\mathsf{A}_{\text{bsc}}$, its depth is equal to the stage based on the induction above.
 Thus, $\mathcal{G}$ has the minimal depth among all the materialization graphs of $P$. \hfill$\Box$
@@
 \textbf{Theorem~\ref{theorem:a1}}
-\emph{For any datalog program $P$, $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ iff
+\emph{For any datalog program $P=\langle R, \textbf{I}\rangle$, $P\in\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$ iff
 $P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
@@
 
-($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{bsc}^{\psi}}$ means that $\mathsf{A}_{bsc}^{\psi}$ can return
+($\Rightarrow$) $P\in\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$ means that $\mathsf{A}_{\text{bsc}}^{\psi}$ can return
 a materialization graph $\mathcal{G}$ of $P$.
@@
 and, thus, upper-bounded by $\psi(|P|)$.
-If $\mathsf{A}_{bsc}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
+If $\mathsf{A}_{\text{bsc}}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
 should have a smaller depth compared with $\mathcal{G}$.
@@
 \emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{opt}$ halts and the output $\mathcal{G}$ is a materialization graph of $P$.}\\
+$\mathsf{A}_{\text{opt}}$ halts and output a materialization graph
+$\mathcal{G}$ of $P$.}\\
 
-\noindent\emph{Proof}: this lemma can be proved by two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{opt}$ is a materialization graph;
+\noindent\emph{Proof}: We prove the lemma in two stages:
+(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{\text{opt}}$ is a materialization graph;
 (2) $\mathcal{G}$ is a complete materialization graph.
-We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$.
+We first show that (1) holds by an induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{\text{opt}}$.
 
@@
 the $i^{th}$ ($i>1$) iteration is a materialization graph, denoted by $\mathcal{G}^{i}$.
-We have to show that the partial graph constructed after the $i+1^{th}$ iteration is
+We have to show that the partial graph constructed after the $(i+1)^{th}$ iteration is
 also a materialization graph, denoted by $\mathcal{G}^{i+1}$.
-The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{opt}$ by performing the step $(\textbf{\romannumeral3})$
-of Algorithm~$\mathsf{Opt}$.
+The partial graph $\mathcal{G}^{i+1}$ is updated in $\mathsf{A}_{\text{opt}}$ by performing Step $(\textbf{\romannumeral3})$
+of Algorithm~$\mathsf{OPT}$.
 Suppose that \texttt{rch}$(B_k,H)\in S_{\textit{\!\tiny rch}}$ is checked.
 It corresponds to the rule instantiation $B_1,..,B_k,..,B_n\rightarrow H$.
-Algorithm~$\mathsf{Opt}$ next checks that there exists a node $B'$ such that
+Algorithm~$\mathsf{OPT}$ next checks that there exists a node $B'$ such that
 \texttt{rch}$(B',B_k)\in S^*_{\!\tiny rch}$
 and $B'$ is in $\mathcal{G}$. This means that $B_k$ and $H$ are derivable.
-The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$ in three cases.
-(1) if $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
+The algorithm then adds new nodes $B_k$ and $H$ to $\mathcal{G}^{i}$
+according to three cases.
+(1) If $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
 then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
-(2) when neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
+(2) If neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
 then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
@@
 $\mathcal{G}^{i+1}$ is acyclic.
-(3) if $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
+(3) If $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
 $B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
@@
 
-To show that (2) holds, we use the same method in the proof for Lemma~\ref{lemma:a1}.
+To show that (2) holds, we use the same method as in the proof of Lemma~\ref{lemma:a1}.
 We want to show that all the ground atoms in $T_R^{i+1}(\textbf{I})$ have to be added to $\mathcal{G}$,
@@
 Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{opt}$.
+performing $\mathsf{A}_{\text{opt}}$.
 For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, $\alpha$ actually has a special SWD path
-of the length 1. This is because that all parents of $\alpha$ have been in $\mathcal{G}$.
+of length~$1$. This is because all parents of $\alpha$ have been in $\mathcal{G}$.
 According to the optimization strategy, $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg3:updateG}
-of $\mathsf{A}_{opt}$.\hfill$\Box$
+of $\mathsf{A}_{\text{opt}}$.\hfill$\Box$
 
@@
 \emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
+each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in
+$\mathcal{G}$ has an SWD path.}
+\BG{now in the main part:\\ For any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
+each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in
+$\mathcal{G}$ has an SWD path.\\ The proof just speaks about DL-Lite
+in general as the original claim. Adapt?}\\
 
-\noindent\emph{Proof}: this lemma can be proved by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.
+\noindent\emph{Proof}: We prove the lemma by an induction on applications of
+the datalog rules corresponding to DL-Lite axioms.}\\
 
@@
 applying (T1) and (T3). Thus, we conduct the induction by
-distinguish these two cases as follows.
+distinguishing these two cases as follows:
 
@@
 
-In both of Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
+For both Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
 node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
@@
 \emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
+$\mathcal{D}_{\textit{\text{dl-lite}}}\subseteq\mathcal{D}_{\mathsf{A}_{\text{opt}}^{\psi}}$.}\\
 
@@
 there always exists a poly-logarithmically bounded function $\psi$ such that
-$\mathsf{A}_{opt}^{\psi}$ can handle the materialization of $\mathcal{O}$,
+$\mathsf{A}_{\text{opt}}^{\psi}$ can handle the materialization of $\mathcal{O}$,
 since in any materialization graph, each node has an SWD path.
@@
 \emph{There exists a poly-logarithmically bounded function $\psi$ s.t.
-$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
+$\mathcal{D}_{\textit{\text{dhl}}}\subseteq\mathcal{D}_{\mathsf{A}_{\text{opt}}^{\psi}}$.}\\
 
@@
 It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{opt}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{opt}^\psi$.
+by performing $\mathcal{A}_{\text{opt}}^\psi$ for some poly-logarithmical function $\psi$, then
+the whole materialization can be handled by $\mathcal{A}_{\text{opt}}^\psi$.
 In what follows, we investigate the above two stages respectively, and show that,
@@
 As mentioned before, there exists an NC algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{opt}^\psi$
+Inspired by this, we can prove that \emph{$\mathcal{A}_{\text{opt}}^\psi$
 handles Stage~1 for some poly-logarithmical function $\psi$}.
@@
 Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
+the computations of (1) and (3) can be handled by $\mathcal{A}_{\text{opt}}^\psi$.
+Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{\text{opt}}^\psi$.
 Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
+such that $\mathcal{A}_{\text{opt}}^\psi$ handles Stage~1.
 
@@
 instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{opt}$ in at most two iterations.
+Thus, Stage~2 can be handled by $\mathcal{A}_{\text{opt}}$ in at most two iterations.
 Based on the above analysis, this theorem holds.
@@
 \textbf{Theorem~\ref{theorem:dhlplus}}
-\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{opt}^{\psi}}$.}\\
+\emph{There exists a poly-logarithmically bounded function $\psi$ s.t. $\mathcal{D}_{\textit{\text{dhl}}(\circ)}\subseteq\mathcal{D}_{\mathsf{A}_{\text{opt}}^{\psi}}$.}\\
 
@@
 
-Our target is to show that $\mathcal{A}_{opt}^\psi$ handles Stage~1. To this end, we also
+Our target is to show that $\mathcal{A}_{\text{opt}}^\psi$ handles Stage~1. To this end, we also
 distinguish all roles by whether they are transitively influenced. Since we have to consider
@@
 least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{opt}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{opt}^\psi$.
+Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{\text{opt}}^\psi$.
+Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{\text{opt}}^\psi$.
 In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{opt}^\psi$ handles Stage~1.
+such that $\mathcal{A}_{\text{opt}}^\psi$ handles Stage~1.
 
@@
 (2) $\mathcal{G}$ is a complete materialization graph.
-One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{opt}$
+One can show that (1) holds by performing the same induction on the iterations of \ref{alg3:updateG} of $\mathsf{A}_{\text{opt}}$
 (see the proof of Lemma~\ref{lemma:a3}). This is because that

### 2018-02-22 parallel-tractability-J-v9/evaluation.tex
unified the subscripts with \text{}

@@
 the materialization of LUBM datasets is tractable in parallel and can be handled by
-Algorithm~$\mathsf{A}_{\texttt{prc}}$.
+Algorithm~$\mathsf{A}_{\text{prc}}$.
 
@@
 for any well-constructed class of YAGO ontologies,
-Algorithm~$\mathsf{A}_{\texttt{prc}}$
+Algorithm~$\mathsf{A}_{\text{prc}}$
 can handle all of the ontologies in the class.
@@
   $\sharp$individual  the number of individuals and $\sharp$assertion
-  the number of assertions in the ontology\BG{I swapped the column
-    order to have TBox and ABox statistics together rather than
-    signature size and then number of axioms and assertions,
-    analogously for Table~\ref{tab:generated}}}
+  the number of assertions in the ontology}
 \begin{tabular}{|l|r|r|r|r|r|}
@@
 
-\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{\texttt{prc}}$}
+\subsection{Evaluating the Implementation of Algorithm~$\mathsf{A}_{\text{prc}}$}
 
 We implement a prototype system ParallelDHL for DHL$(\circ)$ materialization
-based on Algorithm~$\mathsf{A}_{\texttt{prc}}$. Since ParallelDHL is
+based on Algorithm~$\mathsf{A}_{\text{prc}}$. Since ParallelDHL is
 evaluated on a
@@
 the ordinate records the reasoning times in seconds with $24$ threads being allocated.
-In Figure~\ref{fig:reasoningtime}(right), the abscissa records the
-reciprocals \BG{Why the reciprocals and not directly the number of threads?} of the numbers of threads and
+In Figure~\ref{fig:reasoningtime}(right), the abscissa records the numbers of threads and
 the ordinate records the reasoning times in seconds over the yago-core ontology.
@@
 \caption{(left) The reasoning times over the LUBM ontologies; (right)
-  the reasoning times over yago-core \BG{Could you swap the legend
-    entries for (left) so that ParallelDHL is given above RDFox as in (right)}}
+  the reasoning times over yago-core}
 \label{fig:reasoningtime}
@@
 Although ParallelDHL is by far not as optimized as RDFox, it also shows the scalability.
-From the two line graphs in Figure~\ref{fig:reasoningtime},
-we can see a linear trend of the reasoning times of both RDFox and ParallelDHL.
+For both of RDFox and ParallelDHL,
+we can see a linear trend of the reasoning times
+in Figure~\ref{fig:reasoningtime}(left) and
+an obvious downtrend of the reasoning times with an increasing number of threads
+in Figure~\ref{fig:reasoningtime}(right).
 This also indicates that ParallelDHL will finish the materialization tasks on the test ontologies
@@
 
-From the complexity analysis for Algorithm~$\mathsf{A}_{\texttt{bsc}}$ (see Section~\ref{sec:alg-bsc}),
+From the complexity analysis for Algorithm~$\mathsf{A}_{\text{bsc}}$ (see Section~\ref{sec:alg-bsc}),
 we have that the computing time of
-Algorithm~$\mathsf{A}_{\texttt{bsc}}$ depends on the sizes of the input ontologies and the
+Algorithm~$\mathsf{A}_{\text{bsc}}$ depends on the sizes of the input ontologies and the
 numbers of iterations of \ref{alg1:updateG},
@@
 Thus, the MG-depth also determines the computing time of
-Algorithm~$\mathsf{A}_{\texttt{bsc}}$ in theory.
-This conclusion also applies to Algorithm~$\mathsf{A}_{\texttt{opt}}$ and Algorithm~$\mathsf{A}_{\texttt{prc}}$
+Algorithm~$\mathsf{A}_{\text{bsc}}$ in theory.
+This conclusion also applies to Algorithm~$\mathsf{A}_{\text{opt}}$ and Algorithm~$\mathsf{A}_{\text{prc}}$
 based on the analysis in Section~\ref{sec:opt} and Section~\ref{sec:practicalAlg}, respectively.
@@
 \caption{The numbers of nodes in different depths of lubm-250 (left)
-  and yago-core (right) \BG{Could you move the right diagram away from
-  the border so that the axis marks do not run into the border?}}
+  and yago-core (right)}
 \label{fig:graphdepth}
@@
 
-\textbf{Generating Ontologies of Different MG-Depths}.
-In order to examine the effects of MG-depths, we consider modifying the core LUBM ontology
-such that ontologies of different MG-depths can be obtained.
-Inspired by Example~\ref{exp:simpleC},
-we add to the core LUBM ontology the following three axioms to
-describe the reference relationships among articles:\BG{I assume you
-  mean \texttt{CollegeArtic*le*} instead of the consistently used
-  \texttt{CollegeArtic*al*}. Global search and replace should fix that...}
-\begin{align}
-\exists\texttt{referTo}.\texttt{CollegeArtical} & \sqsubseteq\texttt{CollegeConference}\label{ptu:a1}\tag{$\beta_1$}\\
-\exists\texttt{cite}.\top & \sqsubseteq\texttt{CollegeSession}\label{ptu:a2}\tag{$\beta_2$}\\
-\texttt{CollegeConference}\sqcap\texttt{CollegeSession} & \sqsubseteq\texttt{CollegeArtical}\label{ptu:a3}\tag{$\beta_3$}
-\end{align}
-where Axiom~\eqref{ptu:a1} states that any article referring to a
-college article is published in a college conference,
-Axiom~\eqref{ptu:a2} defines that any article having citations is
-published in a college session and Axiom~\eqref{ptu:a3} states that
-any article published in both a college conference and a college
-session is a college article.
-
-We name the above new ontology PTU.
-Based on the newly added axioms in PTU, we further modify the ontology-generator
-of LUBM such that a \emph{reference chain} of articles can be generated as follows:
-$\texttt{referTo}(\texttt{a}_i,\texttt{a}_{i+1})$ and
-$\texttt{cite}(\texttt{a}_i,\texttt{a}_{i+1})$ ($i\in\{0,1,2,...\}$),
-where $\texttt{a}_i$ denotes an article instance.
-As discussed in Section~\ref{sec:lubm-yago},
-the original core ontology of LUBM is tractable in parallel via
-Skolemization. Further, it can be checked that the concepts in PTU
-are all simple concepts. Thus, PTU belongs to the parallel tractability class.
-For comparison, we create another core ontology, named NPTU, which
-is not tractable in parallel. NPTU is almost the same as PTU except that
-axiom~\ref{ptu:a2} in PTU is replaced by:
-\begin{align}
-\exists\texttt{cite}.\texttt{CollegeArtical}\sqsubseteq\texttt{CollegeSession}\label{nptu:a1}\tag{$\beta_4$}
-\end{align}
-which describes that any article citing a college article is published in a
-college session.
-It can be checked that NPTU does not satisfy the simple-concept
-restriction following analogous arguments to those given in Example~\ref{exp:dhl}.
-
-The two core ontologies, PTU and NPTU,
-and the modified ontology-generator are available online.\footnote{https://github.com/quanzz/PT}
-To reduce the effects of ontology sizes, we generate five datasets of
-the similar sizes for PTU (NPTU, respectively), denoted by
-ptu-$4m$-$i$ (nptu-$4m$-$i$, respectively), $i\in\{1,2,4,8,16\}$,
-where $i$ is the number of article reference chains
-and $4m$ denotes that $4$ million articles are involved on average in all of the reference chains.
-The statistics for the these generated datasets are given in Table~\ref{tab:generated}.
-Table~\ref{tab:generated} shows that the datasets ptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$)
-have an almost identical number of assertions while the MG-depth
-decreases proportionally, e.g., the MG-depth of ptu-$4m$-$1$ is
-$8,000,799$, while the MG-depth of ptu-$4m$-$16$ is just
-$500,049$. This is
-analogous for the datasets nptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$).
-
 \begin{table}
@@
 
+\textbf{Generating Ontologies of Different MG-Depths}.
+In order to examine the effects of MG-depths, we consider modifying the core LUBM ontology
+such that ontologies of different MG-depths can be obtained.
+Inspired by Example~\ref{exp:simpleC},
+we add to the core LUBM ontology the following three axioms to
+describe the reference relationships among articles:
+\begin{align}
+\exists\texttt{referTo}.\texttt{CollegeArticle} & \sqsubseteq\texttt{CollegeConference}\label{ptu:a1}\tag{$\beta_1$}\\
+\exists\texttt{cite}.\top & \sqsubseteq\texttt{CollegeSession}\label{ptu:a2}\tag{$\beta_2$}\\
+\texttt{CollegeConference}\sqcap\texttt{CollegeSession} & \sqsubseteq\texttt{CollegeArticle}\label{ptu:a3}\tag{$\beta_3$}
+\end{align}
+where Axiom~\eqref{ptu:a1} states that any article referring to a
+college article is published in a college conference,
+Axiom~\eqref{ptu:a2} defines that any article having citations is
+published in a college session and Axiom~\eqref{ptu:a3} states that
+any article published in both a college conference and a college
+session is a college article.
+
+We name the above new ontology PTU.
+Based on the newly added axioms in PTU, we further modify the ontology-generator
+of LUBM such that a \emph{reference chain} of articles can be generated as follows:
+$\texttt{referTo}(\texttt{a}_i,\texttt{a}_{i+1})$ and
+$\texttt{cite}(\texttt{a}_i,\texttt{a}_{i+1})$ ($i\in\{0,1,2,...\}$),
+where $\texttt{a}_i$ denotes an article instance.
+As discussed in Section~\ref{sec:lubm-yago},
+the original core ontology of LUBM is tractable in parallel via
+Skolemization. Further, it can be checked that the concepts in PTU
+are all simple concepts. Thus, PTU belongs to the parallel tractability class.
+For comparison, we create another core ontology, named NPTU, which
+is not tractable in parallel. NPTU is almost the same as PTU except that
+Axiom~\eqref{ptu:a2} in PTU is replaced by:
+\begin{align}
+\exists\texttt{cite}.\texttt{CollegeArticle}\sqsubseteq\texttt{CollegeSession}\label{nptu:a1}\tag{$\beta_4$}
+\end{align}
+which describes that any article citing a college article is published in a
+college session.
+It can be checked that NPTU does not satisfy the simple-concept
+restriction following analogous arguments to those given in Example~\ref{exp:dhl}.
+
+The two core ontologies, PTU and NPTU,
+and the modified ontology-generator are available online.\footnote{https://github.com/quanzz/PT}
+To reduce the effects of ontology sizes, we generate five datasets of
+the similar sizes for PTU (NPTU, respectively), denoted by
+ptu-$4m$-$i$ (nptu-$4m$-$i$, respectively), $i\in\{1,2,4,8,16\}$,
+where $i$ is the number of article reference chains
+and $4m$ denotes that $4$ million articles are involved on average in all of the reference chains.
+The statistics for the generated datasets are given in Table~\ref{tab:generated}.
+Table~\ref{tab:generated} shows that the datasets ptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$)
+have an almost identical number of assertions while the MG-depth
+decreases proportionally, e.g., the MG-depth of ptu-$4m$-$1$ is
+$8,000,799$, while the MG-depth of ptu-$4m$-$16$ is just
+$500,049$. This is
+analogous for the datasets nptu-$4m$-$i$ ($i\in\{1,2,4,8,16\}$).
+
 \textbf{Experimental Results and Analysis}.
@@
 all the generated datasets with 24 threads being allocated. In Figure~\ref{fig:diffthreads},
-the abscissas of the two line graphs record the reciprocals of the numbers of threads and
+the abscissas of the two line graphs record the numbers of threads and
 the ordinates record the reasoning times over ptu-$4m$-1 and nptu-$4m$-1, respectively.
@@
 \includegraphics[width=1\textwidth]{fig-diff-depths.eps}
-\caption{(left) reasoning times over the NPTU datasets; (right)
-  reasoning times over the PTU datasets\BG{Could we consistently have
-    first ParellelDHL and then RDFox in the legends (also in the text
-    I prefer to name ParallelDHL first as it is the main system
-    treated in the article). I would also suggest to first (left) have
-  the PTU and then (right) the NPTU diagram as this is the order now
-  consistently used in the text and PTU is the main focus here. }}
+\caption{(left) reasoning times over the PTU datasets; (right)
+  reasoning times over the NPTU datasets}
 \label{fig:diffdepths}
@@
 the reasoning times.
-For the five datasets nptu-$4m$-$i$, $i\in\{1,2,4,8,16\}$, the experimental
+For the five datasets ptu-$4m$-$i$, $i\in\{1,2,4,8,16\}$, the experimental
 results show an obvious downtrend of the reasoning times with declining MG-depths for
-both ParallelDHL and RDFox (see Figure~\ref{fig:diffdepths}(left))
-\BG{left should be adjusted to right if you follow my suggestion to
-  swap the two diagrams; analogously for the next sentence}.
+both ParallelDHL and RDFox (see Figure~\ref{fig:diffdepths}(left)).
 The downtrend of reasoning times also exists
-when handling the datasets ptu-$4m$-$i$, $i\in\{1,2,4,8,16\}$ (see Figure~\ref{fig:diffdepths}(right)).
-Although the NPTU and PTU datasets are unrealistic in practice, these experiments indeed
+when handling the datasets nptu-$4m$-$i$, $i\in\{1,2,4,8,16\}$ (see Figure~\ref{fig:diffdepths}(right)).
+Although the PTU and NPTU datasets are unrealistic in practice, these experiments indeed
 verify that MG-depths determines the reasoning time in parallel
-considering that the input ontology sizes are close.\BG{For this whole
-paragraph (and the figures) I would prefer to first discuss the PT
-case (PTU) and then the non PT (NPTU) case and always list/name the main
-system (ParallelDHL) first and then RDFox. }
+considering that the input ontology sizes are close.
 
@@
                                 &16&56.48&4.46&156.05&0.87\\
-                                &24&48.19&5.23&172.81&078\BG{decimal point missing?}\\
+                                &24&48.19&5.23&172.81&0.78\\
 \hline
@@
 results of ptu-$4m$-1 and nptu-$4m$-1.
-From Figure~\ref{fig:diffthreads}(left),
+For the dataset ptu-$4m$-1, the trends of reasoning times are different
+between ParallelDHL and RDFox.
+It can be checked from Table~\ref{tab:speedup} that
+RDFox does not benefit from the allocation of several threads for ptu-$4m$-1;
+the speedups under different numbers of threads stay around 1.
+This means that reasoning times are not reduced with an increasing number of threads.
+ParallelDHL shows a better speedup effect. With only one allocated thread, ParallelDHL finishes
+the materialization of ptu-$4m$-1 in $135.79$ seconds (Table~\ref{tab:speedup}). When four and more threads
+are allocated, the reasoning performance is improved significantly.
+The maximal speedup is $5.23$ using $24$ threads.
+Specially, with $16$ or more threads, ParallelDHL
+requires less time to finish the materialization compared to RDFox.
+From Figure~\ref{fig:diffthreads}(left), there is an obvious downtrend of the reasoning times
+from one thread to $24$ threads.
+The main reason for the difference between ParallelDHL and RDFox
+is that the PTU ontology is tractable in parallel and ParallelDHL
+is optimized based on SWD paths. The PTU ontology follows the
+simple-concept restriction. Thus, there is no twisting path in
+the materialization graph of ptu-$4m$-1 although all articles are involved
+in one reference chain. This allows for computing the relation $S_{\textit{\!\tiny
+    rch}}$ only once in the second iteration of \ref{alg3:updateG} of Algorithm~$\mathsf{A}_{\text{prc}}$
+when handling ptu-$4m$-1 (referring to the analysis for Example~\ref{exp:simpleC}).
+It can also be checked that all the axioms of the form \texttt{CollegeArticle}$(a_i)$ occur in
+an SWD path. Thus, the optimization based on SWD paths works when handling ptu-$4m$-1.
+For RDFox, since it is not optimized specially for this case, it performs the task of
+materialization over ptu-$4m$-1 similarly to that over nptu-$4m$-1;
+specifically, the axioms of the form \texttt{CollegeArticle}$(a_i)$ are derived sequentially.
+From Figure~\ref{fig:diffdepths}(left), we can see that the optimization used in ParallelDHL
+also leads to a better performance compared to
+RDFox when handling ptu-$4m$-1, ptu-$4m$-2 and ptu-$4m$-4 using $24$ threads.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1\textwidth]{fig-diff-threads.eps}
+\caption{(left) the reasoning times over nptu-$4m$-1; (right) the reasoning times over ptu-$4m$-1.}
+\label{fig:diffthreads}
+\end{center}
+\end{figure}
+
+From Figure~\ref{fig:diffthreads}(right),
 we can see that for both ParallelDHL and RDFox the reasoning efficiency is not
@@
 of path twisting which is similar to the case in Example~\ref{exp:dhl}.
-Specifically, the axioms of the form \texttt{CollegeArtical}$(a_i)$ are
+Specifically, the axioms of the form \texttt{CollegeArticle}$(a_i)$ are
 the joint nodes in the twisted path.
@@
 article reference chain. This means that all
-the axioms of the form \texttt{CollegeArtical}$(a_i)$ actually
+the axioms of the form \texttt{CollegeArticle}$(a_i)$ actually
 appear in one path of the target materialization graph.
@@
 cannot improve the total efficiency.
-This is why the materialization of nptu-$4m$-1 using one$1$
+This is why the materialization of nptu-$4m$-1 using $1$
 thread has a better performance.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1\textwidth]{fig-diff-threads.eps}
-\caption{(left) the reasoning times over nptu-$4m$-1; (right) the reasoning times over ptu-$4m$-1.}
-\label{fig:diffthreads}
-\end{center}
-\end{figure}
-
-For the dataset ptu-$4m$-1, the trends of reasoning times are different
-between ParallelDHL and RDFox.
-Similarly to the case of handling nptu-$4m$-1,
-RDFox does not benefit from the allocation of several threads for ptu-$4m$-1. The speedups under different numbers of threads stay around 1 (see Table~\ref{tab:speedup}).
-This means that reasoning times are not reduced with an increasing number of threads.
-ParallelDHL shows a better speedup effect. With only one allocated thread, ParallelDHL finishes
-the materialization of ptu-$4m$-1 in $135.79$ seconds (Table~\ref{tab:speedup}). When four and more threads
-are allocated, the reasoning performance is improved significantly.
-The maximal speedup is $5.23$ using $24$ threads.
-Specially, with $16$ or more threads, ParallelDHL
-requires less time to finish the materialization compared to RDFox.
-From Figure~\ref{fig:diffthreads}(right), there is an obvious downtrend of the reasoning times
-from one thread to $24$ threads.
-The main reason for the difference between ParallelDHL and RDFox
-is that the PTU ontology is tractable in parallel and ParallelDHL
-is optimized based on SWD paths. The PTU ontology follows the
-simple-concept restriction. Thus, there is no twisting path in
-the materialization graph of ptu-$4m$-1 although all articles are involved
-in one reference chain. This allows for computing the relation $S_{\textit{\!\tiny
-    rch}}$ only once in the second iteration of \ref{alg3:updateG} of Algorithm~$\mathsf{A}_{\texttt{prc}}$
-when handling ptu-$4m$-1 (referring to the analysis for Example~\ref{exp:simpleC}).
-It can also be checked that all the axioms of the form \texttt{CollegeArtical}$(a_i)$ occur in
-an SWD path. Thus, the optimization based on SWD paths works when handling ptu-$4m$-1.
-For RDFox, since it is not optimized specially for this case, it performs the task of
-materialization over ptu-$4m$-1 similarly to that over nptu-$4m$-1;
-specifically, the axioms of the form \texttt{CollegeArtical}$(a_i)$ are derived sequentially.
-From Figure~\ref{fig:diffdepths}(right), we can see that the optimization used in ParallelDHL
-also leads to a better performance compared to
-RDFox when handling ptu-$4m$-1, ptu-$4m$-2 and ptu-$4m$-4 using $24$ threads.
 

### 2018-02-22 parallel-tractability-J-v9/optimizedAlgo.tex
unified the subscripts with \text{}

@@
 One can check that $|P^*|$ could be the quadratic or cubic in the number of constants occurring in $P$.
-Recall the analysis of the parallel complexity of Algorithm~$\mathsf{A}_{bsc}$ and Algorithm~$\mathsf{A}_{\text{opt}}$.
+Recall the analysis of the parallel complexity of Algorithm~$\mathsf{A}_{\text{bsc}}$ and Algorithm~$\mathsf{A}_{\text{opt}}$.
 The number of constants is at most $|\textbf{I}|e$ where $e$ denotes the maximum arity of any predicate in $\textbf{I}$.
@@
 Otherwise, the algorithm would
-perform as Algorithm~$\mathsf{A}_{bsc}$ and, thus, the
+perform as Algorithm~$\mathsf{A}_{\text{bsc}}$ and, thus, the
 optimizations used in Algorithm~$\mathsf{A}_{\text{opt}}$ cannot further work.

### 2018-02-22 parallel-tractability-J-v9/relatedWork.tex
unified the subscripts with \text{}

--- 2018-02-07 parallel-tractability-J-v9/relatedWork.tex
@@
 RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
+Algorithm~$\mathsf{A}_{\text{bsc}}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
+The difference lies in that, a group of rule instantiations are handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{\text{bsc}}$, each rule instantiation is assigned to a unique processor.
 Analogous to the method used in RDFox, ParallelDHL is also implemented by assigning a group of

### 2018-02-22 parallel-tractability-J-v9/appendix.tex
revised the eval section
checking appendix

@@
 \emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
-(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
+(1) $\mathsf{A}_{\text{bsc}}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
 (2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\

### 2018-02-22 parallel-tractability-J-v9/appendix.tex

@@
 \emph{For any datalog program $P=\langle R, \textbf{I}\rangle$, $P\in\mathcal{D}_{\mathsf{A}_{\text{bsc}}^{\psi}}$ iff
-$P$ has a materialization graph whose depth is upper-bounded by $\psi(|P|)$.}\\
+$P$ has a materialization graph whose depth is upper-bounded by $\psi(|\textbf{I}|)$.}\\
 
@@
 We define the depths of nodes iteratively as follows:
-for each explicit node $v$, \texttt{depth}($v$)=0;
+for each of the original node $v$, \texttt{depth}($v$)=0;
 for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
@@
 a materialization graph $\mathcal{G}$ of $P$.
-Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|P|)$.
-Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|P|)$.
+Recall that the number of iterations of \ref{alg1:updateG} is bounded by $\psi(|\textbf{I}|)$.
+Thus \texttt{depth}($\mathcal{G}$) is also bounded by $\psi(|\textbf{I}|)$.
 
 ($\Leftarrow$) Suppose $P$ has a materialization graph $\mathcal{G}$ whose depth
-is upper-bounded by $\psi(|P|)$.
+is upper-bounded by $\psi(|\textbf{I}|)$.
 If $\mathcal{G}$ has the minimal depth among other materialization graphs of $P$,
 the number of iterations of \ref{alg1:updateG} is also \texttt{depth}($\mathcal{G}$) (Lemma~\ref{lemma:a1})
-and, thus, upper-bounded by $\psi(|P|)$.
+and, thus, upper-bounded by $\psi(|\textbf{I}|)$.
 If $\mathsf{A}_{\text{bsc}}$ dose not return $\mathcal{G}$, then the returned graph $\mathcal{G}'$
@@
 \emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$,
-$\mathsf{A}_{\text{opt}}$ halts and output a materialization graph
+$\mathsf{A}_{\text{opt}}$ halts and outputs a materialization graph
 $\mathcal{G}$ of $P$.}\\
@@
 
-\emph{Base case}. Initially, $\mathcal{G}$ only contains all the explicit nodes.
+\emph{Base case}. Initially, $\mathcal{G}$ only contains all the original nodes.
 In this case, $\mathcal{G}$ is obviously a materialization graph.
@@
 \textbf{Lemma~\ref{lemma:dllite}}
-\emph{Given a DL-Lite ontology $\mathcal{O}$, for any materialization graph $\mathcal{G}$ of $\mathcal{O}$,
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in
-$\mathcal{G}$ has an SWD path.}
-\BG{now in the main part:\\ For any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
-each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in
-$\mathcal{G}$ has an SWD path.\\ The proof just speaks about DL-Lite
-in general as the original claim. Adapt?}\\
+\emph{For any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$, there exists a materialization graph $\mathcal{G}$ such that
+each atom of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$ in $\mathcal{G}$ has an SWD path.}\\
 
-\noindent\emph{Proof}: We prove the lemma by an induction on applications of
-the datalog rules corresponding to DL-Lite axioms.}\\
+\noindent\emph{Proof}: We first prove the lemma by an induction on applications of
+the datalog rules corresponding to DL-Lite$_\mathcal{R}$ axioms.\\
 
-\emph{Base case}. For each explicit node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
+\emph{Base case}. For each of the original node $v$ of the form $A(x)$ ($A\neq\bot$) or $R(x,y)$,
 $v$ has a special SWD path with $v$ as the unique node. This conclusion holds
@@
 \emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
-that is rewritten from some DL-Lite axiom, we have the induction hypothesis
+that is rewritten from some DL-Lite$_\mathcal{R}$ axiom, we have the induction hypothesis
 that $B_1,...,B_n$ have SWD paths.
@@
 For both Case~2.1 and Case~2.2, node $R(x,y)$ has an SWD path. Thus,
-node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.\hfill$\Box$
+node $R(x,y)$ has an SWD path in all materialization graphs of $\mathcal{O}$.
+We finish the proof for DL-Lite$_\mathcal{R}$. Since 
+DL-Lite$_{\text{core}}$ is a subset of DL-Lite$_\mathcal{R}$
+in terms of the expressivity, the above conclusion also applies
+to DL-Lite$_{\text{core}}$.\hfill$\Box$
 
@@
 \noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
-Specifically, for any DL-lite ontology $\mathcal{O}$,
+Specifically, for any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
 there always exists a poly-logarithmically bounded function $\psi$ such that
@@
 It is obvious that, if both of Stage~1 and Stage~2 can be handled
-by performing $\mathcal{A}_{\text{opt}}^\psi$ for some poly-logarithmical function $\psi$, then
-the whole materialization can be handled by $\mathcal{A}_{\text{opt}}^\psi$.
+by performing $\mathsf{A}_{\text{opt}}^\psi$ for some poly-logarithmical function $\psi$, then
+the whole materialization can be handled by $\mathsf{A}_{\text{opt}}^\psi$.
 In what follows, we investigate the above two stages respectively, and show that,
@@
 As mentioned before, there exists an NC algorithm for transitivity computation.
-Inspired by this, we can prove that \emph{$\mathcal{A}_{\text{opt}}^\psi$
+Inspired by this, we can prove that \emph{$\mathsf{A}_{\text{opt}}^\psi$
 handles Stage~1 for some poly-logarithmical function $\psi$}.
@@
 Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathcal{A}_{\text{opt}}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{\text{opt}}^\psi$.
+the computations of (1) and (3) can be handled by $\mathsf{A}_{\text{opt}}^\psi$.
+Further, transitive computation in part (2) can also be handled by $\mathsf{A}_{\text{opt}}^\psi$.
 Thus, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{\text{opt}}^\psi$ handles Stage~1.
+such that $\mathsf{A}_{\text{opt}}^\psi$ handles Stage~1.
 
 The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are explicit nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
+are the original nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
 generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
 instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathcal{A}_{\text{opt}}$ in at most two iterations.
+Thus, Stage~2 can be handled by $\mathsf{A}_{\text{opt}}$ in at most two iterations.
 Based on the above analysis, this theorem holds.
@@
 
-Our target is to show that $\mathcal{A}_{\text{opt}}^\psi$ handles Stage~1. To this end, we also
+Our target is to show that $\mathsf{A}_{\text{opt}}^\psi$ handles Stage~1. To this end, we also
 distinguish all roles by whether they are transitively influenced. Since we have to consider
@@
 least one role in the left hand side of (R4) are restricted to be a simple role.
-Thus, the computations of (1) and (3) can be handled by $\mathcal{A}_{\text{opt}}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathcal{A}_{\text{opt}}^\psi$.
+Thus, the computations of (1) and (3) can be handled by $\mathsf{A}_{\text{opt}}^\psi$.
+Further, transitive computation in part (2) can also be handled by $\mathsf{A}_{\text{opt}}^\psi$.
 In summary, there exists a poly-logarithmical function $\psi$
-such that $\mathcal{A}_{\text{opt}}^\psi$ handles Stage~1.
+such that $\mathsf{A}_{\text{opt}}^\psi$ handles Stage~1.
 
@@
 \textbf{Theorem~\ref{theorem:aprc}}
-\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{prc}$ halts and outputs
+\emph{For any DHL$(\circ)$ ontology $\mathcal{O}$, Algorithm~$\mathsf{A}_{\text{prc}}$ halts and outputs
 a materialization graph $\mathcal{O}$.}\\
@@
 this theorem is proved in two stages:
-(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{prc}$ is a materialization graph;
+(1) the graph $\mathcal{G}$ returned by $\mathsf{A}_{\text{prc}}$ is a materialization graph;
 (2) $\mathcal{G}$ is a complete materialization graph.
@@
 Suppose the ground atoms in $T_R^{i}(\textbf{I})$ have been added to $\mathcal{G}$ by
-performing $\mathsf{A}_{prc}$.
+performing $\mathsf{A}_{\text{prc}}$.
 For each atom $\alpha$ in $T_R^{i+1}(\textbf{I})$, there has to be a relation $(\beta,\alpha)$
@@
 $\alpha$ has to be added to $\mathcal{G}$ by applying \ref{alg4:updateG}
-of $\mathsf{A}_{prc}$.\hfill$\Box$
+of $\mathsf{A}_{\text{prc}}$.\hfill$\Box$
 
@@
 for each atom of the form $A(a)$ where $A$ is a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$.
+$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{\text{prc}}$.
 Recall Algorithm~$\mathsf{Prc}$. We use an induction to show that
@@
 In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
-$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple concept restriction.
+$A(a)$ has an SWD path in the first iteration of $\mathsf{A}_{\text{prc}}$ due to the simple concept restriction.
 We also use an induction to show that
@@
 It is easy to check that the simple-role materialization can be finished after the
-first iteration of $\mathsf{A}_{prc}$.
+first iteration of $\mathsf{A}_{\text{prc}}$.
 
@@
 and not a transitive role,
-$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{prc}$ due to the simple role restriction.
+$R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{\text{prc}}$ due to the simple role restriction.
 We use an induction to show that
@@
 of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{prc}$ in
+One can check the set $\delta_R$ can computed by $\mathsf{A}_{\text{prc}}$ in
 at most two iterations (see Case~4, Case~5 and Case~6).
@@
     the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
-    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{prc}$ can generate
+    $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{\text{prc}}$ can generate
     all nodes in each level of $t$ in one iteration from the bottom. Thus,

### 2018-02-22 parallel-tractability-J-v9/conclusions.tex

--- 2018-02-07 parallel-tractability-J-v9/conclusions.tex
@@
 To identify the parallel tractability classes,
-we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{bsc}^\psi$
-and Algorithm~$\mathsf{A}_{opt}^\psi$, that perform materialization on
+we proposed two \texttt{NC} algorithms, Algorithm~$\mathsf{A}_{\text{bsc}}^\psi$
+and Algorithm~$\mathsf{A}_{\text{opt}}^\psi$, that perform materialization on
 datalog rewritable ontology languages.
@@
 On the other hand, we used an optimization strategy based on SWD paths
-to give a practical algorithm variant Algorithm~$\mathsf{A}_{prc}$, which can
+to give a practical algorithm variant Algorithm~$\mathsf{A}_{\text{prc}}$, which can
 also be restricted to an \texttt{NC} version.
-We implemented a system based on Algorithm~$\mathsf{A}_{prc}$ and compared it to
+We implemented a system based on Algorithm~$\mathsf{A}_{\text{prc}}$ and compared it to
 the state-of-the-art reasoner RDFox.

### 2018-02-23 parallel-tractability-J-v9/conclusions.tex
fixed some points in abstract, intro, related work, conclusion

@@
 parallel tractability classes such that materialization
-on the datalog programs in these classes is in the NC complexity.
+on the datalog programs in these classes is in \texttt{NC} complexity.
 We further studied two specific ontology languages, DL-Lite and DHL (including one of its extension).
@@
 the state-of-the-art reasoner RDFox.
-The experimental results showed that our system is comparable to RDFox when handling
-the LUBM and the YAGO ontologies.
+The experimental results showed that the optimizations proposed in this paper resulted in a
+better performance on ontologies that were
+tractable in parallel compared with RDFox.
 
@@
 other expressive ontology languages, in addition to
-datalog rewritable ones. Since different expressive OWL languages
+datalog rewritable ontology languages. Since different expressive OWL languages
 have different syntaxes and higher reasoning complexities than \texttt{PTime}-complete, we need to

### 2018-02-23 parallel-tractability-J-v9/introduction.tex
fixed some points in abstract, intro, related work, conclusion

--- 2018-01-29 parallel-tractability-J-v9/introduction.tex
@@
 We further extend the results to an extension of DHL that also allows complex role inclusion axioms.
-Finally, we analyze well-known benchmarks and real-world datasets and show that many real ontologies following the
+Finally, we analyze the well-known benchmark, LUBM, and the real-world dataset, YAGO, and
+show that these ontologies following the
 proposed restrictions belong to the parallel tractability classes.
-We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization, which we compare to the state-of-the-art reasoner RDFox.
-The experimental results show that the optimizations proposed in this paper result in a better performance on ontologies that are 
+We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization,
+which we compare to the state-of-the-art reasoner RDFox.
+The experimental results show that the optimizations proposed in this paper result in a
+better performance on ontologies that are
 tractable in parallel compared with RDFox.

### 2018-02-23 parallel-tractability-J-v9/parallel-tractability-J.tex
Proof-read eval section
fixed some points in abstract, intro, related work, conclusion

@@
 \hyphenation{data-log}
+
+\newcommand{\BG}[1]{\textcolor{red}{BG: #1}}
+%\renewcommand{\BG}[1]{}
 
@@
   tractable in parallel. To verify the practical usability of the
-  above results, we analyze benchmark and real-world datasets, including the LUBM
-  and the YAGO ontologies, and show that for many
+  above results, we analyze different benchmarks and real-world datasets, including LUBM
+  and the YAGO ontology, and show that for many
   ontologies expressed in DHL materialization is tractable in
   parallel. The implementation of our optimized parallel algorithm
-  shows comparable performance with compared to the highly optimized
-  state-of-the-art reasoner RDFox.
+  shows performance improvements over the highly optimized
+  state-of-the-art reasoner RDFox on ontologies for which
+  materialization is tractable in parallel.
 \end{abstract}

### 2018-02-23 parallel-tractability-J-v9/relatedWork.tex
fixed some points in abstract, intro, related work, conclusion

@@
 The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
+RDFox is a highly optimized system that handles reasoning on datalog rewritable ontology languages.
 Algorithm~$\mathsf{A}_{\text{bsc}}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
@@
 rule instantiations to a processor.
-The experimental results show that ParallelDHL is comparable to RDFox when handling
-the LUBM and the YAGO ontologies.
+Specially, ParallelDHL is also optimized by using SWD paths for handling
+ontologies that belong to parallel tractability classes.
+The experimental results show that this optimization results in a
+better performance on ontologies that are
+tractable in parallel compared with RDFox.
 

### 2018-02-26 parallel-tractability-J-v9/response.tex
updated the response

--- 2018-01-30 parallel-tractability-J-v9/response.tex
@@
 
-We added xxx to adress this...
+We added the parallel complexity analysis for Algorithm~$\mathsf{A}_{\text{bsc}}$
+and Algorithm~$\mathsf{A}_{\text{opt}}$
+in Section~3.3 and Section~3.4 respectively.
+Based on the analysis and Theorem~1, we have that the parallel complexity
+of Algorithm~$\mathsf{A}_{\text{bsc}}$ depends only on the graph depths,
+while the parallel complexity of Algorithm~$\mathsf{A}_{\text{opt}}$
+depends on both of the graph depths and the sizes of input ontologies.\\
+
+We added the evaluation and the analysis of graph depths in Section~6.3.
+The experimental results showed that, when the graph depth is comparable to
+the size of the given ontology, it determines the reasoning time.
 
@@
 
-...
+We investigated many real ontologies from different data source. These ontologies cover
+several domains and only contain simple concepts (see Section~6.1). \\
+
+In this work, we focused on exploring the properties
+that make ontologies tractable in parallel. Thus, we did not study how to make ontologies
+tractable in parallel by having simple concepts or making concepts simple.
+We will study this problem in the future work.
 
@@
 We gave an example that RDFS entailment may lead to the situation of path twisting in Section~4.4 of the revision.
-We also discussed in what cases RDFS has parallel tractability of entailment.
+We also discussed in what cases RDFS ontologies are tractable in parallel.
 
@@
 
-...
+We extended Section~6.1 to further discuss in what cases
+the two ontologies, YAGO and LUBM, are tractable in parallel.
+We added the evaluation for these two kinds of ontologies in Section~6.2.
 
@@
 
-...ontologies must satisfy the properties for parallel tractability...
+The eight ontologies were selected since they satisfy the properties for parallel tractability.
+We used them to examine the effects of parallel tractability.\\
+
+In the revision, we did not continue to use the eight ontologies.
+We modified the LUBM ontology to generate ontologies of different graph depths.
+The experimental results were clearer for explaining the issues of graph depths
+and parallel tractability.\\
+
+We used at most 24 threads in the new experiments.
 
@@
 
-...
+In order to make the original experiments close to real scenes, we did not
+construct these eight ontologies for some purpose, e.g., to
+make the graph depth deeper. Thus, these ontologies acted like common ones.\\
+
+In the revision, we modified the LUBM ontology to generate ontologies of
+different graph depths. We gave the description of how these ontologies
+were constructed.
 
@@
 
-...
+In the original experiments, we checked that ParallelDHL costed a large amount of time for computing
+the relation $S_{\textit{\!\tiny rch}}$ when only one thread being allocated.
+When more than one threads are allocated, ParallelDHL has a better efficiency.
+This also resulted in the difference of the speedups between RDFox and ParallelDHL.
 
@@
 
-...
+We used the speedup numbers to show different performances between the
+ontologies in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
+that in $\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$.\\
+
+In the revision, we gave the formula of speedup and analyzed
+the speedup numbers.
 
@@
 
-...
+In order to make the original experiments close to real scenes, we did not
+construct the eight ontologies for some special purpose, e.g., to
+make the graph depth deeper
+Thus, these ontologies acted like common ones.
+The differences between the ontologies in
+$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and that in
+$\mathcal{D}^-_{\textit{\text{dhl}}(\circ)}$ were not clear
+for the test ontologies.\\
+
+In the revision, we did not continue to use the eight ontologies.
+We modified the LUBM ontology to generate ontologies of different graph depths.
+The experimental results were clearer for explaining the issues of graph depths
+and parallel tractability.
 
@@
 
-...
+We added the detailed analysis for LUBM and YAGO and the evaluation of
+graph depths in the revision.
 
@@
 The paper has so many grammatical errors near its beginning that I gave up
-marking them after the first two pages.  
+marking them after the first two pages.  I give a few that I noticed here.\\
+- [high-performance] computing platforms [] to\\
+- do exist ontologies[] for which materialization\\
+- (we use experiments to show [this] in Section 6).\\
+- There has been work [] propos[ing] parallel reasoning algorithms and employ[ing] parallel\\
+- e.g., dictionary encoding, balanc[ing] workload, [and] data partitioning,\\
+- It has also been shown that[] some well-known large-scale ontologies,\\
+The paper needs to be carefully copy-edited before any publication to remove
+these errors.
+
+"parallely tractable" is very grating.  It would be better to rewrite
+sentences to not use it.
 \end{quote}
-
-TODO: Remove the quote above once the issues are fixed.
 
@@
 \end{quote}
-
-TODO: once done, check whether indeed all occurrences are removed
 
@@
 
-We rewrote the paragraph under Lemma~1 to analyze the parallel complexity of Algorithm~$\mathsf{A}_{bsc}$.
+We rewrote the paragraph under Lemma~1 to analyze the parallel complexity of Algorithm~$\mathsf{A}_{\text{bsc}}$.
 We made it clear that $|P^*|$ is polynomial in the size of $I$ for a class of datalog programs.\\
@@
 The statement that Step~2 costs only one time unit is based on the context of one processor. Since one processor
-is allocated one rule instance (see the first paragraph of Algorithm~$\mathsf{A}_{bsc}$),
+is allocated one rule instance (see the first paragraph of Algorithm~$\mathsf{A}_{\text{bsc}}$),
 the procedure can be completed in constant time units. \\
@@
 
-We gave detailed information about the above assumption before Algorithm~$\mathsf{A}_{bsc}$.
+We gave the detailed description of the above assumption before Algorithm~$\mathsf{A}_{\text{bsc}}$.
 
@@
 
-We rewrote the paragraph under Lemma~2 to analyze the parallel complexity of Algorithm~$\mathsf{A}_{opt}$.
-In Step~2 of Algorithm~$\mathsf{A}_{opt}$, an NC algorithm is used to compute the transitive closure of $S_{\text{rch}}$.
+We rewrote the paragraph under Lemma~2 to give a more detailed
+analysis of the parallel complexity of Algorithm~$\mathsf{A}_{\text{opt}}$.
+In Step~2 of Algorithm~$\mathsf{A}_{\text{opt}}$, an \texttt{NC} algorithm is used to compute
+the transitive closure of $S_{\text{rch}}$.
 It can be checked that the scale of $S_{\text{rch}}$ is polynomial in the size of inputs.
@@
 
+- p5, saying ``y is a free variable'' in $A(x) \to \exists y.R(x,y)$ is confusing\\
+-  p6, the definition of (complete) materialisation graphs seems problematic.
+According to Definition~2, a graph containing all ground atoms in $T_R^\omega(I)$ but no edge is a materialisation graph and is complete.
+In particular,  it does not guarantee ``the nodes whose in-degree is $0$ are the original facts in I'' as claimed.\\
+- p6, the use of $\forall$ in Definition~2 is confusing and even worse in p18 Algorithm PRC.\\
 - p20, it mentions a group of materialisation rules in YAGO which belong to $D_{\text{dhl}}$.
@@
 - p20, Table 2, it should mention how these ontologies were selected. \\
+- p21, ``devided'' —> ``divided''\\
 - p21, the discussion on line graph lg1 is confusing (i.e.\ ``line-2 stays higher than line-6, but lower than line-4''). Maybe I was looking at the wrong place. \\
@@
 
-TODO: remove the quote once the issues are fixed.
+All minor issues have been fixed.\\
 
-All minor issues have been fixed.
+We extended Section~6.1 to further discuss in what cases
+the two ontologies, YAGO and LUBM, are tractable in parallel.
+We also added the evaluation for these two kinds of ontologies in Section~6.2.\\
+
+The eight ontologies were selected since they satisfy the properties for parallel tractability.
+We used them to examine the effects of parallel tractability.
+In the revision, we did not continue to use the eight ontologies.
+We modified the LUBM ontology to generate ontologies of different graph depths.
+We gave the description of how these ontologies
+were constructed.\\
+
+In the new experiments, the results were clearer for explaining the issues of graph depths
+and parallel tractability.
 

### 2018-02-26 parallel-tractability-J-v9/appendix.tex
finished checking the appendix, merges changes into rel. work and conclusions

@@
 
-\noindent\emph{Proof}: this theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
+\noindent\emph{Proof}: This theorem can be easily proved based on Lemma~\ref{lemma:dllite}.
 Specifically, for any DL-Lite$_{\text{core}}$ or DL-Lite$_\mathcal{R}$ ontology $\mathcal{O}$,
@@
 since in any materialization graph, each node has an SWD path.
-More precisely, we can set that $\psi=2$.\hfill$\Box$
+More precisely, we can see that $\psi=2$.\hfill$\Box$
 
@@
 
-\noindent\emph{Proof}: observe that, for a datalog program that is transformed from a DHL ontology,
-a rule with a binary atom as its head can only be either of the form (R1), (R2) or (R3).
-This also indicates that, the materialization of a DHL
+\noindent\emph{Proof}: Observe that, for a datalog program that is
+transformed from a DHL ontology $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$,
+a rule with a binary atom as its head can only be of the form either (R1), (R2) or (R3).
+This also indicates that the materialization of a DHL
 ontology can be separated into two stages: in the first stage (Stage~1), all the rules
@@
 the whole materialization can be handled by $\mathsf{A}_{\text{opt}}^\psi$.
-In what follows, we investigate the above two stages respectively, and show that,
+In what follows, we investigate the above two stages, respectively, and show that,
 for any datalog program in $\mathcal{D}_{\textit{\text{dhl}}}$,
@@
 are applied to add new nodes to the constructed materialization graph.
-We can observe that, rule (R3) is used for computation of transitive roles.
-As mentioned before, there exists an NC algorithm for transitivity computation.
+We can observe that rule (R3) is used for computing the transitive
+closure over roles.
+As mentioned before, there exists an \texttt{NC} algorithm for
+computing the transitive closure.
 Inspired by this, we can prove that \emph{$\mathsf{A}_{\text{opt}}^\psi$
@@
 The proof of this result can be shown by separately considering non-transitive roles and
-the roles that are transitive or influenced by transitive roles.
+roles that are transitive or influenced by transitive roles.
 Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
@@
 (2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it is not a TI role.
-We further define a set $\delta_R$ for each role $R\in\textbf{R}$ as follows:
+We say that a role is an NTI (non-transitively influenced) role if it
+is not a TI role.
+\BG{What you call (non-)transitively influenced is normally called
+  (non-)simple (note also that it is unclear where your $\mathcal{R}$
+  comes from, well, one has to guess from the RBox of the considered
+  ontology). I suggest to stick to the standard naming conventions and
+  use (also in the later parts). You have defined simple roles in
+  Sec.~2.3 already. }% \\
+% A role $R$ is \emph{non-simple} w.r.t.\ $\mathcal{O}$ if:
+% \begin{enumerate}
+% \item $\mathcal{R}$ contains an axiom $R \circ R \sqsubseteq R$,
+% \item there exists a non-simple role $R'$ such that $R' \sqsubseteq_*
+%   R$ or $R' \sqsubseteq_* R^-$.
+% \end{enumerate}
+% All other roles are \emph{simple}. 
+% }
+For each role $R\in\textbf{R}$, we further define a set $\delta_R$,
+where \textbf{R} is the set of roles (role names and their inverses)
+in the considered ontology, as follows:
 
 \begin{definition}\label{def:deltaRdhl}
-For each $R\in\textbf{R}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
-\end{enumerate}
+Let $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ be
+a DHL ontology with $\textbf{R}$ the set of roles. For each
+$R\in\textbf{R}$, we define $\delta_R$ as the following set of assertions:
+\begin{align*}
+\delta_R =\ & \{ R(a,b) \mid R(a,b) \in\mathcal{A} \}\ \cup\\
+& \{ R(a,b) \mid R'(a,b)\in\mathcal{A} \text{ and } R' \sqsubseteq_{*}
+  R \}\ \cup\\
+& \{ R(a,b) \mid R'(b,a)\in\mathcal{A} \text{ and } R'\sqsubseteq_{*}
+  R^- \}.
+\end{align*}
+% \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
+% \item for each $R(a,b)\in\mathcal{A}$;
+% \item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
+% \item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$.
+% \end{enumerate}
 \end{definition}
 
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.
+Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is
+a transitive role \BG{Really just transitive or non-simple (implicitly transitive)?}.
 We then have the following lemma.
@@
 \begin{lemma}\label{lemma:ti}
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
-(2) if $R$ is a transitive role, $R(a,b)\in\delta^*_{R}$;
-(3) if $R$ is a TI role, then $R(a,b)\in\delta_R$, or there exists a transitive
-role $R'$ such that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
+  \BG{It is unclear what $P$ is. I assume the datalog translation of
+    $\mathcal{O}$, which was also rather implicit, but I made that
+    already more explicit. I suggest to add:\\Let
+    $P=\langle R, \textbf{I}\rangle$ be the datalog program for an
+    ontology
+    $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$. We
+  then have that }
+  $P\models R(a,b)$ implies: (1) if $R$ is an NTI role,
+  $R(a,b)\in\delta_R$; (2) if $R$ is a transitive role,
+  $R(a,b)\in\delta^*_{R}$; (3) if $R$ is a TI role, then
+  $R(a,b)\in\delta_R$, or there exists a transitive role $R'$ such
+  that $R'\sqsubseteq_* R$ and $R'(a,b)\in\delta^*_{R'}$.
 \end{lemma}
@@
 (2) for each transitive role $R$, all implicit nodes of the form $R(a,b)$ are in the transitive closure $\delta^*_{R}$,
-which can be computed by an NC algorithm on $\delta_{R}$;
+which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
 (3) for each role $R$ that is a TI role but not a transitive role,
-one can further perform (R1) and (R2) iteratively based on all transitive closures $\delta^*_{R'}$
+one can further perform~(R1) and~(R2) iteratively based on all transitive closures $\delta^*_{R'}$
 where $R'$ is a transitive role.
-Since all nodes generated by only applying (R1) and (R2) have SWD paths,
-the computations of (1) and (3) can be handled by $\mathsf{A}_{\text{opt}}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathsf{A}_{\text{opt}}^\psi$.
+Since all nodes generated by only applying~(R1) and~(R2) have SWD paths,
+the computations of~(1) and~(3) can be handled by $\mathsf{A}_{\text{opt}}^\psi$.
+Further, the transitive computation in part~(2) can also be handled by $\mathsf{A}_{\text{opt}}^\psi$.
 Thus, there exists a poly-logarithmical function $\psi$
@@
 The results of Stage~1 serve as the facts of Stage~2. In other words, all binary atoms
-are the original nodes in Stage~2. This also means that the rules of the forms (T1) and (T3)
+are the original nodes in Stage~2. This also means that the rules of form~(T1) and~(T3)
 generate nodes with SWD paths. Due to the simple-concept restriction, for each rule
-instantiation $A_1(a),A_2(a)\rightarrow B(a)$, one of $A_1(a)$ and $A_2(a)$ always has an SWD path.
+instantiation $A_1(a),A_2(a)\rightarrow B(a)$, either $A_1(a)$ or $A_2(a)$ always has an SWD path.
 Thus, Stage~2 can be handled by $\mathsf{A}_{\text{opt}}$ in at most two iterations.
-Based on the above analysis, this theorem holds.
+Based on the above analysis, this theorem holds.\BG{I assume that ``this
+  theorem'' refers to Theorem~\ref{theorem:dhl}. I would prefer to
+  make that explicit. }
 
@@
 
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
+\emph{Base case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
+regardless of whether $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
 
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
+\emph{Inductive case}. We first analyze the case where $R$ is an NTI role.
 
@@
     be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhl}; (Case~1.1.2) If there exists some
+    $R'(a,b)\in\delta_{R'}$ (Case~1.1.1). If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
+    holds according to Definition~\ref{def:deltaRdhl} (Case~1.1.2). If there exists some
     role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have
-    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2).\label{dhl:NTIcaseR1}
+    $R(a,b)\in\delta_{R}$ since $R''\sqsubseteq_* R$ holds (Case~1.1.3). If there exists some
+    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, the case is
+    similar to Case~1.1.2.\label{dhl:NTIcaseR1}
 
@@
 
-We next study the case where $R$ is a transitive role.
+We next analyze the case where $R$ is a transitive role.
 
@@
     \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
+        Similar to Case~1.1.1, $R(a,b)\in\delta_{R}$ holds.
         Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
@@
     which also means $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhl:TcaseR2}
-    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
+    \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*,ref=Case~2.2.\arabic*]
     \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
@@
     \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to (Case~1.1.1), $R(a,b)\in\delta_{R}$ holds.
+        Similar to Case~1.1.1, $R(a,b)\in\delta_{R}$ holds.
         Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
@@
         $R''\sqsubseteq_* R'$ and $R''(a,b)\in\delta_{R''}^*$. Since $R''\sqsubseteq_* R$ and
-        $R''$ is the transitive role, third consequence in this Lemma is satisfied.
+        $R''$ is the transitive role, third consequence in this lemma is satisfied.
     \end{enumerate}
@@
 
-\noindent\emph{Proof}: the proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
+\noindent\emph{Proof}: The proof idea of this theorem is similar to that of Theorem~\ref{theorem:dhl}.
 That is, we separate the materialization of DHL$(\circ)$ ontologies into two stages: in Stage~1,
@@
 (2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of either of the form
+or (3) there exist a TI role $R'$ and an axiom of the form either
 $R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
 We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based on \emph{role sequence set}
+The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based
+on a \emph{role sequence set}
 that is defined as follows:
@@
 \begin{definition}\label{def:language}
-Let $\mathcal{L}(R)$ be the set of role sequences with respect to $R$ as follows:
- \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item $R'$, for each $R'\sqsubseteq_* R$;
-\item $R'^-$, for each $R'\sqsubseteq_* R^-$;
-\item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
-\item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
-\end{enumerate}
+Let $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ be
+a DHL$(\circ)$ ontology with $\textbf{R}$ the set of roles. For each
+$R\in\textbf{R}$, the \emph{set of role sequences} for $R$,
+$\mathcal{L}(R)$, is defined as follows:
+\BG{I assume you understand the items to contribute to elements of the
+set that is to be defined. This is not clear. I simply assume that this is what you had in: }
+\begin{align*}
+\mathcal{L}(R) =\ & \{ R' \mid R'\sqsubseteq_* R \}\ \cup\\
+& \{ R'^- \mid R' \sqsubseteq_* R^- \}\ \cup\\
+& \{ L_1L_2 \mid R_1\circ R_2\sqsubseteq R'\in\mathcal{R} \text{ is
+  not of form (R3)}, L_1\in\mathcal{L}(R_1), L_2\in\mathcal{L}(R_2) \text{ and }
+  R'\in\mathcal{L}(R) \}\ \cup\\
+& \{ L_2^-L_1^- \mid R_1\circ R_2\sqsubseteq R'\in\mathcal{R} \text{ is
+  not of form (R3)}, L_1\in\mathcal{L}(R_1), L_2\in\mathcal{L}(R_2) \text{ and }
+  R'^-\in\mathcal{L}(R) \}.
+\end{align*}
+%  \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
+% \item $R'$, for each $R'\sqsubseteq_* R$;
+% \item $R'^-$, for each $R'\sqsubseteq_* R^-$;
+% \item $L_1L_2$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'\in\mathcal{L}(R)$;
+% \item $L_2^-L_1^-$, for each axiom of the form (except R3) $R_1\circ R_2\sqsubseteq R'\in\mathcal{R}$, $L_i\in\mathcal{L}(R_i)(1\leq i\leq 2)$ and $R'^-\in\mathcal{L}(R)$.
+% \end{enumerate}
 \end{definition}
@@
 \begin{definition}\label{def:deltaRdhlplus}
-For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
-\begin{enumerate}[leftmargin=4ex,label=\arabic*.]
-\item for each $R(a,b)\in\mathcal{A}$;
-\item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
-\item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-\item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-\end{enumerate}
+Let $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$ be
+a DHL$(\circ)$ ontology with $\textbf{RN}$ the set of role names. For each
+$R\in\textbf{NR}$, we define $\delta_R$ as the following set of assertions:
+\begin{align*}
+\delta_R =\ & \{ R(a,b) \mid R(a,b) \in\mathcal{A} \}\ \cup\\
+& \{ R(a,b) \mid R'(a,b)\in\mathcal{A} \text{ and } R' \sqsubseteq_{*}
+  R \}\ \cup\\
+& \{ R(a,b) \mid R'(b,a)\in\mathcal{A} \text{ and } R'\sqsubseteq_{*}
+  R^- \}\\
+& \{ R(a,b) \mid R_0R_2,\ldots,R_n\in\mathcal{L}(R), 
+  R_i(x_i,x_{i+1})\in\mathcal{A}, 0\leq i\leq n, x_0=a, x_{n+1}=b \}.
+\end{align*}
+% For each $R\in\textbf{RN}$, let $\delta_R$ be the set of all assertions as follows:
+% \begin{enumerate}[leftmargin=4ex,label=\arabic*.]
+% \item for each $R(a,b)\in\mathcal{A}$;
+% \item $R(a,b)$, for each $R'(a,b)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R$;
+% \item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
+% \item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
+% \end{enumerate}
 \end{definition}
@@
 \begin{lemma}\label{lemma:tiplus}
+  \BG{It is unclear what $P$ is. I assume the datalog translation of some
+    $\mathcal{O}$. I suggest to add:\\Let
+    $P=\langle R, \textbf{I}\rangle$ be the datalog program for a DHL$(\circ)$
+    ontology
+    $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$. We
+  then have that }
 $P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
@@
 All nodes generated by applying (R1) and (R2) have SWD paths in the first iteration; at
-least one role in the left hand side of (R4) are restricted to be a simple role.
+least one role from the left-hand side of (R4) is restricted to be a simple role.
 Thus, the computations of (1) and (3) can be handled by $\mathsf{A}_{\text{opt}}^\psi$.
-Further, transitive computation in part (2) can also be handled by $\mathsf{A}_{\text{opt}}^\psi$.
+Further, the transitive computation in part (2) can also be handled by $\mathsf{A}_{\text{opt}}^\psi$.
 In summary, there exists a poly-logarithmical function $\psi$
@@
 
-\emph{Basic case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of the case that $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
+\emph{Base case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
+regardless of whether $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
 
@@
     be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(a,b)\in\delta_{R'}$ holds. (Case~1.1.1) If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.1.2) If there exists some
+    $R'(a,b)\in\delta_{R'}$ holds (Case~1.1.1). If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
+    holds according to Definition~\ref{def:deltaRdhlplus} (Case~1.1.2). If there exists some
     role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds; (Case~1.1.3) If there exists some
-    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.1.2); (Case~1.1.4) There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
+    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R$ holds (Case~1.1.3). If there exists some
+    role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, the case is
+    similar to Case~1.1.2 (Case~1.1.4). There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
     where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
     According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R\in\mathcal{R}$.\label{dhlplus:NTIcaseR1}
+    $R'\sqsubseteq R\in\mathcal{R}$ (Case~1.1.5).\label{dhlplus:NTIcaseR1}
 
@@
     be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
-    $R'(b,a)\in\delta_{R'}$. (Case~1.2.1) If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
-    holds according to Definition~\ref{def:deltaRdhlplus}; (Case~1.2.2) If there exists some
+    $R'(b,a)\in\delta_{R'}$ (Case~1.2.1). If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
+    holds according to Definition~\ref{def:deltaRdhlplus} (Case~1.2.2). If there exists some
     role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'$, we also have that
-    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds; (Case~1.2.3) If there exists some
+    $R(a,b)\in\delta_{R}$ because $R''\sqsubseteq_* R^-$ holds (Case~1.2.3). If there exists some
     role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to (Case~1.2.2); (Case~1.2.4) there exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
+    similar to Case~1.2.2 (Case~1.2.4). There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
     where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
     According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
-    $R'\sqsubseteq R^-\in\mathcal{R}$.\label{dhlplus:NTIcaseR2}
+    $R'\sqsubseteq R^-\in\mathcal{R}$ (Case~1.2.5).\label{dhlplus:NTIcaseR2}
 
@@
     Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1})(1\leq i\leq 2)$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
-    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be constructed in following different cases:
+    for each $R_i(c_i,c_{i+1}), 1\leq i\leq 2,$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
+    hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be
+    constructed according to the following cases:
 
@@
 
-    \item If there exists a role sequence $R_0R_2,...,R_m\in\mathcal{L}(R')$, where $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
+    \item If there exists a role sequence
+      $R_0R_2,...,R_m\in\mathcal{L}(R')$ s.t.\ $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
         and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
@@
 
-    Based on $L_i(1\leq i\leq 2)$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
+    Based on $L_i, 1\leq i\leq 2$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
     holds.\label{dhlplus:NTIcaseR4}
@@
 \item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not transitive role.
+    since $R$ is an NTI but not a transitive role.
 \end{enumerate}
@@
     \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
+        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and,
         obviously, $R\in\mathcal{L}(R)$ holds.
@@
     On the other hand, a role sequence $L_{R_2}$ exists in $\mathcal{L}(R_2)$ such that $c_2$ and $b$
-    are the starting and ending individual respectively.
+    are the starting and ending individual, respectively.
     Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
@@
 
-\noindent\emph{Proof}: similar to what we do when proving
-Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus},
-we separate the materialization of a DHL$(\circ)$ ontology
-into two stages: the role materialization (all the rules
-of the forms (R1-R4) are exhaustively applied) and the concept materialization
-(the rules of the forms (T1-T3)
-are then applied). The difference is that, we further separate the role materialization
-into successively two stages: \emph{the simple role materialization} (Stage~SRM) and
+\noindent\emph{Proof}: The proof is analogous to the proof of 
+Theorem~\ref{theorem:dhl} and Theorem~\ref{theorem:dhlplus}.
+We separate the materialization of a DHL$(\circ)$ ontology
+into two stages: role materialization (rules
+of the forms (R1-R4) are exhaustively applied) and concept materialization
+(rules of the forms (T1-T3)
+are exhaustively applied). The difference is that we further separate the role materialization
+into two successive stages: \emph{the simple role materialization} (Stage~SRM) and
 \emph{the non-simple role materialization} (Stage~NSRM).
-Similarly, the concept materialization is also separated into successively two stages:
+Similarly, the concept materialization is also separated into two
+successive stages:
 \emph{the simple concept materialization} (Stage~SCM) and
@@
 
-We aim to prove that, there always exists a poly-logarithmically bounded function $\psi$
+We aim to prove that there always exists a poly-logarithmically bounded function $\psi$
 such that $\mathsf{A}_{prc}^{\psi}$ can handle each of the four stages, Stage~SRM,
@@
 and $\exists R.A\sqsubseteq B$, which correspond to datalog rules of the forms $A(x)\rightarrow B(x)$
-and $R(x,y),A(y)\rightarrow B(x)$ respectively. Since role assertions are supposed to be fixed
-during in Stage~SCM, role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
+and $R(x,y),A(y)\rightarrow B(x)$, respectively. Since role assertions are supposed to be fixed
+during Stage~SCM, the role $R$ in each rule of the form $R(x,y),A(y)\rightarrow B(x)$
 can be viewed as an EDB predicate. This further means that,
@@
 \begin{enumerate}[leftmargin=12ex]
-\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models B\sqsubseteq_* A$. We have
+\item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models
+  B\sqsubseteq_* A$\BG{As per my comment in the main part: the star in
+  $\sqsubseteq_*$ seems unneeded/wrong as entailment handles this.}. We have
     that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\!\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
@@
 According to the simple-concept restriction, for each axiom of the form $A_1\sqcap A_2\sqsubseteq B$,
-one of $A_1$ and $A_2$ should be simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
+one of $A_1$ and $A_2$ should be a simple concept and can be viewed as an EDB predicate, since Stage~SCM is completed.
 In Stage~NSCM, for each atom of the form $A(a)$ where $A$ is not a simple concept,
@@
 such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-The case of the rule instantiation of the form $B(a)\rightarrow A(a)$ (resp., $R(a,b),B(b)\rightarrow A(a)$)
-is referred to Case~1 (resp., Case~2). We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
+We refer to the case of rule instantiations of the form
+$B(a)\rightarrow A(a)$ and $R(a,b),B(b)\rightarrow A(a)$ as Case~1 and
+Case~2, respectively. We only consider the case of the rule instantiation of the form $A_1(a),A_2(a)\rightarrow A(a)$
 here.
@@
     according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $A_2(a)$ can be determined.
+    By the induction hypothesis, the existence of an SWD path for $A_2(a)$ can be determined.
     Thus, the existence of the SWD path of $A(a)$ can also be determined.
-    It is similar for the case where $A_2(a)$ is derived and $A_2$ is a simple concept.
+    The case where $A_2(a)$ is derived and $A_2$ is a simple concept is similar.
 \end{enumerate}
 
-The simple-role materialization (Stage~SRM) can be simply conducted by checking the transitive closure
-of role inclusions, i.e., the axioms of the forms (R1-R2).
-It is easy to check that the simple-role materialization can be finished after the
+The simple-role materialization (Stage~SRM) can simply be conducted by checking the transitive closure
+of role inclusions, i.e., axioms of the forms (R1-R2).
+It is easy to check that the simple-role materialization is finished after the
 first iteration of $\mathsf{A}_{\text{prc}}$.
@@
     according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(a,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
+    By the induction hypothesis, the existence of an SWD path for $S(a,b)$ can be determined.
+    Thus, the existence of an SWD path of $R(a,b)$ can also be determined.
 
@@
     according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $S(b,a)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
+    By the induction hypothesis, the existence of an SWD path for $S(b,a)$ can be determined.
+    Thus, the existence of an SWD path of $R(a,b)$ can also be determined.
 
@@
     according to Algorithm~$\mathsf{Prc}$.
-    By the induction hypothesis, the existence of the SWD path for $R_2(c,b)$ can be determined.
-    Thus, the existence of the SWD path of $R(a,b)$ can also be determined.
-    It is similar for the case where $R_2(c,b)$ is derived and $R_2$ is a simple role.
+    By the induction hypothesis, the existence of an SWD path for $R_2(c,b)$ can be determined.
+    Thus, the existence of an SWD path of $R(a,b)$ can also be determined.
+    The case where $R_2(c,b)$ is derived and $R_2$ is a simple role is similar.
 \end{enumerate}
 
-We finally consider the derivation of the atoms of the form $R(a,b)$, where $R$
+We finally consider the derivation of atoms of the form $R(a,b)$, where $R$
 is a transitive role.
-Recall Lemma~\ref{lemma:tiplus}. We have that, $R(a,b)\in\delta_R$ or
+From Lemma~\ref{lemma:tiplus} we have that, $R(a,b)\in\delta_R$ or
 $R(a,b)\in\delta^*_R$ holds.
-According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role,
-or there exists such axioms
+According to the simple role restriction, for each sub-role $S$ of $R$, $S$ is a simple role
+or there exist axioms
 of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
 One can check the set $\delta_R$ can computed by $\mathsf{A}_{\text{prc}}$ in
-at most two iterations (see Case~4, Case~5 and Case~6).
-We should prove that the transitive closure $\delta^*_R$
+at most two iterations (see Cases~4,~5 and~6).
+We have to prove that the transitive closure $\delta^*_R$
 can also be computed by $\mathsf{A}_{prc}^\psi$ for some
@@
     One can construct a binary tree $t$ where the root node is $R(a,b)$,
-    the leaves are in $\delta_R$ and the hight of $t$ is up-bounded by
+    the leaves are in $\delta_R$ and the height of $t$ is upper-bounded by
     $\log(|\delta_R|)$. It can be checked that, $\mathsf{A}_{\text{prc}}$ can generate

### 2018-02-26 parallel-tractability-J-v9/conclusions.tex
finished checking the appendix, merges changes into rel. work and conclusions

@@
 In this paper, we studied the problem of parallel tractability of
-materialization on the datalog rewritable ontologies.
+materialization on datalog rewritable ontologies.
 To identify the parallel tractability classes,
@@
 the state-of-the-art reasoner RDFox.
-The experimental results showed that the optimizations proposed in this paper resulted in a
-better performance on ontologies that were
-tractable in parallel compared with RDFox.
+The experimental results showed that the optimizations proposed in this paper result in a
+better performance on ontologies that are
+tractable in parallel compared to RDFox.
 
-In the future work, we will extend our work in two lines.
-One line is a further study of the parallel tractability of
+In future work, we plan to extend our work in two lines.
+One line is a further study of parallel tractability of
 other expressive ontology languages, in addition to
@@
 explore more restrictions that are practical and make materialization
-tractable in parallel. Another line of the future work is to
+tractable in parallel. Another line of work is to
 study how to further apply the
 results in practice.
-One idea is to apply the technique of SWD paths to enhance other reasoning-based tasks,
-like ontology classification, ontology debugging and query answering.
+One idea is to apply the technique of SWD paths to enhance other
+reasoning-based tasks such as ontology classification, ontology
+debugging and query answering.
 

### 2018-02-26 parallel-tractability-J-v9/optimizedAlgo.tex
finished checking the appendix, merges changes into rel. work and conclusions

@@
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\!\tiny rch}}$ where $A(a)\rightarrow B(a)\in P^*$, $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in V$;
+\item add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\!\tiny rch}}$
+  where $A(a)\rightarrow B(a)\in P^*$, $\mathcal{O}\models
+  A\sqsubseteq_* B$ \BG{By referring to the entailment relation, the *
+  seems not needed: $\mathcal{O}\models
+  A\sqsubseteq B$. Similarly below. I noticed that, when checking
+  whether we introduced the * notation with a clear reference to the
+  ontology/RBox, but we no not. I added a sentence to say that we omit
+the RBox (as we never introduced the * w.r.t.\ the whole ontology) if
+it is clear from the context. } and $A(a)\in V$;
 

### 2018-02-26 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
Proof-read eval section
finished checking the appendix, merges changes into rel. work and conclusions

@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{fig-pathtwist.pdf}
+\includegraphics[width=\textwidth]{fig-pathtwist.pdf}
 \caption{The materialization graph of $\mathcal{O}_{\text{ex}_6}$
@@
 \item for all axioms of the form $R_1\circ R_2\sqsubseteq R$,
-    if there does exits a transitive role $S$ such that
+    if there exits a transitive role $S$ such that
     $R\sqsubseteq_* S$, then both $R_1$ and $R_2$ are \emph{simple
@@
 The correspondence between RDFS statements and DL axioms is listed in Table~\ref{tab:rdfs}.
-We call RDFS statements of the form (1--4) \emph{the schema data}
-(which correspond to TBox axioms), statements of the form~(5) and~(6)
+We call RDFS statements of the form (S1--S4) \emph{the schema data}
+(which correspond to TBox axioms), statements of the form~(S5) and~(S6)
 \emph{the instance data} (which correspond to ABox axioms).
@@
 \hline
-(1)&$P~~\texttt{rdfs:domain}~~C$& $\top\sqsubseteq\forall P^-.C$\\
+(S1)&$P~~\texttt{rdfs:domain}~~C$& $\top\sqsubseteq\forall P^-.C$\\
 
-(2)&$P~~\texttt{rdfs:range}~~C$& $\top\sqsubseteq\forall P.C$\\
+(S2)&$P~~\texttt{rdfs:range}~~C$& $\top\sqsubseteq\forall P.C$\\
 
-(3)&$B~~\texttt{rdfs:subClassOf}~~C$& $B\sqsubseteq C$\\
+(S3)&$B~~\texttt{rdfs:subClassOf}~~C$& $B\sqsubseteq C$\\
 
-(4)&$R~~\texttt{rdfs:subPropertyOf}~~S$& $R\sqsubseteq S$\\
+(S4)&$R~~\texttt{rdfs:subPropertyOf}~~S$& $R\sqsubseteq S$\\
 \hline
-(5)&$a~~\texttt{rdf:type}~~C$& $C(a)$\\
+(S5)&$a~~\texttt{rdf:type}~~C$& $C(a)$\\
 
-(6)&$a~~R~~b$& $R(a,b)$\\
+(S6)&$a~~R~~b$& $R(a,b)$\\
 \hline

### 2018-02-26 parallel-tractability-J-v9/relatedWork.tex
finished checking the appendix, merges changes into rel. work and conclusions

--- 2018-02-07 parallel-tractability-J-v9/relatedWork.tex
@@
 
-The parallel reasoner RDFox \cite{MotikNPHO14} is used to evaluate our implementation.
-RDFox is a state-of-the-art system that handles reasoning on datalog rewritable ontology languages.
-Algorithm~$\mathsf{A}_{bsc}$ proposed in Section~\ref{sec:ptclass}, is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
-The main difference is that a group of rule instantiations is handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{bsc}$, each rule instantiation is assigned to a unique processor.
-Thus, in theory, the materialization of the datalog program in Example~\ref{exp:mg} is serial in RDFox {\color{red}The example has two rules.
-Why can they not be parallelized in RDFox?}.
-ItThe experiments also show that parallelism does not lead to a remarkable improvement for RDFox for the ontology series not in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
-We use Algorithm~$\mathsf{A}_{opt}$ to show that the ontology in Example~\ref{exp:mg} is also tractable in parallel.
-Our implementation ParallelDHL, which is based on Algorithm~$\mathsf{A}_{prc}$, also shows a better performance than RDFox when handling the test ontologies that belong to $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.
+The parallel reasoner RDFox \cite{MotikNPHO14} is also used in the evaluation of our implementation.
+RDFox is a highly optimized system for reasoning over datalog rewritable ontology languages.
+Algorithm~$\mathsf{A}_{\text{bsc}}$ proposed in Section~\ref{sec:ptclass} is similar to the main algorithm of RDFox (see \cite{MotikNPHO14}, Sections~3 and 4).
+The main difference is that a group of rule instantiations is handled by one processor (namely a thread) in RDFox, while in Algorithm~$\mathsf{A}_{\text{bsc}}$, each rule instantiation is assigned to a unique processor.
+Analogous to the method used in RDFox, ParallelDHL is also implemented by assigning a group of
+rule instantiations to a processor.
+Specially, ParallelDHL is also optimized by using SWD paths for handling
+ontologies that belong to parallel tractability classes.
+The experimental results show that this optimization results in a
+better performance on ontologies that are
+tractable in parallel compared with RDFox.
 

### 2018-02-26 parallel-tractability-J-v9/response.tex
checked response

--- 2018-01-30 parallel-tractability-J-v9/response.tex
@@
 
+\usepackage[usenames, dvipsnames]{color}
+\newcommand{\BG}[1]{\textcolor{red}{BG: #1}}
+%\renewcommand{\BG}[1]{}
+
 \begin{document}
 
-We thank the reviewers for the time and effort invested in the detailed reviews and the valuable suggestions and comments to improve the quality of the paper.
-Below we reply to the individual points of the reviewers.
+We thank the reviewers for the time and effort invested in the
+detailed reviews and the valuable suggestions and comments to improve
+the quality of the paper. The paper has been carefully proof-read and,
+hopefully, all wording and structural issues are fixed now. We also
+fixed all mentioned minor issues. Below we reply to the other points
+raised by the reviewers for which we completely revised the evaluation
+section.
 
@@
 
-We added xxx to adress this...
+We added a parallel complexity analysis for Algorithm~$\mathsf{A}_{\text{bsc}}$
+and Algorithm~$\mathsf{A}_{\text{opt}}$
+in Section~3.3 and Section~3.4 respectively.
+Based on the analysis and Theorem~1, we have that the parallel complexity
+of Algorithm~$\mathsf{A}_{\text{bsc}}$ depends only on the graph depth,
+while the parallel complexity of Algorithm~$\mathsf{A}_{\text{opt}}$
+depends on both of the graph depth and the size of the input ontology.\\
+
+We added an evaluation and analysis of the role of the graph depth in Section~6.3.
+The experimental results show that, when the graph depth is comparable to
+the size of the given ontology, it determines the reasoning time.
 
@@
 
-We did the revision for Example~6 (see the paragraph following Example~6),
+We revised Example~6 (see the paragraph following Example~6) and also
 and Example~1 (see the last paragraph of Section~3.2).
@@
 
-...
+We investigated many real ontologies from different data source. These ontologies cover
+several domains and only contain simple concepts (see
+Section~6.1). \BG{Sec.~6.1 now only covers LUBM and YAGO. I don't think the
+current answer is convincing. Did this refer to the old Sec.~6.1 with
+the many more ontologies?}\\
+
+In this work, we focused on exploring the properties
+that make ontologies tractable in parallel. Thus, we did not study how to make ontologies
+tractable in parallel by having simple concepts or making concepts
+simple. This could be a direction for future work.
 
@@
 
-...
+We extended Section~6.1 to further discuss in which cases
+the two ontologies, YAGO and LUBM, are tractable in parallel.
+We added an evaluation for these ontologies in Section~6.2.
 
@@
 
-...ontologies must satisfy the properties for parallel tractability...
+The eight ontologies were selected since they satisfy the properties for parallel tractability.
+We used them to examine the effects of parallel tractability.\\
+
+In the revision, we did not continue to use the eight ontologies.
+We modified the LUBM ontology to generate ontologies of different graph depths.
+The experimental results were clearer for explaining the issues of graph depths
+and parallel tractability.\\
+
+We used up to 24 threads in the revised experiments.
 
@@
 
-...
+In the original experiments, we did not
+construct these eight ontologies for a certain purpose, e.g., to
+make the graph depth deeper. The main purpose was to closely reflect real-world scenarios. \\
+
+In the revision, we modified the LUBM benchmark to generate ontologies of
+different graph depths. We further provide a description of how these ontologies
+were constructed.
 
@@
 
-...
+In the original experiments, ParallelDHL required a large amount of time for computing
+the relation $S_{\textit{\!\tiny rch}}$ when only one thread is being allocated.
+With several threads allocated, ParallelDHL has a better efficiency.
+This also resulted in the difference of the speedups between RDFox and ParallelDHL.
 
@@
 
-...
+We used the speedup numbers to show different performances between the
+ontologies in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
+that not in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.\\
+
+In the revision, we provide the formula for the speedup and analyze
+the speedup numbers.
 
@@
 
-...
+\BG{The answer is not very much to the point and just a repetition of
+  a previous answer.}
+In order to make the original experiments close to real-world scenarios, we did not
+construct the eight ontologies for some special purpose, e.g., to
+make the graph depth deeper.
+The differences between the ontologies in
+$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and those not in
+$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ were not clear
+for the test ontologies.\\
+
+In the revision, we did not continue to use the eight ontologies.
+We modified the LUBM ontology to generate ontologies of different graph depths.
+The experimental results were clearer for explaining the issues of graph depths
+and parallel tractability.
 
@@
 
-...
-
-\begin{quote}
-Wording and structural problems:
-
-The paper has so many grammatical errors near its beginning that I gave up
-marking them after the first two pages.  
-\end{quote}
-
-TODO: Remove the quote above once the issues are fixed.
-
-The paper has been carefully proof-read and hopefully all wording and structural issues are fixed now.
+We added a detailed analysis for LUBM and YAGO and the evaluation of
+graph depths in the revision.
 
@@
 the problem of boolean matrix multiplication \cite{Raymond95}. Without this assumption, the program
-costs at least linear time to load the inputs. Thus, the requirements of the NC algorithms
+costs at least linear time to load the inputs. Thus, the requirements of the \texttt{NC} algorithms
 cannot be satisfied.\\
 
-We gave detailed information about the above assumption before Algorithm~$\mathsf{A}_{bsc}$.
+We provide a detailed description of the above assumption before Algorithm~$\mathsf{A}_{\text{bsc}}$.
 
@@
 The requirement ``H has been added to G'' in the description of computing the rch relation $S_{\text{rch}}$ ($\dag$) is indeed
-incorrect. It should be ``H has not been added to G''. We fixed this error.\\
+incorrect. It should be ``H has \textbf{not} been added to G''. We fixed this error.\\
 
-We rewrote the paragraph under Lemma~2 to analyze the parallel complexity of Algorithm~$\mathsf{A}_{opt}$.
-In Step~2 of Algorithm~$\mathsf{A}_{opt}$, an NC algorithm is used to compute the transitive closure of $S_{\text{rch}}$.
+We rewrote the paragraph following Lemma~2 to give a more detailed
+analysis of the parallel complexity of Algorithm~$\mathsf{A}_{\text{opt}}$.
+In Step~2 of Algorithm~$\mathsf{A}_{\text{opt}}$, an \texttt{NC} algorithm is used to compute
+the transitive closure of $S_{\text{rch}}$.
 It can be checked that the scale of $S_{\text{rch}}$ is polynomial in the size of inputs.
@@
 
-(TODO) We used a paragraph to discuss this after Algorithm~$\mathsf{A}_{prc}$.
+We added a discussion of how each processor handles rule instantiations at the beginning of Section~6.2.
 
-\begin{quote}
-I list some relatively minor issues regarding presentation and technical details:
+% We extended Section~6.1 to further discuss in what cases
+% the two ontologies, YAGO and LUBM, are tractable in parallel.
+% We also added the evaluation for these two kinds of ontologies in Section~6.2.\\
 
-- p20, it mentions a group of materialisation rules in YAGO which belong to $D_{\text{dhl}}$.
-It deserves a clarification on what these rules are like and why they do not fall into existing parallel tractable classes.\\
-- p20, Table 2, it should mention how these ontologies were selected. \\
-- p21, the discussion on line graph lg1 is confusing (i.e.\ ``line-2 stays higher than line-6, but lower than line-4''). Maybe I was looking at the wrong place. \\
-- p25, the section heading ``Reference'' occur twice.
-\end{quote}
+% The eight ontologies were selected since they satisfy the properties for parallel tractability.
+% We used them to examine the effects of parallel tractability.
+% In the revision, we did not continue to use the eight ontologies.
+% We modified the LUBM ontology to generate ontologies of different graph depths.
+% We gave the description of how these ontologies
+% were constructed.\\
 
-TODO: remove the quote once the issues are fixed.
-
-All minor issues have been fixed.
+% In the new experiments, the results were clearer for explaining the issues of graph depths
+% and parallel tractability.
 
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2018-02-27 parallel-tractability-J-v9/appendix.tex
revised Appendix E-I

@@
 handles Stage~1 for some poly-logarithmical function $\psi$}.
-The proof of this result can be shown by separately considering non-transitive roles and
-roles that are transitive or influenced by transitive roles.
-Specifically, we say that role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$.
-We say that a role is an NTI (non-transitively influenced) role if it
-is not a TI role.
-\BG{What you call (non-)transitively influenced is normally called
-  (non-)simple (note also that it is unclear where your $\mathcal{R}$
-  comes from, well, one has to guess from the RBox of the considered
-  ontology). I suggest to stick to the standard naming conventions and
-  use (also in the later parts). You have defined simple roles in
-  Sec.~2.3 already. }% \\
-% A role $R$ is \emph{non-simple} w.r.t.\ $\mathcal{O}$ if:
-% \begin{enumerate}
-% \item $\mathcal{R}$ contains an axiom $R \circ R \sqsubseteq R$,
-% \item there exists a non-simple role $R'$ such that $R' \sqsubseteq_*
-%   R$ or $R' \sqsubseteq_* R^-$.
-% \end{enumerate}
-% All other roles are \emph{simple}. 
-% }
+The proof of this results can be shown by distinguishing simple roles
+and non-simple roles.
+%
 For each role $R\in\textbf{R}$, we further define a set $\delta_R$,
@@
 
-Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is
-a transitive role \BG{Really just transitive or non-simple (implicitly transitive)?}.
+Let $\delta^*_R$ be the transitive closure of $\delta_R$ where $R$ is a transitive role.\footnote{Note that,
+in DHL, a transitive role is a non-simple role, while a non-simple role may not be a transitive role.}
 We then have the following lemma.
@@
 \begin{lemma}\label{lemma:ti}
-  \BG{It is unclear what $P$ is. I assume the datalog translation of
-    $\mathcal{O}$, which was also rather implicit, but I made that
-    already more explicit. I suggest to add:\\Let
+  Let
     $P=\langle R, \textbf{I}\rangle$ be the datalog program for an
@@
     $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$. We
-  then have that }
-  $P\models R(a,b)$ implies: (1) if $R$ is an NTI role,
+  then have that
+  $P\models R(a,b)$ implies: (1) if $R$ is a simple role,
   $R(a,b)\in\delta_R$; (2) if $R$ is a transitive role,
-  $R(a,b)\in\delta^*_{R}$; (3) if $R$ is a TI role, then
+  $R(a,b)\in\delta^*_{R}$; (3) if $R$ is a non-simple role but not a transitive role, then
   $R(a,b)\in\delta_R$, or there exists a transitive role $R'$ such
@@
 In this sense, Lemma~\ref{lemma:ti} also indicates that:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
+(1) for each implicit node $R(a,b)$ where $R$ is a simple role,
 it can be added to a materialization graph by only applying (R1) and (R2);
@@
 which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI role but not a transitive role,
+(3) for each role $R$ that is a non-simple role but not a transitive role,
 one can further perform~(R1) and~(R2) iteratively based on all transitive closures $\delta^*_{R'}$
@@
 instantiation $A_1(a),A_2(a)\rightarrow B(a)$, either $A_1(a)$ or $A_2(a)$ always has an SWD path.
-Thus, Stage~2 can be handled by $\mathsf{A}_{\text{opt}}$ in at most two iterations.
-Based on the above analysis, this theorem holds.\BG{I assume that ``this
-  theorem'' refers to Theorem~\ref{theorem:dhl}. I would prefer to
-  make that explicit. }
+Thus, Stage~2 can be handled by $\mathsf{A}_{\text{opt}}$ in at most two iterations (see Theorem~\ref{theorem:dhl}).
+Based on the above analysis, this theorem holds.
 
@@
 
-\emph{Base case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of whether $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
+\emph{Base case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$ holds. In this case,
+regardless of whether $R$ is a non-simple or a simple role, all of (1), (2) and (3) in Lemma~\ref{lemma:ti} hold.
 
-\emph{Inductive case}. We first analyze the case where $R$ is an NTI role.
+\emph{Inductive case}. We first analyze the case where $R$ is a simple role.
 
@@
 \item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
+    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is a simple role, $R'$ has to
+    be a simple role according to Definition~\ref{def:deltaRdhl}. According to the induction hypothesis,
     $R'(a,b)\in\delta_{R'}$ (Case~1.1.1). If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
@@
 \item $R(a,b)$ is derived by applying the rule (R3). This case is impossible, since $R$ is
-    an NTI role.
+    a simple role.
 \end{enumerate}
@@
     \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to Case~1.1.1, $R(a,b)\in\delta_{R}$ holds.
+    \item $R'$ is a simple role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
+        Similarly to Case~1.1.1, $R(a,b)\in\delta_{R}$ holds.
         Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
 
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
+    \item $R'$ is a non-simple role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$ holds,
         then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
@@
         Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
+        we have that $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
         also holds.
@@
     \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*,ref=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
+    \item $R'$ is a simple role. By induction hypothesis, $R'(b,a)\in\delta_{R'}$.
+        Similarly to \ref{dhl:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds.
         Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
 
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
+    \item $R'$ is a non-simple role. By the induction hypothesis, if $R'(b,a)\in\delta_{R'}$,
         then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
@@
         Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
+        we have that $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
         also holds.
@@
 
-We finally study the case where $R$ is a TI but not a transitive role.
+We finally study the case where $R$ is a non-simple but not a transitive role.
 
@@
     \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to Case~1.1.1, $R(a,b)\in\delta_{R}$ holds.
+    \item $R'$ is a simple role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
+        Similarly to Case~1.1.1, $R(a,b)\in\delta_{R}$ holds.
         Obviously, $R(a,b)\in\delta_{R}^*$ also holds.
 
-    \item $R'$ is a TI role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
+    \item $R'$ is a non-simple role. By the induction hypothesis, if $R'(a,b)\in\delta_{R'}$,
         then $R(a,b)\in\delta_R$ also holds. On the other hand, if there exists a transitive role
@@
 all the rules of the forms (R1-R4) are exhaustively applied; in Stage~2, the rules of the forms (T1-T2)
-are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of DHL.
-Thus we only consider Stage~1 here.
+are then applied while the results of Stage~1 serve as facts. Stage~2 is as same as that of materializing
+DHL. Thus we only consider Stage~1 here.
 
 Our target is to show that $\mathsf{A}_{\text{opt}}^\psi$ handles Stage~1. To this end, we also
-distinguish all roles by whether they are transitively influenced. Since we have to consider
-complex RIAs, we re-define TI and NTI roles as follows:
-a role $R$ is \emph{transitively influenced} (TI)
-if (1) $R\circ R\sqsubseteq R\in\mathcal{R}$; or
-(2) there exists a TI role $R'$ such that $R'\sqsubseteq_*R$ or $R'\sqsubseteq_*R^-$;
-or (3) there exist a TI role $R'$ and an axiom of the form either
-$R'\circ R''\sqsubseteq R$ or $R''\circ R'\sqsubseteq R$.
-We say that a role is an NTI role if it is not transitively influenced.
-The set $\delta_R$ for each role $R\in\textbf{R}$ is re-defined based
-on a \emph{role sequence set}
-that is defined as follows:
+distinguish all roles by whether they are simple or not. For DHL$(\circ)$, we have to consider
+complex RIAs as well. Thus,
+the set $\delta_R$ for each role $R\in\textbf{R}$ should be re-defined.
+We give the following definition of \emph{role sequence sets} which is
+used to further define the set $\delta_R$.
 
@@
 $\mathcal{L}(R)$, is defined as follows:
-\BG{I assume you understand the items to contribute to elements of the
-set that is to be defined. This is not clear. I simply assume that this is what you had in: }
 \begin{align*}
@@
   R^- \}\\
-& \{ R(a,b) \mid R_0R_2,\ldots,R_n\in\mathcal{L}(R), 
-  R_i(x_i,x_{i+1})\in\mathcal{A}, 0\leq i\leq n, x_0=a, x_{n+1}=b \}.
+& \{ R(a,b) \mid R_0R_1,\ldots,R_n\in\mathcal{L}(R),
+  R_i(x_i,x_{i+1})\in\mathcal{A}, i\in\{0,1,...,n\}, x_0=a, x_{n+1}=b \}.
 \end{align*}
@@
 % \item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-% \item $R(a,b)$, for each $R_0R_2,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
+% \item $R(a,b)$, for each $R_0R_1,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $i\in\{0,1,...,n\}$.
 % \end{enumerate}
@@
 \begin{lemma}\label{lemma:tiplus}
-  \BG{It is unclear what $P$ is. I assume the datalog translation of some
-    $\mathcal{O}$. I suggest to add:\\Let
+Let
     $P=\langle R, \textbf{I}\rangle$ be the datalog program for a DHL$(\circ)$
@@
     $\mathcal{O}=\langle\mathcal{T},\mathcal{R},\mathcal{A}\rangle$. We
-  then have that }
-$P\models R(a,b)$ implies: (1) if $R$ is an NTI role, $R(a,b)\in\delta_R$;
+  then have that
+$P\models R(a,b)$ implies: (1) if $R$ is a simple role, $R(a,b)\in\delta_R$;
 (2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a TI but not transitive role, then there exists a role sequence $R_1R_2,...,R_n\in\mathcal{L}(R)$ such that
+(3) if $R$ is a non-simple but not transitive role, then there exists a role sequence $R_0R_1,...,R_n\in\mathcal{L}(R)$ such that
 $R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $1\leq i\leq n$ and $x_0=a, x_{n+1}=b$.
+where $i\in\{0,1,...,n\}$ and $x_0=a, x_{n+1}=b$.
 \end{lemma}
@@
 The above lemma says:
-(1) for each implicit node $R(a,b)$ where $R$ is an NTI role,
+(1) for each implicit node $R(a,b)$ where $R$ is a simple role,
 it can be added to a materialization graph by only applying (R1), (R2) and (R4);
@@
 which can be computed by an \texttt{NC} algorithm on $\delta_{R}$;
-(3) for each role $R$ that is a TI but not a transitive role,
+(3) for each role $R$ that is a non-simple but not a transitive role,
 one can further perform (R1), (R2) and (R4) iteratively based on all
@@
 
-\emph{Base case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$. In this case,
-regardless of whether $R$ is a TI or an NTI role, all of (1), (2) and (3) hold.
+\emph{Base case}. If $R(a,b)\in\textbf{I}$, $R(a,b)\in\delta_{R}$ holds. In this case,
+regardless of whether $R$ is a non-simple or a simple role, all of
+the consequences (1), (2) and (3) in Lemma~\ref{lemma:tiplus} hold.
 
-\emph{Inductive case}. We first study the case where $R$ is an NTI role.
+\emph{Inductive case}. We first study the case where $R$ is a simple role.
 
@@
 \item $R(a,b)$ is derived by applying the rule (R1), w.l.o.g., $R'(a,b)\rightarrow R(a,b)$,
-    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
+    which also means that $R'\sqsubseteq R\in\mathcal{R}$. Since $R$ is a simple role, $R'$ has to
+    be a simple role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
     $R'(a,b)\in\delta_{R'}$ holds (Case~1.1.1). If $R'(a,b)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
@@
     role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, the case is
-    similar to Case~1.1.2 (Case~1.1.4). There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_0R_2,...,R_n\in\mathcal{L}(R)$ holds since
+    similar to Case~1.1.2 (Case~1.1.4). There exists $R_0R_1,...,R_n\in\mathcal{L}(R')$,
+    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $i\in\{0,1,...,n\}$.
+    According to Definition~\ref{def:language}, $R_0R_1,...,R_n\in\mathcal{L}(R)$ holds since
     $R'\sqsubseteq R\in\mathcal{R}$ (Case~1.1.5).\label{dhlplus:NTIcaseR1}
@@
 \item $R(a,b)$ is derived by applying the rule (R2), w.l.o.g., $R'(a,b)\rightarrow R(b,a)$,
-    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is an NTI role, $R'$ has to
-    be an NTI role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
+    which also means that $R'\sqsubseteq R^-\in\mathcal{R}$. Since $R$ is a simple role, $R'$ has to
+    be a simple role according to Definition~\ref{def:deltaRdhlplus}. By the induction hypothesis,
     $R'(b,a)\in\delta_{R'}$ (Case~1.2.1). If $R'(b,a)\in\mathcal{A}$, $R(a,b)\in\delta_{R}$
@@
     role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to Case~1.2.2 (Case~1.2.4). There exists $R_0R_2,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $0\leq i\leq n$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ holds since
+    similar to Case~1.2.2 (Case~1.2.4). There exists $R_0R_1,...,R_n\in\mathcal{L}(R')$,
+    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $i\in\{0,1,...,n\}$.
+    According to Definition~\ref{def:language}, $R_n^-,...,R_0^-\in\mathcal{L}(R)$ holds since
     $R'\sqsubseteq R^-\in\mathcal{R}$ (Case~1.2.5).\label{dhlplus:NTIcaseR2}
@@
     which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is an NTI role, both of $R_1$ and $R_2$ are NTI roles. By the induction hypothesis,
-    for each $R_i(c_i,c_{i+1}), 1\leq i\leq 2,$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
+    Since $R$ is a simple role, both of $R_1$ and $R_2$ are simple roles. By the induction hypothesis,
+    for each $R_i(c_i,c_{i+1}), i\in\{1,2\},$ where $c_1=a, c_3=b$, $R_i(c_i,c_{i+1})\in\delta_{R_i}$
     hold. We have a role sequence $L_i\in\mathcal{L}(R_i)$ that may be
@@
     \item If there exists a role sequence
-      $R_0R_2,...,R_m\in\mathcal{L}(R')$ s.t.\ $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $0\leq i\leq m$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_2,...,R_m$ holds.
+      $R_0R_1,...,R_m\in\mathcal{L}(R')$ s.t.\ $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $i\in\{0,1,...,m\}$
+        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_1,...,R_m$ holds.
     \end{enumerate}
 
-    Based on $L_i, 1\leq i\leq 2$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
+    Based on $L_i, i\in\{1,2\}$, we have that $L_1L_2\in\mathcal{L}(R)$. Further $R(a,b)\in\delta_R$
     holds.\label{dhlplus:NTIcaseR4}
@@
 \item $R(a,b)$ is derived by applying the rule (R3). This case is impossible,
-    since $R$ is an NTI but not a transitive role.
+    since $R$ is a simple but not a transitive role.
 \end{enumerate}
@@
     \begin{enumerate}[leftmargin=8ex,label=Case~2.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and,
+    \item $R'$ is a simple role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$.
+        Similarly to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and,
         obviously, $R\in\mathcal{L}(R)$ holds.
 
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
+    \item $R'$ is a non-simple but not a transitive role.
+        By the induction hypothesis, there exists $R_0R_1,...,R_n\in\mathcal{L}(R')$
+        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,...,n\}$
+        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_0R_1,...,R_n\in\mathcal{L}(R)$ also holds.
 
@@
     \begin{enumerate}[leftmargin=8ex,label=Case~2.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
+    \item $R'$ is a simple role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
+        Similarly to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
         obviously, $R\in\mathcal{L}(R)$ holds.
 
-    \item $R'$ is a TI but not transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
+    \item $R'$ is a non-simple but not transitive role. By the induction hypothesis, there exists $R_0R_1,...,R_n\in\mathcal{L}(R')$
+        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,...,n\}$
+        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_0^-\in\mathcal{L}(R)$ also holds.
 
@@
     This also
-    means that $R_1, R_2$ are NTI roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
+    means that $R_1, R_2$ are simple roles. Further, $R_1(a,c_2)\in\delta_{R_1}$ and $R_2(c_2,b)\in\delta_{R_2}$.
     This case is similar to \ref{dhlplus:NTIcaseR4}.
@@
     which also means that $R\circ R\sqsubseteq R\in\mathcal{R}$.
-    Since $R$ is a TI role, by the induction hypothesis,
+    Since $R$ is a non-simple role, by the induction hypothesis,
     $R(a,c),R(c,b)\in\delta^*_{R}$ holds. Obviously, $R(a,b)\in\delta^*_{R}$ holds.
@@
     \begin{enumerate}[leftmargin=8ex,label=Case~3.1.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
-        Similar to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
+    \item $R'$ is a simple role. By the induction hypothesis, $R'(a,b)\in\delta_{R'}$ holds.
+        Similarly to \ref{dhlplus:NTIcaseR1}, $R(a,b)\in\delta_{R}$ holds and
         obviously, $R\in\mathcal{L}(R)$ holds.
 
-    \item $R'$ is a TI but not a transitive role.
-        By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_1,...,R_n\in\mathcal{L}(R)$ also holds.
+    \item $R'$ is a non-simple but not a transitive role.
+        By the induction hypothesis, there exists $R_0R_1,...,R_n\in\mathcal{L}(R')$
+        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,...,n\}$
+        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_0R_1,...,R_n\in\mathcal{L}(R)$ also holds.
 
@@
     \begin{enumerate}[leftmargin=8ex,label=Case~3.2.\arabic*]
-    \item $R'$ is an NTI role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
-        Similar to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
+    \item $R'$ is a simple role. By the induction hypothesis, $R'(b,a)\in\delta_{R'}$.
+        Similarly to \ref{dhlplus:NTIcaseR2}, $R(a,b)\in\delta_{R}$ holds and
         obviously, $R\in\mathcal{L}(R)$ holds.
 
-    \item $R'$ is a TI but not a transitive role. By the induction hypothesis, there exists $R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $1\leq i\leq n$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_1^-\in\mathcal{L}(R)$ also holds.
+    \item $R'$ is a non-simple but not a transitive role. By the induction hypothesis, there exists $R_0R_1,...,R_n\in\mathcal{L}(R')$
+        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,...,n\}$
+        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_0^-\in\mathcal{L}(R)$ also holds.
 
@@
     which also means that $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$ holds.
-    Further, $R$ is a TI but not transitive role. According to the simple-role restriction,
+    Further, $R$ is a non-simple but not transitive role. According to the simple-role restriction,
     at least one of $R_1$ and $R_2$ is a simple role.
     W.l.o.g., let $R_2$ be a simple role, which also
-    means that $R_2$ is an NTI role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
+    means that $R_2$ is a simple role. Further, $R_2(c_2,b)\in\delta_{R_2}$ holds.
     For $R_1$, by the induction hypothesis, $R_1(a,c_2)\in\delta^*_{R_1}$ holds.
@@
     are the starting and ending individual, respectively.
-    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ which satisfies the second condition
+    Further, we have that $R_1L_{R_2}\in\mathcal{L}(R)$ holds. This satisfies the second condition
     in Lemma~\ref{lemma:tiplus}.\label{dhlplus:TIcaseR4}
@@
 
-\noindent\emph{Proof}: similar to the proof of Lemma~\ref{lemma:a3},
+\noindent\emph{Proof}: Similarly to the proof of Lemma~\ref{lemma:a3},
 this theorem is proved in two stages:
@@
 \item[Case~1] $B(a)\rightarrow A(a)$, where $\mathcal{O}\models
-  B\sqsubseteq_* A$\BG{As per my comment in the main part: the star in
-  $\sqsubseteq_*$ seems unneeded/wrong as entailment handles this.}. We have
+  B\sqsubseteq A$. We have
     that \texttt{rch}$(B(a),A(a))$ is in $S_{\textit{\!\tiny rch}}$ according to Algorithm~$\mathsf{Prc}$.
@@
 such an SWD path of $A(a)$ can be determined by distinguishing different rule instantiations.
-We refer to the case of rule instantiations of the form
+One can refer to the cases of rule instantiations of the form
 $B(a)\rightarrow A(a)$ and $R(a,b),B(b)\rightarrow A(a)$ as Case~1 and
@@
 
-We now discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is not a simple role
-and not a transitive role,
+We finally discuss Stage~NSRM. For each atom of the form $R(a,b)$ where $R$ is a non-simple role
+but not a transitive role,
 $R(a,b)$ has an SWD path in the first iteration of $\mathsf{A}_{\text{prc}}$ due to the simple role restriction.
@@
 \begin{enumerate}[leftmargin=12ex]
-\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R$.
+\item[Case~4] $S(a,b)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq R$.
     We have that \texttt{rch}$(S(a,b),R(a,b))$ is in $S_{\textit{\!\tiny rch}}$
@@
 
-\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq_* R^-$.
+\item[Case~5] $S(b,a)\rightarrow R(a,b)$ where $\mathcal{O}\models S\sqsubseteq R^-$.
     We have that \texttt{rch}$(S(b,a),R(a,b))$ is in $S_{\textit{\!\tiny rch}}$
@@
 
-\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\mathcal{R}$.
+\item[Case~6] $R_1(a,c),R_2(c,b)\rightarrow R(a,b)$ where $R_1\circ R_2\sqsubseteq R\in\mathcal{R}$.
     If $R_1(a,c)$ is derived where $R_1$ is a simple role,
@@
     Thus, the existence of an SWD path of $R(a,b)$ can also be determined.
-    The case where $R_2(c,b)$ is derived and $R_2$ is a simple role is similar.
+    The case where $R_2(c,b)$ is derived and $R_2$ is a simple role can be similarly proved.
 \end{enumerate}
@@
 of the form $S_1\circ S_2\sqsubseteq S$ where $S_1$ and $S_2$ are simple roles.
-One can check the set $\delta_R$ can computed by $\mathsf{A}_{\text{prc}}$ in
+One can check that the set $\delta_R$ can be computed by $\mathsf{A}_{\text{prc}}$ in
 at most two iterations (see Cases~4,~5 and~6).

### 2018-02-27 parallel-tractability-J-v9/response.tex
revised the response

@@
 
-We investigated many real ontologies from different data source. These ontologies cover
-several domains and only contain simple concepts (see
-Section~6.1). \BG{Sec.~6.1 now only covers LUBM and YAGO. I don't think the
-current answer is convincing. Did this refer to the old Sec.~6.1 with
-the many more ontologies?}\\
+We investigated real ontologies from different data source. These ontologies cover
+several domains and only contain simple concepts (these ontologies can be
+obtained from the address given in the last paragraph of
+Section~6.1).\\
 
@@
 
-\BG{The answer is not very much to the point and just a repetition of
-  a previous answer.}
-In order to make the original experiments close to real-world scenarios, we did not
-construct the eight ontologies for some special purpose, e.g., to
-make the graph depth deeper.
-The differences between the ontologies in
+ParallelDHL is mainly
+optimized based on the graph depth. Thus, when the graph depth is the
+dominate factor that determines the reasoning time, the experiment 
+should have a better performance. 
+In the original experiments, the eight ontologies were used to make
+the experiments close to real-world scenarios.
+Since the graph depths of different ontologies affect the reasoning times
+to different degrees, the experimental results are not very clear
+to explain the issue of parallel tractability.
+This is also why
+Figure 5 does not show the differences between the ontologies in
 $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and those not in
-$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ were not clear
-for the test ontologies.\\
+$\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ well.\\
 
-In the revision, we did not continue to use the eight ontologies.
-We modified the LUBM ontology to generate ontologies of different graph depths.
-The experimental results were clearer for explaining the issues of graph depths
-and parallel tractability.
+In order to make the graph depth as a dominate factor, we modified the LUBM benchmark to 
+generate ontologies of different graph depths and conducted the new experiments
+in the revision.
 

### 2018-02-27 parallel-tractability-J-v9/response.tex
final polishing

@@
 
-We investigated real ontologies from different data source. These ontologies cover
+We investigated real ontologies from different data sources. These ontologies cover
 several domains and only contain simple concepts (these ontologies can be
@@
 
-We used the speedup numbers to show different performances between the
-ontologies in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and
-that not in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.\\
+We used the speedup numbers to show the different performance for
+ontologies in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$ and those
+ not in $\mathcal{D}_{\textit{\text{dhl}}(\circ)}$.\\
 
@@
 optimized based on the graph depth. Thus, when the graph depth is the
-dominate factor that determines the reasoning time, the experiment 
+dominant factor that determines the reasoning time, the experiment 
 should have a better performance. 
@@
 
-In order to make the graph depth as a dominate factor, we modified the LUBM benchmark to 
+In order to make the graph depth a dominant factor, we modified the LUBM benchmark to 
 generate ontologies of different graph depths and conducted the new experiments

### 2018-02-27 parallel-tractability-J-v9/appendix.tex
final polishing

@@
 for each of the original node $v$, \texttt{depth}($v$)=0;
-for each implicit node $v'$ whose parents are $v_1,...,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), ..., \texttt{depth}($v_i$) $\}+1$.
+for each implicit node $v'$ whose parents are $v_1,\ldots ,v_i$, \texttt{depth}($v'$)=$\max$$\{$ \texttt{depth}($v_1$), \ldots , \texttt{depth}($v_i$) $\}+1$.
 By performing an induction on the number of iterations of \ref{alg1:updateG},
@@
 (1) If $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are created.
+then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),\ldots ,e(B_n, H)$ are created.
 (2) If neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
+then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),\ldots ,e(B_n, H)$ are also created.
 In the above two cases, $H$ is a new node. Thus,
@@
 (3) If $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),...,e(B_n, H)$ are also created.
+$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),\ldots ,e(B_n, H)$ are also created.
 For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,
@@
 
-\emph{Inductive cases}. For each datalog rule of the form `$B_1,...,B_n\rightarrow H$'
+\emph{Inductive cases}. For each datalog rule of the form `$B_1,\ldots ,B_n\rightarrow H$'
 that is rewritten from some DL-Lite$_\mathcal{R}$ axiom, we have the induction hypothesis
-that $B_1,...,B_n$ have SWD paths.
+that $B_1,\ldots ,B_n$ have SWD paths.
 We are left to prove that $H$ has an SWD path as well
@@
 \item $B\sqsubseteq A$. According to the induction hypothesis,
-node $B(x)$ has an SWD path, denoted by $(v_1,...,v_n,B(x))$.
+node $B(x)$ has an SWD path, denoted by $(v_1,\ldots ,v_n,B(x))$.
 We have that, in some materialization graph, node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),A(x))$.
+has an SWD path of the form $(v_1,\ldots ,v_n,B(x),A(x))$.
 
 \item $\exists R\sqsubseteq A$. Node $R(x,y)$ has an SWD path,
-denoted by $(v_1,...,v_n,R(x,y))$,
+denoted by $(v_1,\ldots ,v_n,R(x,y))$,
 according to the induction hypothesis.
 It is obvious that node $A(x)$
-has an SWD path of the form $(v_1,...,v_n,B(x),R(x,y))$
+has an SWD path of the form $(v_1,\ldots ,v_n,B(x),R(x,y))$
 in some materialization graph.
@@
 \item $S\sqsubseteq R$. According to the induction hypothesis,
-node $S(x,y)$ has an SWD path, denoted by $(v_1,...,v_n,S(x,y))$.
+node $S(x,y)$ has an SWD path, denoted by $(v_1,\ldots ,v_n,S(x,y))$.
 Obviously, node $R(x,y)$
-has an SWD path of the form $(v_1,...,v_n,S(x,y),R(x,y))$
+has an SWD path of the form $(v_1,\ldots ,v_n,S(x,y),R(x,y))$
 in some materialization graph.
@@
         the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(a,c_1),R''(c_1,c_2),...,R''(c_n,b)$) in $\delta_{R''}$.
+        exist such atoms ($R''(a,c_1),R''(c_1,c_2),\ldots ,R''(c_n,b)$) in $\delta_{R''}$.
         Further, due to $R''\sqsubseteq_* R$ and Definition~\ref{def:deltaRdhl},
-        we have that $R(a,c_1),R(c_1,c_2),...,$ $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
+        we have that $R(a,c_1)$, $R(c_1,c_2)$, \ldots, $R(c_n,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
         also holds.
@@
         the transitive closure of $\delta_{R''}$, we then have that there must
-        exist such atoms ($R''(b,c_1),R''(c_1,c_2),...,R''(c_n,a)$) in $\delta_{R''}$.
+        exist such atoms ($R''(b,c_1),R''(c_1,c_2),\ldots ,R''(c_n,a)$) in $\delta_{R''}$.
         Further, due to $R''\sqsubseteq_* R^-$ and Definition~\ref{def:deltaRdhl},
-        we have that $R(a,c_n),R(c_n,c_{n-1}),...,$ $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
+        we have that $R(a,c_n)$, $R(c_n,c_{n-1})$, \ldots, $R(c_1,b)\in\delta_{R}$. Thus, $R(a,b)\in\delta_{R}^*$
         also holds.
@@
 
-In the above definition, for a role sequence $L=R_1R_2,...,R_n$, let $L^-=R_n^-,...,R_2^-R_1^-$.
+In the above definition, for a role sequence $L=R_1R_2,\ldots ,R_n$, let $L^-=R_n^-,\ldots ,R_2^-R_1^-$.
 We then give the following definition for $\delta_R$.
@@
 & \{ R(a,b) \mid R_0R_1,\ldots,R_n\in\mathcal{L}(R),
-  R_i(x_i,x_{i+1})\in\mathcal{A}, i\in\{0,1,...,n\}, x_0=a, x_{n+1}=b \}.
+  R_i(x_i,x_{i+1})\in\mathcal{A}, i\in\{0,1,\ldots ,n\}, x_0=a, x_{n+1}=b \}.
 \end{align*}
@@
 % \item $R(a,b)$, for each $R'(b,a)\in\mathcal{A}$ and $R'\sqsubseteq_{*}R^-$;
-% \item $R(a,b)$, for each $R_0R_1,...,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $i\in\{0,1,...,n\}$.
+% \item $R(a,b)$, for each $R_0R_1,\ldots ,R_n\in\mathcal{L}(R)$, where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $i\in\{0,1,\ldots ,n\}$.
 % \end{enumerate}
@@
 (2) if $R$ is a transitive role, then $R(a,b)\in\delta^*_R$;
-(3) if $R$ is a non-simple but not transitive role, then there exists a role sequence $R_0R_1,...,R_n\in\mathcal{L}(R)$ such that
+(3) if $R$ is a non-simple but not transitive role, then there exists a role sequence $R_0R_1,\ldots ,R_n\in\mathcal{L}(R)$ such that
 $R_i(x_i,x_{i+1})\in\delta_{R_i}$, or, $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$ if $R_i$ is a transitive role,
-where $i\in\{0,1,...,n\}$ and $x_0=a, x_{n+1}=b$.
+where $i\in\{0,1,\ldots ,n\}$ and $x_0=a, x_{n+1}=b$.
 \end{lemma}
@@
     role $R''$ such that $R''(b,a)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, the case is
-    similar to Case~1.1.2 (Case~1.1.4). There exists $R_0R_1,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $i\in\{0,1,...,n\}$.
-    According to Definition~\ref{def:language}, $R_0R_1,...,R_n\in\mathcal{L}(R)$ holds since
+    similar to Case~1.1.2 (Case~1.1.4). There exists $R_0R_1,\ldots ,R_n\in\mathcal{L}(R')$,
+    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=a, x_{n+1}=b$ for $i\in\{0,1,\ldots ,n\}$.
+    According to Definition~\ref{def:language}, $R_0R_1,\ldots ,R_n\in\mathcal{L}(R)$ holds since
     $R'\sqsubseteq R\in\mathcal{R}$ (Case~1.1.5).\label{dhlplus:NTIcaseR1}
@@
     role $R''$ such that $R''(a,b)\in\mathcal{A}$ and $R''\sqsubseteq R'^-$, this case is
-    similar to Case~1.2.2 (Case~1.2.4). There exists $R_0R_1,...,R_n\in\mathcal{L}(R')$,
-    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $i\in\{0,1,...,n\}$.
-    According to Definition~\ref{def:language}, $R_n^-,...,R_0^-\in\mathcal{L}(R)$ holds since
+    similar to Case~1.2.2 (Case~1.2.4). There exists $R_0R_1,\ldots ,R_n\in\mathcal{L}(R')$,
+    where $R_i(x_i,x_{i+1})\in\mathcal{A}$ and $x_0=b, x_{n+1}=a$ for $i\in\{0,1,\ldots ,n\}$.
+    According to Definition~\ref{def:language}, $R_n^-,\ldots ,R_0^-\in\mathcal{L}(R)$ holds since
     $R'\sqsubseteq R^-\in\mathcal{R}$ (Case~1.2.5).\label{dhlplus:NTIcaseR2}
@@
     \item If there exists a role sequence
-      $R_0R_1,...,R_m\in\mathcal{L}(R')$ s.t.\ $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $i\in\{0,1,...,m\}$
-        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_1,...,R_m$ holds.
+      $R_0R_1,\ldots ,R_m\in\mathcal{L}(R')$ s.t.\ $R_j(x_j,x_{j+1})\in\mathcal{A}$ and $x_0=c_i, x_{n+1}=c_{i+1}$ for $i\in\{0,1,\ldots ,m\}$
+        and $R'\sqsubseteq_* R_i$, then $L_i=R_0R_1,\ldots ,R_m$ holds.
     \end{enumerate}
@@
     \item $R'$ is a non-simple but not a transitive role.
-        By the induction hypothesis, there exists $R_0R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,...,n\}$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_0R_1,...,R_n\in\mathcal{L}(R)$ also holds.
+        By the induction hypothesis, there exists $R_0R_1,\ldots ,R_n\in\mathcal{L}(R')$
+        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,\ldots ,n\}$
+        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$ holds, $R_0R_1,\ldots ,R_n\in\mathcal{L}(R)$ also holds.
 
@@
         By the induction hypothesis, there exists $R'(a,b)\in\delta^*_{R'}$.
-        Further, let $R'(a,c_1),R'(c_1,c_2),...,R'(c_n,b)\in\delta_{R'}$.
+        Further, let $R'(a,c_1),R'(c_1,c_2),\ldots ,R'(c_n,b)\in\delta_{R'}$.
         Since $R'\sqsubseteq R\in\mathcal{R}$ holds, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
+        $R(a,c_1),R(c_1,c_2)$ $,\ldots ,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
     \end{enumerate}
@@
 
-    \item $R'$ is a non-simple but not transitive role. By the induction hypothesis, there exists $R_0R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,...,n\}$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,...,R_0^-\in\mathcal{L}(R)$ also holds.
+    \item $R'$ is a non-simple but not transitive role. By the induction hypothesis, there exists $R_0R_1,\ldots ,R_n\in\mathcal{L}(R')$
+        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,\ldots ,n\}$
+        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$ holds, $R_n^-,\ldots ,R_0^-\in\mathcal{L}(R)$ also holds.
 
@@
         By the induction hypothesis, there exists $R'(b,a)\in\delta^*_{R'}$.
-        Further, let $R'(b,c_1),R'(c_1,c_2),...,R'(c_n,a)\in\delta_{R'}$.
+        Further, let $R'(b,c_1),R'(c_1,c_2),\ldots ,R'(c_n,a)\in\delta_{R'}$.
         Since $R'\sqsubseteq R^-\in\mathcal{R}$, we also have that
-        $R(a,c_1),R(c_1,c_2)$ $,...,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
+        $R(a,c_1),R(c_1,c_2)$ $,\ldots ,R(c_n,b)\in\delta_{R}$. Obviously $R(a,b)\in\delta^*_{R}$ holds.
     \end{enumerate}
@@
     \item $R'$ is a non-simple but not a transitive role.
-        By the induction hypothesis, there exists $R_0R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,...,n\}$
-        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_0R_1,...,R_n\in\mathcal{L}(R)$ also holds.
+        By the induction hypothesis, there exists $R_0R_1,\ldots ,R_n\in\mathcal{L}(R')$
+        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,\ldots ,n\}$
+        and $x_0=a, x_{n+1}=b$. Since $R'\sqsubseteq R$, $R_0R_1,\ldots ,R_n\in\mathcal{L}(R)$ also holds.
 
@@
 
-    \item $R'$ is a non-simple but not a transitive role. By the induction hypothesis, there exists $R_0R_1,...,R_n\in\mathcal{L}(R')$
-        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,...,n\}$
-        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,...,R_0^-\in\mathcal{L}(R)$ also holds.
+    \item $R'$ is a non-simple but not a transitive role. By the induction hypothesis, there exists $R_0R_1,\ldots ,R_n\in\mathcal{L}(R')$
+        such that $R_i(x_i,x_{i+1})\in\delta_{R_i}$ or $R_i(x_i,x_{i+1})\in\delta^*_{R_i}$, where $i\in\{0,1,\ldots ,n\}$
+        and $x_0=b, x_{n+1}=a$. Since $R'\sqsubseteq R^-$, $R_n^-,\ldots ,R_0^-\in\mathcal{L}(R)$ also holds.
 

### 2018-02-27 parallel-tractability-J-v9/background.tex
finished checking the appendix, merges changes into rel. work and conclusions
fixed the point of \sqsubseteq_*
final polishing

--- 2018-02-01 parallel-tractability-J-v9/background.tex
@@
 between roles such that $R_1\sqsubseteq R_2\in\mathcal{R}$ implies $R_1\sqsubseteq_{*}R_2$
-and $R_1^-\sqsubseteq_{*}R_2^-$. In this paper, we also use the
+and $R_1^-\sqsubseteq_{*}R_2^-$. We omit the reference to
+$\mathcal{R}$ if it is clear from the context. In this paper, we also use the
 notion of \emph{simple role}, which was initially proposed to restrict the
@@
 Specifically, given a datalog program $P=\langle R, \textbf{I}\rangle$,
-let $T_R(\textbf{I})=\{H\theta|\forall B_1,\ldots,B_n\rightarrow H\in R,
-B_i\theta\in\textbf{I}, 1\leq i\leq n \}$,
+we set\\[.5\baselineskip]
+\mbox{}\hfill $T_R(\textbf{I})=\{H\theta \mid \forall B_1,\ldots,B_n\rightarrow H\in R,
+B_i\theta\in\textbf{I}, 1\leq i\leq n \}$,\hfill\mbox{}\\[.5\baselineskip]
 where $\theta$ is some substitution; further let $T_R^{0}(\textbf{I})=\textbf{I}$ and

### 2018-02-27 parallel-tractability-J-v9/evaluation.tex
final polishing

@@
 
-\subsection{Parallel Tractability of the LUBM Datasets and YAGO Ontologies}
+\subsection{Parallel Tractability of LUBM Datasets and YAGO}
 \label{sec:lubm-yago}
 
-\textbf{LUBM}. In the Semantic Web community, LUBM
-(The Lehigh University Benchmark) is proposed to
+\textbf{LUBM}. In the Semantic Web community, 
+the Lehigh University Benchmark (LUBM) is proposed to
 facilitate the evaluation of ontology-based systems
@@
 when handling the datasets nptu-$4m$-$i$, $i\in\{1,2,4,8,16\}$ (see Figure~\ref{fig:diffdepths}(right)).
-Although the PTU and NPTU datasets are unrealistic in practice, these experiments indeed
+Although the PTU and NPTU datasets are not real-world examples, these experiments indeed
 verify that MG-depths determines the reasoning time in parallel
@@
 between ParallelDHL and RDFox.
-It can be checked from Table~\ref{tab:speedup} that
+Table~\ref{tab:speedup} shows that
 RDFox does not benefit from the allocation of several threads for ptu-$4m$-1;

### 2018-02-27 parallel-tractability-J-v9/introduction.tex
final polishing

@@
 An \texttt{NC} algorithm is required to terminate in parallel poly-logarithmic time.
-However, current materialization algorithms of datalog rewritable ontology languages
+However, \mbox{current} materialization algorithms of datalog rewritable ontology languages
 (e.g., the core algorithm used in RDFox \cite{MotikNPHO14}) are not \texttt{NC} algorithms
@@
 Finally, we analyze the well-known benchmark, LUBM, and the real-world dataset, YAGO, and
-show that these ontologies following the
-proposed restrictions belong to the parallel tractability classes.
+show that these ontologies satisfy the
+proposed restrictions and, hence, belong to the parallel tractability classes.
 We implement a system based on an optimized \texttt{NC} algorithm for DHL materialization,
-which we compare to the state-of-the-art reasoner RDFox.
+which we compare to the state-of-the-art reasoner RDFox \cite{MotikNPHO14}.
 The experimental results show that the optimizations proposed in this paper result in a
 better performance on ontologies that are
-tractable in parallel compared with RDFox.
+tractable in parallel compared to RDFox.
 
@@
 We then give two \texttt{NC} algorithms for ontology materialization in Section~\ref{sec:ptclass}.
-We study parallel tractability of materialization in DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto}, respectively.
+We study parallel tractability of materialization in DL-Lite, DHL and an extension of DHL in Section~\ref{sec:ptonto}.
 In Section~\ref{sec:practicalAlg},

### 2018-02-27 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
final polishing

@@
 one can further check that, for the materialization graph $\mathcal{G}$ constructed by Algorithm~$\mathsf{A}_{\text{bsc}}$,
-its depth equals the depth of the stage.
+its depth is equal to the depth of the stage.
 \end{proof}

### 2018-02-27 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
final polishing

@@
 the rule set turns out to be complete. The computational complexity
-of RDFS reasoning is NC-complete \cite{Horst05},
+of RDFS reasoning is \texttt{NC}-complete \cite{Horst05},
 which is not considered to be tractable in parallel.
@@
 any class of RDFS ontologies
-(\uppercase\expandafter{\romannumeral2}). This allows for expressing RDFS ontology
+(\uppercase\expandafter{\romannumeral2}). This allows for expressing RDFS ontologies
 in DHL (see Table~\ref{tab:rdfs}). Based on the two restrictions (\uppercase\expandafter{\romannumeral1})

### 2018-06-07 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
fixed \d{all}, it's indeed unclear
added missing plural (programs) in Def. 1

@@
 datalog programs sharing the same rule set, we say that $\mathcal{D}$
-is a class of datalog program with \emph{p}arallel
+is a class of datalog programs with \emph{p}arallel
 \emph{t}ractability, short a \emph{\texttt{PTD} class},
@@
   \item $B_1,\ldots,B_n\rightarrow H\in P^*$ is satisfied if $e(B_1, H),\ldots,e(B_n, H)\in E$ and
-  $B_1,\ldots,B_n$ are \d{all} the parents of $H$.
+  $B_1,\ldots,B_n$ are all the parents of $H$.
 \end{enumerate}

### 2018-06-07 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
revision

@@
 
-\begin{definition}\label{def:ptd}
-\textbf{(Parallel Tractability Class)} Given a class $\mathcal{D}$ of
+\begin{definition}[Parallel Tractability Class]\label{def:ptd}
+Given a class $\mathcal{D}$ of
 datalog programs sharing the same rule set, we say that $\mathcal{D}$
@@
 class of ontologies with parallel tractability, short a \texttt{PTO} class.
+
+\textcolor{red}{Suggested revision:} (Parallel Tractability Class). Let $R$ be a set of Datalog
+  rules. Materialization w.r.t.\ to $R$ is tractable in parallel, if,
+  for every set of facts $\textbf{I}$, there exists an \texttt{NC}
+  algorithm that performs sound and complete materialization for
+  $P=\langle R, \textbf{I}\rangle$; the set $\mathcal{D}$ of all
+  such Datalog programs $P$ is called a \emph{\texttt{PTD} class}.
+  The corresponding class of ontologies of $\mathcal{D}$ is called a
+  class of ontologies with parallel tractability, short a \texttt{PTO}
+  class.
 \end{definition}
@@
 
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
+\begin{definition}[Materialization Graph]\label{def:mg}
 A \emph{materialization graph}, with respect to
@@
   \item $H$ has a parent node or a child node;
-  \item if $H$ has the in-degree of $0$, then $H$ is an original fact of $P$;
+  \item if $H$ has an in-degree of $0$, then $H$ is an original fact of $P$;
   \item $B_1,\ldots,B_n\rightarrow H\in P^*$ is satisfied if $e(B_1, H),\ldots,e(B_n, H)\in E$ and
@@
 \end{enumerate}
+A materialization graph $\mathcal{G}$ is a \emph{complete materialization graph},
+when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
+
+\textcolor{red}{Suggested revision:}
+(Materialization Graph).
+A \emph{materialization graph}, with respect to
+a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
+denoted by $\mathcal{G}=\langle V, E\rangle$ where,
+\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
+  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
+  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
+\end{enumerate}
+For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are two nodes,
+we say that the node $v_1$ is the parent (node) of $v_2$ and the node $v_2$ is the child (node)
+of $v_1$.
+
+Further, for each $H,B_1,\ldots,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
+\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
+  \item if $e(B_1, H),\ldots,e(B_n, H)\in E$ and
+  $B_1,\ldots,B_n$ are all the parents of $H$, then $B_1,\ldots,B_n\rightarrow H\in P^*$;
+  \item if $H$ has an in-degree of $0$, then $H$ is an original fact
+    of $P$.
+\end{enumerate}
+A materialization graph $\mathcal{G}$ is a \emph{complete materialization graph},
+when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
 \end{definition}
@@
 
-We say that a materialization graph $\mathcal{G}$ is a \emph{complete materialization graph}
-when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
 The set of nodes in a complete materialization graph is actually the result

### 2018-06-13 parallel-tractability-J-v9/matGraphFactsOnly.tex
mat graph def

 \documentclass[final,1p,times]{elsarticle}

\usepackage{tikz}
\usetikzlibrary{positioning}
\tikzset{
    mynodee/.style={minimum height=0mm, minimum width=0mm, inner sep=0mm
  },
  mynode/.style={
    draw, circle, minimum height=1.7mm, minimum  width=1.7mm,line width=0.5mm
  },
  rect/.style={
    draw, rectangle, rounded corners, minimum height=7mm, minimum  width=30mm,line
    width=0.5mm, dotted
  }
}

\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}

\newtheorem{example}{Example}
\newtheorem{definition}{Definition}

\begin{document}

\begin{definition}[Materialization Graph]\label{def:mg}
  A \emph{materialization graph} $\mathcal{G}$ with respect to a
  datalog program $P=\langle R, \textbf{I}\rangle$ is a directed
  acyclic graph $\langle V, E\rangle$ such that the set of nodes $V$
  satisfies $\textbf{I} \subseteq V\subseteq T_R^{\omega}(\textbf{I})$
  and the set of edges $E$ satisfies
  $E\subseteq T_R^{\omega}(\textbf{I})\times
  T_R^{\omega}(\textbf{I})$. For each edge $(v_1, v_2)$, we say that
  the node $v_1$ is the \emph{parent} (node) of $v_2$ and the node
  $v_2$ is the \emph{child} (node) of $v_1$. A materialization graph
  further satisfies the following conditions:
  \begin{itemize}
  \item each $v \in \textbf{I}$, $v$ has an in-degree of $0$;
  \item each $H \in V \setminus \textbf{I}$ such that $B_1,\ldots,B_n$
    are all the parents of $H$, there is exactly one
    $B_1,\ldots,B_n\rightarrow H\in P^*$.
  \end{itemize}
  A materialization graph $\mathcal{G}$ is a \emph{complete
    materialization graph} when $V$ contains all ground atoms in
  $T_R^{\omega}(\textbf{I})$.
\end{definition}

\begin{example}\label{exp:dllite}
  Given a (DL-Lite) ontology $\mathcal{O}_{\text{ex}_1}$ where the TBox
  contains the following axioms: $B\sqsubseteq A_1$,
  $B\sqsubseteq A_2$; its ABox contains the assertions $A_1(a)$ and
  $A_2(a)$.  We denote the corresponding datalog program of
  $\mathcal{O}_{\text{ex}_1}$ by
  $P_{\text{ex}_1}=\langle R, \textbf{I}\rangle$, where $R$ contains the
  rules that are transformed from the above axioms ($B(x) \to A_1(x)$,
  $B(x) \to A_2(x)$); $\textbf{I}$ contains $A_1(a)$ and $A_2(a)$.
  The unique complete materialization graph of $P_{\text{ex}_1}$ is denoted by
  $\mathcal{G}_{\text{ex}_1}$ (see Figure~\ref{fig:ex1}).
\end{example}

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
 \node[mynode, label=right:$A_1(a)$] (a1a) at (0, 0) {};
 \node[mynode, label=right:$A_2(a)$] (a2a) at (3, 0) {};
\end{tikzpicture}
\caption{The unique  complete materialization graph of $\mathcal{O}_{\text{ex}_1}$}
\label{fig:ex1}
\end{figure}

\clearpage

\begin{example}\label{exp:dllite}
  Given a (DL-Lite) ontology $\mathcal{O}_{\text{ex}_2}$ where the TBox
  contains the following axioms: $A_1\sqsubseteq B$,
  $A_2\sqsubseteq B$; its ABox contains the assertions $A_1(a)$ and
  $A_2(a)$.  We denote the corresponding datalog program of
  $\mathcal{O}_{\text{ex}_2}$ by
  $P_{\text{ex}_2}=\langle R, \textbf{I}\rangle$, where $R$ contains the
  rules that are transformed from the above axioms ($A_1(x) \to B(x)$,
  $A_2(x) \to A_1(x)$); $\textbf{I}$ contains $A_1(a)$ and $A_2(a)$.
  The two complete materialization graphs of $P_{\text{ex}_2}$ are denoted by
  $\mathcal{G}_{\text{ex}_{2a}}$ and $\mathcal{G}_{\text{ex}_{2b}}$
  (see Figure~\ref{fig:ex2}).

  \textcolor{red}{Note that Figure~\ref{fig:ex2not} does not show a
    materialization graph of $P_{\text{ex}_2}$ since the node $B(a)$
    has the two parents $A_1(a)$ and $A_2(a)$. Hence, there should be
    a rule $A_1(a), A_2(a) \to B(a) \in P_{\text{ex}_2}^*$ by the
    definition of materialization graphs.}
\end{example}

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
  \begin{scope}
   \node[mynode, label=right:$A_1(a)$] (a1a) at (0, 0) {};
   \node[mynode, label=right:$A_2(a)$] (a2a) at (3, 0) {};
   \node[mynode, label=right:$B(a)$] (ba) at (1.5, 1.5) {};

   \draw[-latex,line width=0.5mm] (a1a) -- (ba);
   \draw[very thin,gray] (-.5, .75) -- (4, .75);
 \end{scope}
  \begin{scope}[xshift=7cm]
   \node[mynode, label=right:$A_1(a)$] (a1a) at (0, 0) {};
   \node[mynode, label=right:$A_2(a)$] (a2a) at (3, 0) {};
   \node[mynode, label=right:$B(a)$] (ba) at (1.5, 1.5) {};

   \draw[-latex,line width=0.5mm] (a2a) -- (ba);
   \draw[very thin,gray] (-.5, .75) -- (4, .75);
 \end{scope}
\end{tikzpicture}
\caption{The complete materialization graphs of $\mathcal{O}_{\text{ex}_2}$}
\label{fig:ex2}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
   \node[mynode, label=right:$A_1(a)$] (a1a) at (0, 0) {};
   \node[mynode, label=right:$A_2(a)$] (a2a) at (3, 0) {};
   \node[mynode, label=right:$B(a)$] (ba) at (1.5, 1.5) {};

   \draw[-latex,line width=0.5mm] (a1a) -- (ba);
   \draw[-latex,line width=0.5mm] (a2a) -- (ba);
   \draw[very thin,gray] (-.5, .75) -- (4, .75);
\end{tikzpicture}
\caption{Not a materialization graphs of $\mathcal{O}_{\text{ex}_2}$!}
\label{fig:ex2not}
\end{figure}

\clearpage

\begin{example}\label{exp:dllite}
  Given a (DL-Lite) ontology $\mathcal{O}_{\text{ex}_3}$ where the
  TBox contains the following axiom: $A\sqsubseteq B$; its ABox
  contains the assertions $A(a)$ and $B(a)$.  We denote the
  corresponding datalog program of $\mathcal{O}_{\text{ex}_3}$ by
  $P_{\text{ex}_3}=\langle R, \textbf{I}\rangle$, where $R$ contains
  the rules that are transformed from the above axioms
  ($A(x) \to B(x)$); $\textbf{I}$ contains $A(a)$ and $B(a)$.  The
  unique complete materialization graph of $P_{\text{ex}_3}$ is
  denoted by $\mathcal{G}_{\text{ex}_3}$ (see Figure~\ref{fig:ex3}).

  \textcolor{red}{Note that there cannot be an edge between $A(a)$ and $B(a)$ since
  both are facts and must have in-degree of $0$.}
\end{example}

\begin{figure}[htbp]
\centering
\begin{tikzpicture}
   \node[mynode, label=right:$A(a)$] (aa) at (0, 0) {};
   \node[mynode, label=right:$B(a)$] (ba) at (3, 0) {};
\end{tikzpicture}
\caption{The unique complete materialization graph of $\mathcal{O}_{\text{ex}_3}$}
\label{fig:ex3}
\end{figure}

\clearpage

\begin{example}\label{exp:dllite}
  Given a (DL-Lite) ontology $\mathcal{O}_{\text{ex}_4}$ where the
  TBox contains the following axiom: $A\sqsubseteq B$; its ABox
  contains the assertions $A(a)$ and $B(b)$.  We denote the
  corresponding datalog program of $\mathcal{O}_{\text{ex}_4}$ by
  $P_{\text{ex}_4}=\langle R, \textbf{I}\rangle$, where $R$ contains
  the rules that are transformed from the above axioms
  ($A(x) \to B(x)$); $\textbf{I}$ contains $A(a)$ and $B(b)$.  The
  unique complete materialization graph of $P_{\text{ex}_4}$ is
  denoted by $\mathcal{G}_{\text{ex}_4}$ (see Figure~\ref{fig:ex4}).

  \textcolor{red}{Note that Figure~\ref{fig:ex4incomplete} shows a
    materialization graph of $P_{\text{ex}_4}$, but it is an
    incomplete one since the node $B(a) \not\in V$, but
    $B(a) \in T_R^{\omega}(\textbf{I})$. Figure~\ref{fig:ex4notfacts}
    does not show a materialization graph of $P_{\text{ex}_4}$ since
    $B(b) \not\in V$, but $B(b) \in \textbf{I}$ and
    $\textbf{I} \subseteq V$ is violated. Figure~\ref{fig:ex4not} does
    not show a materialization graph of $P_{\text{ex}_4}$ since the
    node $A(b) \in V \setminus \textbf{I}$ and has no parents. Hence
    there should be $\rightarrow A(b)\in P^*$, which is not the case.}
\end{example}

\begin{figure}[h]
\centering
\begin{tikzpicture}
   \node[mynode, label=right:$A(a)$] (aa) at (0, 0) {};
   \node[mynode, label=right:$B(a)$] (ba) at (0, 1.5) {};
   \node[mynode, label=right:$B(b)$] (bb) at (3, 0) {};
   \phantom{\node[mynode, label=right:$A(b)$] (ab) at (6, 0) {};}

   \draw[-latex,line width=0.5mm] (aa) -- (ba);
   \draw[very thin,gray] (-.5, .75) -- (4, .75);
\end{tikzpicture}
\caption{The unique, complete materialization graph of
  $\mathcal{O}_{\text{ex}_4}$ }
\label{fig:ex4}
\end{figure}

\begin{figure}[h]
\centering
\begin{tikzpicture}
   \node[mynode, label=right:$A(a)$] (aa) at (0, 0) {};
   \node[mynode, label=right:$B(b)$] (bb) at (3, 0) {};
   \phantom{\node[mynode, label=right:$A(b)$] (ab) at (6, 0) {};}
\end{tikzpicture}
\caption{An incomplete materialization graph of
  $\mathcal{O}_{\text{ex}_4}$ }
\label{fig:ex4incomplete}
\end{figure}

\begin{figure}[h]
\centering
\begin{tikzpicture}
   \node[mynode, label=right:$A(a)$] (aa) at (0, 0) {};
   \phantom{\node[mynode, label=right:$A(b)$] (ab) at (6, 0) {};}
\end{tikzpicture}
\caption{Not a materialization graph of
  $\mathcal{O}_{\text{ex}_4}$ due to missing facts}
\label{fig:ex4notfacts}
\end{figure}

\begin{figure}[h]
\centering
\begin{tikzpicture}
   \node[mynode, label=right:$A(a)$] (aa) at (0, 0) {};
   \node[mynode, label=right:$B(a)$] (ba) at (0, 1.5) {};
   \node[mynode, label=right:$B(b)$] (bb) at (3, 0) {};
   \node[mynode, label=right:$A(b)$] (ab) at (6, 0) {};

   \draw[-latex,line width=0.5mm] (aa) -- (ba);
   \draw[very thin,gray] (-.5, .75) -- (7, .75);
\end{tikzpicture}
\caption{Not a materialization graph of $\mathcal{O}_{\text{ex}_4}$}
\label{fig:ex4not}
\end{figure}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "fig-dllite"
%%% End:

### 2018-06-13 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
mat graph def

@@
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
+  \item $V$ is the node set and $\textbf{I} \subseteq V\subseteq T_R^{\omega}(\textbf{I})$;
   \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
@@
 we say that the node $v_1$ is the parent (node) of $v_2$ and the node $v_2$ is the child (node)
-of $v_1$.
-
-Further, for each $H,B_1,\ldots,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
+of $v_1$. A materialization graph satisfies the following conditions:
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item if $e(B_1, H),\ldots,e(B_n, H)\in E$ and
-  $B_1,\ldots,B_n$ are all the parents of $H$, then $B_1,\ldots,B_n\rightarrow H\in P^*$;
-  \item if $H$ has an in-degree of $0$, then $H$ is an original fact
-    of $P$.
+\item each $v \in \textbf{I}$, $v$ has an in-degree of $0$;
+\item each $H \in V \setminus \textbf{I}$ such that $B_1,\ldots,B_n$
+  are all the parents of $H$, there is exactly one
+  $B_1,\ldots,B_n\rightarrow H\in P^*$.
 \end{enumerate}

### 2018-06-13 parallel-tractability-J-v9/background.tex
revision
rebuttal questions addressed

@@
 the form `$\rightarrow H$', i.e., a rule with an empty body and the head $H$ being a ground atom.
-A datalog program $P$ consists of rules and facts.
+A datalog program  $P=\langle R, \textbf{I}\rangle$ consists of a
+finite set of rules $R$ and a finite set of facts $\textbf{I}$.
 A \emph{substitution} $\theta$ is a partial mapping of variables to constants.
@@
 to the datalog program $P=\langle R, \textbf{I}\rangle$ if $A\in T_R^{\omega}(\textbf{I})$.
-In this paper, we consider the data complexity of materialization, i.e., we \emph{assume that the rule set $R$ is fixed}
-for any class of datalog programs.
+In this paper, we consider the \emph{data complexity} of
+materialization, i.e., we \emph{assume that only the data is
+  considered to be an input, whereas the  rule set $R$ is fixed}.
 

### 2018-06-13 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
rebuttal questions addressed

--- 2018-06-07 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
@@
 
-Our target is to find for which kinds of ontologies (not ontology languages)
-materialization is tractable in parallel. We consider data complexity,
-i.e., we consider classes of datalog programs which share a fixed rule set.
-The data complexity of the materialization problem in this case is
-$\texttt{PTime}$-complete, which is considered to be inherently sequential in the worst
-case \cite{Raymond95}.
+Our target is to find for which kinds of ontologies (not ontology
+languages) materialization is tractable in parallel. We consider
+\emph{data complexity}, i.e., we \emph{assume that only the data is
+  considered to be an input, whereas the rule set $R$ is fixed}.
+  The data complexity of the materialization problem in this case
+is $\texttt{PTime}$-complete, which is considered to be inherently
+sequential in the worst case \cite{Raymond95}.
 % Since we assume that, for any class of datalog programs where the rule
@@
 We first give the following definition for a class of datalog programs
-that is tractable in parallel, i.e., an \texttt{NC} algorithm exists for handling each datalog program in this class.
+that is tractable in parallel, i.e., an \texttt{NC} algorithm exists
+for handling each datalog program in this class.
 
-\begin{definition}\label{def:ptd}
-\textbf{(Parallel Tractability Class)} Given a class $\mathcal{D}$ of
-datalog programs sharing the same rule set, we say that $\mathcal{D}$
-is a class of datalog programs with \emph{p}arallel
-\emph{t}ractability, short a \emph{\texttt{PTD} class},
-if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
-in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
-class of ontologies with parallel tractability, short a \texttt{PTO} class.
+\begin{definition}[Parallel Tractability Class]\label{def:ptd}
+% Given a class $\mathcal{D}$ of
+% datalog programs sharing the same rule set, we say that $\mathcal{D}$
+% is a class of datalog programs with \emph{p}arallel
+% \emph{t}ractability, short a \emph{\texttt{PTD} class},
+% if there exists an \texttt{NC} algorithm that performs sound and complete materialization for each datalog program
+% in $\mathcal{D}$. The corresponding class of ontologies of $\mathcal{D}$ is called a
+% class of ontologies with parallel tractability, short a \texttt{PTO} class.
+
+% \textcolor{red}{Suggested revision:} (Parallel Tractability Class). 
+  Let $R$ be a set of Datalog rules. Materialization w.r.t.\ to $R$ is
+  tractable in parallel, if, for every set of facts $\textbf{I}$,
+  there exists an \texttt{NC} algorithm that performs sound and
+  complete materialization for $P=\langle R, \textbf{I}\rangle$; the
+  set $\mathcal{D}$ of all such Datalog programs $P$ is called a
+  \emph{\texttt{PTD} class}.  The corresponding class of ontologies of
+  $\mathcal{D}$ is called a class of ontologies with parallel
+  tractability, short a \texttt{PTO} class.
 \end{definition}
@@
 
-\begin{definition}
-\textbf{(Materialization Graph)}\label{def:mg}
-A \emph{materialization graph}, with respect to
-a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
-denoted by $\mathcal{G}=\langle V, E\rangle$ where,
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
-  \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
-\end{enumerate}
-For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are two nodes,
-we say that the node $v_1$ is the parent (node) of $v_2$ and the node $v_2$ is the child (node)
-of $v_1$. Further, $\forall H,B_1,\ldots,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
-\begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-  \item $H$ has a parent node or a child node;
-  \item if $H$ has the in-degree of $0$, then $H$ is an original fact of $P$;
-  \item $B_1,\ldots,B_n\rightarrow H\in P^*$ is satisfied if $e(B_1, H),\ldots,e(B_n, H)\in E$ and
-  $B_1,\ldots,B_n$ are all the parents of $H$.
-\end{enumerate}
+% \begin{definition}[Materialization Graph]\label{def:mg}
+% A \emph{materialization graph}, with respect to
+% a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
+% denoted by $\mathcal{G}=\langle V, E\rangle$ where,
+% \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
+%   \item $V$ is the node set and $V\subseteq T_R^{\omega}(\textbf{I})$;
+%   \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
+% \end{enumerate}
+% For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are two nodes,
+% we say that the node $v_1$ is the parent (node) of $v_2$ and the node $v_2$ is the child (node)
+% of $v_1$. Further, $\forall H,B_1,\ldots,B_n\in V$, $\mathcal{G}$ satisfies the following conditions:
+% \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
+%   \item $H$ has a parent node or a child node;
+%   \item if $H$ has an in-degree of $0$, then $H$ is an original fact of $P$;
+%   \item $B_1,\ldots,B_n\rightarrow H\in P^*$ is satisfied if $e(B_1, H),\ldots,e(B_n, H)\in E$ and
+%   $B_1,\ldots,B_n$ are all the parents of $H$.
+% \end{enumerate}
+% A materialization graph $\mathcal{G}$ is a \emph{complete materialization graph},
+% when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
+
+% \textcolor{red}{Suggested revision:}
+% (Materialization Graph).
+% A \emph{materialization graph}, with respect to
+% a datalog program $P=\langle R, \textbf{I}\rangle$, is a directed acyclic graph
+% denoted by $\mathcal{G}=\langle V, E\rangle$ where,
+% \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
+%   \item $V$ is the node set and $\textbf{I} \subseteq V\subseteq T_R^{\omega}(\textbf{I})$;
+%   \item $E$ is the edge set and $E\subseteq T_R^{\omega}(\textbf{I})\times T_R^{\omega}(\textbf{I})$.
+% \end{enumerate}
+% For each edge of the form $e(v_1, v_2)$ where $v_1$ and $v_2$ are two nodes,
+% we say that the node $v_1$ is the parent (node) of $v_2$ and the node $v_2$ is the child (node)
+% of $v_1$. A materialization graph satisfies the following conditions:
+% \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
+% \item each $v \in \textbf{I}$, $v$ has an in-degree of $0$;
+% \item each $H \in V \setminus \textbf{I}$ such that $B_1,\ldots,B_n$
+%   are all the parents of $H$, there is exactly one
+%   $B_1,\ldots,B_n\rightarrow H\in P^*$.
+% \end{enumerate}
+% A materialization graph $\mathcal{G}$ is a \emph{complete materialization graph},
+% when $\mathcal{G}$ contains all ground atoms in $T_R^{\omega}(\textbf{I})$.
+% \end{definition}
+
+\begin{definition}[Materialization Graph]\label{def:mg}
+  A \emph{materialization graph} $\mathcal{G}$ with respect to a
+  datalog program $P=\langle R, \textbf{I}\rangle$ is a directed
+  acyclic graph $\langle V, E\rangle$ such that the set of nodes $V$
+  satisfies $\textbf{I} \subseteq V\subseteq T_R^{\omega}(\textbf{I})$
+  and the set of edges $E$ satisfies
+  $E\subseteq T_R^{\omega}(\textbf{I})\times
+  T_R^{\omega}(\textbf{I})$. For each edge $(v_1, v_2)$, we say that
+  the node $v_1$ is the \emph{parent} (node) of $v_2$ and the node
+  $v_2$ is the \emph{child} (node) of $v_1$. A materialization graph
+  further satisfies the following conditions:
+  \begin{itemize}
+  \item each $v \in \textbf{I}$, $v$ has an in-degree of $0$;
+  \item each $H \in V \setminus \textbf{I}$ such that $B_1,\ldots,B_n$
+    are all the parents of $H$, there is exactly one
+    $B_1,\ldots,B_n\rightarrow H\in P^*$.
+  \end{itemize}
+  A materialization graph $\mathcal{G}$ is a \emph{complete
+    materialization graph} when $V$ contains all ground atoms in
+  $T_R^{\omega}(\textbf{I})$.
+
+  The \emph{size} of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the
+  number of nodes in $\mathcal{G}$.  The depth of $\mathcal{G}$,
+  denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a
+  path in $\mathcal{G}$.
 \end{definition}
@@
 described by a materialization graph.
-Suppose $\mathcal{G}$ is a materialization graph such that the nodes
-with in-degree 0 are the
-original facts in $\textbf{I}$.
-The size of $\mathcal{G}$, denoted by $|\mathcal{G}|$, is the number of nodes in $\mathcal{G}$.
-The depth of $\mathcal{G}$, denoted by \texttt{depth}($\mathcal{G}$), is the maximal length of a path
-in $\mathcal{G}$.
+% Suppose $\mathcal{G}$ is a materialization graph such that the nodes
+% with in-degree 0 are the
+% original facts in $\textbf{I}$.
 We next give an example of a materialization graph.\\

### 2018-06-13 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
mat graph def
rebuttal questions addressed

@@
 as the only fact.
-The unique materialization graph of $P_{\text{ex}_5}$ is denoted by $\mathcal{G}_{\text{ex}_5}$ (see Figure~\ref{fig:ex2}).
+The unique materialization graph of $P_{\text{ex}_5}$ is denoted by
+$\mathcal{G}_{\text{ex}_5}$ (see
+Figure~\ref{fig:ex2}). \textcolor{red}{How is $A(a)$ derived from the
+  ontology and $Q(a, b)$?}
 \end{example}
@@
 
-The original rule set for RDFS reasoning is
-given by \citet{RDFSrec04}. By applying the rules in this rule set,
-new schema data could be derived. Thus, the reasoning task of RDFS
-is different from the task of materialization. Further, an RDFS ontology allows
-statements about blank nodes which act like variables. This possibly
-leads to infinite entailments. Additionally, the original rule set is
+The original rule set for RDFS reasoning is given by
+\citet{RDFSrec04}. By applying the rules in this rule set, new schema
+data can be derived. Thus, the reasoning task of RDFS is different
+from the task of materialization. In general, the RDFS (deductive)
+closure is infinite since infinitely many axiomatic triples are
+entailed by any (even the empty) RDF ontology. There are infinitely
+many axiomatic triples due to the infinite numer of container
+membership properties, which can be used to state that a resource is a
+member of some container. Further, RDFS ontologies allow statements
+about blank nodes, which act like variables. This possibly leads to
+infinite entailments. Additionally, the original rule set is
 incomplete with the RDF restriction that

### 2018-06-13 parallel-tractability-J-v9/response2.tex
rebuttal questions addressed

\documentclass{article}
\usepackage{amsmath}
\usepackage{url}

\let\quoteOld\quote
\let\endquoteOld\endquote
\renewenvironment{quote}{\quoteOld\itshape}{\endquoteOld}

% use the following command line to convert to standard text file
% pandoc reviews.tex -o rebuttal.txt
\setlength{\parindent}{0pt}

\usepackage[usenames, dvipsnames]{color}
\newcommand{\BG}[1]{\textcolor{red}{BG: #1}}
%\renewcommand{\BG}[1]{}

\begin{document}

We thank the reviewers for the time and effort invested in the revised
submission and their helpful comments to improve the paper. Below we
reply to the points raised by the reviewers.

\section{Rebuttal to Review 1}

\begin{quote}
In Section 4.4 it should be "can be derived" instead of "could be derived".
The wording in the submission looks as if that is something that is no
longer possible.
\end{quote}

done

\begin{quote}
RDF(S) materialization is also infinite because of the infinite non-trivial
vocabulary for RDF containers.  This doesn't matter in theory because the
inferences can be easily summarized and doesn't matter in practice because
this vocabulary is hardly used.  However, there should be a bit on it
anyway.
\end{quote}

We discuss this now in Sec.~4.4 on p.~17.

\section{Rebuttal to Review 2}

\begin{quote}
  For the revised Definition~1, I wonder why it requires all datalog
  programs in a class $\mathcal{D}$ to share the same rule set. And it
  contradicts to the claim after the definition that each \texttt{NC}
  algorithm $\mathsf{A}$ corresponds to a class
  $\mathcal{D}_\mathsf{A}$. Does it mean a \texttt{NC} algorithm only
  applies to one rule set? To study data complexity, one can assume
  the size of the rule set is fixed, but I do not see why the rules
  need to be fixed.
\end{quote}

Since we study the data complexity (see last sentence before
Section~2.4 and the second sentence of Sec.~3), we consider only the
data (the facts $\textbf{I}$ as input), whereas the rule set is
assumed to be fixed. This is the standard definition for data
complexity. We have rephrased Definition~1 and now use a phrasing
closer to that used by Lutz and Wolter \cite{LuWo17a}, which hopefully
makes this clearer. It is important (and not specific to our work)
that only the data is considered as (variable) input.

This does not mean that an \texttt{NC} algorithm applies to just one
rule set, but it means that for studying the data complexity, we
assume that only the input data can be different (is in the input),
whereas the rule set is considered fixed.

Hence, while the algorithms (e.g.\ Algorithm $\mathsf{A}_\text{bsc}$
or (or $\mathsf{A}_\text{opt}$) involve two inputs (rules and facts),
for the complexity analysis, we assume the rules part of the input to
be fixed. In general, however, the algorithms can handle different
rule sets. Please note that we still have to show taht the (data)
complexity holds for all possible sets of facts.

\begin{quote}
  The revised Definition~2 also has some issues. The second condition
  does not preclude the cases where original facts get parents and
  where derived facts get no parents; and the third condition does not
  mention which rules in $P^*$ the graph $G$ must satisfy or wether
  $G$ need to satisfy any rule at all.
\end{quote}

Thanks for pointing that out. The definition indeed had issues and we
have revised it. Original facts now have to be present in $G$ and have
to have an in-degree of $0$. Derived facts now have to have parents
(otherwise they would have an in-degree of $0$, which is only allowed
for original facts) and the parents correspond to a ground rule that
allows for deriving the fact. We have also moved the definition of a
\emph{complete} materialization graph forward, which was so far in
text and not in the definition environment. This will hopefully make
it clearer that not all derivable facts have to be present in a
materialization graph unless it is a complete materialization graph.

\textcolor{red}{Why do you write $e(v_1, v_2)$ for edges and not just
  $(v_1, v_2)$?}

\textcolor{red}{In the materialization graph for Example~5, how is
  $A(a)$ derived from the ontology and $Q(a, b)$? }

\begin{quote}
  In Algorithm $\mathsf{A}_\text{bst}$, the reason why Step~2 costs
  constant time is still unclear. The paragraph below Lemma~1 does not
  provide any explanation. The authors pointed out two references in
  their response, but I could not find any clue in those articles (one
  of which is just a two page summary \textcolor{red}{I can also not
    see why this reference is of any help. Maybe we should comment on
    this? }). \textcolor{red}{For the second reference
    \cite{Raymond95}, I can also not see where it talks about matrix
    multiplication? Does this follow from what is written below
    Def.~3.2.10?} Again, even under the assumption that there is an
  one-to-one correspondence between processors and rule instances, for
  each processor and the corresponding rule $B_1, \ldots, B_n \to H$,
  the complexity of checking the applicability of
  $B_1, \ldots, B_n \to H$ in $G$ and at the same time updating $G$
  should depend on the size of $G$. 
\end{quote}

For the constant time claims, an important precondition is the
computation model used for analysis. Parallel random access machine
(PRAM for short) is used as the basic computation model in this
paper. PRAM is an extension of the random access machine (RAM) model.

1) Suppose that there is a one-to-one correspondence between
processors and rule instances, and each processor can access the
location of any atom in constant time (given as the parallel
assumption in Section~3.3).  \textcolor{red}{What might be confusing
  is the term rule instance. In Sec.~2.1, we do not introduce the
  term, but we say `ground instantiation of a rule`, which I suppose
  means the same thing, but maybe the reviewer reads `rule instance`
  as `rule', which is a significant difference. If `rule instance'
  indeed means `ground instantiation of a rule', we should unify our
  terminology to avoid confusion. } Since a processor $p$ corresponds
to a rule instance, e.g., $B_1, \ldots, B_n \to H$, processor $p$
knowns the relationship among $B_1, \ldots, B_n$ and $H$. Further,
processor $p$ knows the locations of the nodes $B_1, \ldots, B_n$ and
$H$. Thus, it could check the derivability of $B_1, \ldots, B_n$, and
bridge \textcolor{red}{`to bridge' means to connect in the sense of
  adding the edge to $G$?} $B_i$ and $H$ ($1 \leq i \leq n$) in
constant time instead of searching the whole graph $G$.

2) How to establish such a one-to-one correspondence between processors 
and rule instances and the constant-time access to each atom for processors?

We should also introduce the notion of Boolean circuit, which is a
circuit that consists of logic gates, e.g., AND and OR gates (see
\cite[Section~2.3]{Raymond95}).  A materialization graph can also be
seen as a Boolean circuit by treating the nodes as AND gates.\\
%
First, the evaluation of a Datalog program is equivalent to the evaluation 
of its corresponding Boolean circuit in terms of computational
complexity \cite{DMRT14a}. \\
%
Second, a Boolean circuit can be simulated by PRAM based on an
algorithm called parallel prefix computation \cite{LaFi80a}.  Further,
the complexity of simulation is lower than that of the evaluation of
the Boolean circuit \cite[Lemma~2.4.1]{Raymond95}.\\
%
Third, during the above simulation procedure, a one-to-one
correspondence between each gate in the Boolean circuit and the
processors in PRAM and the constant-time access are established.\\
%
In our case, the one-to-one correspondence between processors and rule
instances and the constant-time access to each node can also be
established by PRAM similarly to the above simulation procedure.

\textcolor{red}{We have added the above argumentation also to the
  paper. (needed?, TBD)}

\begin{quote}
  Again, in Algorithm $\mathsf{A}_\text{opt}$ the claim that the
  computation of $S_\text{rch}$ and updating $G$ cost only constant
  time is unclear.
\end{quote}

\textcolor{red}{The argumentation for this claim is similar to the one
  given above. (?)}

\bibliographystyle{elsarticle-num}
\bibliography{response2}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2018-06-14 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
added an axiom to Example 5

@@
 $A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
+$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $\exists Q.\top\sqsubseteq A$ and $S\sqsubseteq R$;
 its ABox contains an assertion $Q(a,b)$.

### 2018-06-14 parallel-tractability-J-v9/background.tex
unify the usage of 'rule instantiation'

@@
 the terms in this rule with respect to a finite set of constants occurring in $P$.
+For simplicity, we use a \emph{rule instantiation} to denote a ground instantiation of a rule.
 Furthermore the ground instantiation of $P$, denoted by $P^*$,
-consists of all ground instantiations of rules in $P$.
+consists of all rule instantiations with respect to $P$.
 The predicates occurring only in the body  of some rules are called \emph{EDB predicates},

### 2018-06-14 parallel-tractability-J-v9/evaluation.tex
unify the usage of 'rule instantiation'

@@
 the parallel assumption given in Section~\ref{sec:alg-bsc} does not apply to ParallelDHL.
-In the implementation of ParallelDHL, we use a hash function to map any rule instance
+In the implementation of ParallelDHL, we use a hash function to map any rule instantiation
 to the identifier of some processor. Thus, when performing ParallelDHL,
-each processor handles a group of rule instances.
+each processor handles a group of rule instantiations.
 
@@
 $\texttt{cite}(\texttt{a}_i,\texttt{a}_{i+1})$ ($i\in\{0,1,2,...\}$),
-where $\texttt{a}_i$ denotes an article instance.
+where $\texttt{a}_i$ denotes an article instantiation.
 As discussed in Section~\ref{sec:lubm-yago},

### 2018-06-14 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
unify the usage of 'rule instantiation'

@@
 for any datalog program $P=\langle R, \textbf{I}\rangle$,
-any substitution of some atom and any rule instance in $P^*$ can be mapped to a unique memory
-location; further, a one-to-one relation can be established between processors and rule instances.
+any substitution of some atom and any rule instantiation in $P^*$ can be mapped to a unique memory
+location; further, a one-to-one relation can be established between processors and rule instantiations.
 Under this assumption, a processor can check the applicability of its corresponding
-rule instance and access the state of an atom occurring in this rule instance in constant time.
+rule instantiation and access the state of an atom occurring in this rule instantiation in constant time.
 Algorithm~$\mathsf{A}_{\text{bsc}}$ is then given as follows.\\
@@
 We then have that the number of
-constants is at most $|\textbf{I}|e$, and the number of all possible rule instances in $P^*$
+constants is at most $|\textbf{I}|e$, and the number of all possible rule instantiations in $P^*$
 is at most $r(|\textbf{I}|e)^v$.
 Note that $e, v$ and $r$ depend only on the rule set $R$ and not on the fact set $\textbf{I}$.
-Thus, the memory space for storing the atoms and the rule instances is polynomial in the size of $\textbf{I}$.
+Thus, the memory space for storing the atoms and the rule instantiations is polynomial in the size of $\textbf{I}$.
 This also means that the number of processors is polynomially bounded.

### 2018-06-14 parallel-tractability-J-v9/appendix.tex
replace 'e(v1, v2)' with '(v1, v2)'

@@
 (1) If $H$ is not in $\mathcal{G}^{i}$ while $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),\ldots ,e(B_n, H)$ are created.
+then $H$ is added to $\mathcal{G}^{i+1}$, and the edges $(B_1, H),\ldots ,(B_n, H)$ are created.
 (2) If neither of $H$ and $B_k$ is in $\mathcal{G}^{i}$,
-then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),\ldots ,e(B_n, H)$ are also created.
+then $H$ and $B_k$ are added to $\mathcal{G}^{i+1}$, and the edges $(B_1, H),\ldots ,(B_n, H)$ are also created.
 In the above two cases, $H$ is a new node. Thus,
@@
 (3) If $H$ is in $\mathcal{G}^{i}$ and $H$ has no parent,
-$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $e(B_1, H),\ldots ,e(B_n, H)$ are also created.
+$B_k$ is added to $\mathcal{G}^{i+1}$, and the edges $(B_1, H),\ldots ,(B_n, H)$ are also created.
 For the case that $H$ is in $\mathcal{G}^{i}$ and $H$ has parents,

### 2018-06-14 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
replace 'e(v1, v2)' with '(v1, v2)'

@@
     to it, add $H$ and $B_i$ (if $B_i$ is not in $\mathcal{G}$) to $\mathcal{G}$, and create the edges
-    $e(B_1, H), \ldots, e(B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
+    $(B_1, H), \ldots, (B_n, H)$ in $\mathcal{G}$. Do nothing for other statements
     \texttt{rch}$(B_j,H)\in S_{\!\textit{\tiny rch}}$.\label{updateG}\hfill$\Box$

### 2018-06-14 parallel-tractability-J-v9/response2.tex
added some content in Response2

@@
 be fixed. In general, however, the algorithms can handle different
-rule sets. Please note that we still have to show taht the (data)
+rule sets. Please note that we still have to show that the (data)
 complexity holds for all possible sets of facts.
@@
 
-\textcolor{red}{Why do you write $e(v_1, v_2)$ for edges and not just
-  $(v_1, v_2)$?}
-
-\textcolor{red}{In the materialization graph for Example~5, how is
-  $A(a)$ derived from the ontology and $Q(a, b)$? }
-
 \begin{quote}
@@
 
+In the submission, we used both of the two terms `rule instance'
+and `ground instantiation of a rule', which denote the same thing.
+We now unify the term by `rule instantiation' which is introduced
+in Sec.~2.1. A rule instantiation is different from a rule.
+A rule instantiation has no variable while a rule can have variables.
+Checking the applicability of a rule depends on the size of the
+processed graph. However, checking the applicability of a rule
+instantiation only depends on the derivability of the ground atoms
+in this rule instantiation. Suppose that a processor can access the
+location of any atom in constant time. It can also check the applicability of
+a rule instantiation in constant time.
+
+In the last response, we gave another two kinds of problems, i.e.,
+the computation of transitive closure and the matrix manipulation (
+see \cite[Part~\uppercase\expandafter{\romannumeral2}~A]{Raymond95}. 
+We made a mistake to use `matrix multiplication'
+in the last response), to show that the constant time assumption
+is also applicable. The first reference in the last response gives the related works
+about this issue but not covering the details. It is also hard to find
+the clues in the second reference.
+In the following, we give a more detailed explanation.
+
 For the constant time claims, an important precondition is the
@@
 1) Suppose that there is a one-to-one correspondence between
-processors and rule instances, and each processor can access the
+processors and rule instantiations, and each processor can access the
 location of any atom in constant time (given as the parallel
-assumption in Section~3.3).  \textcolor{red}{What might be confusing
-  is the term rule instance. In Sec.~2.1, we do not introduce the
-  term, but we say `ground instantiation of a rule`, which I suppose
-  means the same thing, but maybe the reviewer reads `rule instance`
-  as `rule', which is a significant difference. If `rule instance'
-  indeed means `ground instantiation of a rule', we should unify our
-  terminology to avoid confusion. } Since a processor $p$ corresponds
-to a rule instance, e.g., $B_1, \ldots, B_n \to H$, processor $p$
+assumption in Section~3.3). Since a processor $p$ corresponds
+to a rule instantiation, e.g., $B_1, \ldots, B_n \to H$, processor $p$
 knowns the relationship among $B_1, \ldots, B_n$ and $H$. Further,
@@
 $H$. Thus, it could check the derivability of $B_1, \ldots, B_n$, and
-bridge \textcolor{red}{`to bridge' means to connect in the sense of
-  adding the edge to $G$?} $B_i$ and $H$ ($1 \leq i \leq n$) in
+add an edge from $B_i$ to $H$ ($1 \leq i \leq n$) in
 constant time instead of searching the whole graph $G$.
@@
 2) How to establish such a one-to-one correspondence between processors
-and rule instances and the constant-time access to each atom for processors?
+and rule instantiations and the constant-time access to each atom for processors?
 
@@
 In our case, the one-to-one correspondence between processors and rule
-instances and the constant-time access to each node can also be
+instantiations and the constant-time access to each node can also be
 established by PRAM similarly to the above simulation procedure.
@@
 \textcolor{red}{We have added the above argumentation also to the
-  paper. (needed?, TBD)}
+  paper. (needed?, TBD) \emph{Rephrase the relevant paragraphs in a brief way?}}
 

### 2018-06-17 parallel-tractability-J-v9/evaluation.tex
revised the constant time argumentation

@@
 platform which has limited memory space and a fixed number of processors,
-the parallel assumption given in Section~\ref{sec:alg-bsc} does not apply to ParallelDHL.
+the parallel condition given in Section~\ref{sec:alg-bsc} does not apply to ParallelDHL.
 In the implementation of ParallelDHL, we use a hash function to map any rule instantiation

### 2018-06-17 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
revised the constant time argumentation

@@
 (denoted by Algorithm~$\mathsf{A}_{\text{bsc}}$) that constructs a materialization graph for a given datalog program.
-Our computational model is a PRAM (parallel, random-access machine) that is mostly used to analyze parallel
-complexity. This model allows us to introduce \emph{the parallel assumption}:
-for any datalog program $P=\langle R, \textbf{I}\rangle$,
-any substitution of some atom and any rule instantiation in $P^*$ can be mapped to a unique memory
-location; further, a one-to-one relation can be established between processors and rule instantiations.
-Under this assumption, a processor can check the applicability of its corresponding
-rule instantiation and access the state of an atom occurring in this rule instantiation in constant time.
+The basic computational model is PRAM (parallel, random-access machine) that is mostly used to analyze parallel
+complexity. For any datalog program $P=\langle R, \textbf{I}\rangle$, the PRAM model
+allows each rule instantiation in $P^*$ corresponding to a unique processor, and each processor accessing the
+location of any atom in constant time.\footnote{This is feasible based on the PRAM model and
+the parallel prefix computation \cite{LaFi80a}. We refer the readers to the details in \cite{Raymond95}.} 
+We use \emph{the parallel condition} to denote the above condition.
+On the parallel condition, a processor can check the applicability of its corresponding
+rule instantiation and access the location of an atom occurring in this rule instantiation in constant time.
 Algorithm~$\mathsf{A}_{\text{bsc}}$ is then given as follows.\\
@@
 The computing time of \ref{alg1:addFacts} and \ref{alg1:halt} occupy constant time (denoted by $c_1$) because of parallelism.
-Since Algorithm~$\mathsf{A}_{\text{bsc}}$ works under the parallel assumption, one iteration of
-\ref{alg1:updateG} also costs constant time (denoted by $c_2$). Thus,
+Since Algorithm~$\mathsf{A}_{\text{bsc}}$ works on the parallel condition,
+each processor can check the applicability of its corresponding
+rule instantiation can then create edges between atoms in constant time. Thus,
+one iteration of \ref{alg1:updateG} costs constant time (denoted by $c_2$). In summary,
 the whole computing time of Algorithm~$\mathsf{A}_{\text{bsc}}$ turns out to be $c_1+\ell\cdot c_2$
@@
 computing $S_{\!\textit{\tiny rch}}$ and updating $\mathcal{G}$ also take constant time (denoted by $c_2$)
-under the parallel assumption. Recall that the number of constants is at most $|\textbf{I}|e$ (see Section~\ref{sec:alg-bsc}).
+on the parallel condition. Recall that the number of constants is at most $|\textbf{I}|e$ (see Section~\ref{sec:alg-bsc}).
 Let $w$ and $p$ represent the maximum arity of any predicate and the number of predicates, respectively.

### 2018-06-20 parallel-tractability-J-v9/optimizedAlgo.tex
fixed the point of \sqsubseteq_*
revision

--- 2018-02-22 parallel-tractability-J-v9/optimizedAlgo.tex
@@
 \begin{enumerate}[leftmargin=4ex,label=$\bullet$]
-\item add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\!\tiny rch}}$ where $A(a)\rightarrow B(a)\in P^*$, $\mathcal{O}\models A\sqsubseteq_* B$ and $A(a)\in V$;
+\item add \texttt{rch}$(A(a),B(a))$ to $S_{\textit{\!\tiny rch}}$
+  where $A(a)\rightarrow B(a)\in P^*$, $\mathcal{O}\models
+  A\sqsubseteq B$ and $A(a)\in V$;
 
@@
 \item add \texttt{rch}$(R(a,b)$, $S(a,b))$ to $S_{\textit{\!\tiny rch}}$ where $R(a,b)\rightarrow S(a,b)\in P^*$,
-    $\mathcal{O}\models R\sqsubseteq_* S$ and $R(a,b)\in V$;
+    $\mathcal{O}\models R\sqsubseteq S$ and $R(a,b)\in V$;
 
 \item add \texttt{rch}$(R(a,b)$, $S(b,a))$ to $S_{\textit{\!\tiny rch}}$ where $R(a,b)\rightarrow S(b,a)\in P^*$,
-    $\mathcal{O}\models R\sqsubseteq_* S^-$ and $R(a,b)\in V$;
+    $\mathcal{O}\models R\sqsubseteq S^-$ and $R(a,b)\in V$;
 
@@
 Consider performing Algorithm~$\mathsf{A}_{\text{prc}}$ on the ontology
-$\mathcal{O}_{ex_1}$ of Example~\ref{exp:mg}. Note that the individual
+$\mathcal{O}_{\text{ex}_\ref{exp:mg}}$ of Example~\ref{exp:mg}. Note that the individual
 set \textbf{IN} is $\{a_1,...,a_k,b\}$, i.e., $k+1$ individuals are involved.
@@
 all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{ex_1}$ (\ref{alg4:addFacts}). In the first iteration of
+result $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ (\ref{alg4:addFacts}). In the first iteration of
 \ref{alg4:updateG}, Algorithm~$\mathsf{A}_{\text{prc}}$ computes $S_{\textit{\!\tiny rch}}$ first.
@@
 an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\!\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{ex_1}$,
+$S_{\textit{\!\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$,
 Algorithm~$\mathsf{A}_{\text{prc}}$ checks that all atoms of the form
 $R(a_i,b)$, $2\leq i\leq k$,
-have SWD paths and are added to $\mathcal{G}_{ex_1}$ in the first iteration.
+have SWD paths and are added to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ in the first iteration.
 In the second iteration of \ref{alg4:updateG}, since all atoms of the
 form $R(a_i,b)$, $1\leq i\leq k$,
-have been in $\mathcal{G}_{ex_1}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
+have been in $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
 are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$, $1\leq i\leq k$, are finally added to $\mathcal{G}_{ex_1}$
+atoms of the form $A(a_i)$, $1\leq i\leq k$, are finally added to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$
 by Algorithm~$\mathsf{A}_{\text{prc}}$.

### 2018-06-20 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
revision

@@
 
-For some derived atom $H$, there may exist several rule instantiations where $H$
-occurs as a head atom.
-This also means that $H$ can be derived in different ways.
-The condition in the definition above results in only one way of deriving $H$ being
-described by a materialization graph.
+% For some derived atom $H$, there may exist several rule instantiations where $H$
+% occurs as a head atom.
+% This also means that $H$ can be derived in different ways.
+% The condition in the definition above results in only one way of deriving $H$ being
+% described by a materialization graph.
 % Suppose $\mathcal{G}$ is a materialization graph such that the nodes
@@
 % original facts in $\textbf{I}$.
-We next give an example of a materialization graph.\\
+We next give two examples of materialization graphs.\\
+
+\begin{example}\label{exp:matgraph}
+  Given a (DL-Lite) ontology $\mathcal{O}_{\text{ex}_\ref{exp:matgraph}}$ where the
+  TBox contains the following axioms: $A_1\sqsubseteq B$,
+  $A_2\sqsubseteq B$, $A_1\sqsubseteq A_2$; its ABox contains the
+  assertions $A_1(a)$, $A_2(a)$ and $B(b)$.  We denote the
+  corresponding datalog program of $\mathcal{O}_{\text{ex}_\ref{exp:matgraph}}$ by
+  $P_{\text{ex}_\ref{exp:matgraph}}=\langle R, \textbf{I}\rangle$, where $R$ contains
+  the rules that are transformed from the above axioms
+  ($A_1(x) \to B(x)$, $A_2(x) \to A_1(x)$, $A_1(x) \to A_2(x)$);
+  $\textbf{I}$ contains $A_1(a)$, $A_2(a)$ and $B(b)$. The two
+  complete materialization graphs of $P_{\text{ex}_\ref{exp:matgraph}}$ are
+  shown in Figure~\ref{fig:ex\theexample}.
+
+  Note that despite the rule $A_1(x) \to A_2(x)$, there is no edge
+  between the nodes $A_1(a)$ and $A_2(a)$ since $A_1(a)$ and $A_2(a)$
+  are original facts from $\textbf{I}$ and, hence, must have an
+  in-degree of $0$. Note also that having edges both from $A_1(a)$ to
+  $B(a)$ and from $A_2(a)$ to $B(a)$ is not allowed. In this case the
+  node $B(a)$ would have the two parents $A_1(a)$ and $A_2(a)$ and,
+  hence, there should be a rule
+  $A_1(a), A_2(a) \to B(a) \in P_{\text{ex}_\ref{exp:matgraph}}^*$ by the
+  definition of materialization graphs, which is not the case. When
+  dropping the node $B(a)$ and its incoming edge, we obtain an
+  incomplete materialization graph. Note, however, that all facts must
+  be contained even in an incomplete materialization graph, e.g.,
+  dropping $B(b)$ does not result in a materialization graph.
+\end{example}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\textwidth]{fig-matgraph}
+\caption{The two complete materialization graphs of $\mathcal{O}_{\text{ex}_\ref{exp:matgraph}}$}
+\label{fig:ex\theexample}
+\end{figure}
+
+The following example serves as a running example within this
+section.
 
 \begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{\text{ex}_1}$ where the TBox is
+Consider a DHL($\circ$) ontology $\mathcal{O}_{\text{ex}_\ref{exp:mg}}$ where the TBox is
 $\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
@@
 $k$ an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{\text{ex}_1}=\langle R, \textbf{I}\rangle$
+The corresponding datalog program of this ontology is $P_{\text{ex}_\ref{exp:mg}}=\langle R, \textbf{I}\rangle$
 where $\textbf{I}$ contains all the assertions in the ABox
@@
 and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{\text{ex}_1}$,
-denoted by $\mathcal{G}_{\text{ex}_1}$.
+The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{\text{ex}_\ref{exp:mg}}$,
+denoted by $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$.
 The nodes with in-degree 0 are the original facts in $\textbf{I}$;
@@
 The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{\text{ex}_1}$ is $k$.
+The depth of $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ is $k$.
 \end{example}
@@
 \begin{example}
-We consider the datalog program $P_{\text{ex}_1}$ in Example~\ref{exp:mg} again,
+We consider the datalog program $P_{\text{ex}_\ref{exp:mg}}$ in Example~\ref{exp:mg} again,
 and perform Algorithm~$\mathsf{A}_{\text{bsc}}$ on it.
 Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),\ldots,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{\text{ex}_1}$ (\ref{alg1:addFacts}).
+result $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ (\ref{alg1:addFacts}).
 Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{\text{ex}_1}$ by different processors.
-For example a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{\text{ex}_1}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{\text{ex}_1}$.
-Algorithm~$\mathsf{A}_{\text{bsc}}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{\text{ex}_1}$ (\ref{alg1:halt}).
+$\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ by different processors.
+For example, a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
+Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ after it checks that
+$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$.
+Algorithm~$\mathsf{A}_{\text{bsc}}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ (\ref{alg1:halt}).
 \end{example}
@@
 Consider Example~\ref{exp:mg} again. Let the integer $k$ be a variable. We can
-get a class of datalog programs, denoted by $\mathbb{P}_{\text{ex}_1}$, where the rule set
+get a class of datalog programs, denoted by $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$, where the rule set
 is $\{R(x,y),A(y)\rightarrow A(x), S(x,y),R(y,z)\rightarrow R(x,z)\}$ and the fact
-set varies according to $k$. The algorithm $\mathsf{A}_{\text{bsc}}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{\text{ex}_1}$.
-Let $\mathcal{G}_{\text{ex}_1}$ be some materialization graph corresponding
-to some datalog program in $\mathbb{P}_{\text{ex}_1}$. It can be checked that
-\texttt{depth}($\mathcal{G}_{\text{ex}_1}$)$=k$ for some $k$.
+set varies according to $k$.
+The algorithm $\mathsf{A}_{\text{bsc}}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$.
+Let $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ be some materialization graph corresponding
+to some datalog program in $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$. It can be checked that
+\texttt{depth}($\mathcal{G}_{\text{ex}_\ref{exp:mg}}$)$=k$ for some $k$.
 This means that the depths of the materialization graphs are linearly bounded by $k$.
-On the other hand, the sizes of the datalog programs in $\mathbb{P}_{\text{ex}_1}$ are polynomial in $k$.
+On the other hand, the sizes of the datalog programs in $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$ are polynomial in $k$.
 Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
 enough such that $\mathsf{A}_{\text{bsc}}^{\psi}$ terminates without constructing a materialization
-graph for each datalog program in $\mathbb{P}_{\text{ex}_1}$.
-However, there indeed exists an \texttt{NC} algorithm that can handle $\mathbb{P}_{\text{ex}_1}$.
+graph for each datalog program in $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$.
+However, there indeed exists an \texttt{NC} algorithm that can handle $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$.
 We discuss this in the next part.
@@
 
-In this part, we optimize Algorithm~$\mathsf{A}_{\text{bsc}}$ such that $P_{\text{ex}_1}$
+In this part, we optimize Algorithm~$\mathsf{A}_{\text{bsc}}$ such that $P_{\text{ex}_\ref{exp:mg}}$
 can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{\text{bsc}}$,
@@
 \begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{\text{opt}}$ on the datalog program $P_{\text{ex}_1}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{\text{ex}_1}$.
+We perform Algorithm~$\mathsf{A}_{\text{opt}}$ on the datalog program $P_{\text{ex}_\ref{exp:mg}}$ in Example~\ref{exp:mg}.
+Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$.
 In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
@@
 Thus, $R(a_i,b)$ and $A(a_i)$, $2\leq i\leq k$, can all be added to
-$\mathcal{G}_{\text{ex}_1}$
+$\mathcal{G}_{\text{ex}_\ref{exp:mg}}$
 in the first iteration of \ref{alg3:updateG}.

### 2018-06-20 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
revised the constant time argumentation
revision

--- 2018-06-13 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
@@
 \begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{\text{ex}_5}$
+Given a DL-Lite ontology $\mathcal{O}_{\text{ex}_\ref{exp:dllite}}$
 where the TBox and RBox contain the following axioms:
 $A\sqsubseteq B_1$, $A\sqsubseteq B_2$, $B_1\sqcap B_2\sqsubseteq\bot$,
-$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $S\sqsubseteq R$;
+$\exists R.B_2\sqsubseteq\bot$, $Q\sqsubseteq S^-$, $\exists Q.\top\sqsubseteq A$ and $S\sqsubseteq R$;
 its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_5}$ by $P_{\text{ex}_5}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_\ref{exp:dllite}}$ by $P_{\text{ex}_\ref{exp:dllite}}=\langle R, \textbf{I}\rangle$,
 where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
 as the only fact.
-The unique materialization graph of $P_{\text{ex}_5}$ is denoted by
-$\mathcal{G}_{\text{ex}_5}$ (see
-Figure~\ref{fig:ex2}). \textcolor{red}{How is $A(a)$ derived from the
-  ontology and $Q(a, b)$?}
+The unique materialization graph of $P_{\text{ex}_\ref{exp:dllite}}$ is denoted by
+$\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ (see
+Figure~\ref{fig:ex2}).
 \end{example}
@@
 \includegraphics[width=0.5\textwidth]{fig-dllite.pdf}
-\caption{The materialization graph of $\mathcal{O}_{\text{ex}_5}$}
+\caption{The materialization graph of $\mathcal{O}_{\text{ex}_\ref{exp:dllite}}$}
 \label{fig:ex2}
@@
 
-Consider performing Algorithm~$\mathsf{A}_{\text{opt}}$ on the ontology $\mathcal{O}_{\text{ex}_5}$ in Example~\ref{exp:dllite}.
+Consider performing Algorithm~$\mathsf{A}_{\text{opt}}$ on the ontology $\mathcal{O}_{\text{ex}_\ref{exp:dllite}}$ in Example~\ref{exp:dllite}.
 (\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{\text{opt}}$ adds all ABox assertions (only $Q(a,b)$ here)
-to the initially empty graph $\mathcal{G}_{\text{ex}_5}$ (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{\text{opt}}$).
+to the initially empty graph $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{\text{opt}}$).
 (\uppercase\expandafter{\romannumeral2}) In the first iteration of
@@
 starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{\text{opt}}$
-adds these nodes to $\mathcal{G}_{\text{ex}_5}$ immediately. We take an example of node $B_1(a)$,
+adds these nodes to $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ immediately. We take an example of node $B_1(a)$,
 for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{\text{ex}_5}$ by adding $B_1(a)$ to it,
+When updating $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ by adding $B_1(a)$ to it,
 Algorithm~$\mathsf{A}_{\text{opt}}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{\text{ex}_5}$; if $A(a)$ is already in $\mathcal{G}_{\text{ex}_5}$, $B_1(a)$
-is added to $\mathcal{G}_{\text{ex}_5}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{\text{ex}_5}$,
+has been in $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$; if $A(a)$ is already in $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$, $B_1(a)$
+is added to $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
+if $A(a)$ has not been added to $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$,
 Algorithm~$\mathsf{A}_{\text{opt}}$ adds $A(a)$ ($B_1(a)$, respectively)
-to $\mathcal{G}_{\text{ex}_5}$ and creates an edge pointing from
+to $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ and creates an edge pointing from
 $Q(a,b)$ to $A(a)$ (an edge pointing from $A(a)$ to $B_1(a)$, respectively).\footnote{These two cases may happen simultaneously,
@@
 (\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{\text{opt}}$ finishes constructing $\mathcal{G}_{\text{ex}_5}$
+Finally, Algorithm~$\mathsf{A}_{\text{opt}}$ finishes constructing $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$
 after two iterations (\ref{alg3:halt}).
@@
 of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{\text{ex}_5}$ of
+(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ of
 Example~\ref{exp:dllite}). On the other hand, according to the syntax of DL-Lite,
@@
 \includegraphics[width=\textwidth]{fig-pathtwist.pdf}
-\caption{The materialization graph of $\mathcal{O}_{\text{ex}_6}$
-  (left) and of $\mathcal{O}_{\text{ex}_7}$ (right)}
+\caption{The materialization graph of $\mathcal{O}_{\text{ex}_\ref{exp:dhl}}$
+  (left) and of $\mathcal{O}_{\text{ex}_\ref{exp:simpleC}}$ (right)}
 \label{fig:ex3_4}
@@
 \begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{\text{ex}_6}$ where the TBox contains three axioms:
+Given a DHL ontology $\mathcal{O}_{\text{ex}_\ref{exp:dhl}}$ where the TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
@@
 for $2\leq i\leq k$ and $k$ an integer greater than $2$.
-We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_6}$ by $P_{\text{ex}_6}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_\ref{exp:dhl}}$ by $P_{\text{ex}_\ref{exp:dhl}}=\langle R, \textbf{I}\rangle$,
 where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{\text{ex}_6}$ constructed by
-$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_6}$
+The materialization graph of $P_{\text{ex}_\ref{exp:dhl}}$ constructed by
+$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$
 (see Figure~\ref{fig:ex3_4}~(left)).
@@
 
-One can check that $\mathcal{G}_{\text{ex}_6}$ is the unique materialization graph of $P_{\text{ex}_6}$.
+One can check that $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$ is the unique materialization graph of $P_{\text{ex}_\ref{exp:dhl}}$.
 Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),\ldots,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{\text{opt}}$ on $P_{\text{ex}_6}$, it can be checked that
+When performing Algorithm~$\mathsf{A}_{\text{opt}}$ on $P_{\text{ex}_\ref{exp:dhl}}$, it can be checked that
 each node of the form $A(a_i)$ (filled with black color,
 and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{\text{ex}_6}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{\text{ex}_6}$.
-Similar to the datalog program class $\mathbb{P}_{\text{ex}_1}$, we can also get a
-datalog program class $\mathbb{P}_{\text{ex}_6}$ for the ontology $\mathcal{O}_{\text{ex}_6}$
+in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$,
+and, $A(a_i)$ can also be added to $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$.
+Similar to the datalog program class $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$, we can also get a
+datalog program class $\mathbb{P}_{\text{ex}_\ref{exp:dhl}}$ for the ontology $\mathcal{O}_{\text{ex}_\ref{exp:dhl}}$
 when $k$ is a variable. Based on the above analysis, Algorithm~$\mathsf{A}_{\text{opt}}$ cannot complete the materialization
-for the datalog programs of $\mathbb{P}_{\text{ex}_6}$ in a poly-logarithmic
+for the datalog programs of $\mathbb{P}_{\text{ex}_\ref{exp:dhl}}$ in a poly-logarithmic
 number of iterations.
@@
 That is, for each node $A(a_i)$, $2\leq i\leq k$, until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{\text{ex}_6}$, there would not exist an available SWD path for $A(a_i)$.
+to $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$, there would not exist an available SWD path for $A(a_i)$.
 We use the term `\emph{path twisting}' to refer to such cases.
@@
 \begin{example}\label{exp:simpleC}
-Consider an ontology $\mathcal{O}_{\text{ex}_7}$ where the TBox contains three axioms:
+Consider an ontology $\mathcal{O}_{\text{ex}_\ref{exp:simpleC}}$ where the TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
@@
 for $2\leq i\leq k$ and $k$ an integer greater than $2$.
-We denote the corresponding datalog program by $P_{\text{ex}_7}$ where the rule set contains:
+We denote the corresponding datalog program by $P_{\text{ex}_\ref{exp:simpleC}}$ where the rule set contains:
 `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{\text{ex}_7}$ has a unique materialization graph denoted by $\mathcal{G}_{\text{ex}_7}$ (see Figure~\ref{fig:ex3_4}~(right)).
+$P_{\text{ex}_\ref{exp:simpleC}}$ has a unique materialization graph denoted by $\mathcal{G}_{\text{ex}_\ref{exp:simpleC}}$ (see Figure~\ref{fig:ex3_4}~(right)).
 \end{example}
@@
 This ensures that only one path exists between each two nodes among $A(a_2),\ldots,A(a_k)$.
-Further, when constructing $\mathcal{G}_{\text{ex}_7}$, Algorithm~$\mathsf{A}_{\text{opt}}$ can terminate after
+Further, when constructing $\mathcal{G}_{\text{ex}_\ref{exp:simpleC}}$, Algorithm~$\mathsf{A}_{\text{opt}}$ can terminate after
 two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{\text{opt}}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$, $2\leq i\leq k$, to $\mathcal{G}_{\text{ex}_7}$
+adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$, $2\leq i\leq k$, to $\mathcal{G}_{\text{ex}_\ref{exp:simpleC}}$
 since they have corresponding SWD paths;
 after that, all other nodes
-can be added to $\mathcal{G}_{\text{ex}_7}$ in the second iteration (because each
+can be added to $\mathcal{G}_{\text{ex}_\ref{exp:simpleC}}$ in the second iteration (because each
 node has an SWD path).
@@
 \begin{example}\label{exp:complexRIA}
-Given a DHL$(\circ)$ ontology $\mathcal{O}_{\text{ex}_9}$ where the TBox is empty;
+Given a DHL$(\circ)$ ontology $\mathcal{O}_{\text{ex}_{\ref{exp:complexRIA}}}$ where the TBox is empty;
 the RBox $\mathcal{R}$ contains three axioms:
@@
 for $2\leq i\leq k$ and $k$ an integer greater than $2$.
-The corresponding datalog program $P_{\text{ex}_9}$
+The corresponding datalog program $P_{\text{ex}_{\ref{exp:complexRIA}}}$
 contains three rules: `$R_1(x,y),R_2(y,z)\rightarrow R(x,z)$',
 `$R_3(x,y),R(y,z)\rightarrow R_1(x,z)$' and `$R(x,y),R_4(y,z)\rightarrow R_2(x,z)$'.
-The materialization graph of $P_{\text{ex}_9}$ constructed by Algorithm~$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_9}$.
+The materialization graph of $P_{\text{ex}_{\ref{exp:complexRIA}}}$ constructed by Algorithm~$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_{\ref{exp:complexRIA}}}$.
 \end{example}
 
-One can check that the materialization graph $\mathcal{G}_{\text{ex}_9}$ has the same shape as that
-of $\mathcal{G}_{\text{ex}_6}$ in Figure~\ref{fig:ex3_4}.
-A twisted path exists in $\mathcal{G}_{\text{ex}_9}$ involving
+One can check that the materialization graph $\mathcal{G}_{\text{ex}_{\ref{exp:complexRIA}}}$ has the same shape as that
+of $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$ in Figure~\ref{fig:ex3_4}.
+A twisted path exists in $\mathcal{G}_{\text{ex}_{\ref{exp:complexRIA}}}$ involving
 $R(a_i,a_i)$, $2\leq i\leq k$, as the joint nodes.
@@
 \begin{example}
-For the ontology $\mathcal{O}_{\text{ex}_9}$ in Example~\ref{exp:complexRIA}, all of the roles
-$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{\text{ex}_9}$ does not follow
+For the ontology $\mathcal{O}_{\text{ex}_{\ref{exp:complexRIA}}}$ in Example~\ref{exp:complexRIA}, all of the roles
+$R_1$, $R_2$ and $R$ are non-simple roles. Thus, $\mathcal{O}_{\text{ex}_{\ref{exp:complexRIA}}}$ does not follow
 the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{\text{ex}_1}$
+Consider the ontology $\mathcal{O}_{\text{ex}_\ref{exp:mg}}$
 in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus, $\mathcal{O}_{\text{ex}_1}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{\text{ex}_1}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{\text{ex}_1}$ by Algorithm~$\mathsf{A}_{\text{opt}}$.
+Thus, $\mathcal{O}_{\text{ex}_\ref{exp:mg}}$ follows the simple-role restriction. All the implicit nodes
+in $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ have corresponding SWD paths in the first iteration.
+Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{\text{ex}_\ref{exp:mg}}$ by Algorithm~$\mathsf{A}_{\text{opt}}$.
 \end{example}

### 2018-06-20 parallel-tractability-J-v9/response2.tex
revision

@@
 Hence, while the algorithms (e.g.\ Algorithm $\mathsf{A}_\text{bsc}$
-or (or $\mathsf{A}_\text{opt}$) involve two inputs (rules and facts),
+(or $\mathsf{A}_\text{opt}$) involve two inputs (rules and facts),
 for the complexity analysis, we assume the rules part of the input to
@@
 
+We have further added a simple example (now Example~1) to illustrate
+the different aspects of the definition.
+
 \begin{quote}
@@
 
-In the submission, we used both of the two terms `rule instance'
-and `ground instantiation of a rule', which denote the same thing.
-We now unify the term by `rule instantiation' which is introduced
+One issue might have been our use of the two terms `rule instance'
+and `ground instantiation of a rule', which denote the same thing (but
+this was maybe not clear in the paper).
+We now unify the terms and only use `rule instantiation', which is introduced
 in Sec.~2.1. A rule instantiation is different from a rule.
@@
 location of any atom in constant time. It can also check the applicability of
-a rule instantiation in constant time.
+a rule \emph{instantiation} in constant time.
 
-In the last response, we gave another two kinds of problems, i.e.,
-the computation of transitive closure and the matrix manipulation (
-see \cite[Part~\uppercase\expandafter{\romannumeral2}~A]{Raymond95}. 
-We made a mistake to use `matrix multiplication'
-in the last response), to show that the constant time assumption
-is also applicable. The first reference in the last response gives the related works
-about this issue but not covering the details. It is also hard to find
-the clues in the second reference.
-In the following, we give a more detailed explanation.
+The two references given in the previous response were pointing to two
+other kinds of problems, i.e., the computation of the transitive
+closure and matrix manipulation (see
+\cite[Part~\uppercase\expandafter{\romannumeral2}~A]{Raymond95}, to
+show that the constant time assumption is also
+applicable. Unfortunately, we referred to `matrix manipulation' as
+`matrix multiplication' in the previous response by accident. The
+first reference in the previous response gives related works about
+this issue without covering the details. The second reference is
+indeed too brief to go much beyond the problem description. In the
+following, we give a more detailed explanation.
 
@@
 processors and rule instantiations, and each processor can access the
-location of any atom in constant time (given as the parallel
-assumption in Section~3.3). Since a processor $p$ corresponds
-to a rule instantiation, e.g., $B_1, \ldots, B_n \to H$, processor $p$
-knowns the relationship among $B_1, \ldots, B_n$ and $H$. Further,
-processor $p$ knows the locations of the nodes $B_1, \ldots, B_n$ and
-$H$. Thus, it could check the derivability of $B_1, \ldots, B_n$, and
-add an edge from $B_i$ to $H$ ($1 \leq i \leq n$) in
-constant time instead of searching the whole graph $G$.
+location of any atom \textcolor{red}{within a rule? atom here means
+  derived facts?} in constant time
+(given as the parallel assumption in Section~3.3). Since a processor
+$p$ corresponds to a rule instantiation, e.g.,
+$B_1, \ldots, B_n \to H$, processor $p$ knowns the relationship among
+$B_1, \ldots, B_n$ and $H$. Further, processor $p$ knows the locations
+of the nodes $B_1, \ldots, B_n$ and $H$ \textcolor{red}{within the
+  materialization graph? how?  by checking (in constant time) the
+  derived facts?}. Thus, it could check the
+derivability of $B_1, \ldots, B_n$ \textcolor{red}{Check the
+  derivability or whether the (ground) atoms have been derived?}, and add an edge from $B_i$ to $H$
+($1 \leq i \leq n$) in constant time instead of searching the whole
+graph $G$.
 
@@
 
-We should also introduce the notion of Boolean circuit, which is a
-circuit that consists of logic gates, e.g., AND and OR gates (see
+We should also introduce the notion of Boolean circuits, which are 
+circuits that consist of logic gates, e.g., AND and OR gates (see
 \cite[Section~2.3]{Raymond95}).  A materialization graph can also be
@@
 \textcolor{red}{The argumentation for this claim is similar to the one
-  given above. (?)}
+  given above. (?) Is it? Can we simply reply like that?}
 

### 2018-06-24 parallel-tractability-J-v9/optimizedAlgo.tex
revision of the constant time claims

@@
 Consider performing Algorithm~$\mathsf{A}_{\text{prc}}$ on the ontology
-$\mathcal{O}_{\text{ex}_\ref{exp:mg}}$ of Example~\ref{exp:mg}. Note that the individual
+$\mathcal{O}_{\text{ex}_{\ref{exp:mg}}}$ of Example~\ref{exp:mg}. Note that the individual
 set \textbf{IN} is $\{a_1,...,a_k,b\}$, i.e., $k+1$ individuals are involved.
@@
 all the facts ($A(b),R(a_1,b),S(a_2,a_1),...,S(a_{k},a_{k-1})$) to the
-result $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ (\ref{alg4:addFacts}). In the first iteration of
+result $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$ (\ref{alg4:addFacts}). In the first iteration of
 \ref{alg4:updateG}, Algorithm~$\mathsf{A}_{\text{prc}}$ computes $S_{\textit{\!\tiny rch}}$ first.
@@
 an $\texttt{\emph{rch}}$ relation of the form $\texttt{\emph{rch}}(R(a_{i-1},o),R(a_i,o))$ is added to
-$S_{\textit{\!\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$,
+$S_{\textit{\!\tiny rch}}$. Since the atom $R(a_1,b)$ has been added to $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$,
 Algorithm~$\mathsf{A}_{\text{prc}}$ checks that all atoms of the form
 $R(a_i,b)$, $2\leq i\leq k$,
-have SWD paths and are added to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ in the first iteration.
+have SWD paths and are added to $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$ in the first iteration.
 In the second iteration of \ref{alg4:updateG}, since all atoms of the
 form $R(a_i,b)$, $1\leq i\leq k$,
-have been in $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
+have been in $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$, the $\texttt{\emph{rch}}$ relations of the form $\texttt{\emph{rch}}(A(b),A(a_i))$
 are checked with respect to the axiom $\exists R.A\sqsubseteq A$; further all
-atoms of the form $A(a_i)$, $1\leq i\leq k$, are finally added to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$
+atoms of the form $A(a_i)$, $1\leq i\leq k$, are finally added to $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$
 by Algorithm~$\mathsf{A}_{\text{prc}}$.

### 2018-06-24 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
revision of the constant time claims

@@
 \begin{example}\label{exp:matgraph}
-  Given a (DL-Lite) ontology $\mathcal{O}_{\text{ex}_\ref{exp:matgraph}}$ where the
+  Given a (DL-Lite) ontology $\mathcal{O}_{\text{ex}_{\ref{exp:matgraph}}}$ where the
   TBox contains the following axioms: $A_1\sqsubseteq B$,
@@
   assertions $A_1(a)$, $A_2(a)$ and $B(b)$.  We denote the
-  corresponding datalog program of $\mathcal{O}_{\text{ex}_\ref{exp:matgraph}}$ by
-  $P_{\text{ex}_\ref{exp:matgraph}}=\langle R, \textbf{I}\rangle$, where $R$ contains
+  corresponding datalog program of $\mathcal{O}_{\text{ex}_{\ref{exp:matgraph}}}$ by
+  $P_{\text{ex}_{\ref{exp:matgraph}}}=\langle R, \textbf{I}\rangle$, where $R$ contains
   the rules that are transformed from the above axioms
@@
   $\textbf{I}$ contains $A_1(a)$, $A_2(a)$ and $B(b)$. The two
-  complete materialization graphs of $P_{\text{ex}_\ref{exp:matgraph}}$ are
+  complete materialization graphs of $P_{\text{ex}_{\ref{exp:matgraph}}}$ are
   shown in Figure~\ref{fig:ex\theexample}.
@@
   hence, there should be a rule
-  $A_1(a), A_2(a) \to B(a) \in P_{\text{ex}_\ref{exp:matgraph}}^*$ by the
+  $A_1(a), A_2(a) \to B(a) \in P_{\text{ex}_{\ref{exp:matgraph}}}^*$ by the
   definition of materialization graphs, which is not the case. When
@@
 \includegraphics[width=\textwidth]{fig-matgraph}
-\caption{The two complete materialization graphs of $\mathcal{O}_{\text{ex}_\ref{exp:matgraph}}$}
+\caption{The two complete materialization graphs of $\mathcal{O}_{\text{ex}_{\ref{exp:matgraph}}}$}
 \label{fig:ex\theexample}
@@
 \begin{example}\label{exp:mg}
-Consider a DHL($\circ$) ontology $\mathcal{O}_{\text{ex}_\ref{exp:mg}}$ where the TBox is
+Consider a DHL($\circ$) ontology $\mathcal{O}_{\text{ex}_{\ref{exp:mg}}}$ where the TBox is
 $\{\exists R.A\sqsubseteq A\}$, the RBox is $\{S\circ R\sqsubseteq R\}$ and
@@
 $k$ an integer greater than $2$.
-The corresponding datalog program of this ontology is $P_{\text{ex}_\ref{exp:mg}}=\langle R, \textbf{I}\rangle$
+The corresponding datalog program of this ontology is $P_{\text{ex}_{\ref{exp:mg}}}=\langle R, \textbf{I}\rangle$
 where $\textbf{I}$ contains all the assertions in the ABox
@@
 and `$S(x,y),R(y,z)\rightarrow R(x,z)$'.
-The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{\text{ex}_\ref{exp:mg}}$,
-denoted by $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$.
+The graph in Figure~\ref{fig:mg} is a materialization graph with respect to $P_{\text{ex}_{\ref{exp:mg}}}$,
+denoted by $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$.
 The nodes with in-degree 0 are the original facts in $\textbf{I}$;
@@
 The size of this materialization graph is the number of nodes, that is $3k$.
-The depth of $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ is $k$.
+The depth of $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$ is $k$.
 \end{example}
@@
 allows each rule instantiation in $P^*$ corresponding to a unique processor, and each processor accessing the
-location of any atom in constant time.\footnote{This is feasible based on the PRAM model and
+locations of the atoms in the corresponding rule instantiation in constant time.\footnote{This is feasible based on the PRAM model and
 the parallel prefix computation \cite{LaFi80a}. We refer the readers to the details in \cite{Raymond95}.}
@@
 \begin{example}
-We consider the datalog program $P_{\text{ex}_\ref{exp:mg}}$ in Example~\ref{exp:mg} again,
+We consider the datalog program $P_{\text{ex}_{\ref{exp:mg}}}$ in Example~\ref{exp:mg} again,
 and perform Algorithm~$\mathsf{A}_{\text{bsc}}$ on it.
 Initially, all the facts ($A(b),R(a_1,b),S(a_2,a_1),\ldots,S(a_{k},a_{k-1})$) are added to the
-result $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ (\ref{alg1:addFacts}).
+result $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$ (\ref{alg1:addFacts}).
 Then in different iterations of \ref{alg1:updateG}, the remaining nodes are added to
-$\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ by different processors.
+$\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$ by different processors.
 For example, a processor $p$ is allocated a rule instantiation `$R(a_2,b),A(b)\rightarrow A(a_2)$'.
-Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ after it checks that
-$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$.
-Algorithm~$\mathsf{A}_{\text{bsc}}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ (\ref{alg1:halt}).
+Then, processor $p$ adds $A(a_2)$ to $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$ after it checks that
+$A(b)$ and $R(a_2,b)$ are in $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$.
+Algorithm~$\mathsf{A}_{\text{bsc}}$ halts when $A(a_k)$ has been added to $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$ (\ref{alg1:halt}).
 \end{example}
@@
 each processor can check the applicability of its corresponding
-rule instantiation can then create edges between atoms in constant time. Thus,
+rule instantiation and then create edges between atoms in constant time. Thus,
 one iteration of \ref{alg1:updateG} costs constant time (denoted by $c_2$). In summary,
@@
 Consider Example~\ref{exp:mg} again. Let the integer $k$ be a variable. We can
-get a class of datalog programs, denoted by $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$, where the rule set
+get a class of datalog programs, denoted by $\mathbb{P}_{\text{ex}_{\ref{exp:mg}}}$, where the rule set
 is $\{R(x,y),A(y)\rightarrow A(x), S(x,y),R(y,z)\rightarrow R(x,z)\}$ and the fact
 set varies according to $k$.
-The algorithm $\mathsf{A}_{\text{bsc}}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$.
-Let $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ be some materialization graph corresponding
-to some datalog program in $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$. It can be checked that
-\texttt{depth}($\mathcal{G}_{\text{ex}_\ref{exp:mg}}$)$=k$ for some $k$.
+The algorithm $\mathsf{A}_{\text{bsc}}^{\psi}$ is restricted in the sense that it cannot even work on the rather simple datalog program class $\mathbb{P}_{\text{ex}_{\ref{exp:mg}}}$.
+Let $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$ be some materialization graph corresponding
+to some datalog program in $\mathbb{P}_{\text{ex}_{\ref{exp:mg}}}$. It can be checked that
+\texttt{depth}($\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$)$=k$ for some $k$.
 This means that the depths of the materialization graphs are linearly bounded by $k$.
-On the other hand, the sizes of the datalog programs in $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$ are polynomial in $k$.
+On the other hand, the sizes of the datalog programs in $\mathbb{P}_{\text{ex}_{\ref{exp:mg}}}$ are polynomial in $k$.
 Thus, for any $\psi$ that is poly-logarithmically bounded, we can always find a $k$ large
 enough such that $\mathsf{A}_{\text{bsc}}^{\psi}$ terminates without constructing a materialization
-graph for each datalog program in $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$.
-However, there indeed exists an \texttt{NC} algorithm that can handle $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$.
+graph for each datalog program in $\mathbb{P}_{\text{ex}_{\ref{exp:mg}}}$.
+However, there indeed exists an \texttt{NC} algorithm that can handle $\mathbb{P}_{\text{ex}_{\ref{exp:mg}}}$.
 We discuss this in the next part.
@@
 
-In this part, we optimize Algorithm~$\mathsf{A}_{\text{bsc}}$ such that $P_{\text{ex}_\ref{exp:mg}}$
+In this part, we optimize Algorithm~$\mathsf{A}_{\text{bsc}}$ such that $P_{\text{ex}_{\ref{exp:mg}}}$
 can be handled. Based on the optimized variant of Algorithm~$\mathsf{A}_{\text{bsc}}$,
@@
 \begin{example}\label{exp:opt}
-We perform Algorithm~$\mathsf{A}_{\text{opt}}$ on the datalog program $P_{\text{ex}_\ref{exp:mg}}$ in Example~\ref{exp:mg}.
-Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$.
+We perform Algorithm~$\mathsf{A}_{\text{opt}}$ on the datalog program $P_{\text{ex}_{\ref{exp:mg}}}$ in Example~\ref{exp:mg}.
+Initially, $R(a_1,b)$ is in the materialization graph $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$.
 In the first iteration of \ref{alg3:updateG}, all the rule instantiations are in two kinds of forms:
@@
 Thus, $R(a_i,b)$ and $A(a_i)$, $2\leq i\leq k$, can all be added to
-$\mathcal{G}_{\text{ex}_\ref{exp:mg}}$
+$\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$
 in the first iteration of \ref{alg3:updateG}.
@@
 is obvious that \ref{alg3:addFacts} and
-\ref{alg3:halt} occupy constant time (denoted by $c_1$). In \ref{alg3:updateG}, the phases of
-computing $S_{\!\textit{\tiny rch}}$ and updating $\mathcal{G}$ also take constant time (denoted by $c_2$)
-on the parallel condition. Recall that the number of constants is at most $|\textbf{I}|e$ (see Section~\ref{sec:alg-bsc}).
+\ref{alg3:halt} occupy constant time (denoted by $c_1$).
+Algorithm~$\mathsf{A}_{\text{opt}}$ also works on the parallel condition.
+That is each processor $q$ corresponds to a rule instantiation, e.g., $B_1,\ldots,B_n\rightarrow H$,
+and processor $q$ can access the locations of nodes $B_1,\ldots,B_n, H$ in constant time.
+In order to compute $S_{\!\textit{\tiny rch}}$, processor $q$ should check the derivability
+of nodes $B_1,\ldots,B_n, H$. If only node $B_i$ ($i\in\{1,\ldots n\}$) and node $H$
+are still not derived, then processor $q$ creates a pair $(B_i, H)$ in $S_{\!\textit{\tiny rch}}$.
+The other elements in $S_{\!\textit{\tiny rch}}$ are similarly computed.
+It is obvious that the above procedure occupies constant time as well on the parallel condition.
+Thus, in \ref{alg3:updateG}, the phases of
+computing $S_{\!\textit{\tiny rch}}$ and updating $\mathcal{G}$ also take constant time (denoted by $c_2$).
+Recall that the number of constants is at most $|\textbf{I}|e$ (see Section~\ref{sec:alg-bsc}).
 Let $w$ and $p$ represent the maximum arity of any predicate and the number of predicates, respectively.

### 2018-06-24 parallel-tractability-J-v9/parallelTractabilityOntMat.tex
revision of the constant time claims

@@
 \begin{example}\label{exp:dllite}
-Given a DL-Lite ontology $\mathcal{O}_{\text{ex}_\ref{exp:dllite}}$
+Given a DL-Lite ontology $\mathcal{O}_{\text{ex}_{\ref{exp:dllite}}}$
 where the TBox and RBox contain the following axioms:
@@
 its ABox contains an assertion $Q(a,b)$.
-We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_\ref{exp:dllite}}$ by $P_{\text{ex}_\ref{exp:dllite}}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_{\ref{exp:dllite}}}$ by $P_{\text{ex}_{\ref{exp:dllite}}}=\langle R, \textbf{I}\rangle$,
 where $R$ contains the rules that are transformed from the above axioms; $\textbf{I}$ contains $Q(a,b)$
 as the only fact.
-The unique materialization graph of $P_{\text{ex}_\ref{exp:dllite}}$ is denoted by
-$\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ (see
+The unique materialization graph of $P_{\text{ex}_{\ref{exp:dllite}}}$ is denoted by
+$\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$ (see
 Figure~\ref{fig:ex2}).
@@
 \includegraphics[width=0.5\textwidth]{fig-dllite.pdf}
-\caption{The materialization graph of $\mathcal{O}_{\text{ex}_\ref{exp:dllite}}$}
+\caption{The materialization graph of $\mathcal{O}_{\text{ex}_{\ref{exp:dllite}}}$}
 \label{fig:ex2}
@@
 
-Consider performing Algorithm~$\mathsf{A}_{\text{opt}}$ on the ontology $\mathcal{O}_{\text{ex}_\ref{exp:dllite}}$ in Example~\ref{exp:dllite}.
+Consider performing Algorithm~$\mathsf{A}_{\text{opt}}$ on the ontology $\mathcal{O}_{\text{ex}_{\ref{exp:dllite}}}$ in Example~\ref{exp:dllite}.
 (\uppercase\expandafter{\romannumeral1}) First, Algorithm~$\mathsf{A}_{\text{opt}}$ adds all ABox assertions (only $Q(a,b)$ here)
-to the initially empty graph $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{\text{opt}}$).
+to the initially empty graph $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$ (\ref{alg3:addFacts} of Algorithm~$\mathsf{A}_{\text{opt}}$).
 (\uppercase\expandafter{\romannumeral2}) In the first iteration of
@@
 starting from $Q(a,b)$. Thus, Algorithm~$\mathsf{A}_{\text{opt}}$
-adds these nodes to $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ immediately. We take an example of node $B_1(a)$,
+adds these nodes to $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$ immediately. We take an example of node $B_1(a)$,
 for which an SWD path $(Q(a,b),A(a),B_1(a))$ exists.
-When updating $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ by adding $B_1(a)$ to it,
+When updating $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$ by adding $B_1(a)$ to it,
 Algorithm~$\mathsf{A}_{\text{opt}}$ first checks whether the parent node $A(a)$ of $B_1(a)$
-has been in $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$; if $A(a)$ is already in $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$, $B_1(a)$
-is added to $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
-if $A(a)$ has not been added to $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$,
+has been in $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$; if $A(a)$ is already in $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$, $B_1(a)$
+is added to $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$ by creating an edge pointing from $A(a)$ to $B_1(a)$;
+if $A(a)$ has not been added to $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$,
 Algorithm~$\mathsf{A}_{\text{opt}}$ adds $A(a)$ ($B_1(a)$, respectively)
-to $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ and creates an edge pointing from
+to $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$ and creates an edge pointing from
 $Q(a,b)$ to $A(a)$ (an edge pointing from $A(a)$ to $B_1(a)$, respectively).\footnote{These two cases may happen simultaneously,
@@
 (\uppercase\expandafter{\romannumeral4})
-Finally, Algorithm~$\mathsf{A}_{\text{opt}}$ finishes constructing $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$
+Finally, Algorithm~$\mathsf{A}_{\text{opt}}$ finishes constructing $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$
 after two iterations (\ref{alg3:halt}).
@@
 of \ref{alg3:updateG}, since its derivability depends on its two parent nodes
-(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{\text{ex}_\ref{exp:dllite}}$ of
+(see nodes $\bot(a)$ and $\bot(b)$ in $\mathcal{G}_{\text{ex}_{\ref{exp:dllite}}}$ of
 Example~\ref{exp:dllite}). On the other hand, according to the syntax of DL-Lite,
@@
 \includegraphics[width=\textwidth]{fig-pathtwist.pdf}
-\caption{The materialization graph of $\mathcal{O}_{\text{ex}_\ref{exp:dhl}}$
-  (left) and of $\mathcal{O}_{\text{ex}_\ref{exp:simpleC}}$ (right)}
+\caption{The materialization graph of $\mathcal{O}_{\text{ex}_{\ref{exp:dhl}}}$
+  (left) and of $\mathcal{O}_{\text{ex}_{\ref{exp:simpleC}}}$ (right)}
 \label{fig:ex3_4}
@@
 \begin{example}\label{exp:dhl}
-Given a DHL ontology $\mathcal{O}_{\text{ex}_\ref{exp:dhl}}$ where the TBox contains three axioms:
+Given a DHL ontology $\mathcal{O}_{\text{ex}_{\ref{exp:dhl}}}$ where the TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $\exists R.A\sqsubseteq B_2$;
@@
 for $2\leq i\leq k$ and $k$ an integer greater than $2$.
-We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_\ref{exp:dhl}}$ by $P_{\text{ex}_\ref{exp:dhl}}=\langle R, \textbf{I}\rangle$,
+We denote the corresponding datalog program of $\mathcal{O}_{\text{ex}_{\ref{exp:dhl}}}$ by $P_{\text{ex}_{\ref{exp:dhl}}}=\langle R, \textbf{I}\rangle$,
 where $R$ contains three rules: `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$R(x,y),A(y)\rightarrow B_2(x)$'.
-The materialization graph of $P_{\text{ex}_\ref{exp:dhl}}$ constructed by
-$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$
+The materialization graph of $P_{\text{ex}_{\ref{exp:dhl}}}$ constructed by
+$\mathsf{A}_{\text{opt}}$ is denoted by $\mathcal{G}_{\text{ex}_{\ref{exp:dhl}}}$
 (see Figure~\ref{fig:ex3_4}~(left)).
@@
 
-One can check that $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$ is the unique materialization graph of $P_{\text{ex}_\ref{exp:dhl}}$.
+One can check that $\mathcal{G}_{\text{ex}_{\ref{exp:dhl}}}$ is the unique materialization graph of $P_{\text{ex}_{\ref{exp:dhl}}}$.
 Observe that there exists a path (e.g., $A(a_1),B_1(a_2),A(a_2),\ldots,A(a_k)$) between $A(a_1)$ and $A(a_k)$.
-When performing Algorithm~$\mathsf{A}_{\text{opt}}$ on $P_{\text{ex}_\ref{exp:dhl}}$, it can be checked that
+When performing Algorithm~$\mathsf{A}_{\text{opt}}$ on $P_{\text{ex}_{\ref{exp:dhl}}}$, it can be checked that
 each node of the form $A(a_i)$ (filled with black color,
 and $2\leq i\leq k$) has no SWD path until the $i^{th}$ iteration;
-in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$,
-and, $A(a_i)$ can also be added to $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$.
-Similar to the datalog program class $\mathbb{P}_{\text{ex}_\ref{exp:mg}}$, we can also get a
-datalog program class $\mathbb{P}_{\text{ex}_\ref{exp:dhl}}$ for the ontology $\mathcal{O}_{\text{ex}_\ref{exp:dhl}}$
+in the $i^{th}$ iteration, the parent nodes of $A(a_i)$ have been added to $\mathcal{G}_{\text{ex}_{\ref{exp:dhl}}}$,
+and, $A(a_i)$ can also be added to $\mathcal{G}_{\text{ex}_{\ref{exp:dhl}}}$.
+Similar to the datalog program class $\mathbb{P}_{\text{ex}_{\ref{exp:mg}}}$, we can also get a
+datalog program class $\mathbb{P}_{\text{ex}_{\ref{exp:dhl}}}$ for the ontology $\mathcal{O}_{\text{ex}_{\ref{exp:dhl}}}$
 when $k$ is a variable. Based on the above analysis, Algorithm~$\mathsf{A}_{\text{opt}}$ cannot complete the materialization
-for the datalog programs of $\mathbb{P}_{\text{ex}_\ref{exp:dhl}}$ in a poly-logarithmic
+for the datalog programs of $\mathbb{P}_{\text{ex}_{\ref{exp:dhl}}}$ in a poly-logarithmic
 number of iterations.
@@
 That is, for each node $A(a_i)$, $2\leq i\leq k$, until its parents ($B_1(a_i)$ and $B_2(a_i)$) are added
-to $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$, there would not exist an available SWD path for $A(a_i)$.
+to $\mathcal{G}_{\text{ex}_{\ref{exp:dhl}}}$, there would not exist an available SWD path for $A(a_i)$.
 We use the term `\emph{path twisting}' to refer to such cases.
@@
 \begin{example}\label{exp:simpleC}
-Consider an ontology $\mathcal{O}_{\text{ex}_\ref{exp:simpleC}}$ where the TBox contains three axioms:
+Consider an ontology $\mathcal{O}_{\text{ex}_{\ref{exp:simpleC}}}$ where the TBox contains three axioms:
 $B_1\sqcap B_2\sqsubseteq A$, $\exists S.A\sqsubseteq B_1$ and $B_3\sqsubseteq B_2$;
@@
 for $2\leq i\leq k$ and $k$ an integer greater than $2$.
-We denote the corresponding datalog program by $P_{\text{ex}_\ref{exp:simpleC}}$ where the rule set contains:
+We denote the corresponding datalog program by $P_{\text{ex}_{\ref{exp:simpleC}}}$ where the rule set contains:
 `$B_1(x),B_2(x)\rightarrow A(x)$',`$S(x,y),A(y)\rightarrow B_1(x)$' and `$B_3(x)\rightarrow B_2(x)$'.
-$P_{\text{ex}_\ref{exp:simpleC}}$ has a unique materialization graph denoted by $\mathcal{G}_{\text{ex}_\ref{exp:simpleC}}$ (see Figure~\ref{fig:ex3_4}~(right)).
+$P_{\text{ex}_{\ref{exp:simpleC}}}$ has a unique materialization graph denoted by $\mathcal{G}_{\text{ex}_{\ref{exp:simpleC}}}$ (see Figure~\ref{fig:ex3_4}~(right)).
 \end{example}
@@
 This ensures that only one path exists between each two nodes among $A(a_2),\ldots,A(a_k)$.
-Further, when constructing $\mathcal{G}_{\text{ex}_\ref{exp:simpleC}}$, Algorithm~$\mathsf{A}_{\text{opt}}$ can terminate after
+Further, when constructing $\mathcal{G}_{\text{ex}_{\ref{exp:simpleC}}}$, Algorithm~$\mathsf{A}_{\text{opt}}$ can terminate after
 two iterations of \ref{alg3:updateG}. Specifically, in the first iteration, Algorithm~$\mathsf{A}_{\text{opt}}$
-adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$, $2\leq i\leq k$, to $\mathcal{G}_{\text{ex}_\ref{exp:simpleC}}$
+adds all of the nodes $B_3(a_i)$ and $B_2(a_i)$, $2\leq i\leq k$, to $\mathcal{G}_{\text{ex}_{\ref{exp:simpleC}}}$
 since they have corresponding SWD paths;
 after that, all other nodes
-can be added to $\mathcal{G}_{\text{ex}_\ref{exp:simpleC}}$ in the second iteration (because each
+can be added to $\mathcal{G}_{\text{ex}_{\ref{exp:simpleC}}}$ in the second iteration (because each
 node has an SWD path).
@@
 One can check that the materialization graph $\mathcal{G}_{\text{ex}_{\ref{exp:complexRIA}}}$ has the same shape as that
-of $\mathcal{G}_{\text{ex}_\ref{exp:dhl}}$ in Figure~\ref{fig:ex3_4}.
+of $\mathcal{G}_{\text{ex}_{\ref{exp:dhl}}}$ in Figure~\ref{fig:ex3_4}.
 A twisted path exists in $\mathcal{G}_{\text{ex}_{\ref{exp:complexRIA}}}$ involving
@@
 the simple-role restriction because of $R_1\circ R_2\sqsubseteq R$.
-Consider the ontology $\mathcal{O}_{\text{ex}_\ref{exp:mg}}$
+Consider the ontology $\mathcal{O}_{\text{ex}_{\ref{exp:mg}}}$
 in Example~\ref{exp:mg} again. The role $R$ is a non-simple role, while $S$ is a simple role.
-Thus, $\mathcal{O}_{\text{ex}_\ref{exp:mg}}$ follows the simple-role restriction. All the implicit nodes
-in $\mathcal{G}_{\text{ex}_\ref{exp:mg}}$ have corresponding SWD paths in the first iteration.
-Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{\text{ex}_\ref{exp:mg}}$ by Algorithm~$\mathsf{A}_{\text{opt}}$.
+Thus, $\mathcal{O}_{\text{ex}_{\ref{exp:mg}}}$ follows the simple-role restriction. All the implicit nodes
+in $\mathcal{G}_{\text{ex}_{\ref{exp:mg}}}$ have corresponding SWD paths in the first iteration.
+Thus, `path twisting' cannot occur when materializing $\mathcal{O}_{\text{ex}_{\ref{exp:mg}}}$ by Algorithm~$\mathsf{A}_{\text{opt}}$.
 \end{example}

### 2018-06-24 parallel-tractability-J-v9/response2.tex
revision of the constant time claims

@@
   their response, but I could not find any clue in those articles (one
-  of which is just a two page summary \textcolor{red}{I can also not
-    see why this reference is of any help. Maybe we should comment on
-    this? }). \textcolor{red}{For the second reference
-    \cite{Raymond95}, I can also not see where it talks about matrix
-    multiplication? Does this follow from what is written below
-    Def.~3.2.10?} Again, even under the assumption that there is an
+  of which is just a two page summary. Again, even under the assumption that there is an
   one-to-one correspondence between processors and rule instances, for
@@
 in this rule instantiation. Suppose that a processor can access the
-location of any atom in constant time. It can also check the applicability of
-a rule \emph{instantiation} in constant time.
+locations of the atoms in the corresponding rule instantiation in constant time.
+It can also check the applicability of a rule \emph{instantiation} in constant time.
 
@@
 processors and rule instantiations, and each processor can access the
-location of any atom \textcolor{red}{within a rule? atom here means
-  derived facts?} in constant time
-(given as the parallel assumption in Section~3.3). Since a processor
+locations of the atoms within the rule instantiation in constant time
+(given as the parallel condition in Section~3.3). Since a processor
 $p$ corresponds to a rule instantiation, e.g.,
-$B_1, \ldots, B_n \to H$, processor $p$ knowns the relationship among
+$B_1, \ldots, B_n \to H$, processor $p$ knows the relationship among
 $B_1, \ldots, B_n$ and $H$. Further, processor $p$ knows the locations
-of the nodes $B_1, \ldots, B_n$ and $H$ \textcolor{red}{within the
-  materialization graph? how?  by checking (in constant time) the
-  derived facts?}. Thus, it could check the
-derivability of $B_1, \ldots, B_n$ \textcolor{red}{Check the
-  derivability or whether the (ground) atoms have been derived?}, and add an edge from $B_i$ to $H$
-($1 \leq i \leq n$) in constant time instead of searching the whole
+of the nodes $B_1, \ldots, B_n$ and $H$ which are in the rule instantiation $B_1, \ldots, B_n \to H$.
+Thus, it could check whether the nodes $B_1, \ldots, B_n$ have been derived,
+and add an edge from $B_i$ to $H$ ($1 \leq i \leq n$) in constant time instead of searching the whole
 graph $G$.
@@
 2) How to establish such a one-to-one correspondence between processors
-and rule instantiations and the constant-time access to each atom for processors?
+and rule instantiations and the constant-time access to atoms for processors?
 
@@
 In our case, the one-to-one correspondence between processors and rule
-instantiations and the constant-time access to each node can also be
+instantiations and the constant-time access to the atoms within the corresponding
+rule instantiations can also be
 established by PRAM similarly to the above simulation procedure.
 
-\textcolor{red}{We have added the above argumentation also to the
-  paper. (needed?, TBD) \emph{Rephrase the relevant paragraphs in a brief way?}}
+Since we focus on the parallel tractability of ontology materialization,
+we did not explain the constant time claims in detail.
+We use `\emph{the parallel condition}' in Section~3.3 to directly
+argue that a one-to-one correspondence between processors
+and rule instantiations and the constant-time access to atoms for processors
+can be established. We have added the key references and referred the readers
+to the details.
 
@@
 
-\textcolor{red}{The argumentation for this claim is similar to the one
-  given above. (?) Is it? Can we simply reply like that?}
+Algorithm~$\mathsf{A}_{\text{opt}}$ also works on the parallel condition.
+That is each processor $p$ corresponds to a rule instantiation, e.g., $B_1,\ldots,B_n\rightarrow H$,
+and processor $p$ can access the locations of nodes $B_1,\ldots,B_n, H$ in constant time.
+In order to compute $S_{\!\textit{\tiny rch}}$, processor $p$ should check the derivability
+of nodes $B_1,\ldots,B_n, H$. If only node $B_i$ ($i\in\{1,\ldots n\}$) and node $H$
+are still not derived, then processor $p$ creates a pair $(B_i, H)$ in $S_{\!\textit{\tiny rch}}$.
+The other elements in $S_{\!\textit{\tiny rch}}$ are similarly computed.
+On the parallel condition, the above procedure occupies constant time as well as checking
+the applicability of a rule instantiation.
+We have added the above content to make the claim that computation of $S_\text{rch}$ costs
+constant time clearer.
+The procedure of updating $G$ is similar to that of Algorithm~$\mathsf{A}_{\text{bsc}}$.
 

### 2018-06-25 parallel-tractability-J-v9/parallelTractabilityDatalog.tex
comma added, phrasing question

@@
 Algorithm~$\mathsf{A}_{\text{opt}}$ also works on the parallel condition.
-That is each processor $q$ corresponds to a rule instantiation, e.g., $B_1,\ldots,B_n\rightarrow H$,
+That is, each processor $q$ corresponds to a rule instantiation, e.g., $B_1,\ldots,B_n\rightarrow H$,
 and processor $q$ can access the locations of nodes $B_1,\ldots,B_n, H$ in constant time.
@@
 The other elements in $S_{\!\textit{\tiny rch}}$ are similarly computed.
-It is obvious that the above procedure occupies constant time as well on the parallel condition.
+It is obvious that the above procedure requires constant time as well on the parallel condition.
 Thus, in \ref{alg3:updateG}, the phases of

### 2018-06-25 parallel-tractability-J-v9/response2.tex
comma added, phrasing question

@@
 Algorithm~$\mathsf{A}_{\text{opt}}$ also works on the parallel condition.
-That is each processor $p$ corresponds to a rule instantiation, e.g., $B_1,\ldots,B_n\rightarrow H$,
+That is, each processor $p$ corresponds to a rule instantiation, e.g., $B_1,\ldots,B_n\rightarrow H$,
 and processor $p$ can access the locations of nodes $B_1,\ldots,B_n, H$ in constant time.
@@
 The other elements in $S_{\!\textit{\tiny rch}}$ are similarly computed.
-On the parallel condition, the above procedure occupies constant time as well as checking
-the applicability of a rule instantiation.
-We have added the above content to make the claim that computation of $S_\text{rch}$ costs
+Under the parallel condition, the above procedure uses constant time as well as checking
+the applicability of a rule instantiation. \textcolor{red}{BG: I
+  cannot parse the previous sentence, in particular the `as well as
+  checking\ldots' part.}
+We have added the above arguments \textcolor{red}{to the paper?} to
+make the claim that the computation of $S_\text{rch}$ costs
 constant time clearer.

### 2018-06-26 parallel-tractability-J-v9/response2.tex
revised response

@@
 The other elements in $S_{\!\textit{\tiny rch}}$ are similarly computed.
-Under the parallel condition, the above procedure uses constant time as well as checking
-the applicability of a rule instantiation. \textcolor{red}{BG: I
-  cannot parse the previous sentence, in particular the `as well as
-  checking\ldots' part.}
-We have added the above arguments \textcolor{red}{to the paper?} to
+The main work of the above procedure is to check the derivability
+of the nodes in the processed rule instantiation, which is the same as that of
+checking the applicability of the rule instantiation.
+Under the parallel condition, the above procedure also uses constant time.
+We have added the above arguments to the paper to
 make the claim that the computation of $S_\text{rch}$ costs
